### 2019-07-03 paper.tex
materials and methods

% GigaScience template
\documentclass[a4paper,num-refs]{oup-contemporary}

\journal{gigascience}

%%%% Packages %%%%
\usepackage{siunitx}
\usepackage{minted} % Used for JSON highlighting
\usepackage{algpseudocode} % Algorithmic environment
\usepackage{xspace}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{graphicx}
\usepackage{algorithm}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{listings}
\usepackage{verbatim}
\usepackage{makecell}
\usepackage[flushleft]{threeparttable}

%%%% Commands %%%%
\newcommand{\todo}[1]{\color{red}\textbf{TODO:}#1\color{black}}
\newcommand{\note}[2]{\color{blue}Note: #1\color{black}}
\newcommand{\reprozip}[0]{ReproZip}

\title{Use of Containers and Security threat to Clusters}

\begin{document}

\author[1]{Bhupinder Kaur}
\author[1]{Aiman Latif Hanna}
\author[1]{Tristan Glatard}

\affil[1]{Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada}

\maketitle

\begin{abstract}

Today, containers, which provide operating system level virtualization, are very
popular. This is due to the need for fast development cycles, continuous deliv-
ery, and cost reduction of infrastructure. Moreover, demand for an isolated en-
vironment adds on to the popularity of containers. Indeed, containers accelerate
development cycles as compared to virtual machines and provide near-native performance.
Containers are isolated from each other but they share the host kernel. If the host
is compromised, all containers running on it are at risk. In this paper, we pre-
cisely study the security implications of containers. This includes the study of
vulnerabilities in container images, Linux kernel, and in the network. Here, we
first provide an introduction of containers, review of container’s security, and
later, we discuss how these security loopholes can be a risk to clusters.
\end{abstract}

\begin{keywords}
Containers; Docker; Singularity; Security; 
Clusters.
\end{keywords}

\section{Introduction}

Containers are very lightweight, flexible, and more resource-efficient than virtual
machines. They provide an operating system (OS) level virtualization, which
removes the overhead of having an extra OS layer. However, containers tightly
integrate with the host due to the sharing of the kernel, which raises security
concerns. Linux Containers (LXC) were introduced in 2008 and gained advantage 
over other Linux-based projects due to the integration of virtualization features 
into the upstream Linux kernel, which removed the need of applying patches to
Linux kernel and recompiling. LXC relies on cgroups and namespaces features
of the Linux kernel. Cgroups control the usage of system resources (memory, CPU,
network, etc) among a group of processes. Namespaces define what a process can
see by providing an isolated view of the operating system.

Later in 2013, Docker, which is an extension of LXC capabilities, was introduced.
Docker is a portable container engine used to pack an application
alongwith all its dependencies and libraries. The packed application is known as
a Docker image and it can be run on any Linux server. As Docker is also based
on LXC it also relies on cgroups for limiting resources and namespaces for
container isolation. All Docker containers are managed by the Docker engine
which is knows as Docker daemon. It is a service that runs on the host operating
system and requires root access to operate. Docker containers are
spawned as children of root-owned Docker daemon. Therefore,
users can gain escalated privileges by coercing Docker daemon,
which creates important security risks in shared environments. As a conse-
quence, Docker is usually not supported in multi-user environments.

Couple of years later, Singularity was introduced in 2016 with the main goal
of providing support for multi-user environment.
It offers mobility of compute by facilitating portable environments through 
a single image file, which makes Singularity containers different from 
Docker’s layered containers. Singularity takes snapshot, locks, and 
archives the developed application, which is known as Singularity image
Once Singularity image is created, it is hashed by using SHA256 hashing. 
Hence, it cannot be changed once it is created, consequently, it can be 
used for reproducing the results of scientific experiments.

Mobility of compute is defined as creating and maintaining a workflow on
a local machine that can be easily ported on other hosts, Linux distributions,
and/or cloud service providers. To achieve this, Singularity packs everything
that is required for the application to run in a distributable image. Then that
image can be copied, archived, and shared. Moreover, Singularity containers
are easily portable across different versions of the C library and different kernel
implementations.
Same features of Singularity, which are used for mobility of compute, facil-
itate reproducibility as well. Hash of the image is also stored along with the
image. All Singularity images can be stored at a central place is known as
Singularity hub and Docker images can be stored at Docker hub.

The remainder of this article describes security concerns of containers
and their chances of being exploited on clusters. It closes on a discussion
of ten simple rules that can be followed to release secure container images
for use in clusters.

\begin{figure}
\centering
        \includegraphics[width=\columnwidth]{Figures/virtualization.png}
        \caption{Architecture of Container-based
                Virtualization}
	\label{virtualization}
\end{figure}

\section{Container's Security Review}

In spite of the popularity of containers, there are various security concerns
as well. We categorize security of containers in two broad categories i.e container's 
internal security and security provided by the host which is known as
host hardening. In this article, we mainly focus on security concerns of 
Docker and Singularity containers as both are currently more popular than other 
OS-level virtualizations.

\subsection{Container's Internal Security}

We examine the internal security of containers based on the requirements given by
Reshetova et al.,2014 for comparing the security of a number of OS-level
virtualization techniques. According to this paper, an OS-level virtualization
technique security can be analyzed from its isolation from the host machine and from 
the technique used by it to limit resources. Apart from that, in this section, we discuss various security 
concerns added by vulnerabilities that are present in Docker images.

Isolation of containers from the host can be of different categorize such as process isolation, filesys-
tem isolation, device isolation, IPC isolation, network isolation. In this section, we discuss how
much justice is done to these isolations by Docker and Singularity containers.

\subsubsection{Process Isolation}

The main goal of process isolation is to prevent one container process from
seeing or interfering with another container process. In other words, it limits
9the permissions and visibility of a container process to processes running in other
containers. Docker achieves this goal through the use of namespaces in the Linux
kernel. For this purpose, Docker uses PID namespaces which isolate a process
with particular process ID from the host and other containers. Provided that,
it becomes difficult for an attacker to see processes running in other containers,
hence harder to attack them [24]. In contrast to the Docker, the PID namespace
is not isolated from the host by default in Singularity because it’s main goal is
to provide mobility of compute and reproducibility, not full isolation. But if
there is a need the user can separate the PID namespace using a command line
(or environment variable) setting.

\subsubsection{Filesystem Isolation}

Filesystem isolation is required to prevent illegitimate access to filesystems of
the host and containers. Docker uses filesystem namespaces, also called mount
namespaces, for achieving this goal. Filesystem namespaces hide filesystems
of the host and containers from other containers. However, some of the kernel
filesystems are not namespaced, so Docker containers mount them for operation,
for example, /sys, /proc/sys, /proc/sysrq - trigger, /proc/irq, and /proc/bus
[25]. This causes security concerns as Docker containers are directly able to
access host filesystems. Consequently, Docker provides two filesystem protection
mechanisms. First, Docker gives read-only permissions to containers for these
filesystems. Second, containers are not allowed to remount any filesystem within
containers. Additionally, Docker offers a copy-on-write filesystem mechanism,
which allows containers to write to their specific filesystems and changes are not
visible to other containers. On the other hand, files in Singularity containers
are not isolated using filesystem namespaces because a user inside a Singularity
container is the same user outside the container.

\subsubsection{Device Isolation}

Applications and kernel access devices through special files known as device
nodes. It is very crucial to limit the set of devices nodes that containers can
access. This is primarily because an attacker can own the whole system by
gaining access to some important device nodes such as /dev/mem, /dev/sd*,
or /dev/tty. Docker uses the Device Whitelist Controller [26] feature of con-
trol groups to limit the set of devices that a Docker container can see and use.
Additionally, Docker starts containers with nodev which prevents the use of
already created device nodes inside the image. Furthermore, Docker does not
allow containers to create new device nodes. However, some of the important
device nodes cannot be namespaced such as /dev/mem, /dev/sd* and kernel
modules. Direct access to these device nodes by containers possess serious se-
curity concerns. Besides that, if a Docker container is executed in privileged
mode then it gets access to all devices. Conversely, in Singularity devices are
also not isolated between the host and the container similar to filesystem due to
same user inside and outside the container. In Singularity by default the user
is allowed to interface all the devices of the host.
\subsubsection{IPC Isolation}

IPC is a set of objects through which processes communicate with each other
such as, shared memory segments, semaphores, message queues, and POSIX
message queues. IPC isolation is needed to prevent containers from accessing
or modifying data belonging to other containers, which is transmitted through
these objects. Docker utilizes IPC namespaces to assign an IPC namespace
to each container. Process in one IPC namespace cannot read or write IPC
resources of another IPC namespace.

\subsubsection{Network Isolation}

Isolation of containers network is very important to prevent network-based
attacks such as address resolution protocol (ARP) spoofing and Man-in-the-
Middle (MitM) Attack [27]. ARP spoofing is an attack, which associates the
attacker’s media access control (MAC) address with the internet protocol (IP)
address of another host. ARP is a stateless protocol and hosts save all ARP
replies even if they had not sent any ARP request for it [28], which becomes
a reason of attack. So, the host that has spoofed ARP response is not able to
verify whether it belongs to legitimate host or attacker and hence, it starts send-
ing packets at attacker’s MAC address. Docker uses network namespaces [29]
to isolate the network of Docker containers. Therefore, each Docker container
has its different IP address, IP routing tables, network devices, etc. Conse-
quently, Docker containers interact through the network interfaces with each
other as well as with the host [30]. On the contrary, all containers share the
same network bridge, which makes Docker vulnerable to ARP spoofing attack.
In addition to that, the Docker network bridge forwards all incoming packets
without any kind of filtering which makes it vulnerable to Mac flooding.
In Singularity, by default the container share network
with the host.

Network is also used to pull container images from the central repository.
Images are pulled in compressed format and then uncompressed on the host and
run into containers. This may include storing and processing potentially
untrusted code in images by container engine. The source code can
be tampered during transfer or at the source. If some part of the network
is compromised, an attacker can replace an image with malicious image, and
that image gets downloaded on the host. As the image is in a compressed
format, the attacker can cleverly craft the image (i.e. all zeros) and when it
gets decompressed on the host it can fill whole storage of host causing denial-
of-service (DoS) attack. Other possible attacks are code injection or replay
attacks. Additionally, the malicious image can be uploaded to the image
repository by an adversary. That image can be downloaded by millions of users infecting
millions of machines.

For mitigation of these attacks, Docker introduced content trust which al-
lowed signing images before pushing to Docker Hub. But this content trust can
be disabled and thus disabling image signature check. Another issue is with au-
tomated build and webhooks, which are described earlier, where compromised
GitHub account can lead to the execution of malicious code. According to the
experiment performed in [13] the malicious code was put in production within
5 minutes and 30 seconds of commit on GitHub. The Content trust provides
an environment where a single entity is trusted but in this case, trust is divided
among several external entities.
\subsubsection{Limiting of Resources}

A DoS attack occurs when intended users are not able to use the system or
network resources [32]. To launch DoS, the attacker floods targeted host or
network traffic with superfluous requests to overload the systems. Consequently,
the target crashes, hence disrupting normal execution of the system. To solve
this issue Docker uses cgroups. Cgroups restrict the amount of resources (CPU,
memory, and disk I/O) that are used by Docker containers, thus all containers
get their fair amount of resources.

\subsection{Image vulnerabilities}

There can be vulnerabilities present inside the image itself when it is downloaded
from image repository. According to the technical report [33] over 30\% official im-
ages have high-priority common vulnerabilities and exposures (CVE) identifiers
(IDs) and around 64\% have high or medium level CVE vulnerabilities. This
technical report also states that Docker images with the latest tag also have
vulnerabilities. These vulnerabilities are due to the outdated packages con-
tained by images which can be due to the use of an old base image or due to
12outdated code pulled during build. Vulnerabilities can also be present 
inside Singularity images as well. As these Docker images can also be
wrapped in Singularity images which automatically transfers vulnerabilities
between images.
Docker introduced Docker security scanning through which users can scan
images to check whether they contain vulnerability or not. However, this scan-
ning is limited to only private repositories and it is paid. The scan traverses
all layers of the image and then identifies packages and software in those layers.
Further, it checks vulnerabilities in these software components by taking their
Secure Hash Algorithms (SHAs) and then comparing against a standard list of
CVEs. This scan can take up to 1 to 24 hours depending on the image sizes.
Additionally, this scanning technique do not detect vulnerabilities which are not
mentioned in the standard CVE database.

\subsection{Host Hardening}

Out-of-the-box security provided by the Linux kernel to secure the host from
containers is known as host hardening. Linux provides Linux capabilities and
Linux Security Modules (LSM) to harden the security of the host system. Linux
capabilities divide the privileges of superuser into pieces and assign a subset of
these capabilities to specific processes. Whereas, LSM provides a framework for
Linux to support various security modules. Currently, three security modules
are officially integrated with Linux kernel which includes Security Enhancement
to the Linux system (SELinux), AppArmor, and Seccomp. Out of these three, 
only SELinux and AppArmor are supported by Docker. Docker integrates with 
Seccomp only if LXC are used.

\subsubsection{Linux Capabilities}

According to the main page of Linux capabilities, traditionally Unix systems
categorized processes as privileged processes and unprivileged processes. Priv-
ileged processes are root users with zero user id (UID), whereas unprivileged
users are normal users with nonzero UID. Privileged processes are exempted
from permission check whereas, unprivileged processes are liable to full per-
mission checks. Linux divides the privileges of superuser into different pieces,
known as capabilities, which can be independently enabled or disabled. As a
result, Docker can disable some of the capabilities of containers, thus improv-
ing the security of the system. As Docker containers share the kernel with the
host so, most of their tasks are done by the host. As a consequence, disabling
some of the capabilities in Docker containers do not affect their functionality.
For example, CAP\_NET\_ ADMIN capability allows configuration of the network
which can be disabled in Docker containers because all network configurations
are handled by Docker daemon. By default, most of the Linux capabilities are
disabled when Docker container is started, in order to secure the host system
from attackers.

\subsubsection{Linux Security Modules}

SELinux and AppArmor are both Media Access Control (MAC) solutions for 
enhancing security of Linux systems. MAC strongly separates all 
applications, which in turn decreases potential damage if an 
application is compromised. Unfortunately, Security provided by these modules 
is limited due to generic nature of profiles
provided by these security modules. For example, default SELinux profile
assigns same domain to all Docker containers which helps in protecting host from
containers but not containers from containers. Similarly, default Apparmor
profile provide full access of network system, file system and capabilities to
Docker containers. Solution can be writing specific profiles for the individual
containers.

\section{Materials and Methods}

\subsection{Compute Canada Clusters}
Compute Canada is a national High Performance Computing (HPC) research platform.
It integrates with four regional partners namely ACENET, Calcul Québec, Compute
Ontario, and WestGrid for providing local support.
Compute Canada uses Slurm Workload Manager to schedule jobs.
Control groups are used to limit number of resources that can be used
by a particular user.
Compute Canada do not support Docker as its default configuration
runs containers as root. Whereas, Compute Canada supports Singularity
because it removes the drawback of Docker.
Compute Canada uses Lustre shared file system to provide high
bandwidth to its users.

\subsection{Container Engine: Singularity}

Singlarity, which came in 2016, provides operating system (OS)level.
It offers mobility of compute by facilitating portable environments 
through a single image file. Once Singularity image
is created, it is hashed by using SHA256 hashing. Hence, it cannot be changed
once it is created, consequently, it can be used for reproducing the results of
scientific experiments. Singularity was introduced with the main goal of pro-
viding support for multi-user environment. Main features provided by
Singularity are mobility of compute and reproducibility.
Mobility of compute is defined as creating and maintaining a workflow on
a local machine that can be easily ported on other hosts, Linux distributions,
and/or cloud service providers. To achieve this, Singularity packs everything
that is required for the application to run in a distributable image. Then that
image can be copied, archived, and shared. Moreover, Singularity containers
are easily portable across different versions of the C library and different kernel
implementations [16].
Same features of Singularity, which are used for mobility of compute, facil-
itate reproducibility as well.

\subsection{Container Image Formats}

A container image is a package that contains the application alongwith its
required dependencies and libraries.
Nowadays, two most popular containerization tools used are Docker and Singularity.
Both have different image format.

\subsubsection{Docker Image Format}

There are two ways to create Docker image. The first is to use an existing
Docker image as a base image and then build a new image from that one, by
making changes in the filesystem, which is saved as a new layer of the
Docker image. The second way is to build a new Docker image from scratch.
Docker images are organized as a series of layers which are stacked on top
of each other. Each layer consists of a filesystem diff that is introduced
due to the changes made on the layer below it. All layers of the Docker image
are identified by unique layerIDs. All these layers stacked together gives a
unified and complete view of a Docker image. These layers are
compressed into a single image and can be pushed to the Docker Hub.

\subsubsection{Singularity Image Format}

Singularity takes snapshot, locks, and archives the developed application, which
is known as Singularity image. Due to image hashing, Singularity does not
contain image layers, unlike Docker images. While publishing experimental
results, authors can also publish Singularity image along with its hash, which
allow other researchers to verify results.

\subsection{Application frameworks}

Following are the application frameworks that are using containers
on HPC clusters.

\subsubsection{Boutiques}

Boutiques framework is used to publish, integrate, and execute third-party
applications across CBRAIN platform automatically. Boutiques framework is
employed by CONP. With Boutiques, the command-line of the application is
described through a flexible template, which is called descriptor. Descriptor de-
scribes the input that is required by the application and the output it produces.
It points to a Docker or Singularity image, where the application is installed.
Developers of the application produce Boutiques descriptor, and stores it along
with the application. Boutiques descriptor are described in JSON format. There
is a set of core tools which help in constructing, validating and executing bou-
tiques descriptors. During the application run-time, the execution platform
builds a command line by using input values given by the user and boutiques
descriptor of the application.

\subsubsection{Brain Imaging Data Structure (BIDS)}

 BIDS is a framework

\section{Containers on Clusters}

In this section, we discuss Canadian Open Neuroscience Platform (CONP) which is 
real use case of containers that involves running containers on clusters. 
CONP is a national platform
for sharing neuroscience research data and aims at creating an interactive inter-
face for neuroscientists and clinical neuroscience. The main goal of the CONP
platform is to store, process, and distribute massive amounts of data produced
by modern neuroscience. The effective data sharing by CONP increases data
accessibility and re-usability. Through CONP, neuroscientists remain updated
of on-going and past research efforts, which avoids unnecessary duplication.
CONP uses Compute Canada cluster for providing its services. So we take
this real use case to explain the effect of image vulnerabilities on clusters.

\sections{Cluster}

A cluster is an arrangement of multiple computers together in particular topol-
ogy to increase computational power, memory and reduce processing time than
personal computer. When a single computer becomes insufficient to use due
to the massive amount of data, cluster of computers can be used to run jobs
in parallel. Most importantly, clusters are the resources for high performing
computing (HPC). HPC refers to the use of clusters at large scale and parallel
processing techniques to solve large and difficult problems. Research, aca-
demics, and IT world share clusters for running jobs. Due to the wide use and
popularity of clusters, its security becomes a main concern. Below is the real
use case of clusters that deal with containers and might be at risk.

\bibliographystyle{plain}
\bibliography{bibliography}

\end{document}

### 2019-07-05 paper.tex
Repronim

@@
 
-\title{Use of Containers and Security threat to Clusters}
+\title{Risks of Running Vulnerable Container Images for Data Analysis on HPC
+Clusters}
 
@@
 
+\author[1]{Aiman Latif Hanna}
 \author[1]{Bhupinder Kaur}
-\author[1]{Aiman Latif Hanna}
 \author[1]{Tristan Glatard}
@@
 
-\begin{abstract}
-
-Today, containers, which provide operating system level virtualization, are very
-popular. This is due to the need for fast development cycles, continuous deliv-
-ery, and cost reduction of infrastructure. Moreover, demand for an isolated en-
-vironment adds on to the popularity of containers. Indeed, containers accelerate
-development cycles as compared to virtual machines and provide near-native performance.
-Containers are isolated from each other but they share the host kernel. If the host
-is compromised, all containers running on it are at risk. In this paper, we pre-
-cisely study the security implications of containers. This includes the study of
-vulnerabilities in container images, Linux kernel, and in the network. Here, we
-first provide an introduction of containers, review of container’s security, and
-later, we discuss how these security loopholes can be a risk to clusters.
-\end{abstract}
-
-\begin{keywords}
-Containers; Docker; Singularity; Security; 
-Clusters.
-\end{keywords}
-
-\section{Introduction}
-
-Containers are very lightweight, flexible, and more resource-efficient than virtual
-machines. They provide an operating system (OS) level virtualization, which
-removes the overhead of having an extra OS layer. However, containers tightly
-integrate with the host due to the sharing of the kernel, which raises security
-concerns. Linux Containers (LXC) were introduced in 2008 and gained advantage 
-over other Linux-based projects due to the integration of virtualization features 
-into the upstream Linux kernel, which removed the need of applying patches to
-Linux kernel and recompiling. LXC relies on cgroups and namespaces features
-of the Linux kernel. Cgroups control the usage of system resources (memory, CPU,
-network, etc) among a group of processes. Namespaces define what a process can
-see by providing an isolated view of the operating system.
-
-Later in 2013, Docker, which is an extension of LXC capabilities, was introduced.
-Docker is a portable container engine used to pack an application
-alongwith all its dependencies and libraries. The packed application is known as
-a Docker image and it can be run on any Linux server. As Docker is also based
-on LXC it also relies on cgroups for limiting resources and namespaces for
-container isolation. All Docker containers are managed by the Docker engine
-which is knows as Docker daemon. It is a service that runs on the host operating
-system and requires root access to operate. Docker containers are
-spawned as children of root-owned Docker daemon. Therefore,
-users can gain escalated privileges by coercing Docker daemon,
-which creates important security risks in shared environments. As a conse-
-quence, Docker is usually not supported in multi-user environments.
-
-Couple of years later, Singularity was introduced in 2016 with the main goal
-of providing support for multi-user environment.
-It offers mobility of compute by facilitating portable environments through 
-a single image file, which makes Singularity containers different from 
-Docker’s layered containers. Singularity takes snapshot, locks, and 
-archives the developed application, which is known as Singularity image
-Once Singularity image is created, it is hashed by using SHA256 hashing. 
-Hence, it cannot be changed once it is created, consequently, it can be 
-used for reproducing the results of scientific experiments.
-
-Mobility of compute is defined as creating and maintaining a workflow on
-a local machine that can be easily ported on other hosts, Linux distributions,
-and/or cloud service providers. To achieve this, Singularity packs everything
-that is required for the application to run in a distributable image. Then that
-image can be copied, archived, and shared. Moreover, Singularity containers
-are easily portable across different versions of the C library and different kernel
-implementations.
-Same features of Singularity, which are used for mobility of compute, facil-
-itate reproducibility as well. Hash of the image is also stored along with the
-image. All Singularity images can be stored at a central place is known as
-Singularity hub and Docker images can be stored at Docker hub.
-
-The remainder of this article describes security concerns of containers
-and their chances of being exploited on clusters. It closes on a discussion
-of ten simple rules that can be followed to release secure container images
-for use in clusters.
-
-\begin{figure}
-\centering
-        \includegraphics[width=\columnwidth]{Figures/virtualization.png}
-        \caption{Architecture of Container-based
-                Virtualization}
-	\label{virtualization}
-\end{figure}
-
-\section{Container's Security Review}
-
-In spite of the popularity of containers, there are various security concerns
-as well. We categorize security of containers in two broad categories i.e container's 
-internal security and security provided by the host which is known as
-host hardening. In this article, we mainly focus on security concerns of 
-Docker and Singularity containers as both are currently more popular than other 
-OS-level virtualizations.
-
-\subsection{Container's Internal Security}
-
-We examine the internal security of containers based on the requirements given by
-Reshetova et al.,2014 for comparing the security of a number of OS-level
-virtualization techniques. According to this paper, an OS-level virtualization
-technique security can be analyzed from its isolation from the host machine and from 
-the technique used by it to limit resources. Apart from that, in this section, we discuss various security 
-concerns added by vulnerabilities that are present in Docker images.
-
-Isolation of containers from the host can be of different categorize such as process isolation, filesys-
-tem isolation, device isolation, IPC isolation, network isolation. In this section, we discuss how
-much justice is done to these isolations by Docker and Singularity containers.
-
-\subsubsection{Process Isolation}
-
-The main goal of process isolation is to prevent one container process from
-seeing or interfering with another container process. In other words, it limits
-9the permissions and visibility of a container process to processes running in other
-containers. Docker achieves this goal through the use of namespaces in the Linux
-kernel. For this purpose, Docker uses PID namespaces which isolate a process
-with particular process ID from the host and other containers. Provided that,
-it becomes difficult for an attacker to see processes running in other containers,
-hence harder to attack them [24]. In contrast to the Docker, the PID namespace
-is not isolated from the host by default in Singularity because it’s main goal is
-to provide mobility of compute and reproducibility, not full isolation. But if
-there is a need the user can separate the PID namespace using a command line
-(or environment variable) setting.
-
-\subsubsection{Filesystem Isolation}
-
-Filesystem isolation is required to prevent illegitimate access to filesystems of
-the host and containers. Docker uses filesystem namespaces, also called mount
-namespaces, for achieving this goal. Filesystem namespaces hide filesystems
-of the host and containers from other containers. However, some of the kernel
-filesystems are not namespaced, so Docker containers mount them for operation,
-for example, /sys, /proc/sys, /proc/sysrq - trigger, /proc/irq, and /proc/bus
-[25]. This causes security concerns as Docker containers are directly able to
-access host filesystems. Consequently, Docker provides two filesystem protection
-mechanisms. First, Docker gives read-only permissions to containers for these
-filesystems. Second, containers are not allowed to remount any filesystem within
-containers. Additionally, Docker offers a copy-on-write filesystem mechanism,
-which allows containers to write to their specific filesystems and changes are not
-visible to other containers. On the other hand, files in Singularity containers
-are not isolated using filesystem namespaces because a user inside a Singularity
-container is the same user outside the container.
-
-\subsubsection{Device Isolation}
-
-Applications and kernel access devices through special files known as device
-nodes. It is very crucial to limit the set of devices nodes that containers can
-access. This is primarily because an attacker can own the whole system by
-gaining access to some important device nodes such as /dev/mem, /dev/sd*,
-or /dev/tty. Docker uses the Device Whitelist Controller [26] feature of con-
-trol groups to limit the set of devices that a Docker container can see and use.
-Additionally, Docker starts containers with nodev which prevents the use of
-already created device nodes inside the image. Furthermore, Docker does not
-allow containers to create new device nodes. However, some of the important
-device nodes cannot be namespaced such as /dev/mem, /dev/sd* and kernel
-modules. Direct access to these device nodes by containers possess serious se-
-curity concerns. Besides that, if a Docker container is executed in privileged
-mode then it gets access to all devices. Conversely, in Singularity devices are
-also not isolated between the host and the container similar to filesystem due to
-same user inside and outside the container. In Singularity by default the user
-is allowed to interface all the devices of the host.
-\subsubsection{IPC Isolation}
-
-IPC is a set of objects through which processes communicate with each other
-such as, shared memory segments, semaphores, message queues, and POSIX
-message queues. IPC isolation is needed to prevent containers from accessing
-or modifying data belonging to other containers, which is transmitted through
-these objects. Docker utilizes IPC namespaces to assign an IPC namespace
-to each container. Process in one IPC namespace cannot read or write IPC
-resources of another IPC namespace.
-
-\subsubsection{Network Isolation}
-
-Isolation of containers network is very important to prevent network-based
-attacks such as address resolution protocol (ARP) spoofing and Man-in-the-
-Middle (MitM) Attack [27]. ARP spoofing is an attack, which associates the
-attacker’s media access control (MAC) address with the internet protocol (IP)
-address of another host. ARP is a stateless protocol and hosts save all ARP
-replies even if they had not sent any ARP request for it [28], which becomes
-a reason of attack. So, the host that has spoofed ARP response is not able to
-verify whether it belongs to legitimate host or attacker and hence, it starts send-
-ing packets at attacker’s MAC address. Docker uses network namespaces [29]
-to isolate the network of Docker containers. Therefore, each Docker container
-has its different IP address, IP routing tables, network devices, etc. Conse-
-quently, Docker containers interact through the network interfaces with each
-other as well as with the host [30]. On the contrary, all containers share the
-same network bridge, which makes Docker vulnerable to ARP spoofing attack.
-In addition to that, the Docker network bridge forwards all incoming packets
-without any kind of filtering which makes it vulnerable to Mac flooding.
-In Singularity, by default the container share network
-with the host.
-
-Network is also used to pull container images from the central repository.
-Images are pulled in compressed format and then uncompressed on the host and
-run into containers. This may include storing and processing potentially
-untrusted code in images by container engine. The source code can
-be tampered during transfer or at the source. If some part of the network
-is compromised, an attacker can replace an image with malicious image, and
-that image gets downloaded on the host. As the image is in a compressed
-format, the attacker can cleverly craft the image (i.e. all zeros) and when it
-gets decompressed on the host it can fill whole storage of host causing denial-
-of-service (DoS) attack. Other possible attacks are code injection or replay
-attacks. Additionally, the malicious image can be uploaded to the image
-repository by an adversary. That image can be downloaded by millions of users infecting
-millions of machines.
-
-For mitigation of these attacks, Docker introduced content trust which al-
-lowed signing images before pushing to Docker Hub. But this content trust can
-be disabled and thus disabling image signature check. Another issue is with au-
-tomated build and webhooks, which are described earlier, where compromised
-GitHub account can lead to the execution of malicious code. According to the
-experiment performed in [13] the malicious code was put in production within
-5 minutes and 30 seconds of commit on GitHub. The Content trust provides
-an environment where a single entity is trusted but in this case, trust is divided
-among several external entities.
-\subsubsection{Limiting of Resources}
-
-A DoS attack occurs when intended users are not able to use the system or
-network resources [32]. To launch DoS, the attacker floods targeted host or
-network traffic with superfluous requests to overload the systems. Consequently,
-the target crashes, hence disrupting normal execution of the system. To solve
-this issue Docker uses cgroups. Cgroups restrict the amount of resources (CPU,
-memory, and disk I/O) that are used by Docker containers, thus all containers
-get their fair amount of resources.
-
-\subsection{Image vulnerabilities}
-
-There can be vulnerabilities present inside the image itself when it is downloaded
-from image repository. According to the technical report [33] over 30\% official im-
-ages have high-priority common vulnerabilities and exposures (CVE) identifiers
-(IDs) and around 64\% have high or medium level CVE vulnerabilities. This
-technical report also states that Docker images with the latest tag also have
-vulnerabilities. These vulnerabilities are due to the outdated packages con-
-tained by images which can be due to the use of an old base image or due to
-12outdated code pulled during build. Vulnerabilities can also be present 
-inside Singularity images as well. As these Docker images can also be
-wrapped in Singularity images which automatically transfers vulnerabilities
-between images.
-Docker introduced Docker security scanning through which users can scan
-images to check whether they contain vulnerability or not. However, this scan-
-ning is limited to only private repositories and it is paid. The scan traverses
-all layers of the image and then identifies packages and software in those layers.
-Further, it checks vulnerabilities in these software components by taking their
-Secure Hash Algorithms (SHAs) and then comparing against a standard list of
-CVEs. This scan can take up to 1 to 24 hours depending on the image sizes.
-Additionally, this scanning technique do not detect vulnerabilities which are not
-mentioned in the standard CVE database.
-
-\subsection{Host Hardening}
-
-Out-of-the-box security provided by the Linux kernel to secure the host from
-containers is known as host hardening. Linux provides Linux capabilities and
-Linux Security Modules (LSM) to harden the security of the host system. Linux
-capabilities divide the privileges of superuser into pieces and assign a subset of
-these capabilities to specific processes. Whereas, LSM provides a framework for
-Linux to support various security modules. Currently, three security modules
-are officially integrated with Linux kernel which includes Security Enhancement
-to the Linux system (SELinux), AppArmor, and Seccomp. Out of these three, 
-only SELinux and AppArmor are supported by Docker. Docker integrates with 
-Seccomp only if LXC are used.
-
-\subsubsection{Linux Capabilities}
-
-According to the main page of Linux capabilities, traditionally Unix systems
-categorized processes as privileged processes and unprivileged processes. Priv-
-ileged processes are root users with zero user id (UID), whereas unprivileged
-users are normal users with nonzero UID. Privileged processes are exempted
-from permission check whereas, unprivileged processes are liable to full per-
-mission checks. Linux divides the privileges of superuser into different pieces,
-known as capabilities, which can be independently enabled or disabled. As a
-result, Docker can disable some of the capabilities of containers, thus improv-
-ing the security of the system. As Docker containers share the kernel with the
-host so, most of their tasks are done by the host. As a consequence, disabling
-some of the capabilities in Docker containers do not affect their functionality.
-For example, CAP\_NET\_ ADMIN capability allows configuration of the network
-which can be disabled in Docker containers because all network configurations
-are handled by Docker daemon. By default, most of the Linux capabilities are
-disabled when Docker container is started, in order to secure the host system
-from attackers.
-
-\subsubsection{Linux Security Modules}
-
-SELinux and AppArmor are both Media Access Control (MAC) solutions for 
-enhancing security of Linux systems. MAC strongly separates all 
-applications, which in turn decreases potential damage if an 
-application is compromised. Unfortunately, Security provided by these modules 
-is limited due to generic nature of profiles
-provided by these security modules. For example, default SELinux profile
-assigns same domain to all Docker containers which helps in protecting host from
-containers but not containers from containers. Similarly, default Apparmor
-profile provide full access of network system, file system and capabilities to
-Docker containers. Solution can be writing specific profiles for the individual
-containers.
-
 \section{Materials and Methods}
 
+In this section we summarize a particular use case of containers which is Canadian
+Open Neuroscience Platform (CONP). It is a national platform for sharing neuroscience
+research data and aims at creating an interactive interface for neuroscientists and
+clinical neuroscience. The main goal of the CONP platform is to store, process, and
+distribute massive amounts of data produced by modern neuroscience.
+Here, we summarize all the resources and software tools that are
+used by CONP to function.
+
 \subsection{Compute Canada Clusters}
+
 Compute Canada is a national High Performance Computing (HPC) research platform.
+It provides infrastructure and services for Advanced Research Computing (ARC).
+Its goal is to bring excellence, ease, and innovation in research of Canadian
+research institutions by providing storage, computing power, and required
+softwares to carry out research.
 It integrates with four regional partners namely ACENET, Calcul Québec, Compute
@@
 
-Following are the application frameworks that are using containers
+Following are the application frameworks in neuroscience that are using containers
 on HPC clusters.
@@
 
-Boutiques framework is used to publish, integrate, and execute third-party
-applications across CBRAIN platform automatically. Boutiques framework is
+Boutiques is a application sharing system. It is based on Linux containers
+and can be used to publish, integrate, and execute third-party
+applications across different platforms automatically. Boutiques framework is
 employed by CONP. With Boutiques, the command-line of the application is
-described through a flexible template, which is called descriptor. Descriptor de-
-scribes the input that is required by the application and the output it produces.
+described through a flexible template, which is called descriptor. Descriptor
+describes the input that is required by the application and the output it produces.
 It points to a Docker or Singularity image, where the application is installed.
@@
 
-\subsubsection{Brain Imaging Data Structure (BIDS)}
+\subsubsection{Brain Imaging Data Structure (BIDS) Apps}
 
- BIDS is a framework
+BIDS Apps is a framework designed to share and execute neuroimaging
+analysis pipelines. It improves usability, accesibility, and reproducibility
+of different operating system users as well as HPC users.
 
-\section{Containers on Clusters}
+\subsubsection{ReproNim}
 
-In this section, we discuss Canadian Open Neuroscience Platform (CONP) which is 
-real use case of containers that involves running containers on clusters. 
-CONP is a national platform
-for sharing neuroscience research data and aims at creating an interactive inter-
-face for neuroscientists and clinical neuroscience. The main goal of the CONP
-platform is to store, process, and distribute massive amounts of data produced
-by modern neuroscience. The effective data sharing by CONP increases data
-accessibility and re-usability. Through CONP, neuroscientists remain updated
-of on-going and past research efforts, which avoids unnecessary duplication.
-CONP uses Compute Canada cluster for providing its services. So we take
-this real use case to explain the effect of image vulnerabilities on clusters.
+ReproNim: A Center for Reproducible Neuroimaging Computation is a vision
+to help neuroscientists in reproducing neuroimaging research.
 
-\sections{Cluster}
+\subsection{Container Images Used}
 
-A cluster is an arrangement of multiple computers together in particular topol-
-ogy to increase computational power, memory and reduce processing time than
-personal computer. When a single computer becomes insufficient to use due
-to the massive amount of data, cluster of computers can be used to run jobs
-in parallel. Most importantly, clusters are the resources for high performing
-computing (HPC). HPC refers to the use of clusters at large scale and parallel
-processing techniques to solve large and difficult problems. Research, aca-
-demics, and IT world share clusters for running jobs. Due to the wide use and
-popularity of clusters, its security becomes a main concern. Below is the real
-use case of clusters that deal with containers and might be at risk.
+\subsection{Image Update Process}
+
+If there exist vulnerabilities in the container image, then there are two ways
+to proceed, either not to run that image at all, or run only after updating the
+packages that have vulnerabilities. The latter option effects the reproducibility
+of the image, which means that the image cannot be used to verify research
+findings of other scientists. An alternative approach can be to trim unnecessary
+packages from images, which in turn reduces the number of vulnerabilities
+present in images.
+
+\subsection{Scanning tools used}
+
+There are various scanning tools that are available for scanning container
+images like Vuls, Clair, ClairScanner, Anchore, Dagda, etc. Out of them we
+took Anchore and Vuls for our experiments to scan container
+images which are used by the above discussed application frameworks.
+
+\subsubsection{Anchore}
+
+Anchore is an end-to-end container security, and open-source compliance plat-
+form. Anchore is a static scanning tool that analyses container images and
+lists operating system packages,
+unofficial packages, configuration files, and language modules [58]. In other
+words, Anchore is a set of tools, which users can employ for scanning container
+images and applying custom policies to them. It provides visibility and trans-
+parency of the container environment. Anchore offers services in two ways:
+Anchore Engine and Anchore Engine Command Line Interface (CLI).
+Anchore Engine is available as a Docker image, which is available on Docker
+Hub. Anchore Engine CLI provides command line interface in addition to An-
+chore Engine REST API. Anchore Engine CLI can be installed directly on the
+host and used to inspect images.
+
+\subsubsection{Vuls}
+
+Vuls is an open-source vulnerability scanner for Linux/FreeBSD, written in Go
+language. It is an agentless vulnerability scanner and uses various
+vulnerability databases listed in 4.4a. Using dynamic scanning technique, it offers
+remote and local scan. Remote scan involves setting up only one machine, to
+which other target servers are connected via SSH. Local scan involves running
+the scan on the target server itself. Further, Vuls offer fast scan, fast root scan,
+and deep scan.
+Fast scan is performed without root privileges, whereas fast root scan is
+performed with root privileges. The latter also uses checkrestart utility to de-
+tect processes that are updated but not yet restarted because if they are not
+restarted, updates are not effective. So fast root scan also detects these pro-
+cesses. Both fast scan and fast root scan are performed offline without Internet
+access, and put almost no load on the scan target server. Deep scan uses
+root privileges for scanning, and is used to get a more detailed scan. It checks
+changelogs, which puts more load on the target server. As shown in Figure 4.3
+it is clear that vulnerability detection time of Vuls is much better than An-
+chore. Vuls tool uses dynamic scanning, so the scanning time does not depend
+on the image size.
+Graph 4.5 shows percentage of vulnerabilities that are
+covered by Vuls and Anchore tools. This graph can be explained with the help
+of List 4.4, which shows vulnerability databases that are referred, by both Vuls
+and Anchore. Anchore covers less percentage of vulnerabilities as compared
+to Vuls because Anchore relies mainly on vulnerability databases published by
+Linux distributions, whereas Vuls additionally refers to another sources such as
+databases from Japan, US-CERT, etc.
+
+\subsection{CBRAIN}
+
+Canadian Brain Imaging Research Platform (CBRAIN) is a web portal that is used
+by CONP to exploit services of Compute Canada. CBRAIN is a collaborative
+neuroimaging research platform that is active in production since 2009. CBRAIN
+provides transparent access to various distributed storage sites and computing
+resources across the world. CBRAIN’s infrastructure consists of three main
+layers, namely access layer, service layer, and infrastructure layer. The access
+layer is for CBRAIN users, and can be accessed through any modern browser or
+RESTful API [42]. The service layer consists of CBRAIN portal, which contains
+metadata and databases. It provides information about users, their permissions,
+resources etc. The infrastructure layer consists of data resources and computing
+resources, which are connected through a network.
 

### 2019-07-15 paper.tex
two sections

@@
 
-\author[1]{Aiman Latif Hanna}
 \author[1]{Bhupinder Kaur}
+\author[1]{Aiman Hanna}
 \author[1]{Tristan Glatard}
@@
 
+\begin{keywords}
+Containers; Security; Docker; Singularity; Neuroimaging.
+\end{keywords}
+
+\section{Introduction}
+
+Virtualization, which was introduced in 1960s, refers to the creation of a virtual
+version of something. Its meaning has evolved and took different forms since then, for
+instance hardware virtualization, containerization, desktop virtualization, etc.
+Here, in this paper our main focus is on containerarization and its security concerns,
+specifically in neuroimaging field.
+Containers, which provide operating system (OS) level virtualization, are very
+popular. This is due to the need for fast development cycles, continuous delivery,
+and cost reduction of infrastructure. Moreover, demand for an isolated
+environment adds on to the popularity of containers. Indeed, containers accelerate
+development cycles as compared to virtual machines and provide near-native performance.
+They are very lightweight, flexible, and more resource-efficient than virtual
+machines. By providing OS level virtualization they
+removes the overhead of having an extra OS layer.
+
+Although Linux Containers (LXC) and other alternatives such as Rocket were already
+available, container-based virtualization gained a lot of interest when Docker was
+introduced in 2013~\cite{gantikow2016providing}. Docker makes container's use more straightforward. However, there
+are few limitations of Docker. For example, it is not supported by shared High Performance
+Computing (HPC) environments because its default configuration runs containers
+as root. Secondly, Docker containers cannot be used for reproducibility as Docker
+images can be updated, and hence losing specific package versions required for
+reproducing scientific results. Consequently, Singularity was introduced in 2016 with the main
+goal of removing drawbacks of Docker. Singularity was developed mainly to
+support HPC environments and to provide reproducibility.
+
+No doubt containers have gained a lot of popularity after Docker, however containers tightly
+integrate with the host due to the sharing of the kernel, which raises security
+concerns. Figure \ref{fig:container-overview} provides overview of the containers architecture.
+They also share three main security threats with other virtualization
+techniques~\cite{gantikow2016providing}.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=.7\columnwidth]{Figures/container.png}
+  \caption{Architecture of Container-based
+                Virtualization.}
+  \label{fig:container-overview}
+\end{figure}
+
+\textbf{Privilege Escalation} A malicious attacker can break out of the container
+and gain control of the host system and other containers running on the same host.
+
+\textbf{Denial-of-Service} One container may end up eating all the resources of the
+host hence resulting in the starvation of the host and other containers.
+
+\textbf{Information Leak} Private data of the host and other containers could be
+leaked and can be used for further attacks.
+
+However, two features of the Linux kernel, \textit{control groups} and \textit{namespaces},
+are used by containers to mitigate these threats to a certain extent. Security
+of containers is still most concerning issue.
+Except web applications, containers are also popularly used for scientific computing
+and data science in neuroscience. In fact, Singularity was developed for scientific applications
+by keeping focus on HPC environments.
+The goal of this paper is to report all vulnerabilities that are present in
+container images, specifically used by neuroimaging field, and access their
+related risks for data analysis.
+
+The existing work on containers focuses mainly on the security of Docker
+containers.
+This focus is justified by the fact that, containers expose the host's resources
+(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
+threat for the applications running on the same host. Previous studies evaluated
+security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
+and have scanned vulnerabilities on Docker hub~\cite{Shu2017, gummaraju2015over}.
+Also Singularity came up with Stools, which can be used for scanning Singularity images
+for security and quality checks.
+Here, we focus on the specific context of scientific data analysis on HPC clusters, taking
+neuroimaging as an example.
+
+This paper is organized as follows: in next section, we provide description
+of materials and methods which includes summarizing a particular use case of
+containers in neuroscience, which is used for scientific computing. It involves
+usage of containers on shared HPC cluster. Additionally, in this section we
+describe all the resources that are used by this use case. We also explain
+scanning tools that we use for scanning container images to report
+vulnerabilities. Next section of this paper is about the results. Here, we
+present number and type of vulnerabilites that are present in the container images
+which are used for data analysis on shared HPC clusters, and discuss how many of them are
+critical vulnerabilities. Following section is about discussion of these results
+where we provide more insight into the risks that are caused by these vulnerabilties
+and how they can be leveraged to design attacks. Here, we also provide some such
+vulnerability examples. Finally, we conclude this paper by discussing ten simple
+rules that can be followed to secure container image for use in clusters.
+
 \section{Materials and Methods}
 
-In this section we summarize a particular use case of containers which is Canadian
+In this section we summarize a particular use case of containers, Canadian
 Open Neuroscience Platform (CONP). It is a national platform for sharing neuroscience
@@
 distribute massive amounts of data produced by modern neuroscience.
-Here, we summarize all the resources and software tools that are
+Here, we summarize all the resources that are
 used by CONP to function.
@@
 Ontario, and WestGrid for providing local support.
-Compute Canada uses Slurm Workload Manager to schedule jobs.
-Control groups are used to limit number of resources that can be used
+Compute Canada uses Slurm Workload Manager to schedule jobs and Lustre shared
+file system to provide high bandwidth to its users.
+Control groups are used by it to limit number of resources that can be used
 by a particular user.
 Compute Canada do not support Docker as its default configuration
-runs containers as root. Whereas, Compute Canada supports Singularity
-because it removes the drawback of Docker.
-Compute Canada uses Lustre shared file system to provide high
-bandwidth to its users.
+runs containers as root. However, Compute Canada supports Singularity
+containers because it removes the drawback of Docker.
 
@@
 
-Singlarity, which came in 2016, provides operating system (OS)level.
+Singularity, which is introduced in 2016, provides operating system (OS) level
+virtualization.
 It offers mobility of compute by facilitating portable environments 
-through a single image file. Once Singularity image
+through a single image file~\cite{kurtzer2016singularity}. Once Singularity image
 is created, it is hashed by using SHA256 hashing. Hence, it cannot be changed
 once it is created, consequently, it can be used for reproducing the results of
-scientific experiments. Singularity was introduced with the main goal of pro-
-viding support for multi-user environment. Main features provided by
-Singularity are mobility of compute and reproducibility.
+scientific experiments. Singularity was introduced with the main goal of
+providing support for multi-user environment. Main features provided by
+Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
 Mobility of compute is defined as creating and maintaining a workflow on
@@
 are easily portable across different versions of the C library and different kernel
-implementations [16].
-Same features of Singularity, which are used for mobility of compute, facil-
-itate reproducibility as well.
+implementations.
+Same features of Singularity, which are used for mobility of compute,
+facilitate reproducibility as well~\cite{sochat2017enhancing}.
 
@@
 Nowadays, two most popular containerization tools used are Docker and Singularity.
-Both have different image format.
+Both have different image format. Below we provide description of both image
+formats.
 
@@
 
-There are two ways to create Docker image. The first is to use an existing
-Docker image as a base image and then build a new image from that one, by
-making changes in the filesystem, which is saved as a new layer of the
-Docker image. The second way is to build a new Docker image from scratch.
 Docker images are organized as a series of layers which are stacked on top
@@
 compressed into a single image and can be pushed to the Docker Hub.
+There are two ways to create Docker image. The first is to use an existing
+Docker image as a base image and then build a new image from that one, by
+making changes in the filesystem, which is saved as a new layer of the
+Docker image. The second way is to build a new Docker image from scratch.
 
@@
 is known as Singularity image. Due to image hashing, Singularity does not
-contain image layers, unlike Docker images. While publishing experimental
+contain image layers, unlike Docker images. So Singularity image is a single
+immutable file that can be moved around as any other file. While publishing experimental
 results, authors can also publish Singularity image along with its hash, which
@@
 
-Boutiques is a application sharing system. It is based on Linux containers
+Boutiques is a application sharing system~\cite{glatard2015boutiques}. It is based on Linux containers
 and can be used to publish, integrate, and execute third-party
 applications across different platforms automatically. Boutiques framework is
-employed by CONP. With Boutiques, the command-line of the application is
+employed by CONP to integrate and execute applications on CBRAIN web portal.
+With Boutiques, the command-line of the application is
 described through a flexible template, which is called descriptor. Descriptor
-describes the input that is required by the application and the output it produces.
+describes the input that is required by the application and the output it produces~\cite{glatard2018boutiques}.
 It points to a Docker or Singularity image, where the application is installed.
@@
 descriptor of the application.
+Currently, Boutiques tools use 23 different container images. Out of
+which 7 are Singularity images and rest are Docker images.
 
@@
 
-BIDS Apps is a framework designed to share and execute neuroimaging
+BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
 analysis pipelines. It improves usability, accesibility, and reproducibility
-of different operating system users as well as HPC users.
+of different operating system users as well as HPC users through containerization.
+BIDS apps share reproducibility goal with Boutiques, though they are conceptually different.
+BIDS apps main goal is to standardize application interfaces whereas Boutiques goal is to
+make application sharing and integration easier with different platforms.
+Currently, there are 27 different container images that are used by
+BIDS App. All these are Docker images.
 
@@
 
-ReproNim: A Center for Reproducible Neuroimaging Computation is a vision
-to help neuroscientists in reproducing neuroimaging research.
-
-\subsection{Container Images Used}
+ReproNim is a Center for Reproducible Neuroimaging Computation. It is a vision
+to help neuroscientists in reproducing neuroimaging research. Repronim
+uses RepronIn, BrainVerse, Neuroimaging Computation Environments Manager (NICEMAN),
+and NeuroBlast software tools for its
+functioning. ReproIn is a software that automate acquisition and conversion
+of collected MRI data to BIDS standard format with DataLad version management~\cite{kennedy2019everything}.
+BrainVerse is a cross-platform software framework and collaborative desktop application
+that helps in managing, tracking, and sharing information.
+NICEMAN is a software system that tracks and manages available computation resources
+and makes their use in a scalable and reproducible way.
+Neuroblast is a service that facilitates data sharing of existing studies, and it also
+helps users to search similar studies based on combination of analysis,
+tasks and activation patterns. There are currently 28 different Singularity
+images used by Repronim.
 
@@
 to proceed, either not to run that image at all, or run only after updating the
-packages that have vulnerabilities. The latter option effects the reproducibility
+image. Updating the image involves updating all software packages that are
+inside that image. However, this option effects the reproducibility
 of the image, which means that the image cannot be used to verify research
@@
 There are various scanning tools that are available for scanning container
-images like Vuls, Clair, ClairScanner, Anchore, Dagda, etc. Out of them we
-took Anchore and Vuls for our experiments to scan container
+images like Vuls, Clair, ClairScanner, Anchore, Dagda, etc.
+Out of these we take Anchore, Vuls, and ClairScanner tools for our experiments to scan container
 images which are used by the above discussed application frameworks.
+For scanning Singularity images, Stools scanner is used, which is specifically designed
+for Singularity images. Stools internally make use of Clair-Scanner for
+scanning.
 
@@
 language. It is an agentless vulnerability scanner and uses various
-vulnerability databases listed in 4.4a. Using dynamic scanning technique, it offers
+vulnerability databases. Using dynamic scanning technique, it offers
 remote and local scan. Remote scan involves setting up only one machine, to
@@
 
+\subsubsection{Stools}
+
+Stools combines CoreOS's ClairScanner with the Continuous Integration (Travis and
+Circle) for scanning Singularity images for vulnerabilities.
+Initially, ClairScanner was intented to scan Docker Containers. This tool does not fit well
+to scan Singularity images because of the different image formats. Docker layers
+consist of layers, whereas Singluarity images consist of a single binary file.
+However, TravisCI and CircleCI are commonly used for testing code, and these
+services also offer running containers. So Stools combined both the concepts.
+It involves spinning a ClairScanner container during testing and building a
+Singularity image, and scanning it for filesystem before the image is finalized.
+
 \subsection{CBRAIN}
 
-Canadian Brain Imaging Research Platform (CBRAIN) is a web portal that is used
-by CONP to exploit services of Compute Canada. CBRAIN is a collaborative
+\href{http://github.com/aces/cbrain}{CBRAIN}~\cite{sherif2014cbrain} is a web portal that is
+used for the processing of distributed data on various storage locations of computing
+clusters. CBRAIN system deployed by Montreal Neurological Institute depends on the infrastructure
+delivered by Compute Canada~\cite{das2016mni}.
+It is also used by CONP to exploit services of Compute Canada. CBRAIN is a collaborative
 neuroimaging research platform that is active in production since 2009. CBRAIN
@@
 resources across the world. CBRAIN’s infrastructure consists of three main
-layers, namely access layer, service layer, and infrastructure layer. The access
+layers, namely access layer, service layer, and infrastructure layer~\cite{sherif2014cbrain}. The access
 layer is for CBRAIN users, and can be accessed through any modern browser or
-RESTful API [42]. The service layer consists of CBRAIN portal, which contains
+RESTful API. The service layer consists of CBRAIN portal, which contains
 metadata and databases. It provides information about users, their permissions,
@@
 resources, which are connected through a network. 
+CBRAIN supports Docker, Singularity, BIDS apps, and Boutiques.
+CBRAIN users uses a portal
+account on the cluster. Users are only able to
+run pre-defined applications on the cluster through the CBRAIN portal.
 
-\bibliographystyle{plain}
+%\bibliographystyle{vancouver-authoryear}
 \bibliography{bibliography}

### 2019-07-18 paper.tex
Comments on intro and section II

@@
 \usepackage{siunitx}
-\usepackage{minted} % Used for JSON highlighting
 \usepackage{algpseudocode} % Algorithmic environment
@@
 \newcommand{\reprozip}[0]{ReproZip}
+\newcommand{\TG}[1]{\color{blue}From Tristan: #1 \color{black}}
 
@@
 goal of removing drawbacks of Docker. Singularity was developed mainly to
-support HPC environments and to provide reproducibility.
+support HPC environments and to provide reproducibility. \TG{The previous two paragraphs are too general. You should
+summarize them in 2-3 sharper sentences.}
 
 No doubt containers have gained a lot of popularity after Docker, however containers tightly
-integrate with the host due to the sharing of the kernel, which raises security
+integrate with the host due to the sharing of the kernel \TG{not only the kernel: 
+mounted file systems and devices too}, which raises security
 concerns. Figure \ref{fig:container-overview} provides overview of the containers architecture.
@@
 
+\TG{Avoid bold face in papers}
+
 However, two features of the Linux kernel, \textit{control groups} and \textit{namespaces},
@@
 container images, specifically used by neuroimaging field, and access their
-related risks for data analysis.
+related risks for data analysis. \TG{You should explain the 3 questions discussed during out meeting.}
 
@@
 neuroimaging as an example.
+
+\TG{Some notions that should be introduced in this section (incomplete):
+vulnerability vs malware, paper suggested by Emad Shihab.}
 
@@
 In this section we summarize a particular use case of containers, Canadian
-Open Neuroscience Platform (CONP). It is a national platform for sharing neuroscience
+Open Neuroscience Platform (CONP) \TG{No. In this section you describe the data and tools 
+that were used in your experiments. The fact that they are used in CONP 
+is a side note}. It is a national platform for sharing neuroscience
 research data and aims at creating an interactive interface for neuroscientists and
@@
 containers because it removes the drawback of Docker.
+\TG{Not sure if Compute Canada is used in the experiments. If not, remove and 
+pitch it in the introduction that containers are nowadays used in many clusters, including 
+Compute Canada. You could also refer to the full list of clusters that support singularity.}
 
@@
 
+\TG{This paragraph is too general for a method section. You might summarize this in
+2-3 sentences for the introduction. Here you should talk about the engine,
+i.e., how images are run, focusing on security features. Use of namespaces,
+cgroups, access to devices, etc}
+
+\TG{You should add a subsection presenting Docker.}
+
 \subsection{Container Image Formats}
 
-A container image is a package that contains the application alongwith its
+A container image is a package that contains the application along with its
 required dependencies and libraries.
@@
 
-Docker images are organized as a series of layers which are stacked on top
-of each other. Each layer consists of a filesystem diff that is introduced
-due to the changes made on the layer below it. All layers of the Docker image
-are identified by unique layerIDs. All these layers stacked together gives a
-unified and complete view of a Docker image. These layers are
-compressed into a single image and can be pushed to the Docker Hub.
-There are two ways to create Docker image. The first is to use an existing
-Docker image as a base image and then build a new image from that one, by
-making changes in the filesystem, which is saved as a new layer of the
-Docker image. The second way is to build a new Docker image from scratch.
+Docker images are organized as a series of layers stacked on top of each
+other and identified by unique layer identifiers \TG{If a layer is reused
+in different images, for instance the top layer of a base image, will it
+have the same id across images?}. Each layer consists of a filesystem diff
+with respect to the layer below. Layers are compressed \TG{Are you
+referring to file compression similar to gzip?} into a single image and can
+be pushed to DockerHub. There are two ways to create a Docker image. The
+first is to use an existing Docker image as a base image and then build a
+new image from that one, by making changes in the filesystem, which is
+saved as a new layer of the Docker image. The second way is to build a new
+Docker image from scratch. \TG{It would be relevant to mention the file
+system used to store the images (is it squashfs?).}
 
@@
 
-Singularity takes snapshot, locks, and archives the developed application, which
-is known as Singularity image. Due to image hashing, Singularity does not
-contain image layers, unlike Docker images. So Singularity image is a single
-immutable file that can be moved around as any other file. While publishing experimental
-results, authors can also publish Singularity image along with its hash, which
-allow other researchers to verify results.
+Singularity takes snapshot, locks, and archives the developed application
+\TG{what does it mean?}, which is known as Singularity image. Due to image
+hashing, Singularity does not contain image layers, unlike Docker images
+\TG{is it really due to hashing? why couldn't a hashed image have layers?}.
+So Singularity image is a single immutable file that can be moved around as
+any other file \TG{Talking about the file system used would be relevant}.
+While publishing experimental results, authors can also publish Singularity
+image along with its hash, which allow other researchers to verify results.
 
@@
 
-Following are the application frameworks in neuroscience that are using containers
-on HPC clusters.
+We used containerized applications available in the Boutiques and BIDS Apps
+frameworks used in neuroscience to run analyses on HPC clusters.
 
@@
 
-Boutiques is a application sharing system~\cite{glatard2015boutiques}. It is based on Linux containers
-and can be used to publish, integrate, and execute third-party
-applications across different platforms automatically. Boutiques framework is
-employed by CONP to integrate and execute applications on CBRAIN web portal.
-With Boutiques, the command-line of the application is
-described through a flexible template, which is called descriptor. Descriptor
-describes the input that is required by the application and the output it produces~\cite{glatard2018boutiques}.
-It points to a Docker or Singularity image, where the application is installed.
-Developers of the application produce Boutiques descriptor, and stores it along
-with the application. Boutiques descriptor are described in JSON format. There
-is a set of core tools which help in constructing, validating and executing bou-
-tiques descriptors. During the application run-time, the execution platform
-builds a command line by using input values given by the user and boutiques
-descriptor of the application.
-Currently, Boutiques tools use 23 different container images. Out of
-which 7 are Singularity images and rest are Docker images.
+Boutiques~\cite{glatard2018boutiques} is a application sharing system to
+publish, integrate, and execute command-line applications across different
+platforms. In Boutiques, the command-line of the application is described
+through a flexible JSON descriptor pointing to a Docker or a Singularity
+image where the application is installed. A set of core tools help
+construct, validate, publish and execute Boutiques descriptors. Boutiques
+applications are published on the Zenodo research repository.
+
+We used the 49 Boutiques applications published on Zenodo at the time of
+the writing. These applications use 23 different container images,
+including 7 Singularity images and 16 Docker images. \TG{You should add a
+table showing the images available in each framework, with their base
+image, DOIs, size, and number of files.}
 
@@
 analysis pipelines. It improves usability, accesibility, and reproducibility
-of different operating system users as well as HPC users through containerization.
-BIDS apps share reproducibility goal with Boutiques, though they are conceptually different.
-BIDS apps main goal is to standardize application interfaces whereas Boutiques goal is to
-make application sharing and integration easier with different platforms.
-Currently, there are 27 different container images that are used by
+of different applications through containerization.
+\TG{How many BIDS apps are there? Did you use them all?} Currently, there are 27 different container images that are used by
 BIDS App. All these are Docker images.
@@
 
+\subsection{Other images}
+
+\TG{We could also use selected images from DockerHub or SingularityHub. For
+instances the ones used by AFNI or other neuroimaging tools not represented
+in Boutiques or BIDS Apps. However we wouldn't be able to shrink these
+images unless we identified specific command-lines to run.}
+
 \subsection{Image Update Process}
@@
 packages from images, which in turn reduces the number of vulnerabilities
-present in images.
+present in images. \TG{Here you should describe the method you used to update the images, linking to the 
+software (script) you used to do that. 
+This paragraph is too general and doesn't belong to the methods. }
 
@@
 
-There are various scanning tools that are available for scanning container
-images like Vuls, Clair, ClairScanner, Anchore, Dagda, etc.
-Out of these we take Anchore, Vuls, and ClairScanner tools for our experiments to scan container
-images which are used by the above discussed application frameworks.
-For scanning Singularity images, Stools scanner is used, which is specifically designed
-for Singularity images. Stools internally make use of Clair-Scanner for
-scanning.
+Out of the various container image scanning tools, we selected Anchore,
+Vuls, Stools and ClairScanner for our experiments. \TG{Explain why you used
+more than 1 tool, and why you used these ones speifically.}
 
@@
 
-Anchore is an end-to-end container security, and open-source compliance plat-
-form. Anchore is a static scanning tool that analyses container images and
-lists operating system packages,
-unofficial packages, configuration files, and language modules [58]. In other
-words, Anchore is a set of tools, which users can employ for scanning container
-images and applying custom policies to them. It provides visibility and trans-
-parency of the container environment. Anchore offers services in two ways:
-Anchore Engine and Anchore Engine Command Line Interface (CLI).
-Anchore Engine is available as a Docker image, which is available on Docker
-Hub. Anchore Engine CLI provides command line interface in addition to An-
-chore Engine REST API. Anchore Engine CLI can be installed directly on the
-host and used to inspect images.
+Anchore is an end-to-end, open-source container security platform. Anchore
+is a static \TG{You should explain static vs dynamic scanning in the intro}
+scanning tool that analyses container images and lists operating system
+packages, unofficial packages, configuration files \TG{How about files
+which are not configuration files?}, and language modules [58] \TG{Import
+reference}. \TG{What is a language module?} \TG{Does it list unknown
+packages, files or modules?} Anchore is a set of tools, which users can
+employ for scanning container images and applying custom policies to them.
+It provides visibility and transparency of the container environment.
+Anchore offers services in two ways: Anchore Engine and Anchore Engine
+Command Line Interface (CLI). Anchore Engine is available as a Docker
+image, which is available on Docker Hub. Anchore Engine CLI provides
+command line interface in addition to Anchore Engine REST API. Anchore
+Engine CLI can be installed directly on the host and used to inspect
+images.
+
+\TG{You should refer to the vulnerability databases used, and explain how
+software components, for instance files, are matched to these databases. Is
+the matching based on file checksum?}
 
@@
 
-Vuls is an open-source vulnerability scanner for Linux/FreeBSD, written in Go
-language. It is an agentless vulnerability scanner and uses various
-vulnerability databases. Using dynamic scanning technique, it offers
+Vuls is an open-source vulnerability scanner for Linux and FreeBSD, written in Go
+language \TG{Why is it relevant that it's written in Go?}.
+ It is an agentless vulnerability scanner and uses various
+vulnerability databases \TG{You should list them and explain how they differ to 
+the ones used by Anchore}. Using dynamic scanning technique, it offers
 remote and local scan. Remote scan involves setting up only one machine, to
@@
 Fast scan is performed without root privileges, whereas fast root scan is
-performed with root privileges. The latter also uses checkrestart utility to de-
-tect processes that are updated but not yet restarted because if they are not
+performed with root privileges. The latter also uses checkrestart utility to detect processes that are updated but not yet restarted because if they are not
 restarted, updates are not effective. So fast root scan also detects these pro-
@@
 root privileges for scanning, and is used to get a more detailed scan. It checks
-changelogs, which puts more load on the target server. As shown in Figure 4.3
+changelogs, which puts more load on the target server. As shown in Figure 4.3 \TG{There is no figure 4.3 or graph 4.5 here. Anyway it's not relevant 
+to report results in this section. This paragraph looks like a copy paste from your previous report, it needs to be edited.}
 it is clear that vulnerability detection time of Vuls is much better than An-
@@
 Singularity image, and scanning it for filesystem before the image is finalized.
+\TG{Add link and/or reference.}
 

### 2019-07-31 paper.tex
july 31

@@
 No doubt containers have gained a lot of popularity after Docker, however containers tightly
-integrate with the host due to the sharing of the kernel \TG{not only the kernel: 
-mounted file systems and devices too}, which raises security
+integrate with the host due to the sharing of the kernel, 
+mounted file systems, and devices, which raises security
 concerns. Figure \ref{fig:container-overview} provides overview of the containers architecture.
@@
 
-\textbf{Privilege Escalation} A malicious attacker can break out of the container
+\textit{Privilege Escalation} A malicious attacker can break out of the container
 and gain control of the host system and other containers running on the same host.
 
-\textbf{Denial-of-Service} One container may end up eating all the resources of the
+\textit{Denial-of-Service} One container may end up eating all the resources of the
 host hence resulting in the starvation of the host and other containers.
 
-\textbf{Information Leak} Private data of the host and other containers could be
+\textit{Information Leak} Private data of the host and other containers could be
 leaked and can be used for further attacks.
-
-\TG{Avoid bold face in papers}
 
@@
 are used by containers to mitigate these threats to a certain extent. Security
-of containers is still most concerning issue.
+of containers is still most concerning issue. According to a Forrester survey~\cite{} done in January
+2015, security is the
+biggest concern while deploying containers.
 Except web applications, containers are also popularly used for scientific computing
 and data science in neuroscience. In fact, Singularity was developed for scientific applications
-by keeping focus on HPC environments.
+by keeping focus on HPC environments. This popularity containers lead us to the
+primary research question of this work: \textit{what is the current security state of
+container images that are deployed on HPC clusters}.
+
+To answer this question, we take a real use case of containers into consideration.
 The goal of this paper is to report all vulnerabilities that are present in
 container images, specifically used by neuroimaging field, and access their
-related risks for data analysis. \TG{You should explain the 3 questions discussed during out meeting.}
+related risks for data analysis. Particularly, we aim to answer three primary
+research questions:
+
+\textit{RQ1} Are vulnerabilities present inside container images that are
+deployed on HPC clusters?
+\textit{RQ2} Can we get rid of these vulnerabilities by updating the
+images?
+\textit{RQ3} Can we get rid of these vulnerabilities by shrinking the
+size of the image?
+
+To answer those questions, we take an example of neuroscience field where
+containers are used on HPC clusters.
 
@@
 Docker images are organized as a series of layers stacked on top of each
-other and identified by unique layer identifiers \TG{If a layer is reused
-in different images, for instance the top layer of a base image, will it
-have the same id across images?}. Each layer consists of a filesystem diff
+other and identified by unique layer identifiers. If a layer is reused
+in different images it will
+have the same id across images. Each layer consists of a filesystem diff
 with respect to the layer below. Layers are compressed \TG{Are you
@@
 saved as a new layer of the Docker image. The second way is to build a new
-Docker image from scratch. \TG{It would be relevant to mention the file
-system used to store the images (is it squashfs?).}
+Docker image from scratch. Docker supports several different storage drivers.
+\textit{Overlay2} is the preferred storage driver used by Docker for all currently
+supported Linux versions, whereas \textit{aufs} is preferred for Docker 18.06 and
+older, when using Ubuntu 14.04 on kernel 3.13 as it do not support \textit{overlay2}.
+Other storage drivers that are supported by Docker include \textit{devicemapper, btrfs,
+zfs, and vfs}
 

### 2019-08-03 paper.tex
saturday

@@
 \newcommand{\reprozip}[0]{ReproZip}
-\newcommand{\TG}[1]{\color{blue}From Tristan: #1 \color{black}}
+\newcommand{\TG}[1]{\color{blue}From Tristan: #1\color{black}}
 
@@
 and data science in neuroscience. In fact, Singularity was developed for scientific applications
-by keeping focus on HPC environments. This popularity containers lead us to the
+by keeping focus on HPC environments. This popularity of containers lead us to the
 primary research question of this work: \textit{what is the current security state of
@@
 
-To answer this question, we take a real use case of containers into consideration.
-The goal of this paper is to report all vulnerabilities that are present in
+To answer that question, we scan all images that are used on Compute
+Canada clusters by neuroscience field. Scanning refers to the practice of
+collecting all information about the container image, investigating it
+for vulnerabilities, and finally producing a
+report to summarize scanning results. Scanning is broadly categorized into
+two types: static scanning and dynamic scanning. The former scanning technique
+involves extracting information of an image without running it into a container,
+whereas the latter approach involves launching the container from the target image, and
+then scanning the running container.
+Here, we focus mainly on vulnerability scanning and not on malware.
+Malware is a computer software that is specially designed to attack the target computer,
+whereas vulnerability is a weakness in the developer's software that can be used
+by the attacker to perform unathorized actions on the target computer.
+In this paper, we report all vulnerabilities that are present in
 container images, specifically used by neuroimaging field, and access their
@@
 
-\textit{RQ1} Are vulnerabilities present inside container images that are
+\textit{RQ1:} Are vulnerabilities present inside container images that are
 deployed on HPC clusters?
-\textit{RQ2} Can we get rid of these vulnerabilities by updating the
+
+\textit{RQ2:} Can we get rid of these vulnerabilities by updating the
 images?
-\textit{RQ3} Can we get rid of these vulnerabilities by shrinking the
+
+\textit{RQ3:} Can we get rid of these vulnerabilities by shrinking the
 size of the image?
@@
 To answer those questions, we take an example of neuroscience field where
-containers are used on HPC clusters.
-
-The existing work on containers focuses mainly on the security of Docker
+containers are used on Compute Canada HPC cluster.
+We are not the first to work on vulnerabilities inside container images but
+the existing research work on containers focuses mainly on the security of Docker
 containers.
@@
 
-\TG{Some notions that should be introduced in this section (incomplete):
-vulnerability vs malware, paper suggested by Emad Shihab.}
+\TG{paper suggested by Emad Shihab.}
 
@@
 the writing. These applications use 23 different container images,
-including 7 Singularity images and 16 Docker images. \TG{You should add a
-table showing the images available in each framework, with their base
-image, DOIs, size, and number of files.}
+including 7 Singularity images and 16 Docker images.
 
@@
 of different applications through containerization.
-\TG{How many BIDS apps are there? Did you use them all?} Currently, there are 27 different container images that are used by
-BIDS App. All these are Docker images.
+Currently, there are 27 BIDS apps available and all are using different Docker images.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=.7\columnwidth]{Figures/bids_table.png}
+  \caption{All Container images used by BIDS apps.}
+  \label{fig:bids_apps}
+\end{figure}
 
@@
 
-Out of the various container image scanning tools, we selected Anchore,
-Vuls, Stools and ClairScanner for our experiments. \TG{Explain why you used
-more than 1 tool, and why you used these ones speifically.}
+Out of the various container image scanning tools available to scan Docker images,
+we selected Anchore
+and Vuls because these are the most mature scanning tools. To scan Singularity images
+we use Stools, which is specially designed for Singularity images. This tool internally uses
+ClairScanner tool so we included ClairScanner also in our experiements to compare
+performance of both the tools.
 
@@
 
+\begin{figure}
+  \centering
+  \includegraphics[width=.7\columnwidth]{Figures/anchore.png}
+  \caption{Databases used by Anchore.}
+        \label{fig:anchore_db}
+\end{figure}
+
 \TG{You should refer to the vulnerability databases used, and explain how
@@
 
-Vuls is an open-source vulnerability scanner for Linux and FreeBSD, written in Go
-language \TG{Why is it relevant that it's written in Go?}.
+Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
 It is an agentless vulnerability scanner and uses various
@@
 Fast scan is performed without root privileges, whereas fast root scan is
-performed with root privileges. The latter also uses checkrestart utility to detect processes that are updated but not yet restarted because if they are not
+performed with root privileges. The latter also uses checkrestart utility to 
+detect processes that are updated but not yet restarted because if they are not
 restarted, updates are not effective. So fast root scan also detects these pro-
@@
 root privileges for scanning, and is used to get a more detailed scan. It checks
-changelogs, which puts more load on the target server. As shown in Figure 4.3 \TG{There is no figure 4.3 or graph 4.5 here. Anyway it's not relevant 
-to report results in this section. This paragraph looks like a copy paste from your previous report, it needs to be edited.}
-it is clear that vulnerability detection time of Vuls is much better than An-
-chore. Vuls tool uses dynamic scanning, so the scanning time does not depend
-on the image size.
-Graph 4.5 shows percentage of vulnerabilities that are
-covered by Vuls and Anchore tools. This graph can be explained with the help
-of List 4.4, which shows vulnerability databases that are referred, by both Vuls
-and Anchore. Anchore covers less percentage of vulnerabilities as compared
-to Vuls because Anchore relies mainly on vulnerability databases published by
-Linux distributions, whereas Vuls additionally refers to another sources such as
-databases from Japan, US-CERT, etc.
+changelogs, which puts more load on the target server.
+
+\begin{figure}
+  \centering
+  \includegraphics[width=.7\columnwidth]{Figures/vuls.png}
+  \caption{Databases used by Vuls.}
+	\label{fig:vuls_db}
+\end{figure}
 
@@
 
-Stools combines CoreOS's ClairScanner with the Continuous Integration (Travis and
+\href{https://github.com/singularityhub/stools}{Stools} combines CoreOS's ClairScanner with the Continuous Integration (Travis and
 Circle) for scanning Singularity images for vulnerabilities.
@@
 Singularity image, and scanning it for filesystem before the image is finalized.
-\TG{Add link and/or reference.}
 

### 2019-08-22 paper.tex
updated intro

@@
 \usepackage{xspace}
+\usepackage{minted} % Used for JSON highlighting
 \usepackage{booktabs}
@@
 
-Virtualization, which was introduced in 1960s, refers to the creation of a virtual
-version of something. Its meaning has evolved and took different forms since then, for
-instance hardware virtualization, containerization, desktop virtualization, etc.
-Here, in this paper our main focus is on containerarization and its security concerns,
-specifically in neuroimaging field.
 Containers, which provide operating system (OS) level virtualization, are very
-popular. This is due to the need for fast development cycles, continuous delivery,
-and cost reduction of infrastructure. Moreover, demand for an isolated
-environment adds on to the popularity of containers. Indeed, containers accelerate
-development cycles as compared to virtual machines and provide near-native performance.
-They are very lightweight, flexible, and more resource-efficient than virtual
-machines. By providing OS level virtualization they
-removes the overhead of having an extra OS layer.
+popular. This is because they are very lightweight, flexible, resource-efficient,
+provide fast development cycles, continuous delivery,
+and cost reduction of infrastructure. OS-level virtualization gained a lot of interest when Docker was
+introduced in 2013~\cite{gantikow2016providing}. However, it has security concerns due to which it
+is not supported by High Performance
+Computing (HPC) environments. As a result, Singularity came in 2016 with the goal of providing support
+for HPC environments. It is used in many clusters including Compute Canada.
+Table \ref{fig:cluster_list} illustrates the reported usage of Singularity on HPC clusters~\cite{kurtzer2017singularity}.
 
-Although Linux Containers (LXC) and other alternatives such as Rocket were already
-available, container-based virtualization gained a lot of interest when Docker was
-introduced in 2013~\cite{gantikow2016providing}. Docker makes container's use more straightforward. However, there
-are few limitations of Docker. For example, it is not supported by shared High Performance
-Computing (HPC) environments because its default configuration runs containers
-as root. Secondly, Docker containers cannot be used for reproducibility as Docker
-images can be updated, and hence losing specific package versions required for
-reproducing scientific results. Consequently, Singularity was introduced in 2016 with the main
-goal of removing drawbacks of Docker. Singularity was developed mainly to
-support HPC environments and to provide reproducibility. \TG{The previous two paragraphs are too general. You should
-summarize them in 2-3 sharper sentences.}
+\begin{figure}
+  \centering
+  \includegraphics[width=\columnwidth]{Figures/cluster_list.png}
+	\caption{List of HPC clusters using Singularity~\cite{kurtzer2017singularity}.}
+	\label{fig:cluster_list}
+\end{figure}
 
-No doubt containers have gained a lot of popularity after Docker, however containers tightly
+No doubt containers have gained a lot of popularity, however containers tightly
 integrate with the host due to the sharing of the kernel, 
@@
 for vulnerabilities, and finally producing a
-report to summarize scanning results. Scanning is broadly categorized into
+report to summarize scanning results. It is broadly categorized into
 two types: static scanning and dynamic scanning. The former scanning technique
@@
 
-In this section we summarize a particular use case of containers, Canadian
-Open Neuroscience Platform (CONP) \TG{No. In this section you describe the data and tools 
-that were used in your experiments. The fact that they are used in CONP 
-is a side note}. It is a national platform for sharing neuroscience
+As we are taking a particular use case of containers from
+neuroscience field i.e Canadian Open Neuroscoence Platform (CONP) so  
+in this section we summarize the data and tools 
+that are used in CONP. CONP is a national platform for sharing neuroscience
 research data and aims at creating an interactive interface for neuroscientists and
@@
 
-\subsection{Compute Canada Clusters}
-
-Compute Canada is a national High Performance Computing (HPC) research platform.
-It provides infrastructure and services for Advanced Research Computing (ARC).
-Its goal is to bring excellence, ease, and innovation in research of Canadian
-research institutions by providing storage, computing power, and required
-softwares to carry out research.
-It integrates with four regional partners namely ACENET, Calcul Québec, Compute
-Ontario, and WestGrid for providing local support.
-Compute Canada uses Slurm Workload Manager to schedule jobs and Lustre shared
-file system to provide high bandwidth to its users.
-Control groups are used by it to limit number of resources that can be used
-by a particular user.
-Compute Canada do not support Docker as its default configuration
-runs containers as root. However, Compute Canada supports Singularity
-containers because it removes the drawback of Docker.
-\TG{Not sure if Compute Canada is used in the experiments. If not, remove and 
-pitch it in the introduction that containers are nowadays used in many clusters, including 
-Compute Canada. You could also refer to the full list of clusters that support singularity.}
-
 \subsection{Container Engine: Singularity}
 
-Singularity, which is introduced in 2016, provides operating system (OS) level
-virtualization.
-It offers mobility of compute by facilitating portable environments 
+Singularity offers mobility of compute by facilitating portable environments 
 through a single image file~\cite{kurtzer2016singularity}. Once Singularity image
@@
 once it is created, consequently, it can be used for reproducing the results of
-scientific experiments. Singularity was introduced with the main goal of
-providing support for multi-user environment. Main features provided by
+scientific experiments. Main features provided by
 Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
-Mobility of compute is defined as creating and maintaining a workflow on
-a local machine that can be easily ported on other hosts, Linux distributions,
-and/or cloud service providers. To achieve this, Singularity packs everything
-that is required for the application to run in a distributable image. Then that
-image can be copied, archived, and shared. Moreover, Singularity containers
-are easily portable across different versions of the C library and different kernel
-implementations.
-Same features of Singularity, which are used for mobility of compute,
-facilitate reproducibility as well~\cite{sochat2017enhancing}.
 
-\TG{This paragraph is too general for a method section. You might summarize this in
-2-3 sentences for the introduction. Here you should talk about the engine,
-i.e., how images are run, focusing on security features. Use of namespaces,
-cgroups, access to devices, etc}
+Users can easily access files, devices, sockets, ports of the host system from
+the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
+into the running container. Additional directories can be specified with \textit{--bind}
+to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
+However namespaces can be requested if required. Users cannot escalate privileges inside
+Singularty containers. This is because Singularity do not run containers as root.
+Instead, a user inside Singularity container is the same user outside the container.
 
-\TG{You should add a subsection presenting Docker.}
+\subsubsection{Docker Engine}
+
+Docker runs a software, \textit{Docker daemon}, on the host machine.
+Docker daemon runs as root, and is remotely controlled through a
+UNIX socket. It is responsible for launching containers, their
+isolation, and spawning shells into the containers. It is also
+responsible for managing Docker images i.e \textit{pull} and \textit{push}
+from image repository, building images from Dockerfiles, signing them, etc..
+When a Docker container runs, the container process is spawned as a
+child of this root owned daemon. As Docker users directly interact with the
+Docker daemon, it is possible to force Docker daemon to escalate privileges.
+If a user gets \textit{root} privileges, it introduces unthinkable security risks
+for multi-tenant shared enviornments. Due to this reason, Docker is not
+supported by HPC environments. However, Docker containers can be imported into
+Singularity and then used on HPC clusters.
 
@@
 have the same id across images. Each layer consists of a filesystem diff
-with respect to the layer below. Layers are compressed \TG{Are you
-referring to file compression similar to gzip?} into a single image and can
-be pushed to DockerHub. There are two ways to create a Docker image. The
+with respect to the layer below. DockerHub uses gzip compression for
+transferring layers. There are two ways to create a Docker image. The
 first is to use an existing Docker image as a base image and then build a
@@
 
-Singularity takes snapshot, locks, and archives the developed application
-\TG{what does it mean?}, which is known as Singularity image. Due to image
-hashing, Singularity does not contain image layers, unlike Docker images
-\TG{is it really due to hashing? why couldn't a hashed image have layers?}.
-So Singularity image is a single immutable file that can be moved around as
-any other file \TG{Talking about the file system used would be relevant}.
+Singularity takes snapshot, locks, and archives the developed application,
+which is known as Singularity image.
+It means that Singularity image is a single immutable file that can be moved around as
+any other file. This file can be checksummed, signed, and easily
+used for verification purposes. Singularity containers use Squashfs file format
+by default. However, it also supports two other formats i.e \textit{sandbox} format
+(which is just a chroot
+directory) and \textit{writable} format (the ext3 file system).
 While publishing experimental results, authors can also publish Singularity
@@
   \centering
-  \includegraphics[width=.7\columnwidth]{Figures/bids_table.png}
+	\includegraphics[width=\columnwidth]{Figures/bids_table.png}
   \caption{All Container images used by BIDS apps.}
@@
 packages from images, which in turn reduces the number of vulnerabilities
-present in images. \TG{Here you should describe the method you used to update the images, linking to the 
-software (script) you used to do that. 
-This paragraph is too general and doesn't belong to the methods. }
+present in images. To update container images we used a bash script
+which is given in Figure~\ref{}.
+
+\begin{listing}
+\begin{minted}[frame=single,
+               framesep=3mm,
+               linenos=false,
+               xleftmargin=0pt,
+               tabsize=4]{bash}
+#!/usr/bin/env bash
+
+function die {
+	echo $1
+	exit 1
+}
+
+function find-pm {
+		(type $1 &> /dev/null && echo "> Found $1") || \
+		(echo "> $1 not found" && return 1)
+}
+
+\rm -f .updated
+find-pm yum && (yum update -y && touch .updated) 
+find-pm apt && (apt update -y && apt upgrade -y \
+&& apt autoremove -y && apt autoclean -y \
+&& touch .updated)
+test -f .updated || die "Cannot find package manager \
+or update failed"	       
+\end{minted}
+\caption{update.sh}
+\label{listing:update.sh}
+\end{listing}
+
+\begin{listing}
+\begin{minted}[frame=single,
+               framesep=3mm,
+               linenos=false,
+               xleftmargin=0pt,
+	       tabsize=4]{bash}
+#!/usr/bin/env bash
+
+set -ue
+
+function usage {
+	echo "$0 <image_list>"
+	exit 1
+}
+
+if [ $# -lt 1 ]
+then
+	usage
+fi
+
+for image in $*
+do
+	echo -n "Updating image ${image}... "
+	docker run -e /bin/bash -v $PWD:$PWD -w \
+	$PWD ${image} ./update.sh &>${image}.log \
+	&& echo "[ OK ]"
+	echo -n "Commiting updated image... "
+	ID=$(docker ps -a | head -2 | awk \
+	'$1!="CONTAINER" {print $1}')
+	docker commit ${ID} updated_${image} \
+	&& echo "[ OK ]"
+done
+\end{minted}
+\caption{update-images.sh}
+\label{listing:update-images.sh}
+\end{listing}
 
@@
 Anchore is an end-to-end, open-source container security platform. Anchore
-is a static \TG{You should explain static vs dynamic scanning in the intro}
-scanning tool that analyses container images and lists operating system
-packages, unofficial packages, configuration files \TG{How about files
-which are not configuration files?}, and language modules [58] \TG{Import
-reference}. \TG{What is a language module?} \TG{Does it list unknown
-packages, files or modules?} Anchore is a set of tools, which users can
+is a static
+scanning tool that analyses container images and lists OS
+packages, non-OS packages (Python, Java, Gem, and Npm), and files.
+Anchore is a set of tools, which users can
 employ for scanning container images and applying custom policies to them.
@@
 It is an agentless vulnerability scanner and uses various
-vulnerability databases \TG{You should list them and explain how they differ to 
-the ones used by Anchore}. Using dynamic scanning technique, it offers
+vulnerability databases. Using dynamic scanning technique, it offers
 remote and local scan. Remote scan involves setting up only one machine, to

### 2019-08-22 update-images.sh

@@ -1,0 +1,22 @@
+#!/usr/bin/env bash
+
+set -ue
+
+function usage {
+	echo "$0 <image_list>"
+	exit 1
+}
+
+if [ $# -lt 1 ]
+then
+	usage
+fi
+
+for image in $*
+do
+	echo -n "Updating image ${image}... "
+	docker run -e /bin/bash -v $PWD:$PWD -w $PWD ${image} ./update.sh &>${image}.log && echo "[ OK ]"
+	echo -n "Commiting updated image... "
+	ID=$(docker ps -a | head -2 | awk '$1!="CONTAINER" {print $1}')
+	docker commit ${ID} updated_${image} && echo "[ OK ]"
+done

### 2019-11-07 Scripts/critical_number.py
added results

@@ -1,0 +1,22 @@
+#!/usr/bin/env python
+import csv
+import sys
+import os
+import re
+import pandas as pd
+
+def main():
+    inp=sys.argv[1]
+    #csv.writer(open(r"abx.csv",'w'),delimiter=' ').writerows(filtered)
+    df = pd.read_csv(inp,delimiter=r"\s+")
+    isHigh=df['Severity'] == 'High'
+    filtered=df[isHigh]
+    unique_cves=filtered['Vulnerability_ID'].unique()
+    #filtered = filter(lambda p: 'High' == p[1], df)
+    print(len(unique_cves))
+    #id=df.Vulnerability_ID
+    #print(id)
+
+
+if __name__== "__main__":
+  main()

### 2019-11-07 Scripts/push.sh

@@ -1,0 +1,29 @@
+#!/usr/bin/env bash
+
+set -ue
+
+function usage {
+	echo "$0 <image_list>"
+	exit 1
+}
+
+if [ $# -lt 1 ]
+then
+	usage
+fi
+
+docker login -u kaurbhupinder
+for image in $*
+do
+	
+	name1="$(cut -d'/' -f1 <<<"$image")"
+	name2="$(cut -d'/' -f2 <<<"$image")"
+	#if [[ ${image} =~ ":" ]]
+        #then 
+        #     tag="$(cut -d':' -f2 <<<"$image")"
+        #else
+	#     tag="latest"
+	#fi
+        docker push kaurbhupinder/${name1}_${name2} 
+        echo " pushed kaurbhupinder/${name1}_${name2}"
+done

### 2019-11-07 Scripts/script.py

@@ -1,0 +1,26 @@
+#!/usr/bin/env python3
+
+# Import the necessary libraries
+import matplotlib.pyplot as plt
+import seaborn as sns
+import pandas as pd
+
+# Load the data
+#tips = sns.load_dataset("tips")
+df = pd.read_csv(r"train.csv")
+df.head()
+#p1=sns.regplot(data=df, x="OS_Packages", y="Vulnerabilities",fit_reg=False,marker="o", color="skyblue", scatter_kws={'s':800})
+p1=sns.relplot(x="Packages",y="Vulnerabilities",hue="OS",size="High",sizes=(600,1500), data = df)
+#ax = sns.scatterplot(df.OS_Packages, df.Vulnerabilities,hue=df.names, alpha = 1.0,s = df.High_Vulnerabilities,sizes=(200,700))
+# Show the plot
+#for line in range(0,df.shape[0]):
+#     ax.text(df.OS_Packages[line]+0.2, df.Vulnerabilities[line], df.names[line], horizontalalignment='center', size='small', color='black', weight='normal')
+p1.set(xlabel='#Packages', ylabel='#Vulnerabilities by Anchore')
+p1.set(title="#Packages Vs #Vulnerabilities")
+ax = p1.axes[0,0]
+for idx,row in df.iterrows():
+    x = row[3]
+    y = row[2]
+    text = row[5]
+    ax.text(x+.05,y,text, horizontalalignment='left')
+plt.show()

### 2019-11-07 Scripts/tag.sh

@@ -1,0 +1,21 @@
+#!/usr/bin/env bash
+
+set -ue
+
+function usage {
+	echo "$0 <image_list>"
+	exit 1
+}
+
+if [ $# -lt 1 ]
+then
+	usage
+fi
+for image in $*
+do
+	
+	name1="$(cut -d'/' -f1 <<<"$image")"
+	name2="$(cut -d'/' -f2 <<<"$image")"
+        docker tag updated_${image} kaurbhupinder/${name1}_${name2}
+        echo " tagged kaurbhupinder/${name1}_${name2}"
+done

### 2019-11-07 Scripts/update-images.sh

@@ -15,7 +15,12 @@ fi
 for image in $*
 do
 	echo -n "Updating image ${image}... "
-	docker run -e /bin/bash -v $PWD:$PWD -w $PWD ${image} ./update.sh &>${image}.log && echo "[ OK ]"
+	name1="$(cut -d'/' -f1 <<<"$image")"
+	name2="$(cut -d'/' -f2 <<<"$image")"
+	name="$(cut -d':' -f1 <<<"$name2")"
+	#docker run -e /bin/bash -v $PWD:$PWD -w $PWD ${image} ./update.sh &>${image}.log && echo "[ OK ]"
+        docker run -v $PWD:$PWD -w $PWD --entrypoint /bin/bash ${image} ./update.sh &>${name1}_${name}.log && echo "[ OK ]"
+        #docker run -it --entrypoint /bin/bash ${image} ./update.sh &>${image}.log && echo "[ OK ]"
 	echo -n "Commiting updated image... "
 	ID=$(docker ps -a | head -2 | awk '$1!="CONTAINER" {print $1}')
 	docker commit ${ID} updated_${image} && echo "[ OK ]"

### 2019-11-07 Scripts/update.sh

@@ -12,5 +12,5 @@ function find-pm {
 
 \rm -f .updated
 find-pm yum && (yum update -y && touch .updated)
-find-pm apt && (apt update -y && apt upgrade -y && apt autoremove -y && apt autoclean -y && touch .updated)
+find-pm apt && (apt update -y && apt upgrade -y && apt-get autoremove -y && apt-get autoclean -y && touch .updated)
 test -f .updated || die "Cannot find package manager or update failed"

### 2019-11-07 paper.tex
added results

@@
 \usepackage{xspace}
+\usepackage{csvsimple}
 \usepackage{minted} % Used for JSON highlighting
+\usepackage{datatool}
 \usepackage{booktabs}
 \usepackage{xcolor}
+\usepackage{amsmath}
 \usepackage{graphicx}
@@
 \usepackage{caption}
+\usepackage[justification=centering]{caption}
 \usepackage{subcaption}
@@
 \usepackage{verbatim}
+\usepackage{adjustbox}
 \usepackage{makecell}
@@
 \author[1]{Bhupinder Kaur}
+\author[1]{Tristan Glatard}
 \author[1]{Aiman Hanna}
-\author[1]{Tristan Glatard}
 
@@
 and cost reduction of infrastructure. OS-level virtualization gained a lot of interest when Docker was
-introduced in 2013~\cite{gantikow2016providing}. However, it has security concerns due to which it
+introduced in 2013~\cite{gantikow2016providing}. However, Docker has security concerns due to which it
 is not supported by High Performance
@@
 
+\begin{comment}
 \begin{figure}
@@
 \end{figure}
+\end{comment}
 
@@
 \end{figure}
-
+\end{comment}
 \textit{Privilege Escalation} A malicious attacker can break out of the container
@@
 are used by containers to mitigate these threats to a certain extent. Security
-of containers is still most concerning issue. According to a Forrester survey~\cite{} done in January
-2015, security is the
+of containers is still most concerning issue. According to a Forrester survey~\cite{bettini2015vulnerability}
+done in January 2015, security is the
 biggest concern while deploying containers.
@@
 then scanning the running container.
-Here, we focus mainly on vulnerability scanning and not on malware.
+Here, we focus mainly on vulnerability scanning.
+\begin{comment}
 Malware is a computer software that is specially designed to attack the target computer,
-whereas vulnerability is a weakness in the developer's software that can be used
+whereas 
+\end{comment}
+Vulnerability is a weakness in the developer's software that can be used
 by the attacker to perform unathorized actions on the target computer.
@@
 containers are used on Compute Canada HPC cluster.
-We are not the first to work on vulnerabilities inside container images but
-the existing research work on containers focuses mainly on the security of Docker
+The existing research work on containers focuses mainly on the security of Docker
 containers.
@@
 security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
-and have scanned vulnerabilities on Docker hub~\cite{Shu2017, gummaraju2015over}.
+and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
 Also Singularity came up with Stools, which can be used for scanning Singularity images
@@
 
-\subsection{Container Engine: Singularity}
+\subsection{Container Engines}
+
+\subsection{Singularity}
 
@@
 Currently, there are 27 BIDS apps available and all are using different Docker images.
+%\begin{figure}
+%\csvreader[%
+% respect all,%
+%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
+%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
+%      \begin{adjustbox}{max width=\columnwidth},
+%  after reading=\end{adjustbox},
+% tabular={c |c | c | c | c},
+%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
+% late after line= \\,
+%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
+%]{results.csv}{}{\csvlinetotablerow}%
+%       \centering
+%	\caption{Existing number of Vulnerabilities}
+%\end{figure}
 
-\begin{figure}
-  \centering
-	\includegraphics[width=\columnwidth]{Figures/bids_table.png}
-  \caption{All Container images used by BIDS apps.}
-  \label{fig:bids_apps}
-\end{figure}
-
+\begin{comment}
 \subsubsection{ReproNim}
@@
 
+\end{comment}
+
+\subsection{Linux Distributions}
+
+BIDS and Boutiques images that we took for our experiment have diverse Linux
+distributions such as Ubuntu, Centos, Debian, and Alpine.
+Some Ubuntu distributions that are present inside images are old enough
+that Ubuntu has stopped providing support such as 14.04 Long Term Support (LTS), 17.04, and 17.10. These
+distributions have reached End Of Life (EOL). They are still used in images, and
+as there are no options of getting updates due to EOL, it results in vulnerable images.
+However, Extended Security Maintenance 
+(ESM) can be requested for Ubuntu 14.04 but it is not feasible to use inside images.
+
 \subsection{Image Update Process}
@@
 packages from images, which in turn reduces the number of vulnerabilities
-present in images. To update container images we used a bash script
-which is given in Figure~\ref{}.
-
-\begin{listing}
-\begin{minted}[frame=single,
-               framesep=3mm,
-               linenos=false,
-               xleftmargin=0pt,
-               tabsize=4]{bash}
-#!/usr/bin/env bash
-
-function die {
-	echo $1
-	exit 1
-}
-
-function find-pm {
-		(type $1 &> /dev/null && echo "> Found $1") || \
-		(echo "> $1 not found" && return 1)
-}
-
-\rm -f .updated
-find-pm yum && (yum update -y && touch .updated) 
-find-pm apt && (apt update -y && apt upgrade -y \
-&& apt autoremove -y && apt autoclean -y \
-&& touch .updated)
-test -f .updated || die "Cannot find package manager \
-or update failed"	       
-\end{minted}
-\caption{update.sh}
-\label{listing:update.sh}
-\end{listing}
-
-\begin{listing}
-\begin{minted}[frame=single,
-               framesep=3mm,
-               linenos=false,
-               xleftmargin=0pt,
-	       tabsize=4]{bash}
-#!/usr/bin/env bash
-
-set -ue
-
-function usage {
-	echo "$0 <image_list>"
-	exit 1
-}
-
-if [ $# -lt 1 ]
-then
-	usage
-fi
-
-for image in $*
-do
-	echo -n "Updating image ${image}... "
-	docker run -e /bin/bash -v $PWD:$PWD -w \
-	$PWD ${image} ./update.sh &>${image}.log \
-	&& echo "[ OK ]"
-	echo -n "Commiting updated image... "
-	ID=$(docker ps -a | head -2 | awk \
-	'$1!="CONTAINER" {print $1}')
-	docker commit ${ID} updated_${image} \
-	&& echo "[ OK ]"
-done
-\end{minted}
-\caption{update-images.sh}
-\label{listing:update-images.sh}
-\end{listing}
+present in images.
 
@@
 image, which is available on Docker Hub. Anchore Engine CLI provides
-command line interface in addition to Anchore Engine REST API. Anchore
-Engine CLI can be installed directly on the host and used to inspect
-images.
-
-\begin{figure}
-  \centering
-  \includegraphics[width=.7\columnwidth]{Figures/anchore.png}
-  \caption{Databases used by Anchore.}
-        \label{fig:anchore_db}
-\end{figure}
-
-\TG{You should refer to the vulnerability databases used, and explain how
-software components, for instance files, are matched to these databases. Is
-the matching based on file checksum?}
+command line interface in addition to Anchore Engine REST API. It can be
+installed directly on the host and used to inspect images.
+Anchore compares package versions, which are present inside the
+image, with the vulnerability database to flag vulnerabilities.
 
@@
 
-\begin{figure}
-  \centering
-  \includegraphics[width=.7\columnwidth]{Figures/vuls.png}
-  \caption{Databases used by Vuls.}
-	\label{fig:vuls_db}
-\end{figure}
+\subsection{Clair Scanner}
+
+CoreOS originally created Clair, which is a static vulnerability scanner for containers which
+currently support App Container (appc) and Docker~\cite{coreos_2019}. The main goal of the
+tool is to provide a transparent look of container’s security. Consequently, it is
+named as Clair, simply implying clear. Clair scans container images in regular
+intervals, and stores metadata of vulnerabilities, after getting from configured
+set of sources. Clair API can be used by clients to query its database to get
+the list of vulnerabilities that a particular image has. Clair sends a notification
+to alert systems that there is an updation in the vulnerability metadata. Quay
+registery uses Clair internally as the security engine. However, Clair does not 
+provide facility of comparing
+the vulnerability list of a particular image against a whitelist~\cite{arminc_2019}. So to remove
+that drawback, another tool from CoreOS, Clair Scanner can be used. It scans image, prepares the list of
+vulnerabilities, compares that list against the whitelist, and flags vulnerabilities
+that are not present in whitelist.
 
@@
 
-%\bibliographystyle{vancouver-authoryear}
+\section{Results}
+
+\subsection{Existing Vulnerabilities}
+
+Tables show results of scanning BIDS and Boutiques images with above discussed three scanners.
+The number of vulnerabilities reported by these scanners are drastically different from each other.
+The question arises why these scanners report different number and type of vulnerabilities.
+How their logic differs and what exactly is making these results different than each other.
+According to our investigation of these results pricisely, below are some of the reasons of
+getting different results from these scanners. These reasons include bugs in scanner 's logic,
+some scanners ignoring vulnerabilities in a particular package, referring to different databases,
+how frequently they are updating their database, etc,. We have explained these differences below in detail
+and have provided an example with each reason to make it clear.
+
+\begin{figure}
+\csvreader[%
+ respect all,%
+  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
+      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
+      \begin{adjustbox}{max width=\columnwidth},
+  after reading=\end{adjustbox},
+ tabular={c |c | c | c | c},
+        table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
+ late after line= \\,
+        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
+]{results.csv}{}{\csvlinetotablerow}%
+       \centering
+        \caption{Existing number of Vulnerabilities}
+\end{figure}
+
+\begin{figure}[!htb]
+        {\includegraphics[width=\columnwidth]
+        {Figures/vulngraph.png}}
+        \caption{\label{fig:graph1} Scatterplot representing \#Packages and \#Vulnerabilities}
+      \end{figure}
+
+\subsection{Comparisons between Scanners}
+
+\subsection{V-C}
+
+V-C represents extra vulnerabilities that are shown by Vuls than Clair.
+So the next question is why they are not shown by Clair then. 
+Below are some reasons to answer that question:
+\begin{enumerate}
+
+\item\textbf{With Status as “Not-affected”-} It means these vulnerabilities are affecting Ubuntu but they are not 
+affecting particular Ubuntu release that is present inside the image. The reason why its not affecting 
+that release is also mentioned. For example, one reason can be that code which is creating issue is not 
+present in that release etc. For example CVE-2015-2305 is not affecting package cups in Trusty.
+
+\item\textbf{Ignored(reached end-of-life)-} These vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life 
+but does not exist (status as “DNE”) in Ubuntu 14.04 ESM release. As Clair is only referring Ubuntu 14.04 ESM 
+release it do not detect these vulnerabilities. For example CVE-2017-9994.
+
+\item\textbf{Not present in Ubuntu 14.04 ESM release-} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
+are not detected by Clair but they affect Ubuntu 14.04 LTS That’s why detected by Vuls. For example, CVE-2017-1375.
+
+\item\textbf{False negatives by Clair-} Clair is missing vulnerabilities that it should detect. For example CVE-2016-9082 
+is present in package cairo in Xenial release and it is not detected by Clair.
+\end{enumerate}
+
+\subsection{C-V}
+
+C-V represents extra vulnerabilities that are shown by Clair than Vuls. Following are the reasons to explain that:
+
+\begin{enumerate}
+\item \textbf{False positives by Clair-}These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
+present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
+Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274.
+\item\textbf{False Negatives by Vuls-} For example CVE-2019-5094.
+\end{enumerate}
+
+\subsection{A-C}
+
+A-C represents extra vulnerabilities shown by Anchore than Clair. Below are the reasons:
+\begin{enumerate}
+	\item Linux Package: Clair is not detecting all vulnerabilities in the source “Linux” package. 
+		For example CVE-2019-9506.
+	\item Ignored(reached end-of-life): These vulnerabilities are ignored in Ubuntu 14.04 LTS as it 
+		reached end-of-life but does not exist (DNE) in ESM release. As Clair is only referring 
+		Ubuntu 14.04 ESM release it do not detect it. For example CVE-2017-994
+	\item Database difference: Clair is using a Docker image for database. So it is not updated everyday. 
+		When I scanned images I used the latest available container. For example CVE-2019-5094 was not 
+		updated in Clair container that time.
+	\item False negatives by Clair: Clair is missing vulnerabilities that it should detect. For example 
+		CVE-2016-9082 is present in package cairo in Xenial release and it is not detected by Clair
+\end{enumerate}
+
+\subsection{C-A}
+C-A represents the vulnerabilities that are not detected by Anchore. Below are the reasons:
+\begin{enumerate}
+
+	\item\textbf{EPOCH bug-} There is a bug in the Anchore logic due to which some vulnerabilities are 
+		not detected by Anchore. This bug gets triggered when package’s version have epoch 
+		(1:3.3.9-1ubuntu2.3)  in it. For example CVE-2018-1125 in procps package
+	\item\textbf{Ignored (out of standard support) bug-} There is another bug in Anchore due to 
+		which it is not able to detect some vulnerabilities. Due to this bug Anchore does not detect 
+		vulnerabilities which have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
+		But if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
+		For example CVE-2019-13565 in Ubuntu 14.04
+	\item\textbf{Ignored (reached end-of-life)-}Some vulnerabilities have status as “ignored (reached end-of-life)” 
+		so Anchore checks the last status of these vulnerabilities whether OS package was vulnerable to the cve 
+		prior to the end-of-life. If it was vulnerable only then Anchore will report it, otherwise not. But this 
+		vulnerability is present in Ubuntu 14.04 ESM release Clair is reporting that. For example CVE-2019-9924
+\end{enumerate}
+
+\subsection{A-V}
+
+A-V represents the vulnerabilities that are detected by Anchore but not detected by Vuls. Below are the reasons 
+of these differences:
+\begin{enumerate}
+
+	\item\textbf{Linux Package-} Vuls is not detecting all vulnerabilities in the source “Linux” package. 
+		For example CVE-2019-9506
+	\item\textbf{False Negatives by Vuls-} Vuls is missing some of the vulnerabilities that it should detect. 
+		For example CVE-2019-5094
+\end{enumerate}
+
+\subsection{V-A}
+V-A represents the vulnerabilities that are detected by Vuls but not detected by Anchore. Below are the reasons:
+\begin{enumerate}
+\item\textbf{EPOCH bug-} There is a bug in the Anchore logic due to which some vulnerabilities are not detected 
+	by Anchore. This bug gets triggered when package’s version have epoch (1:3.3.9-1ubuntu2.3)  in it. 
+		For example CVE-2018-1125 in procps package
+\item\textbf{Ignored (out of standard support) bug-} There is another bug in Anchore due to which it is not 
+	able to detect some vulnerabilities. Due to this bug Anchore does not detect vulnerabilities which 
+		have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. But these vulnerabilities 
+		are detected by Vuls in Ubuntu 14.04 LTS. For example CVE-2019-13565 in Ubuntu 14.04
+\item\textbf{With status as “Not-affected”-}  It means these vulnerabilities are affecting Ubuntu but they are not 
+	affecting particular Ubuntu release that is present inside the image. The reason why its not affecting that 
+		release is also mentioned. For example, one reason can be that code which is creating issue is not 
+		present in that release etc. For example CVE-2015-2305 is not affecting package cups in Trusty.
+\item\textbf{Rejected CVEs-} There are some CVE that are rejected because they are duplicate copies of another CVEs. 
+	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753
+	\end{enumerate}
+
+\subsection{Effect Of Update}
+
+The next experiment involves updating all these images and then rescanning them to see how the number of
+vulnerabilities drop inside them. We used a \textit{bash} script to update these images. It will find
+package manager inside the image and then update the image according the package manager it found.
+When these images are rescanned after updation, results changed drastically. However, there are still
+vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
+till date so there is nothing that can be done to remove these vulnerabilties. There are only two
+options either you accept those vulnerabilities and use that image, or you discard that image.
+So one thing is clear here that even if we keep our images up to date there will be still some
+vulnerabilities that we have to face.
+Below given table shows number of vulnerabilities that are detected by Anchore after updating these images.
+
+\begin{figure}[!htb]
+        {\includegraphics[width=\columnwidth]
+        {Figures/afterupdate.png}}
+        \caption{\label{fig:graph2} Scatterplot representing difference in number of vulnerabilities before and 
+	after update of image}
+      \end{figure}
+\subsection{Effect Of Size Reduction}
+
 \bibliography{bibliography}

### 2019-11-12 paper.tex
results section

@@
 for HPC environments. It is used in many clusters including Compute Canada.
-Table \ref{fig:cluster_list} illustrates the reported usage of Singularity on HPC clusters~\cite{kurtzer2017singularity}.
+According to~\cite{kurtzer2017singularity}, Singularity is used in 36 research clusters.
 
@@
 mounted file systems, and devices, which raises security
-concerns. Figure \ref{fig:container-overview} provides overview of the containers architecture.
+concerns.
 They also share three main security threats with other virtualization
@@
 
-To answer that question, we scan all images that are used on Compute
+To answer that question, we scan images that are used on Compute
 Canada clusters by neuroscience field. Scanning refers to the practice of
@@
 
-\TG{paper suggested by Emad Shihab.}
-
 This paper is organized as follows: in next section, we provide description
@@
 
-\subsection{Singularity}
+\subsubsection{Singularity}
 
@@
 
-\subsection{Clair Scanner}
+\subsubsection{Clair Scanner}
 
@@
 
+\begin{comment}
 \subsection{CBRAIN}
@@
 run pre-defined applications on the cluster through the CBRAIN portal.
+\end{comment}
+\section{Results}
 
-\section{Results}
+In this section, we present results of three experiments that are carried out to see
+how the number of vulnerabilities vary inside images. First experiment involves scanning
+these images as it is to see how vulnerable they are. For scanning we use three different scanners
+to see if all are reporting same vulnerabilities or not. Second experiment involves updating
+all these images and then rescanning. The last experiment involves shrinking the size of the image
+meaning that removing all unnecessary packages from the image to see the effect on the number of
+vulnerabilities present inside the image.
 
@@
 
-Tables show results of scanning BIDS and Boutiques images with above discussed three scanners.
-The number of vulnerabilities reported by these scanners are drastically different from each other.
-The question arises why these scanners report different number and type of vulnerabilities.
-How their logic differs and what exactly is making these results different than each other.
-According to our investigation of these results pricisely, below are some of the reasons of
-getting different results from these scanners. These reasons include bugs in scanner 's logic,
-some scanners ignoring vulnerabilities in a particular package, referring to different databases,
-how frequently they are updating their database, etc,. We have explained these differences below in detail
-and have provided an example with each reason to make it clear.
+Table~\ref{table1} shows results of scanning BIDS and Boutiques images with three scanners namely
+Anchore, Clair, and Vuls. These scanners are taking vulnerability feed from different sources. For
+example for Ubuntu OS distribution, Anchore refers to Ubuntu launchpad database, Clair refers to
+Ubuntu CVE Tracker, whereas Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
+The interesting point in the table is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
+meaning that images with these distributions are impossible to scan with Vuls. Also, it is interesting to note that
+Anchore reports more number of vulnerabilities than Clair and Vuls for all images except that have Centos OS.
+Additionally, we notice that Alpine and Centos OS distributions have less number of vulnerabilities as
+compared to Ubuntu and Debian.
 
-\begin{figure}
+\begin{table}
 \csvreader[%
@@
   before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
-      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
       \begin{adjustbox}{max width=\columnwidth},
@@
        \centering
-        \caption{Existing number of Vulnerabilities}
-\end{figure}
+	\caption{\label{table1}Existing number of Vulnerabilities}
+\end{table}
 
@@
 
+The number and type of vulnerabilities reported by these scanners are drastically different from each other.
+The question arises why these scanners report different number and type of vulnerabilities.
+How their logic differs and what exactly is making these results different than each other.
+According to our investigation of these results precisely, below are some of the reasons of
+getting different results from these scanners. These reasons include bugs in scanner's logic,
+some scanners ignoring vulnerabilities in a particular package, referring to different databases,
+how frequently they are updating their database, etc,. We have explained these differences below in detail
+and have provided an example with each reason to make it clear.
+
 \subsection{V-C}
@@
 Below are some reasons to answer that question:
+
 \begin{enumerate}
@@
 that release is also mentioned. For example, one reason can be that code which is creating issue is not 
-present in that release etc. For example CVE-2015-2305 is not affecting package cups in Trusty.
+present in that release etc. In other words, we can say that these are false positives by Vuls.
+For example CVE-2015-2305 is not affecting package cups in Trusty.
 
@@
 \begin{enumerate}
-	\item Linux Package: Clair is not detecting all vulnerabilities in the source “Linux” package. 
+	\item\textbf{Linux Package-} Clair is not detecting all vulnerabilities in the source “Linux” package. 
 		For example CVE-2019-9506.
-	\item Ignored(reached end-of-life): These vulnerabilities are ignored in Ubuntu 14.04 LTS as it 
+	\item\textbf{Ignored(reached end-of-life)-} These vulnerabilities are ignored in Ubuntu 14.04 LTS as it 
 		reached end-of-life but does not exist (DNE) in ESM release. As Clair is only referring 
-		Ubuntu 14.04 ESM release it do not detect it. For example CVE-2017-994
-	\item Database difference: Clair is using a Docker image for database. So it is not updated everyday. 
+		Ubuntu 14.04 ESM release it do not detect it. For example CVE-2017-994.
+	\item\textbf{Database difference-} Clair is using a Docker image for database. So it is not updated everyday. 
 		When I scanned images I used the latest available container. For example CVE-2019-5094 was not 
 		updated in Clair container that time.
-	\item False negatives by Clair: Clair is missing vulnerabilities that it should detect. For example 
-		CVE-2016-9082 is present in package cairo in Xenial release and it is not detected by Clair
+	\item\textbf{False negatives by Clair-} Clair is missing vulnerabilities that it should detect. For example 
+		CVE-2016-9082 is present in package cairo in Xenial release and it is not detected by Clair.
 \end{enumerate}
@@
 
-	\item\textbf{EPOCH bug-} There is a bug in the Anchore logic due to which some vulnerabilities are 
+	\item\textbf{Epoch bug-} There is a bug in the Anchore logic due to which some vulnerabilities are 
 		not detected by Anchore. This bug gets triggered when package’s version have epoch 
-		(1:3.3.9-1ubuntu2.3)  in it. For example CVE-2018-1125 in procps package
+		(1:3.3.9-1ubuntu2.3)  in it. For example CVE-2018-1125 in procps package.
 	\item\textbf{Ignored (out of standard support) bug-} There is another bug in Anchore due to 
@@
 		But if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
-		For example CVE-2019-13565 in Ubuntu 14.04
+		For example CVE-2019-13565 in Ubuntu 14.04.
 	\item\textbf{Ignored (reached end-of-life)-}Some vulnerabilities have status as “ignored (reached end-of-life)” 
@@
 		prior to the end-of-life. If it was vulnerable only then Anchore will report it, otherwise not. But this 
-		vulnerability is present in Ubuntu 14.04 ESM release Clair is reporting that. For example CVE-2019-9924
+		vulnerability is present in Ubuntu 14.04 ESM release so Clair is reporting that. For example CVE-2019-9924.
 \end{enumerate}
@@
 \begin{enumerate}
-\item\textbf{EPOCH bug-} There is a bug in the Anchore logic due to which some vulnerabilities are not detected 
+\item\textbf{Epoch bug-} There is a bug in the Anchore logic due to which some vulnerabilities are not detected 
 	by Anchore. This bug gets triggered when package’s version have epoch (1:3.3.9-1ubuntu2.3)  in it. 
@@
 The next experiment involves updating all these images and then rescanning them to see how the number of
-vulnerabilities drop inside them. We used a \textit{bash} script to update these images. It will find
-package manager inside the image and then update the image according the package manager it found.
+vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
+present in our github repository \href{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}
+{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
+will find package manager inside the image and then update the image according the package manager it finds.
 When these images are rescanned after updation, results changed drastically. However, there are still
@@
 till date so there is nothing that can be done to remove these vulnerabilties. There are only two
-options either you accept those vulnerabilities and use that image, or you discard that image.
+options, either you accept those vulnerabilities and use that image, or you discard that image.
 So one thing is clear here that even if we keep our images up to date there will be still some
 vulnerabilities that we have to face.
-Below given table shows number of vulnerabilities that are detected by Anchore after updating these images.
+Figure~\ref{fig:graph2}shows number of vulnerabilities that are detected by Anchore after updating these images.
 
@@
         {\includegraphics[width=\columnwidth]
-        {Figures/afterupdate.png}}
+        {Figures/aferupdatewithpackage.png}}
         \caption{\label{fig:graph2} Scatterplot representing difference in number of vulnerabilities before and 

### 2020-01-17 paper.tex

@@
 
-\title{Risks of Running Vulnerable Container Images for Data Analysis on HPC
-Clusters}
+\title{Vulnerability Analysis of Container Images in Neuroimaging field}
 
@@
 
+\begin{comment}
 As we are taking a particular use case of containers from
@@
 used by CONP to function.
+\end{comment}
 
@@
 Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
-
+We used Singularity version $2.5.2$ in our experiments.
 Users can easily access files, devices, sockets, ports of the host system from
@@
 for multi-tenant shared enviornments. Due to this reason, Docker is not
-supported by HPC environments. However, Docker containers can be imported into
+supported by HPC environments. However, Docker images can be imported into
 Singularity and then used on HPC clusters.
@@
 required dependencies and libraries.
-Nowadays, two most popular containerization tools used are Docker and Singularity.
-Both have different image format. Below we provide description of both image
+Both, Docker and Singularity, have different image format. Below we provide description of both image
 formats.
@@
 with respect to the layer below. DockerHub uses gzip compression for
-transferring layers. There are two ways to create a Docker image. The
+transferring layers. \begin{comment}There are two ways to create a Docker image. The
 first is to use an existing Docker image as a base image and then build a
@@
 saved as a new layer of the Docker image. The second way is to build a new
-Docker image from scratch. Docker supports several different storage drivers.
+Docker image from scratch.\end{comment} Docker supports several different storage drivers.
 \textit{Overlay2} is the preferred storage driver used by Docker for all currently
@@
 used for verification purposes. Singularity containers use Squashfs file format
-by default. However, it also supports two other formats i.e \textit{sandbox} format
+by default. It is read-only file system in Linux, which uses compression for files,
+inodes, and directories. However, Singularity also supports two other 
+formats i.e \textit{sandbox} format
 (which is just a chroot
@@
 
-BIDS and Boutiques images that we took for our experiment have diverse Linux
-distributions such as Ubuntu, Centos, Debian, and Alpine.
-Some Ubuntu distributions that are present inside images are old enough
-that Ubuntu has stopped providing support such as 14.04 Long Term Support (LTS), 17.04, and 17.10. These
-distributions have reached End Of Life (EOL). They are still used in images, and
-as there are no options of getting updates due to EOL, it results in vulnerable images.
-However, Extended Security Maintenance 
-(ESM) can be requested for Ubuntu 14.04 but it is not feasible to use inside images.
+BIDS app and Boutiques images that we took for our experiment have diverse Linux
+distributions such as Ubuntu, Centos, Debian, and Alpine. In case of Ubuntu, release
+can be of two types i.e regular or LTS(Long Term Support) release.
+Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
+reaches End-Of-Life(EOL), Ubuntu decides whether to provide extended security support or not, which comes
+in the form of Extended Security Maintenance(ESM) release.
+ESM is a paid service that can be requested from Ubuntu to get security 
+updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
+Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
+data in vulnerability databases.
+
+Some Ubuntu distributions that are present inside images have already reached EOL such as 14.04 Long Term Support (LTS),
+17.04, and 17.10. However, Ubuntu is providing ESM support for Ubuntu 14.04. The images in our experiment have Ubuntu 14.04 LTS so scanners should refer
+to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for data it may result
+in false positives and false negatives.
+Also, if these releases with EOL are used in images, there are no chances of getting updates, hence
+resulting in vulnerable images. Additionally, even if ESM release is present for some EOL release it is
+not feasible to use inside images.
 
@@
 
-If there exist vulnerabilities in the container image, then there are two ways
-to proceed, either not to run that image at all, or run only after updating the
+If there exist vulnerabilities in the container image, then we can
+run after updating the
 image. Updating the image involves updating all software packages that are
-inside that image. However, this option effects the reproducibility
+inside that image. We used a bash script(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
+to update all images, which checks
+package manager present inside the image and then according to that it
+updates the image. However, this option effects the reproducibility
 of the image, which means that the image cannot be used to verify research
-findings of other scientists. An alternative approach can be to trim unnecessary
-packages from images, which in turn reduces the number of vulnerabilities
-present in images.
+findings of other scientists.
 
@@
 Out of the various container image scanning tools available to scan Docker images,
-we selected Anchore
-and Vuls because these are the most mature scanning tools. To scan Singularity images
+we selected Anchore~\cite{github_2019}
+and Vuls~\cite{future-architect_2019} because these are the most mature scanning tools. To scan Singularity images
 we use Stools, which is specially designed for Singularity images. This tool internally uses
-ClairScanner tool so we included ClairScanner also in our experiements to compare
-performance of both the tools.
+Clair Scanner tool so we included ClairScanner also in our experiements to compare
+performance of both the tools. So total there are three scanners for Docker images
+and one scanner for Singularity images.
 
@@
 It provides visibility and transparency of the container environment.
-Anchore offers services in two ways: Anchore Engine and Anchore Engine
+It offers services in two ways: Anchore Engine and Anchore Engine
 Command Line Interface (CLI). Anchore Engine is available as a Docker
@@
 image, with the vulnerability database to flag vulnerabilities.
-
+To get vulnerability feed of various OS distribution, Anchore refers to
+different sources. For example Ubuntu launchpad database is used for Ubuntu. 
 \subsubsection{Vuls}
@@
 changelogs, which puts more load on the target server.
+Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
+The interesting point is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
+meaning that images with these distributions are impossible to scan with Vuls.
 
@@
 currently support App Container (appc) and Docker~\cite{coreos_2019}. The main goal of the
-tool is to provide a transparent look of container’s security. Consequently, it is
-named as Clair, simply implying clear. Clair scans container images in regular
+tool is to provide a transparent look of container’s security. Clair scans container images in regular
 intervals, and stores metadata of vulnerabilities, after getting from configured
@@
 that are not present in whitelist.
+Clair Scanner refers to Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
 
@@
 
-\href{https://github.com/singularityhub/stools}{Stools} combines CoreOS's ClairScanner with the Continuous Integration (Travis and
+\href{https://github.com/singularityhub/stools}{Stools} combines CoreOS's Clair Scanner with the Continuous Integration (Travis and
 Circle) for scanning Singularity images for vulnerabilities.
-Initially, ClairScanner was intented to scan Docker Containers. This tool does not fit well
+Initially, Clair Scanner was intented to scan Docker Containers. This tool does not fit well
 to scan Singularity images because of the different image formats. Docker layers
@@
 services also offer running containers. So Stools combined both the concepts.
-It involves spinning a ClairScanner container during testing and building a
+It involves spinning a Clair Scanner container during testing and building a
 Singularity image, and scanning it for filesystem before the image is finalized.
@@
 
-Table~\ref{table1} shows results of scanning BIDS and Boutiques images with three scanners namely
-Anchore, Clair, and Vuls. These scanners are taking vulnerability feed from different sources. For
-example for Ubuntu OS distribution, Anchore refers to Ubuntu launchpad database, Clair refers to
-Ubuntu CVE Tracker, whereas Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
-The interesting point in the table is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
-meaning that images with these distributions are impossible to scan with Vuls. Also, it is interesting to note that
-Anchore reports more number of vulnerabilities than Clair and Vuls for all images except that have Centos OS.
+Figure~\ref{table1} shows results of scanning BIDS and Boutiques images with three scanners namely Anchore,
+Clair scanner and Vuls. Venn Diagram in Figure~\cite{fig:venn} summarizes this table. It is interesting to note that
+Anchore reports 4453 different vulnerabilities, which is way more than both Clair and Vuls.
 Additionally, we notice that Alpine and Centos OS distributions have less number of vulnerabilities as
 compared to Ubuntu and Debian.
-
 \begin{table}
@@
 \begin{figure}[!htb]
-        {\includegraphics[width=\columnwidth]
+        {\includegraphics[scale=2.5,width=\columnwidth]
+        {Figures/vennDiagram.png}}
+        \caption{\label{fig:venn} Venn Diagram representing different scanner results}
+\end{figure}
+
+\begin{figure}[!htb]
+        {\includegraphics[scale=2,width=\columnwidth]
         {Figures/vulngraph.png}}
@@
 According to our investigation of these results precisely, below are some of the reasons of
-getting different results from these scanners. These reasons include bugs in scanner's logic,
+getting different results from these scanners. These reasons include bugs in scanners,
 some scanners ignoring vulnerabilities in a particular package, referring to different databases,
-how frequently they are updating their database, etc,. We have explained these differences below in detail
+how frequently they are updating their databases, etc,. We have explained these differences below in detail
 and have provided an example with each reason to make it clear.
 
-\subsection{V-C}
+Venn Diagram~\cite{fig:venn} illustrates that Anchore reports 4453 different vulnerabilities that are reported
+by Vuls and Clair. Out of this 4443 vulnerabilities are present in linux-kernel-headers. These are ignored by
+both Clair and Vuls.
 
-V-C represents extra vulnerabilities that are shown by Vuls than Clair.
-So the next question is why they are not shown by Clair then. 
-Below are some reasons to answer that question:
+\textbf{Linux Package-} Clair and Vuls are ignoring all vulnerabilities in the "Linux” package
+which is linux-kernel-headers. 4443 out of 4453 vulnerabilities difference is due to linux-kernel-headers.
+For example CVE-2019-9506 is not detected by.
 
-\begin{enumerate}
-
-\item\textbf{With Status as “Not-affected”-} It means these vulnerabilities are affecting Ubuntu but they are not 
+\textbf{With Status as “Not-affected”-} It means these vulnerabilities are affecting Ubuntu but they are not 
 affecting particular Ubuntu release that is present inside the image. The reason why its not affecting 
@@
 
-\item\textbf{Ignored(reached end-of-life)-} These vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life 
+\textbf{Ignored(reached end-of-life)-} These vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life 
 but does not exist (status as “DNE”) in Ubuntu 14.04 ESM release. As Clair is only referring Ubuntu 14.04 ESM 
@@
 
-\item\textbf{Not present in Ubuntu 14.04 ESM release-} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
+\textbf{Not present in Ubuntu 14.04 ESM release-} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
 are not detected by Clair but they affect Ubuntu 14.04 LTS That’s why detected by Vuls. For example, CVE-2017-1375.
 
-\item\textbf{False negatives by Clair-} Clair is missing vulnerabilities that it should detect. For example CVE-2016-9082 
+\textbf{False negatives by Clair-} Clair is missing vulnerabilities that it should detect. For example CVE-2016-9082 
 is present in package cairo in Xenial release and it is not detected by Clair.
-\end{enumerate}
 
-\subsection{C-V}
-
-C-V represents extra vulnerabilities that are shown by Clair than Vuls. Following are the reasons to explain that:
-
-\begin{enumerate}
-\item \textbf{False positives by Clair-}These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
+\textbf{False positives by Clair-}These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
 present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
 Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274.
-\item\textbf{False Negatives by Vuls-} For example CVE-2019-5094.
-\end{enumerate}
 
-\subsection{A-C}
-
-A-C represents extra vulnerabilities shown by Anchore than Clair. Below are the reasons:
-\begin{enumerate}
-	\item\textbf{Linux Package-} Clair is not detecting all vulnerabilities in the source “Linux” package. 
-		For example CVE-2019-9506.
-	\item\textbf{Ignored(reached end-of-life)-} These vulnerabilities are ignored in Ubuntu 14.04 LTS as it 
-		reached end-of-life but does not exist (DNE) in ESM release. As Clair is only referring 
-		Ubuntu 14.04 ESM release it do not detect it. For example CVE-2017-994.
-	\item\textbf{Database difference-} Clair is using a Docker image for database. So it is not updated everyday. 
+\textbf{Database difference-} Clair is using a Docker image for database. So it is not updated everyday. 
 		When I scanned images I used the latest available container. For example CVE-2019-5094 was not 
 		updated in Clair container that time.
-	\item\textbf{False negatives by Clair-} Clair is missing vulnerabilities that it should detect. For example 
-		CVE-2016-9082 is present in package cairo in Xenial release and it is not detected by Clair.
-\end{enumerate}
 
-\subsection{C-A}
-C-A represents the vulnerabilities that are not detected by Anchore. Below are the reasons:
-\begin{enumerate}
-
-	\item\textbf{Epoch bug-} There is a bug in the Anchore logic due to which some vulnerabilities are 
+\textbf{Epoch bug-} There is a bug in the Anchore logic due to which some vulnerabilities are 
 		not detected by Anchore. This bug gets triggered when package’s version have epoch 
 		(1:3.3.9-1ubuntu2.3)  in it. For example CVE-2018-1125 in procps package.
-	\item\textbf{Ignored (out of standard support) bug-} There is another bug in Anchore due to 
+
+\textbf{Ignored (out of standard support) bug-} There is another bug in Anchore due to 
 		which it is not able to detect some vulnerabilities. Due to this bug Anchore does not detect 
@@
 		For example CVE-2019-13565 in Ubuntu 14.04.
-	\item\textbf{Ignored (reached end-of-life)-}Some vulnerabilities have status as “ignored (reached end-of-life)” 
+
+\textbf{Ignored (reached end-of-life)-}Some vulnerabilities have status as “ignored (reached end-of-life)” 
 		so Anchore checks the last status of these vulnerabilities whether OS package was vulnerable to the cve 
@@
 		vulnerability is present in Ubuntu 14.04 ESM release so Clair is reporting that. For example CVE-2019-9924.
-\end{enumerate}
 
-\subsection{A-V}
+\textbf{False Negatives by Vuls-} Vuls is missing some of the vulnerabilities that it should detect. 
+		For example CVE-2019-5094
 
-A-V represents the vulnerabilities that are detected by Anchore but not detected by Vuls. Below are the reasons 
-of these differences:
-\begin{enumerate}
-
-	\item\textbf{Linux Package-} Vuls is not detecting all vulnerabilities in the source “Linux” package. 
-		For example CVE-2019-9506
-	\item\textbf{False Negatives by Vuls-} Vuls is missing some of the vulnerabilities that it should detect. 
-		For example CVE-2019-5094
-\end{enumerate}
-
-\subsection{V-A}
-V-A represents the vulnerabilities that are detected by Vuls but not detected by Anchore. Below are the reasons:
-\begin{enumerate}
-\item\textbf{Epoch bug-} There is a bug in the Anchore logic due to which some vulnerabilities are not detected 
-	by Anchore. This bug gets triggered when package’s version have epoch (1:3.3.9-1ubuntu2.3)  in it. 
-		For example CVE-2018-1125 in procps package
-\item\textbf{Ignored (out of standard support) bug-} There is another bug in Anchore due to which it is not 
-	able to detect some vulnerabilities. Due to this bug Anchore does not detect vulnerabilities which 
-		have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. But these vulnerabilities 
-		are detected by Vuls in Ubuntu 14.04 LTS. For example CVE-2019-13565 in Ubuntu 14.04
-\item\textbf{With status as “Not-affected”-}  It means these vulnerabilities are affecting Ubuntu but they are not 
-	affecting particular Ubuntu release that is present inside the image. The reason why its not affecting that 
-		release is also mentioned. For example, one reason can be that code which is creating issue is not 
-		present in that release etc. For example CVE-2015-2305 is not affecting package cups in Trusty.
-\item\textbf{Rejected CVEs-} There are some CVE that are rejected because they are duplicate copies of another CVEs. 
+\textbf{Rejected CVEs-} There are some CVE that are rejected because they are duplicate copies of another CVEs. 
 	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753
-	\end{enumerate}
 

### 2020-01-17 paper.tex

@@
 Clair Scanner refers to Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
+For that purpose a Docker image is maintained that contains Ubuntu CVE tracker database.
+Whenever Ubuntu updated its database, this image is also updated with the required information.
+We performed scanning on 2019-09-25 and for our experiments, we used a Docker image that was 
+latest updated i.e with the tag 2019-09-18. So it means that Clair Scanner's database was
+old by one week.
 
@@
 
-Figure~\ref{table1} shows results of scanning BIDS and Boutiques images with three scanners namely Anchore,
-Clair scanner and Vuls. Venn Diagram in Figure~\cite{fig:venn} summarizes this table. It is interesting to note that
-Anchore reports 4453 different vulnerabilities, which is way more than both Clair and Vuls.
-Additionally, we notice that Alpine and Centos OS distributions have less number of vulnerabilities as
-compared to Ubuntu and Debian.
+Figure~\ref{fig:graph1} represents the number of vulnerabilities that are present inside images.
+This figure shows that as the number of packages increases in the image, the number of vulnerabilities
+also get increased for Ubuntu OS distribution. The figure also infers that Alpine distribution, being the
+light weight distribution, have least number of vulnerabilities, whereas Ubuntu contains highest number of
+vulnerabilities. Debian contains highest number of critical vulnerabilities among Ubuntu, Alpine, and Centos.
+
 \begin{table}
@@
 
+\begin{table}
+\csvreader[%
+ respect all,%
+  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
+      \begin{adjustbox}{max width=\columnwidth},
+  after reading=\end{adjustbox},
+ tabular={c|c},
+	table head ={Image Tag} & {Image Name}\\\hline,
+ late after line= \\,
+        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
+]{names.csv}{}{\csvlinetotablerow}%
+       \centering
+	\caption{\label{table2}Image names}
+\end{table}
+
 \begin{figure}[!htb]
@@
         {\includegraphics[scale=2,width=\columnwidth]
-        {Figures/vulngraph.png}}
+        {Figures/vulngraph4.png}}
         \caption{\label{fig:graph1} Scatterplot representing \#Packages and \#Vulnerabilities}
@@
 
-The number and type of vulnerabilities reported by these scanners are drastically different from each other.
+Figure~\ref{table1} shows results of scanning BIDS and Boutiques images with three scanners namely Anchore,
+Clair scanner and Vuls. Venn Diagram in Figure~\cite{fig:venn} summarizes this table. It is interesting to note that
+Anchore reports 4453 different vulnerabilities, which is way more than both Clair and Vuls.
+
+The number and type of vulnerabilities reported by three scanners are drastically different from each other.
 The question arises why these scanners report different number and type of vulnerabilities.
 How their logic differs and what exactly is making these results different than each other.
-According to our investigation of these results precisely, below are some of the reasons of
+
+According to our investigation of these results, below are some of the reasons of
 getting different results from these scanners. These reasons include bugs in scanners,
 some scanners ignoring vulnerabilities in a particular package, referring to different databases,
-how frequently they are updating their databases, etc,. We have explained these differences below in detail
+how frequently they are updating their databases, etc.
+
+We have explained these differences below in detail
 and have provided an example with each reason to make it clear.
 
-Venn Diagram~\cite{fig:venn} illustrates that Anchore reports 4453 different vulnerabilities that are reported
+Venn Diagram~\ref{fig:venn} illustrates that Anchore reports 4453 different vulnerabilities that are reported
 by Vuls and Clair. Out of this 4443 vulnerabilities are present in linux-kernel-headers. These are ignored by
@@
 
-\textbf{Linux Package-} Clair and Vuls are ignoring all vulnerabilities in the "Linux” package
-which is linux-kernel-headers. 4443 out of 4453 vulnerabilities difference is due to linux-kernel-headers.
-For example CVE-2019-9506 is not detected by.
+\textbf{Linux-Kernel-Headers-} Clair Scanner and Vuls are ignoring all vulnerabilities in the Linux-kernel-headers.
+4443 out of 4453 vulnerabilities difference is due to linux-kernel-headers.
+For example CVE-2019-9506 present in linux-libc-dev-4.4.0-31.50 is not detected by both Vuls and Clair Scanner
 
@@
 
-\textbf{Ignored(reached end-of-life)-} These vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life 
-but does not exist (status as “DNE”) in Ubuntu 14.04 ESM release. As Clair is only referring Ubuntu 14.04 ESM 
-release it do not detect these vulnerabilities. For example CVE-2017-9994.
+\textbf{With status as "Ignored(reached end-of-life)"-} Some vulnerabilities have status as “ignored (reached end-of-life)”.
+These vulnerabilities are "ignored" in Ubuntu 14.04 LTS as it reached end-of-life. 
+However, in Ubuntu 14.04 ESM release these vulnerabilities can be present or not.
+Anchore checks the last status of these vulnerabilities whether OS package was vulnerable to the cve
+prior to the end-of-life. If it was vulnerable only then Anchore will report it, otherwise not.
+If this kind of vulnerability is present in ESM release then Clair will report it because Clair Scanner
+only refers ESM release. On the other hand, if the vulnerability
+status in ESM release is "DNE", which means does not exist, then Clair Scanner will not report it. 
+For example CVE-2017-9994 vulnerability. As Ubuntu LTS release is present inside the images so
+Clair Scanner's reference to ESM release is wrong here.
 
-\textbf{Not present in Ubuntu 14.04 ESM release-} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
+\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release-} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
 are not detected by Clair but they affect Ubuntu 14.04 LTS That’s why detected by Vuls. For example, CVE-2017-1375.
@@
 
-\textbf{False positives by Clair-}These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
+\textbf{False positives by Clair-} These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
 present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
@@
 
-\textbf{Database difference-} Clair is using a Docker image for database. So it is not updated everyday. 
-		When I scanned images I used the latest available container. For example CVE-2019-5094 was not 
-		updated in Clair container that time.
+\textbf{Database difference-} As we discussed earlier that Clair Scanner's database was old by one week.
+                So some of the vulnerabilities were not updated yet. For example CVE-2019-5094, which
+		was published on 2019-09-24, was not 
+		updated in Clair Scanner's database that time. Due to which it is missed by Clair Scanner.
 
-\textbf{Epoch bug-} There is a bug in the Anchore logic due to which some vulnerabilities are 
+\textbf{Epoch bug-} There is a bug in the Anchore scanner due to which some vulnerabilities are 
 		not detected by Anchore. This bug gets triggered when package’s version have epoch 
@@
 
-\textbf{Ignored (out of standard support) bug-} There is another bug in Anchore due to 
+\textbf{with status as "Ignored (out of standard support)" bug-} There is another bug in Anchore due to 
 		which it is not able to detect some vulnerabilities. Due to this bug Anchore does not detect 
@@
 		For example CVE-2019-13565 in Ubuntu 14.04.
-
-\textbf{Ignored (reached end-of-life)-}Some vulnerabilities have status as “ignored (reached end-of-life)” 
-		so Anchore checks the last status of these vulnerabilities whether OS package was vulnerable to the cve 
-		prior to the end-of-life. If it was vulnerable only then Anchore will report it, otherwise not. But this 
-		vulnerability is present in Ubuntu 14.04 ESM release so Clair is reporting that. For example CVE-2019-9924.
 

### 2020-02-11 paper.tex
modification till results

@@
 \newcommand{\reprozip}[0]{ReproZip}
+\newcommand{\rom}[1]{\lowercase\expandafter{\romannumeral #1\relax}}
 \newcommand{\TG}[1]{\color{blue}From Tristan: #1\color{black}}
 
-\title{Vulnerability Analysis of Container Images in Neuroimaging field}
+\title{Vulnerability Analysis of Container Images in Neuroimaging}
 
@@
 \author[1]{Bhupinder Kaur}
+\author[1]{Aiman Hanna}
 \author[1]{Tristan Glatard}
-\author[1]{Aiman Hanna}
 
@@
 
+In this section, we present our study methodology. We first
+introduce two container tools used for our experiments: Docker and
+Singularity and their image formats. Then we describe Boutiques and BIDS application frameworks
+from where we took containerized applications for our study. Later, we discuss about 
+various Linux distributions and their releases. Lastly, this section
+provides the description of the scanning tools used.
+
 \begin{comment}
@@
 
-\subsection{Container Engines}
+\subsection{Container Tools}
+
+Tools that are capable of packing and running an application in an isolated environment
+are known as container tools. Alongwith an application they also pack the application's dependencies,
+required libraries and configuration files for the
+application to function properly. This functioning of an application in an isolated environment
+is called a container. They directly run on the Host machine's kernel so they are lightweight.
+Consequently, more containers can be run on a given Host machine as compared to virtual machines.
+
+\subsubsection{Docker}
+
+Docker is a tool to run containers.
+Docker containers are managed by the Docker engine, which is a client-server application and
+consists of the following three main components:
+
+\textit{Docker Daemon:} It acts as a server. It is
+a long running process that manages all Docker images, containers, storage volumes, and networks.
+
+\textit{REST API:} It acts as a interface between the server and the client, and is an API which is used by the applications
+to talk to the \textit{Docker Daemon}.
+
+\textit{Client:} It is a Command Line Interface (CLI) client which is used to interact with the \textit{Docker Daemon}.
+
+%Docker runs a software, \textit{Docker daemon}, on the host machine.
+Docker daemon runs as root, and is remotely controlled through a
+UNIX socket. As Docker Daemon is responsible for launching and managing containers,
+when a container runs, the container is spawned as a
+child process of this root owned daemon.
+
+\begin{comment}
+It is responsible for launching containers, their
+isolation, and spawning shells into the containers. It is also
+responsible for managing Docker images i.e \textit{pull} and \textit{push}
+from image repository, building images from Dockerfiles, signing them, etc.
+When a Docker container runs, the container process is spawned as a
+child of this root owned daemon. 
+\end{comment}
+As Docker users directly interact with the
+Docker daemon through CLI i.e \textit{docker} command, it is possible to force Docker daemon to escalate privileges.
+If a user gets \textit{root} privileges, it introduces unthinkable security risks
+for multi-tenant shared enviornments. Due to this reason, Docker is not
+supported by HPC environments.
 
@@
 
+Singularity is another tool for packing and running applications in containers.
+
 Singularity offers mobility of compute by facilitating portable environments 
-through a single image file~\cite{kurtzer2016singularity}. Once Singularity image
-is created, it is hashed by using SHA256 hashing. Hence, it cannot be changed
+through a single image file~\cite{kurtzer2017singularity}. Once Singularity image
+is created, it is hashed using SHA-256. Hence, it cannot be changed
 once it is created, consequently, it can be used for reproducing the results of
@@
 
-\subsubsection{Docker Engine}
-
-Docker runs a software, \textit{Docker daemon}, on the host machine.
-Docker daemon runs as root, and is remotely controlled through a
-UNIX socket. It is responsible for launching containers, their
-isolation, and spawning shells into the containers. It is also
-responsible for managing Docker images i.e \textit{pull} and \textit{push}
-from image repository, building images from Dockerfiles, signing them, etc..
-When a Docker container runs, the container process is spawned as a
-child of this root owned daemon. As Docker users directly interact with the
-Docker daemon, it is possible to force Docker daemon to escalate privileges.
-If a user gets \textit{root} privileges, it introduces unthinkable security risks
-for multi-tenant shared enviornments. Due to this reason, Docker is not
-supported by HPC environments. However, Docker images can be imported into
-Singularity and then used on HPC clusters.
-
 \subsection{Container Image Formats}
 
-A container image is a package that contains the application along with its
+A container image is a package that contains an application along with its
 required dependencies and libraries.
-Both, Docker and Singularity, have different image format. Below we provide description of both image
+Both, Docker and Singularity, have different image formats. Below we provide description of both image
 formats.
@@
 have the same id across images. Each layer consists of a filesystem diff
-with respect to the layer below. DockerHub uses gzip compression for
-transferring layers. \begin{comment}There are two ways to create a Docker image. The
+with respect to the layer below. 
+\begin{comment}
+DockerHub uses gzip compression for
+transferring layers.There are two ways to create a Docker image. The
 first is to use an existing Docker image as a base image and then build a
@@
 saved as a new layer of the Docker image. The second way is to build a new
-Docker image from scratch.\end{comment} Docker supports several different storage drivers.
+Docker image from scratch.Docker supports several different storage drivers.
 \textit{Overlay2} is the preferred storage driver used by Docker for all currently
@@
 zfs, and vfs}
+\end{comment}
 
@@
 
+On the other hand, Singularity image is a single immutable file and 
+does not contain layers.
+\begin{comment}
 Singularity takes snapshot, locks, and archives the developed application,
@@
 
+\subsubsection{Brain Imaging Data Structure (BIDS) Apps}
+
+BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
+analysis pipelines. It improves usability, accesibility, and reproducibility
+of different applications through containerization.
+At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
+Out of these 27 images, we used 26 images for our experiments because one of them was not available
+on Docker hub.
+
 \subsubsection{Boutiques}
@@
 We used the 49 Boutiques applications published on Zenodo at the time of
-the writing. These applications use 23 different container images,
-including 7 Singularity images and 16 Docker images.
+the writing. These applications use 23 different container images. Out of these images,
+3 images are not found and 2 images were already included in BIDS images.
+Therefore we are left with total 18 Boutiques images which includes 6
+Singularity images and 12 Docker images.
 
@@
 of different applications through containerization.
-Currently, there are 27 BIDS apps available and all are using different Docker images.
+At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
+Out of these 27 images, we used 26 images for our experiments because QAP bids app was not available
+on Docker hub.
+
+So we have total 38 Docker images from both BIDS Apps and Boutiques.
+	Table~\ref{table2} displays the names of all the images that we took in our experiments.
 %\begin{figure}
@@
 distributions such as Ubuntu, Centos, Debian, and Alpine. In case of Ubuntu, release
-can be of two types i.e regular or LTS(Long Term Support) release.
+can be of two types : regular or LTS (Long Term Support).
 Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
-reaches End-Of-Life(EOL), Ubuntu decides whether to provide extended security support or not, which comes
-in the form of Extended Security Maintenance(ESM) release.
+reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
+in the form of Extended Security Maintenance (ESM) release.
 ESM is a paid service that can be requested from Ubuntu to get security 
@@
 Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
-data in vulnerability databases.
+data in vulnerability databases because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
+exists in LTS.
 
-Some Ubuntu distributions that are present inside images have already reached EOL such as 14.04 Long Term Support (LTS),
-17.04, and 17.10. However, Ubuntu is providing ESM support for Ubuntu 14.04. The images in our experiment have Ubuntu 14.04 LTS so scanners should refer
+Ubuntu has ended support for some releases such as 14.04 LTS,
+17.04, and 17.10, which means they have reached EOL. However, Ubuntu is providing optional extended support for Ubuntu 14.04.
+To use this extended support, users have to buy ESM release for Ubuntu 14.04.
+The images in our experiments have Ubuntu 14.04 LTS so scanners should refer
 to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for data it may result
 in false positives and false negatives.
-Also, if these releases with EOL are used in images, there are no chances of getting updates, hence
-resulting in vulnerable images. Additionally, even if ESM release is present for some EOL release it is
-not feasible to use inside images.
+Also, if ubuntu releases with ended support are used in images, there are no chances of getting updates, hence
+resulting in vulnerable images. Additionally, even if extended security is provided for some releases by Ubuntu, it is
+not feasible to use it inside images because it is a paid service.
 
-\subsection{Image Update Process}
+\subsection{Scanning Images}
 
-If there exist vulnerabilities in the container image, then we can
-run after updating the
-image. Updating the image involves updating all software packages that are
-inside that image. We used a bash script(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
-to update all images, which checks
-package manager present inside the image and then according to that it
-updates the image. However, this option effects the reproducibility
-of the image, which means that the image cannot be used to verify research
-findings of other scientists.
+Scanning an image means looking into the image, collecting all the information about the image, and
+finally, using this information to detect vulnerabilities present inside the image.
+Scanning can be broadly categorised into two types: \rom{1} Static Scanning and \rom{2}
+Dynamic Scanning.
+In Static scanning, an image is scanned without running it into a container. In respect to that,
+differnt image features are extracted like installed packages, their versions, files, etc.
+On the other hand, Dynamic scanning involves running a container from the image and then scanning the
+dynamic behaviour of the image.
 
-\subsection{Scanning tools used}
-
+\subsubsection{Scanning tools used}
+\begin{comments}
 Out of the various container image scanning tools available to scan Docker images,
@@
 and one scanner for Singularity images.
+\end{comments}
+
+We used three scanners namely Anchore~\cite{github_2019}, Vuls~\cite{future-architect_2019}, and
+Clair Scanner~\cite{arminc_2019} for scanning Docker images because these are the most
+mature scanners. Out of these scanners, only Vuls uses dynamic scanning and remaining two
+are static scanners.
+Also, we freezed vulnerability databases for these scanners on September 25, 2019 and scanned
+all images to avoid getting different results due to the differences in the scanner's database.
+Lastly, for scanning Singularity images, we used Stools.
 
@@
 packages, non-OS packages (Python, Java, Gem, and Npm), and files.
+\begin{comments}
 Anchore is a set of tools, which users can
@@
 It provides visibility and transparency of the container environment.
-It offers services in two ways: Anchore Engine and Anchore Engine
+\end{comments}
+Anchore Engine can be used in two ways: through Docker image or Anchore
+Command Line Interface (CLI).
+\begin{comments}
+Anchore offers services in two ways: Anchore Engine and Anchore
 Command Line Interface (CLI). Anchore Engine is available as a Docker
 image, which is available on Docker Hub. Anchore Engine CLI provides
-command line interface in addition to Anchore Engine REST API. It can be
+command line interface in addition to Anchore Engine REST API. 
+\end{comments}
+It can be
 installed directly on the host and used to inspect images.
+In our experiments, we used a Docker image to get Anchore Engine version 0.5.0 and Engine Database
+version 0.0.11.
+
 Anchore compares package versions, which are present inside the
@@
 different sources. For example Ubuntu launchpad database is used for Ubuntu.
+
 \subsubsection{Vuls}
@@
 Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
-It is an agentless vulnerability scanner and uses various
-vulnerability databases. Using dynamic scanning technique, it offers
+Using dynamic scanning technique, it offers
 remote and local scan. Remote scan involves setting up only one machine, to
@@
 detect processes that are updated but not yet restarted because if they are not
-restarted, updates are not effective. So fast root scan also detects these pro-
-cesses. Both fast scan and fast root scan are performed offline without Internet
+restarted, updates are not effective. So fast root scan also detects these
+processes. Both fast scan and fast root scan are performed offline without Internet
 access, and put almost no load on the scan target server. Deep scan uses
@@
 Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
+
 The interesting point is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
@@
 
-CoreOS originally created Clair, which is a static vulnerability scanner for containers which
-currently support App Container (appc) and Docker~\cite{coreos_2019}. The main goal of the
+CoreOS originally created Clair, a static vulnerability scanner for containers. 
+\begin{Comments}
+The main goal of the
 tool is to provide a transparent look of container’s security. Clair scans container images in regular
 intervals, and stores metadata of vulnerabilities, after getting from configured
-set of sources. Clair API can be used by clients to query its database to get
+set of sources. 
+\end{comments}	
+Clair API can be used by clients to query its database to get
 the list of vulnerabilities that a particular image has. Clair sends a notification
-to alert systems that there is an updation in the vulnerability metadata. Quay
-registery uses Clair internally as the security engine. However, Clair does not 
+to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
+is a registery to store images privately, uses Clair internally as the security engine. However, Clair does not 
 provide facility of comparing
-the vulnerability list of a particular image against a whitelist~\cite{arminc_2019}. So to remove
+the vulnerability list of a particular image against a whitelist of vulnerabilities that you
+want to ignore~\cite{arminc_2019}. 
+So, to remove
 that drawback, another tool from CoreOS, Clair Scanner can be used. It scans image, prepares the list of
 vulnerabilities, compares that list against the whitelist, and flags vulnerabilities
-that are not present in whitelist.
+that are not present in the whitelist.
 Clair Scanner refers to Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
@@
 Whenever Ubuntu updated its database, this image is also updated with the required information.
+
 We performed scanning on 2019-09-25 and for our experiments, we used a Docker image that was 
-latest updated i.e with the tag 2019-09-18. So it means that Clair Scanner's database was
+latest updated i.e with the tag 2019-09-18. So it means that Clair Scanner's database was already
 old by one week.
@@
 
-\href{https://github.com/singularityhub/stools}{Stools} combines CoreOS's Clair Scanner with the Continuous Integration (Travis and
-Circle) for scanning Singularity images for vulnerabilities.
+\href{https://github.com/singularityhub/stools}{Stools} combines CoreOS's Clair Scanner with Continuous Integration (CI)
+for scanning Singularity images for vulnerabilities.
 Initially, Clair Scanner was intented to scan Docker Containers. This tool does not fit well
-to scan Singularity images because of the different image formats. Docker layers
+to scan Singularity images because of the different image formats. Docker images
 consist of layers, whereas Singluarity images consist of a single binary file.
@@
 Singularity image, and scanning it for filesystem before the image is finalized.
+
+In our experiments, we used a Docker image (\href{https://hub.docker.com/r/vanessa/stools-clair}{vanessa/stools-clair:v3.2.1})
+for scanning and followed the steps mentioned in (\href{https://github.com/singularityhub/stools}{Stools Github})
+
+\subsection{Image Update Process}
+
+If there exist vulnerabilities in the container image, then we can
+run after updating the
+image. Updating the image involves updating all software packages that are
+inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
+to update all images, which checks
+package manager present inside the image and then according to that it
+updates the image. However, this option effects the reproducibility
+of the image, which means that the image cannot be used to verify research
+findings of other scientists.
 
@@
 how the number of vulnerabilities vary inside images. First experiment involves scanning
-these images as it is to see how vulnerable they are. For scanning we use three different scanners
+the images. We use three different scanners
 to see if all are reporting same vulnerabilities or not. Second experiment involves updating
@@
 
-Figure~\ref{fig:graph1} represents the number of vulnerabilities that are present inside images.
-This figure shows that as the number of packages increases in the image, the number of vulnerabilities
-also get increased for Ubuntu OS distribution. The figure also infers that Alpine distribution, being the
-light weight distribution, have least number of vulnerabilities, whereas Ubuntu contains highest number of
+Figure~\ref{fig:venn} illustrates the number of vulnerabilities detected by scanners. The
+overlapping regions of Venn diagram shows the number of common vulnerabilities detected by either two or
+three scanners. In total 10691 vulnerabilities are detected by three scanners.
+There are also vulnerabilities that are detected only by one scanner.
+
+Figure~\ref{fig:graph1} gives more image specific information.
+It represents the number of vulnerabilities that are present inside images.
+The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
+also get increased.
+The figure also infers that Alpine distribution, being the
+light-weight distribution, have least number of vulnerabilities, whereas Ubuntu contains highest number of
 vulnerabilities. Debian contains highest number of critical vulnerabilities among Ubuntu, Alpine, and Centos.
@@
 
-Figure~\ref{table1} shows results of scanning BIDS and Boutiques images with three scanners namely Anchore,
-Clair scanner and Vuls. Venn Diagram in Figure~\cite{fig:venn} summarizes this table. It is interesting to note that
-Anchore reports 4453 different vulnerabilities, which is way more than both Clair and Vuls.
+Table~\ref{table1} compares results of scanning images with three scanners.
+Venn Diagram in Figure~\ref{fig:venn} summarizes this table.
 
-The number and type of vulnerabilities reported by three scanners are drastically different from each other.
+We add all regions of Venn diagram
+we get total 20050 vulnerabilities in Bids and Boutiques images.
+It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
+reported by Anchore, 673 only reported by Clair and 325 only detected by Vuls.
+
+The number and type of vulnerabilities reported by the three scanners are drastically different from each other.
 The question arises why these scanners report different number and type of vulnerabilities.
@@
 
-\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release-} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
+\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
 are not detected by Clair but they affect Ubuntu 14.04 LTS That’s why detected by Vuls. For example, CVE-2017-1375.
 
-\textbf{False negatives by Clair-} Clair is missing vulnerabilities that it should detect. For example CVE-2016-9082 
+\textbf{False negatives by Clair:} Clair is missing vulnerabilities that it should detect. For example CVE-2016-9082 
 is present in package cairo in Xenial release and it is not detected by Clair.
 
-\textbf{False positives by Clair-} These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
+\textbf{False positives by Clair:} These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
 present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
@@
 
-\textbf{Database difference-} As we discussed earlier that Clair Scanner's database was old by one week.
+\textbf{Database difference:} As we discussed earlier that Clair Scanner's database was old by one week.
                 So some of the vulnerabilities were not updated yet. For example CVE-2019-5094, which
@@
 
-\textbf{Epoch bug-} There is a bug in the Anchore scanner due to which some vulnerabilities are 
+\textbf{Epoch bug:} There is a bug in the Anchore scanner due to which some vulnerabilities are 
 		not detected by Anchore. This bug gets triggered when package’s version have epoch 
@@
 
-\textbf{with status as "Ignored (out of standard support)" bug-} There is another bug in Anchore due to 
+\textbf{with status as "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
 		which it is not able to detect some vulnerabilities. Due to this bug Anchore does not detect 
@@
 
-\textbf{False Negatives by Vuls-} Vuls is missing some of the vulnerabilities that it should detect. 
+\textbf{False Negatives by Vuls:} Vuls is missing some of the vulnerabilities that it should detect. 
 		For example CVE-2019-5094
 
-\textbf{Rejected CVEs-} There are some CVE that are rejected because they are duplicate copies of another CVEs. 
+\textbf{Rejected CVEs:} There are some CVE that are rejected because they are duplicate copies of another CVEs. 
 	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753
@@
 vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
-present in our github repository \href{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}
+present in our github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
 {https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
@@
         {Figures/aferupdatewithpackage.png}}
-        \caption{\label{fig:graph2} Scatterplot representing difference in number of vulnerabilities before and 
-	after update of image}
+        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
+	after update of the images}
       \end{figure}

### 2020-02-11 Scripts/after_update.py

@@ -1,0 +1,22 @@
+import matplotlib.pyplot as plt
+import pandas as pd
+d = pd.read_csv(r"../Results_after_update.csv")
+df=pd.DataFrame(d)
+packages=[]
+before=[]
+after=[]
+for idx,row in df.iterrows():
+    packages.append(row[0])
+    before.append(row[1])
+    after.append(row[2])
+fig=plt.figure()
+#ax = fig.add_subplot()
+plt.plot([],[])
+#print(packages)
+#ax=fig.add_axes([0,0,1,1])
+p1=plt.scatter(packages, before, color='r',s=150,marker='o',label='Before Update')
+p2=plt.scatter(packages, after, color='b',s=150,marker='D',label='After Update')
+plt.xlabel('#Packages', fontsize=15)
+plt.ylabel('#Vulnerabilities',fontsize=15)
+plt.legend(loc='upper left', bbox_to_anchor=(1.00, 1.00), shadow=True, ncol=1)
+plt.show()

### 2020-02-11 Scripts/script.py

@@ -11,18 +11,20 @@ d.head()
 df=pd.DataFrame(d)
 colors = {'ubuntu:14.04' : '#2E37FE', 'ubuntu:16.04' : '#CAE1FF', 'ubuntu:17.04':'#5190ED','ubuntu:17.10':'#000085','ubuntu:18.04' : '#98F5FF','centos 6':'#800080','centos 7':'#b19cd9',
         'alpine:3.7.1':'#3CB371','alpine:3.8.4':'#00ff00','alpine:3.9.0':'#006400','debian:8':'#ffa500'}
-markers = {"ubuntu:14.04": "s", "ubuntu:16.04": "s",'ubuntu:17.04':'s','ubuntu:17.10':'s','ubuntu:18.04' : 's','centos 6':'X','centos 7':'X',
-        "alpine:3.7.1":'o','alpine:3.8.4':"o","alpine:3.9.0":"o","debian:8":"D"}
-with sns.plotting_context(rc={"legend.fontsize":25,"font.size":18,"axes.titlesize":20,"font.weight":'heavy'}):
-  p1=sns.relplot(x="Packages",y="Vulnerabilities",hue="OS distribution",size="CRITICAL Vulnerabilities",sizes=(20,2000),data = df,palette=colors,markers=markers,style="OS distribution",height=10, aspect=2)
-p1.set(xlabel='#Packages', ylabel='#Vulnerabilities by Anchore')
-p1.set(xticks=[i for i in range(0, max(df['Packages']) + 10, 50)],
+markers = {"ubuntu:14.04": "o", "ubuntu:16.04": "o",'ubuntu:17.04':'o','ubuntu:17.10':'o','ubuntu:18.04' : 'o','centos 6':'o','centos 7':'o',
+        "alpine:3.7.1":'o','alpine:3.8.4':"o","alpine:3.9.0":"o","debian:8":"o"}
+with sns.plotting_context(rc={"legend.fontsize":25,"font.size":18,"axes.titlesize":20,"font.weight":'heavy',"legend.labelspacing":20}):
+  p1=sns.relplot(x="Packages",y="Vulnerabilities",hue="OS distribution",size="CRITICAL Vulnerabilities",sizes=(1000,4000),data = df,palette=colors,markers=markers,style="OS distribution",height=10, aspect=2)
+p1.set(xlabel='#Packages', ylabel='#Vulnerabilities')
[…]

### 2020-02-14 paper.tex
changes after result section

@@
 
+\begin{comment}
+This work involves three experiments.
+First experiment involves scanning
+the images. We use three different scanners
+to see if all are reporting same vulnerabilities or not. Second experiment involves updating
+all these images and then rescanning. The last experiment involves shrinking the size of the image
+meaning that removing all unnecessary packages from the image to see the effect on the number of
+vulnerabilities present inside the image.
+\end{comment}
+
 In this section, we present our study methodology. We first
-introduce two container tools used for our experiments: Docker and
+introduce two container tools used in our experiments: Docker and
 Singularity and their image formats. Then we describe Boutiques and BIDS application frameworks
-from where we took containerized applications for our study. Later, we discuss about 
+from where we took containerized applications for our study. Later, we discuss 
 various Linux distributions and their releases. Lastly, this section
-provides the description of the scanning tools used.
+provides a description of the scanning tools used.
 
@@
 required libraries and configuration files for the
-application to function properly. This functioning of an application in an isolated environment
-is called a container. They directly run on the Host machine's kernel so they are lightweight.
+application to function properly. The functioning of an application in an isolated environment
+is called a container. Containers directly run on the Host machine's kernel so they are lightweight.
 Consequently, more containers can be run on a given Host machine as compared to virtual machines.
@@
 %Docker runs a software, \textit{Docker daemon}, on the host machine.
-Docker daemon runs as root, and is remotely controlled through a
-UNIX socket. As Docker Daemon is responsible for launching and managing containers,
-when a container runs, the container is spawned as a
-child process of this root owned daemon.
+Docker daemon runs as root and is remotely controlled through a
+UNIX socket. It is responsible for launching and managing containers,
+consequently, when a container runs, the container is spawned as a
+child process of this root-owned daemon.
 
@@
 Docker daemon through CLI i.e \textit{docker} command, it is possible to force Docker daemon to escalate privileges.
-If a user gets \textit{root} privileges, it introduces unthinkable security risks
-for multi-tenant shared enviornments. Due to this reason, Docker is not
-supported by HPC environments.
+???BLOCK MISSING
 
@@
 Singularity is another tool for packing and running applications in containers. 
-
+In our experiments, we used $2.5.2$ Singularity version. 
+\begin{comment}
 Singularity offers mobility of compute by facilitating portable environments 
@@
 Instead, a user inside Singularity container is the same user outside the container.
+\end{comment}
 
@@
 So we have total 38 Docker images from both BIDS Apps and Boutiques.
-	Table~\ref{table2} displays the names of all the images that we took in our experiments.
+	Table~\ref{table1} displays the names of all the images that we took in our experiments.
 %\begin{figure}
@@
 \subsubsection{Scanning tools used}
-\begin{comments}
+
+\begin{comment}
 Out of the various container image scanning tools available to scan Docker images,
@@
 and one scanner for Singularity images.
-\end{comments}
+\end{comment}
 
@@
 packages, non-OS packages (Python, Java, Gem, and Npm), and files.
-\begin{comments}
+\begin{comment}
 Anchore is a set of tools, which users can
@@
 It provides visibility and transparency of the container environment.
-\end{comments}
+\end{comment}
 Anchore Engine can be used in two ways: through Docker image or Anchore
 Command Line Interface (CLI).
-\begin{comments}
+\begin{comment}
 Anchore offers services in two ways: Anchore Engine and Anchore
@@
 command line interface in addition to Anchore Engine REST API. 
-\end{comments}
+\end{comment}
 It can be
@@
 different sources. For example Ubuntu launchpad database is used for Ubuntu.
+In Ubuntu launchpad database, for a given CVE, there is entry for all ubuntu releases.
+Ubuntu releases are listed with the package name
+in which vulnerability exists and are entitled a status
+(\href{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
+encoded in following form:
+\newline \\
+
+\noindent <release>\_<source-package>: <status> (<version/notes>) \\
+
+The status can be anyone of the following:
+
+\textbf{DNE:} It means 'Does Not Exist'. The package (inside the given release) does not exist in the
+		archive.
+
+\textbf{needs-triage:} The vulnerability of this package (inside the given release)
+		is not known. It needs to be evaluated.  (No version/notes)
+
+\textbf{not-affected:} The package (inside the given release), while related to the
+		CVE in some way, is not affected by the issue. Notes should
+		provide detailed information, if needed. For e.g
+		"not-affected (1.14.6-1.1)" indicates that this specific
+		package version in the given release is not affected.
+
+\textbf{needed:} The package (inside the given release) is vulnerable to the
+		CVE and needs to be fixed.
+
+\textbf{active:} The package (inside the given release) is vulnerable to the
+		CVE, needs fixing, and is actively being worked on.
+
+\textbf{ignored:} The package (inside the given release), while related to the
+		CVE in some way, is being ignored for some reason.  The
+		notes should provide that reason. For e.g "ignored (reached end-of-life)".
+		This means that this given Ubuntu release already reached
+		end-of-life so this CVE is ignored by Ubuntu. However, if there
+		is an extended security support for this release then this
+		CVE will be handled in ESM release.
+
+\textbf{pending:} The package (inside the given release) is vulnerable, and
+                  has been fixed but an update has not been yet uploaded or
+		  pushlished. The "version" indicates the package version 
+		  that contains the fix.
+
+\textbf{deferred:} The package (inside the given release) is vulnerable, but 
+                   its fix has been deferred for some reason. The notes
+		   should provide further details. If a date is mentioned eg
+		   "deferred (2015-02-02)" this date specifies the date when
+		   the CVE was deferred.
+
+\textbf{released:} The package (inside the given release) was vulnerable, but
+		an update has been already uploaded and published. The package version
+		is also mentioned. For e.g "released (1.2.3)"
+		specifies the package version in which the fix first appeared.
+
+\textbf{released-esm:} The package (inside the given release) was vulnerable and
+		an update has been already uploaded and published. However,
+		this update is published in the Ubuntu ESM release only and not in LTS.
+		The fixed version of such packages is appended by
+		+esmN or ~esmN, indicating that this package version is available
+		only via ESM.
+
+Figure~\ref{example} illustrates how the information of a CVE is represented
+in Ubuntu launchpad database.
+
+\begin{figure}[H]
+	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
+	{Figures/vulnExample2.png}}}
+        \caption{\label{example} Representation of a CVE in Ubuntu Launchpad}
+\end{figure}
 
@@
 CoreOS originally created Clair, a static vulnerability scanner for containers. 
-\begin{Comments}
+\begin{comment}
 The main goal of the
@@
 set of sources. 
-\end{comments}	
+\end{comment}	
 Clair API can be used by clients to query its database to get
@@
 
-In this section, we present results of three experiments that are carried out to see
-how the number of vulnerabilities vary inside images. First experiment involves scanning
-the images. We use three different scanners
-to see if all are reporting same vulnerabilities or not. Second experiment involves updating
-all these images and then rescanning. The last experiment involves shrinking the size of the image
-meaning that removing all unnecessary packages from the image to see the effect on the number of
-vulnerabilities present inside the image.
+In this section, we present and compare scanning results of three scanners.
 
@@
 The figure also infers that Alpine distribution, being the
-light-weight distribution, have least number of vulnerabilities, whereas Ubuntu contains highest number of
-vulnerabilities. Debian contains highest number of critical vulnerabilities among Ubuntu, Alpine, and Centos.
+lightweight distribution, have least number of vulnerabilities, whereas Ubuntu contains highest number of
+vulnerabilities. Debian and Cnetos contain higher number of critical vulnerabilities than Ubuntu and Alpine.
 
-\begin{table}
+\begin{table*}
 \csvreader[%
@@
   before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
-      \begin{adjustbox}{max width=\columnwidth},
+      \begin{adjustbox}{max width=\textwidth},
   after reading=\end{adjustbox},
- tabular={c |c | c | c | c},
-        table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
+ tabular={c |c | c | c | c |c},
+	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
  late after line= \\,
@@
 	\caption{\label{table1}Existing number of Vulnerabilities}
-\end{table}
+\end{table*}
 
+\begin{comment}
 \begin{table}
@@
 \end{table}
+\end{comment}
 
-\begin{figure}[!htb]
+\begin{figure}[H]
         {\includegraphics[scale=2.5,width=\columnwidth]
-        {Figures/vennDiagram.png}}
+        {Figures/vennDiagram.pdf}}
         \caption{\label{fig:venn} Venn Diagram representing different scanner results}
@@
 
-\begin{figure}[!htb]
-        {\includegraphics[scale=2,width=\columnwidth]
-        {Figures/vulngraph4.png}}
+\begin{figure*}[!htb]
+	{\includegraphics[scale=1.5,width=\textwidth]
+	{Figures/vulngraph.pdf}}
         \caption{\label{fig:graph1} Scatterplot representing \#Packages and \#Vulnerabilities}
-      \end{figure}
+      \end{figure*}
 
@@
 
-Table~\ref{table1} compares results of scanning images with three scanners.
+Table~\ref{table1} compares results of scanning images with the three scanners.
 Venn Diagram in Figure~\ref{fig:venn} summarizes this table.
 
-We add all regions of Venn diagram
+When we add all regions of Venn diagram
 we get total 20050 vulnerabilities in Bids and Boutiques images.
 It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
-reported by Anchore, 673 only reported by Clair and 325 only detected by Vuls.
-
+reported by Anchore, 673 only reported by Clair, and 325 only detected by Vuls.
+libavlibavlibavlibavlibavlibavlibav
 The number and type of vulnerabilities reported by the three scanners are drastically different from each other.
@@
 
+\begin{comment}
 Venn Diagram~\ref{fig:venn} illustrates that Anchore reports 4453 different vulnerabilities that are reported
@@
 both Clair and Vuls.
+\end{comment}
 
-\textbf{Linux-Kernel-Headers-} Clair Scanner and Vuls are ignoring all vulnerabilities in the Linux-kernel-headers.
-4443 out of 4453 vulnerabilities difference is due to linux-kernel-headers.
-For example CVE-2019-9506 present in linux-libc-dev-4.4.0-31.50 is not detected by both Vuls and Clair Scanner
+\textbf{Linux-Kernel-Headers:} Clair Scanner and Vuls are ignoring all vulnerabilities in the Linux-kernel-headers,
+whereas Anchore reports them.
+4443 out of 4453 vulnerabilities that are only reported by Anchore are present in linux-kernel-headers.
+For example CVE-2019-9506 present in linux-libc-dev-4.4.0-31.50, which is reported by Anchore, is not
+detected by both Vuls and Clair Scanner.
 
-\textbf{With Status as “Not-affected”-} It means these vulnerabilities are affecting Ubuntu but they are not 
-affecting particular Ubuntu release that is present inside the image. The reason why its not affecting 
-that release is also mentioned. For example, one reason can be that code which is creating issue is not 
-present in that release etc. In other words, we can say that these are false positives by Vuls.
-For example CVE-2015-2305 is not affecting package cups in Trusty.
+\textbf{CVEs with Status as “Not-affected”:} Vuls is reporting vulnerabilities with status
+as "not-affected". So it means Linux distribution which is inside the image is not affected
+by the particular CVE. However, it is reported by Vuls. In other words, we can say that
+these are false positives by Vuls.
+For example, we scanned an image having Trusty release in it and Vuls is reporting CVE-2015-2305
+in the package Cups. However, if we check the vulnerability database, package Cups in Trusty is not
+is not affected by this CVE.
 
-\textbf{With status as "Ignored(reached end-of-life)"-} Some vulnerabilities have status as “ignored (reached end-of-life)”.
-These vulnerabilities are "ignored" in Ubuntu 14.04 LTS as it reached end-of-life. 
-However, in Ubuntu 14.04 ESM release these vulnerabilities can be present or not.
-Anchore checks the last status of these vulnerabilities whether OS package was vulnerable to the cve
+\textbf{With CVE status as "Ignored (reached end-of-life)":}
+Some vulnerabilities are "ignored" in Ubuntu 14.04 LTS as it reached end-of-life. 
+However, in Ubuntu 14.04 ESM release these vulnerabilities may or may not be present.
+Anchore checks the last status of these vulnerabilities whether the package was vulnerable to the CVE
 prior to the end-of-life. If it was vulnerable only then Anchore will report it, otherwise not.
-If this kind of vulnerability is present in ESM release then Clair will report it because Clair Scanner
+If this kind of vulnerability is present in ESM release then Clair Scanner will report it because Clair Scanner
 only refers ESM release. On the other hand, if the vulnerability
 status in ESM release is "DNE", which means does not exist, then Clair Scanner will not report it. 
-For example CVE-2017-9994 vulnerability. As Ubuntu LTS release is present inside the images so
-Clair Scanner's reference to ESM release is wrong here.
+For example CVE-2017-9994 vulnerability in libav package is ignored in Trusty LTS release due end-of-life.
+so it is not reported by Anchore. Whereas, this vulnerability has status as "DNE" in Trusty ESM
+release so Clair Scanner also do not report it. As Ubuntu 14.04 LTS release is present inside the images still
+Clair Scanner is referring to Ubuntu 14.04 ESM release vulnerability database.
 
 \textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
-are not detected by Clair but they affect Ubuntu 14.04 LTS That’s why detected by Vuls. For example, CVE-2017-1375.
+are not detected by Clair Scanner but they affect Ubuntu 14.04 LTS hence detected by Vuls. For example, CVE-2017-1375.
 
@@
 
-\textbf{with status as "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
+\textbf{With CVE status as "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
 		which it is not able to detect some vulnerabilities. Due to this bug Anchore does not detect 
@@
 vulnerabilities that we have to face.
-Figure~\ref{fig:graph2}shows number of vulnerabilities that are detected by Anchore after updating these images.
+Figure~\ref{fig:graph2} shows number of vulnerabilities that are detected by Anchore after updating these images.
 
-\begin{figure}[!htb]
-        {\includegraphics[width=\columnwidth]
-        {Figures/aferupdatewithpackage.png}}
+\begin{figure*}[!htb]
+        {\includegraphics[width=\textwidth]
+        {Figures/afterupdatewithpackage.pdf}}
         \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
 	after update of the images}
-      \end{figure}
+      \end{figure*}
 \subsection{Effect Of Size Reduction}

### 2020-02-14 Scripts/after_update.py

@@ -1,3 +1,5 @@
+#!/usr/bin/env python3
+
 import matplotlib.pyplot as plt
 import pandas as pd
 d = pd.read_csv(r"../Results_after_update.csv")
@@ -14,9 +16,11 @@ fig=plt.figure()
 plt.plot([],[])
 #print(packages)
 #ax=fig.add_axes([0,0,1,1])
+plt.figure(figsize=(20,10))
 p1=plt.scatter(packages, before, color='r',s=150,marker='o',label='Before Update')
 p2=plt.scatter(packages, after, color='b',s=150,marker='D',label='After Update')
 plt.xlabel('#Packages', fontsize=15)
 plt.ylabel('#Vulnerabilities',fontsize=15)
-plt.legend(loc='upper left', bbox_to_anchor=(1.00, 1.00), shadow=True, ncol=1)
-plt.show()
+plt.legend(loc='upper left', bbox_to_anchor=(1.00, 1.00), shadow=True, ncol=1,labelspacing=1.2,borderpad=1.0)
+#plt.show()
+plt.savefig('afterupdatewithpackage.pdf',bbox_inches='tight')

### 2020-02-14 Scripts/check.py

@@ -1,0 +1,40 @@
+#!/usr/bin/env python3
+
+# Import the necessary libraries
+import matplotlib.pyplot as plt
+import seaborn as sns
+import pandas as pd
+
+# Load the data
+d = pd.read_csv(r"../train2.csv")
+d.head()
+df=pd.DataFrame(d)
+plt.figure(figsize=(200,20))
+colors = {'ubuntu:14.04' : '#2E37FE', 'ubuntu:16.04' : '#CAE1FF', 'ubuntu:17.04':'#5190ED','ubuntu:17.10':'#000085','ubuntu:18.04' : '#98F5FF','centos 6':'#800080','centos 7':'#b19cd9',
+        'alpine:3.7.1':'#3CB371','alpine:3.8.4':'#00ff00','alpine:3.9.0':'#006400','debian:8':'#ffa500'}
+markers = {"ubuntu:14.04": "o", "ubuntu:16.04": "o",'ubuntu:17.04':'o','ubuntu:17.10':'o','ubuntu:18.04' : 'o','centos 6':'o','centos 7':'o',
+        "alpine:3.7.1":'o','alpine:3.8.4':"o","alpine:3.9.0":"o","debian:8":"o"}
+with sns.plotting_context(rc={"legend.fontsize":25,"font.size":18,"axes.titlesize":20,"font.weight":'heavy',"legend.labelspacing":20}):
+  p1=sns.relplot(x="Packages",y="Vulnerabilities",hue="OS distribution",size="CRITICAL Vulnerabilities",sizes=(300,1450),data = df,palette=colors,markers=markers,style="OS distribution",height=10, aspect=2)
+p1.set(xlabel='#Packages', ylabel='#Vulnerabilities')
+p1.set(xticks=[i for i in range(0, max(df['Packages']) + 100, 50)],
+       yticks=[i for i in range(0, max(df['Vulnerabilities']) + 20, 250)])
+ax = p1.axes[0,0]
+leg = p1._legend
+#p1.legend(loc='center left', bbox_to_anchor=(1.25, 0.5), ncol=1)
+leg.set_bbox_to_anchor([1.01, 0.04])
+leg._loc = 4
+leg.texts[12].set_text("CRITICAL \nVulnerabilities")
+#leg._labelspacing=10
+for idx,row in df.iterrows():
+    x = row[3]
+    y = row[2]
+    text = row[6]
+    alignment=row[8]
+    v=row[9]
+    rot=row[10]
[…]

### 2020-02-14 paper.tex
after grammer check

@@
 Tools that are capable of packing and running an application in an isolated environment
-are known as container tools. Alongwith an application they also pack the application's dependencies,
+are known as container tools. Alongwith an application, they also pack the application's dependencies,
 required libraries and configuration files for the
@@
 \textit{Docker Daemon:} It acts as a server. It is
-a long running process that manages all Docker images, containers, storage volumes, and networks.
+a long-running process that manages all Docker images, containers, storage volumes, and networks.
 
-\textit{REST API:} It acts as a interface between the server and the client, and is an API which is used by the applications
+\textit{REST API:} It acts as an interface between the server and the client, and is an API which is used by the applications
 to talk to the \textit{Docker Daemon}.
@@
 Docker daemon through CLI i.e \textit{docker} command, it is possible to force Docker daemon to escalate privileges.
-???BLOCK MISSING
+If a user gets root privileges, it
+introduces unthinkable security risks for multi-tenant shared
+environments. Due to this reason, Docker is not supported by
+HPC environments.
 
@@
 Singularity is another tool for packing and running applications in containers. 
-In our experiments, we used $2.5.2$ Singularity version. 
+In our experiments, we used $2.5.2$ Singularity version. In contrast to Docker,
+Singularity does not run containers as root. Consequently, users cannot escalate
+privileges in Singularity containers making it suitable for HPC environments.
+
 \begin{comment}
@@
 required dependencies and libraries.
-Both, Docker and Singularity, have different image formats. Below we provide description of both image
+Both, Docker and Singularity, have different image formats. Below we provide a description of both image
 formats.
@@
 
-On the other hand, Singularity image is a single immutable file and 
+On the other hand, a Singularity image is a single immutable file and 
 does not contain layers.
+Once a Singularity image is created, it cannot be changed, consequently,
+it can be used for reproducing the results of scientific
+experiments.
 \begin{comment}
@@
 image along with its hash, which allow other researchers to verify results.
-
+\end{comment}
 \subsection{Application frameworks}
@@
 Out of these 27 images, we used 26 images for our experiments because one of them was not available
-on Docker hub.
+on the Docker hub.
 
@@
 
-Boutiques~\cite{glatard2018boutiques} is a application sharing system to
+Boutiques~\cite{glatard2018boutiques} is an application sharing system to
 publish, integrate, and execute command-line applications across different
@@
 3 images are not found and 2 images were already included in BIDS images.
-Therefore we are left with total 18 Boutiques images which includes 6
+Therefore we are left with a total 18 Boutiques images which include 6
 Singularity images and 12 Docker images.
@@
 At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
-Out of these 27 images, we used 26 images for our experiments because QAP bids app was not available
+Out of these 27 images, we used 26 images for our experiments because the QAP bids app was not available
 on Docker hub.
 
-So we have total 38 Docker images from both BIDS Apps and Boutiques.
+So we have a total 38 Docker images from both BIDS Apps and Boutiques.
 	Table~\ref{table1} displays the names of all the images that we took in our experiments.
@@
 
-BIDS app and Boutiques images that we took for our experiment have diverse Linux
-distributions such as Ubuntu, Centos, Debian, and Alpine. In case of Ubuntu, release
-can be of two types : regular or LTS (Long Term Support).
+BIDS app and Boutiques images that we took for our experiments have diverse Linux
+distributions such as Ubuntu, Centos, Debian, and Alpine. In the case of Ubuntu, release
+can be of two types: regular or LTS (Long Term Support).
 Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
@@
 finally, using this information to detect vulnerabilities present inside the image.
-Scanning can be broadly categorised into two types: \rom{1} Static Scanning and \rom{2}
+Scanning can be broadly categorized into two types: \rom{1}) Static Scanning and \rom{2})
 Dynamic Scanning.
 In Static scanning, an image is scanned without running it into a container. In respect to that,
-differnt image features are extracted like installed packages, their versions, files, etc.
+different image features are extracted like installed packages, their versions, files, etc.
 On the other hand, Dynamic scanning involves running a container from the image and then scanning the
-dynamic behaviour of the image.
+dynamic behavior of the image.
 
@@
 Clair Scanner~\cite{arminc_2019} for scanning Docker images because these are the most
-mature scanners. Out of these scanners, only Vuls uses dynamic scanning and remaining two
+mature scanners. Out of these scanners, only Vuls uses dynamic scanning and the remaining two
 are static scanners.
-Also, we freezed vulnerability databases for these scanners on September 25, 2019 and scanned
+Also, we froze vulnerability databases for these scanners on September 25, 2019, and scanned
 all images to avoid getting different results due to the differences in the scanner's database.
@@
 image, with the vulnerability database to flag vulnerabilities.
-To get vulnerability feed of various OS distribution, Anchore refers to
-different sources. For example Ubuntu launchpad database is used for Ubuntu.
-In Ubuntu launchpad database, for a given CVE, there is entry for all ubuntu releases.
+To get a vulnerability feed of various OS distribution, Anchore refers to
+different sources. For example, the Ubuntu launchpad database is used for Ubuntu.
+In Ubuntu launchpad database, for a given CVE, there is an entry for all ubuntu releases.
 Ubuntu releases are listed with the package name
@@
 (\href{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
-encoded in following form:
+encoded in the following form:
 \newline \\
@@
 
-The status can be anyone of the following:
+The status can be any one of the following:
 
@@
 		CVE in some way, is not affected by the issue. Notes should
-		provide detailed information, if needed. For e.g
+		provide detailed information if needed. For e.g
 		"not-affected (1.14.6-1.1)" indicates that this specific
@@
 		end-of-life so this CVE is ignored by Ubuntu. However, if there
-		is an extended security support for this release then this
+		is extended security support for this release then this
 		CVE will be handled in ESM release.
 
-\textbf{pending:} The package (inside the given release) is vulnerable, and
+\textbf{pending:} The package (inside the given release) is vulnerable and
                   has been fixed but an update has not been yet uploaded or
-		  pushlished. The "version" indicates the package version 
+		  published. The "version" indicates the package version 
 		  that contains the fix.
@@
 Figure~\ref{example} illustrates how the information of a CVE is represented
-in Ubuntu launchpad database.
+in the Ubuntu launchpad database.
 
@@
 Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
-Using dynamic scanning technique, it offers
-remote and local scan. Remote scan involves setting up only one machine, to
+Using a dynamic scanning technique, it offers
+remote and local scans. The remote scan involves setting up only one machine, to
 which other target servers are connected via SSH. Local scan involves running
-the scan on the target server itself. Further, Vuls offer fast scan, fast root scan,
+the scan on the target server itself. Further, Vuls offer a fast scan, fast root scan,
 and deep scan.
-Fast scan is performed without root privileges, whereas fast root scan is
+The Fast scan is performed without root privileges, whereas a fast root scan is
 performed with root privileges. The latter also uses checkrestart utility to 
@@
 processes. Both fast scan and fast root scan are performed offline without Internet
-access, and put almost no load on the scan target server. Deep scan uses
-root privileges for scanning, and is used to get a more detailed scan. It checks
+access, and put almost no load on the scan target server. The Deep scan uses
+root privileges for scanning and is used to get a more detailed scan. It checks
 changelogs, which puts more load on the target server.
@@
 to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
-is a registery to store images privately, uses Clair internally as the security engine. However, Clair does not 
-provide facility of comparing
+is a registry to store images privately, uses Clair internally as the security engine. However, Clair does not 
+provide the facility for comparing
 the vulnerability list of a particular image against a whitelist of vulnerabilities that you
@@
 So, to remove
-that drawback, another tool from CoreOS, Clair Scanner can be used. It scans image, prepares the list of
+that drawback, another tool from CoreOS, Clair Scanner can be used. It scans the image, prepares the list of
 vulnerabilities, compares that list against the whitelist, and flags vulnerabilities
 that are not present in the whitelist.
-Clair Scanner refers to Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
-For that purpose a Docker image is maintained that contains Ubuntu CVE tracker database.
+Clair Scanner refers to the Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
+For that purpose, a Docker image is maintained that contains the Ubuntu CVE tracker database.
 Whenever Ubuntu updated its database, this image is also updated with the required information.
@@
 for scanning Singularity images for vulnerabilities.
-Initially, Clair Scanner was intented to scan Docker Containers. This tool does not fit well
-to scan Singularity images because of the different image formats. Docker images
-consist of layers, whereas Singluarity images consist of a single binary file.
+Initially, Clair Scanner was intended to scan Docker Containers. This tool does not fit well
+to scan Singularity images because of the different image formats.
 However, TravisCI and CircleCI are commonly used for testing code, and these
@@
 inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
-to update all images, which checks
+to update all images, which checks the
 package manager present inside the image and then according to that it
-updates the image. However, this option effects the reproducibility
-of the image, which means that the image cannot be used to verify research
+updates the image. However, this option affects the reproducibility
+of the image, which means that the image cannot be used to verify the research
 findings of other scientists.
@@
 
-In this section, we present and compare scanning results of three scanners.
+In this section, we present and compare the scanning results of three scanners.
 
@@
 Figure~\ref{fig:venn} illustrates the number of vulnerabilities detected by scanners. The
-overlapping regions of Venn diagram shows the number of common vulnerabilities detected by either two or
+overlapping regions of the Venn diagram show the number of common vulnerabilities detected by either two or
 three scanners. In total 10691 vulnerabilities are detected by three scanners.
@@
 
-Figure~\ref{fig:graph1} gives more image specific information.
+Figure~\ref{fig:graph1} gives more image-specific information.
 It represents the number of vulnerabilities that are present inside images.
@@
 The figure also infers that Alpine distribution, being the
-lightweight distribution, have least number of vulnerabilities, whereas Ubuntu contains highest number of
-vulnerabilities. Debian and Cnetos contain higher number of critical vulnerabilities than Ubuntu and Alpine.
+lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains highest number of
+vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine.
 
@@
 
-Table~\ref{table1} compares results of scanning images with the three scanners.
+Table~\ref{table1} compares the results of scanning images with the three scanners.
 Venn Diagram in Figure~\ref{fig:venn} summarizes this table.
@@
 reported by Anchore, 673 only reported by Clair, and 325 only detected by Vuls.
-libavlibavlibavlibavlibavlibavlibav
+
 The number and type of vulnerabilities reported by the three scanners are drastically different from each other.
-The question arises why these scanners report different number and type of vulnerabilities.
+The question arises why these scanners report different numbers and types of vulnerabilities.
 How their logic differs and what exactly is making these results different than each other.
 
-According to our investigation of these results, below are some of the reasons of
+According to our investigation of these results, below are some of the reasons for
 getting different results from these scanners. These reasons include bugs in scanners,
@@
 whereas Anchore reports them.
-4443 out of 4453 vulnerabilities that are only reported by Anchore are present in linux-kernel-headers.
-For example CVE-2019-9506 present in linux-libc-dev-4.4.0-31.50, which is reported by Anchore, is not
+4443 out of 4453 vulnerabilities that are only reported by Anchore are present in Linux-kernel-headers.
+For example CVE-2019-9506 present in Linux-libc-dev-4.4.0-31.50, which is reported by Anchore, is not
 detected by both Vuls and Clair Scanner.
@@
 these are false positives by Vuls.
-For example, we scanned an image having Trusty release in it and Vuls is reporting CVE-2015-2305
+For example, we scanned an image having the Trusty release in it and Vuls is reporting CVE-2015-2305
 in the package Cups. However, if we check the vulnerability database, package Cups in Trusty is not
@@
 If this kind of vulnerability is present in ESM release then Clair Scanner will report it because Clair Scanner
-only refers ESM release. On the other hand, if the vulnerability
-status in ESM release is "DNE", which means does not exist, then Clair Scanner will not report it. 
-For example CVE-2017-9994 vulnerability in libav package is ignored in Trusty LTS release due end-of-life.
+only refers to ESM release. On the other hand, if the vulnerability
+status in ESM release is "DNE" (Does Not Exist), then Clair Scanner will not report it. 
+For example CVE-2017-9994 vulnerability in Libav package is ignored in Trusty LTS release due to end-of-life.
 so it is not reported by Anchore. Whereas, this vulnerability has status as "DNE" in Trusty ESM
-release so Clair Scanner also do not report it. As Ubuntu 14.04 LTS release is present inside the images still
+release so Clair Scanner also does not report it. As Ubuntu 14.04 LTS release is present inside the images still
 Clair Scanner is referring to Ubuntu 14.04 ESM release vulnerability database.
@@
 
-\textbf{False negatives by Clair:} Clair is missing vulnerabilities that it should detect. For example CVE-2016-9082 
-is present in package cairo in Xenial release and it is not detected by Clair.
+\textbf{False negatives by Clair:} Clair is missing vulnerabilities that it should detect. For example, CVE-2016-9082 
+is present in package Cairo in Xenial release and it is not detected by Clair.
 
@@
 \textbf{Database difference:} As we discussed earlier that Clair Scanner's database was old by one week.
-                So some of the vulnerabilities were not updated yet. For example CVE-2019-5094, which
+                So some of the vulnerabilities were not updated yet. For example, CVE-2019-5094, which
 		was published on 2019-09-24, was not 
@@
 \textbf{Epoch bug:} There is a bug in the Anchore scanner due to which some vulnerabilities are 
-		not detected by Anchore. This bug gets triggered when package’s version have epoch 
-		(1:3.3.9-1ubuntu2.3)  in it. For example CVE-2018-1125 in procps package.
+		not detected by Anchore. This bug gets triggered when a package’s version have epoch 
+		(1:3.3.9-1ubuntu2.3) in it. For example, CVE-2018-1125 in Procps package is not
+		detected by Anchore due to the presence of epoch in the Procps package version.
 
 \textbf{With CVE status as "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
-		which it is not able to detect some vulnerabilities. Due to this bug Anchore does not detect 
-		vulnerabilities which have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
+		which it is not able to detect some vulnerabilities. Due to this bug, Anchore does not detect 
+		vulnerabilities that have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
 		But if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
@@
 
-\textbf{Rejected CVEs:} There are some CVE that are rejected because they are duplicate copies of another CVEs. 
-	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753
+\textbf{Rejected CVEs:} There are some CVE that are rejected because they are duplicate copies of other CVEs. 
+	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753.
 
@@
 vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
-present in our github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
+present in our Github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
 {https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
-will find package manager inside the image and then update the image according the package manager it finds.
-When these images are rescanned after updation, results changed drastically. However, there are still
+will find the package manager inside the image and then update the image according to the package manager it finds.
+When these images are rescanned after the update, results changed drastically. However, there are still
 vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
-till date so there is nothing that can be done to remove these vulnerabilties. There are only two
+to date. There are only two
 options, either you accept those vulnerabilities and use that image, or you discard that image.
@@
 vulnerabilities that we have to face.
-Figure~\ref{fig:graph2} shows number of vulnerabilities that are detected by Anchore after updating these images.
+Figure~\ref{fig:graph2} shows the number of vulnerabilities that are detected by Anchore after updating these images.
 

### 2020-02-17 paper.tex
before meeting
after meeting

@@
 
-\begin{comment}
-This work involves three experiments.
+In this section, we present our study methodology.
+This study involves three image scanning experiments.
 First experiment involves scanning
-the images. We use three different scanners
-to see if all are reporting same vulnerabilities or not. Second experiment involves updating
-all these images and then rescanning. The last experiment involves shrinking the size of the image
+the images. For that purpose, we use three different scanners. Second experiment involves updating
+all these images and then rescanning them. The last experiment involves shrinking the size of the image
 meaning that removing all unnecessary packages from the image to see the effect on the number of
 vulnerabilities present inside the image.
-\end{comment}
 
-In this section, we present our study methodology. We first
+We first
 introduce two container tools used in our experiments: Docker and
@@
 various Linux distributions and their releases. Lastly, this section
-provides a description of the scanning tools used.
+provides a description of the three scanning tools used.
 
@@
 \newline \\
-
 \noindent <release>\_<source-package>: <status> (<version/notes>) \\
-
+\newline\\
 The status can be any one of the following:
@@
 
-In this section, we present and compare the scanning results of three scanners.
+In this section,
+we first discuss the existing vulnerabilities in the images and compare
+results of the three scanners. Then we discuss the effect of the update on the
+existing vulnerabilities and lastly, this section presents the effect of image size reduction on the
+vulnerabilities.
 
@@
 detected by both Vuls and Clair Scanner.
+Linux-kernel-headers are the headers files that only provide function names, its parameters, and its
+return type.
+The actual source code of these functions is present in the Linux kernel and not inside the image.
+So, vulnerability detection in header files
+is irrelevant in this case.
 
@@
 \subsection{Effect Of Update}
-
+\begin{comment}
 The next experiment involves updating all these images and then rescanning them to see how the number of
@@
 will find the package manager inside the image and then update the image according to the package manager it finds.
-When these images are rescanned after the update, results changed drastically. However, there are still
+\end{comment}
+
+When the images are rescanned after the update, results changed drastically. However, there are still
 vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
-to date. There are only two
+to date.
+\begin{comment}
+There are only two
 options, either you accept those vulnerabilities and use that image, or you discard that image.
@@
 vulnerabilities that we have to face.
-Figure~\ref{fig:graph2} shows the number of vulnerabilities that are detected by Anchore after updating these images.
-
+\end{comment}
+Figure~\ref{fig:graph2} compares the number of vulnerabilities that are detected by Anchore before and after 
+the update of these images.
+After the update, the vulnerabilities mostly have \textit{Low, Negligible or Medium} severity status.
+Also, after the update, the number of vulnerabilities have a mild slope meaning that there
+are a fixed set of packages that contain vulnerabilities and have no fix yet.
 \begin{figure*}[!htb]

### 2020-03-03 paper.tex
updated materials and methods

@@
 
-In this section, we present our study methodology.
 This study involves three image scanning experiments.
-First experiment involves scanning
-the images. For that purpose, we use three different scanners. Second experiment involves updating
-all these images and then rescanning them. The last experiment involves shrinking the size of the image
+The first experiment scans the images as is to report the existing vulnerabilities
+inside the images. The scan report of
+these images shows a large number of existing vulnerabilities which may pose
+a potential security risk. These vulnerabilities exist due to the outdated
+packages that are present inside images. So, the next step is to
+take the necessary steps to improve security in the images. Therefore, there exist
+two possible solutions.
+The first one involves updating
+all these images and then rescanning them, which constitutes the next experiment of our study. The second one
+involves shrinking the size of the image
 meaning that removing all unnecessary packages from the image to see the effect on the number of
-vulnerabilities present inside the image.
+vulnerabilities present inside the image, which will be presented as our third experiment.
 
@@
 Singularity and their image formats. Then we describe Boutiques and BIDS application frameworks
-from where we took containerized applications for our study. Later, we discuss 
-various Linux distributions and their releases. Lastly, this section
-provides a description of the three scanning tools used.
+from where we took containerized applications for our study. 
+Later, this section
+presents two scanning techniques followed by a description of image scanners used.
+In this study, we used three different image scanners because they
+use different scanning techniques and/or refer to different vulnerability sources.
+The images used in our study have different Linux distributions/releases, which have
+different vulnerability data. Therefore, in the last, this section presents a
+description of these varying Linux distributions/releases and their
+vulnerability databases.
 
@@
 
-Tools that are capable of packing and running an application in an isolated environment
-are known as container tools. Alongwith an application, they also pack the application's dependencies,
+Container tools are capable of packing and running an application in an isolated environment that have
+the application's dependencies,
 required libraries and configuration files for the
-application to function properly. The functioning of an application in an isolated environment
-is called a container. Containers directly run on the Host machine's kernel so they are lightweight.
-Consequently, more containers can be run on a given Host machine as compared to virtual machines.
+application to function properly.
 
@@
 
-Docker is a tool to run containers.
-Docker containers are managed by the Docker engine, which is a client-server application and
+Docker containers are managed by the Docker engine, which is a client-server application, and
+is also known as Docker Daemon.
+
+\begin{comment}
 consists of the following three main components:
@@
 \textit{Client:} It is a Command Line Interface (CLI) client which is used to interact with the \textit{Docker Daemon}.
-
+convert english to punjabi
+\end{comment}
 %Docker runs a software, \textit{Docker daemon}, on the host machine.
@@
 As Docker users directly interact with the
-Docker daemon through CLI i.e \textit{docker} command, it is possible to force Docker daemon to escalate privileges.
+Docker daemon through Command Line Interface (CLI) i.e \textit{docker} command, it is possible to force Docker daemon to escalate privileges.
 If a user gets root privileges, it
@@
 HPC environments.
+
+Docker images are organized as a series of layers stacked on top of each
+other and identified by unique layer identifiers. If a layer is reused
+in different images it will
+have the same id across images. Each layer consists of a filesystem diff
+with respect to the layer below.
 
@@
 privileges in Singularity containers making it suitable for HPC environments.
+
+On the other hand, a Singularity image is a single immutable file and
+does not contain layers.
+Once a Singularity image is created, it cannot be changed, consequently,
+it can be used for reproducing the results of scientific
+experiments.
 
@@
 Instead, a user inside Singularity container is the same user outside the container.
-\end{comment}
 
@@
 with respect to the layer below. 
-\begin{comment}
 DockerHub uses gzip compression for
@@
 zfs, and vfs}
-\end{comment}
 
@@
 experiments.
-\begin{comment}
 Singularity takes snapshot, locks, and archives the developed application,
@@
 \end{comment}
-
-\subsection{Linux Distributions}
-
-BIDS app and Boutiques images that we took for our experiments have diverse Linux
-distributions such as Ubuntu, Centos, Debian, and Alpine. In the case of Ubuntu, release
-can be of two types: regular or LTS (Long Term Support).
-Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
-reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
-in the form of Extended Security Maintenance (ESM) release.
-ESM is a paid service that can be requested from Ubuntu to get security 
-updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
-Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
-data in vulnerability databases because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
-exists in LTS.
-
-Ubuntu has ended support for some releases such as 14.04 LTS,
-17.04, and 17.10, which means they have reached EOL. However, Ubuntu is providing optional extended support for Ubuntu 14.04.
-To use this extended support, users have to buy ESM release for Ubuntu 14.04.
-The images in our experiments have Ubuntu 14.04 LTS so scanners should refer
-to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for data it may result
-in false positives and false negatives.
-Also, if ubuntu releases with ended support are used in images, there are no chances of getting updates, hence
-resulting in vulnerable images. Additionally, even if extended security is provided for some releases by Ubuntu, it is
-not feasible to use it inside images because it is a paid service.
 
@@
 for scanning and followed the steps mentioned in (\href{https://github.com/singularityhub/stools}{Stools Github})
+
+\subsection{Linux Distributions and Vulnerability Databases}
+
+BIDS app and Boutiques images that we took for our experiments have diverse Linux
+distributions such as Ubuntu, Centos, Debian, and Alpine. In the case of Ubuntu, release
+can be of two types: regular or LTS (Long Term Support).
+Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
+reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
+in the form of Extended Security Maintenance (ESM) release.
+ESM is a paid service that can be requested from Ubuntu to get security 
+updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
+Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
+data in vulnerability databases because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
+exists in LTS.
+
+Ubuntu has ended support for some releases such as 14.04 LTS,
+17.04, and 17.10, which means they have reached EOL. However, Ubuntu is providing optional extended support for Ubuntu 14.04.
+To use this extended support, users have to buy ESM release for Ubuntu 14.04.
+The images in our experiments have Ubuntu 14.04 LTS so scanners should refer
+to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for data it may result
+in false positives and false negatives.
+Also, if ubuntu releases with ended support are used in images, there are no chances of getting updates, hence
+resulting in vulnerable images. Additionally, even if extended security is provided for some releases by Ubuntu, it is
+not feasible to use it inside images because it is a paid service.
 

### 2020-04-06 paper.tex
added package removal script

@@
 
-Docker containers are managed by the Docker engine, which is a client-server application, and
-is also known as Docker Daemon.
+Docker uses a client-server architecture, where client containers communicate to
+the server Docker Daemon also known as Docker engine.
+Docker Daemon is a long-running process that manages all Docker images, containers, storage volumes, and networks.
 
@@
 %Docker runs a software, \textit{Docker daemon}, on the host machine.
-Docker daemon runs as root and is remotely controlled through a
+It runs as root and is remotely controlled through a
 UNIX socket. It is responsible for launching and managing containers,
@@
 
-Singularity is another tool for packing and running applications in containers. 
-In our experiments, we used $2.5.2$ Singularity version. In contrast to Docker,
+As Docker is not suitable for HPC systems therefore, Singularity came up with a new approach
+of packing and running applications in containers. 
+In contrast to Docker,
 Singularity does not run containers as root. Consequently, users cannot escalate
@@
 
-On the other hand, a Singularity image is a single immutable file and
+A Singularity image is a single immutable file and
 does not contain layers.
@@
 
+\begin{comment}
 \subsubsection{Brain Imaging Data Structure (BIDS) Apps}
@@
 on Docker hub.
-
+\end{comment}
 So we have a total 38 Docker images from both BIDS Apps and Boutiques.
@@
 different sources. For example, the Ubuntu launchpad database is used for Ubuntu.
-In Ubuntu launchpad database, for a given CVE, there is an entry for all ubuntu releases.
-Ubuntu releases are listed with the package name
-in which vulnerability exists and are entitled a status
-(\href{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
-encoded in the following form:
-\newline \\
-\noindent <release>\_<source-package>: <status> (<version/notes>) \\
-\newline\\
-The status can be any one of the following:
-
-\textbf{DNE:} It means 'Does Not Exist'. The package (inside the given release) does not exist in the
-		archive.
-
-\textbf{needs-triage:} The vulnerability of this package (inside the given release)
-		is not known. It needs to be evaluated.  (No version/notes)
-
-\textbf{not-affected:} The package (inside the given release), while related to the
-		CVE in some way, is not affected by the issue. Notes should
-		provide detailed information if needed. For e.g
-		"not-affected (1.14.6-1.1)" indicates that this specific
-		package version in the given release is not affected.
-
-\textbf{needed:} The package (inside the given release) is vulnerable to the
-		CVE and needs to be fixed.
-
-\textbf{active:} The package (inside the given release) is vulnerable to the
-		CVE, needs fixing, and is actively being worked on.
-
-\textbf{ignored:} The package (inside the given release), while related to the
-		CVE in some way, is being ignored for some reason.  The
-		notes should provide that reason. For e.g "ignored (reached end-of-life)".
-		This means that this given Ubuntu release already reached
-		end-of-life so this CVE is ignored by Ubuntu. However, if there
-		is extended security support for this release then this
-		CVE will be handled in ESM release.
-
-\textbf{pending:} The package (inside the given release) is vulnerable and
-                  has been fixed but an update has not been yet uploaded or
-		  published. The "version" indicates the package version 
-		  that contains the fix.
-
-\textbf{deferred:} The package (inside the given release) is vulnerable, but 
-                   its fix has been deferred for some reason. The notes
-		   should provide further details. If a date is mentioned eg
-		   "deferred (2015-02-02)" this date specifies the date when
-		   the CVE was deferred.
-
-\textbf{released:} The package (inside the given release) was vulnerable, but
-		an update has been already uploaded and published. The package version
-		is also mentioned. For e.g "released (1.2.3)"
-		specifies the package version in which the fix first appeared.
-
-\textbf{released-esm:} The package (inside the given release) was vulnerable and
-		an update has been already uploaded and published. However,
-		this update is published in the Ubuntu ESM release only and not in LTS.
-		The fixed version of such packages is appended by
-		+esmN or ~esmN, indicating that this package version is available
-		only via ESM.
-
-Figure~\ref{example} illustrates how the information of a CVE is represented
-in the Ubuntu launchpad database.
 
@@
 Also, if ubuntu releases with ended support are used in images, there are no chances of getting updates, hence
-resulting in vulnerable images. Additionally, even if extended security is provided for some releases by Ubuntu, it is
-not feasible to use it inside images because it is a paid service.
+resulting in vulnerable images.
+
+Ubuntu maintains its vulnerability database in Ubuntu launchpad or Ubuntu CVE tracker. For a given CVE, there is an entry for all ubuntu releases.
+Ubuntu releases are listed with the package name
+in which vulnerability exists and are entitled a status
+(\href{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
+encoded in the following form:
+\newline \\
+\noindent <release>\_<source-package>: <status> (<version/notes>) \\
+\newline\\
+The status can be any one of the following:
+
+\textbf{DNE:} It means 'Does Not Exist'. The package (inside the given release) does not exist in the
+		archive.
+
+\textbf{needs-triage:} The vulnerability of this package (inside the given release)
+		is not known. It needs to be evaluated.  (No version/notes)
+
+\textbf{not-affected:} The package (inside the given release), while related to the
+		CVE in some way, is not affected by the issue. Notes should
+		provide detailed information if needed. For e.g
+		"not-affected (1.14.6-1.1)" indicates that this specific
+		package version in the given release is not affected.
+
+\textbf{needed:} The package (inside the given release) is vulnerable to the
+		CVE and needs to be fixed.
+
+\textbf{active:} The package (inside the given release) is vulnerable to the
+		CVE, needs fixing, and is actively being worked on.
+
+\textbf{ignored:} The package (inside the given release), while related to the
+		CVE in some way, is being ignored for some reason.  The
+		notes should provide that reason. For e.g "ignored (reached end-of-life)".
+		This means that this given Ubuntu release already reached
+		end-of-life so this CVE is ignored by Ubuntu. However, if there
+		is extended security support for this release then this
+		CVE will be handled in ESM release.
+
+\textbf{pending:} The package (inside the given release) is vulnerable and
+                  has been fixed but an update has not been yet uploaded or
+		  published. The "version" indicates the package version 
+		  that contains the fix.
+
+\textbf{deferred:} The package (inside the given release) is vulnerable, but 
+                   its fix has been deferred for some reason. The notes
+		   should provide further details. If a date is mentioned eg
+		   "deferred (2015-02-02)" this date specifies the date when
+		   the CVE was deferred.
+
+\textbf{released:} The package (inside the given release) was vulnerable, but
+		an update has been already uploaded and published. The package version
+		is also mentioned. For e.g "released (1.2.3)"
+		specifies the package version in which the fix first appeared.
+
+\textbf{released-esm:} The package (inside the given release) was vulnerable and
+		an update has been already uploaded and published. However,
+		this update is published in the Ubuntu ESM release only and not in LTS.
+		The fixed version of such packages is appended by
+		+esmN or ~esmN, indicating that this package version is available
+		only via ESM.
+
+Figure~\ref{example} illustrates how the information of a CVE is represented
+in the Ubuntu launchpad database.
 
@@
 findings of other scientists.
+
+\subsection{Image size Reduction process}
+
+If we want to reduce number of vulnerabilities without effecting the reproducibility of the image,
+image size reduction process is a good choice. In this process we reduce the number of packages
+installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
+out which packages we need for the pipeline to fucntion properly. Here, we use Reprozip
+\href{https://github.com/VIDA-NYU/reprozip}{https://github.com/VIDA-NYU/reprozip}. It is a tool that
+is used to make applications reproducible~\cite{ChirigatiRSF16}. It traces operating system calls used by the
+application while execution and then based on that it recognizes binaries, files, environment variables,
+and library dependencies that will be used by the application for future reexecution. If the OS is
+Debian or RPM based, Reprozip also
+uses available package manager to acquire a list of distribution packages from where these files come from.
+So, we got this list of packages from Reprozip that are needed for the application execution. 
+After that, we expanded this list by adding important and required packages that are essential
+for the system to function and finally figured out all the dependencies of these packages using debtree
+(\href{http://manpages.ubuntu.com/manpages/xenial/man1/debtree.1.html}{http://manpages.ubuntu.com/manpages/xenial/man1/debtree.1.html}).
+Ultimately, we kept these packages and removed remaining unnecessary packages. We used bash script
 
@@
 
+Our last experiment shows deleting unnecessary packages from the image also helps to reduce
+the number of vulnerabilities by significant number.
 \bibliography{bibliography}

### 2020-04-06 Scripts/check_virtuality.py

@@ -1,0 +1,33 @@
+#!/usr/bin/env python
+
+import sys
+import csv
+
+packages = None
+all = None
+virts = None
+
+f1 = sys.argv[1]
+f2 = sys.argv[2]
+f3 = sys.argv[3]
+with open(f1, 'r') as f:
+  packages = f.readlines()
+
+with open('all-packages.csv', 'r') as f:
+  all = f.readlines()
+
+with open('virtual.csv', 'r') as f:
+  virts = f.readlines()
+
+installed = [ p.strip() for p in packages if p in all ]
+virtual = [ p.strip() for p in packages if p in virts ]
+out = open(f2,'w')
+for line in installed:
+    out.write(line)
+    out.write("\n")
+out.close()
+out = open(f3,'w')
+for line in virtual:
+    out.write(line)
+    out.write("\n")
+

### 2020-04-06 Scripts/to_delete.py

@@ -1,0 +1,23 @@
+#!/usr/bin/env python
+
+
+all = None
+keep = None
+
+with open('all-packages.csv', 'r') as f:
+  all = f.readlines()
+
+with open('uniq_keep_installed.csv', 'r') as f:
+  keep = f.readlines()
+
+hold = [ p.strip() for p in keep ]
+str1 = ' '.join(str(e) for e in hold)
+print("***********************************following packages should be held****************************")
+print(str1)
+remove = [ p.strip() for p in all if not p in keep ]
+str3 = ' '.join(str(e) for e in remove)
+print(str3)
+print(len(remove))
+for p in remove:
+    print(p)
+

### 2020-04-21 paper.tex
changed citations

@@
 \usepackage{makecell}
+\usepackage{titlesec}
 \usepackage[flushleft]{threeparttable}
@@
 a potential security risk. These vulnerabilities exist due to the outdated
-packages that are present inside images. So, the next step is to
+packages that are present inside the images. So, the next step is to
 take the necessary steps to improve security in the images. Therefore, there exist
@@
 The first one involves updating
-all these images and then rescanning them, which constitutes the next experiment of our study. The second one
-involves shrinking the size of the image
+all these images and then rescanning them, which constitutes the second experiment of our study. The next 
+experiment involves shrinking the size of the image
 meaning that removing all unnecessary packages from the image to see the effect on the number of
@@
 
-Docker uses a client-server architecture, where client containers communicate to
-the server Docker Daemon also known as Docker engine.
+Docker uses a client-server architecture, where client, containers, communicate to
+the server, Docker Daemon, which is also known as Docker engine.
 Docker Daemon is a long-running process that manages all Docker images, containers, storage volumes, and networks.
@@
 
-\subsubsection{Scanning tools used}
+%\subsubsection{Scanning tools used}
 
@@
 In our experiments, we used a Docker image (\href{https://hub.docker.com/r/vanessa/stools-clair}{vanessa/stools-clair:v3.2.1})
-for scanning and followed the steps mentioned in (\href{https://github.com/singularityhub/stools}{Stools Github})
+for scanning and followed the steps mentioned in \href{https://github.com/singularityhub/stools}{Stools Github}.
 
@@
 findings of other scientists.
-
+\linespread{0.5}
 \subsection{Image size Reduction process}
@@
 installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
-out which packages we need for the pipeline to fucntion properly. Here, we use Reprozip
-\href{https://github.com/VIDA-NYU/reprozip}{https://github.com/VIDA-NYU/reprozip}. It is a tool that
-is used to make applications reproducible~\cite{ChirigatiRSF16}. It traces operating system calls used by the
+out which packages we need for the pipeline to fucntion properly. Here, we used 
+Reprozip~\cite{rampin2016reprozip}. It is a tool that
+is used to make applications reproducible. It traces operating system calls used by the
 application while execution and then based on that it recognizes binaries, files, environment variables,
@@
 uses available package manager to acquire a list of distribution packages from where these files come from.
-So, we got this list of packages from Reprozip that are needed for the application execution. 
+So, we got a list of packages from Reprozip that are needed for the application execution. 
 After that, we expanded this list by adding important and required packages that are essential
-for the system to function and finally figured out all the dependencies of these packages using debtree
-(\href{http://manpages.ubuntu.com/manpages/xenial/man1/debtree.1.html}{http://manpages.ubuntu.com/manpages/xenial/man1/debtree.1.html}).
-Ultimately, we kept these packages and removed remaining unnecessary packages. We used bash script
+for the system to function and finally figured out all the dependencies of these packages using Debtree
+~\cite{debtree}.
+Ultimately, we kept these packages and removed remaining unnecessary packages. We used a bash script
+(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github}) for getting
+a list of unnecessary packages.
 
@@
 When we add all regions of Venn diagram
-we get total 20050 vulnerabilities in Bids and Boutiques images.
+we get total 20050 vulnerabilities in BIDS apps and Boutiques images.
 It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
-reported by Anchore, 673 only reported by Clair, and 325 only detected by Vuls.
+reported by Anchore, 673 reported only by Clair, and 325 detected only by Vuls.
 
 The number and type of vulnerabilities reported by the three scanners are drastically different from each other.
-The question arises why these scanners report different numbers and types of vulnerabilities.
-How their logic differs and what exactly is making these results different than each other.
+It was interesting to investigate the reasons of these differences.
+%these scanners report different numbers and types of vulnerabilities.
+%How their logic differs and what exactly is making these results different than each other.
 
@@
 getting different results from these scanners. These reasons include bugs in scanners,
-some scanners ignoring vulnerabilities in a particular package, referring to different databases,
+some scanners ignoring vulnerabilities in a Linux-Kernel header packages, referring to different databases,
 how frequently they are updating their databases, etc.
@@
 \end{comment}
-Figure~\ref{fig:graph2} compares the number of vulnerabilities that are detected by Anchore before and after 
+Figure~\ref{fig:graph2} represents the number of vulnerabilities that are detected by Anchore before and after 
 the update of these images.
@@
 Our last experiment shows deleting unnecessary packages from the image also helps to reduce
-the number of vulnerabilities by significant number.
+the number of vulnerabilities by a significant number. We started this experiment with
+\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
+to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
+to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
+from 353 to 101.
 \bibliography{bibliography}

### 2020-05-14 paper.tex
discussion added

@@
 
-\begin{comment}
-\subsubsection{ReproNim}
-
-ReproNim is a Center for Reproducible Neuroimaging Computation. It is a vision
-to help neuroscientists in reproducing neuroimaging research. Repronim
-uses RepronIn, BrainVerse, Neuroimaging Computation Environments Manager (NICEMAN),
-and NeuroBlast software tools for its
-functioning. ReproIn is a software that automate acquisition and conversion
-of collected MRI data to BIDS standard format with DataLad version management~\cite{kennedy2019everything}.
-BrainVerse is a cross-platform software framework and collaborative desktop application
-that helps in managing, tracking, and sharing information.
-NICEMAN is a software system that tracks and manages available computation resources
-and makes their use in a scalable and reproducible way.
-Neuroblast is a service that facilitates data sharing of existing studies, and it also
-helps users to search similar studies based on combination of analysis,
-tasks and activation patterns. There are currently 28 different Singularity
-images used by Repronim.
-
-\subsection{Other images}
-
-\TG{We could also use selected images from DockerHub or SingularityHub. For
-instances the ones used by AFNI or other neuroimaging tools not represented
-in Boutiques or BIDS Apps. However we wouldn't be able to shrink these
-images unless we identified specific command-lines to run.}
-
-\end{comment}
+%\begin{comment}
+%\subsubsection{ReproNim}
+%
+%ReproNim is a Center for Reproducible Neuroimaging Computation. It is a vision
+%to help neuroscientists in reproducing neuroimaging research. Repronim
+%uses RepronIn, BrainVerse, Neuroimaging Computation Environments Manager (NICEMAN),
+%and NeuroBlast software tools for its
+%functioning. ReproIn is a software that automate acquisition and conversion
+%of collected MRI data to BIDS standard format with DataLad version management~\cite{kennedy2019everything}.
+%BrainVerse is a cross-platform software framework and collaborative desktop application
+%that helps in managing, tracking, and sharing information.
+%NICEMAN is a software system that tracks and manages available computation resources
+%and makes their use in a scalable and reproducible way.
+%Neuroblast is a service that facilitates data sharing of existing studies, and it also
+%helps users to search similar studies based on combination of analysis,
+%tasks and activation patterns. There are currently 28 different Singularity
+%images used by Repronim. 
+%
+%\subsection{Other images}
+%
+%\TG{We could also use selected images from DockerHub or SingularityHub. For
+%instances the ones used by AFNI or other neuroimaging tools not represented
+%in Boutiques or BIDS Apps. However we wouldn't be able to shrink these
+%images unless we identified specific command-lines to run.}
+%
+%\end{comment}
 
@@
 
-\begin{comment}
-Out of the various container image scanning tools available to scan Docker images,
-we selected Anchore~\cite{github_2019}
-and Vuls~\cite{future-architect_2019} because these are the most mature scanning tools. To scan Singularity images
-we use Stools, which is specially designed for Singularity images. This tool internally uses
-Clair Scanner tool so we included ClairScanner also in our experiements to compare
-performance of both the tools. So total there are three scanners for Docker images
-and one scanner for Singularity images.
-\end{comment}
+%\begin{comment}
+%Out of the various container image scanning tools available to scan Docker images,
+%we selected Anchore~\cite{github_2019}
+%and Vuls~\cite{future-architect_2019} because these are the most mature scanning tools. To scan Singularity images
+%we use Stools, which is specially designed for Singularity images. This tool internally uses
+%Clair Scanner tool so we included ClairScanner also in our experiements to compare
+%performance of both the tools. So total there are three scanners for Docker images
+%and one scanner for Singularity images.
+%\end{comment}
 
@@
 findings of other scientists.
-\linespread{0.5}
 \subsection{Image size Reduction process}
-
 If we want to reduce number of vulnerabilities without effecting the reproducibility of the image,
@@
 vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine.
-
 \begin{table*}
@@
 \end{table*}
-
-\begin{comment}
-\begin{table}
-\csvreader[%
- respect all,%
-  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
-      \begin{adjustbox}{max width=\columnwidth},
-  after reading=\end{adjustbox},
- tabular={c|c},
-	table head ={Image Tag} & {Image Name}\\\hline,
- late after line= \\,
-        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
-]{names.csv}{}{\csvlinetotablerow}%
-       \centering
-	\caption{\label{table2}Image names}
-\end{table}
-\end{comment}
-
+%\begin{comment}
+%\begin{table}
+%\csvreader[%
+% respect all,%
+%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
+%      \begin{adjustbox}{max width=\columnwidth},
+%  after reading=\end{adjustbox},
+% tabular={c|c},
+%	table head ={Image Tag} & {Image Name}\\\hline,
+% late after line= \\,
+%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
+%]{names.csv}{}{\csvlinetotablerow}%
+%       \centering
+%	\caption{\label{table2}Image names}
+%\end{table}
+%\end{comment}
 \begin{figure}[H]
@@
 
-\begin{figure*}[!htb]
+\begin{figure*}
 	{\includegraphics[scale=1.5,width=\textwidth]
@@
 are a fixed set of packages that contain vulnerabilities and have no fix yet.
-\begin{figure*}[!htb]
+\begin{figure*}
         {\includegraphics[width=\textwidth]
-        {Figures/afterupdatewithpackage.pdf}}
+        {Figures/vulnwithupdate.pdf}}
         \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
@@
 from 353 to 101.
+
+\begin{figure*}
+        {\includegraphics[scale=1.5,width=\textwidth]
+        {Figures/bargraph.png}}
+        \caption{\label{fig:bargraph} Bar graph representing \#Vulnerabilities by different experiments}
+      \end{figure*}
+
+\subsection{Discussion}
+
+None of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
+some are critical vulnerabilities. Yet there is not a single image scanner on which we can reply upon for
+scanning. Additionally, we cannot update all images because some OS already reached end-of-life and are
+no longer getting updates. Futhermore, minimization of images is time consuming process. As we have to run
+the pipeline to get Reprozip trace that can take upto several hours. Also user should have proper knowledge
+of running the pipeline because it is image specific. In addition to that, Reprozip can be only installed
+in the images having Python version 2.7.3 or greater, or 3.3 or greater. Also there is no guarantee that
+the commands that you ran to get Reprozip trace covered the whole program, may be it run a particular
+branch of the program. So there should be some kind of coverage measurement.
+
+\subsection{Conclusion}
+
+In this paper, we performed various experiments to study the security state of the Docker
+and Singularity images, which are used in the neuroimaging field. We found out strong correlation
+between the number of packages and the number of vulnerabilities in the images, which implies
+that the number of vulnerabilities increases with the number of packages. We also found out that
+updating images reduces the number of vulnerabilities by a significant number, however they cannot
+be made invulnerable.
+
 \bibliography{bibliography}

### 2020-05-14 Scripts/RemovalafterUpdate/script.sh

@@ -1,0 +1,69 @@
+#!/bin/bash
+
+apt list --installed | awk -F/ '{print $1}' | tail -n +2 > all-packages.csv
+apt-get update
+apt-get install -y debtree
+apt install aptitude -y
+aptitude -F %p search --disable-columns '~Rprovides:~i ~v' >> virtual.csv
+aptitude -F %p search --disable-columns ~pimportant >> required.csv
+aptitude -F %p search --disable-columns ~prequired >> required.csv
+cat required.csv | sort | uniq >> uniq_required-0.csv
+touch keep_virtual.csv
+IFS=$'\n'
+number=0
+
+###function####
+get_dependencies() {
+for k in $(cat $1)
+do
+(for i in $(debtree --show-installed --no-skip --show-all $k | tail -n +4); do if [[ $i == *"->"* ]]; then     c=$(echo $i | awk '{print $1}' | sed 's/"//g');     if [[ $c == *:* ]];     then       echo echo $c | awk -F: '{print $2}';     else       echo $c;     fi; else if [[ $i == *";"* ]]; then    echo $i |sed -e 's/^[[:space:]]*//' |sed 's/"//g'|head -n1 | awk '{print $1}';elif [[ $i == *"label = "* ]]; then str=$(echo $i | awk '{print $3}'); prefix='"<'; suffix='>';foo=${str#"$prefix"};foo=${foo%"$suffix"}; echo "${foo}" >> $2; fi; fi; done; ) | sort | uniq >> $3
+done
+cat $3 | sort | uniq >> $4
+cat $2 | sort | uniq >> $5
+comm -13 <(sort $4) <(sort $5) >> $6
+}
+
+#####function#####
+get_package() {
+for x in $(cat $1)
+do
+echo "getting package of virtual package "$x
+aptitude -F %p search --disable-columns '~P'$x' ~i' >> $2
+done
+}
+
+while [ $(cat "uniq_required-${number}.csv" | wc --lines) != 0 ]
+do
+echo "************************************************ROUND ${number}***********************************************************************"
+uniq_required="uniq_required-${number}.csv"
+label="label-${number}.csv"
+total_p="total_p-${number}.csv"
+total_packages="total_packages-${number}.csv"
+temp_label="temp_label-${number}.csv"
+uniq_label="uniq_label-${number}.csv"
+installed_p="installed-${number}.csv"
+virtual_p="virtual_p-${number}.csv"
+installed_label="installed_label-${number}.csv"
+virtual_label="virtual_label-${number}.csv"
[…]

### 2020-05-14 Scripts/RemovalafterUpdate/to_delete.py

@@ -1,0 +1,19 @@
+#!/usr/bin/env python
+
+
+all = None
+keep = None
+
+with open('all-packages.csv', 'r') as f:
+  all = f.readlines()
+
+with open('uniq_keep_installed.csv', 'r') as f:
+  keep = f.readlines()
+
+remove = [ p.strip() for p in all if not p in keep ]
+str3 = ' '.join(str(e) for e in remove)
+print(str3)
+print(len(remove))
+#for p in remove:
+#    print(p)
+

### 2020-05-14 Scripts/Updation/update-images.sh

@@ -23,5 +23,5 @@ do
         #docker run -it --entrypoint /bin/bash ${image} ./update.sh &>${image}.log && echo "[ OK ]"
 	echo -n "Commiting updated image... "
 	ID=$(docker ps -a | head -2 | awk '$1!="CONTAINER" {print $1}')
-	docker commit ${ID} updated_${name2} && echo "[ OK ]"
+	docker commit ${ID} kaurbhupinder/updated_${name2} && echo "[ OK ]"
 done

### 2020-05-14 Scripts/Updation/update.sh

@@ -12,6 +12,5 @@ function find-pm {
 
 \rm -f .updated
 find-pm yum && (yum update -y && touch .updated)
-#find-pm apt && (apt update -y && apt upgrade -y && apt-get autoremove -y && apt-get autoclean -y && touch .updated)
-find-pm apt && (apt update -y && apt upgrade -y && touch .updated)
+find-pm apt && (apt update -y && apt upgrade -y && apt-get autoremove -y && apt-get autoclean -y && touch .updated)
 test -f .updated || die "Cannot find package manager or update failed"

### 2020-05-14 Scripts/after_minification.py

@@ -3,7 +3,7 @@
 import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
-d = pd.read_csv(r"../Results_after_update2.csv")
+d = pd.read_csv(r"../Results_after_minification.csv")
 df=pd.DataFrame(d)
 packages=[]
 before=[]
@@ -18,16 +18,16 @@ plt.plot([],[])
 #print(packages)
 #ax=fig.add_axes([0,0,1,1])
 plt.figure(figsize=(20,10))
-p1=plt.scatter(packages, before, color='r',s=150,marker='o',label='Before Update')
-p2=plt.scatter(packages, after, color='b',s=150,marker='D',label='After Update')
-z = np.polyfit(packages, before,1)
+p1=plt.scatter(packages, before, color='r',s=150,marker='o',label='Before Minification')
+p2=plt.scatter(packages, after, color='b',s=150,marker='D',label='After Minification')
+z = np.polyfit(packages, before, 1)
 p = np.poly1d(z)
 plt.plot(packages,p(packages),"r--")
 y = np.polyfit(packages, after, 1)
-p3 = np.poly1d(y)
-plt.plot(packages,p3(packages),"b--")
-plt.xlabel('#Packages', fontsize=15)
+p2 = np.poly1d(y)
+plt.plot(packages,p2(packages),"b--")
+plt.xlabel('#Packages Originally', fontsize=15)
 plt.ylabel('#Vulnerabilities',fontsize=15)
 plt.legend(loc='upper left', bbox_to_anchor=(1.00, 1.00), shadow=True, ncol=1,labelspacing=1.2,borderpad=1.0)
 #plt.show()
-plt.savefig('afterupdatewithpackage.pdf',bbox_inches='tight')
+plt.savefig('afterMinification.pdf',bbox_inches='tight')

### 2020-05-14 Scripts/after_updateANDminification.py

@@ -3,31 +3,25 @@
 import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
-d = pd.read_csv(r"../Results_after_update2.csv")
+d = pd.read_csv(r"../Results_after_updateANDminification.csv")
 df=pd.DataFrame(d)
 packages=[]
-before=[]
-after=[]
+vuln=[]
 for idx,row in df.iterrows():
     packages.append(row[0])
-    before.append(row[1])
-    after.append(row[2])
+    vuln.append(row[1])
 fig=plt.figure()
 #ax = fig.add_subplot()
 plt.plot([],[])
 #print(packages)
 #ax=fig.add_axes([0,0,1,1])
 plt.figure(figsize=(20,10))
-p1=plt.scatter(packages, before, color='r',s=150,marker='o',label='Before Update')
-p2=plt.scatter(packages, after, color='b',s=150,marker='D',label='After Update')
-z = np.polyfit(packages, before,1)
+p1=plt.scatter(packages, vuln, color='r',s=150,marker='o',label='After Minification and Update')
+z = np.polyfit(packages, vuln,1)
 p = np.poly1d(z)
 plt.plot(packages,p(packages),"r--")
-y = np.polyfit(packages, after, 1)
-p3 = np.poly1d(y)
-plt.plot(packages,p3(packages),"b--")
 plt.xlabel('#Packages', fontsize=15)
 plt.ylabel('#Vulnerabilities',fontsize=15)
 plt.legend(loc='upper left', bbox_to_anchor=(1.00, 1.00), shadow=True, ncol=1,labelspacing=1.2,borderpad=1.0)
 #plt.show()
-plt.savefig('afterupdatewithpackage.pdf',bbox_inches='tight')
+plt.savefig('bothUPDATEandMinification.pdf',bbox_inches='tight')

### 2020-05-14 Scripts/barchart.py

@@ -1,0 +1,56 @@
+import numpy as np
+import pandas as pd
+import matplotlib.pyplot as plt
+
+# data to plot
+d = pd.read_csv(r"../allResults.csv")
+df=pd.DataFrame(d)
+imageID=[]
+before=[]
+afterUpdate=[]
+afterMinification=[]
+afterUpdateANDminify=[]
+for idx,row in df.iterrows():
+    imageID.append(row[0])
+    before.append(row[1])
+    afterUpdate.append(row[2])
+    afterMinification.append(row[3])
+    afterUpdateANDminify.append(row[4])
+
+
+n_groups = len(imageID)
+
+# create plot
+fig, ax = plt.subplots()
+index = np.arange(n_groups)
+bar_width = 0.20
+opacity = 0.7
+
+rects1 = plt.bar(index, before, bar_width,
+alpha=opacity,
+color='b',
+label='Originally')
+
+rects2 = plt.bar(index + bar_width, afterUpdate, bar_width,
+alpha=opacity,
+color='g',
+label='After Update')
+
+rects3 = plt.bar(index + 2*bar_width, afterMinification, bar_width,
+alpha=opacity,
+color='r',
+label='After Minification')
+
+rects4 = plt.bar(index + 3*bar_width, afterUpdateANDminify, bar_width,
+alpha=opacity,
+color='c',
+label='After update and minification')
+
+plt.xlabel('Images', fontweight='bold')
+plt.ylabel('#Vulnerabilities', fontweight='bold')
+#plt.title('Vulnerabilities by experiments')
+plt.xticks(index + bar_width, imageID)
+plt.legend()
+
+plt.tight_layout()
+plt.show()

### 2020-05-14 Scripts/check.py

@@ -4,12 +4,13 @@
 import matplotlib.pyplot as plt
 import seaborn as sns
 import pandas as pd
-
+import numpy as np
 # Load the data
-d = pd.read_csv(r"../train2.csv")
+d = pd.read_csv(r"../train3.csv")
 d.head()
 df=pd.DataFrame(d)
 plt.figure(figsize=(200,20))
+plt.rcParams["axes.labelweight"] = "bold"
 colors = {'ubuntu:14.04' : '#2E37FE', 'ubuntu:16.04' : '#CAE1FF', 'ubuntu:17.04':'#5190ED','ubuntu:17.10':'#000085','ubuntu:18.04' : '#98F5FF','centos 6':'#800080','centos 7':'#b19cd9',
         'alpine:3.7.1':'#3CB371','alpine:3.8.4':'#00ff00','alpine:3.9.0':'#006400','debian:8':'#ffa500'}
 markers = {"ubuntu:14.04": "o", "ubuntu:16.04": "o",'ubuntu:17.04':'o','ubuntu:17.10':'o','ubuntu:18.04' : 'o','centos 6':'o','centos 7':'o',
@@ -25,6 +26,9 @@ leg = p1._legend
 leg.set_bbox_to_anchor([1.01, 0.04])
 leg._loc = 4
 leg.texts[12].set_text("CRITICAL \nVulnerabilities")
+z = np.polyfit(df['Packages'], df['Vulnerabilities'], 1)
+p = np.poly1d(z)
+plt.plot(df['Packages'],p(df['Packages']),"r--")
 #leg._labelspacing=10
 for idx,row in df.iterrows():
     x = row[3]

### 2020-05-14 Scripts/deleted_packages_graph.py

@@ -1,0 +1,27 @@
+#!/usr/bin/env python3
+
+import matplotlib.pyplot as plt
+import pandas as pd
+import numpy as np
+d = pd.read_csv(r"../Results_with_deleted_number_of_packages.csv")
+df=pd.DataFrame(d)
+packages=[]
+diff=[]
+for idx,row in df.iterrows():
+    packages.append(row[0])
+    diff.append(row[1])
+fig=plt.figure()
+#ax = fig.add_subplot()
+plt.plot([],[])
+#print(packages)
+#ax=fig.add_axes([0,0,1,1])
+plt.figure(figsize=(20,10))
+p1=plt.scatter(packages, diff, color='r',s=150,marker='o',label='Vulnerability diff after minification')
+z = np.polyfit(packages, diff,1)
+p = np.poly1d(z)
+plt.plot(packages,p(packages),"r--")
+plt.xlabel('#Deleted Packages', fontsize=15)
+plt.ylabel('#Vulnerability diff',fontsize=15)
+plt.legend(loc='upper left', bbox_to_anchor=(1.00, 1.00), shadow=True, ncol=1,labelspacing=1.2,borderpad=1.0)
+#plt.show()
+plt.savefig('graphwithdeletedpackages.pdf',bbox_inches='tight')

### 2020-05-14 Scripts/script.py

@@ -4,7 +4,7 @@
 import matplotlib.pyplot as plt
 import seaborn as sns
 import pandas as pd
-
+import numpy as np
 # Load the data
 d = pd.read_csv(r"../train.csv")
 d.head()
@@ -14,7 +14,7 @@ colors = {'ubuntu:14.04' : '#2E37FE', 'ubuntu:16.04' : '#CAE1FF', 'ubuntu:17.04'
 markers = {"ubuntu:14.04": "o", "ubuntu:16.04": "o",'ubuntu:17.04':'o','ubuntu:17.10':'o','ubuntu:18.04' : 'o','centos 6':'o','centos 7':'o',
         "alpine:3.7.1":'o','alpine:3.8.4':"o","alpine:3.9.0":"o","debian:8":"o"}
 with sns.plotting_context(rc={"legend.fontsize":25,"font.size":18,"axes.titlesize":20,"font.weight":'heavy',"legend.labelspacing":20}):
-  p1=sns.relplot(x="Packages",y="Vulnerabilities",hue="OS distribution",size="CRITICAL Vulnerabilities",sizes=(1000,4000),data = df,palette=colors,markers=markers,style="OS distribution",height=10, aspect=2)
+  p1=sns.relplot(x="Packages",y="Vulnerabilities",hue="OS distribution",size="CRITICAL Vulnerabilities",sizes=(300,800),data = df,palette=colors,markers=markers,style="OS distribution",height=10, aspect=2)
 p1.set(xlabel='#Packages', ylabel='#Vulnerabilities')
 p1.set(xticks=[i for i in range(0, max(df['Packages']) + 100, 50)],
        yticks=[i for i in range(0, max(df['Vulnerabilities']) + 20, 250)])
@@ -25,6 +25,10 @@ leg.set_bbox_to_anchor([1.01, 0.04])
 leg._loc = 4
 leg.texts[12].set_text("CRITICAL \nVulnerabilities")
 leg._labelspacing=50
+z = np.polyfit(df['Packages'], df['Vulnerabilities'], 1)
+p = np.poly1d(z)
+plt.plot(df['Packages'],p(df['Packages']),"r--")
+
 for idx,row in df.iterrows():
     x = row[3]
     y = row[2]
@@ -34,6 +38,6 @@ for idx,row in df.iterrows():
     rot=row[10]
     hoz=row[11]
     ver=row[12]
[…]

### 2020-05-14 Scripts/updateandminification.py

@@ -3,31 +3,37 @@
 import matplotlib.pyplot as plt
 import pandas as pd
 import numpy as np
-d = pd.read_csv(r"../Results_after_update2.csv")
+d = pd.read_csv(r"../updateandminification.csv")
 df=pd.DataFrame(d)
 packages=[]
 before=[]
-after=[]
+update=[]
+delete=[]
 for idx,row in df.iterrows():
     packages.append(row[0])
     before.append(row[1])
-    after.append(row[2])
+    update.append(row[2])
+    delete.append(row[3])
 fig=plt.figure()
 #ax = fig.add_subplot()
 plt.plot([],[])
 #print(packages)
 #ax=fig.add_axes([0,0,1,1])
 plt.figure(figsize=(20,10))
-p1=plt.scatter(packages, before, color='r',s=150,marker='o',label='Before Update')
-p2=plt.scatter(packages, after, color='b',s=150,marker='D',label='After Update')
+p1=plt.scatter(packages, before, color='r',s=150,marker='o',label='Before')
+p2=plt.scatter(packages, update, color='b',s=150,marker='D',label='After Update')
+p3=plt.scatter(packages,delete, color='g',s=150,marker='*',label='After Minification')
 z = np.polyfit(packages, before,1)
 p = np.poly1d(z)
 plt.plot(packages,p(packages),"r--")
-y = np.polyfit(packages, after, 1)
-p3 = np.poly1d(y)
-plt.plot(packages,p3(packages),"b--")
+y = np.polyfit(packages, update, 1)
+p4 = np.poly1d(y)
+plt.plot(packages,p4(packages),"b--")
+x = np.polyfit(packages, delete,1)
+p5 = np.poly1d(x)
+plt.plot(packages,p5(packages),"g--")
 plt.xlabel('#Packages', fontsize=15)
 plt.ylabel('#Vulnerabilities',fontsize=15)
 plt.legend(loc='upper left', bbox_to_anchor=(1.00, 1.00), shadow=True, ncol=1,labelspacing=1.2,borderpad=1.0)
 #plt.show()
-plt.savefig('afterupdatewithpackage.pdf',bbox_inches='tight')
+plt.savefig('updateandminification.pdf',bbox_inches='tight')

### 2020-05-14 Scripts/updation.py

@@ -1,0 +1,64 @@
+#!/usr/bin/env python3
+
+# Import the necessary libraries
+import matplotlib.pyplot as plt
+import seaborn as sns
+import pandas as pd
+import numpy as np
+# Load the data
+d = pd.read_csv(r"../train3.csv")
+d.head()
+df=pd.DataFrame(d)
+plt.figure(figsize=(200,20))
+plt.rcParams["axes.labelweight"] = "bold"
+colors = {'ubuntu:14.04' : '#2E37FE', 'ubuntu:16.04' : '#CAE1FF', 'ubuntu:17.04':'#5190ED','ubuntu:17.10':'#000085','ubuntu:18.04' : '#98F5FF','centos 6':'#800080','centos 7':'#b19cd9',
+        'alpine:3.7.1':'#3CB371','alpine:3.8.4':'#00ff00','alpine:3.9.0':'#006400','debian:8':'#ffa500'}
+markers = {"ubuntu:14.04": "o", "ubuntu:16.04": "o",'ubuntu:17.04':'o','ubuntu:17.10':'o','ubuntu:18.04' : 'o','centos 6':'o','centos 7':'o',
+        "alpine:3.7.1":'o','alpine:3.8.4':"o","alpine:3.9.0":"o","debian:8":"o"}
+p1=sns.relplot(x="Packages",y="Vulnerabilities",hue="OS distribution",size="CRITICAL Vulnerabilities",sizes=(300,1450),data = df,palette=colors,markers=markers,style="OS distribution",height=10, aspect=2,legend=False)
+p1.set(xlabel='#Packages', ylabel='#Vulnerabilities')
+p1.set(xticks=[i for i in range(0, max(df['Packages']) + 100, 50)],
+       yticks=[i for i in range(0, max(df['Vulnerabilities']) + 20, 250)])
+ax = p1.axes[0,0]
+#leg = p1._legend
+#p1.legend(loc='center left', bbox_to_anchor=(1.25, 0.5), ncol=1)
+#leg.set_bbox_to_anchor([1.01, 0.04])
+#leg._loc = 4
+#leg.texts[12].set_text("CRITICAL \nVulnerabilities")
+#leg.remove()
+z = np.polyfit(df['Packages'], df['Vulnerabilities'], 1)
+p = np.poly1d(z)
+plt.plot(df['Packages'],p(df['Packages']),"k--")
+
+
+
+d = pd.read_csv(r"../Results_after_update2.csv")
+df=pd.DataFrame(d)
+packages=[]
[…]

### 2020-05-16 paper.tex
figures correctly placed

@@
 primary research question of this work: \textit{what is the current security state of
-container images that are deployed on HPC clusters}.
+container images that are deployed on HPC clusters?}.
 
@@
 Here, we focus mainly on vulnerability scanning.
-\begin{comment}
-Malware is a computer software that is specially designed to attack the target computer,
-whereas 
-\end{comment}
 Vulnerability is a weakness in the developer's software that can be used
@@
 In this paper, we report all vulnerabilities that are present in
-container images, specifically used by neuroimaging field, and access their
-related risks for data analysis. Particularly, we aim to answer three primary
-research questions:
+container images, specifically used by neuroimaging field. Particularly,
+we aim to answer four primary research questions:
 
@@
 size of the image?
+
+\textit{RQ4:} Can we get rid of these vulnerabilities by both updating
+and shrinking image size?
 
@@
 are not detected by Clair Scanner but they affect Ubuntu 14.04 LTS hence detected by Vuls. For example, CVE-2017-1375.
+\begin{figure*}[b]
+        {\includegraphics[width=\textwidth]
+        {Figures/vulnwithupdate.pdf}}
+        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and
+        after update of the images}
+      \end{figure*}
 
@@
 
+\begin{figure*}[b]
+        {\includegraphics[scale=1.5,width=\textwidth]
+        {Figures/bargraph.png}}
+        \caption{\label{fig:bargraph} Bar graph representing \#Vulnerabilities by different experiments}
+      \end{figure*}
 \subsection{Effect Of Update}
@@
 are a fixed set of packages that contain vulnerabilities and have no fix yet.
-\begin{figure*}
-        {\includegraphics[width=\textwidth]
-        {Figures/vulnwithupdate.pdf}}
-        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
-	after update of the images}
-      \end{figure*}
+%\begin{figure*}[h]
+%        {\includegraphics[width=\textwidth]
+%        {Figures/vulnwithupdate.pdf}}
+%        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
+%	after update of the images}
+%      \end{figure*}
+
 \subsection{Effect Of Size Reduction}
 
-Our last experiment shows deleting unnecessary packages from the image also helps to reduce
+Our third experiment shows deleting unnecessary packages from the image also helps to reduce
 the number of vulnerabilities by a significant number. We started this experiment with
@@
 
-\begin{figure*}
-        {\includegraphics[scale=1.5,width=\textwidth]
-        {Figures/bargraph.png}}
-        \caption{\label{fig:bargraph} Bar graph representing \#Vulnerabilities by different experiments}
-      \end{figure*}
+\subsection{Effect Of Update and Size Reduction}
+
+Our last experiment includes updating the image and then removing unnecessary packages from it.
+Our initial thought was that it will reduce the number of vulnerabilities significantly. Howver
+we analyzed that this is not always true. It depends on which packages you are deleting and how
+many vulnerabilities they contain. In particular, if a package contains a large number of vulnerabilities
+it means deleting that package will help to reduce vulnerabilities in that image by a significant number.
+Contrary
 
@@
 that the number of vulnerabilities increases with the number of packages. We also found out that
-updating images reduces the number of vulnerabilities by a significant number, however they cannot
-be made invulnerable.
+updating images reduces the number of vulnerabilities by a significant number. However, for some
+vulnerabilities there are no fixes available yet so the images cannot 
+be made totally invulnerable. Continuing with our next experiment of minification, we thought that
+it will decrease vulnerabilities by a significant number. However, we found out that this is not
+the case always.
 

### 2020-05-19 paper.tex
changed intro

@@
 Here, we focus mainly on vulnerability scanning.
-Vulnerability is a weakness in the developer's software that can be used
+Vulnerability is a weakness in the developer's software that can be exploited
 by the attacker to perform unathorized actions on the target computer.
@@
 containers are used on Compute Canada HPC cluster.
+
 The existing research work on containers focuses mainly on the security of Docker
@@
 This paper is organized as follows: in next section, we provide description
-of materials and methods which includes summarizing a particular use case of
-containers in neuroscience, which is used for scientific computing. It involves
-usage of containers on shared HPC cluster. Additionally, in this section we
-describe all the resources that are used by this use case. We also explain
+of materials and methods which summarizes our four main experiments. We also explain
 scanning tools that we use for scanning container images to report
 vulnerabilities. Next section of this paper is about the results. Here, we
-present number and type of vulnerabilites that are present in the container images
-which are used for data analysis on shared HPC clusters, and discuss how many of them are
-critical vulnerabilities. Following section is about discussion of these results
-where we provide more insight into the risks that are caused by these vulnerabilties
-and how they can be leveraged to design attacks. Here, we also provide some such
-vulnerability examples. Finally, we conclude this paper by discussing ten simple
-rules that can be followed to secure container image for use in clusters.
+present number of vulnerabilites that are present in the container images
+which are used for data analysis on shared HPC clusters. Following section is about 
+discussion of these results where we provide more insight into the problems that 
+we faced while conducting these experiments. Finally, we conclude this paper by discussing ten simple
+rules that can be followed to secure container images for use in clusters.
 
@@
 
-This study involves three image scanning experiments.
+This study involves four image scanning experiments.
 The first experiment scans the images as is to report the existing vulnerabilities
@@
 vulnerabilities present inside the image, which will be presented as our third experiment.
+Lastly, our fourth experiment involves both updating and shrinking the image size and then
+rescanning for the vulnerabilities.
 
-We first
+Here, we first
 introduce two container tools used in our experiments: Docker and
@@
 
-\begin{comment}
-As we are taking a particular use case of containers from
-neuroscience field i.e Canadian Open Neuroscoence Platform (CONP) so  
-in this section we summarize the data and tools 
-that are used in CONP. CONP is a national platform for sharing neuroscience
-research data and aims at creating an interactive interface for neuroscientists and
-clinical neuroscience. The main goal of the CONP platform is to store, process, and
-distribute massive amounts of data produced by modern neuroscience.
-Here, we summarize all the resources that are
-used by CONP to function.
-\end{comment}
+%As we are taking a particular use case of containers from
+%neuroscience field i.e Canadian Open Neuroscoence Platform (CONP) so  
+%in this section we summarize the data and tools 
+%that are used in CONP. CONP is a national platform for sharing neuroscience
+%research data and aims at creating an interactive interface for neuroscientists and
+%clinical neuroscience. The main goal of the CONP platform is to store, process, and
+%distribute massive amounts of data produced by modern neuroscience.
+%Here, we summarize all the resources that are
+%used by CONP to function.
 
@@
 
-\begin{comment}
-consists of the following three main components:
-
-\textit{Docker Daemon:} It acts as a server. It is
-a long-running process that manages all Docker images, containers, storage volumes, and networks.
-
-\textit{REST API:} It acts as an interface between the server and the client, and is an API which is used by the applications
-to talk to the \textit{Docker Daemon}.
-
-\textit{Client:} It is a Command Line Interface (CLI) client which is used to interact with the \textit{Docker Daemon}.
-convert english to punjabi
-\end{comment}
+%consists of the following three main components: 
+%
+%\textit{Docker Daemon:} It acts as a server. It is
+%a long-running process that manages all Docker images, containers, storage volumes, and networks.
+%
+%\textit{REST API:} It acts as an interface between the server and the client, and is an API which is used by the applications
+%to talk to the \textit{Docker Daemon}.
+%
+%\textit{Client:} It is a Command Line Interface (CLI) client which is used to interact with the \textit{Docker Daemon}.
 %Docker runs a software, \textit{Docker daemon}, on the host machine.
@@
 
-\begin{comment}
-Singularity offers mobility of compute by facilitating portable environments 
-through a single image file~\cite{kurtzer2017singularity}. Once Singularity image
-is created, it is hashed using SHA-256. Hence, it cannot be changed
-once it is created, consequently, it can be used for reproducing the results of
-scientific experiments. Main features provided by
-Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
-We used Singularity version $2.5.2$ in our experiments.
-Users can easily access files, devices, sockets, ports of the host system from
-the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
-into the running container. Additional directories can be specified with \textit{--bind}
-to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
-However namespaces can be requested if required. Users cannot escalate privileges inside
-Singularty containers. This is because Singularity do not run containers as root.
-Instead, a user inside Singularity container is the same user outside the container.
-
-\subsection{Container Image Formats}
-
-A container image is a package that contains an application along with its
-required dependencies and libraries.
-Both, Docker and Singularity, have different image formats. Below we provide a description of both image
-formats.
-
-\subsubsection{Docker Image Format}
-
-Docker images are organized as a series of layers stacked on top of each
-other and identified by unique layer identifiers. If a layer is reused
-in different images it will
-have the same id across images. Each layer consists of a filesystem diff
-with respect to the layer below. 
-DockerHub uses gzip compression for
-transferring layers.There are two ways to create a Docker image. The
-first is to use an existing Docker image as a base image and then build a
-new image from that one, by making changes in the filesystem, which is
-saved as a new layer of the Docker image. The second way is to build a new
-Docker image from scratch.Docker supports several different storage drivers.
-\textit{Overlay2} is the preferred storage driver used by Docker for all currently
-supported Linux versions, whereas \textit{aufs} is preferred for Docker 18.06 and
-older, when using Ubuntu 14.04 on kernel 3.13 as it do not support \textit{overlay2}.
-Other storage drivers that are supported by Docker include \textit{devicemapper, btrfs,
-zfs, and vfs}
-
-\subsubsection{Singularity Image Format}
-
-On the other hand, a Singularity image is a single immutable file and 
-does not contain layers.
-Once a Singularity image is created, it cannot be changed, consequently,
-it can be used for reproducing the results of scientific
-experiments.
-Singularity takes snapshot, locks, and archives the developed application,
-which is known as Singularity image.
-It means that Singularity image is a single immutable file that can be moved around as
-any other file. This file can be checksummed, signed, and easily
-used for verification purposes. Singularity containers use Squashfs file format
-by default. It is read-only file system in Linux, which uses compression for files,
-inodes, and directories. However, Singularity also supports two other 
-formats i.e \textit{sandbox} format
-(which is just a chroot
-directory) and \textit{writable} format (the ext3 file system).
-While publishing experimental results, authors can also publish Singularity
-image along with its hash, which allow other researchers to verify results.
-\end{comment}
+%\begin{comment}
+%Singularity offers mobility of compute by facilitating portable environments 
+%through a single image file~\cite{kurtzer2017singularity}. Once Singularity image
+%is created, it is hashed using SHA-256. Hence, it cannot be changed
+%once it is created, consequently, it can be used for reproducing the results of
+%scientific experiments. Main features provided by
+%Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
+%We used Singularity version $2.5.2$ in our experiments.
+%Users can easily access files, devices, sockets, ports of the host system from
+%the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
+%into the running container. Additional directories can be specified with \textit{--bind}
+%to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
+%However namespaces can be requested if required. Users cannot escalate privileges inside
+%Singularty containers. This is because Singularity do not run containers as root.
+%Instead, a user inside Singularity container is the same user outside the container.
+%
+%\subsection{Container Image Formats}
+%
+%A container image is a package that contains an application along with its
+%required dependencies and libraries.
+%Both, Docker and Singularity, have different image formats. Below we provide a description of both image
+%formats.
+%
+%\subsubsection{Docker Image Format}
+%
+%Docker images are organized as a series of layers stacked on top of each
+%other and identified by unique layer identifiers. If a layer is reused
+%in different images it will
+%have the same id across images. Each layer consists of a filesystem diff
+%with respect to the layer below. 
+%DockerHub uses gzip compression for
+%transferring layers.There are two ways to create a Docker image. The
+%first is to use an existing Docker image as a base image and then build a
+%new image from that one, by making changes in the filesystem, which is
+%saved as a new layer of the Docker image. The second way is to build a new
+%Docker image from scratch.Docker supports several different storage drivers.
+%\textit{Overlay2} is the preferred storage driver used by Docker for all currently
+%supported Linux versions, whereas \textit{aufs} is preferred for Docker 18.06 and
+%older, when using Ubuntu 14.04 on kernel 3.13 as it do not support \textit{overlay2}.
+%Other storage drivers that are supported by Docker include \textit{devicemapper, btrfs,
+%zfs, and vfs}
+%
+%\subsubsection{Singularity Image Format}
+%
+%On the other hand, a Singularity image is a single immutable file and 
+%does not contain layers.
+%Once a Singularity image is created, it cannot be changed, consequently,
+%it can be used for reproducing the results of scientific
+%experiments.
+%Singularity takes snapshot, locks, and archives the developed application,
+%which is known as Singularity image.
+%It means that Singularity image is a single immutable file that can be moved around as
+%any other file. This file can be checksummed, signed, and easily
+%used for verification purposes. Singularity containers use Squashfs file format
+%by default. It is read-only file system in Linux, which uses compression for files,
+%inodes, and directories. However, Singularity also supports two other 
+%formats i.e \textit{sandbox} format
+%(which is just a chroot
+%directory) and \textit{writable} format (the ext3 file system).
+%While publishing experimental results, authors can also publish Singularity
+%image along with its hash, which allow other researchers to verify results.
+%\end{comment}
 \subsection{Application frameworks}
@@
 image where the application is installed. A set of core tools help
-construct, validate, publish and execute Boutiques descriptors. Boutiques
+construct, validate, publish, and execute Boutiques descriptors. Boutiques
 applications are published on the Zenodo research repository.
 
-We used the 49 Boutiques applications published on Zenodo at the time of
+We used 49 Boutiques applications published on Zenodo at the time of
 the writing. These applications use 23 different container images. Out of these images,
-3 images are not found and 2 images were already included in BIDS images.
+we could not get 3 images and 2 images were already included in BIDS images.
 Therefore we are left with a total 18 Boutiques images which include 6
@@
 	Table~\ref{table1} displays the names of all the images that we took in our experiments.
+Table~\ref{sing} lists 6 Singularity images taken from Boutiques framework.
 %\begin{figure}
@@
 In Static scanning, an image is scanned without running it into a container. In respect to that,
-different image features are extracted like installed packages, their versions, files, etc.
+different image features are extracted like installed packages, their versions, files, etc. to list
+the vulnerabilities present inside the image.
 On the other hand, Dynamic scanning involves running a container from the image and then scanning the
@@
 Using a dynamic scanning technique, it offers
-remote and local scans. The remote scan involves setting up only one machine, to
+remote and local scans at the time of writing. The remote scan involves setting up only one machine, to
 which other target servers are connected via SSH. Local scan involves running
 the scan on the target server itself. Further, Vuls offer a fast scan, fast root scan,
-and deep scan.
+and deep scan mode.
 The Fast scan is performed without root privileges, whereas a fast root scan is
@@
 changelogs, which puts more load on the target server.
+
+In our experiments, we used Vuls Docker image having version v0.9.0 with fast scan mode.
 Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
-
 The interesting point is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
@@
 For that purpose, a Docker image is maintained that contains the Ubuntu CVE tracker database.
-Whenever Ubuntu updated its database, this image is also updated with the required information.
+Whenever Ubuntu updates its database, this image is also updated with the required information.
 
@@
 for scanning Singularity images for vulnerabilities.
-Initially, Clair Scanner was intended to scan Docker Containers. This tool does not fit well
+Initially, Clair Scanner was intended to scan Docker containers only. This tool does not fit well
 to scan Singularity images because of the different image formats.
@@
 for scanning and followed the steps mentioned in \href{https://github.com/singularityhub/stools}{Stools Github}.
+
+\begin{table}
+\csvreader[%
+ respect all,%
+  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
+      \begin{adjustbox}{max width=\columnwidth},
+  after reading=\end{adjustbox},
+ tabular={c |c},
+        table head =Singularity Images & {Vulnerabilities by Stools}\\\hline,
+ late after line= \\,
+        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
+]{Singularityresults.csv}{}{\csvlinetotablerow}%
+       \centering
+        \caption{\label{sing}Number of Vulnerabilities in Singularity images}
+\end{table}
 

### 2020-05-21 paper.tex
revised content

@@
 BIDS app and Boutiques images that we took for our experiments have diverse Linux
-distributions such as Ubuntu, Centos, Debian, and Alpine. In the case of Ubuntu, release
+distributions such as Ubuntu, Centos, Debian, and Alpine. Further, a particular
+distribution can have different releases. As images in our experiments mostly have
+Ubuntu distribution we can take this distribution as an example. In the case of Ubuntu, release
 can be of two types: regular or LTS (Long Term Support).
@@
 		CVE in some way, is not affected by the issue. Notes should
-		provide detailed information if needed. For e.g
-		"not-affected (1.14.6-1.1)" indicates that this specific
+		provide detailed information if needed. For e.g if the given
+		status is "not-affected (1.14.6-1.1)" then it indicates that this specific
 		package version in the given release is not affected.
@@
 		CVE in some way, is being ignored for some reason.  The
-		notes should provide that reason. For e.g "ignored (reached end-of-life)".
-		This means that this given Ubuntu release already reached
+		notes should provide that reason. For e.g if status looks  like
+		"ignored (reached end-of-life)", this means that this given Ubuntu release already reached
 		end-of-life so this CVE is ignored by Ubuntu. However, if there
@@
                   has been fixed but an update has not been yet uploaded or
-		  published. The "version" indicates the package version 
-		  that contains the fix.
+		  published. The package version that contains the fix is also
+		  alongwith the status.
 
@@
 		The fixed version of such packages is appended by
-		+esmN or ~esmN, indicating that this package version is available
+		+esmN or /~esmN, indicating that this package version is available
 		only via ESM.
@@
 Ultimately, we kept these packages and removed remaining unnecessary packages. We used a bash script
-(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github}) for getting
-a list of unnecessary packages.
+(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github}) for
+the image size reduction process which installs Reprozip in the image, collects Reprozip trace, and
+finally deletes unnecessary packages.
+
+\subsection{Update and Size Reduction Together}
+
+Our final experiment involves combination of both update and size reduction process
+to lessen the number of vulnerabilities.
+So in this process we first update all the packages in the image and then deletes
+the unnecessary packages. For this process we used the same two scripts that
+we used for earlier experiments.
 
@@
 results of the three scanners. Then we discuss the effect of the update on the
-existing vulnerabilities and lastly, this section presents the effect of image size reduction on the
-vulnerabilities.
+existing vulnerabilities followed by the results of the image size reduction
+process. Lastly, this section presents the combined effect of update and image size reduction on the
+vulnerabilities. Here, we want to mention that after update and minification process we scanned
+images only with one scanner i.e Anchore. We selected Anchore out of three scanners at random.
 
@@
 
-Figure~\ref{fig:venn} illustrates the number of vulnerabilities detected by scanners. The
+Table~\ref{sing} shows the number of vulnerabilities present in Singularity images whereas 
+Figure~\ref{fig:venn} illustrates the number of vulnerabilities in Docker images, which are detected by the three scanners. The
 overlapping regions of the Venn diagram show the number of common vulnerabilities detected by either two or
@@
 vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine.
+Figure~\ref{sing}
 \begin{table*}
@@
 According to our investigation of these results, below are some of the reasons for
-getting different results from these scanners. These reasons include bugs in scanners,
-some scanners ignoring vulnerabilities in a Linux-Kernel header packages, referring to different databases,
-how frequently they are updating their databases, etc.
+getting different results from these scanners. At the time of writing, these reasons include bugs in scanners,
+some scanners ignoring vulnerabilities in Linux-Kernel header packages, scanners referring to different databases,
+and how frequently they are updating their databases, etc.
 
@@
 \textbf{Linux-Kernel-Headers:} Clair Scanner and Vuls are ignoring all vulnerabilities in the Linux-kernel-headers,
-whereas Anchore reports them.
+whereas Anchore reports them all.
 4443 out of 4453 vulnerabilities that are only reported by Anchore are present in Linux-kernel-headers.
@@
 return type.
-The actual source code of these functions is present in the Linux kernel and not inside the image.
+The actual source code of these functions is present in the Linux kernel and is not inside the image.
 So, vulnerability detection in header files
@@
 
-\textbf{CVEs with Status as “Not-affected”:} Vuls is reporting vulnerabilities with status
-as "not-affected". So it means Linux distribution which is inside the image is not affected
+\textbf{CVEs with Status as “Not-affected”:} Vuls is reporting vulnerabilities that have status
+as "not-affected" in the vulnerability database. So it means Linux distribution which is inside the image is not affected
 by the particular CVE. However, it is reported by Vuls. In other words, we can say that
@@
 in the package Cups. However, if we check the vulnerability database, package Cups in Trusty is not
-is not affected by this CVE.
+affected by this CVE.
 
-\textbf{With CVE status as "Ignored (reached end-of-life)":}
-Some vulnerabilities are "ignored" in Ubuntu 14.04 LTS as it reached end-of-life. 
+\textbf{CVEs with status as "Ignored (reached end-of-life)":}
+Some vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life. 
 However, in Ubuntu 14.04 ESM release these vulnerabilities may or may not be present.
@@
 		detected by Anchore due to the presence of epoch in the Procps package version.
+		We reported this bug to the team through the slack channel.
 
-\textbf{With CVE status as "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
+\textbf{CVEs with status "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
 		which it is not able to detect some vulnerabilities. Due to this bug, Anchore does not detect 
 		vulnerabilities that have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
-		But if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
+		However, if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
 		For example CVE-2019-13565 in Ubuntu 14.04.
@@
 \textbf{False Negatives by Vuls:} Vuls is missing some of the vulnerabilities that it should detect. 
-		For example CVE-2019-5094
+		For example CVE-2019-5094 vulnerability.
 
@@
       \end{figure*}
+
 \subsection{Effect Of Update}
-\begin{comment}
-The next experiment involves updating all these images and then rescanning them to see how the number of
-vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
-present in our Github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
-{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
-will find the package manager inside the image and then update the image according to the package manager it finds.
-\end{comment}
+%\begin{comment}
+%The next experiment involves updating all these images and then rescanning them to see how the number of
+%vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
+%present in our Github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
+%{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
+%will find the package manager inside the image and then update the image according to the package manager it finds.
+%\end{comment}
 
-When the images are rescanned after the update, results changed drastically. However, there are still
+As the effect of update,
+scanning results changed drastically. However, there are still
 vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
 to date.
-\begin{comment}
-There are only two
-options, either you accept those vulnerabilities and use that image, or you discard that image.
-So one thing is clear here that even if we keep our images up to date there will be still some
-vulnerabilities that we have to face.
-\end{comment}
+%\begin{comment}
+%There are only two
+%options, either you accept those vulnerabilities and use that image, or you discard that image.
+%So one thing is clear here that even if we keep our images up to date there will be still some
+%vulnerabilities that we have to face.
+%\end{comment}
 Figure~\ref{fig:graph2} represents the number of vulnerabilities that are detected by Anchore before and after 
 the update of these images. 
-After the update, the vulnerabilities mostly have \textit{Low, Negligible or Medium} severity status.
-Also, after the update, the number of vulnerabilities have a mild slope meaning that there
-are a fixed set of packages that contain vulnerabilities and have no fix yet.
+%In fact, this figure depicts an additional results of update to the original Figure~\ref{fig:graph1}.
+In fact, this image combines original results of Figure~\ref{fig:graph1} with the results of update.
+Clearly, the figure illustrates that after the update, the number of vulnerabilities reduces by a
+significant number. Furthermore, a mild slope of vulnerabilities after the update shows that
+there is a set of packages that contain vulnerabilities and have no fix yet. Also, these
+vulnerabilities mostly have \textit{Low, Negligible, or Medium} severity status meaning that
+critical vulnerability are patched with high priority.
+Besides that, it is also interesting to note that some images in the Figure~\ref{fig:graph2}
+do not have update results. This is because some Linux distributions reached end-of-life and
+are not getting updates anymore.
+
+%After the update, the vulnerabilities mostly have \textit{Low, Negligible or Medium} severity status.
+%Also, after the update, the number of vulnerabilities have a mild slope meaning that there
+%are a fixed set of packages that contain vulnerabilities and have no fix yet.
 %\begin{figure*}[h]
@@
 
+\begin{figure}[H]
+        \fbox{{\includegraphics[scale=2.5,width=\columnwidth]
+        {Figures/graphwithdeletedpackages.pdf}}}
+	\caption{\label{deleted}\#Deleted Packages vs \#Reduced Vulnerabilities}
+\end{figure}
+
 \subsection{Effect Of Size Reduction}
 
-Our third experiment shows deleting unnecessary packages from the image also helps to reduce
-the number of vulnerabilities by a significant number. We started this experiment with
-\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
-to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
-to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
-from 353 to 101.
+Our third experiment involves deleting unnecessary packages from the images.
+We did this experiment only on five images because reduction process takes a
+while. We selected these five images at random. We noticed that
+after the size reduction process, the scanning results deviate a little from our initial belief.
+At first, we thought that we will have notable effect of size reduction on
+vulnerabilities. However, this is not the case always. The bar graph shown in
+the Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
+\textit{poldracklab/fmriprep:1.2.3} have insignificant effect of size reduction.
+According to our analyzes here, this can be due to two reasons: \rom{1}) number
+of unnecessary packages that we deleted and \rom{2}) type of packages that we deleted. In other
+words, if we delete a low number of packages then vulnerabilities do not get decreased as expected.
+In contrast, if the number of deleted packages are high, reduction
+in vulnerabilities also becomes high. For instance, we were able to delete only 21 and 25 packages for 
+\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
+reduced only by 4 and 17 respectively. Furthermore, this can be illustrated by Figure~\ref{deleted}.
+Also, if we delete packages that contain a lot of vulnerabilites, it helps in reducing
+vulnerabilities by a significant number. For instance, in case of our experiments
+deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
+by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}. 
+%Our third experiment shows that deleting unnecessary packages from the image also helps to reduce
+%the number of vulnerabilities by a significant number. We started this experiment with
+%\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
+%to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
+%to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
+%from 353 to 101.
 
@@
 Our last experiment includes updating the image and then removing unnecessary packages from it.
-Our initial thought was that it will reduce the number of vulnerabilities significantly. Howver
-we analyzed that this is not always true. It depends on which packages you are deleting and how
-many vulnerabilities they contain. In particular, if a package contains a large number of vulnerabilities
-it means deleting that package will help to reduce vulnerabilities in that image by a significant number.
-Contrary
+Figure~\ref{fig:bargraph} displays the results. 
+Our initial thought was that with the update and size reduction process together, we will be able to
+reduce vulnerabilities even more. However
+we analyzed that this is not always true. Again, it depends on which packages you are deleting and how
+many vulnerabilities they contained. To illustrate, \textit{bids/example} image in the Figure~\ref{fig:bargraph}
+shows no effect of size reduction alongwith update. It has 181 vulnerabilities for both experiments 2 and 4.
+Meaning that packages, which we deleted after updating the image, were already vulnerability free. Therefore,
+scanning results did not change.
 
@@
 
-None of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
-some are critical vulnerabilities. Yet there is not a single image scanner on which we can reply upon for
-scanning. Additionally, we cannot update all images because some OS already reached end-of-life and are
+As we noticed that none of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
+some have critical vulnerabilities as well. Yet there is not a single image scanner on which we can reply upon for
+scanning. Additionally, we cannot update all images because some OS releases, which are used inside images, 
+already reached end-of-life and are
 no longer getting updates. Futhermore, minimization of images is time consuming process. As we have to run
-the pipeline to get Reprozip trace that can take upto several hours. Also user should have proper knowledge
+the pipeline to get Reprozip trace that can take upto several hours. Also, user should have proper knowledge
 of running the pipeline because it is image specific. In addition to that, Reprozip can be only installed
-in the images having Python version 2.7.3 or greater, or 3.3 or greater. Also there is no guarantee that
+in the images having Python version 2.7.3 or greater, or 3.3 or greater. Above all, there is no guarantee that
 the commands that you ran to get Reprozip trace covered the whole program, may be it run a particular

### 2020-05-21 Scripts/deleted_packages_graph.py

@@ -16,12 +16,12 @@ plt.plot([],[])
 #print(packages)
 #ax=fig.add_axes([0,0,1,1])
 plt.figure(figsize=(20,10))
-p1=plt.scatter(packages, diff, color='r',s=150,marker='o',label='Vulnerability diff after minification')
+p1=plt.scatter(packages, diff, color='r',s=150,marker='o',label='Reduced vulnerabilities after minification')
 z = np.polyfit(packages, diff,1)
 p = np.poly1d(z)
 plt.plot(packages,p(packages),"r--")
 plt.xlabel('#Deleted Packages', fontsize=15)
-plt.ylabel('#Vulnerability diff',fontsize=15)
+plt.ylabel('#Reduced Vulnerabilities',fontsize=15)
 plt.legend(loc='upper left', bbox_to_anchor=(1.00, 1.00), shadow=True, ncol=1,labelspacing=1.2,borderpad=1.0)
 #plt.show()
 plt.savefig('graphwithdeletedpackages.pdf',bbox_inches='tight')

### 2020-05-22 Scripts/RemovalafterUpdate/to_delete.py
grammar check

@@ -1,19 +1,0 @@
-#!/usr/bin/env python
-
-
-all = None
-keep = None
-
-with open('all-packages.csv', 'r') as f:
-  all = f.readlines()
-
-with open('uniq_keep_installed.csv', 'r') as f:
-  keep = f.readlines()
-
-remove = [ p.strip() for p in all if not p in keep ]
-str3 = ' '.join(str(e) for e in remove)
-print(str3)
-print(len(remove))
-#for p in remove:
-#    print(p)
-

### 2020-05-22 Scripts/graphs/barchart.py

@@ -46,8 +46,8 @@ alpha=opacity,
 color='c',
 label='After update and minification')
 
-plt.xlabel('Images', fontweight='bold')
-plt.ylabel('#Vulnerabilities', fontweight='bold')
+plt.xlabel('Images', fontsize=15,fontweight='bold')
+plt.ylabel('#Vulnerabilities',fontsize=15, fontweight='bold')
 #plt.title('Vulnerabilities by experiments')
 plt.xticks(index + bar_width, imageID)
 plt.legend()

### 2020-05-22 Scripts/graphs/deleted_packages_graph.py

@@ -16,12 +16,11 @@ plt.plot([],[])
 #print(packages)
 #ax=fig.add_axes([0,0,1,1])
 plt.figure(figsize=(20,10))
-p1=plt.scatter(packages, diff, color='r',s=150,marker='o',label='Reduced vulnerabilities after minification')
+p1=plt.scatter(packages, diff, color='r',s=150,marker='o',label=False)
 z = np.polyfit(packages, diff,1)
 p = np.poly1d(z)
 plt.plot(packages,p(packages),"r--")
-plt.xlabel('#Deleted Packages', fontsize=15)
-plt.ylabel('#Reduced Vulnerabilities',fontsize=15)
-plt.legend(loc='upper left', bbox_to_anchor=(1.00, 1.00), shadow=True, ncol=1,labelspacing=1.2,borderpad=1.0)
-#plt.show()
+plt.xlabel('#Deleted Packages', fontsize=15,fontweight='bold')
+plt.ylabel('#Reduced Vulnerabilities',fontsize=15,fontweight='bold')
+#plt.legend(loc='upper center', bbox_to_anchor=(1.00, 1.00), shadow=True, ncol=2,labelspacing=1.2,borderpad=1.0,prop={'size': 14})
 plt.savefig('graphwithdeletedpackages.pdf',bbox_inches='tight')

### 2020-05-22 Scripts/graphs/script.py

@@ -28,7 +28,7 @@ leg._loc = 4
 leg.texts[12].set_text("CRITICAL \nVulnerabilities")
 z = np.polyfit(df['Packages'], df['Vulnerabilities'], 1)
 p = np.poly1d(z)
-plt.plot(df['Packages'],p(df['Packages']),"r--")
+plt.plot(df['Packages'],p(df['Packages']),"k--")
 #leg._labelspacing=10
 for idx,row in df.iterrows():
     x = row[3]

### 2020-05-22 Scripts/graphs/updation.py

@@ -11,6 +11,7 @@ d.head()
 df=pd.DataFrame(d)
 plt.figure(figsize=(200,20))
 plt.rcParams["axes.labelweight"] = "bold"
+plt.rcParams.update({'font.size': 15})
 colors = {'ubuntu:14.04' : '#2E37FE', 'ubuntu:16.04' : '#CAE1FF', 'ubuntu:17.04':'#5190ED','ubuntu:17.10':'#000085','ubuntu:18.04' : '#98F5FF','centos 6':'#800080','centos 7':'#b19cd9',
         'alpine:3.7.1':'#3CB371','alpine:3.8.4':'#00ff00','alpine:3.9.0':'#006400','debian:8':'#ffa500'}
 markers = {"ubuntu:14.04": "o", "ubuntu:16.04": "o",'ubuntu:17.04':'o','ubuntu:17.10':'o','ubuntu:18.04' : 'o','centos 6':'o','centos 7':'o',

### 2020-05-22 Scripts/minification/check_virtuality.py

@@ -30,4 +30,3 @@ out = open(f3,'w')
 for line in virtual:
     out.write(line)
     out.write("\n")
-

### 2020-05-22 Scripts/minification/run_repro_script.sh

@@ -1,0 +1,21 @@
+#!/bin/bash
+
+set -e
+
+
+if [ $(dpkg-query -W -f='${Status}' reprozip 2>/dev/null | grep -c "ok installed") -eq 0 ];
+then
+  apt-get update -y;
+  apt-get install python python-dev python-pip gcc libsqlite3-dev libssl-dev libffi-dev -y;
+  pip install -U reprozip;
+  if [ $(dpkg-query -W -f='${Status}' reprozip 2>/dev/null | grep -c "ok installed") -eq 0 ];
+  then
+    echo "Some problem occured: Cannot install Reprozip";
+    command || exit 1;
+  else
+    echo "Reprozip installed successfully";
+  fi
+else
+  echo "Reprozip was already installed"
+fi
+

### 2020-05-22 Scripts/minification/script.sh

@@ -1,5 +1,8 @@
 #!/bin/bash
 
+cd /scripts/
+shopt -s extglob
+rm -v !("required.csv"|"to_delete.py"|"check_virtuality.py"|"script.sh"|"run_repro_script.sh")
 apt list --installed | awk -F/ '{print $1}' | tail -n +2 > all-packages.csv
 apt-get update
 apt-get install -y debtree

### 2020-05-22 Scripts/minification/to_delete.py

@@ -10,14 +10,12 @@ with open('all-packages.csv', 'r') as f:
 with open('uniq_keep_installed.csv', 'r') as f:
   keep = f.readlines()
 
-hold = [ p.strip() for p in keep ]
-str1 = ' '.join(str(e) for e in hold)
-print("***********************************following packages should be held****************************")
-print(str1)
 remove = [ p.strip() for p in all if not p in keep ]
 str3 = ' '.join(str(e) for e in remove)
+
+with open('to_remove.txt', 'w') as f:
+      f.write(str3)
 print(str3)
 print(len(remove))
-for p in remove:
-    print(p)
-
+#for p in remove:
+#    print(p)

### 2020-05-22 Scripts/script.py

@@ -1,43 +1,0 @@
-#!/usr/bin/env python3
-
-# Import the necessary libraries
-import matplotlib.pyplot as plt
-import seaborn as sns
-import pandas as pd
-import numpy as np
-# Load the data
-d = pd.read_csv(r"../train.csv")
-d.head()
-df=pd.DataFrame(d)
-colors = {'ubuntu:14.04' : '#2E37FE', 'ubuntu:16.04' : '#CAE1FF', 'ubuntu:17.04':'#5190ED','ubuntu:17.10':'#000085','ubuntu:18.04' : '#98F5FF','centos 6':'#800080','centos 7':'#b19cd9',
-        'alpine:3.7.1':'#3CB371','alpine:3.8.4':'#00ff00','alpine:3.9.0':'#006400','debian:8':'#ffa500'}
-markers = {"ubuntu:14.04": "o", "ubuntu:16.04": "o",'ubuntu:17.04':'o','ubuntu:17.10':'o','ubuntu:18.04' : 'o','centos 6':'o','centos 7':'o',
-        "alpine:3.7.1":'o','alpine:3.8.4':"o","alpine:3.9.0":"o","debian:8":"o"}
-with sns.plotting_context(rc={"legend.fontsize":25,"font.size":18,"axes.titlesize":20,"font.weight":'heavy',"legend.labelspacing":20}):
-  p1=sns.relplot(x="Packages",y="Vulnerabilities",hue="OS distribution",size="CRITICAL Vulnerabilities",sizes=(300,800),data = df,palette=colors,markers=markers,style="OS distribution",height=10, aspect=2)
-p1.set(xlabel='#Packages', ylabel='#Vulnerabilities')
-p1.set(xticks=[i for i in range(0, max(df['Packages']) + 100, 50)],
-       yticks=[i for i in range(0, max(df['Vulnerabilities']) + 20, 250)])
-ax = p1.axes[0,0]
-leg = p1._legend
-#p1.legend(loc='center left', bbox_to_anchor=(1.25, 0.5), ncol=1)
-leg.set_bbox_to_anchor([1.01, 0.04])
-leg._loc = 4
-leg.texts[12].set_text("CRITICAL \nVulnerabilities")
-leg._labelspacing=50
-z = np.polyfit(df['Packages'], df['Vulnerabilities'], 1)
-p = np.poly1d(z)
-plt.plot(df['Packages'],p(df['Packages']),"r--")
-
[…]

### 2020-05-22 Scripts/update-images.sh

@@ -1,27 +1,0 @@
-#!/usr/bin/env bash
-
-set -ue
-
-function usage {
-	echo "$0 <image_list>"
-	exit 1
-}
-
-if [ $# -lt 1 ]
-then
-	usage
-fi
-
-for image in $*
-do
-	echo -n "Updating image ${image}... "
-	name1="$(cut -d'/' -f1 <<<"$image")"
-	name2="$(cut -d'/' -f2 <<<"$image")"
-	name="$(cut -d':' -f1 <<<"$name2")"
-	#docker run -e /bin/bash -v $PWD:$PWD -w $PWD ${image} ./update.sh &>${image}.log && echo "[ OK ]"
-        docker run -v $PWD:$PWD -w $PWD --entrypoint /bin/bash ${image} ./update.sh &>${name1}_${name}.log && echo "[ OK ]"
-        #docker run -it --entrypoint /bin/bash ${image} ./update.sh &>${image}.log && echo "[ OK ]"
-	echo -n "Commiting updated image... "
-	ID=$(docker ps -a | head -2 | awk '$1!="CONTAINER" {print $1}')
-	docker commit ${ID} updated_${name2} && echo "[ OK ]"
-done

### 2020-05-22 Scripts/update.sh

@@ -1,17 +1,0 @@
-#!/usr/bin/env bash
-
-function die {
-	echo $1
-	exit 1
-}
-
-function find-pm {
-		(type $1 &> /dev/null && echo "> Found $1") || \
-		(echo "> $1 not found" && return 1)
-}
-
-\rm -f .updated
-find-pm yum && (yum update -y && touch .updated)
-#find-pm apt && (apt update -y && apt upgrade -y && apt-get autoremove -y && apt-get autoclean -y && touch .updated)
-find-pm apt && (apt update -y && apt upgrade -y && touch .updated)
-test -f .updated || die "Cannot find package manager or update failed"

### 2020-05-22 paper.tex

@@
 \begin{keywords}
-Containers; Security; Docker; Singularity; Neuroimaging.
+Containers; Vulnerabilities; Docker; Singularity; Neuroimaging.
 \end{keywords}
@@
 
-Containers, which provide operating system (OS) level virtualization, are very
-popular. This is because they are very lightweight, flexible, resource-efficient,
+Containers, which provide an operating system (OS) level virtualization, are
+popular. This is because they are lightweight, flexible, resource-efficient,
 provide fast development cycles, continuous delivery,
@@
 
-However, two features of the Linux kernel, \textit{control groups} and \textit{namespaces},
-are used by containers to mitigate these threats to a certain extent. Security
-of containers is still most concerning issue. According to a Forrester survey~\cite{bettini2015vulnerability}
+However, two features of the Linux kernel,\textit{control groups} and \textit{namespaces},
+are used by containers to mitigate these threats to a certain extent. The security
+of containers is still the most concerning issue. According to a Forrester survey~\cite{bettini2015vulnerability}
 done in January 2015, security is the
 biggest concern while deploying containers.
-Except web applications, containers are also popularly used for scientific computing
+Besides web applications, containers are also popularly used for scientific computing
 and data science in neuroscience. In fact, Singularity was developed for scientific applications
-by keeping focus on HPC environments. This popularity of containers lead us to the
+by keeping the focus on HPC environments. This popularity of containers leads us to the
 primary research question of this work: \textit{what is the current security state of
@@
 To answer that question, we scan images that are used on Compute
-Canada clusters by neuroscience field. Scanning refers to the practice of
+Canada clusters by the Neuroscience field. Scanning refers to the practice of
 collecting all information about the container image, investigating it
@@
 report to summarize scanning results. It is broadly categorized into
-two types: static scanning and dynamic scanning. The former scanning technique
+two types: Static scanning and Dynamic scanning. The former scanning technique
 involves extracting information of an image without running it into a container,
@@
 Vulnerability is a weakness in the developer's software that can be exploited
-by the attacker to perform unathorized actions on the target computer.
+by the attacker to perform unauthorized actions on the target computer.
 In this paper, we report all vulnerabilities that are present in
@@
 
-\textit{RQ2:} Can we get rid of these vulnerabilities by updating the
-images?
-
-\textit{RQ3:} Can we get rid of these vulnerabilities by shrinking the
-size of the image?
-
-\textit{RQ4:} Can we get rid of these vulnerabilities by both updating
-and shrinking image size?
+\textit{RQ2:} Can these vulnerabilities be reduced by updating the images?
+
+\textit{RQ3:} Can these vulnerabilities be reduced by shrinking the size of the images?
+
+\textit{RQ4:} What is the effect of both updating
+and shrinking image size on vulnerabilities?
 
@@
 threat for the applications running on the same host. Previous studies evaluated
-security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
+the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
 and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
@@
 
-This paper is organized as follows: in next section, we provide description
-of materials and methods which summarizes our four main experiments. We also explain
+This paper is organized as follows: in the next section, we provide description
+of materials and methods which summarize our four main experiments. We also explain
 scanning tools that we use for scanning container images to report
-vulnerabilities. Next section of this paper is about the results. Here, we
-present number of vulnerabilites that are present in the container images
+vulnerabilities. The next section of this paper is about the results. Here, we
+present a number of vulnerabilities that are present in the container images
 which are used for data analysis on shared HPC clusters. Following section is about 
-discussion of these results where we provide more insight into the problems that 
+the discussion of these results where we provide more insight into the problems that 
 we faced while conducting these experiments. Finally, we conclude this paper by discussing ten simple
@@
 
-Container tools are capable of packing and running an application in an isolated environment that have
+Container tools are capable of packing and running an application in an isolated environment that has
 the application's dependencies,
-required libraries and configuration files for the
+required libraries, and configuration files for the
 application to function properly.
@@
 Docker uses a client-server architecture, where client, containers, communicate to
-the server, Docker Daemon, which is also known as Docker engine.
+the server, Docker Daemon, which is also known as the Docker engine.
 Docker Daemon is a long-running process that manages all Docker images, containers, storage volumes, and networks.
@@
 
-As Docker is not suitable for HPC systems therefore, Singularity came up with a new approach
+As Docker is not suitable for HPC systems, therefore, Singularity came up with a new approach
 of packing and running applications in containers. 
@@
 we could not get 3 images and 2 images were already included in BIDS images.
-Therefore we are left with a total 18 Boutiques images which include 6
+Therefore we are left with a total of 18 Boutiques images which include 6
 Singularity images and 12 Docker images.
@@
 \end{comment}
-So we have a total 38 Docker images from both BIDS Apps and Boutiques.
+So we have a total of 38 Docker images from both BIDS Apps and Boutiques.
 	Table~\ref{table1} displays the names of all the images that we took in our experiments.
-Table~\ref{sing} lists 6 Singularity images taken from Boutiques framework.
+Table~\ref{sing} lists 6 Singularity images taken from the Boutiques framework.
 %\begin{figure}
@@
 
-\begin{figure}[H]
+\begin{figure}
 	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
@@
 in false positives and false negatives.
-Also, if ubuntu releases with ended support are used in images, there are no chances of getting updates, hence
+Also, if ubuntu release with ended support is used in images, there are no chances of getting updates, hence
 resulting in vulnerable images.
 
-Ubuntu maintains its vulnerability database in Ubuntu launchpad or Ubuntu CVE tracker. For a given CVE, there is an entry for all ubuntu releases.
+Ubuntu maintains its vulnerability database in the Ubuntu Launchpad or the Ubuntu CVE Tracker. For a given CVE, there is an entry for all ubuntu releases.
 Ubuntu releases are listed with the package name
@@
 		  published. The package version that contains the fix is also
-		  alongwith the status.
+		  along with the status.
 
@@
 		The fixed version of such packages is appended by
-		+esmN or /~esmN, indicating that this package version is available
+		+esmN or \char`\~esm, indicating that this package version is available
 		only via ESM.
@@
 findings of other scientists.
+
 \subsection{Image size Reduction process}
-If we want to reduce number of vulnerabilities without effecting the reproducibility of the image,
-image size reduction process is a good choice. In this process we reduce the number of packages
+If we want to reduce the number of vulnerabilities without effecting the reproducibility of the image,
+image size reduction process is a good choice. In this process, we reduce the number of packages
 installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
-out which packages we need for the pipeline to fucntion properly. Here, we used 
+out which packages we need for the pipeline to function properly. Here, we used 
 Reprozip~\cite{rampin2016reprozip}. It is a tool that
@@
 application while execution and then based on that it recognizes binaries, files, environment variables,
-and library dependencies that will be used by the application for future reexecution. If the OS is
-Debian or RPM based, Reprozip also
-uses available package manager to acquire a list of distribution packages from where these files come from.
+and library dependencies that will be used by the application for future re-execution. If the OS is
+Debian or RPM-based, Reprozip also
+uses an available package manager to acquire a list of distribution packages from where these files come from.
 So, we got a list of packages from Reprozip that are needed for the application execution. 
@@
 
-Our final experiment involves combination of both update and size reduction process
+Our final experiment involves a combination of both update and size reduction process
 to lessen the number of vulnerabilities.
@@
 In this section,
-we first discuss the existing vulnerabilities in the images and compare
+we first discuss the existing vulnerabilities in the images and compare the
 results of the three scanners. Then we discuss the effect of the update on the
@@
 process. Lastly, this section presents the combined effect of update and image size reduction on the
-vulnerabilities. Here, we want to mention that after update and minification process we scanned
+vulnerabilities. Here, we want to mention that after the update and minification process we scanned
 images only with one scanner i.e Anchore. We selected Anchore out of three scanners at random.
@@
 The figure also infers that Alpine distribution, being the
-lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains highest number of
+lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains the highest number of
 vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine.
-Figure~\ref{sing}
+Similarly, Figure~\ref{sing} illustrates the number of vulnerabilities in Singularity images used in Boutiques images.
 \begin{table*}
@@
 %\end{comment}
-\begin{figure}[H]
+\begin{figure}
         {\includegraphics[scale=2.5,width=\columnwidth]
@@
 
-\begin{figure*}
+\begin{figure*}[t]
 	{\includegraphics[scale=1.5,width=\textwidth]
@@
 
+\begin{figure*}[b]
+        {\includegraphics[width=\textwidth]
+        {Figures/vulnwithupdate.pdf}}
+        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and
+        after update of the images}
+      \end{figure*}
+
 \subsection{Comparisons between Scanners}
@@
 The number and type of vulnerabilities reported by the three scanners are drastically different from each other.
-It was interesting to investigate the reasons of these differences.
+It was interesting to investigate the reasons for these differences.
 %these scanners report different numbers and types of vulnerabilities.
@@
 
+\begin{figure*}[b]
+        {\includegraphics[scale=1.5,width=\textwidth]
+        {Figures/bargraph.png}}
+        \caption{\label{fig:bargraph} Bar graph representing \#Vulnerabilities by different experiments}
+      \end{figure*}
 \textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
 are not detected by Clair Scanner but they affect Ubuntu 14.04 LTS hence detected by Vuls. For example, CVE-2017-1375.
-\begin{figure*}[b]
-        {\includegraphics[width=\textwidth]
-        {Figures/vulnwithupdate.pdf}}
-        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and
-        after update of the images}
-      \end{figure*}
 
@@
 		was published on 2019-09-24, was not 
-		updated in Clair Scanner's database that time. Due to which it is missed by Clair Scanner.
+		updated in Clair Scanner's database at that time. Due to which it is missed by Clair Scanner.
 
@@
 	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753.
-
-\begin{figure*}[b]
-        {\includegraphics[scale=1.5,width=\textwidth]
-        {Figures/bargraph.png}}
-        \caption{\label{fig:bargraph} Bar graph representing \#Vulnerabilities by different experiments}
-      \end{figure*}
 
@@
 %In fact, this figure depicts an additional results of update to the original Figure~\ref{fig:graph1}.
-In fact, this image combines original results of Figure~\ref{fig:graph1} with the results of update.
+In fact, this image combines the original results of Figure~\ref{fig:graph1} with the results of the update
+experiment.
 Clearly, the figure illustrates that after the update, the number of vulnerabilities reduces by a
@@
 vulnerabilities mostly have \textit{Low, Negligible, or Medium} severity status meaning that
-critical vulnerability are patched with high priority.
-Besides that, it is also interesting to note that some images in the Figure~\ref{fig:graph2}
+critical vulnerabilities are patched with high priority.
+Besides that, it is also interesting to note that some images in Figure~\ref{fig:graph2}
 do not have update results. This is because some Linux distributions reached end-of-life and
@@
 
-\begin{figure}[H]
-        \fbox{{\includegraphics[scale=2.5,width=\columnwidth]
-        {Figures/graphwithdeletedpackages.pdf}}}
+\begin{figure*}
+        {\includegraphics[scale=1.5,width=\textwidth]
+        {Figures/graphwithdeletedpackages.pdf}}
 	\caption{\label{deleted}\#Deleted Packages vs \#Reduced Vulnerabilities}
-\end{figure}
+\end{figure*}
 
@@
 Our third experiment involves deleting unnecessary packages from the images.
-We did this experiment only on five images because reduction process takes a
+We did this experiment only on five images because the reduction process takes a
 while. We selected these five images at random. We noticed that
 after the size reduction process, the scanning results deviate a little from our initial belief.
-At first, we thought that we will have notable effect of size reduction on
+At first, we thought that we will have a notable effect of size reduction on
 vulnerabilities. However, this is not the case always. The bar graph shown in
-the Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
-\textit{poldracklab/fmriprep:1.2.3} have insignificant effect of size reduction.
-According to our analyzes here, this can be due to two reasons: \rom{1}) number
-of unnecessary packages that we deleted and \rom{2}) type of packages that we deleted. In other
+Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
+\textit{poldracklab/fmriprep:1.2.3} have an insignificant effect of size reduction.
+According to our analyzes here, this can be due to two reasons: \rom{1}) the number
+and \rom{2}) the kind of packages that we deleted. In other
 words, if we delete a low number of packages then vulnerabilities do not get decreased as expected.
@@
 \textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
-reduced only by 4 and 17 respectively. Furthermore, this can be illustrated by Figure~\ref{deleted}.
-Also, if we delete packages that contain a lot of vulnerabilites, it helps in reducing
+reduced only by 4 and 17 respectively. Furthermore, this is illustrated in Figure~\ref{deleted}.
+Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
 vulnerabilities by a significant number. For instance, in case of our experiments
@@
 we analyzed that this is not always true. Again, it depends on which packages you are deleting and how
-many vulnerabilities they contained. To illustrate, \textit{bids/example} image in the Figure~\ref{fig:bargraph}
-shows no effect of size reduction alongwith update. It has 181 vulnerabilities for both experiments 2 and 4.
+many vulnerabilities they contained. To illustrate, \textit{bids/example} image in Figure~\ref{fig:bargraph}
+shows no effect of size reduction along with update process. It has 181 vulnerabilities for both experiments 2 and 4.
 Meaning that packages, which we deleted after updating the image, were already vulnerability free. Therefore,
@@
 As we noticed that none of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
-some have critical vulnerabilities as well. Yet there is not a single image scanner on which we can reply upon for
+some have critical vulnerabilities as well. Yet there is not a single image scanner on which we can rely upon for
 scanning. Additionally, we cannot update all images because some OS releases, which are used inside images, 
 already reached end-of-life and are
-no longer getting updates. Futhermore, minimization of images is time consuming process. As we have to run
-the pipeline to get Reprozip trace that can take upto several hours. Also, user should have proper knowledge
+no longer getting updates. Furthermore, the minimization of images is a time consuming process. As we have to run
+the pipeline to get Reprozip trace that can take up to several hours. Also, the user should have proper knowledge
 of running the pipeline because it is image specific. In addition to that, Reprozip can be only installed
 in the images having Python version 2.7.3 or greater, or 3.3 or greater. Above all, there is no guarantee that
-the commands that you ran to get Reprozip trace covered the whole program, may be it run a particular
+the commands that you ran to get Reprozip trace covered the whole program, maybe it runs a particular
 branch of the program. So there should be some kind of coverage measurement.
@@
 vulnerabilities there are no fixes available yet so the images cannot 
-be made totally invulnerable. Continuing with our next experiment of minification, we thought that
-it will decrease vulnerabilities by a significant number. However, we found out that this is not
-the case always.
+be made totally invulnerable. Continuing with our next two experiments, we analyzed that the
+image size reduction process also reduces vulnerabilities a lot. However, we found out that this is not
+always true. It depends on two factors: kind and the number of packages that we are
+deleting. Therefore, we conclude this paper by suggesting ten simple rules that can be
+followed to keep container images safe.
+\newline 1. Update packages regularly.
+\newline 2. Remove unnecessary packages.
+\newline 3. Mind your base OS image.
+\newline 4. Run image scanning tools in CI scripts. For instance Anchore.
+\newline 5. Mind your GitHub/DockerHub credentials.
+\newline 6. Minimize dependencies.
+\newline 7. Avoid static linking because it obfuscates vulnerability scanning.
+\newline 8. Use the package manager to facilitate vulnerability detection.
+\newline 9. Use OS releases that have LTS support.
+\newline 10. Sign your images.
 

### 2020-05-22 paper.tex
Some comments

@@
 \newcommand{\rom}[1]{\lowercase\expandafter{\romannumeral #1\relax}}
-\newcommand{\TG}[1]{\color{blue}From Tristan: #1\color{black}}
+\newcommand{\tristan}[1]{\color{blue}From Tristan: #1\color{black}}
 
@@
 
+\tristan{The above text contains true statements, but they are not organized 
+to introduce the paper correctly. It should be rewritten according to the following logic:
+\begin{itemize}
+	\item Containers are popular in various scientific fields, in particular to run Big Data analyses on HPC clusters.
+Mention that neuroimaging is our particular focus, although this work is of general interest.
+	\item However, deploying container images on clusters raises security issues. Some security issues that could possibly lead to privilege escalation, DoS or information leak. Some
+	security issues are related to the architecture of container systems (Docker) but have been largely solved by Singularity.
+	\item Here we are interested in image vulnerabilities [explain research questions as you did]
+	\item [introduce paper outline as done]
+\end{itemize}}
+
 \textit{RQ1:} Are vulnerabilities present inside container images that are
@@
 Lastly, our fourth experiment involves both updating and shrinking the image size and then
-rescanning for the vulnerabilities.
+rescanning for the vulnerabilities. \tristan{Content of this paragraph is fine, but writing is very convoluted.}
 
@@
 \subsection{Container Tools}
+
+\tristan{This sub-section has a lot of boilerplate material. It should be summarized.}
 
@@
 %\end{comment}
-\subsection{Application frameworks}
-
-We used containerized applications available in the Boutiques and BIDS Apps
-frameworks used in neuroscience to run analyses on HPC clusters.
-
-\subsubsection{Brain Imaging Data Structure (BIDS) Apps}
-
-BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
-analysis pipelines. It improves usability, accesibility, and reproducibility
-of different applications through containerization.
-At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
-Out of these 27 images, we used 26 images for our experiments because one of them was not available
-on the Docker hub.
-
-\subsubsection{Boutiques}
-
-Boutiques~\cite{glatard2018boutiques} is an application sharing system to
-publish, integrate, and execute command-line applications across different
-platforms. In Boutiques, the command-line of the application is described
-through a flexible JSON descriptor pointing to a Docker or a Singularity
-image where the application is installed. A set of core tools help
-construct, validate, publish, and execute Boutiques descriptors. Boutiques
-applications are published on the Zenodo research repository.
-
-We used 49 Boutiques applications published on Zenodo at the time of
-the writing. These applications use 23 different container images. Out of these images,
-we could not get 3 images and 2 images were already included in BIDS images.
-Therefore we are left with a total of 18 Boutiques images which include 6
-Singularity images and 12 Docker images.
-
-\begin{comment}
-\subsubsection{Brain Imaging Data Structure (BIDS) Apps}
-
-BIDS apps~\cite{gorgolewski2017bids} is a framework designed to share and execute neuroimaging
-analysis pipelines. It improves usability, accesibility, and reproducibility
-of different applications through containerization.
-At the time of this study, there were 27 BIDS apps available and all are using different Docker images.
-Out of these 27 images, we used 26 images for our experiments because the QAP bids app was not available
-on Docker hub.
-\end{comment}
-So we have a total of 38 Docker images from both BIDS Apps and Boutiques.
-	Table~\ref{table1} displays the names of all the images that we took in our experiments.
-Table~\ref{sing} lists 6 Singularity images taken from the Boutiques framework.
+\subsection{Container images}
+
+We scanned a total of 44 container images taken from the BIDS
+apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}
+frameworks, two containerization frameworks used in neuroscience to share
+and re-use applications. Among the 27 BIDS apps available at the time of
+the study \tristan{mention link where the apps are listed}, we studied 26
+unique Docker images as one wasn't available on DockerHub. Among the 49
+Boutiques applications available at the time of the study, listed using
+Boutiques \texttt{bosh search} command, 23 unique container images were
+listed including 3 that couldn't be retrieved and 2 that were already
+included in BIDS apps. The resulting 18 images included 12 Docker images
+and 6 Singularity images.
+\tristan{I rewrote this paragraph to focus it on the information of relevance for the reader. 
+You could take it as an example for other sections of the paper.}
+
 %\begin{figure}
@@
 
-\subsection{Scanning Images}
-
-Scanning an image means looking into the image, collecting all the information about the image, and
-finally, using this information to detect vulnerabilities present inside the image.
-Scanning can be broadly categorized into two types: \rom{1}) Static Scanning and \rom{2})
-Dynamic Scanning.
-In Static scanning, an image is scanned without running it into a container. In respect to that,
-different image features are extracted like installed packages, their versions, files, etc. to list
-the vulnerabilities present inside the image.
-On the other hand, Dynamic scanning involves running a container from the image and then scanning the
-dynamic behavior of the image.
+\subsection{Image Scanners}
+
+Container image scanners can be broadly categorized into static and dynamic
+scanners. In static scanning, the image vulnerabilities are extracted from
+file and package lists \tristan{Does it really look into files, or only installed packages? Please check. The difference is important 
+when software is installed without using the package manager.}, without deploying the image in a container. In
+dynamic scanning however, a container is started from the image and
+\tristan{... It is still unclear how dynamic scanning works. Your text
+mentions ``running a container from the image and then scanning the dynamic
+behavior of the image'' but in practice it should explain what is executed
+in the image: the package manager? other scanning tools? Please clarify by
+completing this sentence.}
 
@@
 
-We used three scanners namely Anchore~\cite{github_2019}, Vuls~\cite{future-architect_2019}, and
-Clair Scanner~\cite{arminc_2019} for scanning Docker images because these are the most
-mature scanners. Out of these scanners, only Vuls uses dynamic scanning and the remaining two
-are static scanners.
-Also, we froze vulnerability databases for these scanners on September 25, 2019, and scanned
-all images to avoid getting different results due to the differences in the scanner's database.
-Lastly, for scanning Singularity images, we used Stools.
+We used four popular image scanners, namely Anchore~\cite{github_2019},
+Vuls~\cite{future-architect_2019}, Clair Scanner~\cite{arminc_2019} and
+Stools~\cite{refneeded}. Anchore, Vuls and Clair Scanner support Docker
+images while Stools supports Singularity. Vuls is dynamic and the other
+ones are static. To avoid discrepancies, we froze the vulnerability
+databases for these scanners on September 25, 2019.
+
+\tristan{The scanner descriptions need to be streamlined.}
 
@@
 
+\tristan{Mention software not installed thorugh the package manager.}
+
 \subsection{Conclusion}

### 2020-05-22 paper.tex
Feedback 2/2

@@
 
-\tristan{The scanner descriptions need to be streamlined.}
+\tristan{The scanner descriptions need to be streamlined. They are quite verbose and not very consistent for now.}
 
@@
 
+\tristan{This section lacks a sentence to introduce context: why are you even talking about distributions? 
+You should explain that scanners report vulnerabilities differently depending on the release type. 
+Also, is there a similar scheme in CentOS? }
+
 BIDS app and Boutiques images that we took for our experiments have diverse Linux
@@
 distribution can have different releases. As images in our experiments mostly have
-Ubuntu distribution we can take this distribution as an example. In the case of Ubuntu, release
+Ubuntu distribution we can take this distribution as an example \tristan{of what?}. In the case of Ubuntu, release
 can be of two types: regular or LTS (Long Term Support).
@@
 
+\tristan{since the next 3 sections are rather short, I would group them all 
+as paragraphs under the same sub-section.}
+
 If there exist vulnerabilities in the container image, then we can
@@
 image. Updating the image involves updating all software packages that are
-inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github}) 
+inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github} \tristan{link should point to the actual script, not the repo}) 
 to update all images, which checks the
@@
 Ultimately, we kept these packages and removed remaining unnecessary packages. We used a bash script
-(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github}) for
+(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github} \tristan{Link is broken}) for
 the image size reduction process which installs Reprozip in the image, collects Reprozip trace, and
 finally deletes unnecessary packages.
+
+\tristan{You should explain why you didn't use Neurodocker as it's the obvious way to do this.}
 
@@
 we used for earlier experiments.
+
+\tristan{This could go to the first sentences of the new sub-section, no need for a subsection for that.}
 
@@
 vulnerabilities. Here, we want to mention that after the update and minification process we scanned
-images only with one scanner i.e Anchore. We selected Anchore out of three scanners at random.
+images only with one scanner i.e Anchore. We selected Anchore out of three scanners at random \tristan{Probably not really at random... 
+No need to mention anything if it was completely arbitrary. You should mention that just in the experiments themselves, it's giving this comment too much importance to put it here.}.
 
@@
 
-Table~\ref{sing} shows the number of vulnerabilities present in Singularity images whereas 
-Figure~\ref{fig:venn} illustrates the number of vulnerabilities in Docker images, which are detected by the three scanners. The
+Table~\ref{sing} shows the number of vulnerabilities present in Singularity
+images whereas Figure~\ref{fig:venn} illustrates the number of
+vulnerabilities in Docker images, which are detected by the three scanners.
+\tristan{You should refer to tables in the order they are presented (1
+first, then 2). Tables should also be located next to their reference. In
+this case I would actually create a single table, greying out cells that
+aren't pertinent (Anchore, Vuls and Clair for Singularity images.)}
+ The
 overlapping regions of the Venn diagram show the number of common vulnerabilities detected by either two or
 three scanners. In total 10691 vulnerabilities are detected by three scanners.
-There are also vulnerabilities that are detected only by one scanner.
+There are also vulnerabilities that are detected only by one scanner. \tristan{The last 3 sentences bring absolutely no 
+extra information that can't be read on the figure directly. You should replace them with only 1 sentence noting that there 
+are important discrepancies between scanner results (maybe quantify that with a Dice or Jaccard coefficient). This is an example 
+of how writing should be improved throughout the paper.}
 
@@
 The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
-also get increased.
+also get increased \tristan{mention the parameters of the regression line (preferably as a label in the figure) and the regression error}.
 The figure also infers that Alpine distribution, being the
 lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains the highest number of
-vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine.
-Similarly, Figure~\ref{sing} illustrates the number of vulnerabilities in Singularity images used in Boutiques images.
+vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine \tristan{I dont think there is enough data to 
+claim that, claim should be softened.}.
+Similarly, Figure~\ref{sing} \tristan{there is a reference error, and if it's still a different figure I think you should make only 1.} illustrates the number of vulnerabilities in Singularity images used in Boutiques images.
+\tristan{In the Figure, could you increase the marker size in the caption, and order it so that the different versions of a distribution 
+are grouped together and sorted by increasing version?}
 \begin{table*}
@@
 Table~\ref{table1} compares the results of scanning images with the three scanners.
-Venn Diagram in Figure~\ref{fig:venn} summarizes this table.
+Venn Diagram in Figure~\ref{fig:venn} summarizes this table. \tristan{You said it already.}
 
@@
 as "not-affected" in the vulnerability database. So it means Linux distribution which is inside the image is not affected
-by the particular CVE. However, it is reported by Vuls. In other words, we can say that
-these are false positives by Vuls.
+by the particular CVE. However, it is reported by Vuls \tristan{do you mean Anchore? This sounds circular.}. In other words, we can say that
+these are false positives \tristan{the use of ``false positives'' is ambiguous} by Vuls.
 For example, we scanned an image having the Trusty release in it and Vuls is reporting CVE-2015-2305
@@
 \textbf{False negatives by Clair:} Clair is missing vulnerabilities that it should detect. For example, CVE-2016-9082 
-is present in package Cairo in Xenial release and it is not detected by Clair.
+is present in package Cairo in Xenial release and it is not detected by Clair. \tristan{You should report the version of Clair in 
+the methods. If you reported this bug to the developers, you should say so and link it here (same comment for all the bugs).}
 
@@
 We did this experiment only on five images because the reduction process takes a
-while. We selected these five images at random. We noticed that
-after the size reduction process, the scanning results deviate a little from our initial belief.
+while \tristan{This is not a good argument, it is vague, and it is not complete. Size reduction also requires 
+to run a pipeline in the image.}. We selected these five images at random \tristan{really? I don't think so.}. We noticed that
+after the size reduction process, the scanning results deviate a little from our initial belief \tristan{what do you mean?}.
 At first, we thought that we will have a notable effect of size reduction on
@@
 \textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
-reduced only by 4 and 17 respectively. Furthermore, this is illustrated in Figure~\ref{deleted}.
+reduced only by 4 and 17 respectively. Furthermore, this is illustrated in Figure~\ref{deleted} \tristan{I'm not thrilled by this figure, I would 
+just mention in the text that we verified that.}.
+\tristan{The next sentence is interesting because it starts characterizing the images that benefit the most 
+from size reduction. The previous sentences read like a tautology, you should make your comment more specific.} 
 Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
@@
 
-\subsection{Effect Of Update and Size Reduction}
+\subsection{Combined Effect Of Update and Size Reduction}
 
@@
 reduce vulnerabilities even more. However
-we analyzed that this is not always true. Again, it depends on which packages you are deleting and how
+we analyzed that this is not always true. Again, it depends on which packages you \tristan{in general don't use ``you'' in a 
+formal paper.} are deleting and how
 many vulnerabilities they contained. To illustrate, \textit{bids/example} image in Figure~\ref{fig:bargraph}
@@
 branch of the program. So there should be some kind of coverage measurement.
+
+\tristan{You should comment on the important number of vulnerabilities found in the images overall.}
 
@@
 \newline 1. Update packages regularly.
-\newline 2. Remove unnecessary packages.
+\newline 2. Remove unnecessary packages, in particular the ones used for installation (compilers, source packages, etc).
 \newline 3. Mind your base OS image.
@@
 
+\tristan{You should discuss future work here too.}
+
 \bibliography{bibliography}

### 2020-05-28 paper.tex
corrected comments 1

@@
 \newcommand{\todo}[1]{\color{red}\textbf{TODO:}#1\color{black}}
-\newcommand{\note}[2]{\color{blue}Note: #1\color{black}}
+\newcommand{\change}[2]{\color{cyan}Changes: #1\color{black}}
 \newcommand{\reprozip}[0]{ReproZip}
@@
 They also share three main security threats with other virtualization
-techniques~\cite{gantikow2016providing}.
+techniques~\cite{gantikow2016providing}:
 
@@
 
-However, two features of the Linux kernel,\textit{control groups} and \textit{namespaces},
+However, two features of the Linux kernel, \textit{control groups} and \textit{namespaces},
 are used by containers to mitigate these threats to a certain extent. The security
@@
 primary research question of this work: \textit{what is the current security state of
-container images that are deployed on HPC clusters?}.
+container images that are deployed on HPC clusters?}
 
@@
 by the attacker to perform unauthorized actions on the target computer.
-In this paper, we report all vulnerabilities that are present in
+In this paper, we report vulnerabilities that are present in
 container images, specifically used by neuroimaging field. Particularly,
@@
 containers.
-This focus is justified by the fact that, containers expose the host's resources
+This focus is justified by the fact that containers expose the host's resources
 (e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
@@
 and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
-Also Singularity came up with Stools, which can be used for scanning Singularity images
+Also, Singularity came up with Stools \href{https://github.com/singularityhub/stools}{(https://github.com/singularityhub/stools)}, which can be used for scanning Singularity images
 for security and quality checks.
@@
 scanning tools that we use for scanning container images to report
-vulnerabilities. The next section of this paper is about the results. Here, we
-present a number of vulnerabilities that are present in the container images
-which are used for data analysis on shared HPC clusters. Following section is about 
-the discussion of these results where we provide more insight into the problems that 
-we faced while conducting these experiments. Finally, we conclude this paper by discussing ten simple
-rules that can be followed to secure container images for use in clusters.
+vulnerabilities. The next section of this paper provides the results, where we
+present a number of existing vulnerabilities in the container images
+used for data analysis on shared HPC clusters. We then proceed in the following section with 
+discussion and analysis of these results, where we provide more insight into the problems that 
+we faced while conducting these experiments. Finally, we conclude this paper by proposing some
+particular rules that can be followed to secure container images for use in clusters.
 
@@
 
-This study involves four image scanning experiments.
-The first experiment scans the images as is to report the existing vulnerabilities
-inside the images. The scan report of
-these images shows a large number of existing vulnerabilities which may pose
-a potential security risk. These vulnerabilities exist due to the outdated
-packages that are present inside the images. So, the next step is to
-take the necessary steps to improve security in the images. Therefore, there exist
-two possible solutions.
-The first one involves updating
-all these images and then rescanning them, which constitutes the second experiment of our study. The next 
-experiment involves shrinking the size of the image
-meaning that removing all unnecessary packages from the image to see the effect on the number of
-vulnerabilities present inside the image, which will be presented as our third experiment.
-Lastly, our fourth experiment involves both updating and shrinking the image size and then
-rescanning for the vulnerabilities. \tristan{Content of this paragraph is fine, but writing is very convoluted.}
-
-Here, we first
+\change{This study involves several image scanning experiments. To begin with,
+we scan the images as is to report the existing vulnerabilities
+inside the images. Updating these images is likely to play a role in vulnerabilities. Therefore, we
+update the images and then rescan all these
+images.
+Subsequently, we shrink the size of the images
+meaning that remove unnecessary packages from the images to see the effect on the number of
+vulnerabilities in the images.
+Lastly, we update and shrink the image size together and then
+rescan for the vulnerabilities.
+
+In this section, we first
 introduce two container tools used in our experiments: Docker and
-Singularity and their image formats. Then we describe Boutiques and BIDS application frameworks
-from where we took containerized applications for our study. 
-Later, this section
-presents two scanning techniques followed by a description of image scanners used.
-In this study, we used three different image scanners because they
-use different scanning techniques and/or refer to different vulnerability sources.
-The images used in our study have different Linux distributions/releases, which have
-different vulnerability data. Therefore, in the last, this section presents a
+Singularity and their image formats. Then we provide more insight
+into the container images and the image scanners that we used in our study.
+The image scanners are going to report different results due to different Linux
+distributions/releases, which have different vulnerability data. Therefore, in the last, this section presents a
 description of these varying Linux distributions/releases and their
-vulnerability databases.
+vulnerability databases.}
 
@@
 frameworks, two containerization frameworks used in neuroscience to share
-and re-use applications. Among the 27 BIDS apps available at the time of
-the study \tristan{mention link where the apps are listed}, we studied 26
+and re-use applications. Among the 27 BIDS apps \href{https://bids-apps.neuroimaging.io/apps/}
+{(https://bids-apps.neuroimaging.io/apps/)} available at the time of
+the study, we studied 26
 unique Docker images as one wasn't available on DockerHub. Among the 49
@@
 Vuls~\cite{future-architect_2019}, Clair Scanner~\cite{arminc_2019} and
-Stools~\cite{refneeded}. Anchore, Vuls and Clair Scanner support Docker
-images while Stools supports Singularity. Vuls is dynamic and the other
-ones are static. To avoid discrepancies, we froze the vulnerability
+Stools~\cite{stools}. Anchore, Vuls and Clair Scanner support Docker
+images while Stools supports Singularity. Vuls is a dynamic scanner, while the others
+are static scanners. To avoid discrepancies, we froze the vulnerability
 databases for these scanners on September 25, 2019.
@@
 packages, non-OS packages (Python, Java, Gem, and Npm), and files.
-\begin{comment}
-Anchore is a set of tools, which users can
-employ for scanning container images and applying custom policies to them.
-It provides visibility and transparency of the container environment.
-\end{comment}
+%\begin{comment}
+%Anchore is a set of tools, which users can
+%employ for scanning container images and applying custom policies to them.
+%It provides visibility and transparency of the container environment.
+%\end{comment}
 Anchore Engine can be used in two ways: through Docker image or Anchore
 Command Line Interface (CLI).
-\begin{comment}
-Anchore offers services in two ways: Anchore Engine and Anchore
-Command Line Interface (CLI). Anchore Engine is available as a Docker
-image, which is available on Docker Hub. Anchore Engine CLI provides
-command line interface in addition to Anchore Engine REST API. 
-\end{comment}
+%\begin{comment}
+%Anchore offers services in two ways: Anchore Engine and Anchore
+%Command Line Interface (CLI). Anchore Engine is available as a Docker
+%image, which is available on Docker Hub. Anchore Engine CLI provides
+%command line interface in addition to Anchore Engine REST API. 
+%\end{comment}
 It can be
@@
 Anchore compares package versions, which are present inside the
-image, with the vulnerability database to flag vulnerabilities.
+image, with the vulnerability database in order to flag vulnerabilities.
 To get a vulnerability feed of various OS distribution, Anchore refers to
@@
 detect processes that are updated but not yet restarted because if they are not
-restarted, updates are not effective. So fast root scan also detects these
+restarted, updates are not effective. Fast root scan also detects these
 processes. Both fast scan and fast root scan are performed offline without Internet
@@
 
-In our experiments, we used Vuls Docker image having version v0.9.0 with fast scan mode.
+In our experiments, we used Vuls Docker image having version 0.9.0 with fast scan mode.
 Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
@@
 that drawback, another tool from CoreOS, Clair Scanner can be used. It scans the image, prepares the list of
-vulnerabilities, compares that list against the whitelist, and flags vulnerabilities
+vulnerabilities, compares that list against a whitelist, and flags vulnerabilities
 that are not present in the whitelist.
@@
 
-\href{https://github.com/singularityhub/stools}{Stools} combines CoreOS's Clair Scanner with Continuous Integration (CI)
+Stools combines CoreOS's Clair Scanner with Continuous Integration (CI)
 for scanning Singularity images for vulnerabilities.
@@
 However, TravisCI and CircleCI are commonly used for testing code, and these
-services also offer running containers. So Stools combined both the concepts.
+services also offer running containers. Stools combined both these concepts.
 It involves spinning a Clair Scanner container during testing and building a
@@
 distribution can have different releases. As images in our experiments mostly have
-Ubuntu distribution we can take this distribution as an example \tristan{of what?}. In the case of Ubuntu, release
-can be of two types: regular or LTS (Long Term Support).
+Ubuntu distribution, we can take this distribution as an example \tristan{of what?}. In the case of Ubuntu, release
+can be of two types: Regular or Long Term Support (LTS).
 Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
@@
 Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
-data in vulnerability databases because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
+data in vulnerability databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
 exists in LTS.
@@
 The images in our experiments have Ubuntu 14.04 LTS so scanners should refer
-to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for data it may result
-in false positives and false negatives.
+to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for 
+vulnerability data, it may lead to discrepancies in results.
 Also, if ubuntu release with ended support is used in images, there are no chances of getting updates, hence
@@
 installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
-out which packages we need for the pipeline to function properly. Here, we used 
+out which packages we need for the pipeline to function properly. Here, we use
 Reprozip~\cite{rampin2016reprozip}. It is a tool that
@@
 uses an available package manager to acquire a list of distribution packages from where these files come from.
-So, we got a list of packages from Reprozip that are needed for the application execution. 
-After that, we expanded this list by adding important and required packages that are essential
-for the system to function and finally figured out all the dependencies of these packages using Debtree
+So, we get a list of packages from Reprozip that are needed for the application execution. 
+After that, we expand this list by adding important and required packages that are essential
+for the system to function and finally figure out all the dependencies of these packages using Debtree
 ~\cite{debtree}.
-Ultimately, we kept these packages and removed remaining unnecessary packages. We used a bash script
+Ultimately, we keep these packages and remove remaining unnecessary packages. We use a bash script
 (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github} \tristan{Link is broken}) for
-the image size reduction process which installs Reprozip in the image, collects Reprozip trace, and
+the image size reduction process, which installs Reprozip in the image, collects Reprozip trace, and
 finally deletes unnecessary packages.
@@
 we first discuss the existing vulnerabilities in the images and compare the
-results of the three scanners. Then we discuss the effect of the update on the
+results of the three scanners. We then discuss the effect of the update on the
 existing vulnerabilities followed by the results of the image size reduction
 process. Lastly, this section presents the combined effect of update and image size reduction on the
-vulnerabilities. Here, we want to mention that after the update and minification process we scanned
-images only with one scanner i.e Anchore. We selected Anchore out of three scanners at random \tristan{Probably not really at random... 
+vulnerabilities.
+\tristan{Probably not really at random... 
 No need to mention anything if it was completely arbitrary. You should mention that just in the experiments themselves, it's giving this comment too much importance to put it here.}.
@@
         {Figures/vennDiagram.pdf}}
-        \caption{\label{fig:venn} Venn Diagram representing different scanner results}
+        \caption{\label{fig:venn} Scanner results}
 \end{figure}
@@
 	{Figures/vulngraph.pdf}}
-        \caption{\label{fig:graph1} Scatterplot representing \#Packages and \#Vulnerabilities}
+        \caption{\label{fig:graph1} Number of vulnerabilities by packages}
       \end{figure*}
@@
         {Figures/vulnwithupdate.pdf}}
-        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and
+        \caption{\label{fig:graph2} Numner of vulnerabilities before and
         after update of the images}
@@
 According to our investigation of these results, below are some of the reasons for
-getting different results from these scanners. At the time of writing, these reasons include bugs in scanners,
+getting different results from these scanners. At the time of writing, these reasons include
 some scanners ignoring vulnerabilities in Linux-Kernel header packages, scanners referring to different databases,
-and how frequently they are updating their databases, etc.
-
-We have explained these differences below in detail
-and have provided an example with each reason to make it clear.
+how frequently they are updating their databases, and bugs in scanners, etc.
+
+We explain these differences below in detail
+and provide an example with each reason to make it clear.
 
@@
         {Figures/bargraph.png}}
-        \caption{\label{fig:bargraph} Bar graph representing \#Vulnerabilities by different experiments}
+        \caption{\label{fig:bargraph} Vulnerabilities by different experiments}
       \end{figure*}
@@
 Our third experiment involves deleting unnecessary packages from the images.
-We did this experiment only on five images because the reduction process takes a
-while \tristan{This is not a good argument, it is vague, and it is not complete. Size reduction also requires 
+We did this experiment only on five images because the reduction process takes
+several hours.\tristan{This is not a good argument, it is vague, and it is not complete. Size reduction also requires 
 to run a pipeline in the image.}. We selected these five images at random \tristan{really? I don't think so.}. We noticed that

### 2020-05-31 paper.tex
content change 1

@@
 \usepackage{graphicx}
+\usepackage{multirow}
+\usepackage{array}
 \usepackage{algorithm}
@@
 and 6 Singularity images.
-\tristan{I rewrote this paragraph to focus it on the information of relevance for the reader. 
-You could take it as an example for other sections of the paper.}
-
 %\begin{figure}
@@
 
-Container image scanners can be broadly categorized into static and dynamic
-scanners. In static scanning, the image vulnerabilities are extracted from
-file and package lists \tristan{Does it really look into files, or only installed packages? Please check. The difference is important 
+\change{Container image scanners can be broadly categorized into static and dynamic
+scanners. Static scanning performs analysis on a image without running it
+as a container. Therefore, commands cannot be executed to inquire installed packages}
+
+\tristan{Does it really look into files, or only installed packages? Please check. The difference is important 
 when software is installed without using the package manager.}, without deploying the image in a container. In
@@
 
-We performed scanning on 2019-09-25 and for our experiments, we used a Docker image that was 
-latest updated i.e with the tag 2019-09-18. So it means that Clair Scanner's database was already
-old by one week.
+\change{In our experiments, we used a Docker image (arminc/clair-local-scan:v2.0.6) for scanning
+and an another Docker image (arminc/clair-db:latest) for the vulnerability database, which was
+last updated on 2019-09-18. We performed
+scanning on 2019-09-25. So, it means that Clair Scanner's database was already
+old by one week.}
 
@@
 
-\subsection{Linux Distributions and Vulnerability Databases}
-
-\tristan{This section lacks a sentence to introduce context: why are you even talking about distributions? 
-You should explain that scanners report vulnerabilities differently depending on the release type. 
-Also, is there a similar scheme in CentOS? }
-
-BIDS app and Boutiques images that we took for our experiments have diverse Linux
+\begin{table*}
+  \caption{some table}
+	\begin{tabular}{>|{\bfseries}c| c| c| *{4}{c|}}\hline
+	  \multirow{2}{*}{\bfseries Image Labels} & 
+	  \multirow{2}{*}{\bfseries Image Names} & 
+	  \multirow{2}{*}{\bfseries OS} & 
+	  \multicolumn{4}{c|}{\bfseries Vulnerabilities} \\\cline{2-5} 
+                       & \textbf{A} & \textbf{C} & \textbf{V}  & \textbf{S} \\ \hline
+a	& bids/example	& ubuntu:14.04	& 838	& 663	& 683	& \\ \hline
+b	& bids/freesurfer	& ubuntu:14.04	& 353	& 215	& 192	& \\ \hline
+c	& bids/ndmg	& ubuntu:14.04	& 934	& 757	& 782	& \\ \hline
+d	& bids/broccoli:v1.0.0	& centos 6	& 79	& 79	& 117	& \\ \hline
+e	& bids/fibredensityandcrosssection	& ubuntu:14.04	& 1086	& 849	& 868	& \\ \hline
+f	& bids/spm	& ubuntu:14.04	& 191	& 246	& 235	& \\ \hline
+g	& poldracklab/mriqc:0.15.0	& ubuntu:16.04	& 432	& 328	& 332	& \\ \hline
+h	& bids/cpac:v1.0.1a\_22	& ubuntu:16.04	& 698	& 524	& 535	& \\ \hline
+I	& bids/hyperalignment	& ubuntu:16.04	& 1717	& 1327	& 1433	& \\ \hline
+j	& bids/mindboggle:0.0.4-1	& debian:8	& 671	& 955	& 569	& \\ \hline
+k	& bids/mrtrix3\_connectome	& ubuntu:18.04	& 275	& 157	& 158	& \\ \hline
+l	& bids/rs\_signal\_extract:0.1	& ubuntu:16.04	& 867	& 454	& 473	& \\ \hline
+m	& bids/aa:v0.2.0	& ubuntu:14.04	& 189	& 244	& 233	& \\ \hline
+n	& bids/niak	& ubuntu:16.04	& 1482	& 1366	& 1420	& \\ \hline
+o	& bids/oppni:v0.7.0-1	& ubuntu:14.04	& 913	& 698	& 723	& \\ \hline
+p	& poldracklab/fmriprep:unstable	& ubuntu:16.04	& 516	& 355	& 393	& \\ \hline
+q	& bids/brainiak-srm	& ubuntu:16.04	& 897	& 484	& 503	& \\ \hline
+r	& bids/nipypelines:0.3.0	& debian:8	& 641	& 878	& 451	& \\ \hline
+s	& bids/hcppipelines:v3.17.0-18	& debian:8	& 526	& 873	& 620	& \\ \hline
+t	& bids/magetbrain	& ubuntu:18.04	& 112	& 117	& 126	& \\ \hline
+u	& bids/tracula:v6.0.0-4	& ubuntu:14.04	& 874	& 664	& 683	& \\ \hline
+v	& bids/baracus	& ubuntu:14.04	& 172	& 238	& 216	& \\ \hline
+w	& bids/antscorticalthickness:v2.2.0-1	& ubuntu:17.04	& 289	& 27	& no oval data	& \\ \hline 
+x	& bids/dparsf:v4.3.12	& ubuntu:14.04	& 507	& 750	& 757	& \\ \hline
+y	& bids/afni\_proc	& ubuntu:17.10	& 67	& 16	& no oval data	& \\ \hline
+z	& bids/rshrf:1.0.1	& alpine:3.8.4	& 5	& 3	& 3	& \\ \hline
+aa	& bids/ndmg:v0.1.0	& ubuntu 14.04	& 934	& 758	& 782	& \\ \hline
+ab	& mcin/qeeg:latest	& centos 7	& 46	& 46	& 142	& \\ \hline
+ac	& camarasu/creaphase:0.3	& centos 7	& 54	& 54	& 186	& \\ \hline
+ad	& bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest	& centos 7	& 70	& 76	& 157	& \\ \hline
+ae	& mcin/docker-fsl:latest	& centos 7	& 75	& 75	& 201	& \\ \hline
+af	& gkiar/onevoxel:v0.3.0rc2	& alpine 3.7.1	& 5	& 2	& 2	& \\ \hline
+ag	& bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest	& centos 7	& 70	& 76	& 157	& \\ \hline 
+ah	& bt5e/ants:latest	& centos 7	& 150	& 156	& 336	& \\ \hline
+ai	& poldracklab/fmriprep:1.2.3	& ubuntu 16.04	& 591	& 441	& 447	& \\ \hline
+aj	& gkiar/dwipreproc\_fsl-5.0.11\_minified	& ubuntu 16.04	& 391	& 258	& 263	& \\ \hline
+ak	& gkiar/mask2boundary:v0.1.0	& alpine 3.9.0	& 15	& 11	& 11	& \\ \hline
+al	& mcin/ica-aroma:latest	& centos 7	& 75	& 75	& 202	& \\ \hline
+am	& c3genomics/genpipes	& 	& 	& 	& 	& 99 \\ \hline
+an	& bioinformatics-group/aqua-singularity-recipe	& 	& 	& 	& 	& 7 \\ \hline
+ao	& MontrealSergiy/BEst	& 	& 	& 	& 	& 106 \\ \hline
+ap	& shub://aces/cbrain-containers-recipes:fsl\_v6.0.1	& 	& 	& 	& 	& 206 \\ \hline
+aq	& shots47s/bids-freesurfer-6.0	& 	& 	& 	& 	& 212 \\ \hline
+ar	& shots47s/bids-fmriprep-1.2.3	& 	& 	& 	& 	& 453 \\ \hline
+  \end{tabular}
+  \end{table*}
+
+\subsection{Linux Releases and Vulnerability Databases}
+
+\change{Image scanners report vulnerabilities differently depending on the Linux release types.
+Therefore, we provide an overview of these Linux releases by taking an example. 
+BIDS app and Boutiques images in our experiments have diverse Linux
 distributions such as Ubuntu, Centos, Debian, and Alpine. Further, a particular
-distribution can have different releases. As images in our experiments mostly have
-Ubuntu distribution, we can take this distribution as an example \tristan{of what?}. In the case of Ubuntu, release
+distribution have different releases in general. Here, we take Ubuntu as an example
+to discuss different releases and their vulnerability databases. We took Ubuntu's example
+because mostly images in our experiments have this distibution.} In the case of Ubuntu, release
 can be of two types: Regular or Long Term Support (LTS).
@@
 
-Ubuntu has ended support for some releases such as 14.04 LTS,
+For instance, Ubuntu has ended support for some releases such as 14.04 LTS,
 17.04, and 17.10, which means they have reached EOL. However, Ubuntu is providing optional extended support for Ubuntu 14.04.
@@
 
-\subsection{Image Update Process}
-
-\tristan{since the next 3 sections are rather short, I would group them all 
-as paragraphs under the same sub-section.}
-
-If there exist vulnerabilities in the container image, then we can
+\subsection{Image Update and Reduction Process}
+
+\change{If there exist vulnerabilities in the container image, then we can
 run after updating the
 image. Updating the image involves updating all software packages that are
-inside that image. We used a bash script (\href{https://github.com/kaurbhupinder/Vulnerability-Analysis}{Github} \tristan{link should point to the actual script, not the repo}) 
+inside that image. We used a bash script 
+(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/update/update.sh}{Github}) 
 to update all images, which checks the
@@
 
-\subsection{Image size Reduction process}
-If we want to reduce the number of vulnerabilities without effecting the reproducibility of the image,
-image size reduction process is a good choice. In this process, we reduce the number of packages
+On the other hand, if we want to reduce the number of vulnerabilities without effecting the reproducibility of the image,
+image size reduction process is a good choice. The most obvious way of doing this is using 
+Neurodocker (\href{https://github.com/ReproNim/neurodocker}{https://github.com/ReproNim/neurodocker}).
+It traces and deletes unnecessary files.
+However, image scanners reports vulnerabilities according to the installed
+packages, whereas Neurodocker deals with the files only and list of installed packages remains same. Therefore, after
+minimization also scanners report same number of vulnerabilities.
+Hence, we need to reduce the number of packages
 installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
-out which packages we need for the pipeline to function properly. Here, we use
-Reprozip~\cite{rampin2016reprozip}. It is a tool that
+out which packages we need for the pipeline to function properly. We use
+Reprozip~\cite{rampin2016reprozip}, a tool that
 is used to make applications reproducible. It traces operating system calls used by the
@@
 ~\cite{debtree}.
-Ultimately, we keep these packages and remove remaining unnecessary packages. We use a bash script
-(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/script.sh}{Github} \tristan{Link is broken}) for
+Ultimately, we keep these packages and remove remaining unnecessary packages. We use bash scripts
+(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{Github}) for
 the image size reduction process, which installs Reprozip in the image, collects Reprozip trace, and
@@
 
-\tristan{You should explain why you didn't use Neurodocker as it's the obvious way to do this.}
-
-\subsection{Update and Size Reduction Together}
-
-Our final experiment involves a combination of both update and size reduction process
+Finally, we combine both update and size reduction process
 to lessen the number of vulnerabilities.
-So in this process we first update all the packages in the image and then deletes
-the unnecessary packages. For this process we used the same two scripts that
-we used for earlier experiments.
-
-\tristan{This could go to the first sentences of the new sub-section, no need for a subsection for that.}
+Therefore, in this process we first update all the packages in the image and then deletes
+the unnecessary packages. For this process we used the same scripts that
+we used for earlier experiments.}
 
@@
 vulnerabilities.
-\tristan{Probably not really at random... 
-No need to mention anything if it was completely arbitrary. You should mention that just in the experiments themselves, it's giving this comment too much importance to put it here.}.
 
@@
         {\includegraphics[scale=2.5,width=\columnwidth]
-        {Figures/vennDiagram.pdf}}
+        {Figures/venn.pdf}}
         \caption{\label{fig:venn} Scanner results}
@@
 \textbf{False negatives by Clair:} Clair is missing vulnerabilities that it should detect. For example, CVE-2016-9082 
-is present in package Cairo in Xenial release and it is not detected by Clair. \tristan{You should report the version of Clair in 
-the methods. If you reported this bug to the developers, you should say so and link it here (same comment for all the bugs).}
+is present in package Cairo in Xenial release and it is not detected by Clair.
 
@@
 present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
-Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274.
+Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274. \change{The reasons of Clair showing
+false positives and false negatives are unclear. We reported this issue on two Google groups of Clair i.e CoreOS Dev and
+clair-dev (\href{https://groups.google.com/forum/#!topic/clair-dev/8IqCCfd-EEc}{https://groups.google.com/forum/#!topic/clair-dev/8IqCCfd-EEc}).
+However, we did not receive any reply from developers.}
 
@@
 	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753.
-
+%\begin{table*}
+%\csvreader[%
+% respect all,%
+%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
+%      \begin{adjustbox}{max width=\textwidth},
+%  after reading=\end{adjustbox},
+% tabular={c |c | c | c | c |c |c |c |c},
+%	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls} & {a} & {b} & {c}\\\hline,
+% late after line= \\,
+%        late after last line=\\\hline
+%]{status.csv}{}{\csvlinetotablerow}%
+%       \centering
+%        \caption{\label{status}Existing number of Vulnerabilities}
+%\end{table*}
 \subsection{Effect Of Update}
@@
 
-\begin{figure*}
-        {\includegraphics[scale=1.5,width=\textwidth]
-        {Figures/graphwithdeletedpackages.pdf}}
-	\caption{\label{deleted}\#Deleted Packages vs \#Reduced Vulnerabilities}
-\end{figure*}
+%\begin{figure*}
+%        {\includegraphics[scale=1.5,width=\textwidth]
+%        {Figures/graphwithdeletedpackages.pdf}}
+%	\caption{\label{deleted}\#Deleted Packages vs \#Reduced Vulnerabilities}
+%\end{figure*}
 
@@
 Our third experiment involves deleting unnecessary packages from the images.
-We did this experiment only on five images because the reduction process takes
-several hours.\tristan{This is not a good argument, it is vague, and it is not complete. Size reduction also requires 
-to run a pipeline in the image.}. We selected these five images at random \tristan{really? I don't think so.}. We noticed that
-after the size reduction process, the scanning results deviate a little from our initial belief \tristan{what do you mean?}.
+\change{We did this experiment on five images because the reduction process may take
+several hours. Size reduction process also requires 
+to run a pipeline in the image, which takes time}. We noticed that
+after the size reduction process, the scanning results deviate a little from our initial expectation.
 At first, we thought that we will have a notable effect of size reduction on

### 2020-05-31 Scripts/graphs/drawVenn.py

@@ -1,0 +1,22 @@
+from matplotlib import pyplot as plt
+import numpy as np
+from matplotlib_venn import venn3, venn3_circles
+ 
+# Make a Basic Venn
+v = venn3(subsets=(1, 1, 1, 1, 1, 1, 1), set_labels = ('Anchore', 'Clair', 'Vuls'))
+ 
+# Custom it
+v.get_label_by_id('100').set_text('4453')
+v.get_label_by_id('010').set_text('673')
+v.get_label_by_id('110').set_text('1031')
+v.get_label_by_id('001').set_text('325')
+v.get_label_by_id('101').set_text('657')
+v.get_label_by_id('011').set_text('2220')
+v.get_label_by_id('111').set_text('10691')
+for text in v.set_labels:
+    text.set_fontsize(18)
+for text in v.subset_labels:
+    text.set_fontsize(15)
+# Show it
+plt.savefig('venn.pdf',dpi=2000)
+

### 2020-05-31 paper.tex
changed reference

@@
 
-\begin{table*}
-  \caption{some table}
-	\begin{tabular}{>|{\bfseries}c| c| c| *{4}{c|}}\hline
-	  \multirow{2}{*}{\bfseries Image Labels} & 
-	  \multirow{2}{*}{\bfseries Image Names} & 
-	  \multirow{2}{*}{\bfseries OS} & 
-	  \multicolumn{4}{c|}{\bfseries Vulnerabilities} \\\cline{2-5} 
-                       & \textbf{A} & \textbf{C} & \textbf{V}  & \textbf{S} \\ \hline
-a	& bids/example	& ubuntu:14.04	& 838	& 663	& 683	& \\ \hline
-b	& bids/freesurfer	& ubuntu:14.04	& 353	& 215	& 192	& \\ \hline
-c	& bids/ndmg	& ubuntu:14.04	& 934	& 757	& 782	& \\ \hline
-d	& bids/broccoli:v1.0.0	& centos 6	& 79	& 79	& 117	& \\ \hline
-e	& bids/fibredensityandcrosssection	& ubuntu:14.04	& 1086	& 849	& 868	& \\ \hline
-f	& bids/spm	& ubuntu:14.04	& 191	& 246	& 235	& \\ \hline
-g	& poldracklab/mriqc:0.15.0	& ubuntu:16.04	& 432	& 328	& 332	& \\ \hline
-h	& bids/cpac:v1.0.1a\_22	& ubuntu:16.04	& 698	& 524	& 535	& \\ \hline
-I	& bids/hyperalignment	& ubuntu:16.04	& 1717	& 1327	& 1433	& \\ \hline
-j	& bids/mindboggle:0.0.4-1	& debian:8	& 671	& 955	& 569	& \\ \hline
-k	& bids/mrtrix3\_connectome	& ubuntu:18.04	& 275	& 157	& 158	& \\ \hline
-l	& bids/rs\_signal\_extract:0.1	& ubuntu:16.04	& 867	& 454	& 473	& \\ \hline
-m	& bids/aa:v0.2.0	& ubuntu:14.04	& 189	& 244	& 233	& \\ \hline
-n	& bids/niak	& ubuntu:16.04	& 1482	& 1366	& 1420	& \\ \hline
-o	& bids/oppni:v0.7.0-1	& ubuntu:14.04	& 913	& 698	& 723	& \\ \hline
-p	& poldracklab/fmriprep:unstable	& ubuntu:16.04	& 516	& 355	& 393	& \\ \hline
-q	& bids/brainiak-srm	& ubuntu:16.04	& 897	& 484	& 503	& \\ \hline
-r	& bids/nipypelines:0.3.0	& debian:8	& 641	& 878	& 451	& \\ \hline
-s	& bids/hcppipelines:v3.17.0-18	& debian:8	& 526	& 873	& 620	& \\ \hline
-t	& bids/magetbrain	& ubuntu:18.04	& 112	& 117	& 126	& \\ \hline
-u	& bids/tracula:v6.0.0-4	& ubuntu:14.04	& 874	& 664	& 683	& \\ \hline
-v	& bids/baracus	& ubuntu:14.04	& 172	& 238	& 216	& \\ \hline
-w	& bids/antscorticalthickness:v2.2.0-1	& ubuntu:17.04	& 289	& 27	& no oval data	& \\ \hline 
-x	& bids/dparsf:v4.3.12	& ubuntu:14.04	& 507	& 750	& 757	& \\ \hline
-y	& bids/afni\_proc	& ubuntu:17.10	& 67	& 16	& no oval data	& \\ \hline
-z	& bids/rshrf:1.0.1	& alpine:3.8.4	& 5	& 3	& 3	& \\ \hline
-aa	& bids/ndmg:v0.1.0	& ubuntu 14.04	& 934	& 758	& 782	& \\ \hline
-ab	& mcin/qeeg:latest	& centos 7	& 46	& 46	& 142	& \\ \hline
-ac	& camarasu/creaphase:0.3	& centos 7	& 54	& 54	& 186	& \\ \hline
-ad	& bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest	& centos 7	& 70	& 76	& 157	& \\ \hline
-ae	& mcin/docker-fsl:latest	& centos 7	& 75	& 75	& 201	& \\ \hline
-af	& gkiar/onevoxel:v0.3.0rc2	& alpine 3.7.1	& 5	& 2	& 2	& \\ \hline
-ag	& bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest	& centos 7	& 70	& 76	& 157	& \\ \hline 
-ah	& bt5e/ants:latest	& centos 7	& 150	& 156	& 336	& \\ \hline
-ai	& poldracklab/fmriprep:1.2.3	& ubuntu 16.04	& 591	& 441	& 447	& \\ \hline
-aj	& gkiar/dwipreproc\_fsl-5.0.11\_minified	& ubuntu 16.04	& 391	& 258	& 263	& \\ \hline
-ak	& gkiar/mask2boundary:v0.1.0	& alpine 3.9.0	& 15	& 11	& 11	& \\ \hline
-al	& mcin/ica-aroma:latest	& centos 7	& 75	& 75	& 202	& \\ \hline
-am	& c3genomics/genpipes	& 	& 	& 	& 	& 99 \\ \hline
-an	& bioinformatics-group/aqua-singularity-recipe	& 	& 	& 	& 	& 7 \\ \hline
-ao	& MontrealSergiy/BEst	& 	& 	& 	& 	& 106 \\ \hline
-ap	& shub://aces/cbrain-containers-recipes:fsl\_v6.0.1	& 	& 	& 	& 	& 206 \\ \hline
-aq	& shots47s/bids-freesurfer-6.0	& 	& 	& 	& 	& 212 \\ \hline
-ar	& shots47s/bids-fmriprep-1.2.3	& 	& 	& 	& 	& 453 \\ \hline
-  \end{tabular}
-  \end{table*}
+%\begin{table*}
+%  \caption{some table}
+%	\begin{tabular}{>|{\bfseries}c| c| c| *{4}{c|}}\hline
+%	  \multirow{2}{*}{\bfseries Image Labels} & 
+%	  \multirow{2}{*}{\bfseries Image Names} & 
+%	  \multirow{2}{*}{\bfseries OS} & 
+%	  \multicolumn{4}{c|}{\bfseries Vulnerabilities} \\\cline{2-5} 
+%                       & \textbf{A} & \textbf{C} & \textbf{V}  & \textbf{S} \\ \hline
+%a	& bids/example	& ubuntu:14.04	& 838	& 663	& 683	& \\ \hline
+%b	& bids/freesurfer	& ubuntu:14.04	& 353	& 215	& 192	& \\ \hline
+%c	& bids/ndmg	& ubuntu:14.04	& 934	& 757	& 782	& \\ \hline
+%d	& bids/broccoli:v1.0.0	& centos 6	& 79	& 79	& 117	& \\ \hline
+%e	& bids/fibredensityandcrosssection	& ubuntu:14.04	& 1086	& 849	& 868	& \\ \hline
+%f	& bids/spm	& ubuntu:14.04	& 191	& 246	& 235	& \\ \hline
+%g	& poldracklab/mriqc:0.15.0	& ubuntu:16.04	& 432	& 328	& 332	& \\ \hline
+%h	& bids/cpac:v1.0.1a\_22	& ubuntu:16.04	& 698	& 524	& 535	& \\ \hline
+%I	& bids/hyperalignment	& ubuntu:16.04	& 1717	& 1327	& 1433	& \\ \hline
+%j	& bids/mindboggle:0.0.4-1	& debian:8	& 671	& 955	& 569	& \\ \hline
+%k	& bids/mrtrix3\_connectome	& ubuntu:18.04	& 275	& 157	& 158	& \\ \hline
+%l	& bids/rs\_signal\_extract:0.1	& ubuntu:16.04	& 867	& 454	& 473	& \\ \hline
+%m	& bids/aa:v0.2.0	& ubuntu:14.04	& 189	& 244	& 233	& \\ \hline
+%n	& bids/niak	& ubuntu:16.04	& 1482	& 1366	& 1420	& \\ \hline
+%o	& bids/oppni:v0.7.0-1	& ubuntu:14.04	& 913	& 698	& 723	& \\ \hline
+%p	& poldracklab/fmriprep:unstable	& ubuntu:16.04	& 516	& 355	& 393	& \\ \hline
+%q	& bids/brainiak-srm	& ubuntu:16.04	& 897	& 484	& 503	& \\ \hline
+%r	& bids/nipypelines:0.3.0	& debian:8	& 641	& 878	& 451	& \\ \hline
+%s	& bids/hcppipelines:v3.17.0-18	& debian:8	& 526	& 873	& 620	& \\ \hline
+%t	& bids/magetbrain	& ubuntu:18.04	& 112	& 117	& 126	& \\ \hline
+%u	& bids/tracula:v6.0.0-4	& ubuntu:14.04	& 874	& 664	& 683	& \\ \hline
+%v	& bids/baracus	& ubuntu:14.04	& 172	& 238	& 216	& \\ \hline
+%w	& bids/antscorticalthickness:v2.2.0-1	& ubuntu:17.04	& 289	& 27	& no oval data	& \\ \hline 
+%x	& bids/dparsf:v4.3.12	& ubuntu:14.04	& 507	& 750	& 757	& \\ \hline
+%y	& bids/afni\_proc	& ubuntu:17.10	& 67	& 16	& no oval data	& \\ \hline
+%z	& bids/rshrf:1.0.1	& alpine:3.8.4	& 5	& 3	& 3	& \\ \hline
+%aa	& bids/ndmg:v0.1.0	& ubuntu 14.04	& 934	& 758	& 782	& \\ \hline
+%ab	& mcin/qeeg:latest	& centos 7	& 46	& 46	& 142	& \\ \hline
+%ac	& camarasu/creaphase:0.3	& centos 7	& 54	& 54	& 186	& \\ \hline
+%ad	& bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest	& centos 7	& 70	& 76	& 157	& \\ \hline
+%ae	& mcin/docker-fsl:latest	& centos 7	& 75	& 75	& 201	& \\ \hline
+%af	& gkiar/onevoxel:v0.3.0rc2	& alpine 3.7.1	& 5	& 2	& 2	& \\ \hline
+%ag	& bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest	& centos 7	& 70	& 76	& 157	& \\ \hline 
+%ah	& bt5e/ants:latest	& centos 7	& 150	& 156	& 336	& \\ \hline
+%ai	& poldracklab/fmriprep:1.2.3	& ubuntu 16.04	& 591	& 441	& 447	& \\ \hline
+%aj	& gkiar/dwipreproc\_fsl-5.0.11\_minified	& ubuntu 16.04	& 391	& 258	& 263	& \\ \hline
+%ak	& gkiar/mask2boundary:v0.1.0	& alpine 3.9.0	& 15	& 11	& 11	& \\ \hline
+%al	& mcin/ica-aroma:latest	& centos 7	& 75	& 75	& 202	& \\ \hline
+%am	& c3genomics/genpipes	& 	& 	& 	& 	& 99 \\ \hline
+%an	& bioinformatics-group/aqua-singularity-recipe	& 	& 	& 	& 	& 7 \\ \hline
+%ao	& MontrealSergiy/BEst	& 	& 	& 	& 	& 106 \\ \hline
+%ap	& shub://aces/cbrain-containers-recipes:fsl\_v6.0.1	& 	& 	& 	& 	& 206 \\ \hline
+%aq	& shots47s/bids-freesurfer-6.0	& 	& 	& 	& 	& 212 \\ \hline
+%ar	& shots47s/bids-fmriprep-1.2.3	& 	& 	& 	& 	& 453 \\ \hline
+%  \end{tabular}
+%  \end{table*}
 
@@
 false positives and false negatives are unclear. We reported this issue on two Google groups of Clair i.e CoreOS Dev and
-clair-dev (\href{https://groups.google.com/forum/#!topic/clair-dev/8IqCCfd-EEc}{https://groups.google.com/forum/#!topic/clair-dev/8IqCCfd-EEc}).
+clair-dev \href{https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc}{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}
 However, we did not receive any reply from developers.}

### 2020-06-03 paper.tex
ordered markers

@@
 scanners. Static scanning performs analysis on a image without running it
-as a container. Therefore, commands cannot be executed to inquire installed packages}
-
-\tristan{Does it really look into files, or only installed packages? Please check. The difference is important 
-when software is installed without using the package manager.}, without deploying the image in a container. In
-dynamic scanning however, a container is started from the image and
-\tristan{... It is still unclear how dynamic scanning works. Your text
-mentions ``running a container from the image and then scanning the dynamic
-behavior of the image'' but in practice it should explain what is executed
-in the image: the package manager? other scanning tools? Please clarify by
-completing this sentence.}
+as a container. Therefore, package manager, which is a executable file,
+cannot be used to extract required data while statically extracting image data.
+Thus, scanners parse different files for extracting image data e.g, installed packages, their versions,
+and OS distribution etc. For instance, in Debian and Ubuntu, \textit{/var/lib/dpkg/status} file
+can be parsed to get a list of installed packages and in the same way \textit{/etc/os-release} file can be
+parsed to get information about OS distribution.
+Whereas in dynamic scanning, a container is deployed from the image first and then
+package manager of the image is executed inside the container to collect required data.}
 
@@
 
-We used four popular image scanners, namely Anchore~\cite{github_2019},
+\change{We used four popular image scanners, namely Anchore~\cite{github_2019},
 Vuls~\cite{future-architect_2019}, Clair Scanner~\cite{arminc_2019} and
 Stools~\cite{stools}. Anchore, Vuls and Clair Scanner support Docker
-images while Stools supports Singularity. Vuls is a dynamic scanner, while the others
-are static scanners. To avoid discrepancies, we froze the vulnerability
+images while Stools supports Singularity. Vuls support both static as well as dynamic
+scanning till version 0.9.5, however, in our experiments we used it dynamically.
+On the contrary, the others
+are static scanners.} To avoid discrepancies, we froze the vulnerability
 databases for these scanners on September 25, 2019.
@@
 for scanning Singularity images for vulnerabilities.
-Initially, Clair Scanner was intended to scan Docker containers only. This tool does not fit well
+Initially, Clair Scanner was intended to scan Docker images only. This tool does not fit well
 to scan Singularity images because of the different image formats.
@@
 
-\begin{table}
-\csvreader[%
- respect all,%
-  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
-      \begin{adjustbox}{max width=\columnwidth},
-  after reading=\end{adjustbox},
- tabular={c |c},
-        table head =Singularity Images & {Vulnerabilities by Stools}\\\hline,
- late after line= \\,
-        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
-]{Singularityresults.csv}{}{\csvlinetotablerow}%
-       \centering
-        \caption{\label{sing}Number of Vulnerabilities in Singularity images}
-\end{table}
+%\begin{table}
+%\csvreader[%
+% respect all,%
+%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
+%      \begin{adjustbox}{max width=\columnwidth},
+%  after reading=\end{adjustbox},
+% tabular={c |c},
+%        table head =Singularity Images & {Vulnerabilities by Stools}\\\hline,
+% late after line= \\,
+%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
+%]{Singularityresults.csv}{}{\csvlinetotablerow}%
+%       \centering
+%        \caption{\label{sing}Number of Vulnerabilities in Singularity images}
+%\end{table}
 
@@
 
-Table~\ref{sing} shows the number of vulnerabilities present in Singularity
-images whereas Figure~\ref{fig:venn} illustrates the number of
-vulnerabilities in Docker images, which are detected by the three scanners.
+Table~\ref{table1} shows the number of vulnerabilities present in the images,
+which are detected by the scanners.
 \tristan{You should refer to tables in the order they are presented (1
-first, then 2). Tables should also be located next to their reference. In
-this case I would actually create a single table, greying out cells that
-aren't pertinent (Anchore, Vuls and Clair for Singularity images.)}
- The
-overlapping regions of the Venn diagram show the number of common vulnerabilities detected by either two or
-three scanners. In total 10691 vulnerabilities are detected by three scanners.
-There are also vulnerabilities that are detected only by one scanner. \tristan{The last 3 sentences bring absolutely no 
-extra information that can't be read on the figure directly. You should replace them with only 1 sentence noting that there 
-are important discrepancies between scanner results (maybe quantify that with a Dice or Jaccard coefficient). This is an example 
-of how writing should be improved throughout the paper.}
+first, then 2). Tables should also be located next to their reference.}
+It is important to note that results have major discrepancies.
+The Jaccard coefficient of Anchore with both Clair and Vuls is 0.59,
+whereas Vuls and Clair have 0.83.
 
@@
 claim that, claim should be softened.}.
-Similarly, Figure~\ref{sing} \tristan{there is a reference error, and if it's still a different figure I think you should make only 1.} illustrates the number of vulnerabilities in Singularity images used in Boutiques images.
-\tristan{In the Figure, could you increase the marker size in the caption, and order it so that the different versions of a distribution 
-are grouped together and sorted by increasing version?}
-\begin{table*}
+%\begin{table*}
+%\csvreader[%
+% respect all,%
+%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
+%      \begin{adjustbox}{max width=\textwidth},
+%  after reading=\end{adjustbox},
+% tabular={c |c | c | c | c |c},
+%	table head =Image Labels &{Image names} & {OS} & {Anchore} & {Clair} & {Vuls}\\\hline,
+% late after line= \\,
+%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
+%]{results.csv}{}{\csvlinetotablerow}%
+%       \centering
+%	\caption{\label{table1}Existing number of Vulnerabilities}
+%\end{table*}
+
+\begin{table*}[!ht]
 \csvreader[%
@@
  tabular={c |c | c | c | c |c},
-	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
+	table head =Image Labels &{Image names} & {Anchore} & {Clair} & {Vuls} &{Stools}\\\hline,
  late after line= \\,
         late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
-]{results.csv}{}{\csvlinetotablerow}%
+]{fullresults.csv}{}{\csvlinetotablerow}%
        \centering
-	\caption{\label{table1}Existing number of Vulnerabilities}
+        \caption{\label{table1}Number of vulnerabilities by scanners}
 \end{table*}
-%\begin{comment}
-%\begin{table}
-%\csvreader[%
-% respect all,%
-%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
-%      \begin{adjustbox}{max width=\columnwidth},
-%  after reading=\end{adjustbox},
-% tabular={c|c},
-%	table head ={Image Tag} & {Image Name}\\\hline,
-% late after line= \\,
-%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
-%]{names.csv}{}{\csvlinetotablerow}%
-%       \centering
-%	\caption{\label{table2}Image names}
-%\end{table}
-%\end{comment}
+
 \begin{figure}
@@
         {Figures/vulnwithupdate.pdf}}
-        \caption{\label{fig:graph2} Numner of vulnerabilities before and
+        \caption{\label{fig:graph2} Number of vulnerabilities before and
         after update of the images}
@@
 \subsection{Comparisons between Scanners}
-
-Table~\ref{table1} compares the results of scanning images with the three scanners.
-Venn Diagram in Figure~\ref{fig:venn} summarizes this table. \tristan{You said it already.}
 
@@
 
-The number and type of vulnerabilities reported by the three scanners are drastically different from each other.
-It was interesting to investigate the reasons for these differences.
+As the number and type of vulnerabilities reported by the three scanners are drastically different from each other,
+it was interesting to investigate the reasons for these differences.
 %these scanners report different numbers and types of vulnerabilities.
@@
 \textbf{CVEs with Status as “Not-affected”:} Vuls is reporting vulnerabilities that have status
-as "not-affected" in the vulnerability database. So it means Linux distribution which is inside the image is not affected
-by the particular CVE. However, it is reported by Vuls \tristan{do you mean Anchore? This sounds circular.}. In other words, we can say that
-these are false positives \tristan{the use of ``false positives'' is ambiguous} by Vuls.
+as "not-affected" in the vulnerability database. It means Linux distribution which is inside the image is not affected
+by the particular CVE. In other words, Vuls is reporting vulnerabilities that it should not have reported.
 For example, we scanned an image having the Trusty release in it and Vuls is reporting CVE-2015-2305
@@
 \change{We did this experiment on five images because the reduction process may take
-several hours. Size reduction process also requires 
-to run a pipeline in the image, which takes time}. We noticed that
+several hours because it requires 
+a pipeline to run in the image, which takes time. We noticed that
 after the size reduction process, the scanning results deviate a little from our initial expectation.
@@
 and \rom{2}) the kind of packages that we deleted. In other
-words, if we delete a low number of packages then vulnerabilities do not get decreased as expected.
-In contrast, if the number of deleted packages are high, reduction
-in vulnerabilities also becomes high. For instance, we were able to delete only 21 and 25 packages for 
+words, deleting more packages reduces more vulnerabilities. 
+For instance, we were able to delete only 21 and 25 packages for 
 \textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
-reduced only by 4 and 17 respectively. Furthermore, this is illustrated in Figure~\ref{deleted} \tristan{I'm not thrilled by this figure, I would 
-just mention in the text that we verified that.}.
-\tristan{The next sentence is interesting because it starts characterizing the images that benefit the most 
-from size reduction. The previous sentences read like a tautology, you should make your comment more specific.} 
+reduced only by 4 and 17 respectively. 
 Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
@@
 deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
-by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}. 
+by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}.} 
 %Our third experiment shows that deleting unnecessary packages from the image also helps to reduce
@@
 Our initial thought was that with the update and size reduction process together, we will be able to
-reduce vulnerabilities even more. However
-we analyzed that this is not always true. Again, it depends on which packages you \tristan{in general don't use ``you'' in a 
-formal paper.} are deleting and how
+reduce vulnerabilities even more. However,
+we analyzed that this is not always true. Again, it depends on which packages are deleted and how
 many vulnerabilities they contained. To illustrate, \textit{bids/example} image in Figure~\ref{fig:bargraph}
@@
 
-\subsection{Conclusion}
+\subsection{Conclusions and Future Work}
 
@@
 always true. It depends on two factors: kind and the number of packages that we are
-deleting. Therefore, we conclude this paper by suggesting ten simple rules that can be
+deleting. Therefore, we conclude this paper by suggesting some particular rules that can be
 followed to keep container images safe.
@@
 
-\tristan{You should discuss future work here too.}
+In future work we would like to see how these vulnerabilities can be leveraged
+to design attacks from containers. Particularly, we want
+to consider web servers and clusters that processes data using containers.
+
+\tristan{future work}
 

### 2020-06-03 Scripts/graphs/script.py

@@ -6,7 +6,7 @@ import seaborn as sns
 import pandas as pd
 import numpy as np
 # Load the data
-d = pd.read_csv(r"../train3.csv")
+d = pd.read_csv(r"../../train3.csv")
 d.head()
 df=pd.DataFrame(d)
 plt.figure(figsize=(200,20))
@@ -15,8 +15,10 @@ colors = {'ubuntu:14.04' : '#2E37FE', 'ubuntu:16.04' : '#CAE1FF', 'ubuntu:17.04'
         'alpine:3.7.1':'#3CB371','alpine:3.8.4':'#00ff00','alpine:3.9.0':'#006400','debian:8':'#ffa500'}
 markers = {"ubuntu:14.04": "o", "ubuntu:16.04": "o",'ubuntu:17.04':'o','ubuntu:17.10':'o','ubuntu:18.04' : 'o','centos 6':'o','centos 7':'o',
         "alpine:3.7.1":'o','alpine:3.8.4':"o","alpine:3.9.0":"o","debian:8":"o"}
-with sns.plotting_context(rc={"legend.fontsize":25,"font.size":18,"axes.titlesize":20,"font.weight":'heavy',"legend.labelspacing":20}):
-  p1=sns.relplot(x="Packages",y="Vulnerabilities",hue="OS distribution",size="CRITICAL Vulnerabilities",sizes=(300,1450),data = df,palette=colors,markers=markers,style="OS distribution",height=10, aspect=2)
+marker_order=["ubuntu:14.04", "ubuntu:16.04",'ubuntu:17.04','ubuntu:17.10','ubuntu:18.04','centos 6','centos 7',
+        "alpine:3.7.1",'alpine:3.8.4',"alpine:3.9.0","debian:8"]
+with sns.plotting_context(rc={"legend.fontsize":25,"font.size":18,"legend.font_scale":1.5,"axes.titlesize":20,"font.weight":'heavy',"legend.labelspacing":20}):
+  p1=sns.relplot(x="Packages",y="Vulnerabilities",hue="OS distribution",hue_order=marker_order,size="CRITICAL Vulnerabilities",sizes=(300,1450),data = df,palette=colors,markers=markers,style="OS distribution",height=10, aspect=2)
 p1.set(xlabel='#Packages', ylabel='#Vulnerabilities')
 p1.set(xticks=[i for i in range(0, max(df['Packages']) + 100, 50)],
        yticks=[i for i in range(0, max(df['Vulnerabilities']) + 20, 250)])

### 2020-06-03 paper.tex
comment changes 2

@@
 biggest concern while deploying containers.
-Besides web applications, containers are also popularly used for scientific computing
-and data science in neuroscience. In fact, Singularity was developed for scientific applications
-by keeping the focus on HPC environments. This popularity of containers leads us to the
+Containers are popular in various scientific fields, in particular to run Big Data analyses
+on HPC clusters. 
+However, deploying Docker container images on clusters raises security issues. Some security issues 
+that could possibly lead to privilege escalation, DoS or information leak. Some
+security issues are related to the architecture of Docker but have been 
+largely solved by Singularity.
+In fact, Singularity was developed for scientific applications
+by keeping the focus on HPC environments. Although, this work is of general interest,
+our particular focus in this paper is neuroimaging as containers are popularly used for scientific computing and data science
+in neuroscience.
+This popularity of containers in neuroscience leads us to the
 primary research question of this work: \textit{what is the current security state of
-container images that are deployed on HPC clusters?}
+neuroimaging container images that are deployed on HPC clusters?}
 
@@
 
-\tristan{The above text contains true statements, but they are not organized 
-to introduce the paper correctly. It should be rewritten according to the following logic:
-\begin{itemize}
-	\item Containers are popular in various scientific fields, in particular to run Big Data analyses on HPC clusters.
-Mention that neuroimaging is our particular focus, although this work is of general interest.
-	\item However, deploying container images on clusters raises security issues. Some security issues that could possibly lead to privilege escalation, DoS or information leak. Some
-	security issues are related to the architecture of container systems (Docker) but have been largely solved by Singularity.
-	\item Here we are interested in image vulnerabilities [explain research questions as you did]
-	\item [introduce paper outline as done]
-\end{itemize}}
-
-\textit{RQ1:} Are vulnerabilities present inside container images that are
+\textit{RQ1:} Are vulnerabilities present inside neuroimaging container images that are
 deployed on HPC clusters?
@@
 and shrinking image size on vulnerabilities?
-
-To answer those questions, we take an example of neuroscience field where
-containers are used on Compute Canada HPC cluster.
 
@@
 and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
-Also, Singularity came up with Stools \href{https://github.com/singularityhub/stools}{(https://github.com/singularityhub/stools)}, which can be used for scanning Singularity images
+Zerouali et al. in~\cite{zerouali2019relation} studied severity vulnerabilities and bugs in Docker 
+containers due to outdated packages.
+
+There are various image scanners available for scanning Docker images, for
+instance Anchore, CoreOS's Clair, etc.
+However, these scanners cannot be used to scan Singularity images due to different image formats.
+Therefore, Singularity came up with Stools \href{https://github.com/singularityhub/stools}{(https://github.com/singularityhub/stools)}, which can be used for scanning Singularity images
 for security and quality checks.
-Here, we focus on the specific context of scientific data analysis on HPC clusters, taking
-neuroimaging as an example.
 
 This paper is organized as follows: in the next section, we provide description
-of materials and methods which summarize our four main experiments. We also explain
-scanning tools that we use for scanning container images to report
-vulnerabilities. The next section of this paper provides the results, where we
+of materials and methods which summarize our experiments. We also explain different
+image scanners used to report
+vulnerabilities in container images. The next section of this paper provides the results, where we
 present a number of existing vulnerabilities in the container images
@@
 discussion and analysis of these results, where we provide more insight into the problems that 
-we faced while conducting these experiments. Finally, we conclude this paper by proposing some
-particular rules that can be followed to secure container images for use in clusters.
+we faced while conducting these experiments. We also propose some
+particular rules that can be followed to secure container images. Finally, conclusions are drawn
+in the last section of the paper.
 
@@
 
-\change{This study involves several image scanning experiments. To begin with,
+This study involves several image scanning experiments. To begin with,
 we scan the images as is to report the existing vulnerabilities
@@
 description of these varying Linux distributions/releases and their
-vulnerability databases.}
+vulnerability databases.
 
@@
 
-\tristan{This sub-section has a lot of boilerplate material. It should be summarized.}
-
-Container tools are capable of packing and running an application in an isolated environment that has
-the application's dependencies,
-required libraries, and configuration files for the
-application to function properly.
+In this paper, we consider two popular container tools i.e Docker and Singularity because
+neuroimaging uses images from these two tools.
+%Container tools are capable of packing and running an application in an isolated environment that has
+%the application's dependencies,
+%required libraries, and configuration files for the
+%application to function properly.
 
@@
 
-Docker uses a client-server architecture, where client, containers, communicate to
-the server, Docker Daemon, which is also known as the Docker engine.
-Docker Daemon is a long-running process that manages all Docker images, containers, storage volumes, and networks.
+%Docker uses a client-server architecture, where client, containers, communicate to
+%the server, Docker Daemon, which is also known as the Docker engine.
+%Docker Daemon is a long-running process that manages all Docker images, containers, storage volumes, and networks.
 
@@
 %Docker runs a software, \textit{Docker daemon}, on the host machine.
-It runs as root and is remotely controlled through a
+Docker Engine, which runs as root, is remotely controlled through a
 UNIX socket. It is responsible for launching and managing containers,
@@
 
-\change{Container image scanners can be broadly categorized into static and dynamic
+Container image scanners can be broadly categorized into static and dynamic
 scanners. Static scanning performs analysis on a image without running it
@@
 Whereas in dynamic scanning, a container is deployed from the image first and then
-package manager of the image is executed inside the container to collect required data.}
+package manager of the image is executed inside the container to collect required data.
 
@@
 
-\change{We used four popular image scanners, namely Anchore~\cite{github_2019},
+We used four popular image scanners, namely Anchore~\cite{github_2019},
 Vuls~\cite{future-architect_2019}, Clair Scanner~\cite{arminc_2019} and
@@
 On the contrary, the others
-are static scanners.} To avoid discrepancies, we froze the vulnerability
+are static scanners. To avoid discrepancies, we froze the vulnerability
 databases for these scanners on September 25, 2019.
 
-\tristan{The scanner descriptions need to be streamlined. They are quite verbose and not very consistent for now.}
-
 \subsubsection{Anchore}
 
-Anchore is an end-to-end, open-source container security platform. Anchore
+Anchore is an end-to-end, open-source container security platform. It
 is a static
@@
 installed directly on the host and used to inspect images.
-In our experiments, we used a Docker image to get Anchore Engine version 0.5.0 and Engine Database
+In our experiments, we used a Docker image to get Anchore Engine version 0.5.0 and Database
 version 0.0.11.
@@
 
-\begin{figure}
+\begin{figure}[!ht]
 	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
@@
 Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
+It offers both static and dynamic scanning. In our experiments, we used
+it to dynamically scan containers.
 Using a dynamic scanning technique, it offers
@@
 and deep scan mode.
-The Fast scan is performed without root privileges, whereas a fast root scan is
-performed with root privileges. The latter also uses checkrestart utility to 
-detect processes that are updated but not yet restarted because if they are not
-restarted, updates are not effective. Fast root scan also detects these
-processes. Both fast scan and fast root scan are performed offline without Internet
-access, and put almost no load on the scan target server. The Deep scan uses
-root privileges for scanning and is used to get a more detailed scan. It checks
-changelogs, which puts more load on the target server.
+%The Fast scan is performed without root privileges, whereas a fast root scan is
+%performed with root privileges. The latter also uses checkrestart utility to 
+%detect processes that are updated but not yet restarted because if they are not
+%restarted, updates are not effective. Fast root scan also detects these
+%processes. Both fast scan and fast root scan are performed offline without Internet
+%access, and put almost no load on the scan target server. The Deep scan uses
+%root privileges for scanning and is used to get a more detailed scan. It checks
+%changelogs, which puts more load on the target server.
 
@@
 
-\change{In our experiments, we used a Docker image (arminc/clair-local-scan:v2.0.6) for scanning
+In our experiments, we used a Docker image (arminc/clair-local-scan:v2.0.6) for scanning
 and an another Docker image (arminc/clair-db:latest) for the vulnerability database, which was
@@
 scanning on 2019-09-25. So, it means that Clair Scanner's database was already
-old by one week.}
+old by one week.
 
@@
 
-\change{Image scanners report vulnerabilities differently depending on the Linux release types.
-Therefore, we provide an overview of these Linux releases by taking an example. 
+Image scanners report vulnerabilities differently depending on the different Linux release types.
+Therefore, we provide an overview of these Linux releases and scanners re. 
 BIDS app and Boutiques images in our experiments have diverse Linux
 distributions such as Ubuntu, Centos, Debian, and Alpine. Further, a particular
-distribution have different releases in general. Here, we take Ubuntu as an example
+distribution have different releases in general. Here, we take Ubuntu's example
 to discuss different releases and their vulnerability databases. We took Ubuntu's example
-because mostly images in our experiments have this distibution.} In the case of Ubuntu, release
+because mostly images in our experiments have this distibution. However, other distributions also have
+similar release trend. In the case of Ubuntu, release
 can be of two types: Regular or Long Term Support (LTS).
@@
 
-\change{If there exist vulnerabilities in the container image, then we can
+If there exist vulnerabilities in the container image, then we can
 run after updating the
@@
 the unnecessary packages. For this process we used the same scripts that
-we used for earlier experiments.}
+we used for earlier experiments.
 
@@
 which are detected by the scanners.
-\tristan{You should refer to tables in the order they are presented (1
-first, then 2). Tables should also be located next to their reference.}
-It is important to note that results have major discrepancies.
-The Jaccard coefficient of Anchore with both Clair and Vuls is 0.59,
-whereas Vuls and Clair have 0.83.
+It is important to note that results have major discrepancies. In particular,
+Anchore reports far more different results than Vuls and Clair resulting in 
+the Jaccard coefficient of 0.59 with both,
+whereas Vuls and Clair share more common vulnerabilities resulting to the Jaccard coefficient of 0.83.
 
@@
 The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
-also get increased \tristan{mention the parameters of the regression line (preferably as a label in the figure) and the regression error}.
+also get increased.
 The figure also infers that Alpine distribution, being the
-lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains the highest number of
-vulnerabilities. Debian and Centos contain a higher number of critical vulnerabilities than Ubuntu and Alpine \tristan{I dont think there is enough data to 
-claim that, claim should be softened.}.
+lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains more packages and hence report more vulnerabilities.
+We also analyzed that out of the total Docker images scanned in our experiment, Debian reported more critical vulnerabilties than others, reaching
+up to 180.
 %\begin{table*}
@@
 
-\begin{figure}
+\begin{figure*}[!ht]
+        {\includegraphics[scale=1.5,width=\textwidth]
+        {Figures/vulngraph.pdf}}
+        \caption{\label{fig:graph1} Number of vulnerabilities by packages}
+      \end{figure*}
+
+\begin{figure}[!ht]
         {\includegraphics[scale=2.5,width=\columnwidth]
@@
 
-\begin{figure*}[t]
-	{\includegraphics[scale=1.5,width=\textwidth]
-	{Figures/vulngraph.pdf}}
-        \caption{\label{fig:graph1} Number of vulnerabilities by packages}
-      \end{figure*}
-
-\begin{figure*}[b]
-        {\includegraphics[width=\textwidth]
-        {Figures/vulnwithupdate.pdf}}
-        \caption{\label{fig:graph2} Number of vulnerabilities before and
-        after update of the images}
-      \end{figure*}
+%\begin{figure*}[b]
+%        {\includegraphics[width=\textwidth]
+%        {Figures/vulnwithupdate.pdf}}
+%        \caption{\label{fig:graph2} Number of vulnerabilities before and
+%        after update of the images}
+%      \end{figure*}
 
@@
 
+Figure~\ref{fig:venn} represents the number of common and different vulnerabilities
+that are shown by scanners.
 When we add all regions of Venn diagram
@@
 
-\begin{figure*}[b]
+\begin{figure*}[!ht]
+        {\includegraphics[width=\textwidth]
+        {Figures/vulnwithupdate.pdf}}
+        \caption{\label{fig:graph2} Number of vulnerabilities before and
+        after update of the images}
+      \end{figure*}
+
+\begin{figure*}[!ht]
         {\includegraphics[scale=1.5,width=\textwidth]
@@
 present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
-Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274. \change{The reasons of Clair showing
+Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274. The reasons of Clair showing
 false positives and false negatives are unclear. We reported this issue on two Google groups of Clair i.e CoreOS Dev and
 clair-dev \href{https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc}{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}
-However, we did not receive any reply from developers.}
 
@@
 		However, if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
-		For example CVE-2019-13565 in Ubuntu 14.04.
+		For example CVE-2019-13565 in Ubuntu 14.04. We reported this bug as well through slack
+		channel.
 
@@
 Our third experiment involves deleting unnecessary packages from the images.
-\change{We did this experiment on five images because the reduction process may take
+We did this experiment on five images because the reduction process may take
 several hours because it requires 
@@
 deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
-by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}.} 
+by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}. 
 %Our third experiment shows that deleting unnecessary packages from the image also helps to reduce
@@
 As we noticed that none of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
-some have critical vulnerabilities as well. Yet there is not a single image scanner on which we can rely upon for
+so many are critical vulnerabilities as well. Yet there is not a single image scanner on which we can rely upon for
 scanning. Additionally, we cannot update all images because some OS releases, which are used inside images, 
@@
 branch of the program. So there should be some kind of coverage measurement.
-
-\tristan{You should comment on the important number of vulnerabilities found in the images overall.}
-
-\tristan{Mention software not installed thorugh the package manager.}
+Besides this, as scanners report vulnerabilities according to the versions of the installed packages,
+they are likely to miss packages that are not installed using package manager. 
+Therefore, we suggest some particular rules that can be
+followed to keep container images safe.
+\newline 1. Update packages regularly.
+\newline 2. Remove unnecessary packages, in particular the ones used for installation (compilers, source packages, etc).
+\newline 3. Choose your base OS image wisely.
+\newline 4. Run image scanning tools in CI scripts. For instance Anchore.
+\newline 5. Protect your GitHub/DockerHub credentials because if automated builds is set up
+in Docker Hub, it can automatically build images from external repositories, for instance GitHub.
+\newline 6. Minimize dependencies.
+\newline 7. Avoid static linking because it obfuscates vulnerability scanning.
+\newline 8. Use the package manager to facilitate vulnerability detection.
+\newline 9. Use OS releases that have LTS support.
+\newline 10. Sign your images. Docker Content Trust (DCT) provides ability to digitally sign
+images to verify the integrity of the images.
 
@@
 always true. It depends on two factors: kind and the number of packages that we are
-deleting. Therefore, we conclude this paper by suggesting some particular rules that can be
-followed to keep container images safe.
-\newline 1. Update packages regularly.
-\newline 2. Remove unnecessary packages, in particular the ones used for installation (compilers, source packages, etc).
-\newline 3. Mind your base OS image.
-\newline 4. Run image scanning tools in CI scripts. For instance Anchore.
-\newline 5. Mind your GitHub/DockerHub credentials.
-\newline 6. Minimize dependencies.
-\newline 7. Avoid static linking because it obfuscates vulnerability scanning.
-\newline 8. Use the package manager to facilitate vulnerability detection.
-\newline 9. Use OS releases that have LTS support.
-\newline 10. Sign your images.
+deleting.
 
@@
 
-\tristan{future work}
-
 \bibliography{bibliography}

### 2020-06-22 paper.tex
before structure modifications

@@
 provide fast development cycles, continuous delivery,
-and cost reduction of infrastructure. OS-level virtualization gained a lot of interest when Docker was
+and cost reduction of infrastructure. OS-level virtualization gained a lot of interest when Docker~\cite{docker19} was
 introduced in 2013~\cite{gantikow2016providing}. However, Docker has security concerns due to which it
 is not supported by High Performance
-Computing (HPC) environments. As a result, Singularity came in 2016 with the goal of providing support
+Computing (HPC) environments. As a result, Singularity~\cite{singularity19} came in 2016 with the goal of providing support
 for HPC environments. It is used in many clusters including Compute Canada.
@@
 However, these scanners cannot be used to scan Singularity images due to different image formats.
-Therefore, Singularity came up with Stools \href{https://github.com/singularityhub/stools}{(https://github.com/singularityhub/stools)}, which can be used for scanning Singularity images
+Therefore, Singularity came up with Stools~\cite{stools}, which can be used for scanning Singularity images
 for security and quality checks.
@@
 This study involves several image scanning experiments. To begin with,
-we scan the images as is to report the existing vulnerabilities
-inside the images. Updating these images is likely to play a role in vulnerabilities. Therefore, we
+we scan the images as is to report the vulnerabilities
+inside the images. Updating and shrinking the size of these images is likely to play a role in vulnerabilities. Therefore, we
 update the images and then rescan all these
@@
 
-In this section, we first
-introduce two container tools used in our experiments: Docker and
-Singularity and their image formats. Then we provide more insight
+In this section, we provide
+insight
 into the container images and the image scanners that we used in our study.
-The image scanners are going to report different results due to different Linux
-distributions/releases, which have different vulnerability data. Therefore, in the last, this section presents a
+The image scanners refer to different Linux
+distributions/releases, which have different vulnerability data and is likely to
+create discrepancies in results. Therefore, in the last, this section presents a
 description of these varying Linux distributions/releases and their
@@
 
-\subsection{Container Tools}
-
-In this paper, we consider two popular container tools i.e Docker and Singularity because
-neuroimaging uses images from these two tools.
+%\subsection{Container Tools}
+%
+%
+%In this paper, we consider two popular container tools i.e Docker and Singularity because
+%neuroimaging uses images from these two tools.
 %Container tools are capable of packing and running an application in an isolated environment that has
@@
 
-\subsubsection{Docker}
+%\subsubsection{Docker}
 
@@
 %Docker runs a software, \textit{Docker daemon}, on the host machine.
-Docker Engine, which runs as root, is remotely controlled through a
-UNIX socket. It is responsible for launching and managing containers,
-consequently, when a container runs, the container is spawned as a
-child process of this root-owned daemon.
-
-\begin{comment}
-It is responsible for launching containers, their
-isolation, and spawning shells into the containers. It is also
-responsible for managing Docker images i.e \textit{pull} and \textit{push}
-from image repository, building images from Dockerfiles, signing them, etc.
-When a Docker container runs, the container process is spawned as a
-child of this root owned daemon. 
-\end{comment}
-As Docker users directly interact with the
-Docker daemon through Command Line Interface (CLI) i.e \textit{docker} command, it is possible to force Docker daemon to escalate privileges.
-If a user gets root privileges, it
-introduces unthinkable security risks for multi-tenant shared
-environments. Due to this reason, Docker is not supported by
-HPC environments.
-
-Docker images are organized as a series of layers stacked on top of each
-other and identified by unique layer identifiers. If a layer is reused
-in different images it will
-have the same id across images. Each layer consists of a filesystem diff
-with respect to the layer below.
-
-\subsubsection{Singularity}
-
-As Docker is not suitable for HPC systems, therefore, Singularity came up with a new approach
-of packing and running applications in containers. 
-In contrast to Docker,
-Singularity does not run containers as root. Consequently, users cannot escalate
-privileges in Singularity containers making it suitable for HPC environments.
-
-A Singularity image is a single immutable file and
-does not contain layers.
-Once a Singularity image is created, it cannot be changed, consequently,
-it can be used for reproducing the results of scientific
-experiments.
+
+%Docker Engine, which runs as root, is remotely controlled through a
+%UNIX socket. It is responsible for launching and managing containers,
+%consequently, when a container runs, the container is spawned as a
+%child process of this root-owned daemon.
+%
+%\begin{comment}
+%It is responsible for launching containers, their
+%isolation, and spawning shells into the containers. It is also
+%responsible for managing Docker images i.e \textit{pull} and \textit{push}
+%from image repository, building images from Dockerfiles, signing them, etc.
+%When a Docker container runs, the container process is spawned as a
+%child of this root owned daemon. 
+%\end{comment}
+%As Docker users directly interact with the
+%Docker daemon through Command Line Interface (CLI) i.e \textit{docker} command, it is possible to force Docker daemon to escalate privileges.
+%If a user gets root privileges, it
+%introduces unthinkable security risks for multi-tenant shared
+%environments. Due to this reason, Docker is not supported by
+%HPC environments.
+%
+%Docker images are organized as a series of layers stacked on top of each
+%other and identified by unique layer identifiers. If a layer is reused
+%in different images it will
+%have the same id across images. Each layer consists of a filesystem diff
+%with respect to the layer below.
+%
+%\subsubsection{Singularity}
+%
+%As Docker is not suitable for HPC systems, therefore, Singularity came up with a new approach
+%of packing and running applications in containers. 
+%In contrast to Docker,
+%Singularity does not run containers as root. Consequently, users cannot escalate
+%privileges in Singularity containers making it suitable for HPC environments.
+%
+%A Singularity image is a single immutable file and
+%does not contain layers.
+%Once a Singularity image is created, it cannot be changed, consequently,
+%it can be used for reproducing the results of scientific
+%experiments.
 
@@
 
-We scanned a total of 44 container images taken from the BIDS
+We scan a total of 44 container images taken from the BIDS
 apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}
@@
 
-Container image scanners can be broadly categorized into static and dynamic
-scanners. Static scanning performs analysis on a image without running it
-as a container. Therefore, package manager, which is a executable file,
-cannot be used to extract required data while statically extracting image data.
-Thus, scanners parse different files for extracting image data e.g, installed packages, their versions,
-and OS distribution etc. For instance, in Debian and Ubuntu, \textit{/var/lib/dpkg/status} file
-can be parsed to get a list of installed packages and in the same way \textit{/etc/os-release} file can be
-parsed to get information about OS distribution.
-Whereas in dynamic scanning, a container is deployed from the image first and then
-package manager of the image is executed inside the container to collect required data.
+%Container image scanners can be broadly categorized into static and dynamic
+%scanners. Static scanning performs analysis on a image without running it
+%as a container.
+
+%Therefore, package manager, which is a executable file,
+%cannot be used to extract required data while statically extracting image data.
+%Thus, scanners parse different files for extracting image data e.g, installed packages, their versions,
+%and OS distribution etc. For instance, in Debian and Ubuntu, \textit{/var/lib/dpkg/status} file
+%can be parsed to get a list of installed packages and in the same way \textit{/etc/os-release} file can be
+%parsed to get information about OS distribution.
+%Whereas in dynamic scanning, a container is deployed from the image first and then
+%package manager of the image is executed inside the container to collect required data.
 
@@
 Stools~\cite{stools}. Anchore, Vuls and Clair Scanner support Docker
-images while Stools supports Singularity. Vuls support both static as well as dynamic
-scanning till version 0.9.5, however, in our experiments we used it dynamically.
-On the contrary, the others
-are static scanners. To avoid discrepancies, we froze the vulnerability
+images while Stools supports Singularity. 
+To avoid discrepancies, we froze the vulnerability
 databases for these scanners on September 25, 2019.
+
+%Vuls support both static as well as dynamic
+%scanning till version 0.9.5, however, in our experiments we used it dynamically.
+%On the contrary, the others
+%are static scanners.
 
@@
 The interesting point is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
-meaning that images with these distributions are impossible to scan with Vuls.
+meaning that images with these distributions are hard to scan with Vuls.
 
@@
 Image scanners report vulnerabilities differently depending on the different Linux release types.
-Therefore, we provide an overview of these Linux releases and scanners re. 
+Therefore, we provide an overview of these Linux releases and scanners. 
 BIDS app and Boutiques images in our experiments have diverse Linux
@@
 distribution have different releases in general. Here, we take Ubuntu's example
-to discuss different releases and their vulnerability databases. We took Ubuntu's example
+to discuss its different releases and their vulnerability databases. We took Ubuntu's example
 because mostly images in our experiments have this distibution. However, other distributions also have
@@
 		The fixed version of such packages is appended by
-		+esmN or \char`\~esm, indicating that this package version is available
+		+esm or \char`\~esm, indicating that this package version is available
 		only via ESM.
@@
 in the Ubuntu launchpad database.
+
+%\begin{figure*} \centering{
+%\includegraphics{status.pdf}}
+%\caption{Experiment 1}
+%\end{figure*}
+
+%\includegraphics[width=300, max width=\textwidth]{status.pdf}
+
+%\begin{table*}[!ht]
+%\csvreader[%
+% respect all,%
+%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
+%      \begin{adjustbox}{max width=\textwidth},
+%  after reading=\end{adjustbox},
+% tabular={c |c | c | c | c | c | c | c| c | c},
+%	table head =Image Labels & {Image names} & {Anchore} & {Clair} & {Vuls} &{Stools} & {a} & {b} & {c} & {d}\\\hline,
+% late after line= \\,
+%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
+%]{status.csv}{}{\csvlinetotablerow}%
+%       \centering
+%        \caption{\label{status}Number of vulnerabilities by scanners}
+%\end{table*}
 
@@
 image size reduction process is a good choice. The most obvious way of doing this is using 
-Neurodocker (\href{https://github.com/ReproNim/neurodocker}{https://github.com/ReproNim/neurodocker}).
+Neurodocker~\cite{neurodocker}.
 It traces and deletes unnecessary files.
@@
 
-\subsection{Existing Vulnerabilities}
+\subsection{Detected Vulnerabilities}
 
@@
 
-\subsection{Comparisons between Scanners}
+\subsection{Discrepancies between Scanners}
 
@@
 that are shown by scanners.
-When we add all regions of Venn diagram
+
 we get total 20050 vulnerabilities in BIDS apps and Boutiques images.

### 2020-06-22 Scripts/compare_results/test.py

@@ -1,0 +1,45 @@
+#!/usr/bin/env python3
+
+import csv
+import sys
+import os
+import re
+
+def compare(file1,file2):
+    with open(file1, 'r') as t1, open(file2, 'r') as t2:
+        fileone = t1.readlines()
+        filetwo = t2.readlines()
+    
+    with open('C-A.csv', 'w') as f1:
+        for line in filetwo:
+            if line not in fileone:
+                f1.write(line)
+    with open('A-C.csv', 'w') as f2:
+        for line in fileone:
+            if line not in filetwo:
+                f2.write(line)
+    with open('Common.csv', 'w') as f3:
+        for line in fileone:
+            if line in filetwo:
+                f3.write(line)
+
+def main():
+    file1=sys.argv[1]
+    file2=sys.argv[2]
+    count=0
+    compare(file1,file2)
+    with open('A-C.csv','r') as fp1:
+        anchore = fp1.readlines()
+    count=len(anchore)
+    print('A-C = ' , count)
+    with open('C-A.csv','r') as fp8:
+        clair=fp8.readlines()
+    count=len(clair)
+    print('C-A ',count)
+    with open('Common.csv','r') as fp1:
+        common = fp1.readlines()
+    count=len(common)
+    print('Common = ' , count)
+
+if __name__== "__main__":
+  main()

### 2020-06-22 Scripts/graphs/script.py

@@ -5,33 +5,54 @@ import matplotlib.pyplot as plt
 import seaborn as sns
 import pandas as pd
 import numpy as np
+import scipy.stats as st
 # Load the data
 d = pd.read_csv(r"../../train3.csv")
 d.head()
 df=pd.DataFrame(d)
 plt.figure(figsize=(200,20))
 plt.rcParams["axes.labelweight"] = "bold"
+b, a = np.polyfit(df['Packages'], df['Vulnerabilities'], 1)
+xtest = np.linspace(df['Packages'].min(),df['Vulnerabilities'].max(),10)
 colors = {'ubuntu:14.04' : '#2E37FE', 'ubuntu:16.04' : '#CAE1FF', 'ubuntu:17.04':'#5190ED','ubuntu:17.10':'#000085','ubuntu:18.04' : '#98F5FF','centos 6':'#800080','centos 7':'#b19cd9',
         'alpine:3.7.1':'#3CB371','alpine:3.8.4':'#00ff00','alpine:3.9.0':'#006400','debian:8':'#ffa500'}
 markers = {"ubuntu:14.04": "o", "ubuntu:16.04": "o",'ubuntu:17.04':'o','ubuntu:17.10':'o','ubuntu:18.04' : 'o','centos 6':'o','centos 7':'o',
         "alpine:3.7.1":'o','alpine:3.8.4':"o","alpine:3.9.0":"o","debian:8":"o"}
 marker_order=["ubuntu:14.04", "ubuntu:16.04",'ubuntu:17.04','ubuntu:17.10','ubuntu:18.04','centos 6','centos 7',
         "alpine:3.7.1",'alpine:3.8.4',"alpine:3.9.0","debian:8"]
-with sns.plotting_context(rc={"legend.fontsize":25,"font.size":18,"legend.font_scale":1.5,"axes.titlesize":20,"font.weight":'heavy',"legend.labelspacing":20}):
+with sns.plotting_context(rc={"legend.fontsize":25,"legend.markersize":18,"axes.titlesize":20,"font.weight":'heavy',"legend.labelspacing":20}):
   p1=sns.relplot(x="Packages",y="Vulnerabilities",hue="OS distribution",hue_order=marker_order,size="CRITICAL Vulnerabilities",sizes=(300,1450),data = df,palette=colors,markers=markers,style="OS distribution",height=10, aspect=2)
 p1.set(xlabel='#Packages', ylabel='#Vulnerabilities')
[…]

### 2020-06-22 Scripts/graphs/test.py

@@ -1,0 +1,68 @@
+#from matplotlib import pyplot as plt
+#import pandas as pd
+#import seaborn as sns
+#import numpy as np
+#
+#d = {'x-axis':[71,35,61,253,145,157,218,241,291,277,159,167,171,188,240,254,258,269,277,288,298,347,349,353,360,380,441,443,506,528,530,537,538,566,600,762,815,889], 
+#        'y-axis': [5,5,15,79,75,641,172,867,289,67,75,112,46,150,70,70,897,391,671,54,353,275,191,189,432,526,591,516,507,838,874,934,934,1086,698,913,1717,1482],
+#        'text':['p1','p2','p3','p4','p5','p6','p7','p8','p9','p10','p11','p12','p13','p14','p15','p16','p17','p18','p19','p20','p21','p22','p23','p24','p25','p26','p27','p28','p29','p30','p31','p32','p33','p34','p35','p36','p37','p38'], 
+#        'size':[4,4,3,54,22,162,3,44,9,0,22,4,12,67,32,32,46,6,159,17,13,3,4,3,11,79,15,12,5,19,22,20,20,34,18,27,50,35],'hue':['good','bad','average','poor','good','bad','average','poor','good','bad','average','poor','poor','poor','poor','poor','poor','poor','poor','good','bad','good','bad','good','bad','good','bad','good','bad','good','bad','average','average','average','average','average','average','average']}
+#df = pd.DataFrame(d)
+#b, a = np.polyfit(df['x-axis'], df['y-axis'], 1)
+#xtest = np.linspace(df['x-axis'].min(),df['x-axis'].max(),10)
+#with sns.plotting_context(rc={"legend.fontsize":25,"legend.markersize":18,"axes.titlesize":20,"font.weight":'heavy',"legend.labelspacing":20}):
+#  p1 = sns.relplot(x='x-axis', y='y-axis',hue='hue',size='size',sizes=(300,1450),data=df,height=10, aspect=2 )
+#ax = p1.axes[0,0]
+##ax.plot(xtest, a + b* xtest, '--')
+#for idx,row in df.iterrows():
+#    x = row[0]
+#    y = row[1]
+#    text = row[2]
+#    ax.text(x+.05,y,text, horizontalalignment='left')
+##z = np.polyfit(df['x-axis'], df['y-axis'], 1)
+##p = np.poly1d(z)
+##plt.plot(df['x-axis'],p(df['x-axis']),"k--")
[…]

### 2020-06-22 Scripts/graphs/updation.py

@@ -5,8 +5,9 @@ import matplotlib.pyplot as plt
 import seaborn as sns
 import pandas as pd
 import numpy as np
+import scipy.stats as st
 # Load the data
-d = pd.read_csv(r"../train3.csv")
+d = pd.read_csv(r"../../train3.csv")
 d.head()
 df=pd.DataFrame(d)
 plt.figure(figsize=(200,20))
@@ -27,13 +28,22 @@ ax = p1.axes[0,0]
 #leg._loc = 4
 #leg.texts[12].set_text("CRITICAL \nVulnerabilities")
 #leg.remove()
-z = np.polyfit(df['Packages'], df['Vulnerabilities'], 1)
-p = np.poly1d(z)
-plt.plot(df['Packages'],p(df['Packages']),"k--")
+#z = np.polyfit(df['Packages'], df['Vulnerabilities'], 1)
+#p = np.poly1d(z)
+#plt.plot(df['Packages'],p(df['Packages']),"k--")
+
+slope, intercept, r_value, p_value, std_err = st.linregress(df['Packages'],df['Vulnerabilities'])
+line_df = pd.DataFrame()
+line_df['line'] = slope*df['Packages']+intercept
+print(std_err)
+plt.plot(df['Packages'], line_df['line'],"k-")
+#plt.legend()
+for idx,row in line_df.iterrows():
+    l = row[0]
+    ax.text(700,1050,'y=({:.2f})x+({:.2f})'.format(slope,intercept),weight='bold')
 
 
-
-d = pd.read_csv(r"../Results_after_update2.csv")
+d = pd.read_csv(r"../../Results_after_update2.csv")
 df=pd.DataFrame(d)
 packages=[]
 #before=[]
@@ -44,11 +54,20 @@ for idx,row in df.iterrows():
     after.append(row[2])
 plt.plot([],[])
 p2=plt.scatter(packages, after, color='r',s=150,marker='2',label='Vulnerabilities after update')
-y = np.polyfit(packages, after, 1)
-p3 = np.poly1d(y)
-plt.plot(packages,p3(packages),"r--")
+#y = np.polyfit(packages, after, 1)
+#p3 = np.poly1d(y)
+#plt.plot(packages,p3(packages),"r--")
 plt.legend(loc='upper left', shadow=True, ncol=2,labelspacing=1.2,borderpad=1.0,prop={'size': 14})
 #leg.remove()
[…]

### 2020-06-23 paper.tex
structure modification 1

@@
 
+\renewcommand{\labelitemi}{$\textendash$}
 \title{Vulnerability Analysis of Container Images in Neuroimaging}
@@
 \begin{keywords}
-Containers; Vulnerabilities; Docker; Singularity; Neuroimaging.
+Containers; Docker; Singularity; Security; Vulnerabilities; Image Scanning; Outdated packages; Shrinking Images; Neuroimaging.
 \end{keywords}
@@
 Containers, which provide an operating system (OS) level virtualization, are
-popular. This is because they are lightweight, flexible, resource-efficient,
-provide fast development cycles, continuous delivery,
-and cost reduction of infrastructure. OS-level virtualization gained a lot of interest when Docker~\cite{docker19} was
-introduced in 2013~\cite{gantikow2016providing}. However, Docker has security concerns due to which it
-is not supported by High Performance
-Computing (HPC) environments. As a result, Singularity~\cite{singularity19} came in 2016 with the goal of providing support
-for HPC environments. It is used in many clusters including Compute Canada.
+popular. This is due to them being lightweight, flexible, and resource-efficient.
+Additionally, they are capable of providing fast development cycles and continuous delivery with the
+reduction of infrastructure cost~\cite{martin2018docker}. Containers are heavily utilised in various scientific fields,
+in particular, to run big data analysis. OS-level virtualization gained a lot of interest when Docker~\cite{docker19} was
+introduced in 2013. However, Docker is not supported by High Performance Computing (HPC)
+environments, mainly due to the fact that Docker user can act as superuser inside the container.
+As a result, Singularity~\cite{singularity19} was developed
+for scientific applications by keeping the focus on HPC environments. In addition, Singularity also solves some other security issues
+related to the architecture of Docker. It is used in many clusters including Compute Canada.
 According to~\cite{kurtzer2017singularity}, Singularity is used in 36 research clusters.
@@
 
-No doubt containers have gained a lot of popularity, however containers tightly
+Inspite of their popularity, containers tightly
 integrate with the host due to the sharing of the kernel, 
@@
 concerns.
-They also share three main security threats with other virtualization
-techniques~\cite{gantikow2016providing}:
+In fact, in relation to other virtualization techniques, they share three main security threats~\cite{gantikow2016providing}:
 
@@
 \textit{Privilege Escalation} A malicious attacker can break out of the container
-and gain control of the host system and other containers running on the same host.
-
-\textit{Denial-of-Service} One container may end up eating all the resources of the
-host hence resulting in the starvation of the host and other containers.
+and gain control of the host system and other containers running on the same host;
+
+\textit{Denial-of-Service} One container may end up consuming all the resources of the
+host, hence resulting in the starvation of the host and other containers;
 
@@
 
-However, two features of the Linux kernel, \textit{control groups} and \textit{namespaces},
-are used by containers to mitigate these threats to a certain extent. The security
-of containers is still the most concerning issue. According to a Forrester survey~\cite{bettini2015vulnerability}
-done in January 2015, security is the
-biggest concern while deploying containers.
-Containers are popular in various scientific fields, in particular to run Big Data analyses
-on HPC clusters. 
-However, deploying Docker container images on clusters raises security issues. Some security issues 
-that could possibly lead to privilege escalation, DoS or information leak. Some
-security issues are related to the architecture of Docker but have been 
-largely solved by Singularity.
-In fact, Singularity was developed for scientific applications
-by keeping the focus on HPC environments. Although, this work is of general interest,
-our particular focus in this paper is neuroimaging as containers are popularly used for scientific computing and data science
-in neuroscience.
-This popularity of containers in neuroscience leads us to the
-primary research question of this work: \textit{what is the current security state of
-neuroimaging container images that are deployed on HPC clusters?}
-
-To answer that question, we scan images that are used on Compute
-Canada clusters by the Neuroscience field. Scanning refers to the practice of
-collecting all information about the container image, investigating it
-for vulnerabilities, and finally producing a
-report to summarize scanning results. It is broadly categorized into
-two types: Static scanning and Dynamic scanning. The former scanning technique
-involves extracting information of an image without running it into a container,
-whereas the latter approach involves launching the container from the target image, and
-then scanning the running container.
-Here, we focus mainly on vulnerability scanning.
-Vulnerability is a weakness in the developer's software that can be exploited
-by the attacker to perform unauthorized actions on the target computer.
-In this paper, we report vulnerabilities that are present in
-container images, specifically used by neuroimaging field. Particularly,
-we aim to answer four primary research questions:
-
-\textit{RQ1:} Are vulnerabilities present inside neuroimaging container images that are
-deployed on HPC clusters?
-
-\textit{RQ2:} Can these vulnerabilities be reduced by updating the images?
-
-\textit{RQ3:} Can these vulnerabilities be reduced by shrinking the size of the images?
+In order to mitigate these threats, containers use some features of the Linux kernel
+such as \textit{control groups, namespaces}, etc. For instance, \textit{control groups}
+are used to restrict the amount of resources that a container can use. Nonetheless, container's
+security is still one of the concerning issues.
+%However, two features of the Linux kernel, \textit{control groups} and \textit{namespaces},
+%are used by containers to mitigate these threats to a certain extent. The security
+%of containers is still the most concerning issue. 
+According to a 2015 Forrester survey, security is the
+biggest concern when deploying containers~\cite{bettini2015vulnerability}.
+%Containers are popular in various scientific fields, in particular to run Big Data analyses
+%on HPC clusters. 
+%However, deploying Docker container images on clusters raises security issues. Some security issues 
+%that could possibly lead to privilege escalation, DoS or information leak. Some
+%Above mentioned threats are not the only security issues that containers may suffer.
+%Other security issues are related to the architecture of Docker but have been 
+%largely solved by Singularity.
+%In fact, Singularity was developed for scientific applications
+%by keeping the focus on HPC environments. Although, this work is of general interest,
+%our particular focus in this paper is neuroimaging as containers are popularly used for scientific computing and data science
+%in neuroscience.
+While containers still suffer general security problems that may affect any application using
+them, our particular focus in this research is the security of container images.
+In this research work, we aim to study and analyse the security of container images.
+Although this work, is of general interest and can be applied on any field, we focus in this
+paper on neuroimaging. This is due to the fact that containers are particulary popular in
+scientific computing and heavily utiilised in neuroscience, which makes it a good candidate
+for this research.
+This popularity of containers in neuroscience leads us to the following
+primary research question:
+
+\textit{RQ1: What is the current security state of
+neuroscience container images that are deployed on HPC clusters?}
+
+In fact, answering this question leads us to further questions as described below. 
+To answer our primary research question, we scan neuroscience images. The purpose
+of this scanning process is to collect information about the container images
+and then investigate these findings against security vulnerabilities.
+%we scan images that are used on Compute
+%Canada clusters by the Neuroscience field. Scanning refers to the practice of
+%collecting all information about the container image, investigating it
+%for vulnerabilities, and finally producing a
+%report to summarize scanning results. 
+It is broadly categorized into
+two types: \textit{Static} and \textit{Dynamic} scanning. The former
+involves extracting information of an image without running that image into a container,
+whereas the latter involves running a container with the target image.
+While scanning may provide different information, here, we focus mainly on security vulnerability.
+These types of vulnerabilities may be caused by an exploitable weakness in developer's software.
+Such exploitation may result in serious attacks such as gaining unauthorized access on the target
+computer, deletion of mounted files, etc. In this work, we target the detection of vulnerabilities
+that are present in neuroscience container images. It is further important to answer following three 
+secondary questions:
+%Vulnerability is a weakness in the developer's software that can be exploited
+%by the attacker to perform unauthorized actions on the target computer.
+%In this paper, we report vulnerabilities that are present in
+%container images, specifically used by neuroimaging field. Particularly,
+%we aim to answer four primary research questions:
+
+\textit{RQ2:} Can vulnerabilities be reduced by updating the images?
+
+\textit{RQ3:} Can vulnerabilities be reduced by shrinking the size of the images?
 
@@
 
-The existing research work on containers focuses mainly on the security of Docker
-containers.
-This focus is justified by the fact that containers expose the host's resources
-(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
-threat for the applications running on the same host. Previous studies evaluated
-the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
-and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
-Zerouali et al. in~\cite{zerouali2019relation} studied severity vulnerabilities and bugs in Docker 
-containers due to outdated packages.
-
-There are various image scanners available for scanning Docker images, for
-instance Anchore, CoreOS's Clair, etc.
-However, these scanners cannot be used to scan Singularity images due to different image formats.
-Therefore, Singularity came up with Stools~\cite{stools}, which can be used for scanning Singularity images
-for security and quality checks.
-
-This paper is organized as follows: in the next section, we provide description
-of materials and methods which summarize our experiments. We also explain different
-image scanners used to report
-vulnerabilities in container images. The next section of this paper provides the results, where we
-present a number of existing vulnerabilities in the container images
-used for data analysis on shared HPC clusters. We then proceed in the following section with 
-discussion and analysis of these results, where we provide more insight into the problems that 
-we faced while conducting these experiments. We also propose some
-particular rules that can be followed to secure container images. Finally, conclusions are drawn
-in the last section of the paper.
-
-\section{Materials and Methods}
-
-This study involves several image scanning experiments. To begin with,
-we scan the images as is to report the vulnerabilities
-inside the images. Updating and shrinking the size of these images is likely to play a role in vulnerabilities. Therefore, we
-update the images and then rescan all these
-images.
-Subsequently, we shrink the size of the images
-meaning that remove unnecessary packages from the images to see the effect on the number of
-vulnerabilities in the images.
-Lastly, we update and shrink the image size together and then
-rescan for the vulnerabilities.
-
-In this section, we provide
-insight
-into the container images and the image scanners that we used in our study.
-The image scanners refer to different Linux
-distributions/releases, which have different vulnerability data and is likely to
-create discrepancies in results. Therefore, in the last, this section presents a
-description of these varying Linux distributions/releases and their
-vulnerability databases.
-
+%%%%%%%%%Related Work%%%%%%%
+%The existing research work on containers focuses mainly on the security of Docker
+%containers.
+%This focus is justified by the fact that containers expose the host's resources
+%(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
+%threat for the applications running on the same host. Previous studies evaluated
+%the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
+%and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
+%Zerouali et al. in~\cite{zerouali2019relation} studied severity vulnerabilities and bugs in Docker 
+%containers due to outdated packages. 
+%
+%There are various image scanners available for scanning Docker images, for
+%instance Anchore, CoreOS's Clair, etc.
+%However, these scanners cannot be used to scan Singularity images due to different image formats.
+%Therefore, Singularity came up with Stools~\cite{stools}, which can be used for scanning Singularity images
+%for security and quality checks.
+
+This paper is organized as follows: in the next section, we provide a description
+of materials and tools, which we utilise throughout our experiments. We also present
+different image scanners used for vulnerability reporting in container images.
+The following section of this paper provides our approach and methodology, where we
+mainly examine the effect of image update and image reduction for the purpose
+of reducing vulnerabilities. Afterwards, we provide the results of our experiments,
+where we indicate a number of detected vulnerabilities in container images used for
+data analysis on shared HPC clusters. The last two sections provide a conclusion of this
+work following by a summary and an indication of our future work.
+
+%This paper is organized as follows: in the next section, we provide a description
+%of materials and methods which summarize our experiments. We also explain different
+%image scanners used to report
+%vulnerabilities in container images. The next section of this paper provides the results, where we
+%present a number of existing vulnerabilities in the container images
+%used for data analysis on shared HPC clusters. We then proceed in the following section with 
+%discussion and analysis of these results, where we provide more insight into the problems that 
+%we faced while conducting these experiments. We also propose some
+%particular rules that can be followed to secure container images. Finally, conclusions are drawn
+%in the last section of the paper.
+
+\section{Materials and Tools}
+
+Since the aim of this reseach work is to detect security vulnerabilities
+in container images and attempt to examine the effect of different
+manipulation of these images, it is needed to have sufficient number of
+images. Additionally, for the purpose of detecting vulnerabilities,
+utilization of image scanners is required. We utilize container
+images from two different containerization frameworks as well as
+various image scanners tools.
+
+%This study involves several image scanning experiments. To begin with,
+%we scan the images as is to report the vulnerabilities
+%inside the images. Updating and shrinking the size of these images is likely to play a role in vulnerabilities. Therefore, we
+%update the images and then rescan all these
+%images.
+%Subsequently, we shrink the size of the images
+%meaning that remove unnecessary packages from the images to see the effect on the number of
+%vulnerabilities in the images.
+%Lastly, we update and shrink the image size together and then
+%rescan for the vulnerabilities.
+%
+%In this section, we provide
+%insight
+%into the container images and the image scanners that we used in our study.
+%The image scanners refer to different Linux
+%distributions/releases, which have different vulnerability data and is likely to
+%create discrepancies in results. Therefore, in the last, this section presents a
+%description of these varying Linux distributions/releases and their
+%vulnerability databases.
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %As we are taking a particular use case of containers from
@@
 %\end{comment}
-\subsection{Container images}
-
-We scan a total of 44 container images taken from the BIDS
+\subsection{Container Images}
+
+We scan a total of 44 container images taken from two containerization frameworks
+used in neuroscience: BIDS
 apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}
-frameworks, two containerization frameworks used in neuroscience to share
-and re-use applications. Among the 27 BIDS apps \href{https://bids-apps.neuroimaging.io/apps/}
-{(https://bids-apps.neuroimaging.io/apps/)} available at the time of
-the study, we studied 26
-unique Docker images as one wasn't available on DockerHub. Among the 49
-Boutiques applications available at the time of the study, listed using
-Boutiques \texttt{bosh search} command, 23 unique container images were
-listed including 3 that couldn't be retrieved and 2 that were already
-included in BIDS apps. The resulting 18 images included 12 Docker images
+Out of these 44 images, 26 were obtained from BIDS apps
+\href{https://bids-apps.neuroimaging.io/apps/}{(https://bids-apps.neuroimaging.io/apps/)} 
+and 18 from Boutiques. In fact, at the time of the study, BIDS apps has 27 images,
+out of which one wasn't available on DockerHub. Boutiques has 49 images, listed using
+Boutiques \texttt{bosh search} command,
+however, only 23 unique were listed, out of which 3 couldn't be retrieved and 2
+we decided to ignore as they were already included in BIDS apps. All the final 26 images
+from BIDS apps are Docker images, whereas Boutiques contain 18 Docker images
 and 6 Singularity images.
+
+%Among the 27 BIDS apps \href{https://bids-apps.neuroimaging.io/apps/}
+%{(https://bids-apps.neuroimaging.io/apps/)} available at the time of
+%the study, we studied 26
+%unique Docker images as one wasn't available on DockerHub. Among the 49
+%Boutiques applications available at the time of the study, listed using
+%Boutiques \texttt{bosh search} command, 23 unique container images were
+%listed including 3 that couldn't be retrieved and 2 that were already
+%included in BIDS apps. The resulting 18 images included 12 Docker images
+%and 6 Singularity images.
 %\begin{figure}
@@
 
-We used four popular image scanners, namely Anchore~\cite{github_2019},
-Vuls~\cite{future-architect_2019}, Clair Scanner~\cite{arminc_2019} and
-Stools~\cite{stools}. Anchore, Vuls and Clair Scanner support Docker
-images while Stools supports Singularity. 
-To avoid discrepancies, we froze the vulnerability
-databases for these scanners on September 25, 2019.
+We use four popular image scanners, namely Anchore~\cite{github_2019},
+Vuls~\cite{future-architect_2019}, Clair-scanner~\cite{arminc_2019} and
+Stools~\cite{stools}. Anchore, Vuls and Clair-scanner support Docker
+images while Stools supports Singularity. Different vulnerabilities may be
+reported if scanning experiments take place on different dates.
+To avoid such discrepancies, we freeze the vulnerability
+databases used by these scanners as of 2019-09-25, when we initiate our
+experiments. This allows for a fair comparison between the scanners.
 
@@
 installed directly on the host and used to inspect images.
-In our experiments, we used a Docker image to get Anchore Engine version 0.5.0 and Database
-version 0.0.11.
+In our experiments, we use a Docker image in order to have access to Anchore Engine version 0.5.0 with the 
+Anchore vulnerability database version 0.0.11.
 
@@
 To get a vulnerability feed of various OS distribution, Anchore refers to
-different sources. For example, the Ubuntu launchpad database is used for Ubuntu.
+different sources, for instance, Ubuntu launchpad database to get
+vulnerability data related to Ubuntu.
 
@@
 Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
-It offers both static and dynamic scanning. In our experiments, we used
+It offers both static and dynamic scanning. In our experiments, we use
 it to dynamically scan containers.
 Using a dynamic scanning technique, it offers
-remote and local scans at the time of writing. The remote scan involves setting up only one machine, to
+remote and local scans at the time of writing. The remote scan sets up only one machine to
 which other target servers are connected via SSH. Local scan involves running
-the scan on the target server itself. Further, Vuls offer a fast scan, fast root scan,
-and deep scan mode.
+the scan on the target server itself. 
+%Further, Vuls offer a fast scan, fast root scan,
+%and deep scan mode.
 %The Fast scan is performed without root privileges, whereas a fast root scan is
@@
 
-In our experiments, we used Vuls Docker image having version 0.9.0 with fast scan mode.
+In our experiments, we use a Vuls Docker image having version 0.9.0. %with fast scan mode.
 Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
-The interesting point is that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
+It is worth noting that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
 meaning that images with these distributions are hard to scan with Vuls.
 
-\subsubsection{Clair Scanner}
-
-CoreOS originally created Clair, a static vulnerability scanner for containers. 
-\begin{comment}
-The main goal of the
-tool is to provide a transparent look of container’s security. Clair scans container images in regular
-intervals, and stores metadata of vulnerabilities, after getting from configured
-set of sources. 
-\end{comment}	
-Clair API can be used by clients to query its database to get
-the list of vulnerabilities that a particular image has. Clair sends a notification
-to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
-is a registry to store images privately, uses Clair internally as the security engine. However, Clair does not 
-provide the facility for comparing
-the vulnerability list of a particular image against a whitelist of vulnerabilities that you
-want to ignore~\cite{arminc_2019}. 
-So, to remove
-that drawback, another tool from CoreOS, Clair Scanner can be used. It scans the image, prepares the list of
+\subsubsection{Clair-scanner}
+
+Clair-scanner is a static vulnerability scanner for Docker containers.
+%CoreOS originally created Clair, a static vulnerability scanner for containers. 
+%The main goal of the
+%tool is to provide a transparent look of container’s security. Clair scans container images in regular
+%intervals, and stores metadata of vulnerabilities, after getting from configured
+%set of sources. 
+%Clair API can be used by clients to query its database to get
+%the list of vulnerabilities that a particular image has. Clair sends a notification
+%to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
+%is a registry to store images privately, uses Clair internally as the security engine. 
+%However, Clair does not 
+%provide the facility for comparing
+%the vulnerability list of a particular image against a whitelist of vulnerabilities that you
+%want to ignore~\cite{arminc_2019}. 
+%So, to remove
+%that drawback, another tool, Clair Scanner can be used. 
+It scans the image, prepares the list of
 vulnerabilities, compares that list against a whitelist, and flags vulnerabilities
 that are not present in the whitelist.
-Clair Scanner refers to the Ubuntu CVE tracker for getting Ubuntu vulnerability feed.
+Clair-scanner utilizes the Ubuntu CVE tracker to obtain  Ubuntu vulnerability feed.
 For that purpose, a Docker image is maintained that contains the Ubuntu CVE tracker database.
@@
 
-In our experiments, we used a Docker image (arminc/clair-local-scan:v2.0.6) for scanning
+In our experiments, we use a Docker image (arminc/clair-local-scan:v2.0.6) for scanning
 and an another Docker image (arminc/clair-db:latest) for the vulnerability database, which was
-last updated on 2019-09-18. We performed
-scanning on 2019-09-25. So, it means that Clair Scanner's database was already
-old by one week.
+last updated on 2019-09-18. We perform
+scanning on 2019-09-25.
 
@@
 
-Stools combines CoreOS's Clair Scanner with Continuous Integration (CI)
-for scanning Singularity images for vulnerabilities.
-Initially, Clair Scanner was intended to scan Docker images only. This tool does not fit well
-to scan Singularity images because of the different image formats.
-However, TravisCI and CircleCI are commonly used for testing code, and these
-services also offer running containers. Stools combined both these concepts.
-It involves spinning a Clair Scanner container during testing and building a
-Singularity image, and scanning it for filesystem before the image is finalized.
-
-In our experiments, we used a Docker image (\href{https://hub.docker.com/r/vanessa/stools-clair}{vanessa/stools-clair:v3.2.1})
-for scanning and followed the steps mentioned in \href{https://github.com/singularityhub/stools}{Stools Github}.
+Continuous Integration (CI) allows smaller code changes, fault isolations,
+faster release date, etc. Two types of CI are commonly used : TravisCI and
+CircleCI. The former targets open source projects that need to be tested in
+different environments, whereas the latter targets smaller projects where
+integration needs to be done as fast as possible. Stools uses CoreOS's Clair, which
+is used for Docker images, in combination with CI to allow scanning of
+Singularity images.
+%Stools combines CoreOS's Clair with Continuous Integration (CI)
+%for scanning Singularity images for vulnerabilities.
+%Initially, Clair was intended to scan Docker images only. This tool does not fit well
+%to scan Singularity images because of the different image formats.
+%However, TravisCI and CircleCI are commonly used for testing code, and these
+%services also offer running containers. Stools combined both these concepts.
+It involves spinning a Clair container during testing and building a
+Singularity image, and scanning it before the image is finalized.
+
+In our experiments, we use a Docker image (\href{https://hub.docker.com/r/vanessa/stools-clair}{vanessa/stools-clair:v3.2.1})
+following the steps mentioned in \href{https://github.com/singularityhub/stools}{Stools Github} for scanning
+Singularity images.
 
@@
 
-Image scanners report vulnerabilities differently depending on the different Linux release types.
-Therefore, we provide an overview of these Linux releases and scanners. 
+Through our experiments, we find that image scanners report vulnerabilities 
+differently depending on the different Linux release types. So, it is 
+important to provide an overview of these Linux releases types. 
 BIDS app and Boutiques images in our experiments have diverse Linux
-distributions such as Ubuntu, Centos, Debian, and Alpine. Further, a particular
-distribution have different releases in general. Here, we take Ubuntu's example
-to discuss its different releases and their vulnerability databases. We took Ubuntu's example
-because mostly images in our experiments have this distibution. However, other distributions also have
-similar release trend. In the case of Ubuntu, release
+distributions, such as Ubuntu, Centos, Debian, and Alpine. Further, a particular
+distribution has different releases in general. To illustrate, we here examine Ubuntu as an example,
+since it is heavily utilised in our experiments. However, other distributions also have
+similar release trend. Ubuntu releases
 can be of two types: Regular or Long Term Support (LTS).
@@
 ESM is a paid service that can be requested from Ubuntu to get security 
-updates even after the EOL of a particular Ubuntu release. The ESM support period is decided by
-Ubuntu. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
-data in vulnerability databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM, however, it still
+updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
+databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
 exists in LTS.
 
-For instance, Ubuntu has ended support for some releases such as 14.04 LTS,
-17.04, and 17.10, which means they have reached EOL. However, Ubuntu is providing optional extended support for Ubuntu 14.04.
-To use this extended support, users have to buy ESM release for Ubuntu 14.04.
-The images in our experiments have Ubuntu 14.04 LTS so scanners should refer
-to LTS release only while collecting data from vulnerability databases. If scanners refer to ESM release for 
-vulnerability data, it may lead to discrepancies in results.
-Also, if ubuntu release with ended support is used in images, there are no chances of getting updates, hence
-resulting in vulnerable images.
+As an example, Ubuntu has ended support for some releases, such as 14.04 LTS,
+17.04, and 17.10, as they reached EOL. However, Ubuntu decided to provide optional extended support for Ubuntu 14.04.
+To use this extended support, users have to purchase ESM release for Ubuntu 14.04.
+The images in our experiments have Ubuntu 14.04 LTS, so scanners should refer
+to LTS release only while collecting data from the vulnerability databases.
+More interestingly, scanners are able to refer to ESM release vulnerability database
+even without purchase, however, this may lead to discrepancies in results.
+%If scanners refer to ESM release for 
+%vulnerability data, it may lead to discrepancies in results.
+Further, if an image is using a Linux release where EOL has been reached that image may
+turns to be vulnerable as it is not possible to retrieve any updates.
+%Also, if ubuntu release with ended support is used in images, there are no chances of getting updates, hence
+%resulting in vulnerable images.
 
@@
 \newline\\
-The status can be any one of the following:
-
-\textbf{DNE:} It means 'Does Not Exist'. The package (inside the given release) does not exist in the
+For a given release, the status can be any one of the following:
+
+\textbf{DNE (Does Not Exist):} The package does not exist in the
 		archive.
 
-\textbf{needs-triage:} The vulnerability of this package (inside the given release)
-		is not known. It needs to be evaluated.  (No version/notes)
-
-\textbf{not-affected:} The package (inside the given release), while related to the
+\textbf{needs-triage:} The vulnerability of this package
+		is not known, and hence evaluation is needed.
+
+\textbf{not-affected:} The package, while related to the
 		CVE in some way, is not affected by the issue. Notes should
-		provide detailed information if needed. For e.g if the given
-		status is "not-affected (1.14.6-1.1)" then it indicates that this specific
-		package version in the given release is not affected.
-
-\textbf{needed:} The package (inside the given release) is vulnerable to the
+		provide detailed information, if needed. For instance, if the given
+		status is "not-affected (1.14.6-1.1)" then this indicates that this specific
+		package version is not affected.
+
+\textbf{needed:} The package is vulnerable to the
 		CVE and needs to be fixed.
 
-\textbf{active:} The package (inside the given release) is vulnerable to the
+\textbf{active:} The package is vulnerable to the
 		CVE, needs fixing, and is actively being worked on.
 
-\textbf{ignored:} The package (inside the given release), while related to the
+\textbf{ignored:} The package, while related to the
 		CVE in some way, is being ignored for some reason. The
-		notes should provide that reason. For e.g if status looks  like
-		"ignored (reached end-of-life)", this means that this given Ubuntu release already reached
-		end-of-life so this CVE is ignored by Ubuntu. However, if there
+		<notes> should provide that reason. For instance, if status looks like
+		"ignored (reached end-of-life)", this means that the given Ubuntu release already reached
+		end-of-life, so this CVE is ignored by Ubuntu. However, if there
 		is extended security support for this release then this
@@
 
-\textbf{pending:} The package (inside the given release) is vulnerable and
+\textbf{pending:} The package is vulnerable and
                   has been fixed but an update has not been yet uploaded or
-		  published. The package version that contains the fix is also
-		  along with the status.
-
-\textbf{deferred:} The package (inside the given release) is vulnerable, but 
-                   its fix has been deferred for some reason. The notes
-		   should provide further details. If a date is mentioned eg
-		   "deferred (2015-02-02)" this date specifies the date when
+		  published. The <version> is given to indicate the particular 
+		  version where the fix has been done.
+
+\textbf{deferred:} The package is vulnerable, but 
+                   its fix has been deferred for some reason. The <notes>
+		   should provide further details. If a date is mentioned, e.g.
+		   "deferred (2015-02-02)", the given date specifies the date when
 		   the CVE was deferred.
 
-\textbf{released:} The package (inside the given release) was vulnerable, but
-		an update has been already uploaded and published. The package version
-		is also mentioned. For e.g "released (1.2.3)"
-		specifies the package version in which the fix first appeared.
-
-\textbf{released-esm:} The package (inside the given release) was vulnerable and
+\textbf{released:} The package was vulnerable, but
+		an update has been already uploaded and published, e.g. "released (1.2.3)",
+		<version> indicates the first version where the fix was applied.
+
+\textbf{released-esm:} The package was vulnerable and
 		an update has been already uploaded and published. However,
 		this update is published in the Ubuntu ESM release only and not in LTS.
-		The fixed version of such packages is appended by
+		The fixed version of such packages is appended by either
 		+esm or \char`\~esm, indicating that this package version is available
@@
 
-\subsection{Image Update and Reduction Process}
-
-If there exist vulnerabilities in the container image, then we can
-run after updating the
-image. Updating the image involves updating all software packages that are
-inside that image. We used a bash script 
-(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/update/update.sh}{Github}) 
-to update all images, which checks the
-package manager present inside the image and then according to that it
-updates the image. However, this option affects the reproducibility
-of the image, which means that the image cannot be used to verify the research
-findings of other scientists.
-
-On the other hand, if we want to reduce the number of vulnerabilities without effecting the reproducibility of the image,
-image size reduction process is a good choice. The most obvious way of doing this is using 
+\section{Our Approach}
+
+In this section, we present our approach, where we attempt the reduction
+of security vulnerabilities in images by updating or
+shrinking these images.
+
+\subsection{Image Update Process}
+
+If vulnerabilities exist in the container images, then our first approach
+is to update these images in order to see the effects of such updates
+on the vulnerabilities.
+Updating an image involves updating all software packages that are
+inside that image. We use a 
+\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/update/update.sh}{bash script} 
+to update all images. That script checks the
+package manager, which is present inside the image, and updates the image
+accordingly. However, this action affects the reproducibility
+of that image. For example, if a package is used by a scientist to conduct an experiment
+and later that package is updated, other scientists want to reproduce initial results may actually
+get different results due to updates.
+%which means that the image cannot be used to verify the research
+%findings of other scientists.
+
+\subsection{Image Reduction/Minimization Process}
+On the other hand, if it is desired to reduce the number of vulnerabilities without affecting the reproducibility of the image,
+then we revert to image size reduction instead of image update. An interesting choice to do so would be to use 
 Neurodocker~\cite{neurodocker}.
-It traces and deletes unnecessary files.
-However, image scanners reports vulnerabilities according to the installed
-packages, whereas Neurodocker deals with the files only and list of installed packages remains same. Therefore, after
-minimization also scanners report same number of vulnerabilities.
-Hence, we need to reduce the number of packages
-installed in the image by deleting unnecessary packages. For that to happen, we need to first figure
-out which packages we need for the pipeline to function properly. We use
-Reprozip~\cite{rampin2016reprozip}, a tool that
-is used to make applications reproducible. It traces operating system calls used by the
-application while execution and then based on that it recognizes binaries, files, environment variables,
-and library dependencies that will be used by the application for future re-execution. If the OS is
+This tool traces and deletes unnecessary files.
+However, it does not affect the number of installed packages.
+Since image scanners report vulnerabilities according to the installed
+packages. Therefore, after
+minimization the same number of vulnerabilities is still reported.
+Consequently, we need to reduce the number of installed packages
+in the images by deleting unnecessary packages. For that, it is required to figure
+out which packages we need for the pipeline to function properly. To allow for that, we utilize
+Reprozip~\cite{rampin2016reprozip}, which is a tool that
+is used to make applications reproducible. This tool traces operating system calls used by the
+application while execution, and then based on this trace, it recognizes binaries, files, environment variables,
+and library dependencies that are used by the application for future re-execution. If the OS is
 Debian or RPM-based, Reprozip also
 uses an available package manager to acquire a list of distribution packages from where these files come from.
-So, we get a list of packages from Reprozip that are needed for the application execution. 
-After that, we expand this list by adding important and required packages that are essential
-for the system to function and finally figure out all the dependencies of these packages using Debtree
+So, a list of packages that are needed for the application re-execution is determined. Following that, the list
+is expanded by adding important and required packages that are essential
+for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
 ~\cite{debtree}.
-Ultimately, we keep these packages and remove remaining unnecessary packages. We use bash scripts
-(\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{Github}) for
-the image size reduction process, which installs Reprozip in the image, collects Reprozip trace, and
-finally deletes unnecessary packages.
-
-Finally, we combine both update and size reduction process
-to lessen the number of vulnerabilities.
-Therefore, in this process we first update all the packages in the image and then deletes
-the unnecessary packages. For this process we used the same scripts that
-we used for earlier experiments.
-
-\begin{comment}
-\subsection{CBRAIN}
-
-\href{http://github.com/aces/cbrain}{CBRAIN}~\cite{sherif2014cbrain} is a web portal that is
-used for the processing of distributed data on various storage locations of computing
-clusters. CBRAIN system deployed by Montreal Neurological Institute depends on the infrastructure
-delivered by Compute Canada~\cite{das2016mni}.
-It is also used by CONP to exploit services of Compute Canada. CBRAIN is a collaborative
-neuroimaging research platform that is active in production since 2009. CBRAIN
-provides transparent access to various distributed storage sites and computing
-resources across the world. CBRAIN’s infrastructure consists of three main
-layers, namely access layer, service layer, and infrastructure layer~\cite{sherif2014cbrain}. The access
-layer is for CBRAIN users, and can be accessed through any modern browser or
-RESTful API. The service layer consists of CBRAIN portal, which contains
-metadata and databases. It provides information about users, their permissions,
-resources etc. The infrastructure layer consists of data resources and computing
-resources, which are connected through a network. 
-CBRAIN supports Docker, Singularity, BIDS apps, and Boutiques.
-CBRAIN users uses a portal
-account on the cluster. Users are only able to
-run pre-defined applications on the cluster through the CBRAIN portal.
-\end{comment}
+Effectively all needed packages are kept and remaining unnecessary packages are removed. We use
+\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
+the image size reduction process, which install Reprozip in the image, collect Reprozip trace, and
+finally delete all unnecessary packages.
+
+Following the above two approaches, we employ a hybrid approach, where
+we combine both update and size reduction processes in an attempt to
+lessen number of vulnerabilities or to test the effect of
+combining two approaches. To allow for that, we first update all packages
+the image, then delete all unnecessary packages. Applying these processes in reverse
+may reduce the needed work; however this is not possible in all cases. For instance,
+some packages, such as apt-transport-https, are required to fetch updates, deleting these packages
+ahead of time will disallow the update process to take place.
+%Finally, we combine both update and size reduction process
+%to lessen the number of vulnerabilities.
+%Therefore, in this process we first update all the packages in the image and then deletes
+%the unnecessary packages. For this process we used the same scripts that
+%we used for earlier experiments.
+%\begin{comment}
+%\subsection{CBRAIN}
+%
+%\href{http://github.com/aces/cbrain}{CBRAIN}~\cite{sherif2014cbrain} is a web portal that is
+%used for the processing of distributed data on various storage locations of computing
+%clusters. CBRAIN system deployed by Montreal Neurological Institute depends on the infrastructure
+%delivered by Compute Canada~\cite{das2016mni}.
+%It is also used by CONP to exploit services of Compute Canada. CBRAIN is a collaborative
+%neuroimaging research platform that is active in production since 2009. CBRAIN
+%provides transparent access to various distributed storage sites and computing
+%resources across the world. CBRAIN’s infrastructure consists of three main
+%layers, namely access layer, service layer, and infrastructure layer~\cite{sherif2014cbrain}. The access
+%layer is for CBRAIN users, and can be accessed through any modern browser or
+%RESTful API. The service layer consists of CBRAIN portal, which contains
+%metadata and databases. It provides information about users, their permissions,
+%resources etc. The infrastructure layer consists of data resources and computing
+%resources, which are connected through a network. 
+%CBRAIN supports Docker, Singularity, BIDS apps, and Boutiques.
+%CBRAIN users uses a portal
+%account on the cluster. Users are only able to
+%run pre-defined applications on the cluster through the CBRAIN portal.
+%\end{comment}
 \section{Results}
@@
 In this section,
-we first discuss the existing vulnerabilities in the images and compare the
-results of the three scanners. We then discuss the effect of the update on the
-existing vulnerabilities followed by the results of the image size reduction
-process. Lastly, this section presents the combined effect of update and image size reduction on the
-vulnerabilities.
+we first discuss our detected vulnerabilities in the images, using the three scanners, and compare the
+results. We then discuss the effect of the image updating/minimizing and applying the hybrid
+approach on the detected vulnerabilities.
+Lastly, we do an analysis of obtained results and explain the reasons behind our
+findings.
 
@@
 
-Table~\ref{table1} shows the number of vulnerabilities present in the images,
-which are detected by the scanners.
-It is important to note that results have major discrepancies. In particular,
-Anchore reports far more different results than Vuls and Clair resulting in 
+Table~\ref{table1} shows the number of detected vulnerabilities in the different images,
+detected by each of the scanners.
+Interestingly, our experiments concluded considerable discrepancies in the results obtained by
+these scanners. In particular, in most cases,
+Anchore reports more vulnerabilities than Vuls and Clair-scanner resulting in 
 the Jaccard coefficient of 0.59 with both,
-whereas Vuls and Clair share more common vulnerabilities resulting to the Jaccard coefficient of 0.83.
-
-Figure~\ref{fig:graph1} gives more image-specific information.
+whereas Vuls and Clair-scanner share more common vulnerability detection resulting to the Jaccard coefficient of 0.83.
+
+Figure~\ref{fig:graph1} provides more image-specific information.
 It represents the number of vulnerabilities that are present inside images.
-The overall trend of the Figure shows that as the number of packages increases in the image, the number of vulnerabilities
+The overall trend shows that as the number of packages increases in the image, the number of vulnerabilities
 also get increased.
-The figure also infers that Alpine distribution, being the
-lightweight distribution, have the least number of vulnerabilities, whereas Ubuntu contains more packages and hence report more vulnerabilities.
-We also analyzed that out of the total Docker images scanned in our experiment, Debian reported more critical vulnerabilties than others, reaching
-up to 180.
+The figure also infers that Alpine distribution, being a
+lightweight distribution, has the least number of vulnerabilities, whereas more vulnerabilities are reported for
+Ubuntu as it contains more packages.
+We also analyze that out of the total Docker images scanned by our experiments, Debian reports more high vulnerabilties, as
+classified by databases, than others.
 %\begin{table*}
@@
 
-Figure~\ref{fig:venn} represents the number of common and different vulnerabilities
-that are shown by scanners.
-
-we get total 20050 vulnerabilities in BIDS apps and Boutiques images.
+Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
+the scanners and the overlap between them.
+
+We find a total of 20,050 vulnerabilities in BIDS apps and Boutiques images.
 It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
-reported by Anchore, 673 reported only by Clair, and 325 detected only by Vuls.
-
-As the number and type of vulnerabilities reported by the three scanners are drastically different from each other,
-it was interesting to investigate the reasons for these differences.
+reported by Anchore, 673 by Clair, and 325 by Vuls.
+
+As the number and type of vulnerabilities reported by the three scanners are significantly different from each other,
+we desire to investigate the reasons behind these differences.
 %these scanners report different numbers and types of vulnerabilities.
@@
 
-According to our investigation of these results, below are some of the reasons for
-getting different results from these scanners. At the time of writing, these reasons include
-some scanners ignoring vulnerabilities in Linux-Kernel header packages, scanners referring to different databases,
-how frequently they are updating their databases, and bugs in scanners, etc.
-
-We explain these differences below in detail
-and provide an example with each reason to make it clear.
-
-\begin{comment}
-Venn Diagram~\ref{fig:venn} illustrates that Anchore reports 4453 different vulnerabilities that are reported
-by Vuls and Clair. Out of this 4443 vulnerabilities are present in linux-kernel-headers. These are ignored by
-both Clair and Vuls.
-\end{comment}
-
-\textbf{Linux-Kernel-Headers:} Clair Scanner and Vuls are ignoring all vulnerabilities in the Linux-kernel-headers,
-whereas Anchore reports them all.
-4443 out of 4453 vulnerabilities that are only reported by Anchore are present in Linux-kernel-headers.
+Following our investigation, we are able to explain some of the reasons behind
+the differences. 
+Such reasons were resulted from the way these scanners function or behave 
+in particular, the following actions by the scanners are indicative:
+\begin{itemize}
+   \item scanners ignoring vulnerabilities in Linux-kernel-header packages,
+   \item scanners referring to different vulnerability databases,
+   \item different frequency of updating their databases,
+   \item bugs in scanners. 
+\end{itemize}
+
+Below, we explain these reasons in further details and provide examples
+for clear illustrations.
+%these reasons include
+%some scanners ignoring vulnerabilities in Linux-Kernel header packages, scanners referring to different databases,
+%how frequently they are updating their databases, and bugs in scanners, etc. 
+%We explain these differences below in detail
+%and provide an example with each reason to make it clear.
+%
+%\begin{comment}
+%Venn Diagram~\ref{fig:venn} illustrates that Anchore reports 4453 different vulnerabilities that are reported
+%by Vuls and Clair. Out of this 4443 vulnerabilities are present in linux-kernel-headers. These are ignored by
+%both Clair and Vuls.
+%\end{comment}
+
+\textbf{Linux-kernel-headers:} Clair-scanner and Vuls are ignoring all vulnerabilities in the Linux-kernel-headers,
+whereas Anchore reports all of them.
+We find that 4443 out of 4453 vulnerabilities that are only reported by Anchore are present in Linux-kernel-headers.
 For example CVE-2019-9506 present in Linux-libc-dev-4.4.0-31.50, which is reported by Anchore, is not
-detected by both Vuls and Clair Scanner.
-Linux-kernel-headers are the headers files that only provide function names, its parameters, and its
-return type.
+detected by both Vuls and Clair-scanner.
+Linux-kernel-headers are the headers files that only provide function names, their parameters, and their
+return types.
 The actual source code of these functions is present in the Linux kernel and is not inside the image.
@@
 as "not-affected" in the vulnerability database. It means Linux distribution which is inside the image is not affected
-by the particular CVE. In other words, Vuls is reporting vulnerabilities that it should not have reported.
-For example, we scanned an image having the Trusty release in it and Vuls is reporting CVE-2015-2305
-in the package Cups. However, if we check the vulnerability database, package Cups in Trusty is not
+by the particular CVE. In other words, Vuls is reporting vulnerabilities that it should not have been reported.
+For example, we scan an image having the Trusty release in it and Vuls is reporting CVE-2015-2305
+in the package Cups. However, upon checking the vulnerability database, we find that package Cups in Trusty is not
 affected by this CVE.
@@
 Some vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life. 
-However, in Ubuntu 14.04 ESM release these vulnerabilities may or may not be present.
+However, in Ubuntu 14.04 ESM release, these vulnerabilities may or may not be present.
 Anchore checks the last status of these vulnerabilities whether the package was vulnerable to the CVE
-prior to the end-of-life. If it was vulnerable only then Anchore will report it, otherwise not.
-If this kind of vulnerability is present in ESM release then Clair Scanner will report it because Clair Scanner
+prior to the end-of-life. Only if it was vulnerable, Anchore reports it, otherwise it does not.
+If this kind of vulnerability is present in ESM release then Clair-scanner reports it because it
 only refers to ESM release. On the other hand, if the vulnerability
-status in ESM release is "DNE" (Does Not Exist), then Clair Scanner will not report it. 
-For example CVE-2017-9994 vulnerability in Libav package is ignored in Trusty LTS release due to end-of-life.
-so it is not reported by Anchore. Whereas, this vulnerability has status as "DNE" in Trusty ESM
-release so Clair Scanner also does not report it. As Ubuntu 14.04 LTS release is present inside the images still
-Clair Scanner is referring to Ubuntu 14.04 ESM release vulnerability database.
+status in ESM release is "DNE" (Does Not Exist), then Clair-scanner does not report it. 
+For example, CVE-2017-9994 vulnerability in Libav package is ignored in Trusty LTS release due to end-of-life.
+Consequently, it is not reported by Anchore. This vulnerability has status as "DNE" in Trusty ESM
+release so Clair-scanner also does not report it. As Ubuntu 14.04 LTS release is present inside the images,
+Clair-scanner still refers to Ubuntu 14.04 ESM release vulnerability database, which is incorrect.
 
@@
 \textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
-are not detected by Clair Scanner but they affect Ubuntu 14.04 LTS hence detected by Vuls. For example, CVE-2017-1375.
-
-\textbf{False negatives by Clair:} Clair is missing vulnerabilities that it should detect. For example, CVE-2016-9082 
-is present in package Cairo in Xenial release and it is not detected by Clair.
-
-\textbf{False positives by Clair:} These vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
-present inside the image but Clair is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
-Clair is only referring to Ubuntu 14.04 ESM release. For example CVE-2019-1274. The reasons of Clair showing
-false positives and false negatives are unclear. We reported this issue on two Google groups of Clair i.e CoreOS Dev and
-clair-dev \href{https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc}{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}
-
-\textbf{Database difference:} As we discussed earlier that Clair Scanner's database was old by one week.
-                So some of the vulnerabilities were not updated yet. For example, CVE-2019-5094, which
+are not detected by Clair-scanner but they affect Ubuntu 14.04 LTS, and hence detected by Vuls. The CVE-2017-1375 is an example
+of such vulnerabilities.
+
+\textbf{False negatives:} False negative reporting is detected. Clair-scanner and Vuls
+are missing vulnerabilities that they should have detected. For example, the CVE-2016-9082 
+is present in package Cairo in Xenial release and it is not detected by Clair-scanner.
+Vuls is also missing vulnerabilities such as CVE-2019-5094.
+
+\textbf{False positives:} False positive reporting is also detected. For instance,
+there are false positives in clair-scanner.
+Some vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
+present inside the image, however, Clair-scanner have reported such vulnerabilities.
+For instance, CVE-2019-1274 is an example of such vulnerabilities. 
+%is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
+%Clair is only referring to Ubuntu 14.04 ESM release. 
+%The reasons of Clair showing
+%false positives and false negatives are unclear. We reported this issue on two Google groups of Clair i.e CoreOS Dev and
+%clair-dev \href{https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc}{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}
+
+\textbf{Database difference:} At the time we pulled Clair-scanner's database, it was one week old.
+                              As a result some vulnerabilities were not updated. For instance, CVE-2019-5094, which
 		              was published on 2019-09-24, was not 
-		updated in Clair Scanner's database at that time. Due to which it is missed by Clair Scanner.
+		              updated in Clair-scanner's database. Due to which it is missed by Clair-scanner.
+			      Consequently, these discrepancies, even small, are sufficient to change the detection of
+			      the scanners.
 
@@
 		detected by Anchore due to the presence of epoch in the Procps package version.
-		We reported this bug to the team through the slack channel.
+		We reported this bug to the Anchore development team through their Slack channel.
 
@@
 		vulnerabilities that have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
-		However, if this vulnerability is present in Ubuntu 14.04 ESM release it is detected by Clair. 
-		For example CVE-2019-13565 in Ubuntu 14.04. We reported this bug as well through slack
+		However, if this vulnerability is present in Ubuntu 14.04 ESM release, it is detected by Clair-scanner. 
+		For instance, CVE-2019-13565, which is present in Ubuntu 14.04, is an example of such vulnerabilities. 
+		We reported this bug as well to the Anchore development team through their Slack
 		channel.
 
-\textbf{False Negatives by Vuls:} Vuls is missing some of the vulnerabilities that it should detect. 
-		For example CVE-2019-5094 vulnerability.
-
-\textbf{Rejected CVEs:} There are some CVE that are rejected because they are duplicate copies of other CVEs. 
-	So Anchore is not reporting those rejected CVEs but Vuls is reporting those. For example CVE-2017-13753.
+\textbf{Rejected CVEs:} There are some CVEs, such as CVE-2017-13753, that are rejected because they are duplicate copies of other CVEs. 
+	So, Anchore is not reporting those rejected CVEs, but Vuls is reporting them.
 %\begin{table*}
@@
 %\end{table*}
-\subsection{Effect Of Update}
 %\begin{comment}
@@
 
-As the effect of update,
-scanning results changed drastically. However, there are still
-vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
-to date.
+\subsection{Effect Of Update}
+As a result of image updating,
+scanning results change significantly.
+%However, there are still
+%vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
+%to date.
 %\begin{comment}
@@
 Figure~\ref{fig:graph2} represents the number of vulnerabilities that are detected by Anchore before and after 
-the update of these images. 
+image update. 
 %In fact, this figure depicts an additional results of update to the original Figure~\ref{fig:graph1}.
-In fact, this image combines the original results of Figure~\ref{fig:graph1} with the results of the update
+In fact, this Figure combines the original results of Figure~\ref{fig:graph1} with the results of the image update
 experiment.
-Clearly, the figure illustrates that after the update, the number of vulnerabilities reduces by a
-significant number. Furthermore, a mild slope of vulnerabilities after the update shows that
-there is a set of packages that contain vulnerabilities and have no fix yet. Also, these
-vulnerabilities mostly have \textit{Low, Negligible, or Medium} severity status meaning that
-critical vulnerabilities are patched with high priority.
+Clearly, the figure illustrates that when image are updated, the number of vulnerabilities reduces by a
+significant number. Furthermore, a mild slope of vulnerabilities after the image update shows that
+there is a set of packages that contain vulnerabilities and have not been fixed yet. Also, these
+vulnerabilities mostly have \textit{Low, Negligible, or Medium} severity status, meaning that
+high vulnerabilities are prioritised and fixed fast.
 Besides that, it is also interesting to note that some images in Figure~\ref{fig:graph2}
 do not have update results. This is because some Linux distributions reached end-of-life and
-are not getting updates anymore.
+are not being updated anymore.
+Despite of the significant drop in the number of vulnerabilities as a result of image updating,
+there is still a number of vulnerabilities reported by the scanners. There is due to the
+vulnerabilities which do not have fix yet.
 
@@
 
-Our third experiment involves deleting unnecessary packages from the images.
-We did this experiment on five images because the reduction process may take
-several hours because it requires 
-a pipeline to run in the image, which takes time. We noticed that
-after the size reduction process, the scanning results deviate a little from our initial expectation.
-At first, we thought that we will have a notable effect of size reduction on
-vulnerabilities. However, this is not the case always. The bar graph shown in
-Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
-\textit{poldracklab/fmriprep:1.2.3} have an insignificant effect of size reduction.
-According to our analyzes here, this can be due to two reasons: \rom{1}) the number
-and \rom{2}) the kind of packages that we deleted. In other
+Our second approach involves the deletion of unnecessary packages from the images.
+We tested our approach on 5 different images. We find that
+after the size reduction process, sometimes the scanning results deviate only a little from the results
+without minimization. While the minimization process results in significant reduction
+in the number of vulnerabilities in some cases, we find that in other cases the effect
+is negligible. In other words, the image reduction was inconsistent.
+%At first, we thought that we will have a notable effect of size reduction on
+%vulnerabilities. However, this is not the case always. The bar graph shown in
+%Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
+%\textit{poldracklab/fmriprep:1.2.3} have an insignificant effect of size reduction.
+According to our analyses, this can be due to two reasons: \rom{1}) the number of
+deleted packages
+and \rom{2}) the kind of deleted packages. 
+For an instance, if the deletion is for a package that includes a lot of vulnerabilities,
+that particular deletion naturally results in the drop of number of vulnerabilities.
+In other
 words, deleting more packages reduces more vulnerabilities. 
@@
 
-\subsection{Discussion}
+\section{Conclusions}
 
@@
 
-\subsection{Conclusions and Future Work}
+\section{Summary and Future Work}
 

### 2020-06-23 paper.tex
Rewrote introduction

@@
 
+\begin{abstract}
+	\tristan{Abstract goes here}
+\end{abstract}
+
 \begin{keywords}
-Containers; Docker; Singularity; Security; Vulnerabilities; Image Scanning; Outdated packages; Shrinking Images; Neuroimaging.
+Containers; Docker; Singularity; Security Vulnerabilities; Neuroimaging.
 \end{keywords}
@@
 
-Containers, which provide an operating system (OS) level virtualization, are
-popular. This is due to them being lightweight, flexible, and resource-efficient.
-Additionally, they are capable of providing fast development cycles and continuous delivery with the
-reduction of infrastructure cost~\cite{martin2018docker}. Containers are heavily utilised in various scientific fields,
-in particular, to run big data analysis. OS-level virtualization gained a lot of interest when Docker~\cite{docker19} was
-introduced in 2013. However, Docker is not supported by High Performance Computing (HPC)
-environments, mainly due to the fact that Docker user can act as superuser inside the container.
-As a result, Singularity~\cite{singularity19} was developed
-for scientific applications by keeping the focus on HPC environments. In addition, Singularity also solves some other security issues
-related to the architecture of Docker. It is used in many clusters including Compute Canada.
-According to~\cite{kurtzer2017singularity}, Singularity is used in 36 research clusters.
-
-\begin{comment}
-\begin{figure}
-  \centering
-  \includegraphics[width=\columnwidth]{Figures/cluster_list.png}
-	\caption{List of HPC clusters using Singularity~\cite{kurtzer2017singularity}.}
-	\label{fig:cluster_list}
-\end{figure}
-\end{comment}
-
-Inspite of their popularity, containers tightly
-integrate with the host due to the sharing of the kernel, 
-mounted file systems, and devices, which raises security
-concerns.
-In fact, in relation to other virtualization techniques, they share three main security threats~\cite{gantikow2016providing}:
-
-\begin{comment}
-\begin{figure}
-  \centering
-  \includegraphics[width=.7\columnwidth]{Figures/container.png}
-  \caption{Architecture of Container-based
-                Virtualization.}
-  \label{fig:container-overview}
-\end{figure}
-\end{comment}
-\textit{Privilege Escalation} A malicious attacker can break out of the container
-and gain control of the host system and other containers running on the same host;
-
-\textit{Denial-of-Service} One container may end up consuming all the resources of the
-host, hence resulting in the starvation of the host and other containers;
-
-\textit{Information Leak} Private data of the host and other containers could be
-leaked and can be used for further attacks.
-
-In order to mitigate these threats, containers use some features of the Linux kernel
-such as \textit{control groups, namespaces}, etc. For instance, \textit{control groups}
-are used to restrict the amount of resources that a container can use. Nonetheless, container's
-security is still one of the concerning issues.
-%However, two features of the Linux kernel, \textit{control groups} and \textit{namespaces},
-%are used by containers to mitigate these threats to a certain extent. The security
-%of containers is still the most concerning issue. 
-According to a 2015 Forrester survey, security is the
-biggest concern when deploying containers~\cite{bettini2015vulnerability}.
-%Containers are popular in various scientific fields, in particular to run Big Data analyses
-%on HPC clusters. 
-%However, deploying Docker container images on clusters raises security issues. Some security issues 
-%that could possibly lead to privilege escalation, DoS or information leak. Some
-%Above mentioned threats are not the only security issues that containers may suffer.
-%Other security issues are related to the architecture of Docker but have been 
-%largely solved by Singularity.
-%In fact, Singularity was developed for scientific applications
-%by keeping the focus on HPC environments. Although, this work is of general interest,
-%our particular focus in this paper is neuroimaging as containers are popularly used for scientific computing and data science
-%in neuroscience.
-While containers still suffer general security problems that may affect any application using
-them, our particular focus in this research is the security of container images.
-In this research work, we aim to study and analyse the security of container images.
-Although this work, is of general interest and can be applied on any field, we focus in this
-paper on neuroimaging. This is due to the fact that containers are particulary popular in
-scientific computing and heavily utiilised in neuroscience, which makes it a good candidate
-for this research.
-This popularity of containers in neuroscience leads us to the following
-primary research question:
-
-\textit{RQ1: What is the current security state of
-neuroscience container images that are deployed on HPC clusters?}
-
-In fact, answering this question leads us to further questions as described below. 
-To answer our primary research question, we scan neuroscience images. The purpose
-of this scanning process is to collect information about the container images
-and then investigate these findings against security vulnerabilities.
-%we scan images that are used on Compute
-%Canada clusters by the Neuroscience field. Scanning refers to the practice of
-%collecting all information about the container image, investigating it
-%for vulnerabilities, and finally producing a
-%report to summarize scanning results. 
-It is broadly categorized into
-two types: \textit{Static} and \textit{Dynamic} scanning. The former
-involves extracting information of an image without running that image into a container,
-whereas the latter involves running a container with the target image.
-While scanning may provide different information, here, we focus mainly on security vulnerability.
-These types of vulnerabilities may be caused by an exploitable weakness in developer's software.
-Such exploitation may result in serious attacks such as gaining unauthorized access on the target
-computer, deletion of mounted files, etc. In this work, we target the detection of vulnerabilities
-that are present in neuroscience container images. It is further important to answer following three 
-secondary questions:
-%Vulnerability is a weakness in the developer's software that can be exploited
-%by the attacker to perform unauthorized actions on the target computer.
-%In this paper, we report vulnerabilities that are present in
-%container images, specifically used by neuroimaging field. Particularly,
-%we aim to answer four primary research questions:
-
-\textit{RQ2:} Can vulnerabilities be reduced by updating the images?
-
-\textit{RQ3:} Can vulnerabilities be reduced by shrinking the size of the images?
-
-\textit{RQ4:} What is the effect of both updating
-and shrinking image size on vulnerabilities?
-
-%%%%%%%%%Related Work%%%%%%%
-%The existing research work on containers focuses mainly on the security of Docker
-%containers.
-%This focus is justified by the fact that containers expose the host's resources
-%(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
-%threat for the applications running on the same host. Previous studies evaluated
-%the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis},
-%and have scanned vulnerabilities on Docker hub images~\cite{Shu2017, gummaraju2015over}.
-%Zerouali et al. in~\cite{zerouali2019relation} studied severity vulnerabilities and bugs in Docker 
-%containers due to outdated packages. 
-%
-%There are various image scanners available for scanning Docker images, for
-%instance Anchore, CoreOS's Clair, etc.
-%However, these scanners cannot be used to scan Singularity images due to different image formats.
-%Therefore, Singularity came up with Stools~\cite{stools}, which can be used for scanning Singularity images
-%for security and quality checks.
-
-This paper is organized as follows: in the next section, we provide a description
-of materials and tools, which we utilise throughout our experiments. We also present
-different image scanners used for vulnerability reporting in container images.
-The following section of this paper provides our approach and methodology, where we
-mainly examine the effect of image update and image reduction for the purpose
-of reducing vulnerabilities. Afterwards, we provide the results of our experiments,
-where we indicate a number of detected vulnerabilities in container images used for
-data analysis on shared HPC clusters. The last two sections provide a conclusion of this
-work following by a summary and an indication of our future work.
+% Containers are popular on HPC, in particular Singularity
+Software containers have emerged has an efficient solution to deploy
+scientific data analyses on High Performance Computing (HPC) clusters, due
+to their portability, ease of use, and limited overhead. The
+Singularity~\cite{kurtzer2017singularity} framework is often preferred to
+Docker\footnote{\url{http://docker.com}} on HPC clusters, due to its
+secure handling of multi-user environments, and its convenient support for
+Docker images. Singularity is now available in dozens of HPC
+clusters around the globe, and used routinely for Big Data analyses.
+
+% Containers are meant to isolate applications from the host, but security remains an issue
+Using core features of the Linux kernel such as namespaces, control groups
+and chroot, containers isolate processes from the
+host computer,  
+and control the memory, CPU, network and file-system resources assigned to
+them. However, containers still share the kernel, mounted file systems and
+some devices with the host, which raises potential security issues. In
+particular, privilege escalation, denial of service and information leak
+are always plausible~\cite{gantikow2016providing}. Therefore, security remains 
+an important concern when deploying containers~\cite{bettini2015vulnerability}.
+
+% Container images, our study
+This study is a vulnerability analysis of container images used in HPC
+clusters. Container images contain complete operating-system distributions,
+including the data analysis software and its required dependencies.
+Images are rarely updated, as they are often built once
+for the entire duration of an analysis, to avoid results perturbations
+coming from software updates~\cite{gronenschild, glatard2015}. Images also
+commonly include more dependencies than required by a specific analysis, to 
+enable reusability across experiments.
+
+Our research questions are the following:
+
+\textit{RQ1: What is the current amount of known vulnerabilities in
+container images deployed on HPC clusters?} Vulnerabilities are possible
+attack vectors that may seriously compromise the security of HPC clusters
+and the integrity of user data. We report vulnerability analyses produced
+by four popular image scanning tools, Anchore, Vuls, Clair and Stools.
+
+\textit{RQ2: Can the amount of vulnerabilities be reduced by updating the images?}  
+For many reasons related to reproducibility and the life-cycle of research
+projects, container images deployed on HPC clusters often include outdated
+software. We report on the effect of software updates on the vulnerability
+analysis of RQ1.
+
+\textit{RQ3: Can the amount of vulnerabilities be reduced by shrinking the images?} 
+Container images often include more software packages than required for a
+typical analysis. We report on the impact of this additional software on
+the presence of vulnerabilities.
+
+We answer these questions taking the particular example of neuroimaging, a
+domain that has entered the Big Data era as many other
+ones~\cite{vanhorn-toga}. We focus on the analysis of container images
+present in BIDS apps~\cite{xxx} and Boutiques~\cite{xxx}, two containerized
+application frameworks commonly used in neuroimaging.
+
+The next section describes the materials and tools used in the experiments,
+including image scanners and container images. We then describe our image
+update and shrinking methodology to reduce vulnerabilities. Results review
+the detected vulnerabilities in container images, explain observed
+discrepancies between scanners, and report on the efficiency of image
+update and size reduction. As a conclusion, we provide a set of image
+creation guidelines for a secure deployment on HPC clusters.
 
@@
 
+\section{Discussion}
+
+% Would the results apply to other domains than neuroimaging
+
 \section{Conclusions}

### 2020-06-30 paper.tex
added abstract

@@
 \begin{abstract}
-	\tristan{Abstract goes here}
+
+Today, containers, which provide operating system level virtualization, are
+popular. Correspondingly, they are widely used for scientific data analyses on 
+High Performance Computing (HPC) clusters. However, the security of containers
+still remains the concerning issue. Here, we focus on the security of container
+images in particular. Container images are often built for the entire
+duration of an analysis, so scientific researchers do not prefer to update
+them. Consequently, their chances of containing vulnerabilities increases.  
+In this study, we analyze vulnerabilities in container images used in 
+HPC clusters.
+We conduct two different
+experiments, image update and image shrinking, to report the effect 
+on the number of vulnerabilities.
+
 \end{abstract}
@@
 for the entire duration of an analysis, to avoid results perturbations
-coming from software updates~\cite{gronenschild, glatard2015}. Images also
+coming from software updates~\cite{gronenschild2012effects, glatard2015reproducibility}. Images also
 commonly include more dependencies than required by a specific analysis, to 
@@
 and the integrity of user data. We report vulnerability analyses produced
-by four popular image scanning tools, Anchore, Vuls, Clair and Stools.
+by four popular image scanning tools, Anchore, Vuls, Clair-scanner and Stools.
 
@@
 domain that has entered the Big Data era as many other
-ones~\cite{vanhorn-toga}. We focus on the analysis of container images
-present in BIDS apps~\cite{xxx} and Boutiques~\cite{xxx}, two containerized
+ones~\cite{van2014human}. We focus on the analysis of container images
+present in BIDS apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}, two containerized
 application frameworks commonly used in neuroimaging.
@@
 It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
-reported by Anchore, 673 by Clair, and 325 by Vuls.
+reported by Anchore, 673 by Clair-scanner, and 325 by Vuls.
 
@@
 
+% Would the results apply to other domains than neuroimaging
+
 \section{Discussion}
 
-% Would the results apply to other domains than neuroimaging
-
-\section{Conclusions}
-
 As we noticed that none of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
-so many are critical vulnerabilities as well. Yet there is not a single image scanner on which we can rely upon for
+so many are high vulnerabilities as well. Yet there is not a single image scanner on which we can rely upon for
 scanning. Additionally, we cannot update all images because some OS releases, which are used inside images, 
@@
 
-\section{Summary and Future Work}
+\section{Conclusions and Future Work}
 

### 2020-06-30 Scripts/graphs/drawVenn.py

@@ -3,7 +3,7 @@ import numpy as np
 from matplotlib_venn import venn3, venn3_circles
  
 # Make a Basic Venn
-v = venn3(subsets=(1, 1, 1, 1, 1, 1, 1), set_labels = ('Anchore', 'Clair', 'Vuls'))
+v = venn3(subsets=(1, 1, 1, 1, 1, 1, 1), set_labels = ('Anchore', 'Clair-scanner', 'Vuls'))
  
 # Custom it
 v.get_label_by_id('100').set_text('4453')

### 2020-06-30 paper.tex
Comments and edits in section II

@@
 
+\todo{Add related work on vulnerability scanning}
+
 \section{Materials and Tools}
 
-Since the aim of this reseach work is to detect security vulnerabilities
+Since the aim of this research work is to detect security vulnerabilities
 in container images and attempt to examine the effect of different
-manipulation of these images, it is needed to have sufficient number of
+manipulation of these images, it is needed to have a representative set
 images. Additionally, for the purpose of detecting vulnerabilities,
 utilization of image scanners is required. We utilize container
-images from two different containerization frameworks as well as
-various image scanners tools.
+images from two popular application frameworks, as well as
+four of the main image scanners.
 
-%This study involves several image scanning experiments. To begin with,
-%we scan the images as is to report the vulnerabilities
-%inside the images. Updating and shrinking the size of these images is likely to play a role in vulnerabilities. Therefore, we
-%update the images and then rescan all these
-%images.
-%Subsequently, we shrink the size of the images
-%meaning that remove unnecessary packages from the images to see the effect on the number of
-%vulnerabilities in the images.
-%Lastly, we update and shrink the image size together and then
-%rescan for the vulnerabilities.
-%
-%In this section, we provide
-%insight
-%into the container images and the image scanners that we used in our study.
-%The image scanners refer to different Linux
-%distributions/releases, which have different vulnerability data and is likely to
-%create discrepancies in results. Therefore, in the last, this section presents a
-%description of these varying Linux distributions/releases and their
-%vulnerability databases.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%As we are taking a particular use case of containers from
-%neuroscience field i.e Canadian Open Neuroscoence Platform (CONP) so  
-%in this section we summarize the data and tools 
-%that are used in CONP. CONP is a national platform for sharing neuroscience
-%research data and aims at creating an interactive interface for neuroscientists and
-%clinical neuroscience. The main goal of the CONP platform is to store, process, and
-%distribute massive amounts of data produced by modern neuroscience.
-%Here, we summarize all the resources that are
-%used by CONP to function.
-
-%\subsection{Container Tools}
-%
-%
-%In this paper, we consider two popular container tools i.e Docker and Singularity because
-%neuroimaging uses images from these two tools.
-%Container tools are capable of packing and running an application in an isolated environment that has
-%the application's dependencies,
-%required libraries, and configuration files for the
-%application to function properly.
-
-%\subsubsection{Docker}
-
-%Docker uses a client-server architecture, where client, containers, communicate to
-%the server, Docker Daemon, which is also known as the Docker engine.
-%Docker Daemon is a long-running process that manages all Docker images, containers, storage volumes, and networks.
-
-%consists of the following three main components: 
-%
-%\textit{Docker Daemon:} It acts as a server. It is
-%a long-running process that manages all Docker images, containers, storage volumes, and networks.
-%
-%\textit{REST API:} It acts as an interface between the server and the client, and is an API which is used by the applications
-%to talk to the \textit{Docker Daemon}.
-%
-%\textit{Client:} It is a Command Line Interface (CLI) client which is used to interact with the \textit{Docker Daemon}.
-%Docker runs a software, \textit{Docker daemon}, on the host machine.
-
-%Docker Engine, which runs as root, is remotely controlled through a
-%UNIX socket. It is responsible for launching and managing containers,
-%consequently, when a container runs, the container is spawned as a
-%child process of this root-owned daemon.
-%
-%\begin{comment}
-%It is responsible for launching containers, their
-%isolation, and spawning shells into the containers. It is also
-%responsible for managing Docker images i.e \textit{pull} and \textit{push}
-%from image repository, building images from Dockerfiles, signing them, etc.
-%When a Docker container runs, the container process is spawned as a
-%child of this root owned daemon. 
-%\end{comment}
-%As Docker users directly interact with the
-%Docker daemon through Command Line Interface (CLI) i.e \textit{docker} command, it is possible to force Docker daemon to escalate privileges.
-%If a user gets root privileges, it
-%introduces unthinkable security risks for multi-tenant shared
-%environments. Due to this reason, Docker is not supported by
-%HPC environments.
-%
-%Docker images are organized as a series of layers stacked on top of each
-%other and identified by unique layer identifiers. If a layer is reused
-%in different images it will
-%have the same id across images. Each layer consists of a filesystem diff
-%with respect to the layer below.
-%
-%\subsubsection{Singularity}
-%
-%As Docker is not suitable for HPC systems, therefore, Singularity came up with a new approach
-%of packing and running applications in containers. 
-%In contrast to Docker,
-%Singularity does not run containers as root. Consequently, users cannot escalate
-%privileges in Singularity containers making it suitable for HPC environments.
-%
-%A Singularity image is a single immutable file and
-%does not contain layers.
-%Once a Singularity image is created, it cannot be changed, consequently,
-%it can be used for reproducing the results of scientific
-%experiments.
-
-%\begin{comment}
-%Singularity offers mobility of compute by facilitating portable environments 
-%through a single image file~\cite{kurtzer2017singularity}. Once Singularity image
-%is created, it is hashed using SHA-256. Hence, it cannot be changed
-%once it is created, consequently, it can be used for reproducing the results of
-%scientific experiments. Main features provided by
-%Singularity are mobility of compute and reproducibility~\cite{kurtzer2017singularity}.
-%We used Singularity version $2.5.2$ in our experiments.
-%Users can easily access files, devices, sockets, ports of the host system from
-%the Singularity container. By default, Singularity bind mounts /home/\$USER, /tmp, and \$PWD
-%into the running container. Additional directories can be specified with \textit{--bind}
-%to bind mount into the container. By defaut, Singularity uses as less as possible namespaces.
-%However namespaces can be requested if required. Users cannot escalate privileges inside
-%Singularty containers. This is because Singularity do not run containers as root.
-%Instead, a user inside Singularity container is the same user outside the container.
-%
-%\subsection{Container Image Formats}
-%
-%A container image is a package that contains an application along with its
-%required dependencies and libraries.
-%Both, Docker and Singularity, have different image formats. Below we provide a description of both image
-%formats.
-%
-%\subsubsection{Docker Image Format}
-%
-%Docker images are organized as a series of layers stacked on top of each
-%other and identified by unique layer identifiers. If a layer is reused
-%in different images it will
-%have the same id across images. Each layer consists of a filesystem diff
-%with respect to the layer below. 
-%DockerHub uses gzip compression for
-%transferring layers.There are two ways to create a Docker image. The
-%first is to use an existing Docker image as a base image and then build a
-%new image from that one, by making changes in the filesystem, which is
-%saved as a new layer of the Docker image. The second way is to build a new
-%Docker image from scratch.Docker supports several different storage drivers.
-%\textit{Overlay2} is the preferred storage driver used by Docker for all currently
-%supported Linux versions, whereas \textit{aufs} is preferred for Docker 18.06 and
-%older, when using Ubuntu 14.04 on kernel 3.13 as it do not support \textit{overlay2}.
-%Other storage drivers that are supported by Docker include \textit{devicemapper, btrfs,
-%zfs, and vfs}
-%
-%\subsubsection{Singularity Image Format}
-%
-%On the other hand, a Singularity image is a single immutable file and 
-%does not contain layers.
-%Once a Singularity image is created, it cannot be changed, consequently,
-%it can be used for reproducing the results of scientific
-%experiments.
-%Singularity takes snapshot, locks, and archives the developed application,
-%which is known as Singularity image.
-%It means that Singularity image is a single immutable file that can be moved around as
-%any other file. This file can be checksummed, signed, and easily
-%used for verification purposes. Singularity containers use Squashfs file format
-%by default. It is read-only file system in Linux, which uses compression for files,
-%inodes, and directories. However, Singularity also supports two other 
-%formats i.e \textit{sandbox} format
-%(which is just a chroot
-%directory) and \textit{writable} format (the ext3 file system).
-%While publishing experimental results, authors can also publish Singularity
-%image along with its hash, which allow other researchers to verify results.
-%\end{comment}
 \subsection{Container Images}
@@
 used in neuroscience: BIDS
-apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}
+apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}.
 Out of these 44 images, 26 were obtained from BIDS apps
 \href{https://bids-apps.neuroimaging.io/apps/}{(https://bids-apps.neuroimaging.io/apps/)} 
-and 18 from Boutiques. In fact, at the time of the study, BIDS apps has 27 images,
-out of which one wasn't available on DockerHub. Boutiques has 49 images, listed using
+and 18 from Boutiques. In fact, at the time of the study, BIDS apps had 27 images,
+out of which one wasn't available on DockerHub. Boutiques had 49 images, listed using
 Boutiques \texttt{bosh search} command,
-however, only 23 unique were listed, out of which 3 couldn't be retrieved and 2
-we decided to ignore as they were already included in BIDS apps. All the final 26 images
-from BIDS apps are Docker images, whereas Boutiques contain 18 Docker images
+however, only 23 unique images were listed, out of which 3 couldn't be retrieved and 2
+ were already included in BIDS apps. All the final 26 images
+from BIDS apps are Docker images, whereas Boutiques contains 18 Docker images
 and 6 Singularity images.
 
-%Among the 27 BIDS apps \href{https://bids-apps.neuroimaging.io/apps/}
-%{(https://bids-apps.neuroimaging.io/apps/)} available at the time of
-%the study, we studied 26
-%unique Docker images as one wasn't available on DockerHub. Among the 49
-%Boutiques applications available at the time of the study, listed using
-%Boutiques \texttt{bosh search} command, 23 unique container images were
-%listed including 3 that couldn't be retrieved and 2 that were already
-%included in BIDS apps. The resulting 18 images included 12 Docker images
-%and 6 Singularity images.
-%\begin{figure}
-%\csvreader[%
-% respect all,%
-%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
-%      %\caption{Baseline GF Competition Circle Track 2014}\label{tab:baselline1}
-%      \begin{adjustbox}{max width=\columnwidth},
-%  after reading=\end{adjustbox},
-% tabular={c |c | c | c | c},
-%	table head =Image & {OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls}\\\hline,
-% late after line= \\,
-%	late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
-%]{results.csv}{}{\csvlinetotablerow}%
-%       \centering
-%	\caption{Existing number of Vulnerabilities}
-%\end{figure}
-
-%\begin{comment}
-%\subsubsection{ReproNim}
-%
-%ReproNim is a Center for Reproducible Neuroimaging Computation. It is a vision
-%to help neuroscientists in reproducing neuroimaging research. Repronim
-%uses RepronIn, BrainVerse, Neuroimaging Computation Environments Manager (NICEMAN),
-%and NeuroBlast software tools for its
-%functioning. ReproIn is a software that automate acquisition and conversion
-%of collected MRI data to BIDS standard format with DataLad version management~\cite{kennedy2019everything}.
-%BrainVerse is a cross-platform software framework and collaborative desktop application
-%that helps in managing, tracking, and sharing information.
-%NICEMAN is a software system that tracks and manages available computation resources
-%and makes their use in a scalable and reproducible way.
-%Neuroblast is a service that facilitates data sharing of existing studies, and it also
-%helps users to search similar studies based on combination of analysis,
-%tasks and activation patterns. There are currently 28 different Singularity
-%images used by Repronim. 
-%
-%\subsection{Other images}
-%
-%\TG{We could also use selected images from DockerHub or SingularityHub. For
-%instances the ones used by AFNI or other neuroimaging tools not represented
-%in Boutiques or BIDS Apps. However we wouldn't be able to shrink these
-%images unless we identified specific command-lines to run.}
-%
-%\end{comment}
-
 \subsection{Image Scanners}
-
-%Container image scanners can be broadly categorized into static and dynamic
-%scanners. Static scanning performs analysis on a image without running it
-%as a container.
-
-%Therefore, package manager, which is a executable file,
-%cannot be used to extract required data while statically extracting image data.
-%Thus, scanners parse different files for extracting image data e.g, installed packages, their versions,
-%and OS distribution etc. For instance, in Debian and Ubuntu, \textit{/var/lib/dpkg/status} file
-%can be parsed to get a list of installed packages and in the same way \textit{/etc/os-release} file can be
-%parsed to get information about OS distribution.
-%Whereas in dynamic scanning, a container is deployed from the image first and then
-%package manager of the image is executed inside the container to collect required data.
-
-%\subsubsection{Scanning tools used}
-
-%\begin{comment}
-%Out of the various container image scanning tools available to scan Docker images,
-%we selected Anchore~\cite{github_2019}
-%and Vuls~\cite{future-architect_2019} because these are the most mature scanning tools. To scan Singularity images
-%we use Stools, which is specially designed for Singularity images. This tool internally uses
-%Clair Scanner tool so we included ClairScanner also in our experiements to compare
-%performance of both the tools. So total there are three scanners for Docker images
-%and one scanner for Singularity images.
-%\end{comment}
 
@@
 
-%Vuls support both static as well as dynamic
-%scanning till version 0.9.5, however, in our experiments we used it dynamically.
-%On the contrary, the others
-%are static scanners.
-
 \subsubsection{Anchore}
@@
 packages, non-OS packages (Python, Java, Gem, and Npm), and files.
-%\begin{comment}
-%Anchore is a set of tools, which users can
-%employ for scanning container images and applying custom policies to them.
-%It provides visibility and transparency of the container environment.
-%\end{comment}
 Anchore Engine can be used in two ways: through Docker image or Anchore
 Command Line Interface (CLI).
-%\begin{comment}
-%Anchore offers services in two ways: Anchore Engine and Anchore
-%Command Line Interface (CLI). Anchore Engine is available as a Docker
-%image, which is available on Docker Hub. Anchore Engine CLI provides
-%command line interface in addition to Anchore Engine REST API. 
-%\end{comment}
 It can be
 installed directly on the host and used to inspect images.
-In our experiments, we use a Docker image in order to have access to Anchore Engine version 0.5.0 with the 
+In our experiments, we use Anchore Engine version 0.5.0 through Docker image \todo{insert name}, and
 Anchore vulnerability database version 0.0.11.
@@
 image, with the vulnerability database in order to flag vulnerabilities.
-To get a vulnerability feed of various OS distribution, Anchore refers to
+To get a vulnerability feed of various OS distributions, Anchore refers to
 different sources, for instance, Ubuntu launchpad database to get
@@
 
-\begin{figure}[!ht]
-	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
-	{Figures/vulnExample2.png}}}
-        \caption{\label{example} Representation of a CVE in Ubuntu Launchpad}
-\end{figure}
-
 \subsubsection{Vuls}
 
-Vuls is an open-source vulnerability scanner for Linux and FreeBSD.
-It offers both static and dynamic scanning. In our experiments, we use
-it to dynamically scan containers.
-Using a dynamic scanning technique, it offers
-remote and local scans at the time of writing. The remote scan sets up only one machine to
-which other target servers are connected via SSH. Local scan involves running
-the scan on the target server itself. 
-%Further, Vuls offer a fast scan, fast root scan,
-%and deep scan mode.
-%The Fast scan is performed without root privileges, whereas a fast root scan is
-%performed with root privileges. The latter also uses checkrestart utility to 
-%detect processes that are updated but not yet restarted because if they are not
-%restarted, updates are not effective. Fast root scan also detects these
-%processes. Both fast scan and fast root scan are performed offline without Internet
-%access, and put almost no load on the scan target server. The Deep scan uses
-%root privileges for scanning and is used to get a more detailed scan. It checks
-%changelogs, which puts more load on the target server.
-
-In our experiments, we use a Vuls Docker image having version 0.9.0. %with fast scan mode.
-Vuls gets data from Open Vulnerability and Assessment Language (OVAL).
-It is worth noting that there is no OVAL data for Ubuntu 17.04 and 17.10 distribution,
-meaning that images with these distributions are hard to scan with Vuls.
+Vuls is an open-source vulnerability scanner for Linux and FreeBSD. It
+offers both static and dynamic scanning, and both local and remote
+scanning. In our experiments, we use remote dynamic scanning, that is, Vuls
+starts a container for every image to test, and queries the package manager in the image through SSH.
+We use Vuls 0.9.0, executed through Docker image \todo{add Docker image name}. Vuls gets data from the Open Vulnerability and Assessment Language (OVAL) database.
+It is worth noting that there is no OVAL data for Ubuntu 17.04 and 17.10 distributions,
+meaning that images with these distributions cannot be scanned with Vuls.
 
@@
 Clair-scanner is a static vulnerability scanner for Docker containers.
-%CoreOS originally created Clair, a static vulnerability scanner for containers. 
-%The main goal of the
-%tool is to provide a transparent look of container’s security. Clair scans container images in regular
-%intervals, and stores metadata of vulnerabilities, after getting from configured
-%set of sources. 
-%Clair API can be used by clients to query its database to get
-%the list of vulnerabilities that a particular image has. Clair sends a notification
-%to alert the systems if there is an update in the vulnerability metadata. Quay.io, which
-%is a registry to store images privately, uses Clair internally as the security engine. 
-%However, Clair does not 
-%provide the facility for comparing
-%the vulnerability list of a particular image against a whitelist of vulnerabilities that you
-%want to ignore~\cite{arminc_2019}. 
-%So, to remove
-%that drawback, another tool, Clair Scanner can be used. 
 It scans the image, prepares the list of
@@
 Whenever Ubuntu updates its database, this image is also updated with the required information.
-
-In our experiments, we use a Docker image (arminc/clair-local-scan:v2.0.6) for scanning
-and an another Docker image (arminc/clair-db:latest) for the vulnerability database, which was
-last updated on 2019-09-18. We perform
-scanning on 2019-09-25.
+We use Clair-scanner version 2.0.6, executed through  Docker image arminc/clair-local-scan:v2.0.6. 
+We use another Docker image (arminc/clair-db:latest) for the vulnerability database, which was
+last updated on 2019-09-18.
 
@@
 
+\todo{remove mentioning of CI, rewrite this paragraph.}
 Continuous Integration (CI) allows smaller code changes, fault isolations,
@@
 different environments, whereas the latter targets smaller projects where
-integration needs to be done as fast as possible. Stools uses CoreOS's Clair, which
+integration needs to be done as fast as possible.
+
+Stools uses CoreOS's Clair, which
 is used for Docker images, in combination with CI to allow scanning of
 Singularity images.
-%Stools combines CoreOS's Clair with Continuous Integration (CI)
-%for scanning Singularity images for vulnerabilities.
-%Initially, Clair was intended to scan Docker images only. This tool does not fit well
-%to scan Singularity images because of the different image formats.
-%However, TravisCI and CircleCI are commonly used for testing code, and these
-%services also offer running containers. Stools combined both these concepts.
 It involves spinning a Clair container during testing and building a
@@
 
-%\begin{table}
-%\csvreader[%
-% respect all,%
-%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
-%      \begin{adjustbox}{max width=\columnwidth},
-%  after reading=\end{adjustbox},
-% tabular={c |c},
-%        table head =Singularity Images & {Vulnerabilities by Stools}\\\hline,
-% late after line= \\,
-%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
-%]{Singularityresults.csv}{}{\csvlinetotablerow}%
-%       \centering
-%        \caption{\label{sing}Number of Vulnerabilities in Singularity images}
-%\end{table}
-
-%\begin{table*}
-%  \caption{some table}
-%	\begin{tabular}{>|{\bfseries}c| c| c| *{4}{c|}}\hline
-%	  \multirow{2}{*}{\bfseries Image Labels} & 
-%	  \multirow{2}{*}{\bfseries Image Names} & 
-%	  \multirow{2}{*}{\bfseries OS} & 
-%	  \multicolumn{4}{c|}{\bfseries Vulnerabilities} \\\cline{2-5} 
-%                       & \textbf{A} & \textbf{C} & \textbf{V}  & \textbf{S} \\ \hline
-%a	& bids/example	& ubuntu:14.04	& 838	& 663	& 683	& \\ \hline
-%b	& bids/freesurfer	& ubuntu:14.04	& 353	& 215	& 192	& \\ \hline
-%c	& bids/ndmg	& ubuntu:14.04	& 934	& 757	& 782	& \\ \hline
-%d	& bids/broccoli:v1.0.0	& centos 6	& 79	& 79	& 117	& \\ \hline
-%e	& bids/fibredensityandcrosssection	& ubuntu:14.04	& 1086	& 849	& 868	& \\ \hline
-%f	& bids/spm	& ubuntu:14.04	& 191	& 246	& 235	& \\ \hline
-%g	& poldracklab/mriqc:0.15.0	& ubuntu:16.04	& 432	& 328	& 332	& \\ \hline
-%h	& bids/cpac:v1.0.1a\_22	& ubuntu:16.04	& 698	& 524	& 535	& \\ \hline
-%I	& bids/hyperalignment	& ubuntu:16.04	& 1717	& 1327	& 1433	& \\ \hline
-%j	& bids/mindboggle:0.0.4-1	& debian:8	& 671	& 955	& 569	& \\ \hline
-%k	& bids/mrtrix3\_connectome	& ubuntu:18.04	& 275	& 157	& 158	& \\ \hline
-%l	& bids/rs\_signal\_extract:0.1	& ubuntu:16.04	& 867	& 454	& 473	& \\ \hline
-%m	& bids/aa:v0.2.0	& ubuntu:14.04	& 189	& 244	& 233	& \\ \hline
-%n	& bids/niak	& ubuntu:16.04	& 1482	& 1366	& 1420	& \\ \hline
-%o	& bids/oppni:v0.7.0-1	& ubuntu:14.04	& 913	& 698	& 723	& \\ \hline
-%p	& poldracklab/fmriprep:unstable	& ubuntu:16.04	& 516	& 355	& 393	& \\ \hline
-%q	& bids/brainiak-srm	& ubuntu:16.04	& 897	& 484	& 503	& \\ \hline
-%r	& bids/nipypelines:0.3.0	& debian:8	& 641	& 878	& 451	& \\ \hline
-%s	& bids/hcppipelines:v3.17.0-18	& debian:8	& 526	& 873	& 620	& \\ \hline
-%t	& bids/magetbrain	& ubuntu:18.04	& 112	& 117	& 126	& \\ \hline
-%u	& bids/tracula:v6.0.0-4	& ubuntu:14.04	& 874	& 664	& 683	& \\ \hline
-%v	& bids/baracus	& ubuntu:14.04	& 172	& 238	& 216	& \\ \hline
-%w	& bids/antscorticalthickness:v2.2.0-1	& ubuntu:17.04	& 289	& 27	& no oval data	& \\ \hline 
-%x	& bids/dparsf:v4.3.12	& ubuntu:14.04	& 507	& 750	& 757	& \\ \hline
-%y	& bids/afni\_proc	& ubuntu:17.10	& 67	& 16	& no oval data	& \\ \hline
-%z	& bids/rshrf:1.0.1	& alpine:3.8.4	& 5	& 3	& 3	& \\ \hline
-%aa	& bids/ndmg:v0.1.0	& ubuntu 14.04	& 934	& 758	& 782	& \\ \hline
-%ab	& mcin/qeeg:latest	& centos 7	& 46	& 46	& 142	& \\ \hline
-%ac	& camarasu/creaphase:0.3	& centos 7	& 54	& 54	& 186	& \\ \hline
-%ad	& bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest	& centos 7	& 70	& 76	& 157	& \\ \hline
-%ae	& mcin/docker-fsl:latest	& centos 7	& 75	& 75	& 201	& \\ \hline
-%af	& gkiar/onevoxel:v0.3.0rc2	& alpine 3.7.1	& 5	& 2	& 2	& \\ \hline
-%ag	& bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest	& centos 7	& 70	& 76	& 157	& \\ \hline 
-%ah	& bt5e/ants:latest	& centos 7	& 150	& 156	& 336	& \\ \hline
-%ai	& poldracklab/fmriprep:1.2.3	& ubuntu 16.04	& 591	& 441	& 447	& \\ \hline
-%aj	& gkiar/dwipreproc\_fsl-5.0.11\_minified	& ubuntu 16.04	& 391	& 258	& 263	& \\ \hline
-%ak	& gkiar/mask2boundary:v0.1.0	& alpine 3.9.0	& 15	& 11	& 11	& \\ \hline
-%al	& mcin/ica-aroma:latest	& centos 7	& 75	& 75	& 202	& \\ \hline
-%am	& c3genomics/genpipes	& 	& 	& 	& 	& 99 \\ \hline
-%an	& bioinformatics-group/aqua-singularity-recipe	& 	& 	& 	& 	& 7 \\ \hline
-%ao	& MontrealSergiy/BEst	& 	& 	& 	& 	& 106 \\ \hline
-%ap	& shub://aces/cbrain-containers-recipes:fsl\_v6.0.1	& 	& 	& 	& 	& 206 \\ \hline
-%aq	& shots47s/bids-freesurfer-6.0	& 	& 	& 	& 	& 212 \\ \hline
-%ar	& shots47s/bids-fmriprep-1.2.3	& 	& 	& 	& 	& 453 \\ \hline
-%  \end{tabular}
-%  \end{table*}
-
 \subsection{Linux Releases and Vulnerability Databases}
@@
 BIDS app and Boutiques images in our experiments have diverse Linux
-distributions, such as Ubuntu, Centos, Debian, and Alpine. Further, a particular
+distributions, such as Ubuntu, CentOS, Debian, and Alpine. Further, a particular
 distribution has different releases in general. To illustrate, we here examine Ubuntu as an example,
-since it is heavily utilised in our experiments. However, other distributions also have
+since it is heavily utilized in our experiments. 
+\todo{Explain the situation with centos, update figure 3 accordingly.}
+However, other distributions also have
 similar release trend. Ubuntu releases
@@
 in the Ubuntu launchpad database.
+
+\begin{figure}[!ht]
+	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
+	{Figures/vulnExample2.png}}}
+        \caption{\label{example} Representation of a CVE in Ubuntu Launchpad}
+\end{figure}
 

### 2020-07-01 paper.tex

@@
 \author[1]{Bhupinder Kaur}
+\author[1]{Mathieu Dugr\'e}
 \author[1]{Aiman Hanna}
@@
 We conduct two different
-experiments, image update and image shrinking, to report the effect 
+experiments, image update and image minimization, to report the effect 
 on the number of vulnerabilities.
@@
 
-\textit{RQ3: Can the amount of vulnerabilities be reduced by shrinking the images?} 
+\textit{RQ3: Can the amount of vulnerabilities be reduced by minimizing the images?} 
 Container images often include more software packages than required for a
@@
 including image scanners and container images. We then describe our image
-update and shrinking methodology to reduce vulnerabilities. Results review
+update and minimization methodology to reduce vulnerabilities. Results review
 the detected vulnerabilities in container images, explain observed
@@
 in container images and attempt to examine the effect of different
-manipulation of these images, it is needed to have a representative set
+manipulation of these images, it is needed to have a representative set of
 images. Additionally, for the purpose of detecting vulnerabilities,
@@
 We use four popular image scanners, namely Anchore~\cite{github_2019},
-Vuls~\cite{future-architect_2019}, Clair-scanner~\cite{arminc_2019} and
-Stools~\cite{stools}. Anchore, Vuls and Clair-scanner support Docker
-images while Stools supports Singularity. Different vulnerabilities may be
+Vuls~\cite{future-architect_2019}, Clair~\cite{arminc_2019} and
+Singularity Container Tools --- Stools~\cite{stools}. Anchore, Vuls and Clair support Docker
+images while Stools support Singularity. Different vulnerabilities may be
 reported if scanning experiments take place on different dates.
@@
 Anchore is an end-to-end, open-source container security platform. It
-is a static
-scanning tool that analyses container images and lists OS
+analyses container images and lists OS
 packages, non-OS packages (Python, Java, Gem, and Npm), and files.
-Anchore Engine can be used in two ways: through Docker image or Anchore
-Command Line Interface (CLI).
-It can be
-installed directly on the host and used to inspect images.
 In our experiments, we use Anchore Engine version 0.5.0 through Docker image \todo{insert name}, and
@@
 different sources, for instance, Ubuntu launchpad database to get
-vulnerability data related to Ubuntu.
+vulnerability data related to Ubuntu \tristan{You need to be accurate on these sources, this is not ``for instance". 
+You should list all the sources used in the experiments, for all image types: Ubuntu but also CentOS, Debian, Alpine.}.
 
@@
 scanning. In our experiments, we use remote dynamic scanning, that is, Vuls
-starts a container for every image to test, and queries the package manager in the image through SSH.
-We use Vuls 0.9.0, executed through Docker image \todo{add Docker image name}. Vuls gets data from the Open Vulnerability and Assessment Language (OVAL) database.
-It is worth noting that there is no OVAL data for Ubuntu 17.04 and 17.10 distributions,
-meaning that images with these distributions cannot be scanned with Vuls.
+starts a container for every image to test, and queries the package manager
+in the image through SSH. We use Vuls 0.9.0, executed through Docker image
+\todo{add Docker image name}. Vuls gets data from the Open Vulnerability
+and Assessment Language (OVAL) database \tristan{Does it contain
+vulnerabilities for all distributions?} \tristan{The Vuls website says that it uses multiple vulnerability databases: https://vuls.io/docs/en/main-features.html Are you sure 
+that you only used OVAL and if so, why?}. It is worth noting that there is
+no OVAL data for Ubuntu 17.04 and 17.10 distributions, meaning that images
+with these distributions cannot be scanned with Vuls.
 
-\subsubsection{Clair-scanner}
+\subsubsection{Clair}
 
-Clair-scanner is a static vulnerability scanner for Docker containers.
-It scans the image, prepares the list of
-vulnerabilities, compares that list against a whitelist, and flags vulnerabilities
-that are not present in the whitelist.
-Clair-scanner utilizes the Ubuntu CVE tracker to obtain  Ubuntu vulnerability feed.
-For that purpose, a Docker image is maintained that contains the Ubuntu CVE tracker database.
-Whenever Ubuntu updates its database, this image is also updated with the required information.
-We use Clair-scanner version 2.0.6, executed through  Docker image arminc/clair-local-scan:v2.0.6. 
-We use another Docker image (arminc/clair-db:latest) for the vulnerability database, which was
-last updated on 2019-09-18.
+Clair (\url{https://github.com/quay/clair}) is an open-source and extensible
+vulnerability scanner for Docker and appc container images, developed by
+CoreOS (now Container Linux), a Linux distribution to deploy container
+clusters. Clair has a client-server architecture, in which the server
+maintains a database of vulnerabilities. We use Clair through Clair scanner
+(\url{https://github.com/arminc/clair-scanner}), a tool to facilitate the testing
+of container images against a local Clair server. Clair scanner scans the image,
+prepares the list of vulnerabilities, compares that list against a
+whitelist, and flags vulnerabilities that are not present in the whitelist
+\tristan{What is this whitelist about, and which one did you use?}. Clair
+scanner maintains a Docker image with the up-to-date Ubuntu CVE tracker
+database, used for the analysis \tristan{Please mention the vulnerability sources for all distributions}.
+ We use Clair-scanner version 2.0.6, executed through
+Docker image \texttt{arminc/clair-local-scan:v2.0.6}. For the vulnerability
+database, we use Docker image \texttt{arminc/clair-db:latest}, last
+updated on 2019-09-18.
 
-\subsubsection{Stools}
+\subsubsection{Singularity Tools}
 
-\todo{remove mentioning of CI, rewrite this paragraph.}
-Continuous Integration (CI) allows smaller code changes, fault isolations,
-faster release date, etc. Two types of CI are commonly used : TravisCI and
-CircleCI. The former targets open source projects that need to be tested in
-different environments, whereas the latter targets smaller projects where
-integration needs to be done as fast as possible.
-
-Stools uses CoreOS's Clair, which
-is used for Docker images, in combination with CI to allow scanning of
-Singularity images.
-It involves spinning a Clair container during testing and building a
-Singularity image, and scanning it before the image is finalized.
-
-In our experiments, we use a Docker image (\href{https://hub.docker.com/r/vanessa/stools-clair}{vanessa/stools-clair:v3.2.1})
-following the steps mentioned in \href{https://github.com/singularityhub/stools}{Stools Github} for scanning
-Singularity images.
+Singularity Tools (Stools)
+are an extension of Clair scanner for Singularity images. Stools
+directly scan the image files in a local installation of the Clair
+scanner, to circumvent the Docker-specific requirements in the Clair API.
+In our experiments, we use Singularity Tools version 3.2.1  through Docker
+image
+\texttt{vanessa/stools-clair:v3.2.1}
+and we follow the steps mentioned in
+\href{https://github.com/singularityhub/stools}{Stools Github} to scan
+Singularity images. \tristan{which docker images did you use for clair and clair database?}
 
@@
 
+\tristan{This section is still very confusing. I can rewrite it but would first need to
+have a clear picture of vulnerability statuses across the tested Linux distributions. 
+Are vulnerability statuses present only in Ubuntu, or are there statuses in other distributions too?
+If so, what are the vulnerability statuses in the other distributions?
+}
 Through our experiments, we find that image scanners report vulnerabilities 
@@
 
-\section{Our Approach}
+\section{Reducing the amount of vulnerabilities}
 
-In this section, we present our approach, where we attempt the reduction
-of security vulnerabilities in images by updating or
-shrinking these images.
+In this section, we present our approach to reduce the number of
+vulnerabilities in container images  by updating and minimizing these
+images.
 
@@
 accordingly. However, this action affects the reproducibility
-of that image. For example, if a package is used by a scientist to conduct an experiment
-and later that package is updated, other scientists want to reproduce initial results may actually
-get different results due to updates.
+of that image. For example, if a package is used in an experiment
+and later that package is updated, subsequent instances of the experiment may actually
+get different results.
 %which means that the image cannot be used to verify the research
@@
 
-\subsection{Image Reduction/Minimization Process}
-On the other hand, if it is desired to reduce the number of vulnerabilities without affecting the reproducibility of the image,
-then we revert to image size reduction instead of image update. An interesting choice to do so would be to use 
+\subsection{Image Minimization Process}
+We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
+An interesting choice to do so would be to use 
 Neurodocker~\cite{neurodocker}.
@@
 Reprozip~\cite{rampin2016reprozip}, which is a tool that
-is used to make applications reproducible. This tool traces operating system calls used by the
+is used to make applications reproducible \tristan{No it doesn't make applications reproducible}. This tool traces operating system calls used by the
 application while execution, and then based on this trace, it recognizes binaries, files, environment variables,
@@
 uses an available package manager to acquire a list of distribution packages from where these files come from.
-So, a list of packages that are needed for the application re-execution is determined. Following that, the list
+So, a list of packages that are needed for the application re-execution is determined. \tristan{How did you run the applications? Which command lines, why, etc} Following that, the list
 is expanded by adding important and required packages that are essential
 for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
-~\cite{debtree}.
+~\cite{debtree} \tristan{does debtree work in centos? if not, how do you minimize centos images?}.
 Effectively all needed packages are kept and remaining unnecessary packages are removed. We use
 \href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
-the image size reduction process, which install Reprozip in the image, collect Reprozip trace, and
+the image size reduction process \tristan{Can we please have at least a README for these scripts?}, which install Reprozip in the image, collect Reprozip trace, and
 finally delete all unnecessary packages.
@@
 Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
-the scanners and the overlap between them.
+the scanners and the overlap between them. \tristan{According to our discussion, this is only for Ubuntu. This should be clarified.}
 

### 2020-07-05 paper.tex
worked on comments 1

@@
 
+%%%%%%%%%Related Work%%%%%%%
+The existing research work on containers focuses mainly on the security of containers.
+This focus is justified by the fact that containers expose the host's resources
+(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
+threat for the applications running on the same host. Previous studies evaluated
+the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis}.
+Other work studied security vulnerabilities on Docker hub. A study in 2015 by Gummaraju et al.
+states that over 30\% of official images in docker hub contain high priority 
+security vulnerabilities~\cite{gummaraju2015over}. Shu et al. show that both official and community images 
+contain more than 180 vulnerabilities on an average~\cite{Shu2017}.
+Zerouali et al. studied that 
+outdated packages lead to bugs and severity vulnerabilities in Docker
+images~\cite{zerouali2019relation}.
+
 \todo{Add related work on vulnerability scanning}
@@
 Out of these 44 images, 26 were obtained from BIDS apps
-\href{https://bids-apps.neuroimaging.io/apps/}{(https://bids-apps.neuroimaging.io/apps/)} 
+(\url{https://bids-apps.neuroimaging.io/apps/}) 
 and 18 from Boutiques. In fact, at the time of the study, BIDS apps had 27 images,
@@
 packages, non-OS packages (Python, Java, Gem, and Npm), and files.
-In our experiments, we use Anchore Engine version 0.5.0 through Docker image \todo{insert name}, and
+In our experiments, we use Anchore Engine version 0.5.0 through Docker image \texttt{anchore/anchore-engine:v0.5.0}, and
 Anchore vulnerability database version 0.0.11.
@@
 To get a vulnerability feed of various OS distributions, Anchore refers to
-different sources, for instance, Ubuntu launchpad database to get
-vulnerability data related to Ubuntu \tristan{You need to be accurate on these sources, this is not ``for instance". 
+different sources. The figure~\ref{anchore} displays a list of all sources
+that it refers at the time of this study.
+
+%for instance, Ubuntu launchpad database to get
+%vulnerability data related to Ubuntu 
+\tristan{You need to be accurate on these sources, this is not ``for instance". 
 You should list all the sources used in the experiments, for all image types: Ubuntu but also CentOS, Debian, Alpine.}.
+
+\begin{figure*}[!ht]
+    \centering
+	\begin{subfigure}[t]{0.3\textwidth}
+        \includegraphics[height=2.0in]{Figures/anchore.png}
+        \caption{Anchore}
+        \label{anchore}
+    \end{subfigure}%
+    ~ 
+	\begin{subfigure}[t]{0.3\textwidth}
+        \includegraphics[height=2.5in]{Figures/vuls.png}
+        \caption{Vuls}
+        \label{vuls}
+    \end{subfigure}
+     ~
+	\begin{subfigure}[t]{0.3\textwidth}
+        \includegraphics[height=2.0in]{Figures/clair.png}
+        \caption{Clair}
+	\label{clair}
+    \end{subfigure}
+    \caption{Vulnerability databases used by scanners}
+    \label{database}
+\end{figure*}
 
@@
 in the image through SSH. We use Vuls 0.9.0, executed through Docker image
-\todo{add Docker image name}. Vuls gets data from the Open Vulnerability
-and Assessment Language (OVAL) database \tristan{Does it contain
-vulnerabilities for all distributions?} \tristan{The Vuls website says that it uses multiple vulnerability databases: https://vuls.io/docs/en/main-features.html Are you sure 
-that you only used OVAL and if so, why?}. It is worth noting that there is
+\texttt{vuls/vuls:latest}. At the time of this study, Vuls gets vulnerability feed
+from a configured set of sources, which are listed in Figure~\ref{vuls}.
+%from the Open Vulnerability
+%and Assessment Language (OVAL) database 
+\tristan{Does it contain
+vulnerabilities for all distributions?} 
+\tristan{The Vuls website says that it uses multiple vulnerability databases: https://vuls.io/docs/en/main-features.html Are you sure 
+that you only used OVAL and if so, why?}. According to this list, Vuls
+refers to OVAL database for some distribution e.g. Ubuntu, Debian, etc.
+It is worth noting that there is
 no OVAL data for Ubuntu 17.04 and 17.10 distributions, meaning that images
@@
 prepares the list of vulnerabilities, compares that list against a
-whitelist, and flags vulnerabilities that are not present in the whitelist
+whitelist, and flags vulnerabilities that are not present in the whitelist.
+In our experiments, we did not use a whitelist to filter scanning results in
+order to make a fair comparison between scanners.
 \tristan{What is this whitelist about, and which one did you use?}. Clair
-scanner maintains a Docker image with the up-to-date Ubuntu CVE tracker
-database, used for the analysis \tristan{Please mention the vulnerability sources for all distributions}.
+scanner maintains a Docker image with the up-to-date vulnerability
+database from a set of different sources listed in Figure~\ref{clair}.  \tristan{Please mention the vulnerability sources for all distributions}.
  We use Clair-scanner version 2.0.6, executed through
@@
 image
-\texttt{vanessa/stools-clair:v3.2.1}
-and we follow the steps mentioned in
+\texttt{vanessa/stools-clair:v3.2.1}, which is using another Docker
+image \texttt{arminc/clair-db:latest} for referring to vulnerability feed.
+We follow the steps mentioned in
 \href{https://github.com/singularityhub/stools}{Stools Github} to scan
@@
 in which vulnerability exists and are entitled a status
-(\href{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
+(\url{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
 encoded in the following form:
@@
 uses an available package manager to acquire a list of distribution packages from where these files come from.
-So, a list of packages that are needed for the application re-execution is determined. \tristan{How did you run the applications? Which command lines, why, etc} Following that, the list
+So, a list of packages that are needed for the application re-execution is determined. We run applications
+using specific command lines given on application's Github repository in order to collect Reprozip trace.
+These command lines represent how applications should be used.
+\tristan{How did you run the applications? Which command lines, why, etc} Following that, the list
 is expanded by adding important and required packages that are essential
 for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
-~\cite{debtree} \tristan{does debtree work in centos? if not, how do you minimize centos images?}.
+~\cite{debtree}, which is avaiable in Debian and Ubuntu. Its alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
+gives a complete dependency tree.\tristan{does debtree work in centos? if not, how do you minimize centos images?}.
 Effectively all needed packages are kept and remaining unnecessary packages are removed. We use
@@
 may reduce the needed work; however this is not possible in all cases. For instance,
-some packages, such as apt-transport-https, are required to fetch updates, deleting these packages
+some packages, such as \texttt{apt-transport-https}, are required to fetch updates, deleting these packages
 ahead of time will disallow the update process to take place.
@@
 Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
-the scanners and the overlap between them. \tristan{According to our discussion, this is only for Ubuntu. This should be clarified.}
+the scanners in Docker images and the overlap between them.
+This figure excludes Centos Docker images because scanners report results in different
+formats for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
+to report pending patches that need to be applied to specific packages
+,whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
+vulnerabilities in packages. Also, we excluded two other images \texttt{bids/antscorticalthickness:v2.2.0-1} and
+\texttt{bids/afni\_proc} from this figure, since we do not have Vuls scanning results for these images. 
+\tristan{According to our discussion, this is only for Ubuntu. This should be clarified.}
 

### 2020-07-05 Scripts/graphs/script.py

@@ -36,7 +36,7 @@ for i in range(1,12):
 leg.set_bbox_to_anchor([1.01, 0.04])
 leg._loc = 4
 #leg.markerscale=2
-leg.texts[12].set_text("CRITICAL \nVulnerabilities")
+leg.texts[12].set_text("HIGH \nVulnerabilities")
 
 #leg(markerscale=6)
 #z = np.polyfit(df['Packages'], df['Vulnerabilities'], 1)

### 2020-07-05 Scripts/graphs/venn_for_centos.py

@@ -1,0 +1,50 @@
+#!/usr/bin/env python3
+import csv
+import sys
+import os
+import re
+
+
+def compare(file1,file2):
+    with open(file1, 'r') as a, open(file2, 'r') as c:
+        anchore = a.readlines()
+        clair = c.readlines()
+    with open('A+C.csv', 'w') as f3:
+        for line in anchore:
+               if line in clair:
+                       f3.write(line)
+    with open('A+C.csv','r') as f4:
+        ac=f4.readlines()
+    with open('A.csv','w') as f5:
+        for line in anchore:
+            if line not in clair:
+                    f5.write(line)
+    with open('A.csv','r') as f6:
+        a=f6.readlines()
+    
+    with open('C.csv','w') as f7:
+        for line in clair:
+            if line not in anchore:
+                    f7.write(line)
+    with open('C.csv','r') as f8:
+        c=f8.readlines()
+
+
+    print("Anchore",len(a))
+    print("Clair",len(c))
+    print("A+C",len(ac))
+    
+
+def main():
+#    dir_name = "./"
+#    test = os.listdir(dir_name)
+#    for item in test:
+#       if item.endswith(".csv"):
+#            os.remove(os.path.join(dir_name, item))
+#
+    file1=sys.argv[1]
+    file2=sys.argv[2]
+    compare(file1,file2)
+
+if __name__== "__main__":
+  main()

### 2020-07-06 paper.tex
edit README.md

@@
 out which packages we need for the pipeline to function properly. To allow for that, we utilize
-Reprozip~\cite{rampin2016reprozip}, which is a tool that
-is used to make applications reproducible \tristan{No it doesn't make applications reproducible}. This tool traces operating system calls used by the
+Reprozip~\cite{rampin2016reprozip}, which is a open-source tool that
+helps scientists to make their research reproducible \tristan{No it doesn't make applications reproducible}. This tool traces operating system calls used by the
 application while execution, and then based on this trace, it recognizes binaries, files, environment variables,
@@
 ~\cite{debtree}, which is avaiable in Debian and Ubuntu. Its alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
-gives a complete dependency tree.\tristan{does debtree work in centos? if not, how do you minimize centos images?}.
+gives a complete dependency tree of a particular package.\tristan{does debtree work in centos? if not, how do you minimize centos images?}.
 Effectively all needed packages are kept and remaining unnecessary packages are removed. We use

### 2020-07-07 paper.tex
worked on comments 2

@@
 To get a vulnerability feed of various OS distributions, Anchore refers to
-different sources. The figure~\ref{anchore} displays a list of all sources
+different sources. The Figure~\ref{anchore} displays a list of all sources
 that it refers at the time of this study.
@@
 These command lines represent how applications should be used.
-\tristan{How did you run the applications? Which command lines, why, etc} Following that, the list
+\tristan{How did you run the applications? Which command lines, why, etc}. Following that, the list
 is expanded by adding important and required packages that are essential
 for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
-~\cite{debtree}, which is avaiable in Debian and Ubuntu. Its alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
+~\cite{debtree}, which is avaiable in Debian and Ubuntu. It's alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
 gives a complete dependency tree of a particular package.\tristan{does debtree work in centos? if not, how do you minimize centos images?}.

### 2020-07-07 Scripts/compare_results/test.py

@@ -5,16 +5,57 @@ import sys
 import os
 import re
 
-def compare(file1,file2):
+def find_epoch(inFile,input_file):
+    with open(input_file,'r') as f:
+        lines=f.readlines()
+    new_list=list()
+    for line in lines:
+        new_list.append(line.strip())
+    with open(inFile, 'r') as file:
+      file.readline() # skip the first line
+      rows = [[str(x) for x in line.split('|')[:-1]] for line in file]
+      cols = [list(col) for col in zip(*rows)]
+    epoch_cves=list()
+    for row in rows:
+        if len(row) > 1:
+           if ":" in row[4].strip():
+               cve=row[2].split()[1]
+               if cve in new_list:
+                   epoch_cves.append(cve)
+    required_cves=list(set(epoch_cves))
+    with open('epoch.csv','w') as out:
+        for entry in required_cves:
+            out.write(entry)
+            out.write("\n")
+    file.close()
+
+def compare2(file1,file2):
     with open(file1, 'r') as t1, open(file2, 'r') as t2:
         fileone = t1.readlines()
         filetwo = t2.readlines()
     
-    with open('C-A.csv', 'w') as f1:
+    with open('V-C.csv', 'w') as f1:
         for line in filetwo:
             if line not in fileone:
                 f1.write(line)
-    with open('A-C.csv', 'w') as f2:
+    with open('C-V.csv', 'w') as f2:
+        for line in fileone:
+            if line not in filetwo:
+                f2.write(line)
+    with open('Common.csv', 'w') as f3:
+        for line in fileone:
+            if line in filetwo:
+                f3.write(line)
+def compare1(file1,file2):
+    with open(file1, 'r') as t1, open(file2, 'r') as t2:
+        fileone = t1.readlines()
+        filetwo = t2.readlines()
+
+    with open('V-A.csv', 'w') as f1:
+        for line in filetwo:
+            if line not in fileone:
+                f1.write(line)
+    with open('A-V.csv', 'w') as f2:
         for line in fileone:
             if line not in filetwo:
                 f2.write(line)
@@ -23,23 +64,58 @@ def compare(file1,file2):
             if line in filetwo:
                 f3.write(line)
 
+def get_package(file1,file2):
+    with open(file1, 'r') as t1, open(file2, 'r') as t2:
+        fileone = t1.readlines()
+        filetwo = t2.readlines()
+        default=list()
[…]

### 2020-07-07 Scripts/compare_results/test2.py

@@ -1,0 +1,11 @@
+import pandas as pd
+import csv
+
+with open('mindboggle_vendorfalse_info.csv', "r") as f:
+        reader = csv.reader(f, delimiter=" ")
+        filtered = filter(lambda x: x[1] in ("linux-libc-dev-3.16.43-2"), list(reader))
+uni=list()
+for row in filtered:
+    uni.append(row[0])
+req=list(set(uni))
+print(len(req))

### 2020-07-07 Scripts/minification/run_repro_script.sh

@@ -8,14 +8,4 @@ then
   apt-get update -y;
   apt-get install python python-dev python-pip gcc libsqlite3-dev libssl-dev libffi-dev -y;
   pip install -U reprozip;
-  if [ $(dpkg-query -W -f='${Status}' reprozip 2>/dev/null | grep -c "ok installed") -eq 0 ];
-  then
-    echo "Some problem occured: Cannot install Reprozip";
-    command || exit 1;
-  else
-    echo "Reprozip installed successfully";
-  fi
-else
-  echo "Reprozip was already installed"
 fi
-

### 2020-07-07 Scripts/minification/run_script.sh

@@ -1,34 +1,48 @@
 #!/bin/bash
 
+###these commands are image specific ######
 export cmd1='python3 /run.py /data /data/outputs participant --participant_label 0003001 0003002 --license_file /data/license.txt'
 export cmd2='python3 /run.py /data /data/outputs group1 --participant_label 0003001 0003002 --license_file /data/license.txt'
 export cmd3='python3 /run.py /data /data/outputs group2 --participant_label 0003001 0003002 --license_file /data/license.txt'
+###splitting image name and tag
 name1="$(cut -d'/' -f1 <<<"$2")"
 name2="$(cut -d'/' -f2 <<<"$2")"
 name="$(cut -d':' -f1 <<<"$name2")"
+###run image and mount the required dataset
 docker run -itd --entrypoint="bash" --name $name --security-opt seccomp=unconfined -v $1/:/data $2
+###removing outputs folder and required file if already there
 docker exec -i $name bash -c "rm -rf /data/outputs/*"
+docker exec -i $name bash -c "rm -f /data/scripts/required.csv"
+###removing log files if already exist
 rm -f ${name1}_${name}_repro.log
 rm -f ${name1}_${name}_After_repro.log
+###running script inside container to install Reprozip
 docker exec -i $name bash -c "/data/scripts/run_repro_script.sh" &>> ${name1}_${name}_repro.log && echo "[ OK..Reprozip Installed Successfully ]"
-docker exec -i $name bash -c "rm -f /data/scripts/required.csv"
-docker exec -i $name bash -c "reprozip trace echo hello" &>> ${name1}_${name}_repro.log && echo "[ OK..Reprozip traced cmd1 Successfully]"
-#docker exec -i $name bash -c "reprozip trace $cmd1" &>> ${name1}_${name}_repro.log && echo "[ OK..Reprozip traced cmd1 Successfully]"
-#docker exec -i $name bash -c "reprozip trace --continue $cmd2" &>> ${name1}_${name}_repro.log && echo "[ OK..Reprozip traced cmd2 Successfully ]"
-#docker exec -i $name bash -c "reprozip trace --continue $cmd3" &>> ${name1}_${name}_repro.log && echo "[ OK..Reprozip traced cmd3 Successfully ]"
+###running reprozip trace inside container
+docker exec -i $name bash -c "reprozip trace $cmd1" &>> ${name1}_${name}_repro.log && echo "[ OK..Reprozip traced cmd1 Successfully]"
[…]

### 2020-07-07 Scripts/compare_results/test.py
removed csv files

@@ -64,21 +64,6 @@ def compare1(file1,file2):
             if line in filetwo:
                 f3.write(line)
 
-def get_package(file1,file2):
-    with open(file1, 'r') as t1, open(file2, 'r') as t2:
-        fileone = t1.readlines()
-        filetwo = t2.readlines()
-        default=list()
-        for line in filetwo:
-            if line['Vulnerability_ID']:
-                 default.append(line[0])
-        req=list(set(default))
-    with open('default.csv','w') as out:
-        for entry in req:
-            out.write(entry)
-            out.write("\n")
-    file.close()
-
 
 def main():
     file1=sys.argv[1]

### 2020-07-07 Scripts/compare_results/test2.py

@@ -1,11 +1,0 @@
-import pandas as pd
-import csv
-
-with open('mindboggle_vendorfalse_info.csv', "r") as f:
-        reader = csv.reader(f, delimiter=" ")
-        filtered = filter(lambda x: x[1] in ("linux-libc-dev-3.16.43-2"), list(reader))
-uni=list()
-for row in filtered:
-    uni.append(row[0])
-req=list(set(uni))
-print(len(req))

### 2020-07-07 paper.tex
minor fixes

@@
 clusters. Clair has a client-server architecture, in which the server
-maintains a database of vulnerabilities. We use Clair through Clair scanner
+scans Docker images layer by layer and maintains a database of vulnerabilities. We use Clair through Clair-scanner
 (\url{https://github.com/arminc/clair-scanner}), a tool to facilitate the testing
-of container images against a local Clair server. Clair scanner scans the image,
+of container images against a local Clair server. Clair-scanner scans the image,
 prepares the list of vulnerabilities, compares that list against a
@@
 are an extension of Clair scanner for Singularity images. Stools
-directly scan the image files in a local installation of the Clair
-scanner, to circumvent the Docker-specific requirements in the Clair API.
+exports Singularity image to \url{tar.gz} format, masquerading as a single layer docker image
+to circumvent the Docker-specific requirements in the Clair API.
 In our experiments, we use Singularity Tools version 3.2.1 through Docker
@@
 
-\subsection{Linux Releases and Vulnerability Databases}
+\subsection{Ubuntu Releases and its Vulnerability Database}
 
@@
 }
-Through our experiments, we find that image scanners report vulnerabilities 
-differently depending on the different Linux release types. So, it is 
-important to provide an overview of these Linux releases types. 
 BIDS app and Boutiques images in our experiments have diverse Linux
-distributions, such as Ubuntu, CentOS, Debian, and Alpine. Further, a particular
-distribution has different releases in general. To illustrate, we here examine Ubuntu as an example,
-since it is heavily utilized in our experiments. 
+distributions, such as Ubuntu, CentOS, Debian, and Alpine. A particular
+distribution has different releases in general. Regarding Ubuntu, it has different
+types of releases e.g. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release.
+Through our experiments, we find that image scanners report Ubuntu vulnerabilities 
+differently depending on the different Ubuntu release types. It is 
+important to provide an overview of these Ubuntu releases types, 
+since Ubuntu is heavily utilized in our experiments. 
 \todo{Explain the situation with centos, update figure 3 accordingly.}
-However, other distributions also have
-similar release trend. Ubuntu releases
-can be of two types: Regular or Long Term Support (LTS).
-Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
+Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
 reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
-in the form of Extended Security Maintenance (ESM) release.
+in the form of ESM release.
 ESM is a paid service that can be requested from Ubuntu to get security 
-updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu distribution have different vulnerability
+updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu version have different vulnerability
 databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
@@
 17.04, and 17.10, as they reached EOL. However, Ubuntu decided to provide optional extended support for Ubuntu 14.04.
-To use this extended support, users have to purchase ESM release for Ubuntu 14.04.
+To use this extended support, users have to purchase Ubuntu 14.04 ESM release.
 The images in our experiments have Ubuntu 14.04 LTS, so scanners should refer
@@
 
-Ubuntu maintains its vulnerability database in the Ubuntu Launchpad or the Ubuntu CVE Tracker. For a given CVE, there is an entry for all ubuntu releases.
+Ubuntu maintains its vulnerability database in the Ubuntu CVE Tracker. For a given CVE, there is an entry for all ubuntu releases.
 Ubuntu releases are listed with the package name
@@
 %Clair is only referring to Ubuntu 14.04 ESM release. 
-%The reasons of Clair showing
-%false positives and false negatives are unclear. We reported this issue on two Google groups of Clair i.e CoreOS Dev and
-%clair-dev \href{https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc}{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}
+The reasons of Clair showing
+false positives and false negatives are unclear. We reported this issue on two Google groups of Clair i.e CoreOS Dev and
+clair-dev \href{https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc}{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}
 

### 2020-07-13 paper.tex
fixed databases

@@
 \usepackage{titlesec}
+\usepackage{anyfontsize}
 \usepackage[flushleft]{threeparttable}
@@
 \title{Vulnerability Analysis of Container Images in Neuroimaging}
+\begin{filecontents*}{resul.csv}
+labels,names,A,C,V,Stools
+a,bids/example,838,663,683,
+b,bids/freesurfer,353,215,192,
+c,bids/ndmg,934,757,782,
+d,\textcolor{red}{bids/broccoli:v1.0.0},79,79,117,
+e,bids/fibredensityandcrosssection,1086,849,868,
+f,bids/spm,191,246,235,
+g,poldracklab/mriqc:0.15.0,432,328,332,
+h,bids/cpac:v1.0.1a\_22,698,524,535,
+I,bids/hyperalignment,1717,1327,1433,
+j,bids/mindboggle:0.0.4-1,671,955,569,
+k,bids/mrtrix3\_connectome,275,157,158,
+l,bids/rs\_signal\_extract:0.1,867,454,473,
+m,bids/aa:v0.2.0,189,244,233,
+n,bids/niak,1482,1366,1420,
+o,bids/oppni:v0.7.0-1,913,698,723,
+p,poldracklab/fmriprep:unstable,516,355,393,
+q,bids/brainiak-srm,897,484,503,
+r,bids/nipypelines:0.3.0,641,878,451,
+s,bids/hcppipelines:v3.17.0-18,526,873,620,
+t,bids/magetbrain,112,117,126,
+u,bids/tracula:v6.0.0-4,874,664,683,
+v,bids/baracus,172,238,216,
+w,bids/antscorticalthickness:v2.2.0-1,289,27,no oval data,
+x,bids/dparsf:v4.3.12,507,750,757,
+y,bids/afni\_proc,67,16,no oval data,
+z,bids/rshrf:1.0.1,5,3,3,
+aa,bids/ndmg:v0.1.0,934,758,782,
+ab,\textcolor{red}{mcin/qeeg:latest},46,46,142,
+ac,\textcolor{red}{camarasu/creaphase:0.3},54,54,186,
+ad,\textcolor{red}{bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest},70,76,157,
+ae,\textcolor{red}{mcin/docker-fsl:latest},75,75,201,
+af,gkiar/onevoxel:v0.3.0rc2,5,2,2,
+ag,\textcolor{red}{bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest},70,76,157,
+ah,\textcolor{red}{bt5e/ants:latest},150,156,336,
+ai,poldracklab/fmriprep:1.2.3,591,441,447,
+aj,gkiar/dwipreproc\_fsl-5.0.11\_minified,391,258,263,
+ak,gkiar/mask2boundary:v0.1.0,15,11,11,
+al,\textcolor{red}{mcin/ica-aroma:latest},75,75,202,
+am,c3genomics/genpipes,,,,99
+an,bioinformatics-group/aqua-singularity-recipe,,,,7
+ao,MontrealSergiy/BEst,,,,106
+ap,shub://aces/cbrain-containers-recipes:fsl\_v6.0.1,,,,206
+aq,shots47s/bids-freesurfer-6.0,,,,212
+ar,shots47s/bids-fmriprep-1.2.3,,,,453
+\end{filecontents*}
 
@@
 
-\todo{Add related work on vulnerability scanning}
-
 \section{Materials and Tools}
@@
 To get a vulnerability feed of various OS distributions, Anchore refers to
-different sources. The Figure~\ref{anchore} displays a list of all sources
+different sources. The Table~\ref{database} displays a list of all sources
 that it refers at the time of this study.
@@
 %vulnerability data related to Ubuntu
-\tristan{You need to be accurate on these sources, this is not ``for instance". 
-You should list all the sources used in the experiments, for all image types: Ubuntu but also CentOS, Debian, Alpine.}.
 
-\begin{figure*}[!ht]
-    \centering
-	\begin{subfigure}[t]{0.3\textwidth}
-        \includegraphics[height=2.0in]{Figures/anchore.png}
-        \caption{Anchore}
-        \label{anchore}
-    \end{subfigure}%
-    ~ 
-	\begin{subfigure}[t]{0.3\textwidth}
-        \includegraphics[height=2.5in]{Figures/vuls.png}
-        \caption{Vuls}
-        \label{vuls}
-    \end{subfigure}
-     ~
-	\begin{subfigure}[t]{0.3\textwidth}
-        \includegraphics[height=2.0in]{Figures/clair.png}
-        \caption{Clair}
-	\label{clair}
-    \end{subfigure}
-    \caption{Vulnerability databases used by scanners}
+%\begin{figure*}[!ht]
+%    \centering
+%	\begin{subfigure}[t]{0.3\textwidth}
+%        \includegraphics[height=2.0in]{Figures/anchore.png}
+%        \caption{Anchore}
+%        \label{anchore}
+%    \end{subfigure}%
+%    ~ 
+%	\begin{subfigure}[t]{0.3\textwidth}
+%        \includegraphics[height=2.5in]{Figures/vuls.png}
+%        \caption{Vuls}
+%        \label{vuls}
+%    \end{subfigure}
+%     ~
+%	\begin{subfigure}[t]{0.3\textwidth}
+%        \includegraphics[height=2.0in]{Figures/clair.png}
+%        \caption{Clair}
+%	\label{clair}
+%    \end{subfigure}
+%    \caption{Vulnerability databases used by scanners}
+%    \label{database}
+%\end{figure*}
+\begin{figure*}
+\begin{tabular}{ |c|c|c|c| }
+ \hline
+\textbf{OS} &	\textbf{Anchore} &	\textbf{Vuls} &	\textbf{Clair} \\
+\hline
+	\textbf{Alpine} & Alpine-SecDB &	Alpine-SecDB &	Alpine-SecDB \\
+\hline
+	\textbf{CentOS} & Red Hat Enterprise Linux Oval & Red Hat Enterprise Linux OVAL And Red Hat Security Advisories & Red Hat Security Data \\
+\hline
+	\textbf{Debian} & Debian Security Bug Tracker &	Debian OVAL and Debian Security Bug Tracker & Debian Security Bug Tracker \\
+\hline
+	\textbf{Ubuntu} & Ubuntu CVE Tracker &	Ubuntu OVAL &	Ubuntu CVE Tracker \\
+ \hline
+\end{tabular}
+\caption{Vulnerability databases used by scanners for different OS distributions}
 \label{database}
@@
 \texttt{vuls/vuls:latest}. At the time of this study, Vuls gets vulnerability feed
-from a configured set of sources, which are listed in Figure~\ref{vuls}.
+from a configured set of sources, which are listed in the Table~\ref{database}.
 %from the Open Vulnerability
 %and Assessment Language (OVAL) database 
-\tristan{Does it contain
-vulnerabilities for all distributions?} 
-\tristan{The Vuls website says that it uses multiple vulnerability databases: https://vuls.io/docs/en/main-features.html Are you sure 
-that you only used OVAL and if so, why?}. According to this list, Vuls
+According to this list, Vuls
 refers to OVAL database for some distribution e.g. Ubuntu, Debian, etc.
@@
 order to make a fair comparison between scanners.
-\tristan{What is this whitelist about, and which one did you use?}. Clair
-scanner maintains a Docker image with the up-to-date vulnerability
-database from a set of different sources listed in Figure~\ref{clair}.  \tristan{Please mention the vulnerability sources for all distributions}.
+Clair scanner maintains a Docker image with the up-to-date vulnerability
+database from a set of different sources listed in the Table~\ref{database}.
 We use Clair-scanner version 2.0.6, executed through
@@
 are an extension of Clair scanner for Singularity images. Stools
-exports Singularity image to \url{tar.gz} format, masquerading as a single layer docker image
+exports Singularity image to \texttt{tar.gz} format, masquerading as a single layer docker image
 to circumvent the Docker-specific requirements in the Clair API.
@@
 \href{https://github.com/singularityhub/stools}{Stools Github} to scan
-Singularity images. \tristan{which docker images did you use for clair and clair database?}
+Singularity images.
 
@@
 
-\tristan{This section is still very confusing. I can rewrite it but would first need to
-have a clear picture of vulnerability statuses across the tested Linux distributions. 
-Are vulnerability statuses present only in Ubuntu, or are there statuses in other distributions too?
-If so, what are the vulnerability statuses in the other distributions?
-}
 BIDS app and Boutiques images in our experiments have diverse Linux
@@
 since Ubuntu is heavily utilized in our experiments. 
-\todo{Explain the situation with centos, update figure 3 accordingly.}
 Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
@@
 Reprozip~\cite{rampin2016reprozip}, which is a open-source tool that
-helps scientists to make their research reproducible \tristan{No it doesn't make applications reproducible}. This tool traces operating system calls used by the
+helps scientists to make their research reproducible. This tool traces operating system calls used by the
 application while execution, and then based on this trace, it recognizes binaries, files, environment variables,
@@
 These command lines represent how applications should be used.
-\tristan{How did you run the applications? Which command lines, why, etc}. Following that, the list
+Following that, the list
 is expanded by adding important and required packages that are essential
@@
 ~\cite{debtree}, which is avaiable in Debian and Ubuntu. It's alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
-gives a complete dependency tree of a particular package.\tristan{does debtree work in centos? if not, how do you minimize centos images?}.
+gives a complete dependency tree of a particular package.
 Effectively all needed packages are kept and remaining unnecessary packages are removed. We use
 \href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
-the image size reduction process \tristan{Can we please have at least a README for these scripts?}, which install Reprozip in the image, collect Reprozip trace, and
+the image size reduction process, which install Reprozip in the image, collect Reprozip trace, and
 finally delete all unnecessary packages.
@@
 
+%\csvreader[tabular=|l|l|l|l|l|l|,
+%         table head=\hline \textbf{ First Name} & \textbf{Last Nmae} & {a} & {b} & {c} & {d}\\\hline,
+%     late after line = \\\hline]%
+% {resul.csv}{labels=\labels,names=\names,A=\A,C=\C,V=\V,Stools=\Stools}%
+%         {\labels & \names & \A & \C & \V & \Stools}%
+%
+
 \begin{table*}[!ht]
 \csvreader[%
- respect all,%
-  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
-      \begin{adjustbox}{max width=\textwidth},
-  after reading=\end{adjustbox},
- tabular={c |c | c | c | c |c},
-	table head =Image Labels &{Image names} & {Anchore} & {Clair} & {Vuls} &{Stools}\\\hline,
+ %respect all,%
+ % before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
+  %    \begin{adjustbox}{max width=\textwidth},
+  %after reading=\end{adjustbox},
+ tabular={|c|c|c|c|c|c|},
+	table head = \hline\textbf{Image Labels} &\textbf{{Image names}} & \textbf{Anchore} & \textbf{Clair} & \textbf{Vuls} & \textbf{Stools}\\\hline,
 	late after line= \\,
-        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
-]{fullresults.csv}{}{\csvlinetotablerow}%
+        late after last line=\\\hline %
+	]{resul.csv}{labels=\labels,names=\names,A=\A,C=\C,V=\V,Stools=\Stools}%
+        {\labels & \names & \A & \C & \V & \Stools}
        \centering
-        \caption{\label{table1}Number of vulnerabilities by scanners}
+	\vspace*{1mm}
+	\caption{\label{table1}Number of vulnerabilities by scanners (all Centos images are highlighted)} 
 \end{table*}
@@
         {Figures/vulngraph.pdf}}
+	\vspace*{-7mm}
         \caption{\label{fig:graph1} Number of vulnerabilities by packages}
@@
         {Figures/venn.pdf}}
-        \caption{\label{fig:venn} Scanner results}
+	\vspace*{-10mm}
+	\caption{\label{fig:venn} Scanner results (excluding non-comparable image results)}
 \end{figure}
@@
 the scanners in Docker images and the overlap between them.
-This figure excludes Centos Docker images because scanners report results in different
+This Figure excludes Centos Docker images (highlighted images in Table\~ref{table1}) because scanners report results in different
 formats for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
-to report pending patches that need to be applied to specific packages
-,whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
+to report pending patches that need to be applied to specific packages,
+whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
 vulnerabilities in packages. Also, we excluded two other images \texttt{bids/antscorticalthickness:v2.2.0-1} and
 \texttt{bids/afni\_proc} from this figure, since we do not have Vuls scanning results for these images.
-\tristan{According to our discussion, this is only for Ubuntu. This should be clarified.}
 
@@
         {Figures/vulnwithupdate.pdf}}
+	\vspace*{-7mm}
         \caption{\label{fig:graph2} Number of vulnerabilities before and
@@
         {Figures/bargraph.png}}
+	\vspace*{-5mm}
         \caption{\label{fig:bargraph} Vulnerabilities by different experiments}
@@
 
-\textbf{False negatives:} False negative reporting is detected. Clair-scanner and Vuls
+\textbf{Misses:} Clair-scanner and Vuls
 are missing vulnerabilities that they should have detected. For example, the CVE-2016-9082 
@@
 
-\textbf{False positives:} False positive reporting is also detected. For instance,
-there are false positives in clair-scanner.
+\textbf{Wrong Detections:} 
 Some vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
-present inside the image, however, Clair-scanner have reported such vulnerabilities.
+present inside the image, however, Clair have reported such vulnerabilities.
 For instance, CVE-2019-1274 is an example of such vulnerabilities. 
@@
 %Clair is only referring to Ubuntu 14.04 ESM release. 
-The reasons of Clair showing
-false positives and false negatives are unclear. We reported this issue on two Google groups of Clair i.e CoreOS Dev and
-clair-dev \href{https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc}{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}
+We reported this issue on two Google groups of Clair i.e CoreOS Dev and
+clair-dev \url{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}
 

### 2020-07-13 Scripts/graphs/barchart.py

@@ -3,7 +3,7 @@ import pandas as pd
 import matplotlib.pyplot as plt
 
 # data to plot
-d = pd.read_csv(r"../allResults.csv")
+d = pd.read_csv(r"../../allResults.csv")
 df=pd.DataFrame(d)
 imageID=[]
 before=[]

### 2020-07-13 Scripts/graphs/drawVenn.py

@@ -18,5 +18,5 @@ for text in v.set_labels:
 for text in v.subset_labels:
     text.set_fontsize(15)
 # Show it
-plt.savefig('venn.pdf',dpi=2000)
-
+#plt.savefig('venn.pdf',dpi=2000)
+plt.show()

### 2020-07-16 paper.tex
fixes

@@
 labels,names,A,C,V,Stools
-a,bids/example,838,663,683,
-b,bids/freesurfer,353,215,192,
-c,bids/ndmg,934,757,782,
+a,bids/example:latest,838,663,683,
+b,bids/freesurfer:latest,353,215,192,
+c,bids/ndmg:latest,934,757,782,
 d,\textcolor{red}{bids/broccoli:v1.0.0},79,79,117,
-e,bids/fibredensityandcrosssection,1086,849,868,
-f,bids/spm,191,246,235,
+e,bids/fibredensityandcrosssection:latest,1086,849,868,
+f,bids/spm:latest,191,246,235,
 g,poldracklab/mriqc:0.15.0,432,328,332,
 h,bids/cpac:v1.0.1a\_22,698,524,535,
-I,bids/hyperalignment,1717,1327,1433,
+I,bids/hyperalignment:latest,1717,1327,1433,
 j,bids/mindboggle:0.0.4-1,671,955,569,
-k,bids/mrtrix3\_connectome,275,157,158,
+k,bids/mrtrix3\_connectome:latest,275,157,158,
 l,bids/rs\_signal\_extract:0.1,867,454,473,
 m,bids/aa:v0.2.0,189,244,233,
-n,bids/niak,1482,1366,1420,
+n,bids/niak:latest,1482,1366,1420,
 o,bids/oppni:v0.7.0-1,913,698,723,
 p,poldracklab/fmriprep:unstable,516,355,393,
-q,bids/brainiak-srm,897,484,503,
+q,bids/brainiak-srm:latest,897,484,503,
 r,bids/nipypelines:0.3.0,641,878,451,
 s,bids/hcppipelines:v3.17.0-18,526,873,620,
-t,bids/magetbrain,112,117,126,
+t,bids/magetbrain:latest,112,117,126,
 u,bids/tracula:v6.0.0-4,874,664,683,
-v,bids/baracus,172,238,216,
-w,bids/antscorticalthickness:v2.2.0-1,289,27,no oval data,
+v,bids/baracus:latest,172,238,216,
+w,bids/antscorticalthickness:v2.2.0-1,289,27,no OVAL data,
 x,bids/dparsf:v4.3.12,507,750,757,
-y,bids/afni\_proc,67,16,no oval data,
+y,bids/afni\_proc:latest,67,16,no OVAL data,
 z,bids/rshrf:1.0.1,5,3,3,
@@
 ac,\textcolor{red}{camarasu/creaphase:0.3},54,54,186,
-ad,\textcolor{red}{bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest},70,76,157,
+ad,\textcolor{red}{bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest:latest},70,76,157,
 ae,\textcolor{red}{mcin/docker-fsl:latest},75,75,201,
 af,gkiar/onevoxel:v0.3.0rc2,5,2,2,
-ag,\textcolor{red}{bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest},70,76,157,
+ag,\textcolor{red}{bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest:latest},70,76,157,
 ah,\textcolor{red}{bt5e/ants:latest},150,156,336,
 ai,poldracklab/fmriprep:1.2.3,591,441,447,
-aj,gkiar/dwipreproc\_fsl-5.0.11\_minified,391,258,263,
+aj,gkiar/dwipreproc\_fsl-5.0.11\_minified:latest,391,258,263,
 ak,gkiar/mask2boundary:v0.1.0,15,11,11,
@@
 High Performance Computing (HPC) clusters. However, the security of containers
-still remains the concerning issue. Here, we focus on the security of container
-images in particular. Container images are often built for the entire
-duration of an analysis, so scientific researchers do not prefer to update
+still remains a concerning issue. Here, we focus on the security of container
+images, which are often built for the entire
+duration of an analysis, so scientific researchers prefer not to update
 them. Consequently, their chances of containing vulnerabilities increases.  
@@
 According to this list, Vuls
-refers to OVAL database for some distribution e.g. Ubuntu, Debian, etc.
+refers to Open Vulnerability and Assessment Language (OVAL) database for some distribution e.g. Ubuntu, Debian, etc.
 It is worth noting that there is
@@
 
-BIDS app and Boutiques images in our experiments have diverse Linux
+BIDS apps and Boutiques images in our experiments have diverse Linux
 distributions, such as Ubuntu, CentOS, Debian, and Alpine. A particular
@@
 out which packages we need for the pipeline to function properly. To allow for that, we utilize
-Reprozip~\cite{rampin2016reprozip}, which is a open-source tool that
+Reprozip~\cite{rampin2016reprozip}, an open-source tool that
 helps scientists to make their research reproducible. This tool traces operating system calls used by the
-application while execution, and then based on this trace, it recognizes binaries, files, environment variables,
+application during execution, and then based on this trace, it recognizes binaries, files, environment variables,
 and library dependencies that are used by the application for future re-execution. If the OS is
@@
 
-Following the above two approaches, we employ a hybrid approach, where
+Following the two previous approaches, we employ a hybrid approach, where
 we combine both update and size reduction processes in an attempt to
 lessen number of vulnerabilities or to test the effect of
-combining two approaches. To allow for that, we first update all packages
+combining two approaches. To allow for that, we first update all packages in
 the image, then delete all unnecessary packages. Applying these processes in reverse
@@
 In this section,
-we first discuss our detected vulnerabilities in the images, using the three scanners, and compare the
-results. We then discuss the effect of the image updating/minimizing and applying the hybrid
+we first discuss the detected vulnerabilities in the images and compare the
+results. We then discuss the effect of updating/minimizing the image and applying the hybrid
 approach on the detected vulnerabilities.
@@
 Table~\ref{table1} shows the number of detected vulnerabilities in the different images,
-detected by each of the scanners.
+detected by each of the scanners. Image labels from \texttt{a} to \texttt{al} represents
+Docker images, whereas remaining ones belong to Singularity. It is worth noting that Vuls
+is not able to scan two Docker images \textttt{w} and \textttt{y} because these images
+have Ubuntu 17.04 and 17.10 respectively, and there is no vulnerability data for these
+distributions in OVAL database, which Vuls refers for scanning. 
 Interestingly, our experiments concluded considerable discrepancies in the results obtained by

### 2020-07-17 paper.tex
content fix 1

@@
 \journal{gigascience}
-
 %%%% Packages %%%%
@@
 c,bids/ndmg:latest,934,757,782,
-d,\textcolor{red}{bids/broccoli:v1.0.0},79,79,117,
+d,\textbf{bids/broccoli:v1.0.0},79,79,117,
 e,bids/fibredensityandcrosssection:latest,1086,849,868,
@@
 aa,bids/ndmg:v0.1.0,934,758,782,
-ab,\textcolor{red}{mcin/qeeg:latest},46,46,142,
-ac,\textcolor{red}{camarasu/creaphase:0.3},54,54,186,
-ad,\textcolor{red}{bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest:latest},70,76,157,
-ae,\textcolor{red}{mcin/docker-fsl:latest},75,75,201,
+ab,\textbf{mcin/qeeg:latest},46,46,142,
+ac,\textbf{camarasu/creaphase:0.3},54,54,186,
+ad,\textbf{bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest:latest},70,76,157,
+ae,\textbf{mcin/docker-fsl:latest},75,75,201,
 af,gkiar/onevoxel:v0.3.0rc2,5,2,2,
-ag,\textcolor{red}{bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest:latest},70,76,157,
-ah,\textcolor{red}{bt5e/ants:latest},150,156,336,
+ag,\textbf{bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest:latest},70,76,157,
+ah,\textbf{bt5e/ants:latest},150,156,336,
 ai,poldracklab/fmriprep:1.2.3,591,441,447,
@@
 ak,gkiar/mask2boundary:v0.1.0,15,11,11,
-al,\textcolor{red}{mcin/ica-aroma:latest},75,75,202,
+al,\textbf{mcin/ica-aroma:latest},75,75,202,
 am,c3genomics/genpipes,,,,99
@@
 \affil[1]{Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada}
-
 \maketitle
@@
 
-Today, containers, which provide operating system level virtualization, are
+Today, containers, which provide operating-system level virtualization, are
 popular. Correspondingly, they are widely used for scientific data analyses on 
@@
 This study is a vulnerability analysis of container images used in HPC
-clusters. Container images contain complete operating-system distributions,
-including the data analysis software and its required dependencies.
+clusters. Container images contain complete operating-system distributions, including
+the data analysis software and its required dependencies.
 Images are rarely updated, as they are often built once
@@
 and the integrity of user data. We report vulnerability analyses produced
-by four popular image scanning tools, Anchore, Vuls, Clair-scanner and Stools.
+by four popular image scanning tools, Anchore, Vuls, Clair, and Stools.
 
@@
 The next section describes the materials and tools used in the experiments,
-including image scanners and container images. We then describe our image
+including container images and image scanners. We then describe our image
 update and minimization methodology to reduce vulnerabilities. Results review
@@
 
-%This paper is organized as follows: in the next section, we provide a description
-%of materials and methods which summarize our experiments. We also explain different
-%image scanners used to report
-%vulnerabilities in container images. The next section of this paper provides the results, where we
-%present a number of existing vulnerabilities in the container images
-%used for data analysis on shared HPC clusters. We then proceed in the following section with 
-%discussion and analysis of these results, where we provide more insight into the problems that 
-%we faced while conducting these experiments. We also propose some
-%particular rules that can be followed to secure container images. Finally, conclusions are drawn
-%in the last section of the paper.
-
-%%%%%%%%%Related Work%%%%%%%
 The existing research work on containers focuses mainly on the security of containers.
@@
 the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis}.
-Other work studied security vulnerabilities on Docker hub. A study in 2015 by Gummaraju et al.
+Other work studied security vulnerabilities in Docker images. A study in 2015 by Gummaraju et al.
 states that over 30\% of official images in docker hub contain high priority 
@@
 in container images and attempt to examine the effect of different
-manipulation of these images, it is needed to have a representative set of
+manipulations on these images, it is needed to have a representative set of
 images. Additionally, for the purpose of detecting vulnerabilities,
@@
 
-We scan a total of 44 container images taken from two containerization frameworks
+We scan all container images, available at the time of this study, on two containerization frameworks
 used in neuroscience: BIDS
-apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}.
+apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}, totalling
+44 container images.
 Out of these 44 images, 26 were obtained from BIDS apps
@@
 and 18 from Boutiques. In fact, at the time of the study, BIDS apps had 27 images,
-out of which one wasn't available on DockerHub. Boutiques had 49 images, listed using
-Boutiques \texttt{bosh search} command,
+out of which one wasn't available on DockerHub. Boutiques had 49 images,
+%listed using Boutiques \texttt{bosh search} command,
 however, only 23 unique images were listed, out of which 3 couldn't be retrieved and 2
@@
 images while Stools support Singularity. Different vulnerabilities may be
-reported if scanning experiments take place on different dates.
+reported by scanners if scanning experiments take place on different dates.
 To avoid such discrepancies, we freeze the vulnerability
@@
 Anchore is an end-to-end, open-source container security platform. It
-analyses container images and lists OS
+analyze	container images and lists OS
 packages, non-OS packages (Python, Java, Gem, and Npm), and files.
@@
 To get a vulnerability feed of various OS distributions, Anchore refers to
-different sources. The Table~\ref{database} displays a list of all sources
-that it refers at the time of this study.
+different sources. Table~\ref{database} displays Anchore's vulnerability sources for
+Ubuntu, Debian, Alpine, and Centos, which are present inside taken images.
+Anchore also refers to National
+Vulnerability Database (NVD) to get metadata of vulnerabilities.
 
-%for instance, Ubuntu launchpad database to get
-%vulnerability data related to Ubuntu
-
-%\begin{figure*}[!ht]
-%    \centering
-%	\begin{subfigure}[t]{0.3\textwidth}
-%        \includegraphics[height=2.0in]{Figures/anchore.png}
-%        \caption{Anchore}
-%        \label{anchore}
-%    \end{subfigure}%
-%    ~ 
-%	\begin{subfigure}[t]{0.3\textwidth}
-%        \includegraphics[height=2.5in]{Figures/vuls.png}
-%        \caption{Vuls}
-%        \label{vuls}
-%    \end{subfigure}
-%     ~
-%	\begin{subfigure}[t]{0.3\textwidth}
-%        \includegraphics[height=2.0in]{Figures/clair.png}
-%        \caption{Clair}
-%	\label{clair}
-%    \end{subfigure}
-%    \caption{Vulnerability databases used by scanners}
-%    \label{database}
-%\end{figure*}
 \begin{figure*}
@@
 scanning. In our experiments, we use remote dynamic scanning, that is, Vuls
-starts a container for every image to test, and queries the package manager
-in the image through SSH. We use Vuls 0.9.0, executed through Docker image
-\texttt{vuls/vuls:latest}. At the time of this study, Vuls gets vulnerability feed
-from a configured set of sources, which are listed in the Table~\ref{database}.
-%from the Open Vulnerability
-%and Assessment Language (OVAL) database 
-According to this list, Vuls
-refers to Open Vulnerability and Assessment Language (OVAL) database for some distribution e.g. Ubuntu, Debian, etc.
+connects to the running containers that needs to be scanned through SSH, and queries the package manager
+in the container. We use Vuls 0.9.0, executed through Docker image
+\texttt{vuls/vuls:0.9.0}. At the time of this study, Vuls gets vulnerability feed
+from a configured set of sources. Table~\ref{database} lists vulnerability databases
+referred by Vuls for scanned four OS distributions i.e. Alpine, Ubuntu, Debian, and Centos.
+Apart from this, like Anchore, Vuls also refers NVD database for getting vulnerability metadata.
+Table~\ref{database} shows that Vuls
+refers to Open Vulnerability and Assessment Language (OVAL) database for Ubuntu, Debian, and Centos.
 It is worth noting that there is
-no OVAL data for Ubuntu 17.04 and 17.10 distributions, meaning that images
+no vulnerability data for Ubuntu 17.04 and 17.10 distributions in OVAL database, meaning that images
 with these distributions cannot be scanned with Vuls.
@@
 of container images against a local Clair server. Clair-scanner scans the image,
-prepares the list of vulnerabilities, compares that list against a
+prepares a list of vulnerabilities, compares that list against a
 whitelist, and flags vulnerabilities that are not present in the whitelist.
@@
 order to make a fair comparison between scanners.
-Clair scanner maintains a Docker image with the up-to-date vulnerability
-database from a set of different sources listed in the Table~\ref{database}.
-We use Clair-scanner version 2.0.6, executed through
+Clair-scanner maintains a Docker image with the up-to-date vulnerability
+database from a set of different sources. Table~\ref{database} lists
+vulnerability databases that Clair referred for Alpine, Ubuntu, Debian, and Centos.
+Clair also uses NVD database for getting vulnerability metadata.
+We use Clair version 2.0.6, executed through
 Docker image \texttt{arminc/clair-local-scan:v2.0.6}. For the vulnerability
@@
 Singularity Tools (Stools)
-are an extension of Clair scanner for Singularity images. Stools
-exports Singularity image to \texttt{tar.gz} format, masquerading as a single layer docker image
+are an extension of Clair for Singularity images. Stools
+exports Singularity images to \texttt{tar.gz} format, acting as a single layer Docker image
 to circumvent the Docker-specific requirements in the Clair API.
@@
 image \texttt{arminc/clair-db:latest} for referring to vulnerability feed.
-We follow the steps mentioned in
-\href{https://github.com/singularityhub/stools}{Stools Github} to scan
-Singularity images.
+Since Stools uses Clair internally for scanning, vulnerability databases used
+by Stools are same as mentioned for Clair.
+To scan Singularity images, we follow the steps mentioned in
+\href{https://github.com/singularityhub/stools}{Stools Github}.
 
@@
 
-BIDS apps and Boutiques images in our experiments have diverse Linux
-distributions, such as Ubuntu, CentOS, Debian, and Alpine. A particular
+BIDS apps and Boutiques images in our experiments have four Linux
+distributions i.e. Ubuntu, CentOS, Debian, and Alpine. A particular
 distribution has different releases in general. Regarding Ubuntu, it has different
@@
 even without purchase, however, this may lead to discrepancies in results.
-%If scanners refer to ESM release for 
-%vulnerability data, it may lead to discrepancies in results.
 Further, if an image is using a Linux release where EOL has been reached that image may
 turns to be vulnerable as it is not possible to retrieve any updates.
-%Also, if ubuntu release with ended support is used in images, there are no chances of getting updates, hence
-%resulting in vulnerable images.
 
@@
 \end{figure}
-
-%\begin{figure*} \centering{
-%\includegraphics{status.pdf}}
-%\caption{Experiment 1}
-%\end{figure*}
-
-%\includegraphics[width=300, max width=\textwidth]{status.pdf}
-
-%\begin{table*}[!ht]
-%\csvreader[%
-% respect all,%
-%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
-%      \begin{adjustbox}{max width=\textwidth},
-%  after reading=\end{adjustbox},
-% tabular={c |c | c | c | c | c | c | c| c | c},
-%	table head =Image Labels & {Image names} & {Anchore} & {Clair} & {Vuls} &{Stools} & {a} & {b} & {c} & {d}\\\hline,
-% late after line= \\,
-%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
-%]{status.csv}{}{\csvlinetotablerow}%
-%       \centering
-%        \caption{\label{status}Number of vulnerabilities by scanners}
-%\end{table*}
-
+\vspace*{-7mm}
 \section{Reducing the amount of vulnerabilities}
@@
 images.
-
+\vspace*{-2mm}
 \subsection{Image Update Process}
@@
 get different results.
-%which means that the image cannot be used to verify the research
-%findings of other scientists.
+\vspace*{-2mm}
+\subsection{Image Minimization Process}
 
-\subsection{Image Minimization Process}
 We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
@@
 ahead of time will disallow the update process to take place.
-%Finally, we combine both update and size reduction process
-%to lessen the number of vulnerabilities.
-%Therefore, in this process we first update all the packages in the image and then deletes
-%the unnecessary packages. For this process we used the same scripts that
-%we used for earlier experiments.
-%\begin{comment}
-%\subsection{CBRAIN}
-%
-%\href{http://github.com/aces/cbrain}{CBRAIN}~\cite{sherif2014cbrain} is a web portal that is
-%used for the processing of distributed data on various storage locations of computing
-%clusters. CBRAIN system deployed by Montreal Neurological Institute depends on the infrastructure
-%delivered by Compute Canada~\cite{das2016mni}.
-%It is also used by CONP to exploit services of Compute Canada. CBRAIN is a collaborative
-%neuroimaging research platform that is active in production since 2009. CBRAIN
-%provides transparent access to various distributed storage sites and computing
-%resources across the world. CBRAIN’s infrastructure consists of three main
-%layers, namely access layer, service layer, and infrastructure layer~\cite{sherif2014cbrain}. The access
-%layer is for CBRAIN users, and can be accessed through any modern browser or
-%RESTful API. The service layer consists of CBRAIN portal, which contains
-%metadata and databases. It provides information about users, their permissions,
-%resources etc. The infrastructure layer consists of data resources and computing
-%resources, which are connected through a network. 
-%CBRAIN supports Docker, Singularity, BIDS apps, and Boutiques.
-%CBRAIN users uses a portal
-%account on the cluster. Users are only able to
-%run pre-defined applications on the cluster through the CBRAIN portal.
-%\end{comment}
+\vspace*{-2mm}
 \section{Results}
@@
 findings.
-
+\vspace*{-2mm}
 \subsection{Detected Vulnerabilities}
@@
 detected by each of the scanners. Image labels from \texttt{a} to \texttt{al} represents
-Docker images, whereas remaining ones belong to Singularity. It is worth noting that Vuls
-is not able to scan two Docker images \textttt{w} and \textttt{y} because these images
-have Ubuntu 17.04 and 17.10 respectively, and there is no vulnerability data for these
-distributions in OVAL database, which Vuls refers for scanning. 
-Interestingly, our experiments concluded considerable discrepancies in the results obtained by
-these scanners. In particular, in most cases,
-Anchore reports more vulnerabilities than Vuls and Clair-scanner resulting in 
-the Jaccard coefficient of 0.59 with both,
-whereas Vuls and Clair-scanner share more common vulnerability detection resulting to the Jaccard coefficient of 0.83.
+Docker images, whereas remaining ones belong to Singularity.
+Vuls shows \textit{no OVAL data} for image \texttt{w} and \texttt{y},
+which have Ubuntu 17.04 and 17.10 OS distribution respectively. This is because there is no
+vulnerability data present in OVAL database, which Vuls refers for Ubuntu distributions, for these two releases.
 
 Figure~\ref{fig:graph1} provides more image-specific information.
-It represents the number of vulnerabilities that are present inside images.
+It represents the number of vulnerabilities that are present inside each images.
 The overall trend shows that as the number of packages increases in the image, the number of vulnerabilities
 also get increased.
-The figure also infers that Alpine distribution, being a
+The Figure also infers that the Alpine distribution, being a
 lightweight distribution, has the least number of vulnerabilities, whereas more vulnerabilities are reported for
-Ubuntu as it contains more packages.
+distributions with more packages such as Ubuntu.
 We also analyze that out of the total Docker images scanned by our experiments, Debian reports more high vulnerabilties, as
 classified by databases, than others.
-%\begin{table*}
-%\csvreader[%
-% respect all,%
-%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
-%      \begin{adjustbox}{max width=\textwidth},
-%  after reading=\end{adjustbox},
-% tabular={c |c | c | c | c |c},
-%	table head =Image Labels &{Image names} & {OS} & {Anchore} & {Clair} & {Vuls}\\\hline,
-% late after line= \\,
-%        late after last line=\\\hline %\multicolumn{5}{c}{Total Score: 1481}
-%]{results.csv}{}{\csvlinetotablerow}%
-%       \centering
-%	\caption{\label{table1}Existing number of Vulnerabilities}
-%\end{table*}
-
-%\csvreader[tabular=|l|l|l|l|l|l|,
-%         table head=\hline \textbf{ First Name} & \textbf{Last Nmae} & {a} & {b} & {c} & {d}\\\hline,
-%     late after line = \\\hline]%
-% {resul.csv}{labels=\labels,names=\names,A=\A,C=\C,V=\V,Stools=\Stools}%
-%         {\labels & \names & \A & \C & \V & \Stools}%
-%
-
 \begin{table*}[!ht]
 \csvreader[%
- %respect all,%
- % before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
-  %    \begin{adjustbox}{max width=\textwidth},
-  %after reading=\end{adjustbox},
  tabular={|c|c|c|c|c|c|},
@@
 
-%\begin{figure*}[b]
-%        {\includegraphics[width=\textwidth]
-%        {Figures/vulnwithupdate.pdf}}
-%        \caption{\label{fig:graph2} Number of vulnerabilities before and
-%        after update of the images}
-%      \end{figure*}
-
 \subsection{Discrepancies between Scanners}
 
+Our experiments concluded considerable discrepancies in the results obtained by
+these scanners. %We higlighted all Centos images in the Table~\ref{table1} since.
+While comparing scanner results, we exluded all Centos images (highlighted images in Table~\ref{table1})
+and two other images \texttt{w} and
+\texttt{y}. The reason behind excluding Centos images is that scanners report results using different
+vulnerability identifiers for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
+to report pending patches that need to be applied to specific packages,
+whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
+vulnerabilities in packages. We exluded \texttt{w} and \texttt{y} images because Vuls
+can not scan these image, hence no results to compare.
+In most cases,
+Anchore reports more vulnerabilities than Vuls and Clair resulting in 
+the Jaccard coefficient of 0.59 with both,
+whereas Vuls and Clair share more common vulnerability detection resulting to the Jaccard coefficient of 0.83.
 Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
 the scanners in Docker images and the overlap between them.
-This Figure excludes Centos Docker images (highlighted images in Table\~ref{table1}) because scanners report results in different
-formats for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
-to report pending patches that need to be applied to specific packages,
-whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
-vulnerabilities in packages. Also, we excluded two other images \texttt{bids/antscorticalthickness:v2.2.0-1} and
-\texttt{bids/afni\_proc} from this figure, since we do not have Vuls scanning results for these images.
+This Figure also excludes Centos Docker images and \texttt{w} and \texttt{y} images.
+It is interesting to note that out of all reported vulnerabilities, 4453 vulnerabilities are only
+reported by Anchore, 673 by Clair, and 325 by Vuls.
 
-We find a total of 20,050 vulnerabilities in BIDS apps and Boutiques images.
-It is interesting to note that out of these vulnerabilities, 4453 vulnerabilities are only
-reported by Anchore, 673 by Clair-scanner, and 325 by Vuls.
-
-As the number and type of vulnerabilities reported by the three scanners are significantly different from each other,
+As the number and type of vulnerabilities reported by the these scanners are significantly different from each other,
 we desire to investigate the reasons behind these differences.
-%these scanners report different numbers and types of vulnerabilities.
-%How their logic differs and what exactly is making these results different than each other.
-
 Following our investigation, we are able to explain some of the reasons behind
@@
 for clear illustrations.
-%these reasons include
-%some scanners ignoring vulnerabilities in Linux-Kernel header packages, scanners referring to different databases,
-%how frequently they are updating their databases, and bugs in scanners, etc. 
-%We explain these differences below in detail
-%and provide an example with each reason to make it clear.
-%
-%\begin{comment}
-%Venn Diagram~\ref{fig:venn} illustrates that Anchore reports 4453 different vulnerabilities that are reported
-%by Vuls and Clair. Out of this 4443 vulnerabilities are present in linux-kernel-headers. These are ignored by
-%both Clair and Vuls.
-%\end{comment}
 
-\textbf{Linux-kernel-headers:} Clair-scanner and Vuls are ignoring all vulnerabilities in the Linux-kernel-headers,
+\textbf{Linux-kernel-headers:} Clair and Vuls are ignore all vulnerabilities in the Linux-kernel-headers,
 whereas Anchore reports all of them.
@@
 For example CVE-2019-9506 present in Linux-libc-dev-4.4.0-31.50, which is reported by Anchore, is not
-detected by both Vuls and Clair-scanner.
+detected by both Vuls and Clair.
 Linux-kernel-headers are the headers files that only provide function names, their parameters, and their
@@
 
-\textbf{CVEs with Status as “Not-affected”:} Vuls is reporting vulnerabilities that have status
-as "not-affected" in the vulnerability database. It means Linux distribution which is inside the image is not affected
-by the particular CVE. In other words, Vuls is reporting vulnerabilities that it should not have been reported.
+\textbf{CVEs with Status as “Not-affected”:} Vuls reports vulnerabilities that have status
+as "not-affected" in the vulnerability database. It means the Linux distribution of the image is not affected
+by the particular CVE. In other words, Vuls reports vulnerabilities that it should not have been reported.
 For example, we scan an image having the Trusty release in it and Vuls is reporting CVE-2015-2305
@@
 prior to the end-of-life. Only if it was vulnerable, Anchore reports it, otherwise it does not.
-If this kind of vulnerability is present in ESM release then Clair-scanner reports it because it
+If this kind of vulnerability is present in ESM release then Clair reports it because it
 only refers to ESM release. On the other hand, if the vulnerability
-status in ESM release is "DNE" (Does Not Exist), then Clair-scanner does not report it. 
+status in ESM release is "DNE" (Does Not Exist), then Clair does not report it. 
 For example, CVE-2017-9994 vulnerability in Libav package is ignored in Trusty LTS release due to end-of-life.
 Consequently, it is not reported by Anchore. This vulnerability has status as "DNE" in Trusty ESM
-release so Clair-scanner also does not report it. As Ubuntu 14.04 LTS release is present inside the images,
-Clair-scanner still refers to Ubuntu 14.04 ESM release vulnerability database, which is incorrect.
+release so Clair also does not report it. As Ubuntu 14.04 LTS release is present inside the images,
+Clair still refers to Ubuntu 14.04 ESM release vulnerability database, which is incorrect.
 
@@
 \textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
-are not detected by Clair-scanner but they affect Ubuntu 14.04 LTS, and hence detected by Vuls. The CVE-2017-1375 is an example
+are not detected by Clair but they affect Ubuntu 14.04 LTS, and hence detected by Vuls. The CVE-2017-1375 is an example
 of such vulnerabilities.
 
-\textbf{Misses:} Clair-scanner and Vuls
-are missing vulnerabilities that they should have detected. For example, the CVE-2016-9082 
-is present in package Cairo in Xenial release and it is not detected by Clair-scanner.
-Vuls is also missing vulnerabilities such as CVE-2019-5094.
+\textbf{Misses:} Clair and Vuls
+missed vulnerabilities that they should have detected. For example, the CVE-2016-9082 
+is present in package Cairo in Xenial release and it is not detected by Clair.
+Vuls also missed vulnerabilities such as CVE-2019-5094.
 
@@
 %Clair is only referring to Ubuntu 14.04 ESM release. 
-We reported this issue on two Google groups of Clair i.e CoreOS Dev and
+We reported this issue on two Google groups of Clair i.e. CoreOS Dev and
 clair-dev \url{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}
 
-\textbf{Database difference:} At the time we pulled Clair-scanner's database, it was one week old.
+\textbf{Database difference:} At the time we pulled Clair's database image, it was one week old.
                               As a result some vulnerabilities were not updated. For instance, CVE-2019-5094, which
 		              was published on 2019-09-24, was not 
-		              updated in Clair-scanner's database. Due to which it is missed by Clair-scanner.
+		              updated in Clair's database. Due to which it is missed by Clair.
 			      Consequently, these discrepancies, even small, are sufficient to change the detection of
@@
 		vulnerabilities that have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
-		However, if this vulnerability is present in Ubuntu 14.04 ESM release, it is detected by Clair-scanner. 
+		However, if this vulnerability is present in Ubuntu 14.04 ESM release, it is detected by Clair. 
 		For instance, CVE-2019-13565, which is present in Ubuntu 14.04, is an example of such vulnerabilities. 
@@
 \textbf{Rejected CVEs:} There are some CVEs, such as CVE-2017-13753, that are rejected because they are duplicate copies of other CVEs. 
-	So, Anchore is not reporting those rejected CVEs, but Vuls is reporting them.
-%\begin{table*}
-%\csvreader[%
-% respect all,%
-%  before reading=\footnotesize\sisetup{round-mode=places,round-precision=2,round-integer-to-decimal}
-%      \begin{adjustbox}{max width=\textwidth},
-%  after reading=\end{adjustbox},
-% tabular={c |c | c | c | c |c |c |c |c},
-%	table head =Image Labels &{Image names} &{OS Distro} & {Vulnerabilities by Anchore} & {Vulnerabilities by Clair} & {Vulnerabilities by Vuls} & {a} & {b} & {c}\\\hline,
-% late after line= \\,
-%        late after last line=\\\hline
-%]{status.csv}{}{\csvlinetotablerow}%
-%       \centering
-%        \caption{\label{status}Existing number of Vulnerabilities}
-%\end{table*}
-%\begin{comment}
-%The next experiment involves updating all these images and then rescanning them to see how the number of
-%vulnerabilities drop inside them. We used a \textit{bash} script to update these images. This script is
-%present in our Github repository \href{https://github.com/kaurbhupinder/Vulnerability-Analysis}
-%{https://github.com/kaurbhupinder/Risk-to-Clusters-Paper}. This script 
-%will find the package manager inside the image and then update the image according to the package manager it finds.
-%\end{comment}
+	So, Anchore does not report those rejected CVEs, but Vuls reports them.
 
 \subsection{Effect Of Update}
+
 As a result of image updating,
 scanning results change significantly.
-%However, there are still
-%vulnerabilities reported by these scanners but there are no fixes available for these vulnerabilities
-%to date.
-%\begin{comment}
-%There are only two
-%options, either you accept those vulnerabilities and use that image, or you discard that image.
-%So one thing is clear here that even if we keep our images up to date there will be still some
-%vulnerabilities that we have to face.
-%\end{comment}
 Figure~\ref{fig:graph2} represents the number of vulnerabilities that are detected by Anchore before and after 
 image update. 
-%In fact, this figure depicts an additional results of update to the original Figure~\ref{fig:graph1}.
 In fact, this Figure combines the original results of Figure~\ref{fig:graph1} with the results of the image update
@@
 
-%After the update, the vulnerabilities mostly have \textit{Low, Negligible or Medium} severity status.
-%Also, after the update, the number of vulnerabilities have a mild slope meaning that there
-%are a fixed set of packages that contain vulnerabilities and have no fix yet.
-%\begin{figure*}[h]
-%        {\includegraphics[width=\textwidth]
-%        {Figures/vulnwithupdate.pdf}}
-%        \caption{\label{fig:graph2} Scatterplot representing the number of vulnerabilities before and 
-%	after update of the images}
-%      \end{figure*}
-
-%\begin{figure*}
-%        {\includegraphics[scale=1.5,width=\textwidth]
-%        {Figures/graphwithdeletedpackages.pdf}}
-%	\caption{\label{deleted}\#Deleted Packages vs \#Reduced Vulnerabilities}
-%\end{figure*}
-
 \subsection{Effect Of Size Reduction}
@@
 is negligible. In other words, the image reduction was inconsistent.
-%At first, we thought that we will have a notable effect of size reduction on
-%vulnerabilities. However, this is not the case always. The bar graph shown in
-%Figure~\ref{fig:bargraph} illustrates that images \textit{bids/ndmg} and
-%\textit{poldracklab/fmriprep:1.2.3} have an insignificant effect of size reduction.
-According to our analyses, this can be due to two reasons: \rom{1}) the number of
+According to our analysis, this can be due to two reasons: \rom{1}) the number of
 deleted packages
@@
 by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}.
-%Our third experiment shows that deleting unnecessary packages from the image also helps to reduce
-%the number of vulnerabilities by a significant number. We started this experiment with
-%\textit{bids/example} image and deleted 61 unnecessary packages out of total 528 packages, which helped
-%to reduce 838 vulnerabilities to 523. Later, we also checked with \textit{bids/freesurfer} image, which allowed
-%to delete 71 unnecessary packages out of total 298 packages. Consequently, reducing number of vulnerabilities
-%from 353 to 101.
 
@@
 scanning results did not change.
-
-% Would the results apply to other domains than neuroimaging
-
+\vspace*{-2mm}
 \section{Discussion}
@@
 images to verify the integrity of the images.
-
+\vspace*{-2mm}
 \section{Conclusions and Future Work}
@@
 \bibliography{bibliography}
-
 \end{document}

### 2020-07-17 paper.tex
content fix 2

@@
 v,bids/baracus:latest,172,238,216,
-w,bids/antscorticalthickness:v2.2.0-1,289,27,no OVAL data,
+w,bids/antscorticalthickness:v2.2.0-1,289,27,no data,
 x,bids/dparsf:v4.3.12,507,750,757,
-y,bids/afni\_proc:latest,67,16,no OVAL data,
+y,bids/afni\_proc:latest,67,16,no data,
 z,bids/rshrf:1.0.1,5,3,3,
@@
 \begin{figure*}
-\begin{tabular}{ |c|c|c|c| }
+\begin{tabular}{|c|c|c|c|}
  \hline
@@
 \hline
-	\textbf{CentOS} & Red Hat Enterprise Linux Oval & Red Hat Enterprise Linux OVAL And Red Hat Security Advisories & Red Hat Security Data \\
+	\textbf{CentOS} & Red Hat OVAL Database & Red Hat OVAL Database and Red Hat Security Advisories & Red Hat Security Data \\
 \hline
-	\textbf{Debian} & Debian Security Bug Tracker &	Debian OVAL and Debian Security Bug Tracker & Debian Security Bug Tracker \\
+	\textbf{Debian} & Debian Security Bug Tracker &	Debian OVAL Database and Debian Security Bug Tracker & Debian Security Bug Tracker \\
 \hline
-	\textbf{Ubuntu} & Ubuntu CVE Tracker &	Ubuntu OVAL &	Ubuntu CVE Tracker \\
+	\textbf{Ubuntu} & Ubuntu CVE Tracker &	Ubuntu OVAL Database &	Ubuntu CVE Tracker \\
  \hline
@@
 
-\subsection{Ubuntu Releases and its Vulnerability Database}
+\subsection{Ubuntu Release types and its Vulnerability statuses}
 
 BIDS apps and Boutiques images in our experiments have four Linux
-distributions i.e. Ubuntu, CentOS, Debian, and Alpine. A particular
-distribution has different releases in general. Regarding Ubuntu, it has different
-types of releases e.g. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release.
-Through our experiments, we find that image scanners report Ubuntu vulnerabilities 
-differently depending on the different Ubuntu release types. It is 
-important to provide an overview of these Ubuntu releases types, 
+distributions i.e. Ubuntu, CentOS, Debian, and Alpine. 
+Out of these distributions, Ubuntu assigns a vulnerability status to
+all vulnerabilities before keeping them in its vulnerability database.
+Each vulnerability is assigned a unique Common Vulnerabilities and Exposures (CVE) number
+by the MITRE corporation, who maintains a list of all vulnerabilities of all distributions.
+Ubuntu keeps a record of Ubuntu-specific vulnerabilities in Ubuntu CVE Tracker using their CVE
+numbers. In this paper, we use vulnerability and CVE interchangeably.
+The vulnerability status in Ubuntu CVE Tracker is subjected to change
+depending on the work progress to fix that vulnerability.
+%Regarding Ubuntu, it has different
+%types of releases e.g. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release.
+%Ubuntu maintains its vulnerability data in Ubuntu CVE tracker, which is referred by Anchore and Clair.
+%There is another vulnerability database i.e. Open Vulnerability and Assessment Language (OVAL) repository,
+%which is maintained by MITRE corporation. Vuls refers to OVAL repository for getting Ubuntu vulnerability feed.
+%The vulnerability data format of both databases is different. OVAL keeps a separate xml file for each release,
+%which contains that release specific vulnerability information.
+Ubuntu keeps a separate file for each vulnerability, which
+has an entry for all Ubuntu releases combined with the current status
+of that vulnerability in that release.
+Further, in Ubuntu a particular release can be of different types i.e. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release. 
+Through our experiments, we find that Anchore and Clair report Ubuntu vulnerabilities 
+differently depending on either the different Ubuntu release type or vulnerability status. It is 
+important to provide an overview of these Ubuntu releases types and vulnerability statuses, 
 since Ubuntu is heavily utilized in our experiments. 
@@
 to LTS release only while collecting data from the vulnerability databases.
-More interestingly, scanners are able to refer to ESM release vulnerability database
-even without purchase, however, this may lead to discrepancies in results.
+More interestingly, Clair refers to ESM release vulnerability database, however, this may lead to discrepancies in results.
 Further, if an image is using a Linux release where EOL has been reached that image may
@@
 
-Ubuntu maintains its vulnerability database in the Ubuntu CVE Tracker. For a given CVE, there is an entry for all ubuntu releases.
-Ubuntu releases are listed with the package name
-in which vulnerability exists and are entitled a status
+In Ubuntu CVE Tracker, all Ubuntu releases are listed with the package name
+in which vulnerability exists and are entitled a vulnerability status
 (\url{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
@@
 \newline\\
-For a given release, the status can be any one of the following:
+For a given release, the vulnerability status can be any one of the following:
 
@@
 \textbf{not-affected:} The package, while related to the
-		CVE in some way, is not affected by the issue. Notes should
+		CVE in some way, is not affected by the issue. The <notes> should
 		provide detailed information, if needed. For instance, if the given
@@
 Figure~\ref{example} illustrates how the information of a CVE is represented
-in the Ubuntu launchpad database.
+in the Ubuntu CVE Tracker.
 
@@
 	{Figures/vulnExample2.png}}}
-        \caption{\label{example} Representation of a CVE in Ubuntu Launchpad}
+        \caption{\label{example} Representation of a CVE in Ubuntu CVE Tracker}
 \end{figure}
@@
 
-Table~\ref{table1} shows the number of detected vulnerabilities in the different images,
-detected by each of the scanners. Image labels from \texttt{a} to \texttt{al} represents
+Table~\ref{table1} shows the number of vulnerabilities in the different images,
+detected by each of the scanners. Image labels from a to al represents
 Docker images, whereas remaining ones belong to Singularity.
-Vuls shows \textit{no OVAL data} for image \texttt{w} and \texttt{y},
+Vuls shows \textit{no data} for images \texttt{bids/antscorticalthickness:v2.2.0-1} and \texttt{bids/afni\_proc:latest},
 which have Ubuntu 17.04 and 17.10 OS distribution respectively. This is because there is no
@@
 also get increased.
-The Figure also infers that the Alpine distribution, being a
+This Figure also infers that the Alpine distribution, being a
 lightweight distribution, has the least number of vulnerabilities, whereas more vulnerabilities are reported for
 distributions with more packages such as Ubuntu.
-We also analyze that out of the total Docker images scanned by our experiments, Debian reports more high vulnerabilties, as
+We also analyze that out of the total Docker images scanned by our experiments, Debian reports more high-level vulnerabilties, as
 classified by databases, than others.
-\begin{table*}[!ht]
+\begin{table*}
 \csvreader[%
  tabular={|c|c|c|c|c|c|},
-	table head = \hline\textbf{Image Labels} &\textbf{{Image names}} & \textbf{Anchore} & \textbf{Clair} & \textbf{Vuls} & \textbf{Stools}\\\hline,
+	table head = \hline\textbf{Labels} &\textbf{{Image names}} & \textbf{Anchore} & \textbf{Clair} & \textbf{Vuls} & \textbf{Stools}\\\hline,
 	late after line= \\,
@@
 
-\begin{figure*}[!ht]
+\begin{figure*}
         {\includegraphics[scale=1.5,width=\textwidth]
@@
 
-\begin{figure}[!ht]
+\begin{figure}
         {\includegraphics[scale=2.5,width=\columnwidth]
@@
 While comparing scanner results, we exluded all Centos images (highlighted images in Table~\ref{table1})
-and two other images \texttt{w} and
-\texttt{y}. The reason behind excluding Centos images is that scanners report results using different
+and two other images \texttt{bids/antscorticalthickness:v2.2.0-1} and
+\texttt{bids/antscorticalthickness:v2.2.0-1}. The reason behind excluding Centos images is that scanners report results using different
 vulnerability identifiers for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
@@
 whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
-vulnerabilities in packages. We exluded \texttt{w} and \texttt{y} images because Vuls
-can not scan these image, hence no results to compare.
+vulnerabilities in packages. We exluded other two images because Vuls
+can not scan these image, hence no results are present to compare.
 In most cases,
@@
 the scanners in Docker images and the overlap between them.
-This Figure also excludes Centos Docker images and \texttt{w} and \texttt{y} images.
+This Figure also excludes Centos Docker images and other two non-comparable images.
 It is interesting to note that out of all reported vulnerabilities, 4453 vulnerabilities are only
@@
 
-\textbf{Linux-kernel-headers:} Clair and Vuls are ignore all vulnerabilities in the Linux-kernel-headers,
+\textbf{Linux-kernel-headers:} Clair and Vuls ignore all vulnerabilities in the Linux-kernel-headers,
 whereas Anchore reports all of them.
 We find that 4443 out of 4453 vulnerabilities that are only reported by Anchore are present in Linux-kernel-headers.
-For example CVE-2019-9506 present in Linux-libc-dev-4.4.0-31.50, which is reported by Anchore, is not
+For example, CVE-2019-9506 present in Linux-libc-dev-4.4.0-31.50, reported by Anchore, is not
 detected by both Vuls and Clair.
-Linux-kernel-headers are the headers files that only provide function names, their parameters, and their
+Linux-kernel-headers are the header files that only provide function names, their parameters, and their
 return types.
-The actual source code of these functions is present in the Linux kernel and is not inside the image.
+The actual source code of those functions is present in the Linux kernel and is not inside the image.
 So, vulnerability detection in header files
@@
 
-\textbf{CVEs with Status as “Not-affected”:} Vuls reports vulnerabilities that have status
-as "not-affected" in the vulnerability database. It means the Linux distribution of the image is not affected
-by the particular CVE. In other words, Vuls reports vulnerabilities that it should not have been reported.
-For example, we scan an image having the Trusty release in it and Vuls is reporting CVE-2015-2305
-in the package Cups. However, upon checking the vulnerability database, we find that package Cups in Trusty is not
+\textbf{Ubuntu CVEs with status as “Not-affected”:} Vuls reports vulnerabilities that have status
+as "not-affected" in the Ubuntu database. It means that according to Ubuntu the image is not affected
+by the particular vulnerability. In other words, Vuls reports vulnerabilities that it should not have been reported.
+For example, when we scan an image having the Trusty release in it and Vuls reports CVE-2015-2305
+in the package Cups. However, upon checking the Ubuntu vulnerability database, we find that package Cups in Trusty is not
 affected by this CVE.
 
-\textbf{CVEs with status as "Ignored (reached end-of-life)":}
+\textbf{Ubuntu CVEs with status as "Ignored (reached end-of-life)":}
 Some vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life. 
@@
 status in ESM release is "DNE" (Does Not Exist), then Clair does not report it. 
-For example, CVE-2017-9994 vulnerability in Libav package is ignored in Trusty LTS release due to end-of-life.
+For example, CVE-2017-9994 vulnerability in Libav package is ignored in Trusty LTS release due to its end-of-life.
 Consequently, it is not reported by Anchore. This vulnerability has status as "DNE" in Trusty ESM
 release so Clair also does not report it. As Ubuntu 14.04 LTS release is present inside the images,
-Clair still refers to Ubuntu 14.04 ESM release vulnerability database, which is incorrect.
+Clair's referring to Ubuntu 14.04 ESM release vulnerability database is incorrect.
 
@@
 \textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
-are not detected by Clair but they affect Ubuntu 14.04 LTS, and hence detected by Vuls. The CVE-2017-1375 is an example
+are not detected by Clair but they affect Ubuntu 14.04 LTS, and hence detected by Vuls and Anchore. The CVE-2017-13758 is an example
 of such vulnerabilities.
@@
 
-\textbf{Database difference:} At the time we pulled Clair's database image, it was one week old.
-                              As a result some vulnerabilities were not updated. For instance, CVE-2019-5094, which
+\textbf{Database difference:} At the time we pulled Clair's database, through \texttt{arminc/clair-db:latest} Docker image, it was one week old.
+                              As a result some vulnerabilities were not updated in the database. For instance, CVE-2019-5094, which
 		              was published on 2019-09-24, was not 
@@
 
-\textbf{CVEs with status "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
+\textbf{Ubuntu CVEs with status "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
 		which it is not able to detect some vulnerabilities. Due to this bug, Anchore does not detect 
@@
 		However, if this vulnerability is present in Ubuntu 14.04 ESM release, it is detected by Clair. 
-		For instance, CVE-2019-13565, which is present in Ubuntu 14.04, is an example of such vulnerabilities. 
+		For instance, CVE-2019-13565, which is present in Ubuntu 14.04 LTS, is an example of such vulnerabilities. 
 		We reported this bug as well to the Anchore development team through their Slack
@@
 \textbf{Rejected CVEs:} There are some CVEs, such as CVE-2017-13753, that are rejected because they are duplicate copies of other CVEs. 
-	So, Anchore does not report those rejected CVEs, but Vuls reports them.
+	So, Anchore and Clair does not report those rejected CVEs, but Vuls reports them.
 
@@
 experiment.
-Clearly, the figure illustrates that when image are updated, the number of vulnerabilities reduces by a
+Clearly, the figure illustrates that when images are updated, the number of vulnerabilities reduces by a
 significant number. Furthermore, a mild slope of vulnerabilities after the image update shows that
@@
 vulnerabilities mostly have \textit{Low, Negligible, or Medium} severity status, meaning that
-high vulnerabilities are prioritised and fixed fast.
+\textit{high} severity vulnerabilities are prioritized and fixed fast.
 Besides that, it is also interesting to note that some images in Figure~\ref{fig:graph2}
@@
 Despite of the significant drop in the number of vulnerabilities as a result of image updating,
-there is still a number of vulnerabilities reported by the scanners. There is due to the
+there is still a number of vulnerabilities reported by the scanners. This is due to the
 vulnerabilities which do not have fix yet.
@@
 Our second approach involves the deletion of unnecessary packages from the images.
-We tested our approach on 5 different images. We find that
+We tested our approach on 5 different images covering the spectrum of Figure~\ref{fig:graph1}. We find that
 after the size reduction process, sometimes the scanning results deviate only a little from the results
@@
 Figure~\ref{fig:bargraph} displays the results. 
-Our initial thought was that with the update and size reduction process together, we will be able to
+Our initial expectation was that with the update and size reduction process together, we will be able to
 reduce vulnerabilities even more. However,
@@
 many vulnerabilities they contained. To illustrate, \textit{bids/example} image in Figure~\ref{fig:bargraph}
-shows no effect of size reduction along with update process. It has 181 vulnerabilities for both experiments 2 and 4.
+shows no effect of size reduction along with update process. It has 181 vulnerabilities for both experiments.
 Meaning that packages, which we deleted after updating the image, were already vulnerability free. Therefore,
@@
 As we noticed that none of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
-so many are high vulnerabilities as well. Yet there is not a single image scanner on which we can rely upon for
+so many are high severity vulnerabilities as well. Yet there is not a single image scanner on which we can rely upon for
 scanning. Additionally, we cannot update all images because some OS releases, which are used inside images, 
@@
 the pipeline to get Reprozip trace that can take up to several hours. Also, the user should have proper knowledge
-of running the pipeline because it is image specific. In addition to that, Reprozip can be only installed
+of running the pipeline because it is image-specific. In addition to that, Reprozip can be only installed
 in the images having Python version 2.7.3 or greater, or 3.3 or greater. Above all, there is no guarantee that
-the commands that you ran to get Reprozip trace covered the whole program, maybe it runs a particular
-branch of the program. So there should be some kind of coverage measurement.
+the commands that you run to get Reprozip trace covers the whole program, maybe it runs a particular
+branch of the program. So, there should be some kind of coverage measurement.
 Besides this, as scanners report vulnerabilities according to the versions of the installed packages,
@@
 followed to keep container images safe.
-\newline 1. Update packages regularly.
-\newline 2. Remove unnecessary packages, in particular the ones used for installation (compilers, source packages, etc).
-\newline 3. Choose your base OS image wisely.
-\newline 4. Run image scanning tools in CI scripts. For instance Anchore.
-\newline 5. Protect your GitHub/DockerHub credentials because if automated builds is set up
+\begin{itemize}
+	\item Update packages regularly inside images.
+	\item Remove unnecessary packages, in particular the ones used for installation (compilers, source packages, etc.).
+	\item Choose your base OS image wisely.
+	\item Run image scanning tools in CI scripts. For instance Anchore.
+	\item Protect your GitHub/DockerHub credentials because if automated builds is set up
 in Docker Hub, it can automatically build images from external repositories, for instance GitHub.
-\newline 6. Minimize dependencies.
-\newline 7. Avoid static linking because it obfuscates vulnerability scanning.
-\newline 8. Use the package manager to facilitate vulnerability detection.
-\newline 9. Use OS releases that have LTS support.
-\newline 10. Sign your images. Docker Content Trust (DCT) provides ability to digitally sign
-images to verify the integrity of the images.
+\item Minimize dependencies inside images.
+\item Avoid static linking because it obfuscates vulnerability scanning.
+\item Use the package manager to facilitate vulnerability detection.
+\item Use OS releases that have LTS support.
+\end{itemize}
 \vspace*{-2mm}
@@
 image size reduction process also reduces vulnerabilities a lot. However, we found out that this is not
-always true. It depends on two factors: kind and the number of packages that we are
+always true. It depends on two factors: the kind of packages and the number of packages that we are
 deleting.

### 2020-07-17 Scripts/graphs/drawVenn.py

@@ -3,7 +3,7 @@ import numpy as np
 from matplotlib_venn import venn3, venn3_circles
  
 # Make a Basic Venn
-v = venn3(subsets=(1, 1, 1, 1, 1, 1, 1), set_labels = ('Anchore', 'Clair-scanner', 'Vuls'))
+v = venn3(subsets=(1, 1, 1, 1, 1, 1, 1), set_labels = ('Anchore', 'Clair', 'Vuls'))
  
 # Custom it
 v.get_label_by_id('100').set_text('4453')
@@ -18,5 +18,5 @@ for text in v.set_labels:
 for text in v.subset_labels:
     text.set_fontsize(15)
 # Show it
-#plt.savefig('venn.pdf',dpi=2000)
-plt.show()
+plt.savefig('venn.pdf',dpi=2000)
+#plt.show()

### 2020-07-27 paper.tex
centos mapping

@@
 c,bids/ndmg:latest,934,757,782,
-d,\textbf{bids/broccoli:v1.0.0},79,79,117,
+d,bids/broccoli:v1.0.0,203,203,117,
 e,bids/fibredensityandcrosssection:latest,1086,849,868,
@@
 aa,bids/ndmg:v0.1.0,934,758,782,
-ab,\textbf{mcin/qeeg:latest},46,46,142,
-ac,\textbf{camarasu/creaphase:0.3},54,54,186,
-ad,\textbf{bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest:latest},70,76,157,
-ae,\textbf{mcin/docker-fsl:latest},75,75,201,
+ab,mcin/qeeg:latest,121,121,142,
+ac,camarasu/creaphase:0.3,148,148,186,
+ad,bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest:latest,257,266,157,
+ae,mcin/docker-fsl:latest,178,178,201,
 af,gkiar/onevoxel:v0.3.0rc2,5,2,2,
-ag,\textbf{bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest:latest},70,76,157,
-ah,\textbf{bt5e/ants:latest},150,156,336,
+ag,bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest:latest,257,266,157,
+ah,bt5e/ants:latest,592,600,336,
 ai,poldracklab/fmriprep:1.2.3,591,441,447,
@@
 ak,gkiar/mask2boundary:v0.1.0,15,11,11,
-al,\textbf{mcin/ica-aroma:latest},75,75,202,
+al,mcin/ica-aroma:latest,178,178,202,
 am,c3genomics/genpipes,,,,99
@@
 	\vspace*{-10mm}
-	\caption{\label{fig:venn} Scanner results (excluding non-comparable image results)}
+	\caption{\label{fig:venn} Scanner results}
 \end{figure}

### 2020-07-27 Scripts/graphs/drawVenn.py

@@ -7,12 +7,12 @@ v = venn3(subsets=(1, 1, 1, 1, 1, 1, 1), set_labels = ('Anchore', 'Clair', 'Vuls
  
 # Custom it
 v.get_label_by_id('100').set_text('4453')
-v.get_label_by_id('010').set_text('673')
-v.get_label_by_id('110').set_text('1031')
-v.get_label_by_id('001').set_text('325')
+v.get_label_by_id('010').set_text('699')
+v.get_label_by_id('110').set_text('1678')
+v.get_label_by_id('001').set_text('536')
 v.get_label_by_id('101').set_text('657')
 v.get_label_by_id('011').set_text('2220')
-v.get_label_by_id('111').set_text('10691')
+v.get_label_by_id('111').set_text('11978')
 for text in v.set_labels:
     text.set_fontsize(18)
 for text in v.subset_labels:

### 2020-07-27 Scripts/graphs/venn.py

@@ -78,12 +78,6 @@ def compare(file1,file2,file3):
     
 
 def main():
-    dir_name = "./"
-    test = os.listdir(dir_name)
-    for item in test:
-       if item.endswith(".csv"):
-            os.remove(os.path.join(dir_name, item))
-
     file1=sys.argv[1]
     file2=sys.argv[2]
     file3=sys.argv[3]

### 2020-07-30 paper.tex
ubuntu database fixes

@@
 \affil[1]{Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada}
+
 \maketitle
@@
 To get a vulnerability feed of various OS distributions, Anchore refers to
-different sources. Table~\ref{database} displays Anchore's vulnerability sources for
+different sources. Figure~\ref{database} displays Anchore's vulnerability sources for
 Ubuntu, Debian, Alpine, and Centos, which are present inside taken images.
@@
 \texttt{vuls/vuls:0.9.0}. At the time of this study, Vuls gets vulnerability feed
-from a configured set of sources. Table~\ref{database} lists vulnerability databases
+from a configured set of sources. Figure~\ref{database} lists vulnerability databases
 referred by Vuls for scanned four OS distributions i.e. Alpine, Ubuntu, Debian, and Centos.
 Apart from this, like Anchore, Vuls also refers NVD database for getting vulnerability metadata.
-Table~\ref{database} shows that Vuls
+Figure~\ref{database} shows that Vuls
 refers to Open Vulnerability and Assessment Language (OVAL) database for Ubuntu, Debian, and Centos.
@@
 Clair-scanner maintains a Docker image with the up-to-date vulnerability
-database from a set of different sources. Table~\ref{database} lists
+database from a set of different sources. Figure~\ref{database} lists
 vulnerability databases that Clair referred for Alpine, Ubuntu, Debian, and Centos.
@@
 
-\subsection{Ubuntu Release types and its Vulnerability statuses}
+\subsection{Ubuntu Vulnerability Database}
 
-BIDS apps and Boutiques images in our experiments have four Linux
-distributions i.e. Ubuntu, CentOS, Debian, and Alpine. 
-Out of these distributions, Ubuntu assigns a vulnerability status to
-all vulnerabilities before keeping them in its vulnerability database.
-Each vulnerability is assigned a unique Common Vulnerabilities and Exposures (CVE) number
-by the MITRE corporation, who maintains a list of all vulnerabilities of all distributions.
-Ubuntu keeps a record of Ubuntu-specific vulnerabilities in Ubuntu CVE Tracker using their CVE
-numbers. In this paper, we use vulnerability and CVE interchangeably.
-The vulnerability status in Ubuntu CVE Tracker is subjected to change
-depending on the work progress to fix that vulnerability.
+\change{There are two types of vulnerability databases that are referred
+by the scanners in these experiments. First one is Open Vulnerability and Assessment Language (OVAL)
+database, which is an international open standard and a common means of determining the existence of
+vulnerabilities in softwares. OVAL supports various OS distributions e.g. Ubuntu, Debian, Centos, etc.
+Second type of databases used by scanners are vulnerability databases from specific OS vendors e.g. Alpine-SecDB
+from Alpine,
+Debian Bug Tracker from Debian, Ubuntu CVE Tracker from Ubuntu, etc., where they
+keep a track of their OS-specific vulnerabilities by assigning a status.
+%In particular, there is a discrepancy in the way Anchore and Clair
+%interpret Ubuntu CVE Tracker.
+Out of four distributions that are present in our images Vuls uses
+OVAL database for Debian, Ubuntu, Centos and refers to Alpine-SecDB
+database for Alpine as this distribution is currently not supported by OVAL.
+Clair and Anchore mostly refers to vulnerability databases provided by specific OS
+vendors except in one case, where Anchore refers to OVAL i.e. Centos.
+
+The major discrepancies are shown by Anchore and Clair in Ubuntu. Both refers to Ubuntu CVE Tracker database for Ubuntu images.
+The way in which both scanners interpret this database is different.
+%
+%There are different vulnerability databases, which have
+%different formats of data.
+%Out of which Open Vulnerability and Assessment Language (OVAL) is an international
+%open standard and a common
+%means of promoting publicly available security issues. 
+%It provides details about software vulnerabilities. It helps to determine
+%whether vulnerabilities exist in local machines or not. Apart from OVAL, operating system
+%vendors also keep track of their vulnerabilities separately and assign
+%a status to each vulnerability.
+%For example, Ubuntu maintains
+%Ubuntu CVE Tracker, Debian maintains Debian Security Bug Tracker, etc.
+%Each vulnerability is assigned a unique Common Vulnerabilities and Exposures (CVE) number
+%by the MITRE corporation, who maintains a list of all vulnerabilities of all distributions.
+%In this paper, we use vulnerability and CVE interchangeably.
+%Ubuntu CVE Tracker is used by Anchore and Clair in our experiments
+%and there is discrepancies in the way both scanners interpret results.
+%
+%BIDS apps and Boutiques images in our experiments have four Linux
+%distributions i.e. Ubuntu, CentOS, Debian, and Alpine. 
+%Out of these distributions, Ubuntu assigns a vulnerability status to
+%all vulnerabilities before keeping them in its vulnerability database.
+%Each vulnerability is assigned a unique Common Vulnerabilities and Exposures (CVE) number
+%by the MITRE corporation, who maintains a list of all vulnerabilities of all distributions.
+%Ubuntu keeps a record of Ubuntu-specific vulnerabilities in Ubuntu CVE Tracker using their CVE
+%numbers. In this paper, we use vulnerability and CVE interchangeably.
+%The vulnerability status in Ubuntu CVE Tracker is subjected to change
+%depending on the work progress to fix that vulnerability.
+%
 %Regarding Ubuntu, it has different
@@
 %which contains that release specific vulnerability information.
-Ubuntu keeps a separate file for each vulnerability, which
+Ubuntu CVE Tracker keeps a separate file for each vulnerability, which
 has an entry for all Ubuntu releases combined with the current status
 of that vulnerability in that release.
-Further, in Ubuntu a particular release can be of different types i.e. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release. 
-Through our experiments, we find that Anchore and Clair report Ubuntu vulnerabilities 
-differently depending on either the different Ubuntu release type or vulnerability status. It is 
-important to provide an overview of these Ubuntu releases types and vulnerability statuses, 
+In particular, Clair and Anchore show discrepancies for Ubuntu 14.04 which have
+two entries for each vulnerability, one for Ubuntu 14.04 Long Term Support (LTS)
+and second for Ubuntu 14.04 Extended Security Maintenance (ESM) release. As Ubuntu 14.04 LTS
+reached end-of-life on 2019-04-30, so Ubuntu ignores new vulnerabilities in LTS release and
+fix them only in ESM release. Consequently, a same vulnerability may have different vulnerability status in LTS and ESM releases,
+which is causing discrepancies. This is because Anchore refers to Ubuntu 14.04 LTS, whereas Clair refers to
+ESM.
+%Further, in Ubuntu a particular release can be of different types i.e. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release. 
+%Through our experiments, we find that Anchore and Clair report Ubuntu vulnerabilities 
+%differently depending on either the different Ubuntu release type or vulnerability status. 
+It is important to provide an overview of these Ubuntu vulnerability statuses, 
 since Ubuntu is heavily utilized in our experiments. 
-Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
-reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
-in the form of ESM release.
-ESM is a paid service that can be requested from Ubuntu to get security 
-updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu version have different vulnerability
-databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
-exists in LTS.
-
-As an example, Ubuntu has ended support for some releases, such as 14.04 LTS,
-17.04, and 17.10, as they reached EOL. However, Ubuntu decided to provide optional extended support for Ubuntu 14.04.
-To use this extended support, users have to purchase Ubuntu 14.04 ESM release.
-The images in our experiments have Ubuntu 14.04 LTS, so scanners should refer
-to LTS release only while collecting data from the vulnerability databases.
-More interestingly, Clair refers to ESM release vulnerability database, however, this may lead to discrepancies in results.
-Further, if an image is using a Linux release where EOL has been reached that image may
-turns to be vulnerable as it is not possible to retrieve any updates.
-
-In Ubuntu CVE Tracker, all Ubuntu releases are listed with the package name
-in which vulnerability exists and are entitled a vulnerability status
+%Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
+%reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
+%in the form of ESM release.
+%ESM is a paid service that can be requested from Ubuntu to get security 
+%updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu version have different vulnerability
+%databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
+%exists in LTS.
+%
+%As an example, Ubuntu has ended support for some releases, such as 14.04 LTS,
+%17.04, and 17.10, as they reached EOL. However, Ubuntu decided to provide optional extended support for Ubuntu 14.04.
+%To use this extended support, users have to purchase Ubuntu 14.04 ESM release.
+%The images in our experiments have Ubuntu 14.04 LTS, so scanners should refer
+%to LTS release only while collecting data from the vulnerability databases.
+%More interestingly, Clair refers to ESM release vulnerability database, however, this may lead to discrepancies in results.
+%Further, if an image is using a Linux release where EOL has been reached that image may
+%turns to be vulnerable as it is not possible to retrieve any updates.
+%
+In Ubuntu CVE Tracker, for a vulnerability all Ubuntu releases are listed with the package name
+in which that vulnerability exists and are entitled a vulnerability status
 (\url{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
@@
 \newline \\
-\noindent <release>\_<source-package>: <status> (<version/notes>) \\
+\noindent <release>\_<source-package>: <status> (<version/notes>)
 \newline\\
+The <version/notes> given with a vulnerability status provide more
+information about the vulnerability.
 For a given release, the vulnerability status can be any one of the following:
@@
 \textbf{DNE (Does Not Exist):} The package does not exist in the
-		archive.
+		release.
 
@@
 \textbf{not-affected:} The package, while related to the
-		CVE in some way, is not affected by the issue. The <notes> should
-		provide detailed information, if needed. For instance, if the given
-		status is "not-affected (1.14.6-1.1)" then this indicates that this specific
-		package version is not affected.
+		vulnerability in some way, is not affected by the issue.
+	%	The <notes> should
+	%	provide detailed information, if needed.
+		%For instance, if the given
+		%status is "not-affected (1.14.6-1.1)" then this indicates that this specific
+		%package version is not affected.
 
-\textbf{needed:} The package is vulnerable to the
-		CVE and needs to be fixed.
+\textbf{needed:} The package is vulnerable and needs to be fixed.
 
-\textbf{active:} The package is vulnerable to the
-		CVE, needs fixing, and is actively being worked on.
+\textbf{active:} The package is vulnerable, needs fixing, and is 
+                 actively being worked on.
 
 \textbf{ignored:} The package, while related to the
-		CVE in some way, is being ignored for some reason. The
-		<notes> should provide that reason. For instance, if status looks like
-		"ignored (reached end-of-life)", this means that the given Ubuntu release already reached
-		end-of-life, so this CVE is ignored by Ubuntu. However, if there
-		is extended security support for this release then this
-		CVE will be handled in ESM release.
+		vulnerability in some way, is being ignored for some reason. 
+	%	The
+	%	<notes> should provide that reason.
+	%	For instance, if status looks like
+	%	"ignored (reached end-of-life)", this means that the given Ubuntu release already reached
+	%	end-of-life, so this CVE is ignored by Ubuntu. However, if there
+	%	is extended security support for this release then this
+	%	CVE will be handled in ESM release.
 
@@
                   has been fixed but an update has not been yet uploaded or
-		  published. The <version> is given to indicate the particular 
-		  version where the fix has been done.
+		  published.
+		 % The <version> is given to indicate the particular 
+		 % version where the fix has been done.
 
 \textbf{deferred:} The package is vulnerable, but 
-                   its fix has been deferred for some reason. The <notes>
-		   should provide further details. If a date is mentioned, e.g.
-		   "deferred (2015-02-02)", the given date specifies the date when
-		   the CVE was deferred.
+                   its fix has been deferred for some reason. 
+		  % The <notes>
+		  % should provide further details.
+		  % If a date is mentioned, e.g.
+		  % "deferred (2015-02-02)", the given date specifies the date when
+		  % the CVE was deferred.
 
 \textbf{released:} The package was vulnerable, but
-		an update has been already uploaded and published, e.g. "released (1.2.3)",
-		<version> indicates the first version where the fix was applied.
+		an update has been already uploaded and published.
+	%	e.g. "released (1.2.3)",
+	%	<version> indicates the first version where the fix was applied.
 
@@
 		an update has been already uploaded and published. However,
-		this update is published in the Ubuntu ESM release only and not in LTS.
-		The fixed version of such packages is appended by either
-		+esm or \char`\~esm, indicating that this package version is available
-		only via ESM.
-
-Figure~\ref{example} illustrates how the information of a CVE is represented
+		this update is published in the Ubuntu ESM release only and not in LTS.}
+		%The fixed version of such packages is appended by either
+		%+esm or \char`\~esm, indicating that this package version is available
+		%only via ESM.
+\newlne\\
+Figure~\ref{example} illustrates how the information of a vulnerability is represented
 in the Ubuntu CVE Tracker.
@@
 	{Figures/vulnExample2.png}}}
-        \caption{\label{example} Representation of a CVE in Ubuntu CVE Tracker}
+        \caption{\label{example} Representation of a vulnerability in Ubuntu CVE Tracker}
 \end{figure}
@@
 
-Table~\ref{table1} shows the number of vulnerabilities in the different images,
+\change{Table~\ref{table1} shows the number of vulnerabilities in the different images,
 detected by each of the scanners. Image labels from a to al represents
@@
 Vuls shows \textit{no data} for images \texttt{bids/antscorticalthickness:v2.2.0-1} and \texttt{bids/afni\_proc:latest},
-which have Ubuntu 17.04 and 17.10 OS distribution respectively. This is because there is no
-vulnerability data present in OVAL database, which Vuls refers for Ubuntu distributions, for these two releases.
-
+which have Ubuntu 17.04 and 17.10 OS distribution respectively. This is because Vuls
+cannot support scanning of these two distributions as they reached end of life.
+For Centos images, Anchore and Clair gives scanning results using Red Hat Security Advisory
+(RHSA) identifiers for Centos images, whereas Vuls uses CVE identifiers.
+RHSA identifiers specifies security patches that are pending to apply and
+CVE identifiers specifies vulnerabilities that exist in the system.
+So, we mapped RHSA identifiers to corresponding CVE identifiers to make
+a fair comparison of scanners. Table~\ref{table1} shows
+all vulnerabilities using CVE identifiers.}
+\newline\\
 Figure~\ref{fig:graph1} provides more image-specific information.
@@
 	\vspace*{1mm}
-	\caption{\label{table1}Number of vulnerabilities by scanners (all Centos images are highlighted)} 
+	\caption{\label{table1}Number of vulnerabilities by scanners} 
 \end{table*}
@@
 
-Our experiments concluded considerable discrepancies in the results obtained by
+\change{Our experiments concluded considerable discrepancies in the results obtained by
 these scanners. %We higlighted all Centos images in the Table~\ref{table1} since.
-While comparing scanner results, we exluded all Centos images (highlighted images in Table~\ref{table1})
-and two other images \texttt{bids/antscorticalthickness:v2.2.0-1} and
-\texttt{bids/antscorticalthickness:v2.2.0-1}. The reason behind excluding Centos images is that scanners report results using different
-vulnerability identifiers for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
-to report pending patches that need to be applied to specific packages,
-whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
-vulnerabilities in packages. We exluded other two images because Vuls
-can not scan these image, hence no results are present to compare.
+While comparing scanner results, we exluded two images \texttt{bids/antscorticalthickness:v2.2.0-1} and
+\texttt{bids/antscorticalthickness:v2.2.0-1} because Vuls
+cannot scan these image, hence no results are present to compare.
+%The reason behind excluding
+%vulnerability identifiers for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
+%to report pending patches that need to be applied to specific packages,
+%whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
+%vulnerabilities in packages. We exluded other two images because Vuls
+%can not scan these image, hence no results are present to compare.
 In most cases,
 Anchore reports more vulnerabilities than Vuls and Clair resulting in 
-the Jaccard coefficient of 0.59 with both,
-whereas Vuls and Clair share more common vulnerability detection resulting to the Jaccard coefficient of 0.83.
+the Jaccard coefficient of 0.63 with Clair, 0.59 with Vuls,
+whereas Vuls and Clair share more common vulnerability detection resulting to the Jaccard coefficient of 0.86.
 Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
 the scanners in Docker images and the overlap between them.
-This Figure also excludes Centos Docker images and other two non-comparable images.
+This Figure also excludes two non-comparable images, which cannot be scanned with Vuls.
 It is interesting to note that out of all reported vulnerabilities, 4453 vulnerabilities are only
-reported by Anchore, 673 by Clair, and 325 by Vuls.
-
+reported by Anchore, 699 by Clair, and 536 by Vuls.}
+\newline\\
 As the number and type of vulnerabilities reported by the these scanners are significantly different from each other,
@@
 
-\textbf{Ubuntu CVEs with status as “Not-affected”:} Vuls reports vulnerabilities that have status
+\textbf{Ubuntu vulnerabilities with status as “Not-affected”:} Vuls reports vulnerabilities that have status
 as "not-affected" in the Ubuntu database. It means that according to Ubuntu the image is not affected
@@
 in the package Cups. However, upon checking the Ubuntu vulnerability database, we find that package Cups in Trusty is not
-affected by this CVE.
+affected by this vulnerability.
 
-\textbf{Ubuntu CVEs with status as "Ignored (reached end-of-life)":}
+\textbf{Ubuntu vulnerabilities with status as "Ignored (reached end-of-life)":}
 Some vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life. 
 However, in Ubuntu 14.04 ESM release, these vulnerabilities may or may not be present.
-Anchore checks the last status of these vulnerabilities whether the package was vulnerable to the CVE
+Anchore checks the last status of these vulnerabilities in LTS whether the package was vulnerable
 prior to the end-of-life. Only if it was vulnerable, Anchore reports it, otherwise it does not.
@@
 
-\textbf{Ubuntu CVEs with status "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
+\textbf{Ubuntu vulnerabilities with status "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
 		which it is not able to detect some vulnerabilities. Due to this bug, Anchore does not detect 

### 2020-08-06 paper.tex
worked on Mathieu's comments

@@
 \href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/update/update.sh}{bash script} 
-to update all images. That script checks the
-package manager, which is present inside the image, and updates the image
+to update all images. That script checks which
+package manager is present inside the image, and based on that
+it updates OS packages of the image
 accordingly. However, this action affects the reproducibility
@@
 
-We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
-An interesting choice to do so would be to use 
-Neurodocker~\cite{neurodocker}.
-This tool traces and deletes unnecessary files.
-However, it does not affect the number of installed packages.
-Since image scanners report vulnerabilities according to the installed
-packages. Therefore, after
-minimization the same number of vulnerabilities is still reported.
-Consequently, we need to reduce the number of installed packages
-in the images by deleting unnecessary packages. For that, it is required to figure
-out which packages we need for the pipeline to function properly. To allow for that, we utilize
+%We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
+%An interesting choice to do so would be to use 
+%Neurodocker~\cite{neurodocker}.
+%This tool traces and deletes unnecessary files.
+%However, it does not affect the number of installed packages.
+%Since image scanners report vulnerabilities according to the installed
+%packages. Therefore, after
+%minimization the same number of vulnerabilities is still reported.
+%Consequently, we need to reduce the number of installed packages
+%in the images by deleting unnecessary packages. For that, it is required to figure
+%out which packages we need for the pipeline to function properly.
+\change{We revert to our second approach i.e. image minimization to reduce the number of vulnerabilities in the
+images with the aim to remove unused packages from the images.
+We use Neurodocker for this purpose.
+This tool traces and deletes unnecessary files from an image execution, however
+the removal of a packages file is not reflected in the installation status of
+the package manger.
+Therefore, after minimization, the same amount of vulnerabilities is still
+reported since image scanners report vulnerabilities according to the installed
+packages.
+In order to update the package manager information, it is essential to
+determine which packages are required for the pipeline to function properly}.
+To allow for that, we utilize
 Reprozip~\cite{rampin2016reprozip}, an open-source tool that
@@
 gives a complete dependency tree of a particular package.
-Effectively all needed packages are kept and remaining unnecessary packages are removed. We use
+Effectively all needed packages are kept and remaining unnecessary packages are removed. \change{We use
 \href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
 the image size reduction process, which install Reprozip in the image, collect Reprozip trace, and
-finally delete all unnecessary packages.
+finally delete all unnecessary packages. In this script, we use two temporary
+image containers to install Reprozip, collect its trace,
+identify the dependencies of the needed packages and then finally use
+a fresh image container to
+delete unnecessary packages from the image}.
+
+\subsection{Hybrid Approach}
 
@@
 While comparing scanner results, we exluded two images \texttt{bids/antscorticalthickness:v2.2.0-1} and
-\texttt{bids/antscorticalthickness:v2.2.0-1} because Vuls
+\texttt{bids/afni\_proc:latest} because Vuls
 cannot scan these image, hence no results are present to compare.
@@
 Our second approach involves the deletion of unnecessary packages from the images.
-We tested our approach on 5 different images covering the spectrum of Figure~\ref{fig:graph1}. We find that
-after the size reduction process, sometimes the scanning results deviate only a little from the results
-without minimization. While the minimization process results in significant reduction
-in the number of vulnerabilities in some cases, we find that in other cases the effect
-is negligible. In other words, the image reduction was inconsistent.
+We tested our approach on 5 different images covering the spectrum of Figure~\ref{fig:graph1}.
+We find that the image reduction process brings inconsistent deviation in scanning results.
+%We find that
+%after the size reduction process, sometimes the scanning results deviate only a little from the results
+%without minimization. While the minimization process results in significant reduction
+%in the number of vulnerabilities in some cases, we find that in other cases the effect
+%is negligible. 
+In other words, the image reduction was inconsistent.
 According to our analysis, this can be due to two reasons: \rom{1}) the number of
@@
 For instance, we were able to delete only 21 and 25 packages for 
-\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images. Consequently, vulnerabilities
+\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images respectively. Consequently, vulnerabilities
 reduced only by 4 and 17 respectively. 

### 2020-09-01 paper.tex
Updated abstract

@@
 \begin{abstract}
-
-Today, containers, which provide operating-system level virtualization, are
-popular. Correspondingly, they are widely used for scientific data analyses on 
-High Performance Computing (HPC) clusters. However, the security of containers
-still remains a concerning issue. Here, we focus on the security of container
-images, which are often built for the entire
-duration of an analysis, so scientific researchers prefer not to update
-them. Consequently, their chances of containing vulnerabilities increases.  
-In this study, we analyze vulnerabilities in container images used in 
-HPC clusters.
-We conduct two different
-experiments, image update and image minimization, to report the effect 
-on the number of vulnerabilities.
+Software containers have become key technologies for the deployment of
+scientific data analyses on high-performance computing (HPC)
+infrastructures. They facilitate analysis portability, deployment, and
+reproducibility. Container images, however, often contain slightly outdated
+software packages compared to HPC environments maintained by professional
+and dedicated system administrators. In addition, they often carry more
+software packages than required by analyses, including compilers or unused
+system librairies. As a result, container images are likely to contain
+important amounts of security vulnerability, increasing the attack surface
+for the entire infrastructure. This paper presents a vulnerability analysis
+of container images for scientific data analysis. We analyze container
+images with four vulnerability scanners, focusing on the use case of
+neuroscience data analyses. We quantify the effect of images updates and
+size reduction on the number of vulnerabilities, and conclude with
+recommendations on how to build container images with a reduced amount of
+vulnerabilities.
 

### 2020-09-01 paper.tex
More updates in abstract

@@
 scientific data analyses on high-performance computing (HPC)
-infrastructures. They facilitate analysis portability, deployment, and
-reproducibility. Container images, however, often contain slightly outdated
+infrastructures, due to their positive impact on the portability, deployment, and
+reproducibility of computations. Container images, however, often contain slightly outdated
 software packages compared to HPC environments maintained by professional
-and dedicated system administrators. In addition, they often carry more
+ system administrators, and they often carry more
 software packages than required by analyses, including compilers or unused

### 2020-09-09 paper.tex
Major edits in paper, reimplemented analysis in Jupyter

@@
 \usepackage[flushleft]{threeparttable}
+\usepackage{xspace}
 
@@
 \newcommand{\change}[2]{\color{cyan}Changes: #1\color{black}}
-\newcommand{\reprozip}[0]{ReproZip}
+\newcommand{\reprozip}[0]{ReproZip\xspace}
 \newcommand{\rom}[1]{\lowercase\expandafter{\romannumeral #1\relax}}
@@
 \renewcommand{\labelitemi}{$\textendash$}
-\title{Vulnerability Analysis of Container Images in Neuroimaging}
+\title{Security Vulnerabilities of Container Images in Neuroimaging}
 \begin{filecontents*}{resul.csv}
@@
 Singularity~\cite{kurtzer2017singularity} framework is often preferred to
-Docker\footnote{\url{http://docker.com}} on HPC clusters, due to its
+Docker\footnote{\url{http://docker.com}} for HPC deployments, due to its
 secure handling of multi-user environments, and its convenient support for
@@
 
-% Containers are meant to isolate applications from the host, but security remains an issue
-Using core features of the Linux kernel such as namespaces, control groups
-and chroot, containers isolate processes from the
-host computer,  
+% Containers are meant to isolate applications from the host, but security
+% remains an issue
+Leveraging core features of the Linux kernel such as namespaces, control
+groups and chroot, containers isolate processes from the host computer,  
 and control the memory, CPU, network and file-system resources assigned to
-them. However, containers still share the kernel, mounted file systems and
-some devices with the host, which raises potential security issues. In
-particular, privilege escalation, denial of service and information leak
-are always plausible~\cite{gantikow2016providing}. Therefore, security remains 
-an important concern when deploying containers~\cite{bettini2015vulnerability}.
+them. Nevertheless, containers still share the kernel, mounted file systems
+and some devices with the host, which raises security
+issues~\cite{martin2018docker, sultan2019container, combe2016docker} and
+opens the door to privilege escalation, denial of service, information
+leak and other types of attacks~\cite{gantikow2016providing}.
 
 % Container images, our study
-This study is a vulnerability analysis of container images used in HPC
-clusters. Container images contain complete operating-system distributions, including
-the data analysis software and its required dependencies.
-Images are rarely updated, as they are often built once
-for the entire duration of an analysis, to avoid results perturbations
-coming from software updates~\cite{gronenschild2012effects, glatard2015reproducibility}. Images also
-commonly include more dependencies than required by a specific analysis, to 
-enable reusability across experiments.
+Container images often include nearly complete operating-system
+distributions in addition to the data analysis software and its required
+dependencies. Images are rarely updated, as they are often built once for
+the entire duration of an analysis, to avoid results perturbations due to
+software updates~\cite{gronenschild2012effects,
+glatard2015reproducibility}. Images also commonly include more dependencies
+than required by a specific analysis, to facilitate reusability across
+experiments. As a result, it has been shown that over 30\% of official
+images in DockerHub contain high priority security
+vulnerabilities~\cite{gummaraju2015over}, that both official and community
+images contain more than 180 vulnerabilities on average~\cite{Shu2017}, and
+that vulnerabilities are often due to outdated
+packages~\cite{zerouali2019relation}.
 
+In this study, we focus on the vulnerability analysis of container images
+used in HPC clusters.  
 Our research questions are the following:
@@
 
-\textit{RQ3: Can the amount of vulnerabilities be reduced by minimizing the images?} 
+\textit{RQ3: Can the amount of vulnerabilities be reduced by minifying the images?} 
 Container images often include more software packages than required for a
@@
 
-We answer these questions taking the particular example of neuroimaging, a
-domain that has entered the Big Data era as many other
-ones~\cite{van2014human}. We focus on the analysis of container images
-present in BIDS apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}, two containerized
-application frameworks commonly used in neuroimaging.
+We answer these questions by taking the particular example of neuroimaging,
+a domain that has entered the Big Data era as many other
+ones~\cite{van2014human}. The next section describes the materials and
+tools used in the experiments, including container images and image
+scanners. We then describe our image update and minification methodology to
+reduce vulnerabilities. Results present the detected vulnerabilities in
+container images, explain observed discrepancies between scanners, and
+report on the efficiency of image update and size reduction. As a
+conclusion, we provide a set of image creation guidelines for a more secure
+deployment on HPC clusters.
 
-The next section describes the materials and tools used in the experiments,
-including container images and image scanners. We then describe our image
-update and minimization methodology to reduce vulnerabilities. Results review
-the detected vulnerabilities in container images, explain observed
-discrepancies between scanners, and report on the efficiency of image
-update and size reduction. As a conclusion, we provide a set of image
-creation guidelines for a secure deployment on HPC clusters.
-
-The existing research work on containers focuses mainly on the security of containers.
-This focus is justified by the fact that containers expose the host's resources
-(e.g., file system/ IPC) to the guest system. This feature raises a confidentiality
-threat for the applications running on the same host. Previous studies evaluated
-the security of Docker engine ~\cite{martin2018docker, sultan2019container, combe2016docker, bui2015analysis}.
-Other work studied security vulnerabilities in Docker images. A study in 2015 by Gummaraju et al.
-states that over 30\% of official images in docker hub contain high priority 
-security vulnerabilities~\cite{gummaraju2015over}. Shu et al. show that both official and community images 
-contain more than 180 vulnerabilities on an average~\cite{Shu2017}.
-Zerouali et al. studied that 
-outdated packages lead to bugs and severity vulnerabilities in Docker
-images~\cite{zerouali2019relation}.
+% We focus on the analysis of container images
+% present in BIDS apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}, two containerized
+% application frameworks commonly used in neuroimaging.
 
@@
 
-Since the aim of this research work is to detect security vulnerabilities
-in container images and attempt to examine the effect of different
-manipulations on these images, it is needed to have a representative set of
-images. Additionally, for the purpose of detecting vulnerabilities,
-utilization of image scanners is required. We utilize container
+To detect security vulnerabilities
+in container images and examine the effect of different
+manipulations on these images, we used container
 images from two popular application frameworks, as well as
@@
 
-We scan all container images, available at the time of this study, on two containerization frameworks
+We scanned all container images available at the time of this study on two containerization frameworks
 used in neuroscience: BIDS
-apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}, totalling
+apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques},
+totalling
 44 container images.
 Out of these 44 images, 26 were obtained from BIDS apps 
-(\url{https://bids-apps.neuroimaging.io/apps/}) 
-and 18 from Boutiques. In fact, at the time of the study, BIDS apps had 27 images,
+and 18 from Boutiques. At the time of the study, BIDS apps had 27 images,
 out of which one wasn't available on DockerHub. Boutiques had 49 images,
@@
 were already included in BIDS apps. All the final 26 images
-from BIDS apps are Docker images, whereas Boutiques contains 18 Docker images
+from BIDS apps were Docker images, whereas Boutiques contained 18 Docker images
 and 6 Singularity images.
@@
 
-We use four popular image scanners, namely Anchore~\cite{github_2019},
+We used four popular image scanners, namely Anchore~\cite{github_2019},
 Vuls~\cite{future-architect_2019}, Clair~\cite{arminc_2019} and
 Singularity Container Tools --- Stools~\cite{stools}. Anchore, Vuls and Clair support Docker
-images while Stools support Singularity. Different vulnerabilities may be
-reported by scanners if scanning experiments take place on different dates.
-To avoid such discrepancies, we freeze the vulnerability
-databases used by these scanners as of 2019-09-25, when we initiate our
-experiments. This allows for a fair comparison between the scanners.
-
-\subsubsection{Anchore}
+images while Stools support Singularity.
 
 Anchore is an end-to-end, open-source container security platform. It
-analyze	container images and lists OS
+analyzes container images and lists OS
 packages, non-OS packages (Python, Java, Gem, and Npm), and files.
@@
 Anchore vulnerability database version 0.0.11.
-
-Anchore compares package versions, which are present inside the
-image, with the vulnerability database in order to flag vulnerabilities.
-To get a vulnerability feed of various OS distributions, Anchore refers to
-different sources. Figure~\ref{database} displays Anchore's vulnerability sources for
-Ubuntu, Debian, Alpine, and Centos, which are present inside taken images.
-Anchore also refers to National
-Vulnerability Database (NVD) to get metadata of vulnerabilities.
 
@@
 
-\subsubsection{Vuls}
-
 Vuls is an open-source vulnerability scanner for Linux and FreeBSD. It
 offers both static and dynamic scanning, and both local and remote
-scanning. In our experiments, we use remote dynamic scanning, that is, Vuls
-connects to the running containers that needs to be scanned through SSH, and queries the package manager
-in the container. We use Vuls 0.9.0, executed through Docker image
-\texttt{vuls/vuls:0.9.0}. At the time of this study, Vuls gets vulnerability feed
-from a configured set of sources. Figure~\ref{database} lists vulnerability databases
-referred by Vuls for scanned four OS distributions i.e. Alpine, Ubuntu, Debian, and Centos.
-Apart from this, like Anchore, Vuls also refers NVD database for getting vulnerability metadata.
-Figure~\ref{database} shows that Vuls
-refers to Open Vulnerability and Assessment Language (OVAL) database for Ubuntu, Debian, and Centos.
-It is worth noting that there is
-no vulnerability data for Ubuntu 17.04 and 17.10 distributions in OVAL database, meaning that images
-with these distributions cannot be scanned with Vuls.
-
-\subsubsection{Clair}
+scanning. In our experiments,we used Vuls 0.9.0, executed through Docker image
+\texttt{vuls/vuls:0.9.0} in remote dynamic mode.
 
@@
 clusters. Clair has a client-server architecture, in which the server
-scans Docker images layer by layer and maintains a database of vulnerabilities. We use Clair through Clair-scanner
+scans Docker images layer by layer and maintains a database of vulnerabilities. We used Clair through Clair-scanner
 (\url{https://github.com/arminc/clair-scanner}), a tool to facilitate the testing
-of container images against a local Clair server. Clair-scanner scans the image,
-prepares a list of vulnerabilities, compares that list against a
-whitelist, and flags vulnerabilities that are not present in the whitelist.
-In our experiments, we did not use a whitelist to filter scanning results in
-order to make a fair comparison between scanners.
-Clair-scanner maintains a Docker image with the up-to-date vulnerability
-database from a set of different sources. Figure~\ref{database} lists
-vulnerability databases that Clair referred for Alpine, Ubuntu, Debian, and Centos.
-Clair also uses NVD database for getting vulnerability metadata.
-We use Clair version 2.0.6, executed through
+of container images against a local Clair server. 
+% Clair-scanner scans the image,
+% prepares a list of vulnerabilities, compares that list against a
+% whitelist, and flags vulnerabilities that are not present in the whitelist.
+% In our experiments, we did not use a whitelist to filter scanning results in
+% order to make a fair comparison between scanners.
+% Clair-scanner maintains a Docker image with the up-to-date vulnerability
+% database from a set of different sources.
+% Figure~\ref{database} lists
+% vulnerability databases that Clair referred for Alpine, Ubuntu, Debian, and Centos.
+% Clair also uses NVD database for getting vulnerability metadata.
+We used Clair version 2.0.6, executed through
 Docker image \texttt{arminc/clair-local-scan:v2.0.6}. For the vulnerability
@@
 updated on 2019-09-18.
-
-\subsubsection{Singularity Tools}
 
@@
 to circumvent the Docker-specific requirements in the Clair API.
-In our experiments, we use Singularity Tools version 3.2.1 through Docker
+In our experiments, we used Singularity Tools version 3.2.1 through Docker
 image
-\texttt{vanessa/stools-clair:v3.2.1}, which is using another Docker
-image \texttt{arminc/clair-db:latest} for referring to vulnerability feed.
+\texttt{vanessa/stools-clair:v3.2.1}.
+% , which is using another Docker
+% image \texttt{arminc/clair-db:latest} for referring to vulnerability feed.
 Since Stools uses Clair internally for scanning, vulnerability databases used
 by Stools are same as mentioned for Clair.
-To scan Singularity images, we follow the steps mentioned in
+To scan Singularity images, we followed the steps mentioned in
 \href{https://github.com/singularityhub/stools}{Stools Github}.
 
-\subsection{Ubuntu Vulnerability Database}
+\subsection{Vulnerability Databases}
 
-\change{There are two types of vulnerability databases that are referred
-by the scanners in these experiments. First one is Open Vulnerability and Assessment Language (OVAL)
-database, which is an international open standard and a common means of determining the existence of
-vulnerabilities in softwares. OVAL supports various OS distributions e.g. Ubuntu, Debian, Centos, etc.
-Second type of databases used by scanners are vulnerability databases from specific OS vendors e.g. Alpine-SecDB
-from Alpine,
-Debian Bug Tracker from Debian, Ubuntu CVE Tracker from Ubuntu, etc., where they
-keep a track of their OS-specific vulnerabilities by assigning a status.
-%In particular, there is a discrepancy in the way Anchore and Clair
-%interpret Ubuntu CVE Tracker.
-Out of four distributions that are present in our images Vuls uses
-OVAL database for Debian, Ubuntu, Centos and refers to Alpine-SecDB
-database for Alpine as this distribution is currently not supported by OVAL.
-Clair and Anchore mostly refers to vulnerability databases provided by specific OS
-vendors except in one case, where Anchore refers to OVAL i.e. Centos.
+Scanners refer to two types of vulnerability databases. The first one is
+the Open Vulnerability and Assessment Language (OVAL) database, an
+international open standard that supports various OS distributions
+including Ubuntu, Debian and Centos but not Alpine. The second one are vulnerability
+databases from specific OS distributions, such as Alpine-SecDB, Debian
+Security Bug Tracker, Ubuntu CVE Tracker, or Red Hat Security Data. OS
+distributions often assign a status to each vulnerability, to keep track of
+required and available security fixes in different versions of the
+distribution. Figure~\ref{database} shows the vulnerabilities databases used by each scanner 
+by OS distribution. Vuls uses OVAL databases for all distributions except Alpine, since Alpine is not available in OVAL. On the contrary, 
+Clair exclusively refers to distribution-specific databases. Anchore uses OVAL only for CentOS \tristan{why?}. It is also worth noting that there is
+no vulnerability data for Ubuntu 17.04 and 17.10 distributions in the OVAL database, since these distributions have reached end of life, meaning that images
+with these distributions cannot be scanned with Vuls \tristan{why doesn't vuls use Ubuntu CVE tracker?}.
+\tristan{In Vuls, what happens when 2 databases are used?}
 
-The major discrepancies are shown by Anchore and Clair in Ubuntu. Both refers to Ubuntu CVE Tracker database for Ubuntu images.
-The way in which both scanners interpret this database is different.
-%
-%There are different vulnerability databases, which have
-%different formats of data.
-%Out of which Open Vulnerability and Assessment Language (OVAL) is an international
-%open standard and a common
-%means of promoting publicly available security issues. 
-%It provides details about software vulnerabilities. It helps to determine
-%whether vulnerabilities exist in local machines or not. Apart from OVAL, operating system
-%vendors also keep track of their vulnerabilities separately and assign
-%a status to each vulnerability.
-%For example, Ubuntu maintains
-%Ubuntu CVE Tracker, Debian maintains Debian Security Bug Tracker, etc.
-%Each vulnerability is assigned a unique Common Vulnerabilities and Exposures (CVE) number
-%by the MITRE corporation, who maintains a list of all vulnerabilities of all distributions.
-%In this paper, we use vulnerability and CVE interchangeably.
-%Ubuntu CVE Tracker is used by Anchore and Clair in our experiments
-%and there is discrepancies in the way both scanners interpret results.
-%
-%BIDS apps and Boutiques images in our experiments have four Linux
-%distributions i.e. Ubuntu, CentOS, Debian, and Alpine. 
-%Out of these distributions, Ubuntu assigns a vulnerability status to
-%all vulnerabilities before keeping them in its vulnerability database.
-%Each vulnerability is assigned a unique Common Vulnerabilities and Exposures (CVE) number
-%by the MITRE corporation, who maintains a list of all vulnerabilities of all distributions.
-%Ubuntu keeps a record of Ubuntu-specific vulnerabilities in Ubuntu CVE Tracker using their CVE
-%numbers. In this paper, we use vulnerability and CVE interchangeably.
-%The vulnerability status in Ubuntu CVE Tracker is subjected to change
-%depending on the work progress to fix that vulnerability.
-%
-%Regarding Ubuntu, it has different
-%types of releases e.g. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release.
-%Ubuntu maintains its vulnerability data in Ubuntu CVE tracker, which is referred by Anchore and Clair.
-%There is another vulnerability database i.e. Open Vulnerability and Assessment Language (OVAL) repository,
-%which is maintained by MITRE corporation. Vuls refers to OVAL repository for getting Ubuntu vulnerability feed.
-%The vulnerability data format of both databases is different. OVAL keeps a separate xml file for each release,
-%which contains that release specific vulnerability information.
-Ubuntu CVE Tracker keeps a separate file for each vulnerability, which
-has an entry for all Ubuntu releases combined with the current status
-of that vulnerability in that release.
-In particular, Clair and Anchore show discrepancies for Ubuntu 14.04 which have
-two entries for each vulnerability, one for Ubuntu 14.04 Long Term Support (LTS)
-and second for Ubuntu 14.04 Extended Security Maintenance (ESM) release. As Ubuntu 14.04 LTS
-reached end-of-life on 2019-04-30, so Ubuntu ignores new vulnerabilities in LTS release and
-fix them only in ESM release. Consequently, a same vulnerability may have different vulnerability status in LTS and ESM releases,
-which is causing discrepancies. This is because Anchore refers to Ubuntu 14.04 LTS, whereas Clair refers to
-ESM.
-%Further, in Ubuntu a particular release can be of different types i.e. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release. 
-%Through our experiments, we find that Anchore and Clair report Ubuntu vulnerabilities 
-%differently depending on either the different Ubuntu release type or vulnerability status. 
-It is important to provide an overview of these Ubuntu vulnerability statuses, 
-since Ubuntu is heavily utilized in our experiments. 
-%Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
-%reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
-%in the form of ESM release.
-%ESM is a paid service that can be requested from Ubuntu to get security 
-%updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu version have different vulnerability
-%databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
-%exists in LTS.
-%
-%As an example, Ubuntu has ended support for some releases, such as 14.04 LTS,
-%17.04, and 17.10, as they reached EOL. However, Ubuntu decided to provide optional extended support for Ubuntu 14.04.
-%To use this extended support, users have to purchase Ubuntu 14.04 ESM release.
-%The images in our experiments have Ubuntu 14.04 LTS, so scanners should refer
-%to LTS release only while collecting data from the vulnerability databases.
-%More interestingly, Clair refers to ESM release vulnerability database, however, this may lead to discrepancies in results.
-%Further, if an image is using a Linux release where EOL has been reached that image may
-%turns to be vulnerable as it is not possible to retrieve any updates.
-%
-In Ubuntu CVE Tracker, for a vulnerability all Ubuntu releases are listed with the package name
-in which that vulnerability exists and are entitled a vulnerability status
-(\url{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
-encoded in the following form:
-\newline \\
-\noindent <release>\_<source-package>: <status> (<version/notes>)
-\newline\\
-The <version/notes> given with a vulnerability status provide more
-information about the vulnerability.
-For a given release, the vulnerability status can be any one of the following:
+Anchore also refers to National Vulnerability Database (NVD) to get
+metadata of vulnerabilities. Apart from this, like Anchore, Vuls also
+refers NVD database for getting vulnerability metadata \tristan{same
+question}. \tristan{why is it not in the table?}.
 
-\textbf{DNE (Does Not Exist):} The package does not exist in the
-		release.
+For Centos images, Anchore and Clair gives scanning results using Red Hat
+Security Advisory (RHSA) identifiers for Centos images, whereas Vuls uses
+CVE identifiers. RHSA identifiers specifies security patches that are
+pending to apply and CVE identifiers specifies vulnerabilities that exist
+in the system. We mapped RHSA identifiers to corresponding CVE identifiers,
+to allow for a comparison between scanners.
 
-\textbf{needs-triage:} The vulnerability of this package
-		is not known, and hence evaluation is needed.
+Different vulnerabilities may be
+reported by scanners if scanning experiments take place on different dates.
+To avoid such discrepancies, we froze the vulnerability
+databases used by these scanners as of 2019-09-25, when we initiated our
+experiments.\tristan{this contradicts the date used for Clair}
 
-\textbf{not-affected:} The package, while related to the
-		vulnerability in some way, is not affected by the issue.
-	%	The <notes> should
-	%	provide detailed information, if needed.
-		%For instance, if the given
-		%status is "not-affected (1.14.6-1.1)" then this indicates that this specific
-		%package version is not affected.
+\subsection{Image Update}
 
-\textbf{needed:} The package is vulnerable and needs to be fixed.
+A first approach to reduce the number of vulnerabilities in container
+images is to update their packages to the latest version packaged by the OS
+distribution. To study the effect of such updates, we developed a script
+(available
+\href{https://github.com/big-data-lab-team/container-vulnerabilities-paper/blob/master/Scripts/update}{here})
+to identify the package manager in the image, and invoke it to update all
+OS packages. \tristan{what was the date at which update was run?}
 
-\textbf{active:} The package is vulnerable, needs fixing, and is 
-                 actively being worked on.
-
-\textbf{ignored:} The package, while related to the
-		vulnerability in some way, is being ignored for some reason. 
-	%	The
-	%	<notes> should provide that reason.
-	%	For instance, if status looks like
-	%	"ignored (reached end-of-life)", this means that the given Ubuntu release already reached
-	%	end-of-life, so this CVE is ignored by Ubuntu. However, if there
-	%	is extended security support for this release then this
-	%	CVE will be handled in ESM release.
-
-\textbf{pending:} The package is vulnerable and
-                  has been fixed but an update has not been yet uploaded or
-		  published.
-		 % The <version> is given to indicate the particular 
-		 % version where the fix has been done.
-
-\textbf{deferred:} The package is vulnerable, but 
-                   its fix has been deferred for some reason. 
-		  % The <notes>
-		  % should provide further details.
-		  % If a date is mentioned, e.g.
-		  % "deferred (2015-02-02)", the given date specifies the date when
-		  % the CVE was deferred.
-
-\textbf{released:} The package was vulnerable, but
-		an update has been already uploaded and published.
-	%	e.g. "released (1.2.3)",
-	%	<version> indicates the first version where the fix was applied.
-
-\textbf{released-esm:} The package was vulnerable and
-		an update has been already uploaded and published. However,
-		this update is published in the Ubuntu ESM release only and not in LTS.}
-		%The fixed version of such packages is appended by either
-		%+esm or \char`\~esm, indicating that this package version is available
-		%only via ESM.
-\newlne\\
-Figure~\ref{example} illustrates how the information of a vulnerability is represented
-in the Ubuntu CVE Tracker.
-
-\begin{figure}[!ht]
-	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
-	{Figures/vulnExample2.png}}}
-        \caption{\label{example} Representation of a vulnerability in Ubuntu CVE Tracker}
-\end{figure}
-\vspace*{-7mm}
-\section{Reducing the amount of vulnerabilities}
-
-In this section, we present our approach to reduce the number of
-vulnerabilities in container images  by updating and minimizing these
-images.
-\vspace*{-2mm}
-\subsection{Image Update Process}
-
-If vulnerabilities exist in the container images, then our first approach
-is to update these images in order to see the effects of such updates
-on the vulnerabilities.
-Updating an image involves updating all software packages that are
-inside that image. We use a 
-\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/blob/master/Scripts/update/update.sh}{bash script} 
-to update all images. That script checks which
-package manager is present inside the image, and based on that
-it updates OS packages of the image
-accordingly. However, this action affects the reproducibility
-of that image. For example, if a package is used in an experiment
-and later that package is updated, subsequent instances of the experiment may actually
-get different results.
-\vspace*{-2mm}
-\subsection{Image Minimization Process}
+\subsection{Image Minification}
 
@@
 %out which packages we need for the pipeline to function properly.
-\change{We revert to our second approach i.e. image minimization to reduce the number of vulnerabilities in the
-images with the aim to remove unused packages from the images.
-We use Neurodocker for this purpose.
-This tool traces and deletes unnecessary files from an image execution, however
-the removal of a packages file is not reflected in the installation status of
-the package manger.
-Therefore, after minimization, the same amount of vulnerabilities is still
-reported since image scanners report vulnerabilities according to the installed
-packages.
-In order to update the package manager information, it is essential to
-determine which packages are required for the pipeline to function properly}.
-To allow for that, we utilize
-Reprozip~\cite{rampin2016reprozip}, an open-source tool that
-helps scientists to make their research reproducible. This tool traces operating system calls used by the
-application during execution, and then based on this trace, it recognizes binaries, files, environment variables,
-and library dependencies that are used by the application for future re-execution. If the OS is
-Debian or RPM-based, Reprozip also
-uses an available package manager to acquire a list of distribution packages from where these files come from.
-So, a list of packages that are needed for the application re-execution is determined. We run applications
-using specific command lines given on application's Github repository in order to collect Reprozip trace.
-These command lines represent how applications should be used.
-Following that, the list
-is expanded by adding important and required packages that are essential
-for the system to function. Finally, we figure out all the dependencies of these packages using Debtree
-~\cite{debtree}, which is avaiable in Debian and Ubuntu. It's alternative in Centos is Repoquery (\url{https://linux.die.net/man/1/repoquery}), which
-gives a complete dependency tree of a particular package.
-Effectively all needed packages are kept and remaining unnecessary packages are removed. \change{We use
-\href{https://github.com/kaurbhupinder/Vulnerability-Analysis/tree/master/Scripts/minification}{bash scripts} for
-the image size reduction process, which install Reprozip in the image, collect Reprozip trace, and
-finally delete all unnecessary packages. In this script, we use two temporary
-image containers to install Reprozip, collect its trace,
-identify the dependencies of the needed packages and then finally use
-a fresh image container to
-delete unnecessary packages from the image}.
 
-\subsection{Hybrid Approach}
+A second approach to reduce the number of vulnerabilities in the images is
+to remove unnecessary packages, an operation potentially specific to each
+analysis. We used the open-source \reprozip tool~\cite{rampin2016reprozip}
+to capture the list of packages used by an analysis. For this purpose,
+\reprozip first captures the list of files involved in the analysis,
+through system call interception, then retrieves the list of associated
+software packages, by querying the package manager. We extend this list
+with a passlist of packages required for the system to function
+\tristan{can you give an example?}, and with all the dependencies of the
+required packages, retrieved using Debtree~\cite{debtree} (Repoquery
+(\url{https://linux.die.net/man/1/repoquery}) could be used in RPM-based
+distributions instead). Our minification script, available
+\href{https://github.com/big-data-lab-team/container-vulnerabilities-paper/tree/master/Scripts/minification}{here},
+installs \reprozip in the image to minify, runs an analysis to collect a
+\reprozip trace, and finally deletes all unnecessary packages.
 
-Following the two previous approaches, we employ a hybrid approach, where
-we combine both update and size reduction processes in an attempt to
-lessen number of vulnerabilities or to test the effect of
-combining two approaches. To allow for that, we first update all packages in
-the image, then delete all unnecessary packages. Applying these processes in reverse
-may reduce the needed work; however this is not possible in all cases. For instance,
-some packages, such as \texttt{apt-transport-https}, are required to fetch updates, deleting these packages
-ahead of time will disallow the update process to take place.
-\vspace*{-2mm}
+Using this approach, we minified five Debian- or Ubuntu-based BIDS app images,
+using basic analysis examples found in the applications documentation.
+
+% \subsection{Hybrid Approach}
+
+% Following the two previous approaches, we employ a hybrid approach, where
+% we combine both update and size reduction processes in an attempt to
+% lessen number of vulnerabilities or to test the effect of
+% combining two approaches. To allow for that, we first update all packages in
+% the image, then delete all unnecessary packages. Applying these processes in reverse
+% may reduce the needed work; however this is not possible in all cases. For instance,
+% some packages, such as \texttt{apt-transport-https}, are required to fetch updates, deleting these packages
+% ahead of time will disallow the update process to take place.
+
 \section{Results}
 
-In this section,
-we first discuss the detected vulnerabilities in the images and compare the
-results. We then discuss the effect of updating/minimizing the image and applying the hybrid
-approach on the detected vulnerabilities.
-Lastly, we do an analysis of obtained results and explain the reasons behind our
-findings.
-\vspace*{-2mm}
+Figure~\ref{fig:vulnerabilities} summarizes our results. All the collected
+data are available in our GitHub repository at
+\url{https://github.com/big-data-lab-team/container-vulnerabilities-paper}
+with a Jupyter notebook to generate the figures.
+
 \subsection{Detected Vulnerabilities}
 
-\change{Table~\ref{table1} shows the number of vulnerabilities in the different images,
-detected by each of the scanners. Image labels from a to al represents
-Docker images, whereas remaining ones belong to Singularity.
-Vuls shows \textit{no data} for images \texttt{bids/antscorticalthickness:v2.2.0-1} and \texttt{bids/afni\_proc:latest},
-which have Ubuntu 17.04 and 17.10 OS distribution respectively. This is because Vuls
-cannot support scanning of these two distributions as they reached end of life.
-For Centos images, Anchore and Clair gives scanning results using Red Hat Security Advisory
-(RHSA) identifiers for Centos images, whereas Vuls uses CVE identifiers.
-RHSA identifiers specifies security patches that are pending to apply and
-CVE identifiers specifies vulnerabilities that exist in the system.
-So, we mapped RHSA identifiers to corresponding CVE identifiers to make
-a fair comparison of scanners. Table~\ref{table1} shows
-all vulnerabilities using CVE identifiers.}
-\newline\\
-Figure~\ref{fig:graph1} provides more image-specific information.
-It represents the number of vulnerabilities that are present inside each images.
-The overall trend shows that as the number of packages increases in the image, the number of vulnerabilities
-also get increased.
-This Figure also infers that the Alpine distribution, being a
-lightweight distribution, has the least number of vulnerabilities, whereas more vulnerabilities are reported for
-distributions with more packages such as Ubuntu.
-We also analyze that out of the total Docker images scanned by our experiments, Debian reports more high-level vulnerabilties, as
-classified by databases, than others.
-\begin{table*}
-\csvreader[%
- tabular={|c|c|c|c|c|c|},
-	table head = \hline\textbf{Labels} &\textbf{{Image names}} & \textbf{Anchore} & \textbf{Clair} & \textbf{Vuls} & \textbf{Stools}\\\hline,
-	late after line= \\,
-        late after last line=\\\hline %
-	]{resul.csv}{labels=\labels,names=\names,A=\A,C=\C,V=\V,Stools=\Stools}%
-        {\labels & \names & \A & \C & \V & \Stools}
-       \centering
-	\vspace*{1mm}
-	\caption{\label{table1}Number of vulnerabilities by scanners} 
-\end{table*}
-
 \begin{figure*}
-        {\includegraphics[scale=1.5,width=\textwidth]
-        {Figures/vulngraph.pdf}}
-	\vspace*{-7mm}
-        \caption{\label{fig:graph1} Number of vulnerabilities by packages}
+\includegraphics[width=\textwidth]{Figures/figure.pdf}
+\caption{\label{fig:vulnerabilities} Number of vulnerabilities detected
+by Anchore in container images. \textbf{(A)} Number of vulnerabilities
+by container image and severity. \textbf{(B)} Combined
+effect of image minification and package update on 5 container images. \textbf{(C, D)}
+Number of vulnerabilities by number of packages, before and after
+package update.}
 \end{figure*}
 
+A substantial number of vulnerabilities were found in the tested container
+ images (Fig~\ref{fig:vulnerabilities}-\textbf{A}), with an average of 466 vulnerabilities
+  per image and a median of 372. In comparison, no vulnerabilities were found in base
+ Docker images \texttt{ubuntu:20.04} and \texttt{centos:7} after package
+ update. Moreover, a significant fraction of detected vulnerabilities are
+ of high severity
+ (\href{https://www.first.org/cvss/specification-document}{CVSS} score
+ >=7.0) and a few of them are of critical severity (CVSS >= 9.0). Remote
+ attackers could possibly exploit these vulnerabilities to execute
+ arbitrary code in the container, by crafting responses to specific network
+ requests. The OS distribution is reported only for illustration purposes,
+ as no obvious association between the OS distribution and numbers of
+ vulnerabilities could be found.
+
+Unsuprisingly, a strong linear relationship is found between the number of
+detected vulnerabilities and the number of packages present in the
+container image (Fig~\ref{fig:vulnerabilities}-\textbf{C}, r=0.83,
+$p\textless10^{-10}$). On average, 1.8 vulnerabilities are introduced for
+each new package installation. This observation motivates a systematic
+review of software dependencies by application developers, to avoid
+unnecessary packages in container images. This is also an argument in favor of lightweight
+distributions such as Alpine. Compared to Ubuntu and Debian distributions,
+CentOS images seem to have a lower number of vulnerabilities by package on
+average, although data is too scarce to conclude.
+
+\subsection{Effect of image udpate}
+
+Updating container images reduces the number of vulnerabilities by package
+by a factor of 3 on average, leading to an extra 0.6 vulnerabilities by
+package (Fig~\ref{fig:vulnerabilities}-\textbf{D}, r=0.81,
+$p\textless10^{-7}$). Six container images are missing on this figure; they
+could not be updated since their OS distributions reached end of life
+\tristan{give more details, one of these images is centos 7 which didnt
+reach EOL}. In spite of the associated reproducibility challenges, updating
+packages therefore appears as a very good way to avoid vulnerabilities. It
+is not an ultimate solution though, as substantial numbers of
+vulnerabilities remain.
+
+\subsection{Effect of minification}
+
+Another approach to reduce the number of vulnerabilities involves deleting
+unnecessary packages from the container images. It is a tedious operation,
+as it requires running an actual data analysis in the container image, to
+identify the packages required by the application. In addition, the
+resulting container image is only valid for the specific type of analysis
+used in the minification process, as other executions might require a
+different set of packages.
+
+Using the ReproZip-based approach described previously, we minified 5
+different images covering the spectrum of detected vulnerabilities
+(Fig~\ref{fig:vulnerabilities}-\textbf{B}). We find that minification reduces the
+number of vulnerabilities, albeit less systematically than package update.
+For some container images, such as image \textbf{S}, minification removes more
+than 70\% of the detected vulnerabilities. For other images, such as
+image \textbf{f}, it only reduces the number of vulnerabilities by less than 1\%.
+The effect of minification stems from the number of packages
+than can be removed, which varies greatly across images. For
+instance, images \textbf{f} and \textbf{a} have a large number of packages,
+but the last majority of them is required by the analysis, which makes
+minification less useful. In other cases, a limited number of unnecessary packages contain 
+a significant number of vulnerabilities, which makes minification very impactful. 
+This was the case in images \textbf{d}, \textbf{S} and \textbf{U}, where removing compilers
+and kernel headers reduced the number of vulnerabilities by an important fraction.
+
+\subsection{Combined effect of image update and  minification}
+
+Package update and image minification remove different types of
+vulnerabilities. The former is efficient against vulnerabilities that have
+been fixed by the package maintainers, while the latter targets unused
+software. In four of the five tested images, we find that combining update
+and minification further reduces the number of vulnerabilities compared to
+using only one of these processes
+(Fig~\ref{fig:vulnerabilities}-\textbf{B}) \tristan{revise when
+minification in image f is clarified}. The combined effect of update and
+minification seems to be dependent mostly on the effect of minification: if
+minification is useful, then it is beneficial to run it in combination with
+package update.
+
+\subsection{Discrepancies between scanners}
+
+The results presented so far were obtained with Anchore, a popular
+container image scanning tool. We scanned the images with two other tools,
+Clair and Vuls, to evaluate the stability of our results.
+
+% \begin{table*}
+% 	\csvreader[%
+% 	 tabular={|c|c|c|c|c|c|},
+% 		table head = \hline\textbf{Labels} &\textbf{{Image names}} & \textbf{Anchore} & \textbf{Clair} & \textbf{Vuls} & \textbf{Stools}\\\hline,
+% 		late after line= \\,
+% 			late after last line=\\\hline %
+% 		]{resul.csv}{labels=\labels,names=\names,A=\A,C=\C,V=\V,Stools=\Stools}%
+% 			{\labels & \names & \A & \C & \V & \Stools}
+% 		   \centering
+% 		\vspace*{1mm}
+% 		\caption{\label{table1}Number of vulnerabilities detected by the four scanners.
+Vuls shows \textit{no data} for images \texttt{bids/antscorticalthickness:v2.2.0-1} and \texttt{bids/afni\_proc:latest}
+% 		since their OS distributions reached end of life.} 
+% 	\end{table*}
 	\begin{figure}
@@
 
-\subsection{Discrepancies between Scanners}
+% Table~\ref{table1} shows the number of vulnerabilities detected in the different images
+% by the four scanners. 
+% \change{Our experiments concluded considerable discrepancies in the results obtained by
+% these scanners. %We higlighted all Centos images in the Table~\ref{table1} since.
+% While comparing scanner results, we exluded two images \texttt{bids/antscorticalthickness:v2.2.0-1} and
+% \texttt{bids/afni\_proc:latest} because Vuls
+% cannot scan these image, hence no results are present to compare.
+% %The reason behind excluding
+% %vulnerability identifiers for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
+% %to report pending patches that need to be applied to specific packages,
+% %whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
+% %vulnerabilities in packages. We exluded other two images because Vuls
+% %can not scan these image, hence no results are present to compare.
+% In most cases,
+% Anchore reports more vulnerabilities than Vuls and Clair resulting in 
+% the Jaccard coefficient of 0.63 with Clair, 0.59 with Vuls,
+% whereas Vuls and Clair share more common vulnerability detection resulting to the Jaccard coefficient of 0.86.
+% Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
+% the scanners in Docker images and the overlap between them.
+% This Figure also excludes two non-comparable images, which cannot be scanned with Vuls.
+% It is interesting to note that out of all reported vulnerabilities, 4453 vulnerabilities are only
+% reported by Anchore, 699 by Clair, and 536 by Vuls.}
+% \newline\\
+% As the number and type of vulnerabilities reported by the these scanners are significantly different from each other,
+% we desire to investigate the reasons behind these differences.
+% Following our investigation, we are able to explain some of the reasons behind
+% the differences. 
+% Such reasons were resulted from the way these scanners function or behave 
+% in particular, the following actions by the scanners are indicative:
+% \begin{itemize}
+%    \item scanners ignoring vulnerabilities in Linux-kernel-header packages,
+%    \item scanners referring to different vulnerability databases,
+%    \item different frequency of updating their databases,
+%    \item bugs in scanners. 
+% \end{itemize}
 
-\change{Our experiments concluded considerable discrepancies in the results obtained by
-these scanners. %We higlighted all Centos images in the Table~\ref{table1} since.
-While comparing scanner results, we exluded two images \texttt{bids/antscorticalthickness:v2.2.0-1} and
-\texttt{bids/afni\_proc:latest} because Vuls
-cannot scan these image, hence no results are present to compare.
-%The reason behind excluding
-%vulnerability identifiers for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
-%to report pending patches that need to be applied to specific packages,
-%whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
-%vulnerabilities in packages. We exluded other two images because Vuls
-%can not scan these image, hence no results are present to compare.
-In most cases,
-Anchore reports more vulnerabilities than Vuls and Clair resulting in 
-the Jaccard coefficient of 0.63 with Clair, 0.59 with Vuls,
-whereas Vuls and Clair share more common vulnerability detection resulting to the Jaccard coefficient of 0.86.
-Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
-the scanners in Docker images and the overlap between them.
-This Figure also excludes two non-comparable images, which cannot be scanned with Vuls.
-It is interesting to note that out of all reported vulnerabilities, 4453 vulnerabilities are only
-reported by Anchore, 699 by Clair, and 536 by Vuls.}
-\newline\\
-As the number and type of vulnerabilities reported by the these scanners are significantly different from each other,
-we desire to investigate the reasons behind these differences.
-Following our investigation, we are able to explain some of the reasons behind
-the differences. 
-Such reasons were resulted from the way these scanners function or behave 
-in particular, the following actions by the scanners are indicative:
-\begin{itemize}
-   \item scanners ignoring vulnerabilities in Linux-kernel-header packages,
-   \item scanners referring to different vulnerability databases,
-   \item different frequency of updating their databases,
-   \item bugs in scanners. 
-\end{itemize}
+% Below, we explain these reasons in further details and provide examples
+% for clear illustrations.
 
-Below, we explain these reasons in further details and provide examples
-for clear illustrations.
+% \textbf{Linux-kernel-headers:} Clair and Vuls ignore all vulnerabilities in the Linux-kernel-headers,
+% whereas Anchore reports all of them.
+% We find that 4443 out of 4453 vulnerabilities that are only reported by Anchore are present in Linux-kernel-headers.
+% For example, CVE-2019-9506 present in Linux-libc-dev-4.4.0-31.50, reported by Anchore, is not
+% detected by both Vuls and Clair.
+% Linux-kernel-headers are the header files that only provide function names, their parameters, and their
+% return types.
+% The actual source code of those functions is present in the Linux kernel and is not inside the image.
+% So, vulnerability detection in header files
+% is irrelevant in this case.
 
-\textbf{Linux-kernel-headers:} Clair and Vuls ignore all vulnerabilities in the Linux-kernel-headers,
-whereas Anchore reports all of them.
-We find that 4443 out of 4453 vulnerabilities that are only reported by Anchore are present in Linux-kernel-headers.
-For example, CVE-2019-9506 present in Linux-libc-dev-4.4.0-31.50, reported by Anchore, is not
-detected by both Vuls and Clair.
-Linux-kernel-headers are the header files that only provide function names, their parameters, and their
-return types.
-The actual source code of those functions is present in the Linux kernel and is not inside the image.
-So, vulnerability detection in header files
-is irrelevant in this case.
+% \textbf{Ubuntu vulnerabilities with status as “Not-affected”:} Vuls reports vulnerabilities that have status
+% as "not-affected" in the Ubuntu database. It means that according to Ubuntu the image is not affected
+% by the particular vulnerability. In other words, Vuls reports vulnerabilities that it should not have been reported.
+% For example, when we scan an image having the Trusty release in it and Vuls reports CVE-2015-2305
+% in the package Cups. However, upon checking the Ubuntu vulnerability database, we find that package Cups in Trusty is not
+% affected by this vulnerability.
 
-\textbf{Ubuntu vulnerabilities with status as “Not-affected”:} Vuls reports vulnerabilities that have status
-as "not-affected" in the Ubuntu database. It means that according to Ubuntu the image is not affected
-by the particular vulnerability. In other words, Vuls reports vulnerabilities that it should not have been reported.
-For example, when we scan an image having the Trusty release in it and Vuls reports CVE-2015-2305
-in the package Cups. However, upon checking the Ubuntu vulnerability database, we find that package Cups in Trusty is not
-affected by this vulnerability.
+% \textbf{Ubuntu vulnerabilities with status as "Ignored (reached end-of-life)":}
+% Some vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life. 
+% However, in Ubuntu 14.04 ESM release, these vulnerabilities may or may not be present.
+% Anchore checks the last status of these vulnerabilities in LTS whether the package was vulnerable
+% prior to the end-of-life. Only if it was vulnerable, Anchore reports it, otherwise it does not.
+% If this kind of vulnerability is present in ESM release then Clair reports it because it
+% only refers to ESM release. On the other hand, if the vulnerability
+% status in ESM release is "DNE" (Does Not Exist), then Clair does not report it. 
+% For example, CVE-2017-9994 vulnerability in Libav package is ignored in Trusty LTS release due to its end-of-life.
+% Consequently, it is not reported by Anchore. This vulnerability has status as "DNE" in Trusty ESM
+% release so Clair also does not report it. As Ubuntu 14.04 LTS release is present inside the images,
+% Clair's referring to Ubuntu 14.04 ESM release vulnerability database is incorrect.
 
-\textbf{Ubuntu vulnerabilities with status as "Ignored (reached end-of-life)":}
-Some vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life. 
-However, in Ubuntu 14.04 ESM release, these vulnerabilities may or may not be present.
-Anchore checks the last status of these vulnerabilities in LTS whether the package was vulnerable
-prior to the end-of-life. Only if it was vulnerable, Anchore reports it, otherwise it does not.
-If this kind of vulnerability is present in ESM release then Clair reports it because it
-only refers to ESM release. On the other hand, if the vulnerability
-status in ESM release is "DNE" (Does Not Exist), then Clair does not report it. 
-For example, CVE-2017-9994 vulnerability in Libav package is ignored in Trusty LTS release due to its end-of-life.
-Consequently, it is not reported by Anchore. This vulnerability has status as "DNE" in Trusty ESM
-release so Clair also does not report it. As Ubuntu 14.04 LTS release is present inside the images,
-Clair's referring to Ubuntu 14.04 ESM release vulnerability database is incorrect.
+% \textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
+% are not detected by Clair but they affect Ubuntu 14.04 LTS, and hence detected by Vuls and Anchore. The CVE-2017-13758 is an example
+% of such vulnerabilities.
 
-\begin{figure*}[!ht]
-        {\includegraphics[width=\textwidth]
-        {Figures/vulnwithupdate.pdf}}
-	\vspace*{-7mm}
-        \caption{\label{fig:graph2} Number of vulnerabilities before and
-        after update of the images}
-      \end{figure*}
+% \textbf{Misses:} Clair and Vuls
+% missed vulnerabilities that they should have detected. For example, the CVE-2016-9082 
+% is present in package Cairo in Xenial release and it is not detected by Clair.
+% Vuls also missed vulnerabilities such as CVE-2019-5094.
 
-\begin{figure*}[!ht]
-        {\includegraphics[scale=1.5,width=\textwidth]
-        {Figures/bargraph.png}}
-	\vspace*{-5mm}
-        \caption{\label{fig:bargraph} Vulnerabilities by different experiments}
-      \end{figure*}
-\textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
-are not detected by Clair but they affect Ubuntu 14.04 LTS, and hence detected by Vuls and Anchore. The CVE-2017-13758 is an example
-of such vulnerabilities.
+% \textbf{Wrong Detections:} 
+% Some vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
+% present inside the image, however, Clair have reported such vulnerabilities.
+% For instance, CVE-2019-1274 is an example of such vulnerabilities. 
+% %is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
+% %Clair is only referring to Ubuntu 14.04 ESM release. 
+% We reported this issue on two Google groups of Clair i.e. CoreOS Dev and
+% clair-dev \url{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}
 
-\textbf{Misses:} Clair and Vuls
-missed vulnerabilities that they should have detected. For example, the CVE-2016-9082 
-is present in package Cairo in Xenial release and it is not detected by Clair.
-Vuls also missed vulnerabilities such as CVE-2019-5094.
+% \textbf{Database difference:} At the time we pulled Clair's database, through \texttt{arminc/clair-db:latest} Docker image, it was one week old.
+%                               As a result some vulnerabilities were not updated in the database. For instance, CVE-2019-5094, which
+% 		              was published on 2019-09-24, was not 
+% 		              updated in Clair's database. Due to which it is missed by Clair.
+% 			      Consequently, these discrepancies, even small, are sufficient to change the detection of
+% 			      the scanners.
 
-\textbf{Wrong Detections:} 
-Some vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
-present inside the image, however, Clair have reported such vulnerabilities.
-For instance, CVE-2019-1274 is an example of such vulnerabilities. 
-%is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
-%Clair is only referring to Ubuntu 14.04 ESM release. 
-We reported this issue on two Google groups of Clair i.e. CoreOS Dev and
-clair-dev \url{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}
+% \textbf{Epoch bug:} There is a bug in the Anchore scanner due to which some vulnerabilities are 
+% 		not detected by Anchore. This bug gets triggered when a package’s version have epoch 
+% 		(1:3.3.9-1ubuntu2.3) in it. For example, CVE-2018-1125 in Procps package is not
+% 		detected by Anchore due to the presence of epoch in the Procps package version.
+% 		We reported this bug to the Anchore development team through their Slack channel.
 
-\textbf{Database difference:} At the time we pulled Clair's database, through \texttt{arminc/clair-db:latest} Docker image, it was one week old.
-                              As a result some vulnerabilities were not updated in the database. For instance, CVE-2019-5094, which
-		              was published on 2019-09-24, was not 
-		              updated in Clair's database. Due to which it is missed by Clair.
-			      Consequently, these discrepancies, even small, are sufficient to change the detection of
-			      the scanners.
+% \textbf{Ubuntu vulnerabilities with status "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
+% 		which it is not able to detect some vulnerabilities. Due to this bug, Anchore does not detect 
+% 		vulnerabilities that have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
+% 		However, if this vulnerability is present in Ubuntu 14.04 ESM release, it is detected by Clair. 
+% 		For instance, CVE-2019-13565, which is present in Ubuntu 14.04 LTS, is an example of such vulnerabilities. 
+% 		We reported this bug as well to the Anchore development team through their Slack
+% 		channel.
 
-\textbf{Epoch bug:} There is a bug in the Anchore scanner due to which some vulnerabilities are 
-		not detected by Anchore. This bug gets triggered when a package’s version have epoch 
-		(1:3.3.9-1ubuntu2.3) in it. For example, CVE-2018-1125 in Procps package is not
-		detected by Anchore due to the presence of epoch in the Procps package version.
-		We reported this bug to the Anchore development team through their Slack channel.
+% \textbf{Rejected CVEs:} There are some CVEs, such as CVE-2017-13753, that are rejected because they are duplicate copies of other CVEs. 
+% 	So, Anchore and Clair does not report those rejected CVEs, but Vuls reports them.
 
-\textbf{Ubuntu vulnerabilities with status "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
-		which it is not able to detect some vulnerabilities. Due to this bug, Anchore does not detect 
-		vulnerabilities that have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
-		However, if this vulnerability is present in Ubuntu 14.04 ESM release, it is detected by Clair. 
-		For instance, CVE-2019-13565, which is present in Ubuntu 14.04 LTS, is an example of such vulnerabilities. 
-		We reported this bug as well to the Anchore development team through their Slack
-		channel.
+% \tristan{integrate this part:
 
-\textbf{Rejected CVEs:} There are some CVEs, such as CVE-2017-13753, that are rejected because they are duplicate copies of other CVEs. 
-	So, Anchore and Clair does not report those rejected CVEs, but Vuls reports them.
+% \change{
 
-\subsection{Effect Of Update}
+% The major discrepancies are shown by Anchore and Clair in Ubuntu \tristan{why?}. Both refers to Ubuntu CVE Tracker database for Ubuntu images.
+% The way in which both scanners interpret this database is different.
+% %
+% %There are different vulnerability databases, which have
+% %different formats of data.
+% %Out of which Open Vulnerability and Assessment Language (OVAL) is an international
+% %open standard and a common
+% %means of promoting publicly available security issues. 
+% %It provides details about software vulnerabilities. It helps to determine
+% %whether vulnerabilities exist in local machines or not. Apart from OVAL, operating system
+% %vendors also keep track of their vulnerabilities separately and assign
+% %a status to each vulnerability.
+% %For example, Ubuntu maintains
+% %Ubuntu CVE Tracker, Debian maintains Debian Security Bug Tracker, etc.
+% %Each vulnerability is assigned a unique Common Vulnerabilities and Exposures (CVE) number
+% %by the MITRE corporation, who maintains a list of all vulnerabilities of all distributions.
+% %In this paper, we use vulnerability and CVE interchangeably.
+% %Ubuntu CVE Tracker is used by Anchore and Clair in our experiments
+% %and there is discrepancies in the way both scanners interpret results.
+% %
+% %BIDS apps and Boutiques images in our experiments have four Linux
+% %distributions i.e. Ubuntu, CentOS, Debian, and Alpine. 
+% %Out of these distributions, Ubuntu assigns a vulnerability status to
+% %all vulnerabilities before keeping them in its vulnerability database.
+% %Each vulnerability is assigned a unique Common Vulnerabilities and Exposures (CVE) number
+% %by the MITRE corporation, who maintains a list of all vulnerabilities of all distributions.
+% %Ubuntu keeps a record of Ubuntu-specific vulnerabilities in Ubuntu CVE Tracker using their CVE
+% %numbers. In this paper, we use vulnerability and CVE interchangeably.
+% %The vulnerability status in Ubuntu CVE Tracker is subjected to change
+% %depending on the work progress to fix that vulnerability.
+% %
+% %Regarding Ubuntu, it has different
+% %types of releases e.g. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release.
+% %Ubuntu maintains its vulnerability data in Ubuntu CVE tracker, which is referred by Anchore and Clair.
+% %There is another vulnerability database i.e. Open Vulnerability and Assessment Language (OVAL) repository,
+% %which is maintained by MITRE corporation. Vuls refers to OVAL repository for getting Ubuntu vulnerability feed.
+% %The vulnerability data format of both databases is different. OVAL keeps a separate xml file for each release,
+% %which contains that release specific vulnerability information.
+% Ubuntu CVE Tracker keeps a separate file for each vulnerability, which
+% has an entry for all Ubuntu releases combined with the current status
+% of that vulnerability in that release.
+% In particular, Clair and Anchore show discrepancies for Ubuntu 14.04 which have
+% two entries for each vulnerability, one for Ubuntu 14.04 Long Term Support (LTS)
+% and second for Ubuntu 14.04 Extended Security Maintenance (ESM) release. As Ubuntu 14.04 LTS
+% reached end-of-life on 2019-04-30, so Ubuntu ignores new vulnerabilities in LTS release and
+% fix them only in ESM release. Consequently, a same vulnerability may have different vulnerability status in LTS and ESM releases,
+% which is causing discrepancies. This is because Anchore refers to Ubuntu 14.04 LTS, whereas Clair refers to
+% ESM.
+% %Further, in Ubuntu a particular release can be of different types i.e. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release. 
+% %Through our experiments, we find that Anchore and Clair report Ubuntu vulnerabilities 
+% %differently depending on either the different Ubuntu release type or vulnerability status. 
+% It is important to provide an overview of these Ubuntu vulnerability statuses, 
+% since Ubuntu is heavily utilized in our experiments. 
+% %Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
+% %reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
+% %in the form of ESM release.
+% %ESM is a paid service that can be requested from Ubuntu to get security 
+% %updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu version have different vulnerability
+% %databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
+% %exists in LTS.
+% %
+% %As an example, Ubuntu has ended support for some releases, such as 14.04 LTS,
+% %17.04, and 17.10, as they reached EOL. However, Ubuntu decided to provide optional extended support for Ubuntu 14.04.
+% %To use this extended support, users have to purchase Ubuntu 14.04 ESM release.
+% %The images in our experiments have Ubuntu 14.04 LTS, so scanners should refer
+% %to LTS release only while collecting data from the vulnerability databases.
+% %More interestingly, Clair refers to ESM release vulnerability database, however, this may lead to discrepancies in results.
+% %Further, if an image is using a Linux release where EOL has been reached that image may
+% %turns to be vulnerable as it is not possible to retrieve any updates.
+% %
+% In Ubuntu CVE Tracker, for a vulnerability all Ubuntu releases are listed with the package name
+% in which that vulnerability exists and are entitled a vulnerability status
+% (\url{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
+% encoded in the following form:
+% \newline \\
+% \noindent <release>\_<source-package>: <status> (<version/notes>)
+% \newline\\
+% The <version/notes> given with a vulnerability status provide more
+% information about the vulnerability.
+% For a given release, the vulnerability status can be any one of the following:
 
-As a result of image updating,
-scanning results change significantly.
-Figure~\ref{fig:graph2} represents the number of vulnerabilities that are detected by Anchore before and after 
-image update. 
-In fact, this Figure combines the original results of Figure~\ref{fig:graph1} with the results of the image update
-experiment.
-Clearly, the figure illustrates that when images are updated, the number of vulnerabilities reduces by a
-significant number. Furthermore, a mild slope of vulnerabilities after the image update shows that
-there is a set of packages that contain vulnerabilities and have not been fixed yet. Also, these
-vulnerabilities mostly have \textit{Low, Negligible, or Medium} severity status, meaning that
-\textit{high} severity vulnerabilities are prioritized and fixed fast.
-Besides that, it is also interesting to note that some images in Figure~\ref{fig:graph2}
-do not have update results. This is because some Linux distributions reached end-of-life and
-are not being updated anymore.
-Despite of the significant drop in the number of vulnerabilities as a result of image updating,
-there is still a number of vulnerabilities reported by the scanners. This is due to the
-vulnerabilities which do not have fix yet.
+% \textbf{DNE (Does Not Exist):} The package does not exist in the
+% 		release.
 
-\subsection{Effect Of Size Reduction}
+% \textbf{needs-triage:} The vulnerability of this package
+% 		is not known, and hence evaluation is needed.
 
-Our second approach involves the deletion of unnecessary packages from the images.
-We tested our approach on 5 different images covering the spectrum of Figure~\ref{fig:graph1}.
-We find that the image reduction process brings inconsistent deviation in scanning results.
-%We find that
-%after the size reduction process, sometimes the scanning results deviate only a little from the results
-%without minimization. While the minimization process results in significant reduction
-%in the number of vulnerabilities in some cases, we find that in other cases the effect
-%is negligible. 
-In other words, the image reduction was inconsistent.
-According to our analysis, this can be due to two reasons: \rom{1}) the number of
-deleted packages
-and \rom{2}) the kind of deleted packages. 
-For an instance, if the deletion is for a package that includes a lot of vulnerabilities,
-that particular deletion naturally results in the drop of number of vulnerabilities.
-In other
-words, deleting more packages reduces more vulnerabilities. 
-For instance, we were able to delete only 21 and 25 packages for 
-\textit{bids/ndmg} and \textit{poldracklab/fmriprep:1.2.3} images respectively. Consequently, vulnerabilities
-reduced only by 4 and 17 respectively. 
-Also, if we delete packages that contain a lot of vulnerabilities, it helps in reducing
-vulnerabilities by a significant number. For instance, in case of our experiments
-deleting compilers and Linux-kernel-header packages helped to minimize vulnerabilities
-by a significant number in \textit{bids/example, bids/freesurfer, and bids/mindboggle:0.0.4-1}.
+% \textbf{not-affected:} The package, while related to the
+% 		vulnerability in some way, is not affected by the issue.
+% 	%	The <notes> should
+% 	%	provide detailed information, if needed.
+% 		%For instance, if the given
+% 		%status is "not-affected (1.14.6-1.1)" then this indicates that this specific
+% 		%package version is not affected.
 
-\subsection{Combined Effect Of Update and Size Reduction}
+% \textbf{needed:} The package is vulnerable and needs to be fixed.
 
-Our last experiment includes updating the image and then removing unnecessary packages from it.
-Figure~\ref{fig:bargraph} displays the results. 
-Our initial expectation was that with the update and size reduction process together, we will be able to
-reduce vulnerabilities even more. However,
-we analyzed that this is not always true. Again, it depends on which packages are deleted and how
-many vulnerabilities they contained. To illustrate, \textit{bids/example} image in Figure~\ref{fig:bargraph}
-shows no effect of size reduction along with update process. It has 181 vulnerabilities for both experiments.
-Meaning that packages, which we deleted after updating the image, were already vulnerability free. Therefore,
-scanning results did not change.
-\vspace*{-2mm}
+% \textbf{active:} The package is vulnerable, needs fixing, and is 
+%                  actively being worked on.
+
+% \textbf{ignored:} The package, while related to the
+% 		vulnerability in some way, is being ignored for some reason. 
+% 	%	The
+% 	%	<notes> should provide that reason.
+% 	%	For instance, if status looks like
+% 	%	"ignored (reached end-of-life)", this means that the given Ubuntu release already reached
+% 	%	end-of-life, so this CVE is ignored by Ubuntu. However, if there
+% 	%	is extended security support for this release then this
+% 	%	CVE will be handled in ESM release.
+
+% \textbf{pending:} The package is vulnerable and
+%                   has been fixed but an update has not been yet uploaded or
+% 		  published.
+% 		 % The <version> is given to indicate the particular 
+% 		 % version where the fix has been done.
+
+% \textbf{deferred:} The package is vulnerable, but 
+%                    its fix has been deferred for some reason. 
+% 		  % The <notes>
+% 		  % should provide further details.
+% 		  % If a date is mentioned, e.g.
+% 		  % "deferred (2015-02-02)", the given date specifies the date when
+% 		  % the CVE was deferred.
+
+% \textbf{released:} The package was vulnerable, but
+% 		an update has been already uploaded and published.
+% 	%	e.g. "released (1.2.3)",
+% 	%	<version> indicates the first version where the fix was applied.
+
+% \textbf{released-esm:} The package was vulnerable and
+% 		an update has been already uploaded and published. However,
+% 		this update is published in the Ubuntu ESM release only and not in LTS.}
+% 		%The fixed version of such packages is appended by either
+% 		%+esm or \char`\~esm, indicating that this package version is available
+% 		%only via ESM.
+
+% 		% \newlne\\
+% % Figure~\ref{example} illustrates how the information of a vulnerability is represented
+% % in the Ubuntu CVE Tracker.
+
+% % \begin{figure}[!ht]
+% % 	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
+% % 	{Figures/vulnExample2.png}}}
+% %         \caption{\label{example} Representation of a vulnerability in Ubuntu CVE Tracker}
+% % \end{figure}
+% % \vspace*{-7mm}
+% }
+
 \section{Discussion}
+
+% files vs packages
+
+% reproducibility vs update
+However, this action affects the reproducibility
+of that image. For example, if a package is used in an experiment
+and later that package is updated, subsequent instances of the experiment may actually
+get different results.
+
+% minification is specific to the analysis
+% tried neurodocker
+% don't point at specific applications, it's a general issue
 
@@
 already reached end-of-life and are
-no longer getting updates. Furthermore, the minimization of images is a time consuming process. As we have to run
+no longer getting updates. Furthermore, the minification of images is a time consuming process. As we have to run
 the pipeline to get Reprozip trace that can take up to several hours. Also, the user should have proper knowledge

### 2020-09-10 Scripts/compare_results/AnchoremapRHSAtoCVE.py
added mapping scripts

@@ -1,0 +1,47 @@
+# Import BeautifulSoup
+from bs4 import BeautifulSoup as bs
+import csv
+import sys
+content = []
+result = []
+cves = []
+def domapping(file1,file2):
+    with open(file1,'r') as fp:
+              rows=fp.readlines()
+    for row in rows:
+        row = row.strip()
+    
+    #Read the XML file
+    with open("redhat.xml", "r") as file:
+        # Read each line in the file, readlines() returns a list of lines
+        content = file.readlines()
+        # Combine the lines in the list into a string
+        content = "".join(content)
+        bs_content = bs(content, "lxml")
+        for row in rows:
+         row = row.strip()
+         req_id = bs_content.find("reference", {"ref_id": row})
+         result = list(req_id.next_siblings)
+         for each in result:
+           try:
+               cves.append(each['ref_id'])
+               print(each['ref_id'])
+           except:
+             continue
+    cves_req = list(set(cves))
+    #print(cves_req)
+    #print(len(cves_req))
+    with open(file2,'w') as out:
+            for entry in cves_req:
+                out.write(entry)
+                out.write("\n")
+
+def main():
+    file1=sys.argv[1] ## csv file containing RHSA and needed to be mapped
+    file2=sys.argv[2] ## csv file where mapped CVE needs to be written
+    domapping(file1,file2)
+
+
+
+if __name__== "__main__":
+  main()

### 2020-09-10 paper.tex
Added discrepancy analysis to notebook
Fixed figure path
Rewrote discussion and conclusion

@@
 \renewcommand{\labelitemi}{$\textendash$}
-\title{Security Vulnerabilities of Container Images in Neuroimaging}
+\title{Security Vulnerabilities in Neuroimaging Container Images}
 \begin{filecontents*}{resul.csv}
@@
 \begin{abstract}
-Software containers have become key technologies for the deployment of
+Software containers have become key to the deployment of
 scientific data analyses on high-performance computing (HPC)
@@
 from BIDS apps were Docker images, whereas Boutiques contained 18 Docker images
-and 6 Singularity images.
+and 6 Singularity images. \tristan{check the numbers, we have 38 images in the results}
 
@@
 
+\todo{mention neuro docker}
+
 A second approach to reduce the number of vulnerabilities in the images is
@@
 \begin{figure*}
-\includegraphics[width=\textwidth]{Figures/figure.pdf}
+\includegraphics[width=\textwidth]{Figures/results.pdf}
 \caption{\label{fig:vulnerabilities} Number of vulnerabilities detected
@@
 	\begin{figure}
-        {\includegraphics[scale=2.5,width=\columnwidth]
-        {Figures/venn.pdf}}
-	\vspace*{-10mm}
-	\caption{\label{fig:venn} Scanner results}
+        \includegraphics[width=\columnwidth]{Figures/venn.pdf}
+	\caption{\label{fig:venn} Comparison between image scanners.}
 \end{figure}
@@
 
-% files vs packages
+There is a widespread issue with security vulnerabilities in container
+images for neuroimaging analyses, and it is likely to impact other
+scientific disciplines as well. Indeed, it is common for container images
+to hold hundreds of vulnerabilities, including several of critical
+severity. Container images are impacted regardless of the type of analyses
+that they support, and the main OS distributions Ubuntu, Debian and CentOS
+are all impacted.
 
-% reproducibility vs update
-However, this action affects the reproducibility
-of that image. For example, if a package is used in an experiment
-and later that package is updated, subsequent instances of the experiment may actually
-get different results.
+Software updates remove about two-thirds of the vulnerabilities found and
+should certainly be considered the primary solution to this problem.
+However, in neuroimaging as in other disciplines, software updates are
+generally discouraged because they can affect analysis results by
+introducing numerical perturbations in the
+computations~\cite{gronenschild2012effects,glatard2015reproducibility}. We
+believe that this position is not viable from an IT security perspective,
+and that it could endanger the entire Big Data processing infrastructure,
+starting with the HPC centers. Instead, we advocate a more systematic
+analysis of the numerical schemes involved in data analyses, which, coupled
+with software testing, would make the analyses robust to software updates.
+As a first step, the packages impacting the analyses could be specifically
+identified and the others updated, which would largely remove
+vulnerabilities.
 
-% minification is specific to the analysis
-% tried neurodocker
-% don't point at specific applications, it's a general issue
+Ultimately, software updates should even occur at runtime rather than when
+the container image is built. Indeed, it is likely that container images
+used for scientific data analyses be built only occasionally, perhaps every
+few weeks when a release becomes available, which may not be compatible
+with the frequency of required security updates. In fact, there is no
+definite reason for the application software release cycle to be
+synchronized with security updates, and security updates shouldn't be
+dependent on application software developers. Instead, we think it would be
+relevant for analytics engines to (1) systematically apply security updates
+when containers start, and (2) run software tests provided by application
+developers, including numerical tests, before running analyses.
 
-As we noticed that none of the Boutiques and BIDS images at the time of the study are free of vulnerabilities, out of which
-so many are high severity vulnerabilities as well. Yet there is not a single image scanner on which we can rely upon for
-scanning. Additionally, we cannot update all images because some OS releases, which are used inside images, 
-already reached end-of-life and are
-no longer getting updates. Furthermore, the minification of images is a time consuming process. As we have to run
-the pipeline to get Reprozip trace that can take up to several hours. Also, the user should have proper knowledge
-of running the pipeline because it is image-specific. In addition to that, Reprozip can be only installed
-in the images having Python version 2.7.3 or greater, or 3.3 or greater. Above all, there is no guarantee that
-the commands that you run to get Reprozip trace covers the whole program, maybe it runs a particular
-branch of the program. So, there should be some kind of coverage measurement.
-Besides this, as scanners report vulnerabilities according to the versions of the installed packages,
-they are likely to miss packages that are not installed using package manager. 
-Therefore, we suggest some particular rules that can be
-followed to keep container images safe.
-\begin{itemize}
-	\item Update packages regularly inside images.
-	\item Remove unnecessary packages, in particular the ones used for installation (compilers, source packages, etc.).
-	\item Choose your base OS image wisely.
-	\item Run image scanning tools in CI scripts. For instance Anchore.
-	\item Protect your GitHub/DockerHub credentials because if automated builds is set up
-in Docker Hub, it can automatically build images from external repositories, for instance GitHub.
-\item Minimize dependencies inside images.
-\item Avoid static linking because it obfuscates vulnerability scanning.
-\item Use the package manager to facilitate vulnerability detection.
-\item Use OS releases that have LTS support.
-\end{itemize}
-\vspace*{-2mm}
-\section{Conclusions and Future Work}
+Implementing such a workflow, however, requires a long-term endeavour to
+evaluate broadly the stability of data analysis pipelines, and to develop
+the associated software tests. For the shorter term, we identified the
+following recommendations for application developers to reduce the number
+of security vulnerabilities in container images:
 
-In this paper, we performed various experiments to study the security state of the Docker
-and Singularity images, which are used in the neuroimaging field. We found out strong correlation
-between the number of packages and the number of vulnerabilities in the images, which implies
-that the number of vulnerabilities increases with the number of packages. We also found out that
-updating images reduces the number of vulnerabilities by a significant number. However, for some
-vulnerabilities there are no fixes available yet so the images cannot 
-be made totally invulnerable. Continuing with our next two experiments, we analyzed that the
-image size reduction process also reduces vulnerabilities a lot. However, we found out that this is not
-always true. It depends on two factors: the kind of packages and the number of packages that we are
-deleting.
+\begin{enumerate}[leftmargin=0pt,itemindent=*]
+\item \emph{Introduce software dependencies cautiously}. Software
+dependencies come with a potential security toll that is often neglected.
+For instance, it can be tempting to add a complete toolbox to implement a
+relatively minor operation in a data analysis pipeline, such as a data
+format conversion, while the same functionality might be available in the
+existing dependencies of the pipeline, albeit in a less convenient way.
+\item \emph{Use lightweight base images such as Alpine Linux}. Base
+images often come with packages that are useful in personnal computers or
+servers, but not in containers dedicated to a specific data analysis. In
+addition, lightweight distributions define packages with a fine
+granularity, allowing developers to avoid installing unnecessary
+dependencies. For instance, the compressed size of the Alpine Linux base
+image on DockerHub is only 2.7~MB while that of the Ubuntu base image is
+27~MB.
+\item \emph{Use OS releases with long-term support.} Security updates are
+not provided for OS distributions that reached end of life. When a given
+release of a data analysis pipeline is expected to be used over a long
+period of time, typically several years as it is common in neurosciences,
+the life cycle of the distribution release should be considered when
+choosing a base container image. OS distributions have very different life
+cycle durations, as long and short life cycles serve different purposes.
+For instance, among RedHat-based distributions Fedora release a new version
+every 6 months and provide maintenance for about a year, while CentOS
+releases every 3-5 years and provide maintenance for 10 years. Similarly,
+Ubuntu LTS (long-term support) distributions provide free security updates
+for 5 years, and Debian stable releases are maintained for 3 years (the
+Debian LTS project intends to extend this duration to 5 years). Commercial
+offers for extended maintenance periods are common. 
+\item \emph{Install packages, not files}. Vulnerability scanners such as
+Anchore, Clair or Vuls detect vulnerabilities from the list of packages
+installed in a container image. Therefore, vulnerabilities contained in
+software tools installed through direct file download rather than through
+the package manager would go completely undetected. Domain-specific
+distributions such as \href{http://neuro.debian.net}{NeuroDebian} or
+\href{https://docs.fedoraproject.org/en-US/neurofedora/overview/}{NeuroFedora}
+in neuroimaging are useful in this respect.
+\item \emph{Minify container images.} The automated minification
+process that we used in our study is unwieldy for a routine use, as it
+requires capturing execution traces with ReproZip to reconstruct the graph
+of package dependencies required for the analysis. In practice, it would be
+more practical for software developers to identify and remove unnecessary
+dependencies when they build containers, based on their knowledge of the
+application.
+\item \emph{Run image scanners during continuous integration.} Scanning
+container images cann be a cumbersome process (for instance, scanning the
+\todo{x} images involved in this study takes about \todo{y} hours) that
+could be asynchronously executed during continuous integration (CI),
+through tools such as Travis CI or Circle CI. Including security scans in
+CI also allows developers to identify vulnerabilities quickly,
+before new software contributions are released.
+\end{enumerate}
 
-In future work we would like to see how these vulnerabilities can be leveraged
-to design attacks from containers. Particularly, we want
-to consider web servers and clusters that processes data using containers.
+Describing specific attacks against HPC systems that would exploit
+vulnerabilities in container images is out of the scope of our study. We
+believe that such attacks are likely to exist, although attacking HPC
+systems through containers is challenging due to their relative isolation
+from the host system. First, under the safe assumption that legitimate HPC
+users can be trusted, attackers would have to be remote to the container,
+either in the same network or on a remote network. Two main types of
+attacks can be envisaged in these conditions: network-based attacks,
+exploiting vulnerabilities in network clients installed in the container,
+and data-based attacks, exploiting vulnerabilities through the processing
+of malicious data injected through third-party systems.
+
+Several types of escalation attacks could be envisaged once remote
+attackers gain access to the container, in particular related to (1) using
+the resources allocated to the container for malicious use, such as storing
+data in the file system or using CPU cycles, resulting in denial of service
+for the user running the container, and possibly for other HPC users, and
+(2) attacking a host network service, for instance a scheduler or a file
+system daemon. Exploits in the host kernel to break out of the container
+are always possible but unlikely assuming that the host system is
+maintained by professional system administrators.
+
+\section{Conclusion}
+
+Container images deployed on HPC clusters for scientific data analyses are
+likely to contain hundreds of security vulnerabilities, many of which are
+critical. In the short term, application software developers can address
+this issue by: (1) minifying container images, by using lightweight OS
+distributions and reducing software dependencies, and (2) applying regular
+security updates, which requires using OS distributions with long-term
+support. Longer term, data analysis pipelines would benefit from in-depth
+stability analysis, to ensure that analytical results are not affected by
+security updates.
+
+This conclusion is not an alarming message urging HPC administrators  
+to ban containers from their systems. User-controlled container images are
+just one of many end-user artifacts that could serve as attack vectors,
+and to our knowledge no attack has been described to exploit them. Other,
+more traditional types of attacks targeting user credentials or network
+connections are likely to remain more common.
 

### 2020-09-10 paper.tex
Improved abstract

@@
 \begin{abstract}
-Software containers have become key to the deployment of
-scientific data analyses on high-performance computing (HPC)
-infrastructures, due to their positive impact on the portability, deployment, and
-reproducibility of computations. Container images, however, often contain slightly outdated
-software packages compared to HPC environments maintained by professional
- system administrators, and they often carry more
-software packages than required by analyses, including compilers or unused
-system librairies. As a result, container images are likely to contain
-important amounts of security vulnerability, increasing the attack surface
-for the entire infrastructure. This paper presents a vulnerability analysis
-of container images for scientific data analysis. We analyze container
-images with four vulnerability scanners, focusing on the use case of
-neuroscience data analyses. We quantify the effect of images updates and
-size reduction on the number of vulnerabilities, and conclude with
-recommendations on how to build container images with a reduced amount of
-vulnerabilities.
+Software containers greatly facilitate the deployment of scientific
+data analyses on high-performance computing (HPC) infrastructures, due
+to their positive impact on the portability, deployment, and
+reproducibility of computations. However, container images often
+contain outdated or unnecessary software packages, which increases the
+number of security vulnerabilities present in the images, and widens
+the attack surface for the entire infrastructure. This paper presents a
+vulnerability analysis of container images for scientific data
+analysis. We analyze container images with four vulnerability scanners,
+focusing on the use case of neuroscience data analyses, and quantifying
+the effect of images updates and minification on the number of
+vulnerabilities. We conclude with recommendations on how to build
+container images with a reduced amount of vulnerabilities.
 

### 2020-09-11 paper.tex
Started analysis of discrepancies

@@
 \renewcommand{\labelitemi}{$\textendash$}
-\title{Security Vulnerabilities in Neuroimaging Container Images}
+\title{An Analysis of Security Vulnerabilities in Container Images for Scientific Data Analysis}
 \begin{filecontents*}{resul.csv}
@@
 
-\begin{figure*}
+\begin{table*}
 \begin{tabular}{|c|c|c|c|}
@@
 \label{database}
-\end{figure*}
+\end{table*}
 
@@
 container image scanning tool. We scanned the images with two other tools,
-Clair and Vuls, to evaluate the stability of our results.
+Clair and Vuls, to evaluate the stability of our results. Important
+discrepancies were found between scanners (Fig~\ref{fig:venn}), in particular between Anchore
+and the other two, for which Jaccard coefficients are as low as 0.6, meaning
+that only 60\% of all the detected vulnerabilities are detected by both
+Anchore and the other scanner. Vuls and Clair appear to be in better
+agreement, with a Jaccard coefficient of 0.8.
+
+% where do the discrepancies come from?
+The vulnerabilities detected only by Anchore (region
+\textbf{(1)} in Fig~\ref{fig:venn}) are all in the development package
+(headers) of the C library (\texttt{linux-libc-dev} in Ubuntu).
 
@@
         \includegraphics[width=\columnwidth]{Figures/venn.pdf}
-	\caption{\label{fig:venn} Comparison between image scanners.}
+	\caption{\label{fig:venn} Discrepancies in the vulnerabilities detected
+	by the different scanners. The Jaccard coefficients between the sets of
+	detected vulnerabilities are quite low, showing important discrepancies
+	between the scanners: Jaccard(Anchor, Clair) = 0.59, Jaccard(Anchore, Vuls) =
+	0.59, Jaccard(Vuls, Clair) = 0.82. Two Ubunty 17.04 images weren't included in this comparison as they cannot be scanned by Vuls. \todo{add Centos images}}
 \end{figure}
 
-% Table~\ref{table1} shows the number of vulnerabilities detected in the different images
-% by the four scanners. 
-% \change{Our experiments concluded considerable discrepancies in the results obtained by
-% these scanners. %We higlighted all Centos images in the Table~\ref{table1} since.
-% While comparing scanner results, we exluded two images \texttt{bids/antscorticalthickness:v2.2.0-1} and
-% \texttt{bids/afni\_proc:latest} because Vuls
-% cannot scan these image, hence no results are present to compare.
-% %The reason behind excluding
-% %vulnerability identifiers for Centos. Anchore and Clair use Red Hat Security Advisories (RHSAs)
-% %to report pending patches that need to be applied to specific packages,
-% %whereas Vuls uses Common Vulnerabilities and Exposures (CVE) number to report
-% %vulnerabilities in packages. We exluded other two images because Vuls
-% %can not scan these image, hence no results are present to compare.
 % In most cases,

### 2020-09-12 paper.tex
Cleaned up data files, added explanations to notebook, fixed README

@@
 In this study, we focus on the vulnerability analysis of container images
-used in HPC clusters.  
-Our research questions are the following:
+used in HPC clusters, focussing on the following questions:
 
-\textit{RQ1: What is the current amount of known vulnerabilities in
+\textit{What is the current amount of known vulnerabilities in
 container images deployed on HPC clusters?} Vulnerabilities are possible
@@
 
-\textit{RQ2: Can the amount of vulnerabilities be reduced by updating the images?}  
+\textit{Can the amount of vulnerabilities be reduced by updating the images?}  
 For many reasons related to reproducibility and the life-cycle of research
@@
 
-\textit{RQ3: Can the amount of vulnerabilities be reduced by minifying the images?} 
+\textit{Can the amount of vulnerabilities be reduced by minifying the images?} 
 Container images often include more software packages than required for a
@@
 
+% REGION (7)
 % \textbf{Ubuntu vulnerabilities with status as “Not-affected”:} Vuls reports vulnerabilities that have status
@@
 
+% HOW ABOUT VULS?
 % \textbf{Ubuntu vulnerabilities with status as "Ignored (reached end-of-life)":}
@@
 
+% REGION (4)
 % \textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
@@
 
+% CHECK THAT
 % \textbf{Misses:} Clair and Vuls
@@
 
+% REGION (3)
 % \textbf{Wrong Detections:} 
@@
 
+% REGION (6)
 % \textbf{Epoch bug:} There is a bug in the Anchore scanner due to which some vulnerabilities are 

### 2020-09-12 Scripts/compare_results/anchore_vuls.py

@@ -1,292 +1,0 @@
-import csv
-import sys
-import os
-import re
-
-
-'''
-    For the given path, get the List of all files in the directory tree
-'''
-def getListOfFiles(dirName):
-    listOfFiles=list()
-    for (dirpath, dirnames, filenames) in os.walk(dirName):
-        listOfFiles += [os.path.join(dirpath, file) for file in filenames]
-    return listOfFiles
-
-def default_package(listOfFiles,distro,input_file):
-    with open(input_file,'r') as myfile:
-        lines = myfile.readlines()
-    condition=None
-    cves_default = list()
-    for l in lines:
-            l = l.strip()
-            for elem in listOfFiles:
-                if elem.endswith(l):
-                    with open(elem) as fp:
-                         line =fp.readlines()
-                    for x in line:
-                        if "_linux" in x:
-                            condition=True
-                            break
-                    if condition:
-                        cves_default.append(l)
-                        condition=False
-                    break
-    cves_required=list(set(cves_default))
-    with open('defaulter.csv','w') as out:
-            for entry in cves_required:
-                out.write(entry)
-                out.write("\n")
-
-def find_epoch(listOfFiles,input_file,distro):
-    with open(input_file,'r') as myfile:
-        lines = myfile.readlines()
-        condition=None
-        cves=list()
-        for l in lines:
-            l = l.strip()
-            for elem in listOfFiles:
-                if elem.endswith(l):
-                    with open(elem) as fp:
-                         line =fp.readlines()
-                    for x in line:
-                        if distro+"_" in x:
-                            splitted = x.split('(')
-                            if len(splitted) > 1:
-                                if ":" in splitted[1]:
-                                    condition=True
-                                    break
-                    if condition:
-                       # print("condition is met")
-                        cves.append(l)
-                       # with open('defaulter.csv','a') as out:
-                       #      writer = csv.writer(out)
-                       #      writer.write(l)
-                       #      #out.write(l)
-                        condition=False
-                    break
-    cves_required=list(set(cves))
-    with open('epoch.csv','w') as out:
-        for entry in cves_required:
-            out.write(entry)
-            out.write("\n")
-
-def not_affected(listOfFiles,distro,input_file):
-    with open(input_file,'r') as myfile:
-        lines = myfile.readlines()
-        condition=None
[…]

### 2020-09-12 Scripts/compare_results/anchore_vuls_debian.py

@@ -1,145 +1,0 @@
-import csv
-import sys
-import os
-import re
-import numpy
-import math
-import pandas as pd
-
-
-def default_package(info_file,input_file):
-    with open(input_file,'r') as myfile:
-        lines = myfile.readlines()
-    condition=None
-    cves_default = list()
-    df = pd.read_csv(info_file,delimiter=r"\s+")
-    packages = df.Package
-    cves = df.Vulnerability_ID
-    for package in packages:
-         if "linux-libc-dev" in package:
-             defaulter=package
-             break
-    is_defaulter = df['Package']==defaulter
-    defaulter_info = df[is_defaulter]
-    cves = defaulter_info['Vulnerability_ID'] 
-    unique_cves=set(cves)
-    with open('defaulter.csv','w') as out:
-            for entry in unique_cves:
-                out.write(entry)
-                out.write("\n")
-
-def find_epoch(info_file,input_file):
-    with open(input_file,'r') as myfile:
-        lines = myfile.readlines()
-    condition=None
-    cves=list()  
-    df = pd.read_csv(info_file,delimiter=",",header=None)
-    for l in lines:
-        l = l.strip()
-        for index, row in df.iterrows():
-            if not pd.isnull(row[0]):
-                if row[0].strip().endswith(l):
-                    if not row[0].strip().startswith('TEMP'):
-              #if l in row[0].strip():
-                        if ":" in row[2].strip():
-                          condition=True
-                          break
-        if condition:
-            cves.append(l)
-            condition=False
-    unique_cves=set(cves)
-    with open('epoch.csv','w') as out:
-            for entry in unique_cves:
-                out.write(entry)
-                out.write("\n")
-
-        #print(row['Vulnerability'], row['Package'])
-    #package_version = df.Version
-    #cves = df.Vulnerability
-    #for l in lines:
-    #    l=l.strip()
-    #    if l in cves:
-
-    #for version in package_version:
-    #    if ":" in version:
-    #         defaulter=package
-    #         break
-    #is_defaulter = df['Package']==defaulter
-    #defaulter_info = df[is_defaulter]
-    #cves = defaulter_info['Vulnerability_ID']
-    #unique_cves=set(cves)
-    #with open('defaulter.csv','w') as out:
-    #        for entry in unique_cves:
-    #            out.write(entry)
-    #            out.write("\n")
-
-
[…]

### 2020-09-12 Scripts/compare_results/clair_vuls_debian.py

@@ -1,89 +1,0 @@
-import csv
-import sys
-import os
-import re
-
-
-def find_package(inFile,cve):
-    with open(inFile, 'r') as file:
-      file.readline() # skip the first line
-      rows = [[str(x) for x in line.split('|')[:-1]] for line in file]
-      cols = [list(col) for col in zip(*rows)]
-    package = ""
-    for row in rows:
-        if len(row) > 1:
-           split_cve = row[2].split()
-           if len(split_cve) > 1:
-                 only_cve=split_cve[1]
-                 if only_cve == cve.strip():
-                    package = row[3].strip()
-                    break
-    file.close()
-    return package
-
-def Linux_package(input_file,info_file):
-    with open(input_file,'r') as inp:
-        lines=inp.readlines()
-    cves=list()
-    for l in lines:
-        l=l.strip()
-        package=find_package(info_file,l)
-        if package == "linux":
-           cves.append(l)
-    with open('default.csv','w') as out:
-         for entry in cves:
-                out.write(entry)
-                out.write("\n")
-
-
-def compare(file1,file2):
-    with open(file1, 'r') as t1, open(file2, 'r') as t2:
-        fileone = t1.readlines()
-        filetwo = t2.readlines()
-    
-    with open('V-C.csv', 'w') as f1:
-        for line in filetwo:
-            if line not in fileone:
-                f1.write(line)
-    with open('C-V.csv', 'w') as f2:
-        for line in fileone:
-            if line not in filetwo:
-                f2.write(line)
-    with open('Common.csv', 'w') as f3:
-        for line in fileone:
-            if line in filetwo:
-                f3.write(line)
-
-
-def main():
-    dir_name = "./"
-    test = os.listdir(dir_name)
-    for item in test:
-       if item.endswith(".csv"):
-            os.remove(os.path.join(dir_name, item))
-    file1=sys.argv[1]
-    file2=sys.argv[2]
-    file3=sys.argv[3]
-    file4=sys.argv[4]
-    compare(file1,file2)
-    with open('V-C.csv','r') as fp1:
-        vuls=fp1.readlines()
-    print('V-C ',len(vuls))
-    print('***************************************')
-    with open('C-V.csv','r') as fp2:
-        clair=fp2.readlines()
-    print('C-V ',len(clair))
-    Linux_package('C-V.csv',file3)
-    with open('default.csv','r') as fp3:
-        defaulter=fp3.readlines()
-    print('Default package ',len(defaulter))
[…]

### 2020-09-12 Scripts/compare_results/compare_csv.py

@@ -1,312 +1,0 @@
-import csv
-import sys
-import os
-import re
-
-
-'''
-    For the given path, get the List of all files in the directory tree
-'''
-def getListOfFiles(dirName):
-    listOfFiles=list()
-    for (dirpath, dirnames, filenames) in os.walk(dirName):
-        listOfFiles += [os.path.join(dirpath, file) for file in filenames]
-    return listOfFiles
-
-def default_package(listOfFiles,distro,input_file):
-    with open(input_file,'r') as myfile:
-        lines = myfile.readlines()
-    condition=None
-    cves_default = list()
-    for l in lines:
-            l = l.strip()
-            for elem in listOfFiles:
-                if elem.endswith(l):
-                    with open(elem) as fp:
-                         line =fp.readlines()
-                    for x in line:
-                        if "_linux" in x:
-                            condition=True
-                            break
-                    if condition:
-                        cves_default.append(l)
-                        condition=False
-                    break
-    cves_required=list(set(cves_default))
-    with open('defaulter.csv','w') as out:
-            for entry in cves_required:
-                out.write(entry)
-                out.write("\n")
-
-def find_epoch(inFile,input_file):
-    with open(input_file,'r') as f:
-        lines=f.readlines()
-    new_list=list()
-    for line in lines:
-        new_list.append(line.strip())
-    with open(inFile, 'r') as file:
-      file.readline() # skip the first line
-      rows = [[str(x) for x in line.split('|')[:-1]] for line in file]
-      cols = [list(col) for col in zip(*rows)]
-    epoch_cves=list()
-    for row in rows:
-        if len(row) > 1:
-           if ":" in row[4].strip():
-               cve=row[2].split()[1]
-               if cve in new_list:
-                   epoch_cves.append(cve)
-    required_cves=list(set(epoch_cves))
-    with open('epoch.csv','w') as out:
-        for entry in required_cves:
-            out.write(entry)
-            out.write("\n")
-    file.close()
-
-def find_package(inFile,cve):
-    with open(inFile, 'r') as file:
-      file.readline() # skip the first line
-      rows = [[str(x) for x in line.split('|')[:-1]] for line in file]
-      cols = [list(col) for col in zip(*rows)]
-    package = ""
-    for row in rows:
-        if len(row) > 1:
-           split_cve = row[2].split()
-           if len(split_cve) > 1:
-                 only_cve=split_cve[1]
-                 if only_cve == cve.strip():
-                    package = row[3].strip()
-                    break
-    file.close()
-    return package
-
[…]

### 2020-09-12 Scripts/compare_results/critical_number.py

@@ -1,22 +1,0 @@
-#!/usr/bin/env python
-import csv
-import sys
-import os
-import re
-import pandas as pd
-
-def main():
-    inp=sys.argv[1]
-    #csv.writer(open(r"abx.csv",'w'),delimiter=' ').writerows(filtered)
-    df = pd.read_csv(inp,delimiter=r"\s+")
-    isHigh=df['Severity'] == 'High'
-    filtered=df[isHigh]
-    unique_cves=filtered['Vulnerability_ID'].unique()
-    #filtered = filter(lambda p: 'High' == p[1], df)
-    print(len(unique_cves))
-    #id=df.Vulnerability_ID
-    #print(id)
-
-
-if __name__== "__main__":
-  main()

### 2020-09-12 Scripts/compare_results/test.py

@@ -1,106 +1,0 @@
-#!/usr/bin/env python3
-
-import csv
-import sys
-import os
-import re
-
-def find_epoch(inFile,input_file):
-    with open(input_file,'r') as f:
-        lines=f.readlines()
-    new_list=list()
-    for line in lines:
-        new_list.append(line.strip())
-    with open(inFile, 'r') as file:
-      file.readline() # skip the first line
-      rows = [[str(x) for x in line.split('|')[:-1]] for line in file]
-      cols = [list(col) for col in zip(*rows)]
-    epoch_cves=list()
-    for row in rows:
-        if len(row) > 1:
-           if ":" in row[4].strip():
-               cve=row[2].split()[1]
-               if cve in new_list:
-                   epoch_cves.append(cve)
-    required_cves=list(set(epoch_cves))
-    with open('epoch.csv','w') as out:
-        for entry in required_cves:
-            out.write(entry)
-            out.write("\n")
-    file.close()
-
-def compare2(file1,file2):
-    with open(file1, 'r') as t1, open(file2, 'r') as t2:
-        fileone = t1.readlines()
-        filetwo = t2.readlines()
-    
-    with open('V-C.csv', 'w') as f1:
-        for line in filetwo:
-            if line not in fileone:
-                f1.write(line)
-    with open('C-V.csv', 'w') as f2:
-        for line in fileone:
-            if line not in filetwo:
-                f2.write(line)
-    with open('Common.csv', 'w') as f3:
-        for line in fileone:
-            if line in filetwo:
-                f3.write(line)
-def compare1(file1,file2):
-    with open(file1, 'r') as t1, open(file2, 'r') as t2:
-        fileone = t1.readlines()
-        filetwo = t2.readlines()
-
-    with open('V-A.csv', 'w') as f1:
-        for line in filetwo:
-            if line not in fileone:
-                f1.write(line)
-    with open('A-V.csv', 'w') as f2:
-        for line in fileone:
-            if line not in filetwo:
-                f2.write(line)
-    with open('Common.csv', 'w') as f3:
-        for line in fileone:
-            if line in filetwo:
-                f3.write(line)
-
-
-def main():
-    file1=sys.argv[1]
-    file2=sys.argv[2]
-    count=0
-    #compare(file1,file2)
-    #with open('C-V.csv','r') as fp1:
-    #    anchore = fp1.readlines()
-    #count=len(anchore)
[…]

### 2020-09-12 Scripts/compare_results/vuls_clair.py

@@ -1,240 +1,0 @@
-import csv
-import sys
-import os
-import re
-
-def getListOfFiles(dirName):
-    listOfFiles=list()
-    for (dirpath, dirnames, filenames) in os.walk(dirName):
-        listOfFiles += [os.path.join(dirpath, file) for file in filenames]
-    return listOfFiles
-
-
-
-
-def find_package(inFile,cve):
-    with open(inFile, 'r') as file:
-      file.readline() # skip the first line
-      rows = [[str(x) for x in line.split('|')[:-1]] for line in file]
-      cols = [list(col) for col in zip(*rows)]
-    package = ""
-    for row in rows:
-        if len(row) > 1:
-           split_cve = row[2].split()
-           if len(split_cve) > 1:
-                 only_cve=split_cve[1]
-                 if only_cve == cve.strip():
-                    package = row[3].strip()
-                    break
-    file.close()
-    return package
-
-def get_end_of_life(listOfFiles,distro,input_file):
-    with open(input_file,'r') as myfile:
-        lines = myfile.readlines()
-        condition=None
-        cves=list()
-        for l in lines:
-            l = l.strip()
-            for elem in listOfFiles:
-                if elem.endswith(l):
-                    with open(elem) as fp:
-                         line =fp.readlines()
-                    for x in line:
-                        if distro+"_" in x:
-                            if "reached end-of-life" in x:
-                               condition=True
-                               break
-                    if condition:
-                        cves.append(l)
-                        condition=False
-                    break
-    return list(set(cves))
-
-
-def compare(file1,file2):
-    with open(file1, 'r') as t1, open(file2, 'r') as t2:
-        fileone = t1.readlines()
-        filetwo = t2.readlines()
-    
-    with open('V-C.csv', 'w') as f1:
-        for line in filetwo:
-            if line not in fileone:
-                f1.write(line)
-    with open('C-V.csv', 'w') as f2:
-        for line in fileone:
-            if line not in filetwo:
-                f2.write(line)
-    with open('Common.csv', 'w') as f3:
-        for line in fileone:
-            if line in filetwo:
-                f3.write(line)
-
-def not_affected(listOfFiles,distro,input_file):
-    with open(input_file,'r') as myfile:
-        lines = myfile.readlines()
-        condition=None
-        cves=list()
-        for l in lines:
-            l = l.strip()
-            for elem in listOfFiles:
-                if elem.endswith(l):
-                    with open(elem) as fp:
-                         line =fp.readlines()
-                    for x in line:
[…]

### 2020-09-12 Scripts/graphs/after_minification.py

@@ -1,33 +1,0 @@
-#!/usr/bin/env python3
-
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-d = pd.read_csv(r"../Results_after_minification.csv")
-df=pd.DataFrame(d)
-packages=[]
-before=[]
-after=[]
-for idx,row in df.iterrows():
-    packages.append(row[0])
-    before.append(row[1])
-    after.append(row[2])
-fig=plt.figure()
-#ax = fig.add_subplot()
-plt.plot([],[])
-#print(packages)
-#ax=fig.add_axes([0,0,1,1])
-plt.figure(figsize=(20,10))
-p1=plt.scatter(packages, before, color='r',s=150,marker='o',label='Before Minification')
-p2=plt.scatter(packages, after, color='b',s=150,marker='D',label='After Minification')
-z = np.polyfit(packages, before, 1)
-p = np.poly1d(z)
-plt.plot(packages,p(packages),"r--")
-y = np.polyfit(packages, after, 1)
-p2 = np.poly1d(y)
-plt.plot(packages,p2(packages),"b--")
-plt.xlabel('#Packages Originally', fontsize=15)
-plt.ylabel('#Vulnerabilities',fontsize=15)
-plt.legend(loc='upper left', bbox_to_anchor=(1.00, 1.00), shadow=True, ncol=1,labelspacing=1.2,borderpad=1.0)
-#plt.show()
-plt.savefig('afterMinification.pdf',bbox_inches='tight')

### 2020-09-12 Scripts/graphs/after_update.py

@@ -1,33 +1,0 @@
-#!/usr/bin/env python3
-
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-d = pd.read_csv(r"../Results_after_update2.csv")
-df=pd.DataFrame(d)
-packages=[]
-before=[]
-after=[]
-for idx,row in df.iterrows():
-    packages.append(row[0])
-    before.append(row[1])
-    after.append(row[2])
-fig=plt.figure()
-#ax = fig.add_subplot()
-plt.plot([],[])
-#print(packages)
-#ax=fig.add_axes([0,0,1,1])
-plt.figure(figsize=(20,10))
-p1=plt.scatter(packages, before, color='r',s=150,marker='o',label='Before Update')
-p2=plt.scatter(packages, after, color='b',s=150,marker='D',label='After Update')
-z = np.polyfit(packages, before,1)
-p = np.poly1d(z)
-plt.plot(packages,p(packages),"r--")
-y = np.polyfit(packages, after, 1)
-p3 = np.poly1d(y)
-plt.plot(packages,p3(packages),"b--")
-plt.xlabel('#Packages', fontsize=15)
-plt.ylabel('#Vulnerabilities',fontsize=15)
-plt.legend(loc='upper left', bbox_to_anchor=(1.00, 1.00), shadow=True, ncol=1,labelspacing=1.2,borderpad=1.0)
-#plt.show()
-plt.savefig('afterupdatewithpackage.pdf',bbox_inches='tight')

### 2020-09-12 Scripts/graphs/after_updateANDminification.py

@@ -1,27 +1,0 @@
-#!/usr/bin/env python3
-
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-d = pd.read_csv(r"../Results_after_updateANDminification.csv")
-df=pd.DataFrame(d)
-packages=[]
-vuln=[]
-for idx,row in df.iterrows():
-    packages.append(row[0])
-    vuln.append(row[1])
-fig=plt.figure()
-#ax = fig.add_subplot()
-plt.plot([],[])
-#print(packages)
-#ax=fig.add_axes([0,0,1,1])
-plt.figure(figsize=(20,10))
-p1=plt.scatter(packages, vuln, color='r',s=150,marker='o',label='After Minification and Update')
-z = np.polyfit(packages, vuln,1)
-p = np.poly1d(z)
-plt.plot(packages,p(packages),"r--")
-plt.xlabel('#Packages', fontsize=15)
-plt.ylabel('#Vulnerabilities',fontsize=15)
-plt.legend(loc='upper left', bbox_to_anchor=(1.00, 1.00), shadow=True, ncol=1,labelspacing=1.2,borderpad=1.0)
-#plt.show()
-plt.savefig('bothUPDATEandMinification.pdf',bbox_inches='tight')

### 2020-09-12 Scripts/graphs/barchart.py

@@ -1,56 +1,0 @@
-import numpy as np
-import pandas as pd
-import matplotlib.pyplot as plt
-
-# data to plot
-d = pd.read_csv(r"../../allResults.csv")
-df=pd.DataFrame(d)
-imageID=[]
-before=[]
-afterUpdate=[]
-afterMinification=[]
-afterUpdateANDminify=[]
-for idx,row in df.iterrows():
-    imageID.append(row[0])
-    before.append(row[1])
-    afterUpdate.append(row[2])
-    afterMinification.append(row[3])
-    afterUpdateANDminify.append(row[4])
-
-
-n_groups = len(imageID)
-
-# create plot
-fig, ax = plt.subplots()
-index = np.arange(n_groups)
-bar_width = 0.20
-opacity = 0.7
-
-rects1 = plt.bar(index, before, bar_width,
-alpha=opacity,
-color='b',
-label='Originally')
-
-rects2 = plt.bar(index + bar_width, afterUpdate, bar_width,
-alpha=opacity,
-color='g',
-label='After Update')
-
-rects3 = plt.bar(index + 2*bar_width, afterMinification, bar_width,
-alpha=opacity,
-color='r',
-label='After Minification')
-
-rects4 = plt.bar(index + 3*bar_width, afterUpdateANDminify, bar_width,
-alpha=opacity,
-color='c',
-label='After update and minification')
-
-plt.xlabel('Images', fontsize=15,fontweight='bold')
-plt.ylabel('#Vulnerabilities',fontsize=15, fontweight='bold')
-#plt.title('Vulnerabilities by experiments')
-plt.xticks(index + bar_width, imageID)
-plt.legend()
-
-plt.tight_layout()
-plt.show()

### 2020-09-12 Scripts/graphs/deleted_packages_graph.py

@@ -1,26 +1,0 @@
-#!/usr/bin/env python3
-
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-d = pd.read_csv(r"../Results_with_deleted_number_of_packages.csv")
-df=pd.DataFrame(d)
-packages=[]
-diff=[]
-for idx,row in df.iterrows():
-    packages.append(row[0])
-    diff.append(row[1])
-fig=plt.figure()
-#ax = fig.add_subplot()
-plt.plot([],[])
-#print(packages)
-#ax=fig.add_axes([0,0,1,1])
-plt.figure(figsize=(20,10))
-p1=plt.scatter(packages, diff, color='r',s=150,marker='o',label=False)
-z = np.polyfit(packages, diff,1)
-p = np.poly1d(z)
-plt.plot(packages,p(packages),"r--")
-plt.xlabel('#Deleted Packages', fontsize=15,fontweight='bold')
-plt.ylabel('#Reduced Vulnerabilities',fontsize=15,fontweight='bold')
-#plt.legend(loc='upper center', bbox_to_anchor=(1.00, 1.00), shadow=True, ncol=2,labelspacing=1.2,borderpad=1.0,prop={'size': 14})
-plt.savefig('graphwithdeletedpackages.pdf',bbox_inches='tight')

### 2020-09-12 Scripts/graphs/drawVenn.py

@@ -1,22 +1,0 @@
-from matplotlib import pyplot as plt
-import numpy as np
-from matplotlib_venn import venn3, venn3_circles
- 
-# Make a Basic Venn
-v = venn3(subsets=(1, 1, 1, 1, 1, 1, 1), set_labels = ('Anchore', 'Clair', 'Vuls'))
- 
-# Custom it
-v.get_label_by_id('100').set_text('4453')
-v.get_label_by_id('010').set_text('699')
-v.get_label_by_id('110').set_text('1678')
-v.get_label_by_id('001').set_text('536')
-v.get_label_by_id('101').set_text('657')
-v.get_label_by_id('011').set_text('2220')
-v.get_label_by_id('111').set_text('11978')
-for text in v.set_labels:
-    text.set_fontsize(18)
-for text in v.subset_labels:
-    text.set_fontsize(15)
-# Show it
-plt.savefig('venn.pdf',dpi=2000)
-#plt.show()

### 2020-09-12 Scripts/graphs/script.py

@@ -1,67 +1,0 @@
-#!/usr/bin/env python3
-
-# Import the necessary libraries
-import matplotlib.pyplot as plt
-import seaborn as sns
-import pandas as pd
-import numpy as np
-import scipy.stats as st
-# Load the data
-d = pd.read_csv(r"../../train3.csv")
-d.head()
-df=pd.DataFrame(d)
-plt.figure(figsize=(200,20))
-plt.rcParams["axes.labelweight"] = "bold"
-b, a = np.polyfit(df['Packages'], df['Vulnerabilities'], 1)
-xtest = np.linspace(df['Packages'].min(),df['Vulnerabilities'].max(),10)
-colors = {'ubuntu:14.04' : '#2E37FE', 'ubuntu:16.04' : '#CAE1FF', 'ubuntu:17.04':'#5190ED','ubuntu:17.10':'#000085','ubuntu:18.04' : '#98F5FF','centos 6':'#800080','centos 7':'#b19cd9',
-        'alpine:3.7.1':'#3CB371','alpine:3.8.4':'#00ff00','alpine:3.9.0':'#006400','debian:8':'#ffa500'}
-markers = {"ubuntu:14.04": "o", "ubuntu:16.04": "o",'ubuntu:17.04':'o','ubuntu:17.10':'o','ubuntu:18.04' : 'o','centos 6':'o','centos 7':'o',
-        "alpine:3.7.1":'o','alpine:3.8.4':"o","alpine:3.9.0":"o","debian:8":"o"}
-marker_order=["ubuntu:14.04", "ubuntu:16.04",'ubuntu:17.04','ubuntu:17.10','ubuntu:18.04','centos 6','centos 7',
-        "alpine:3.7.1",'alpine:3.8.4',"alpine:3.9.0","debian:8"]
-with sns.plotting_context(rc={"legend.fontsize":25,"legend.markersize":18,"axes.titlesize":20,"font.weight":'heavy',"legend.labelspacing":20}):
-  p1=sns.relplot(x="Packages",y="Vulnerabilities",hue="OS distribution",hue_order=marker_order,size="CRITICAL Vulnerabilities",sizes=(300,1450),data = df,palette=colors,markers=markers,style="OS distribution",height=10, aspect=2)
-p1.set(xlabel='#Packages', ylabel='#Vulnerabilities')
-p1.set(xticks=[i for i in range(0, max(df['Packages']) + 100, 50)],
[…]

### 2020-09-12 Scripts/graphs/script.sh

@@ -1,103 +1,0 @@
-#!/bin/bash
-
-#apt-get update
-#apt-get install -y debtree
-#apt install aptitude -y
-#apt list --installed | awk -F/ '{print $1}' | tail -n +2 > all-packages.csv
-#aptitude -F %p search --disable-columns '~Rprovides:~i ~v' >> virtual.csv
-#aptitude -F %p search --disable-columns ~pimportant >> required.csv
-#aptitude -F %p search --disable-columns ~prequired >> required.csv
-cat required.csv | sort | uniq >> uniq_required-0.csv
-touch keep_virtual.csv
-IFS=$'\n'
-number=0
-
-###function####
-get_dependencies() {
-for k in $(cat $1)
-do
-(for i in $(debtree --show-installed --no-skip --show-all $k | tail -n +4); do if [[ $i == *"->"* ]]; then     c=$(echo $i | awk '{print $1}' | sed 's/"//g');     if [[ $c == *:* ]];     then       echo echo $c | awk -F: '{print $2}';     else       echo $c;     fi; else if [[ $i == *";"* ]]; then    echo $i |sed -e 's/^[[:space:]]*//' |sed 's/"//g'|head -n1 | awk '{print $1}';elif [[ $i == *"label = "* ]]; then str=$(echo $i | awk '{print $3}'); prefix='"<'; suffix='>';foo=${str#"$prefix"};foo=${foo%"$suffix"}; echo "${foo}" >> $2; fi; fi; done; ) | sort | uniq >> $3
-done
-cat $3 | sort | uniq >> $4
-cat $2 | sort | uniq >> $5
-comm -13 <(sort $4) <(sort $5) >> $6
-}
-
-#####function#####
-get_package() {
-for x in $(cat $1)
-do
-echo "getting package of virtual package "$x
-aptitude -F %p search --disable-columns '~P'$x' ~i' >> $2
-done
-}
-
-while [ $(cat "uniq_required-${number}.csv" | wc --lines) != 0 ]
-do
-echo "************************************************ROUND ${number}***********************************************************************"
-uniq_required="uniq_required-${number}.csv"
-label="label-${number}.csv"
-total_p="total_p-${number}.csv"
-total_packages="total_packages-${number}.csv"
-temp_label="temp_label-${number}.csv"
-uniq_label="uniq_label-${number}.csv"
-installed_p="installed-${number}.csv"
-virtual_p="virtual_p-${number}.csv"
[…]

### 2020-09-12 Scripts/graphs/test.py

@@ -1,68 +1,0 @@
-#from matplotlib import pyplot as plt
-#import pandas as pd
-#import seaborn as sns
-#import numpy as np
-#
-#d = {'x-axis':[71,35,61,253,145,157,218,241,291,277,159,167,171,188,240,254,258,269,277,288,298,347,349,353,360,380,441,443,506,528,530,537,538,566,600,762,815,889], 
-#        'y-axis': [5,5,15,79,75,641,172,867,289,67,75,112,46,150,70,70,897,391,671,54,353,275,191,189,432,526,591,516,507,838,874,934,934,1086,698,913,1717,1482],
-#        'text':['p1','p2','p3','p4','p5','p6','p7','p8','p9','p10','p11','p12','p13','p14','p15','p16','p17','p18','p19','p20','p21','p22','p23','p24','p25','p26','p27','p28','p29','p30','p31','p32','p33','p34','p35','p36','p37','p38'], 
-#        'size':[4,4,3,54,22,162,3,44,9,0,22,4,12,67,32,32,46,6,159,17,13,3,4,3,11,79,15,12,5,19,22,20,20,34,18,27,50,35],'hue':['good','bad','average','poor','good','bad','average','poor','good','bad','average','poor','poor','poor','poor','poor','poor','poor','poor','good','bad','good','bad','good','bad','good','bad','good','bad','good','bad','average','average','average','average','average','average','average']}
-#df = pd.DataFrame(d)
-#b, a = np.polyfit(df['x-axis'], df['y-axis'], 1)
-#xtest = np.linspace(df['x-axis'].min(),df['x-axis'].max(),10)
-#with sns.plotting_context(rc={"legend.fontsize":25,"legend.markersize":18,"axes.titlesize":20,"font.weight":'heavy',"legend.labelspacing":20}):
-#  p1 = sns.relplot(x='x-axis', y='y-axis',hue='hue',size='size',sizes=(300,1450),data=df,height=10, aspect=2 )
-#ax = p1.axes[0,0]
-##ax.plot(xtest, a + b* xtest, '--')
-#for idx,row in df.iterrows():
-#    x = row[0]
-#    y = row[1]
-#    text = row[2]
-#    ax.text(x+.05,y,text, horizontalalignment='left')
-##z = np.polyfit(df['x-axis'], df['y-axis'], 1)
-##p = np.poly1d(z)
-##plt.plot(df['x-axis'],p(df['x-axis']),"k--")
[…]

### 2020-09-12 Scripts/graphs/updateandminification.py

@@ -1,39 +1,0 @@
-#!/usr/bin/env python3
-
-import matplotlib.pyplot as plt
-import pandas as pd
-import numpy as np
-d = pd.read_csv(r"../updateandminification.csv")
-df=pd.DataFrame(d)
-packages=[]
-before=[]
-update=[]
-delete=[]
-for idx,row in df.iterrows():
-    packages.append(row[0])
-    before.append(row[1])
-    update.append(row[2])
-    delete.append(row[3])
-fig=plt.figure()
-#ax = fig.add_subplot()
-plt.plot([],[])
-#print(packages)
-#ax=fig.add_axes([0,0,1,1])
-plt.figure(figsize=(20,10))
-p1=plt.scatter(packages, before, color='r',s=150,marker='o',label='Before')
-p2=plt.scatter(packages, update, color='b',s=150,marker='D',label='After Update')
-p3=plt.scatter(packages,delete, color='g',s=150,marker='*',label='After Minification')
-z = np.polyfit(packages, before,1)
-p = np.poly1d(z)
-plt.plot(packages,p(packages),"r--")
-y = np.polyfit(packages, update, 1)
-p4 = np.poly1d(y)
-plt.plot(packages,p4(packages),"b--")
-x = np.polyfit(packages, delete,1)
-p5 = np.poly1d(x)
-plt.plot(packages,p5(packages),"g--")
-plt.xlabel('#Packages', fontsize=15)
-plt.ylabel('#Vulnerabilities',fontsize=15)
-plt.legend(loc='upper left', bbox_to_anchor=(1.00, 1.00), shadow=True, ncol=1,labelspacing=1.2,borderpad=1.0)
-#plt.show()
-plt.savefig('updateandminification.pdf',bbox_inches='tight')

### 2020-09-12 Scripts/graphs/updation.py

@@ -1,84 +1,0 @@
-#!/usr/bin/env python3
-
-# Import the necessary libraries
-import matplotlib.pyplot as plt
-import seaborn as sns
-import pandas as pd
-import numpy as np
-import scipy.stats as st
-# Load the data
-d = pd.read_csv(r"../../train3.csv")
-d.head()
-df=pd.DataFrame(d)
-plt.figure(figsize=(200,20))
-plt.rcParams["axes.labelweight"] = "bold"
-plt.rcParams.update({'font.size': 15})
-colors = {'ubuntu:14.04' : '#2E37FE', 'ubuntu:16.04' : '#CAE1FF', 'ubuntu:17.04':'#5190ED','ubuntu:17.10':'#000085','ubuntu:18.04' : '#98F5FF','centos 6':'#800080','centos 7':'#b19cd9',
-        'alpine:3.7.1':'#3CB371','alpine:3.8.4':'#00ff00','alpine:3.9.0':'#006400','debian:8':'#ffa500'}
-markers = {"ubuntu:14.04": "o", "ubuntu:16.04": "o",'ubuntu:17.04':'o','ubuntu:17.10':'o','ubuntu:18.04' : 'o','centos 6':'o','centos 7':'o',
-        "alpine:3.7.1":'o','alpine:3.8.4':"o","alpine:3.9.0":"o","debian:8":"o"}
-p1=sns.relplot(x="Packages",y="Vulnerabilities",hue="OS distribution",size="CRITICAL Vulnerabilities",sizes=(300,1450),data = df,palette=colors,markers=markers,style="OS distribution",height=10, aspect=2,legend=False)
-p1.set(xlabel='#Packages', ylabel='#Vulnerabilities')
-p1.set(xticks=[i for i in range(0, max(df['Packages']) + 100, 50)],
-       yticks=[i for i in range(0, max(df['Vulnerabilities']) + 20, 250)])
-ax = p1.axes[0,0]
-#leg = p1._legend
-#p1.legend(loc='center left', bbox_to_anchor=(1.25, 0.5), ncol=1)
-#leg.set_bbox_to_anchor([1.01, 0.04])
-#leg._loc = 4
-#leg.texts[12].set_text("CRITICAL \nVulnerabilities")
-#leg.remove()
-#z = np.polyfit(df['Packages'], df['Vulnerabilities'], 1)
-#p = np.poly1d(z)
-#plt.plot(df['Packages'],p(df['Packages']),"k--")
-
[…]

### 2020-09-12 Scripts/graphs/venn.py

@@ -1,87 +1,0 @@
-#!/usr/bin/env python3
-import csv
-import sys
-import os
-import re
-
-
-def compare(file1,file2,file3):
-    with open(file1, 'r') as a, open(file2, 'r') as c, open(file3,'r') as v:
-        anchore = a.readlines()
-        clair = c.readlines()
-        vuls= v.readlines()
-    with open('A+C+V.csv', 'w') as f1:
-        for line in anchore:
-            if line in clair:
-                if line in vuls:
-                     f1.write(line)
-    with open('A+C+V.csv','r') as f2:
-        common=f2.readlines()
-    with open('A+C.csv', 'w') as f3:
-        for line in anchore:
-               if line in clair:
-                   if line not in vuls:
-                       f3.write(line)
-    with open('A+C.csv','r') as f4:
-        ac=f4.readlines()
-    with open('A.csv','w') as f5:
-        for line in anchore:
-            if line not in clair:
-                if line not in vuls:
-                    f5.write(line)
-    with open('A.csv','r') as f6:
-        a=f6.readlines()
-    
-    with open('C.csv','w') as f7:
-        for line in clair:
-            if line not in anchore:
-                if line not in vuls:
-                    f7.write(line)
-    with open('C.csv','r') as f8:
-        c=f8.readlines()
-
-
-    with open('V.csv','w') as f9:
-        for line in vuls:
-            if line not in clair:
-                if line not in anchore:
-                    f9.write(line)
-    with open('V.csv','r') as f:
-        v=f.readlines()
-
-
-
-    with open('A+V.csv', 'w') as f10:
-        for line in anchore:
-               if line in vuls:
-                   if line not in clair:
-                       f10.write(line)
-    with open('A+V.csv','r') as f11:
-        av=f11.readlines()
-
-    with open('C+V.csv', 'w') as f12:
-        for line in clair:
-               if line in vuls:
-                   if line not in anchore:
-                       f12.write(line)
-    with open('C+V.csv','r') as f13:
-        cv=f13.readlines()
-
-    print("A+C+V ",len(common))
-    print("Anchore",len(a))
-    print("Clair",len(c))
-    print("Vuls",len(v))
-
-    print("A+C",len(ac))
-    print("A+V",len(av))
-    print("C+V",len(cv))
-    
-
-def main():
-    file1=sys.argv[1]
-    file2=sys.argv[2]
-    file3=sys.argv[3]
-    compare(file1,file2,file3)
-
-if __name__== "__main__":
-  main()

### 2020-09-12 Scripts/graphs/venn_for_centos.py

@@ -1,50 +1,0 @@
-#!/usr/bin/env python3
-import csv
-import sys
-import os
-import re
-
-
-def compare(file1,file2):
-    with open(file1, 'r') as a, open(file2, 'r') as c:
-        anchore = a.readlines()
-        clair = c.readlines()
-    with open('A+C.csv', 'w') as f3:
-        for line in anchore:
-               if line in clair:
-                       f3.write(line)
-    with open('A+C.csv','r') as f4:
-        ac=f4.readlines()
-    with open('A.csv','w') as f5:
-        for line in anchore:
-            if line not in clair:
-                    f5.write(line)
-    with open('A.csv','r') as f6:
-        a=f6.readlines()
-    
-    with open('C.csv','w') as f7:
-        for line in clair:
-            if line not in anchore:
-                    f7.write(line)
-    with open('C.csv','r') as f8:
-        c=f8.readlines()
-
-
-    print("Anchore",len(a))
-    print("Clair",len(c))
-    print("A+C",len(ac))
-    
-
-def main():
-#    dir_name = "./"
-#    test = os.listdir(dir_name)
-#    for item in test:
-#       if item.endswith(".csv"):
-#            os.remove(os.path.join(dir_name, item))
-#
-    file1=sys.argv[1]
-    file2=sys.argv[2]
-    compare(file1,file2)
-
-if __name__== "__main__":
-  main()

### 2020-09-14 paper.tex
Edited abstract and intro

@@
 
-\author[1]{Bhupinder Kaur}
-\author[1]{Mathieu Dugr\'e}
-\author[1]{Aiman Hanna}
-\author[1]{Tristan Glatard}
+\author{Bhupinder Kaur}
+\author{Mathieu Dugr\'e}
+\author{Aiman Hanna}
+\author{Tristan Glatard}
 
-\affil[1]{Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada}
+\affil{Department of Computer Science and Software Engineering, Concordia University, Montreal, Canada}
 
@@
 \begin{abstract}
-Software containers greatly facilitate the deployment of scientific
-data analyses on high-performance computing (HPC) infrastructures, due
-to their positive impact on the portability, deployment, and
-reproducibility of computations. However, container images often
-contain outdated or unnecessary software packages, which increases the
-number of security vulnerabilities present in the images, and widens
-the attack surface for the entire infrastructure. This paper presents a
-vulnerability analysis of container images for scientific data
-analysis. We analyze container images with four vulnerability scanners,
-focusing on the use case of neuroscience data analyses, and quantifying
-the effect of images updates and minification on the number of
-vulnerabilities. We conclude with recommendations on how to build
-container images with a reduced amount of vulnerabilities.
+Software containers greatly facilitate the deployment and reproducibility
+of scientific data analyses on high-performance computing clusters
+(HPC). However, container images often contain outdated or unnecessary
+software packages, which increases the number of security vulnerabilities
+in the images and widens the attack surface of the infrastructure. This
+paper presents a vulnerability analysis of container images for scientific
+data analysis. We analyze container images with four vulnerability
+scanners, focusing on the use case of neuroscience data analyses, and
+quantifying the effect of images updates and minification on the number of
+vulnerabilities. We find that container images used for data analysis
+contain hundreds of vulnerabilities, that software updates remove about two
+thirds of these vulnerabilities, and that removing unused packages is also
+effective. We conclude with recommendations on how to build container
+images with a reduced amount of vulnerabilities.
 
@@
 
-% Containers are popular on HPC, in particular Singularity
 Software containers have emerged has an efficient solution to deploy
-scientific data analyses on High Performance Computing (HPC) clusters, due
-to their portability, ease of use, and limited overhead. The
+scientific data analyses on HPC clusters, due
+to their portability, ease of use, and limited overhead. On HPC systems, the
 Singularity~\cite{kurtzer2017singularity} framework is often preferred to
-Docker\footnote{\url{http://docker.com}} for HPC deployments, due to its
-secure handling of multi-user environments, and its convenient support for
+\href{http://docker.com}{Docker} because of its
+secure handling of multi-user environments and convenient support for
 Docker images. Singularity is now available in dozens of HPC
-clusters around the globe, and used routinely for Big Data analyses.
+clusters around the world and routinely used for Big Data analysis.
 
-% Containers are meant to isolate applications from the host, but security
-% remains an issue
-Leveraging core features of the Linux kernel such as namespaces, control
-groups and chroot, containers isolate processes from the host computer,  
-and control the memory, CPU, network and file-system resources assigned to
-them. Nevertheless, containers still share the kernel, mounted file systems
-and some devices with the host, which raises security
-issues~\cite{martin2018docker, sultan2019container, combe2016docker} and
-opens the door to privilege escalation, denial of service, information
-leak and other types of attacks~\cite{gantikow2016providing}.
+Taking advantage of core Linux kernel features such as namespaces, control
+groups and chroot, containers isolate processes from the host computer, and
+control the memory, CPU, network and file-system resources assigned to
+them. However, containers still share the kernel, mounted file systems and
+some devices with the host, which raises security
+concerns~\cite{martin2018docker, sultan2019container, combe2016docker} and
+opens the door to privilege escalation, denial of service, information leak
+and other types of attacks~\cite{gantikow2016providing}.
 
-% Container images, our study
-Container images often include nearly complete operating-system
-distributions in addition to the data analysis software and its required
-dependencies. Images are rarely updated, as they are often built once for
-the entire duration of an analysis, to avoid results perturbations due to
-software updates~\cite{gronenschild2012effects,
-glatard2015reproducibility}. Images also commonly include more dependencies
-than required by a specific analysis, to facilitate reusability across
-experiments. As a result, it has been shown that over 30\% of official
-images in DockerHub contain high priority security
-vulnerabilities~\cite{gummaraju2015over}, that both official and community
-images contain more than 180 vulnerabilities on average~\cite{Shu2017}, and
-that vulnerabilities are often due to outdated
-packages~\cite{zerouali2019relation}.
+Container images typically include full operating system distributions in
+addition to data analysis software and their dependencies. They are rarely
+updated because there is concern that software updates will interfere with
+the results~\cite{gronenschild2012effects, glatard2015reproducibility}.
+Images also typically include more dependencies than required, to make them
+easier to reuse between experiments. As a result, over 30\% of official
+images in DockerHub have been shown to contain high priority security
+vulnerabilities~\cite{gummaraju2015over}, images on average contain over
+180 vulnerabilities~\cite{Shu2017}, and vulnerabilities are often caused by
+outdated packages~\cite{zerouali2019relation}.
 
-In this study, we focus on the vulnerability analysis of container images
-used in HPC clusters, focussing on the following questions:
+In this study, we focus on the vulnerabilities present in container images
+deployed on HPC clusters for scientific data analysis, and we answer the
+following questions:
 
-\textit{What is the current amount of known vulnerabilities in
+\textit{What is the current amount of vulnerabilities in
 container images deployed on HPC clusters?} Vulnerabilities are possible
-attack vectors that may seriously compromise the security of HPC clusters
-and the integrity of user data. We report vulnerability analyses produced
-by four popular image scanning tools, Anchore, Vuls, Clair, and Stools.
+attack vectors that can seriously compromise the security of HPC clusters
+and the integrity of user data. We report vulnerability scans produced
+by four popular image scanning tools: Anchore, Vuls, Clair, and Stools.
 
 \textit{Can the amount of vulnerabilities be reduced by updating the images?}  
-For many reasons related to reproducibility and the life-cycle of research
+For many reasons related to reproducibility and lifecycle of research
 projects, container images deployed on HPC clusters often include outdated
-software. We report on the effect of software updates on the vulnerability
-analysis of RQ1.
+software. We report on the effect of software updates on the amount of
+vulnerabilities found in images.
 
-\textit{Can the amount of vulnerabilities be reduced by minifying the images?} 
-Container images often include more software packages than required for a
-typical analysis. We report on the impact of this additional software on
+\textit{Can the amount of vulnerabilities be reduced by minifying images?} 
+Container images often include more software packages than necessary for 
+typical analysis. We report on the impact of unused software packages on
 the presence of vulnerabilities.
 
-We answer these questions by taking the particular example of neuroimaging,
-a domain that has entered the Big Data era as many other
-ones~\cite{van2014human}. The next section describes the materials and
-tools used in the experiments, including container images and image
-scanners. We then describe our image update and minification methodology to
-reduce vulnerabilities. Results present the detected vulnerabilities in
-container images, explain observed discrepancies between scanners, and
-report on the efficiency of image update and size reduction. As a
-conclusion, we provide a set of image creation guidelines for a more secure
-deployment on HPC clusters.
-
-% We focus on the analysis of container images
-% present in BIDS apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques}, two containerized
-% application frameworks commonly used in neuroimaging.
+We answer these questions through the example of neuroimaging, a field that
+has entered the era of Big Data as many others~\cite{van2014human}. The
+following section describes the materials and tools used in the
+experiments, including container images and image scanners. We then
+describe our methodology for updating and minifying images to reduce
+vulnerabilities. The results present the vulnerabilities detected in container
+images, quantify the effectiveness of updating and minifying images, and
+explain the differences observed between scanners. In conclusion, we
+provide a set of image creation guidelines for a more secure deployment of
+containers on HPC clusters.
 
@@
 	between the scanners: Jaccard(Anchor, Clair) = 0.59, Jaccard(Anchore, Vuls) =
-	0.59, Jaccard(Vuls, Clair) = 0.82. Two Ubunty 17.04 images weren't included in this comparison as they cannot be scanned by Vuls. \todo{add Centos images}}
+	0.59, Jaccard(Vuls, Clair) = 0.82. Two Ubuntu 17.04 images weren't included in this comparison as they cannot be scanned by Vuls. \todo{add Centos images}}
 \end{figure}

### 2020-09-14 paper.tex
Edits in paper and bibliography

@@
 
-Container images typically include full operating system distributions in
+Container images typically include full operating system (OS) distributions in
 addition to data analysis software and their dependencies. They are rarely
@@
 in container images and examine the effect of different
-manipulations on these images, we used container
+manipulations on those images, we used container
 images from two popular application frameworks, as well as
-four of the main image scanners.
+four of the major image scanners.
 
@@
 totalling
-44 container images.
-Out of these 44 images, 26 were obtained from BIDS apps 
-and 18 from Boutiques. At the time of the study, BIDS apps had 27 images,
+44 container images: 26 from BIDS apps, and 18 from Boutiques. At the time of the study, BIDS apps had 27 images,
 out of which one wasn't available on DockerHub. Boutiques had 49 images,
@@
 from BIDS apps were Docker images, whereas Boutiques contained 18 Docker images
-and 6 Singularity images. \tristan{check the numbers, we have 38 images in the results}
+and 6 Singularity images. \tristan{Check the numbers: that makes 24 Boutiques images, not 18.}
 
@@
 
-We used four popular image scanners, namely Anchore~\cite{github_2019},
-Vuls~\cite{future-architect_2019}, Clair~\cite{arminc_2019} and
-Singularity Container Tools --- Stools~\cite{stools}. Anchore, Vuls and Clair support Docker
-images while Stools support Singularity.
+We used four popular image scanners, namely Anchore,
+Vuls and Clair, supporting Docker, and
+Singularity Container Tools --- Stools~\cite{stools}, supporting Singularity.
 
-Anchore is an end-to-end, open-source container security platform. It
-analyzes container images and lists OS
-packages, non-OS packages (Python, Java, Gem, and Npm), and files.
+\href{https://github.com/anchore/anchore-engine}{Anchore} is an end-to-end, open-source container security platform. It
+analyzes container images and lists vulnerable OS
+packages, non-OS packages (Python, Java, Gem, and npm), and files.
 In our experiments, we use Anchore Engine version 0.5.0 through Docker image \texttt{anchore/anchore-engine:v0.5.0}, and
@@
 \caption{Vulnerability databases used by scanners for different OS distributions}
-\label{database}
+\label{table:databases}
 \end{table*}
 
-Vuls is an open-source vulnerability scanner for Linux and FreeBSD. It
+\href{https://github.com/future-architect/vuls}{Vuls} is an open-source vulnerability scanner for Linux and FreeBSD. It
 offers both static and dynamic scanning, and both local and remote
@@
 
-Clair (\url{https://github.com/quay/clair}) is an open-source and extensible
-vulnerability scanner for Docker and appc container images, developed by
-CoreOS (now Container Linux), a Linux distribution to deploy container
-clusters. Clair has a client-server architecture, in which the server
-scans Docker images layer by layer and maintains a database of vulnerabilities. We used Clair through Clair-scanner
-(\url{https://github.com/arminc/clair-scanner}), a tool to facilitate the testing
-of container images against a local Clair server. 
+\href{https://github.com/quay/clair}{Clair} is an open-source and
+extensible vulnerability scanner for Docker and appc container images,
+developed by CoreOS (now Container Linux), a Linux distribution to deploy
+container clusters. Clair has a client-server architecture, in which the
+server scans Docker images layer by layer and maintains a database of
+vulnerabilities. We used Clair through
+\href{https://github.com/arminc/clair-scanner}{Clair-scanner}, a tool to
+facilitate the testing of container images against a local Clair server. 
 % Clair-scanner scans the image,
@@
 
-Singularity Tools (Stools)
+\href{https://github.com/singularityhub/stools}{Singularity Tools} (Stools)
 are an extension of Clair for Singularity images. Stools
@@
 
-Scanners refer to two types of vulnerability databases. The first one is
-the Open Vulnerability and Assessment Language (OVAL) database, an
-international open standard that supports various OS distributions
-including Ubuntu, Debian and Centos but not Alpine. The second one are vulnerability
-databases from specific OS distributions, such as Alpine-SecDB, Debian
-Security Bug Tracker, Ubuntu CVE Tracker, or Red Hat Security Data. OS
-distributions often assign a status to each vulnerability, to keep track of
-required and available security fixes in different versions of the
-distribution. Figure~\ref{database} shows the vulnerabilities databases used by each scanner 
-by OS distribution. Vuls uses OVAL databases for all distributions except Alpine, since Alpine is not available in OVAL. On the contrary, 
-Clair exclusively refers to distribution-specific databases. Anchore uses OVAL only for CentOS \tristan{why?}. It is also worth noting that there is
-no vulnerability data for Ubuntu 17.04 and 17.10 distributions in the OVAL database, since these distributions have reached end of life, meaning that images
-with these distributions cannot be scanned with Vuls \tristan{why doesn't vuls use Ubuntu CVE tracker?}.
+Table~\ref{table:databases} shows the vulnerabilities databases used by
+each scanner by OS distribution. Scanners refer to two types of
+vulnerability databases. The first one is the Open Vulnerability and
+Assessment Language (OVAL) database, an international open standard that
+supports various OS distributions including Ubuntu, Debian and Centos but
+not Alpine. The second one are vulnerability databases from specific OS
+distributions, such as Alpine-SecDB, Debian Security Bug Tracker, Ubuntu
+CVE Tracker, or Red Hat Security Data. OS distributions often assign a
+status to each vulnerability, to keep track of required and available
+security fixes in different versions of the distribution. Vuls uses OVAL
+databases for all distributions except Alpine, since Alpine is not
+available in OVAL. On the contrary, Clair exclusively refers to
+distribution-specific databases. Anchore uses OVAL only for CentOS
+\tristan{any idea why?}. It is also worth noting that there is no vulnerability data
+for Ubuntu 17.04 and 17.10 distributions in the OVAL database, since these
+distributions have reached end of life, meaning that images with these
+distributions cannot be scanned with Vuls \tristan{why doesn't vuls use
+Ubuntu CVE tracker?}.
 \tristan{In Vuls, what happens when 2 databases are used?}
@@
 metadata of vulnerabilities. Apart from this, like Anchore, Vuls also
-refers NVD database for getting vulnerability metadata \tristan{same
-question}. \tristan{why is it not in the table?}.
+refers NVD database for getting vulnerability metadata \tristan{why is NVD not in the table?}.
 
-For Centos images, Anchore and Clair gives scanning results using Red Hat
-Security Advisory (RHSA) identifiers for Centos images, whereas Vuls uses
-CVE identifiers. RHSA identifiers specifies security patches that are
-pending to apply and CVE identifiers specifies vulnerabilities that exist
-in the system. We mapped RHSA identifiers to corresponding CVE identifiers,
-to allow for a comparison between scanners.
+For CentOS images, Anchore and Clair give scanning results using Red Hat
+Security Advisory (RHSA) identifiers, whereas Vuls uses the Common
+Vulnerabilities and Exposures (CVE) identifiers used in OVAL. We mapped
+RHSA identifiers to corresponding CVE identifiers, to allow for a
+comparison between scanners.
 
-Different vulnerabilities may be
-reported by scanners if scanning experiments take place on different dates.
-To avoid such discrepancies, we froze the vulnerability
-databases used by these scanners as of 2019-09-25, when we initiated our
-experiments.\tristan{this contradicts the date used for Clair}
+Different vulnerabilities may be reported by scanners if scanning
+experiments take place on different dates. To avoid such discrepancies, we
+froze the vulnerability databases used by these scanners as of 2019-09-25
+\tristan{this contradicts the date mentioned in the paragraph on Clair}.
 
@@
 
-%We revert to image minimization to reduce the number of vulnerabilities without affecting results reproducibility.
-%An interesting choice to do so would be to use 
-%Neurodocker~\cite{neurodocker}.
-%This tool traces and deletes unnecessary files.
-%However, it does not affect the number of installed packages.
-%Since image scanners report vulnerabilities according to the installed
-%packages. Therefore, after
-%minimization the same number of vulnerabilities is still reported.
-%Consequently, we need to reduce the number of installed packages
-%in the images by deleting unnecessary packages. For that, it is required to figure
-%out which packages we need for the pipeline to function properly.
-
-\todo{mention neuro docker}
-
 A second approach to reduce the number of vulnerabilities in the images is
@@
 analysis. We used the open-source \reprozip tool~\cite{rampin2016reprozip}
-to capture the list of packages used by an analysis. For this purpose,
-\reprozip first captures the list of files involved in the analysis,
-through system call interception, then retrieves the list of associated
-software packages, by querying the package manager. We extend this list
-with a passlist of packages required for the system to function
-\tristan{can you give an example?}, and with all the dependencies of the
-required packages, retrieved using Debtree~\cite{debtree} (Repoquery
-(\url{https://linux.die.net/man/1/repoquery}) could be used in RPM-based
-distributions instead). Our minification script, available
-\href{https://github.com/big-data-lab-team/container-vulnerabilities-paper/tree/master/Scripts/minification}{here},
-installs \reprozip in the image to minify, runs an analysis to collect a
-\reprozip trace, and finally deletes all unnecessary packages.
+to capture the list of packages used by an analysis. \reprozip first
+captures the list of files involved in the analysis, through system call
+interception, then retrieves the list of associated software packages, by
+querying the package manager. We extend this list with a passlist of
+packages required for the system to function \tristan{can you give an
+example?}, and with all the dependencies of the required packages,
+retrieved using
+\href{http://manpages.ubuntu.com/manpages/xenial/man1/debtree.1.html}{Debtree}.
+\href{https://linux.die.net/man/1/repoquery}{Repoquery} could be used in
+RPM-based distributions instead. Our minification script, available
+\href{https://github.com/big-data-lab-team/container-vulnerabilities-paper/tree/master/Scripts/minification}{here}
+\tristan{Add info in README, clean up code wherever needed}, installs
+\reprozip in the image to minify, runs an analysis to collect a \reprozip
+trace, and finally deletes all unnecessary packages. We had used the
+\href{https://github.com/ReproNim/neurodocker}{Neurodocker} tool initially, but it did not have any impact on the detected
+vulnerabilities because it was removing unused files from the file system
+directly instead of using the package manager \tristan{Please check this last sentence}.
 
@@
 
-% \subsection{Hybrid Approach}
-
-% Following the two previous approaches, we employ a hybrid approach, where
-% we combine both update and size reduction processes in an attempt to
-% lessen number of vulnerabilities or to test the effect of
-% combining two approaches. To allow for that, we first update all packages in
-% the image, then delete all unnecessary packages. Applying these processes in reverse
-% may reduce the needed work; however this is not possible in all cases. For instance,
-% some packages, such as \texttt{apt-transport-https}, are required to fetch updates, deleting these packages
-% ahead of time will disallow the update process to take place.
-
 \section{Results}
 
-Figure~\ref{fig:vulnerabilities} summarizes our results. All the collected
+Figure~\ref{fig:vulnerabilities} presents our results. All the collected
 data are available in our GitHub repository at
@@
 \includegraphics[width=\textwidth]{Figures/results.pdf}
-\caption{\label{fig:vulnerabilities} Number of vulnerabilities detected
-by Anchore in container images. \textbf{(A)} Number of vulnerabilities
-by container image and severity. \textbf{(B)} Combined
-effect of image minification and package update on 5 container images. \textbf{(C, D)}
-Number of vulnerabilities by number of packages, before and after
-package update.}
+\caption{\label{fig:vulnerabilities} Number of vulnerabilities detected by
+Anchore in container images. \textbf{(A)} Number of vulnerabilities by
+container image and severity, showing hundreds of detected vulnerabilities
+per image (mean: 468). \textbf{(B)} Effect of image minification and
+package update on 5 container images, showing that both techniques are
+complementary \tristan{image f has 0 vulnerabilities after update and minification, is it really the case?
+it is also weird that minification before update has almost no effect, but it removes all the remaining vulnerabilities after update}.
+ \textbf{(C)} Number of vulnerabilities by number of
+packages, showing a strong linear relationship. \textbf{(D)} Number of
+vulnerabilities by number of packages \emph{after package update}, showing that software updates 
+importantly reduce the number of detected vulnerabilities.}
 \end{figure*}
 
-A substantial number of vulnerabilities were found in the tested container
- images (Fig~\ref{fig:vulnerabilities}-\textbf{A}), with an average of 466 vulnerabilities
+An important amount of vulnerabilities were found in the tested container
+ images (Fig~\ref{fig:vulnerabilities}-\textbf{A}), with an average of 468 vulnerabilities
   per image and a median of 372. In comparison, no vulnerabilities were found in base
@@
  as no obvious association between the OS distribution and numbers of
- vulnerabilities could be found.
+ vulnerabilities was observed \tristan{note to self: this isn't true for Alpine}.
 
@@
 detected vulnerabilities and the number of packages present in the
-container image (Fig~\ref{fig:vulnerabilities}-\textbf{C}, r=0.83,
+image (Fig~\ref{fig:vulnerabilities}-\textbf{C}, r=0.83,
 $p\textless10^{-10}$). On average, 1.8 vulnerabilities are introduced for
@@
 Updating container images reduces the number of vulnerabilities by package
-by a factor of 3 on average, leading to an extra 0.6 vulnerabilities by
+by a factor of 3 on average, resulting in only 0.6 extra vulnerabilities by
 package (Fig~\ref{fig:vulnerabilities}-\textbf{D}, r=0.81,
@@
 reach EOL}. In spite of the associated reproducibility challenges, updating
-packages therefore appears as a very good way to avoid vulnerabilities. It
+packages therefore appears as a very efficient way to avoid vulnerabilities. It
 is not an ultimate solution though, as substantial numbers of
@@
 The effect of minification stems from the number of packages
-than can be removed, which varies greatly across images. For
+that can be removed, which varies greatly across images. For
 instance, images \textbf{f} and \textbf{a} have a large number of packages,
@@
 vulnerabilities. The former is efficient against vulnerabilities that have
-been fixed by the package maintainers, while the latter targets unused
+been fixed by package maintainers, while the latter targets unused
 software. In four of the five tested images, we find that combining update
@@
 
-\subsection{Discrepancies between scanners}
+\subsection{Differences between scanners}
 
-The results presented so far were obtained with Anchore, a popular
-container image scanning tool. We scanned the images with two other tools,
+The results presented so far were obtained with Anchore. We scanned the images with two other tools,
 Clair and Vuls, to evaluate the stability of our results. Important
 discrepancies were found between scanners (Fig~\ref{fig:venn}), in particular between Anchore
-and the other two, for which Jaccard coefficients are as low as 0.6, meaning
-that only 60\% of all the detected vulnerabilities are detected by both
-Anchore and the other scanner. Vuls and Clair appear to be in better
+and the other two scanners, for which Jaccard coefficients as low as 0.6 were found, meaning
+that scanning results only overlapped by 60\%. Vuls and Clair appear to be in better
 agreement, with a Jaccard coefficient of 0.8.
@@
 % where do the discrepancies come from?
-The vulnerabilities detected only by Anchore (region
-\textbf{(1)} in Fig~\ref{fig:venn}) are all in the development package
-(headers) of the C library (\texttt{linux-libc-dev} in Ubuntu).
+The vulnerabilities detected by Anchore only (region \textbf{(1)} in
+Fig~\ref{fig:venn}) are all in the development package (headers) of the C
+library (\texttt{linux-libc-dev} in Ubuntu). \tristan{not all in fact... I
+wasn't sure how to interpret all these differences (see last section in the
+notebook), let's discuss it during a meeting.}
 
@@
         \includegraphics[width=\columnwidth]{Figures/venn.pdf}
-	\caption{\label{fig:venn} Discrepancies in the vulnerabilities detected
+	\caption{\label{fig:venn} Differences between the vulnerabilities detected
 	by the different scanners. The Jaccard coefficients between the sets of
 	detected vulnerabilities are quite low, showing important discrepancies
-	between the scanners: Jaccard(Anchor, Clair) = 0.59, Jaccard(Anchore, Vuls) =
-	0.59, Jaccard(Vuls, Clair) = 0.82. Two Ubuntu 17.04 images weren't included in this comparison as they cannot be scanned by Vuls. \todo{add Centos images}}
+	between the scanners: Jaccard(Anchore, Clair) = 0.59, Jaccard(Anchore, Vuls) =
+	0.59, Jaccard(Vuls, Clair) = 0.82. Two Ubuntu 17.04 images weren't
+	included in this comparison as they cannot be scanned by Vuls.
+	\tristan{add Centos images to the analysis using the notebook}}
 \end{figure}
@@
 every 6 months and provide maintenance for about a year, while CentOS
-releases every 3-5 years and provide maintenance for 10 years. Similarly,
+release every 3-5 years and provide maintenance for 10 years. Similarly,
 Ubuntu LTS (long-term support) distributions provide free security updates
-for 5 years, and Debian stable releases are maintained for 3 years (the
-Debian LTS project intends to extend this duration to 5 years). Commercial
+for 5 years, and Debian stable releases are maintained for 3 years. Commercial
 offers for extended maintenance periods are common. 
@@
 \item \emph{Run image scanners during continuous integration.} Scanning
-container images cann be a cumbersome process (for instance, scanning the
-\todo{x} images involved in this study takes about \todo{y} hours) that
+container images can be a cumbersome process (for instance, scanning the
+38 images involved in this study takes about \todo{y} hours) that
 could be asynchronously executed during continuous integration (CI),
@@
 data in the file system or using CPU cycles, resulting in denial of service
-for the user running the container, and possibly for other HPC users, and
+for the user running the container and possibly for other HPC users, and
 (2) attacking a host network service, for instance a scheduler or a file
@@
 
-Container images deployed on HPC clusters for scientific data analyses are
-likely to contain hundreds of security vulnerabilities, many of which are
-critical. In the short term, application software developers can address
-this issue by: (1) minifying container images, by using lightweight OS
-distributions and reducing software dependencies, and (2) applying regular
-security updates, which requires using OS distributions with long-term
-support. Longer term, data analysis pipelines would benefit from in-depth
-stability analysis, to ensure that analytical results are not affected by
-security updates.
+Most container images deployed on HPC clusters for scientific data analyses
+contain hundreds of security vulnerabilities, many of which are critical.
+In the short term, application software developers can address this issue
+by: (1) minifying container images, by using lightweight OS distributions
+and reducing software dependencies, and (2) applying regular security
+updates, which requires using OS distributions with long-term support.
+Longer term, data analysis pipelines would benefit from in-depth stability
+analysis, to ensure that analytical results are not affected by security
+updates.
 
@@
 to ban containers from their systems. User-controlled container images are
-just one of many end-user artifacts that could serve as attack vectors,
-and to our knowledge no attack has been described to exploit them. Other,
-more traditional types of attacks targeting user credentials or network
+just one of many end-user artifacts that could serve as attack vectors, and
+to our knowledge no attack has been described to exploit them. More
+traditional types of attacks targeting user credentials or network
 connections are likely to remain more common.

### 2020-09-14 paper.tex
Minor checks and typos

@@
 \newcommand{\rom}[1]{\lowercase\expandafter{\romannumeral #1\relax}}
-\newcommand{\tristan}[1]{\color{blue}From Tristan: #1\color{black}}
+\newcommand{\tristan}[1]{\color{red}From Tristan: #1\color{black}}
 
@@
 Vuls and Clair, supporting Docker, and
-Singularity Container Tools --- Stools~\cite{stools}, supporting Singularity.
+Singularity Container Tools --- Stools, supporting Singularity.
 
@@
 metadata of vulnerabilities. Apart from this, like Anchore, Vuls also
-refers NVD database for getting vulnerability metadata \tristan{why is NVD not in the table?}.
+refers to the NVD database for getting vulnerability metadata \tristan{why is NVD not in the table?}.
 
@@
 
-Unsuprisingly, a strong linear relationship is found between the number of
+Unsurprisingly, a strong linear relationship is found between the number of
 detected vulnerabilities and the number of packages present in the
@@
 
-\subsection{Effect of image udpate}
+\subsection{Effect of image update}
 
@@
 \item \emph{Use lightweight base images such as Alpine Linux}. Base
-images often come with packages that are useful in personnal computers or
+images often come with packages that are useful in personal computers or
 servers, but not in containers dedicated to a specific data analysis. In

### 2020-10-19 paper.tex

@@
 were already included in BIDS apps. All the final 26 images
-from BIDS apps were Docker images, whereas Boutiques contained 18 Docker images
+from BIDS apps were Docker images, whereas 18 Boutiques contained 12 Docker images
 and 6 Singularity images. \tristan{Check the numbers: that makes 24 Boutiques images, not 18.}
+\change{Boutiques images are total 18 which is 12(docker)+6(Singularity)}.
 
@@
 distribution-specific databases. Anchore uses OVAL only for CentOS
-\tristan{any idea why?}. It is also worth noting that there is no vulnerability data
+\tristan{any idea why?}.\change{Through our scanning experiments I learned that
+Oval Centos database was not listing all vulnerabilities and Anchore team already
+realized that. In their recent releeases Centos OVAL is deprecated and they started 
+referring to Red Hat Enterprise Linux (RHEL) data} It is also worth noting that there is no vulnerability data
 for Ubuntu 17.04 and 17.10 distributions in the OVAL database, since these
@@
 distributions cannot be scanned with Vuls \tristan{why doesn't vuls use
-Ubuntu CVE tracker?}.
-\tristan{In Vuls, what happens when 2 databases are used?}
+Ubuntu CVE tracker?}.\change{They have it
+in their TODO list}.
+\tristan{In Vuls, what happens when 2 databases are used?}.
+\change{Using OVAL database alone is not sufficient because
+OVAL does not contain all vulnerabilities as the main intention
+of the OVAL database is to provide a detailed description of the most recent vulnerabilities}.
 
@@
 refers to the NVD database for getting vulnerability metadata \tristan{why is NVD not in the table?}.
+\change{NVD is used by all scanners for all Operating systems for getting
+generic vulnerability metadata so if we write in table it will be
+repetitive info}.
 
@@
 \tristan{this contradicts the date mentioned in the paragraph on Clair}.
-
+\change{No, its not. Because the date mentioned in Clair is the date
+when Clair's database was last updated (because its database is present as
+a Docker container so we fetched that was latest updated). However, here the date represents
+the date when we
+froze the vulnerability databases for all the scanners}.
 \subsection{Image Update}
@@
 OS packages. \tristan{what was the date at which update was run?}
+\change{We updated images on 2019-11-05}.
 
@@
 querying the package manager. We extend this list with a passlist of
-packages required for the system to function \tristan{can you give an
-example?}, and with all the dependencies of the required packages,
+packages required for the system to function, \tristan{can you give an
+example?}\change{such as \texttt{coreutils} and \texttt{bash}}, and with all the dependencies of the required packages,
 retrieved using
@@
 directly instead of using the package manager \tristan{Please check this last sentence}.
+\change{correct}.
 
@@
 it is also weird that minification before update has almost no effect, but it removes all the remaining vulnerabilities after update}.
- \textbf{(C)} Number of vulnerabilities by number of
+	\change{image f is bids/ndmg:latest and it have 329 vulnerabilities after update
+	and minification together. However, minification alone does not have much effect and it have 930
+	vulnerabilities after minification} \textbf{(C)} Number of vulnerabilities by number of
 packages, showing a strong linear relationship. \textbf{(D)} Number of
@@
 \tristan{give more details, one of these images is centos 7 which didnt
-reach EOL}. In spite of the associated reproducibility challenges, updating
+reach EOL}. \change{3 out of these missing 6 images retured an error while updating which
+indicates a problem with the package installer, 2 were unable to update because they
+reached EOL and last one with Centos 7.1.1503 returned libselinux conflicts with systemd}. 
+In spite of the associated reproducibility challenges, updating
 packages therefore appears as a very efficient way to avoid vulnerabilities. It
@@
 container images can be a cumbersome process (for instance, scanning the
-38 images involved in this study takes about \todo{y} hours) that
+		38 images involved in this study takes about \todo{y} hours) \change{scanning time
+		is different with different images. It took time between 3 minutes to one hour sometimes
+		per image} that
 could be asynchronously executed during continuous integration (CI),

### 2020-10-20 paper.tex
A few fixes

--- 2020-09-14 paper.tex
@@
 \title{An Analysis of Security Vulnerabilities in Container Images for Scientific Data Analysis}
-\begin{filecontents*}{resul.csv}
-labels,names,A,C,V,Stools
-a,bids/example:latest,838,663,683,
-b,bids/freesurfer:latest,353,215,192,
-c,bids/ndmg:latest,934,757,782,
-d,bids/broccoli:v1.0.0,203,203,117,
-e,bids/fibredensityandcrosssection:latest,1086,849,868,
-f,bids/spm:latest,191,246,235,
-g,poldracklab/mriqc:0.15.0,432,328,332,
-h,bids/cpac:v1.0.1a\_22,698,524,535,
-I,bids/hyperalignment:latest,1717,1327,1433,
-j,bids/mindboggle:0.0.4-1,671,955,569,
-k,bids/mrtrix3\_connectome:latest,275,157,158,
-l,bids/rs\_signal\_extract:0.1,867,454,473,
-m,bids/aa:v0.2.0,189,244,233,
-n,bids/niak:latest,1482,1366,1420,
-o,bids/oppni:v0.7.0-1,913,698,723,
-p,poldracklab/fmriprep:unstable,516,355,393,
-q,bids/brainiak-srm:latest,897,484,503,
-r,bids/nipypelines:0.3.0,641,878,451,
-s,bids/hcppipelines:v3.17.0-18,526,873,620,
-t,bids/magetbrain:latest,112,117,126,
-u,bids/tracula:v6.0.0-4,874,664,683,
-v,bids/baracus:latest,172,238,216,
-w,bids/antscorticalthickness:v2.2.0-1,289,27,no data,
-x,bids/dparsf:v4.3.12,507,750,757,
-y,bids/afni\_proc:latest,67,16,no data,
-z,bids/rshrf:1.0.1,5,3,3,
-aa,bids/ndmg:v0.1.0,934,758,782,
-ab,mcin/qeeg:latest,121,121,142,
-ac,camarasu/creaphase:0.3,148,148,186,
-ad,bigdatalabteam/hcp-prefreesurfer:exec-centos7.freesurferbuild-centos4-latest:latest,257,266,157,
-ae,mcin/docker-fsl:latest,178,178,201,
-af,gkiar/onevoxel:v0.3.0rc2,5,2,2,
-ag,bigdatalabteam/hcp-prefreesurfer:exec-centos7-fslbuild-centos5-latest:latest,257,266,157,
-ah,bt5e/ants:latest,592,600,336,
-ai,poldracklab/fmriprep:1.2.3,591,441,447,
-aj,gkiar/dwipreproc\_fsl-5.0.11\_minified:latest,391,258,263,
-ak,gkiar/mask2boundary:v0.1.0,15,11,11,
-al,mcin/ica-aroma:latest,178,178,202,
-am,c3genomics/genpipes,,,,99
-an,bioinformatics-group/aqua-singularity-recipe,,,,7
-ao,MontrealSergiy/BEst,,,,106
-ap,shub://aces/cbrain-containers-recipes:fsl\_v6.0.1,,,,206
-aq,shots47s/bids-freesurfer-6.0,,,,212
-ar,shots47s/bids-fmriprep-1.2.3,,,,453
-\end{filecontents*}
 
@@
 data analysis. We analyze container images with four vulnerability
-scanners, focusing on the use case of neuroscience data analyses, and
+scanners, focusing on the use case of neuroscience data analysis, and
 quantifying the effect of images updates and minification on the number of
@@
 Singularity~\cite{kurtzer2017singularity} framework is often preferred to
-\href{http://docker.com}{Docker} because of its
+\href{http://docker.com}{Docker} due to its
 secure handling of multi-user environments and convenient support for
@@
 addition to data analysis software and their dependencies. They are rarely
-updated because there is concern that software updates will interfere with
+updated due to concerns that software updates will interfere with
 the results~\cite{gronenschild2012effects, glatard2015reproducibility}.
@@
 and the integrity of user data. We report vulnerability scans produced
-by four popular image scanning tools: Anchore, Vuls, Clair, and Stools.
+by four popular image scanning tools: Anchore, Vuls, Clair, and Singularity tools.
 
@@
 
-We answer these questions through the example of neuroimaging, a field that
-has entered the era of Big Data as many others~\cite{van2014human}. The
-following section describes the materials and tools used in the
-experiments, including container images and image scanners. We then
-describe our methodology for updating and minifying images to reduce
-vulnerabilities. The results present the vulnerabilities detected in container
+We answer these questions through the example of neuroimaging analyses. The remainder of this paper 
+describes the materials and tools used in the
+experiments, including container images, image scanners, and our methodology for updating and minifying images.
+Results present the vulnerabilities detected in container
 images, quantify the effectiveness of updating and minifying images, and
@@
 were already included in BIDS apps. All the final 26 images
-from BIDS apps were Docker images, whereas Boutiques contained 18 Docker images
-and 6 Singularity images. \tristan{Check the numbers: that makes 24 Boutiques images, not 18.}
+from BIDS apps were Docker images, whereas 18 Boutiques contained 12 Docker images
+and 6 Singularity images.
 
@@
 
-We used four popular image scanners, namely Anchore,
-Vuls and Clair, supporting Docker, and
-Singularity Container Tools --- Stools, supporting Singularity.
+We used four popular image scanners: Anchore,
+Vuls and Clair to scan Docker images, and
+Singularity Container Tools (Stools) to scan Singularity images.
 
@@
 \end{tabular}
-\caption{Vulnerability databases used by scanners for different OS distributions}
+\caption{Vulnerability databases used by scanners for different OS distributions. All scanners also refer to 
+the National Vulnerability Database (NVD) for metadata about vulnerabilities.}
 \label{table:databases}
@@
 by Stools are same as mentioned for Clair.
-To scan Singularity images, we followed the steps mentioned in
-\href{https://github.com/singularityhub/stools}{Stools Github}.
+To scan Singularity images, we followed the steps mentioned in the
+\href{https://github.com/singularityhub/stools}{Stools documentation}.
 
@@
 
-Table~\ref{table:databases} shows the vulnerabilities databases used by
-each scanner by OS distribution. Scanners refer to two types of
-vulnerability databases. The first one is the Open Vulnerability and
+Scanners refer to two types of
+vulnerability databases (Table~\ref{table:databases}). The first one is the Open Vulnerability and
 Assessment Language (OVAL) database, an international open standard that
-supports various OS distributions including Ubuntu, Debian and Centos but
+supports various OS distributions including Ubuntu, Debian and CentOS but
 not Alpine. The second one are vulnerability databases from specific OS
@@
 security fixes in different versions of the distribution. Vuls uses OVAL
-databases for all distributions except Alpine, since Alpine is not
-available in OVAL. On the contrary, Clair exclusively refers to
+databases for all distributions except Alpine. On the contrary, Clair exclusively refers to
 distribution-specific databases. Anchore uses OVAL only for CentOS
-\tristan{any idea why?}. It is also worth noting that there is no vulnerability data
+\tristan{any idea why?}.\change{Through our scanning experiments I learned that
+Oval CentOS database was not listing all vulnerabilities and Anchore team already
+realized that. In their recent releases CentOS OVAL is deprecated and they started 
+referring to Red Hat Enterprise Linux (RHEL) data}
+ It is also worth noting that there is no vulnerability data
 for Ubuntu 17.04 and 17.10 distributions in the OVAL database, since these
@@
 distributions cannot be scanned with Vuls \tristan{why doesn't vuls use
-Ubuntu CVE tracker?}.
-\tristan{In Vuls, what happens when 2 databases are used?}
-
-Anchore also refers to National Vulnerability Database (NVD) to get
-metadata of vulnerabilities. Apart from this, like Anchore, Vuls also
-refers to the NVD database for getting vulnerability metadata \tristan{why is NVD not in the table?}.
+Ubuntu CVE tracker?}.\change{They have it
+in their TODO list}.
+\tristan{In Vuls, what happens when 2 databases are used?}.
+\change{Using OVAL database alone is not sufficient because
+OVAL does not contain all vulnerabilities as the main intention
+of the OVAL database is to provide a detailed description of the most recent vulnerabilities}.
 
@@
 experiments take place on different dates. To avoid such discrepancies, we
-froze the vulnerability databases used by these scanners as of 2019-09-25
-\tristan{this contradicts the date mentioned in the paragraph on Clair}.
+froze the vulnerability databases used by these scanners as of 2019-09-25.
+% \tristan{this contradicts the date mentioned in the paragraph on Clair}.
+% \change{No, its not. Because the date mentioned in Clair is the date
+% when Clair's database was last updated (because its database is present as
+% a Docker container so we fetched that was latest updated). However, here the date represents
+% the date when we
+% froze the vulnerability databases for all the scanners}.
 
@@
 A first approach to reduce the number of vulnerabilities in container
-images is to update their packages to the latest version packaged by the OS
+images is to update their packages to the latest version available in the OS
 distribution. To study the effect of such updates, we developed a script
@@
 to identify the package manager in the image, and invoke it to update all
-OS packages. \tristan{what was the date at which update was run?}
+OS packages. We updated images on 2019-11-05.
 
@@
 querying the package manager. We extend this list with a passlist of
-packages required for the system to function \tristan{can you give an
-example?}, and with all the dependencies of the required packages,
+packages required for the system to function, such as \texttt{coreutils}
+and \texttt{bash}, and with all the dependencies of the required packages,
 retrieved using
@@
 RPM-based distributions instead. Our minification script, available
-\href{https://github.com/big-data-lab-team/container-vulnerabilities-paper/tree/master/Scripts/minification}{here}
-\tristan{Add info in README, clean up code wherever needed}, installs
-\reprozip in the image to minify, runs an analysis to collect a \reprozip
-trace, and finally deletes all unnecessary packages. We had used the
-\href{https://github.com/ReproNim/neurodocker}{Neurodocker} tool initially, but it did not have any impact on the detected
-vulnerabilities because it was removing unused files from the file system
-directly instead of using the package manager \tristan{Please check this last sentence}.
+\href{https://github.com/big-data-lab-team/container-vulnerabilities-paper/tree/master/Scripts/minification}{here},
+installs \reprozip in the image to minify, runs an analysis to collect a
+\reprozip trace, and finally deletes all unnecessary packages. We had used
+the \href{https://github.com/ReproNim/neurodocker}{Neurodocker} tool
+initially, but its application did not affect the detected vulnerabilities
+as it was removing unused files without using the package manager.
 
@@
 \url{https://github.com/big-data-lab-team/container-vulnerabilities-paper}
-with a Jupyter notebook to generate the figures.
+with a Jupyter notebook to regenerate the figures.
 
@@
 package update on 5 container images, showing that both techniques are
-complementary \tristan{image f has 0 vulnerabilities after update and minification, is it really the case?
-it is also weird that minification before update has almost no effect, but it removes all the remaining vulnerabilities after update}.
- \textbf{(C)} Number of vulnerabilities by number of
+complementary \textbf{(C)} Number of vulnerabilities by number of
 packages, showing a strong linear relationship. \textbf{(D)} Number of
@@
  arbitrary code in the container, by crafting responses to specific network
- requests. The OS distribution is reported only for illustration purposes,
- as no obvious association between the OS distribution and numbers of
- vulnerabilities was observed \tristan{note to self: this isn't true for Alpine}.
+ requests. Images based on the Alpine distribution 
+ had the lowest numbers of vulnerabilities, but no significant difference
+ in the numbers of vulnerabilities detected in 
+ Ubuntu, Debian or CentOS distributions was observed.
 
@@
 $p\textless10^{-7}$). Six container images are missing on this figure; they
-could not be updated since their OS distributions reached end of life
-\tristan{give more details, one of these images is centos 7 which didnt
-reach EOL}. In spite of the associated reproducibility challenges, updating
+could not be updated due to various issues with the package manager.
+% \change{3 out of these missing 6 images retured an error while updating which
+% indicates a problem with the package installer, 2 were unable to update because they
+% reached EOL and last one with CentOS 7.1.1503 returned libselinux conflicts with systemd} 
+In spite of the associated reproducibility challenges, updating
 packages therefore appears as a very efficient way to avoid vulnerabilities. It
@@
 than 70\% of the detected vulnerabilities. For other images, such as
-image \textbf{f}, it only reduces the number of vulnerabilities by less than 1\%.
+image \textbf{g}, it only reduces the number of vulnerabilities by less than 1\%.
 The effect of minification stems from the number of packages
 that can be removed, which varies greatly across images. For
-instance, images \textbf{f} and \textbf{a} have a large number of packages,
+instance, images \textbf{g} and \textbf{a} have a large number of packages,
 but the last majority of them is required by the analysis, which makes
@@
 been fixed by package maintainers, while the latter targets unused
-software. In four of the five tested images, we find that combining update
+software. In two of the five tested images, we find that combining update
 and minification further reduces the number of vulnerabilities compared to
 using only one of these processes
-(Fig~\ref{fig:vulnerabilities}-\textbf{B}) \tristan{revise when
-minification in image f is clarified}. The combined effect of update and
+(Fig~\ref{fig:vulnerabilities}-\textbf{B}). The combined effect of update and
 minification seems to be dependent mostly on the effect of minification: if
@@
 There is a widespread issue with security vulnerabilities in container
-images for neuroimaging analyses, and it is likely to impact other
-scientific disciplines as well. Indeed, it is common for container images
+images used for neuroimaging analyses, and it is likely to impact other
+scientific disciplines as well. As shown in our results, it is common for container images
 to hold hundreds of vulnerabilities, including several of critical
@@
 that they support, and the main OS distributions Ubuntu, Debian and CentOS
-are all impacted.
+are all affected.
 
@@
 cycle durations, as long and short life cycles serve different purposes.
-For instance, among RedHat-based distributions Fedora release a new version
+For instance, among RedHat-based distributions, Fedora release a new version
 every 6 months and provide maintenance for about a year, while CentOS
@@
 Ubuntu LTS (long-term support) distributions provide free security updates
-for 5 years, and Debian stable releases are maintained for 3 years. Commercial
-offers for extended maintenance periods are common. 
+for 5 years, and Debian stable releases are maintained for 3 years. 
+% Commercial
+% offers for extended maintenance periods are common. 
 \item \emph{Install packages, not files}. Vulnerability scanners such as

### 2020-10-23 paper.tex
added descrepancies paragraph

@@
 \caption{\label{fig:vulnerabilities} Number of vulnerabilities detected by
-Anchore in container images. \textbf{(A)} Number of vulnerabilities by
+Anchore and Stools in container images. \textbf{(A)} Number of vulnerabilities by
 container image and severity, showing hundreds of detected vulnerabilities
-per image (mean: 468). \textbf{(B)} Effect of image minification and
+per image. Images s*,t*,u*,v*,w* and x* are Singularity images and scanned by Stools. \textbf{(B)} Effect of image minification and
 package update on 5 container images, showing that both techniques are
@@
 % where do the discrepancies come from?
-The vulnerabilities detected by Anchore only (region \textbf{(1)} in
-Fig~\ref{fig:venn}) are all in the development package (headers) of the C
-library (\texttt{linux-libc-dev} in Ubuntu). \tristan{not all in fact... I
-wasn't sure how to interpret all these differences (see last section in the
-notebook), let's discuss it during a meeting.}
+We analyzed these results and figured out some reasons behind the discrepancies of the results.
+The 4443 out of 4453 vulnerabilities detected by Anchore only (region \textbf{(1)} in
+Fig~\ref{fig:venn}) are in the development package (headers) of the C
+library (\texttt{linux-libc-dev} in Ubuntu and Debian). Clair detects only Debian vulnerabilities
+in \texttt{linux-libc-dev}, whereas Vuls do not detect vulnerabilities in this package at all.
+The remaining 10 vulnerabilities in region \textbf{1} are reported in the binary or subpackages 
+of vulnerable packages, which is not reported by Vuls and Clair.
+Also, Anchore filters the vulnerabilities that are \texttt{minor} and 
+ignored by Debian. These are the main reasons behind vulnerabilities in 
+region \textbf{2} and region \textbf{3}. Clair's wrong detections also adds up to region \textbf{3}.
+Vulnerabilities in region \textbf{4} all exist in Ubuntu distribution 
+and are not detected by Clair. We noticed that this is happening because Clair refers 
+to Ubuntu CVE tracker database and in this database there are two entries for Ubuntu 14.04, 
+one for LTS and another for ESM release. Clair mistakenly grabs ESM entry and detects vulnerabilities 
+according to it, whereas LTS release is present in the image. There are also a couple of 
+bugs in Anchore which we noticed in our analysis and reported to the Anchore's developer 
+team through their Slack channel. First is the \textit{epoch bug}, which gets triggered 
+when there is an epoch (\texttt{:}) in the package version. Another is \textit{out of standard bug}, 
+which gets triggered when the vulnerability is ignored 
+by Ubuntu. These two bugs are also the reasons behind vulnerabilities in region \textbf{6} 
+in addition to Anchore intentionally ignoring \texttt{minor} Debian vulnerabilities. 
+Furthermore, Vuls reports vulnerabilities which have \textit{TEMP} 
+identifier, whereas both Clair and Anchore decides not to report them. These 
+vulnerabilities have a temporary identifier and can be changed anytime so it is not
+recommended for external references. There are 32 temporary vulnerabilities in region \textbf{7}.
+The remaining vulnerabilities in this region exist in Centos distribution and according to our analysis
+these are the misses in Anchore and Clair.
 
@@
 	0.59, Jaccard(Vuls, Clair) = 0.82. Two Ubuntu 17.04 images weren't
-	included in this comparison as they cannot be scanned by Vuls.
-	\tristan{add Centos images to the analysis using the notebook}}
+	included in this comparison as they cannot be scanned by Vuls.}
 \end{figure}

### 2020-10-26 paper.tex
A few edits

--- 2020-10-20 paper.tex
@@
 paper presents a vulnerability analysis of container images for scientific
-data analysis. We analyze container images with four vulnerability
+data analysis. We compare results obtained with four vulnerability
 scanners, focusing on the use case of neuroscience data analysis, and
 quantifying the effect of images updates and minification on the number of
-vulnerabilities. We find that container images used for data analysis
+vulnerabilities. We find that container images used for neuroscience data analysis
 contain hundreds of vulnerabilities, that software updates remove about two
@@
 In this study, we focus on the vulnerabilities present in container images
-deployed on HPC clusters for scientific data analysis, and we answer the
+deployed on HPC clusters for scientific data analysis. We address the
 following questions:
@@
 
-We answer these questions through the example of neuroimaging analyses. The remainder of this paper 
+The remainder of this paper 
 describes the materials and tools used in the
@@
 used in neuroscience: BIDS
-apps~\cite{gorgolewski2017bids} and Boutiques~\cite{glatard2018boutiques},
+apps~\cite{gorgolewski2017bids} (26 images) and Boutiques~\cite{glatard2018boutiques} (18 images),
 totalling
-44 container images: 26 from BIDS apps, and 18 from Boutiques. At the time of the study, BIDS apps had 27 images,
+44 container images. At the time of the study, BIDS apps had 27 images,
 out of which one wasn't available on DockerHub. Boutiques had 49 images,
@@
 
-We used four popular image scanners: Anchore,
-Vuls and Clair to scan Docker images, and
-Singularity Container Tools (Stools) to scan Singularity images.
+We compared the results obtained with four container image scanners: Anchore, Vuls, and
+Clair to scan Docker images, and Singularity Container Tools
+(Stools) to scan Singularity images.
 
@@
 packages, non-OS packages (Python, Java, Gem, and npm), and files.
-In our experiments, we use Anchore Engine version 0.5.0 through Docker image \texttt{anchore/anchore-engine:v0.5.0}, and
+In our experiments, we used Anchore Engine version 0.5.0 through Docker image \texttt{anchore/anchore-engine:v0.5.0}, and
 Anchore vulnerability database version 0.0.11.
@@
 \caption{Vulnerability databases used by scanners for different OS distributions. All scanners also refer to 
-the National Vulnerability Database (NVD) for metadata about vulnerabilities.}
+the National Vulnerability Database (NVD) for vulnerability metadata.}
 \label{table:databases}
@@
 offers both static and dynamic scanning, and both local and remote
-scanning. In our experiments,we used Vuls 0.9.0, executed through Docker image
+scanning. In our experiments, we used Vuls 0.9.0, executed through Docker image
 \texttt{vuls/vuls:0.9.0} in remote dynamic mode.
@@
 developed by CoreOS (now Container Linux), a Linux distribution to deploy
-container clusters. Clair has a client-server architecture, in which the
-server scans Docker images layer by layer and maintains a database of
-vulnerabilities. We used Clair through
+container clusters.
+%  Clair has a client-server architecture, in which the
+% server scans Docker images layer by layer and maintains a database of
+% vulnerabilities.
+ We used Clair through
 \href{https://github.com/arminc/clair-scanner}{Clair-scanner}, a tool to
@@
 Docker image \texttt{arminc/clair-local-scan:v2.0.6}. For the vulnerability
-database, we use Docker image \texttt{arminc/clair-db:latest}, last
+database, we used Docker image \texttt{arminc/clair-db:latest}, last
 updated on 2019-09-18.
@@
 distributions, such as Alpine-SecDB, Debian Security Bug Tracker, Ubuntu
-CVE Tracker, or Red Hat Security Data. OS distributions often assign a
+CVE Tracker, or Red Hat Security Data. In these databases, OS distributions often assign a
 status to each vulnerability, to keep track of required and available
@@
 databases for all distributions except Alpine. On the contrary, Clair exclusively refers to
-distribution-specific databases. Anchore uses OVAL only for CentOS
-\tristan{any idea why?}.\change{Through our scanning experiments I learned that
-Oval CentOS database was not listing all vulnerabilities and Anchore team already
-realized that. In their recent releases CentOS OVAL is deprecated and they started 
-referring to Red Hat Enterprise Linux (RHEL) data}
+distribution-specific databases. Anchore uses OVAL only for CentOS, as distribution-specific databases
+are assumed to be more complete.
 It is also worth noting that there is no vulnerability data
@@
 distributions have reached end of life, meaning that images with these
-distributions cannot be scanned with Vuls \tristan{why doesn't vuls use
-Ubuntu CVE tracker?}.\change{They have it
-in their TODO list}.
+distributions cannot be scanned with Vuls.
+%  \tristan{why doesn't vuls use
+% Ubuntu CVE tracker?}.\change{They have it
+% in their TODO list}.
 \tristan{In Vuls, what happens when 2 databases are used?}.

### 2020-10-26 paper.tex
edits in abstract and intro

@@
 scanners, focusing on the use case of neuroscience data analysis, and
-quantifying the effect of images updates and minification on the number of
+quantifying the effect of image update and minification on the number of
 vulnerabilities. We find that container images used for neuroscience data analysis
@@
 easier to reuse between experiments. As a result, over 30\% of official
-images in DockerHub have been shown to contain high priority security
+images in DockerHub have been shown to contain high-priority security
 vulnerabilities~\cite{gummaraju2015over}, images on average contain over
@@
 In this study, we focus on the vulnerabilities present in container images
-deployed on HPC clusters for scientific data analysis. We address the
-following questions:
+deployed on HPC clusters for scientific data analysis, in particular in the
+neuroimaging domain. We address the following questions:
 
@@
 \textit{Can the amount of vulnerabilities be reduced by updating the images?}  
-For many reasons related to reproducibility and lifecycle of research
+For many reasons related to reproducibility and the lifecycle of research
 projects, container images deployed on HPC clusters often include outdated
@@
 Container images often include more software packages than necessary for 
-typical analysis. We report on the impact of unused software packages on
+a typical analysis. We report on the impact of unused software packages on
 the presence of vulnerabilities.
@@
 The remainder of this paper 
-describes the materials and tools used in the
-experiments, including container images, image scanners, and our methodology for updating and minifying images.
+describes the container images and scanners used in our experiment, and our methodology for updating and minifying images.
 Results present the vulnerabilities detected in container

### 2020-10-26 paper.tex
Edits in scanners differences, minor edits throughout

@@
 
-To detect security vulnerabilities
-in container images and examine the effect of different
-manipulations on those images, we used container
+We used container
 images from two popular application frameworks, as well as
@@
 were already included in BIDS apps. All the final 26 images
-from BIDS apps were Docker images, whereas 18 Boutiques contained 12 Docker images
+from BIDS apps were Docker images, whereas the 18 Boutiques images contained 12 Docker images
 and 6 Singularity images.
@@
 % in their TODO list}.
-\tristan{In Vuls, what happens when 2 databases are used?}.
-\change{Using OVAL database alone is not sufficient because
-OVAL does not contain all vulnerabilities as the main intention
-of the OVAL database is to provide a detailed description of the most recent vulnerabilities}.
+% \tristan{In Vuls, what happens when 2 databases are used?}.
+% \change{Using OVAL database alone is not sufficient because
+% OVAL does not contain all vulnerabilities as the main intention
+% of the OVAL database is to provide a detailed description of the most recent vulnerabilities}.
 
@@
 the \href{https://github.com/ReproNim/neurodocker}{Neurodocker} tool
-initially, but its application did not affect the detected vulnerabilities
+initially, but it did not affect the detected vulnerabilities
 as it was removing unused files without using the package manager.
@@
 container image and severity, showing hundreds of detected vulnerabilities
-per image. Images s*,t*,u*,v*,w* and x* are Singularity images and scanned by Stools. \textbf{(B)} Effect of image minification and
+per image. Images s*,t*,u*,v*,w* and x* are Singularity images scanned by Stools. \textbf{(B)} Effect of image minification and
 package update on 5 container images, showing that both techniques are
 complementary \textbf{(C)} Number of vulnerabilities by number of
-packages, showing a strong linear relationship. \textbf{(D)} Number of
+packages, showing a strong linear relationship \tristan{add Singularity images and update regression parameters accordingly.}. \textbf{(D)} Number of
 vulnerabilities by number of packages \emph{after package update}, showing that software updates 
@@
  images (Fig~\ref{fig:vulnerabilities}-\textbf{A}), with an average of 468 vulnerabilities
-  per image and a median of 372. In comparison, no vulnerabilities were found in base
+  per image and a median of 372 \tristan{update values with singularity images}. In comparison, no vulnerabilities were found in base
  Docker images \texttt{ubuntu:20.04} and \texttt{centos:7} after package
@@
 image (Fig~\ref{fig:vulnerabilities}-\textbf{C}, r=0.83,
-$p\textless10^{-10}$). On average, 1.8 vulnerabilities are introduced for
+$p\textless10^{-10}$) \tristan{update values with singularity images}. On average, 1.8 vulnerabilities are introduced for
 each new package installation. This observation motivates a systematic
@@
 package (Fig~\ref{fig:vulnerabilities}-\textbf{D}, r=0.81,
-$p\textless10^{-7}$). Six container images are missing on this figure; they
-could not be updated due to various issues with the package manager.
+$p\textless10^{-7}$). Twelve container images are missing on this figure:
+six of them could not be updated due to various issues with the package
+manager, and six of them are Singularity images that we didn't update.
 % \change{3 out of these missing 6 images retured an error while updating which
@@
 In spite of the associated reproducibility challenges, updating
-packages therefore appears as a very efficient way to avoid vulnerabilities. It
-is not an ultimate solution though, as substantial numbers of
+packages therefore appears to be an efficient way to avoid vulnerabilities. It
+is not an ultimate solution though, as a substantial number of
 vulnerabilities remain.
@@
 been fixed by package maintainers, while the latter targets unused
-software. In two of the five tested images, we find that combining update
+software. In two of the five tested images (images \textbf{S} and \textbf{U}), we find that combining update
 and minification further reduces the number of vulnerabilities compared to
 using only one of these processes
-(Fig~\ref{fig:vulnerabilities}-\textbf{B}). The combined effect of update and
-minification seems to be dependent mostly on the effect of minification: if
-minification is useful, then it is beneficial to run it in combination with
-package update.
+(Fig~\ref{fig:vulnerabilities}-\textbf{B}). \
 
@@
 
-The results presented so far were obtained with Anchore. We scanned the images with two other tools,
+The results presented so far were obtained with Anchore (Docker images) and
+Stools (Singularity images). We scanned the Docker images with two other tools,
 Clair and Vuls, to evaluate the stability of our results. Important
-discrepancies were found between scanners (Fig~\ref{fig:venn}), in particular between Anchore
-and the other two scanners, for which Jaccard coefficients as low as 0.6 were found, meaning
-that scanning results only overlapped by 60\%. Vuls and Clair appear to be in better
-agreement, with a Jaccard coefficient of 0.8.
+discrepancies were found between scanners (Fig~\ref{fig:venn}), in
+particular between Anchore and the other two scanners, for which Jaccard
+coefficients as low as 0.6 were found, meaning that scanning results only
+overlapped by 60\%. Vuls and Clair appear to be in better agreement, with a
+Jaccard coefficient of 0.8.
 
 % where do the discrepancies come from?
-We analyzed these results and figured out some reasons behind the discrepancies of the results.
-The 4443 out of 4453 vulnerabilities detected by Anchore only (region \textbf{(1)} in
-Fig~\ref{fig:venn}) are in the development package (headers) of the C
-library (\texttt{linux-libc-dev} in Ubuntu and Debian). Clair detects only Debian vulnerabilities
-in \texttt{linux-libc-dev}, whereas Vuls do not detect vulnerabilities in this package at all.
-The remaining 10 vulnerabilities in region \textbf{1} are reported in the binary or subpackages 
-of vulnerable packages, which is not reported by Vuls and Clair.
-Also, Anchore filters the vulnerabilities that are \texttt{minor} and 
-ignored by Debian. These are the main reasons behind vulnerabilities in 
-region \textbf{2} and region \textbf{3}. Clair's wrong detections also adds up to region \textbf{3}.
-Vulnerabilities in region \textbf{4} all exist in Ubuntu distribution 
-and are not detected by Clair. We noticed that this is happening because Clair refers 
-to Ubuntu CVE tracker database and in this database there are two entries for Ubuntu 14.04, 
-one for LTS and another for ESM release. Clair mistakenly grabs ESM entry and detects vulnerabilities 
-according to it, whereas LTS release is present in the image. There are also a couple of 
-bugs in Anchore which we noticed in our analysis and reported to the Anchore's developer 
-team through their Slack channel. First is the \textit{epoch bug}, which gets triggered 
-when there is an epoch (\texttt{:}) in the package version. Another is \textit{out of standard bug}, 
-which gets triggered when the vulnerability is ignored 
-by Ubuntu. These two bugs are also the reasons behind vulnerabilities in region \textbf{6} 
-in addition to Anchore intentionally ignoring \texttt{minor} Debian vulnerabilities. 
-Furthermore, Vuls reports vulnerabilities which have \textit{TEMP} 
-identifier, whereas both Clair and Anchore decides not to report them. These 
-vulnerabilities have a temporary identifier and can be changed anytime so it is not
-recommended for external references. There are 32 temporary vulnerabilities in region \textbf{7}.
-The remaining vulnerabilities in this region exist in Centos distribution and according to our analysis
-these are the misses in Anchore and Clair.
+We analyzed these results and explained some reasons behind the observed
+discrepancies. Out of 4453 vulnerabilities detected by Anchore only (region
+\textbf{1} in Fig~\ref{fig:venn}), 4443 are found in the development
+package of the C library (\texttt{linux-libc-dev} in Ubuntu and Debian).
+Clair detects only Debian vulnerabilities in \texttt{linux-libc-dev},
+whereas Vuls do not detect vulnerabilities in this package at all. Since Anchore
+ignores Debian
+vulnerabilities flagged as \texttt{minor}, it
+might either detect (region \textbf{2}) or ignore (region \textbf{3})
+the
+Debian vulnerabilities detected by Clair in \texttt{linux-libc-dev}. The
+remaining 10 vulnerabilities in region \textbf{1} are found in sub-packages
+of vulnerable packages: they are correctly reported by Anchore and missed
+by Vuls and Clair.
+
+Many vulnerabilities in region \textbf{3} and \textbf{4} are from images
+based on Ubuntu 14.04. In the Ubuntu CVE tracker database used by Clair and
+Anchore, there are two entries for Ubuntu 14.04: one for LTS (Long-Term
+Support), a Ubuntu release with 5 years of technical support, and another one
+for ESM (Extended Security Maintenance), a release that provides security
+patches beyond the 5 years covered by LTS. Although all the scanned images
+are LTS, Clair refers to the ESM database entry while Anchore and Vuls refer to the
+LTS database entry. The vulnerabilities present in region \textbf{3} due to
+this discrepancy are incorrectly missed by Anchore and Vuls: they have been
+detected in ESM but were already present in LTS. The vulneratibilities in
+region \textbf{4} are incorrectly missed by Clair: they have been fixed in
+ESM but are still present in LTS.
+
+Some vulnerabilities in region \textbf{6} are due to bugs in Anchore: the
+\textit{epoch bug} ignores vulnerabilities related to package versions that
+contain an epoch (\texttt{:}); the \textit{out of standard bug} ignores
+vulnerabilities that are ignored by the Ubuntu distribution. We reported
+these bugs to the Anchore developers through their Slack channel. Some
+vulnerabilities in region \textbf{6} are also due to the fact that Anchore
+intentionally ignores Debian vulnerabilities flagged as \texttt{minor}.
+
+Finally, 32 vulnerabilities that are flagged temporary by the Debian
+distribution are reported by Vuls but not by Anchore or Clair (region
+\textbf{7}). The remaining 504 vulnerabilities in this region are all found
+in CentOS images. We weren't able to explain why they were detected by Vuls
+only.
 
@@
         \includegraphics[width=\columnwidth]{Figures/venn.pdf}
-	\caption{\label{fig:venn} Differences between the vulnerabilities detected
+	\caption{\label{fig:venn} Differences between vulnerabilities detected
 	by the different scanners. The Jaccard coefficients between the sets of
 	detected vulnerabilities are quite low, showing important discrepancies
-	between the scanners: Jaccard(Anchore, Clair) = 0.59, Jaccard(Anchore, Vuls) =
-	0.59, Jaccard(Vuls, Clair) = 0.82. Two Ubuntu 17.04 images weren't
+	between the scanners: Jaccard(Anchore, Clair) = 0.63, Jaccard(Anchore, Vuls) =
+	0.59, Jaccard(Vuls, Clair) = 0.80. Two Ubuntu 17.04 images weren't
 	included in this comparison as they cannot be scanned by Vuls.}
@@
 \item \emph{Run image scanners during continuous integration.} Scanning
-container images can be a cumbersome process (for instance, scanning the
-		38 images involved in this study takes about \todo{y} hours) \change{scanning time
-		is different with different images. It took time between 3 minutes to one hour sometimes
-		per image} that
+container images can be a cumbersome process that
 could be asynchronously executed during continuous integration (CI),
@@
 CI also allows developers to identify vulnerabilities quickly,
-before new software contributions are released.
+before new software versions are released.
 \end{enumerate}
@@
 systems through containers is challenging due to their relative isolation
-from the host system. First, under the safe assumption that legitimate HPC
+from the host system. First, under the assumption that legitimate HPC
 users can be trusted, attackers would have to be remote to the container,

### 2020-10-26 paper.tex

@@
 container image and severity, showing hundreds of detected vulnerabilities
-per image. Images s*,t*,u*,v*,w* and x* are Singularity images scanned by Stools. \textbf{(B)} Effect of image minification and
+per image. Images s*,t*,u*,v*,w* and x* are Singularity images scanned by Stools and
+others are Docker images scanned using Anchore. \textbf{(B)} Effect of image minification and
 package update on 5 container images, showing that both techniques are
 complementary \textbf{(C)} Number of vulnerabilities by number of
-packages, showing a strong linear relationship \tristan{add Singularity images and update regression parameters accordingly.}. \textbf{(D)} Number of
+packages, showing a strong linear relationship. \textbf{(D)} Number of
 vulnerabilities by number of packages \emph{after package update}, showing that software updates 
@@
 An important amount of vulnerabilities were found in the tested container
- images (Fig~\ref{fig:vulnerabilities}-\textbf{A}), with an average of 468 vulnerabilities
-  per image and a median of 372 \tristan{update values with singularity images}. In comparison, no vulnerabilities were found in base
+ images (Fig~\ref{fig:vulnerabilities}-\textbf{A}), with an average of 460 vulnerabilities
+  per image and a median of 321. In comparison, no vulnerabilities were found in base
  Docker images \texttt{ubuntu:20.04} and \texttt{centos:7} after package
@@
 detected vulnerabilities and the number of packages present in the
-image (Fig~\ref{fig:vulnerabilities}-\textbf{C}, r=0.83,
-$p\textless10^{-10}$) \tristan{update values with singularity images}. On average, 1.8 vulnerabilities are introduced for
+image (Fig~\ref{fig:vulnerabilities}-\textbf{C}, r=0.82,
+$p\textless10^{-12}$). On average, 1.7 vulnerabilities are introduced for
 each new package installation. This observation motivates a systematic
@@
 package (Fig~\ref{fig:vulnerabilities}-\textbf{D}, r=0.81,
-$p\textless10^{-7}$). Twelve container images are missing on this figure:
+$p\textless10^{-8}$). Twelve container images are missing on this figure:
 six of them could not be updated due to various issues with the package

### 2020-10-26 paper.tex
typos

--- 2020-10-26 paper.tex
@@
 % image \texttt{arminc/clair-db:latest} for referring to vulnerability feed.
-Since Stools uses Clair internally for scanning, vulnerability databases used
-by Stools are same as mentioned for Clair.
+Since Stools uses Clair internally for scanning, the vulnerability databases used
+by Stools are the same as mentioned for Clair.
 To scan Singularity images, we followed the steps mentioned in the
@@
 this discrepancy are incorrectly missed by Anchore and Vuls: they have been
-detected in ESM but were already present in LTS. The vulneratibilities in
+detected in ESM but were already present in LTS. The vulnerabilities in
 region \textbf{4} are incorrectly missed by Clair: they have been fixed in

### 2020-10-26 paper.tex
Re-generated figures, fixed typos in p values

@@
 image (Fig~\ref{fig:vulnerabilities}-\textbf{C}, r=0.82,
-$p\textless10^{-12}$). On average, 1.7 vulnerabilities are introduced for
+$p\textless10^{-11}$). On average, 1.7 vulnerabilities are introduced for
 each new package installation. This observation motivates a systematic
@@
 package (Fig~\ref{fig:vulnerabilities}-\textbf{D}, r=0.81,
-$p\textless10^{-8}$). Twelve container images are missing on this figure:
+$p\textless10^{-7}$). Twelve container images are missing on this figure:
 six of them could not be updated due to various issues with the package

### 2021-02-25 paper.tex
Fixed README and compilation flags
Added required sections
typo
Addressing review comments (WIP)

@@
 \usepackage{csvsimple}
-\usepackage{minted} % Used for JSON highlighting
 \usepackage{datatool}
@@
 \newcommand{\tristan}[1]{\color{red}From Tristan: #1\color{black}}
+\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
+\newcommand{\revision}[1]{\color{ao(english)}#1\color{black}\xspace}
 
@@
 Software containers greatly facilitate the deployment and reproducibility
-of scientific data analyses on high-performance computing clusters
+of scientific data analyses, \revision{especially} on high-performance computing clusters
 (HPC). However, container images often contain outdated or unnecessary
@@
 Software containers have emerged has an efficient solution to deploy
-scientific data analyses on HPC clusters, due
+scientific data analyses, due
 to their portability, ease of use, and limited overhead. On HPC systems, the
@@
 Taking advantage of core Linux kernel features such as namespaces, control
-groups and chroot, containers isolate processes from the host computer, and
+groups and chroot, containers isolate processes from the host computer, and \revision{often can}
 control the memory, CPU, network and file-system resources assigned to
@@
 
-Container images typically include full operating system (OS) distributions in
-addition to data analysis software and their dependencies. They are rarely
-updated due to concerns that software updates will interfere with
-the results~\cite{gronenschild2012effects, glatard2015reproducibility}.
+Container images typically include full operating system (OS) distributions
+in addition to data analysis software and their dependencies. They are
+rarely updated due to concerns that \revision{updated} software may \revision{be
+incompatible or may} interfere with the
+results \revision{via numerical perturbations propagating in the
+analyses in unknown ways}~\cite{gronenschild2012effects, glatard2015reproducibility}.
 Images also typically include more dependencies than required, to make them
@@
 \textit{Can the amount of vulnerabilities be reduced by updating the images?}  
-For many reasons related to reproducibility and the lifecycle of research
-projects, container images deployed on HPC clusters often include outdated
-software. We report on the effect of software updates on the amount of
+\revision{To avoid breaking software dependencies and introducing numerical
+ perturbations, container images deployed on HPC clusters often include
+ outdated software}. We report
+on the effect of software updates on the amount of
 vulnerabilities found in images.
@@
 \href{https://github.com/quay/clair}{Clair} is an open-source and
-extensible vulnerability scanner for Docker and appc container images,
+extensible vulnerability scanner for Docker and \revision{OCI (Open Container Initiative)} container images,
 developed by CoreOS (now Container Linux), a Linux distribution to deploy
@@
 
-For CentOS images, Anchore and Clair give scanning results using Red Hat
+For CentOS images, Anchore and Clair \revision{report} scanning results using Red Hat
 Security Advisory (RHSA) identifiers, whereas Vuls uses the Common
@@
 
-Using this approach, we minified five Debian- or Ubuntu-based BIDS app images,
-using basic analysis examples found in the applications documentation.
+Image minification is a tedious operation\revision{, as it requires (1) creating
+relevant analysis examples and (2) running these examples in the container
+image}, to identify the packages required by the application. The
+resulting \revision{minified} container image is only valid for the examples selected
+in the minification process, as other executions might require a
+different set of packages.
+
+\revision{While the Boutiques specification allows developers to 
+specify analysis tests, we found that this feature was not consistently used in 
+the studied container images. Therefore, we relied on analysis examples found in the 
+documentation of the applications.   
+Using this approach, we minified five Debian- or Ubuntu-based BIDS app images.}
 
@@
 per image. Images s*,t*,u*,v*,w* and x* are Singularity images scanned by Stools and
-others are Docker images scanned using Anchore. \textbf{(B)} Effect of image minification and
+others are Docker images scanned using Anchore. \revision{High and critical vulnerabilities are 
+represented with the same solid color and critical vulnerabilities are reported between brackets.} \textbf{(B)} Effect of image minification and
 package update on 5 container images, showing that both techniques are
@@
  images (Fig~\ref{fig:vulnerabilities}-\textbf{A}), with an average of 460 vulnerabilities
-  per image and a median of 321. In comparison, no vulnerabilities were found in base
- Docker images \texttt{ubuntu:20.04} and \texttt{centos:7} after package
- update. Moreover, a significant fraction of detected vulnerabilities are
+  per image and a median of 321. Moreover, a significant fraction of detected vulnerabilities are
  of high severity
@@
  attackers could possibly exploit these vulnerabilities to execute
- arbitrary code in the container, by crafting responses to specific network
- requests. Images based on the Alpine distribution 
+ arbitrary code in the container \revision{or to store arbitrary files in the system}. 
+ \revision{For instance, vulnerability CVE-2019-3462 could lead to remote
+ code execution through human-in-the-middle attacks and vulnerability CVE-2018-1000802
+ could lead to arbitrary file injections in the filesystem through unfiltered Python user input.}
+ \revision{Among other consequences, remote code execution and injection of
+ arbitrary files could be leveraged to steal user credentials, to use CPU
+ cycles or storage space for illegitimate purposes, or to attempt
+ denial-of-service attacks against the system.}
+
+ Images based on the Alpine distribution 
  had the lowest numbers of vulnerabilities, but no significant difference
@@
 six of them could not be updated due to various issues with the package
-manager, and six of them are Singularity images that we didn't update.
+manager, and six of them are Singularity images that we did not update.
 % \change{3 out of these missing 6 images retured an error while updating which
@@
 % reached EOL and last one with CentOS 7.1.1503 returned libselinux conflicts with systemd} 
-In spite of the associated reproducibility challenges, updating
-packages therefore appears to be an efficient way to avoid vulnerabilities. It
+\revision{Software updates did not break the tested
+analyses in the remaining images. We did not investigate the potential consequences of image updates
+on numerical stability as it would require a full separate study. Updating}
+packages appears to be an efficient way to avoid vulnerabilities. It
 is not an ultimate solution though, as a substantial number of
@@
 \subsection{Effect of minification}
-
-Another approach to reduce the number of vulnerabilities involves deleting
-unnecessary packages from the container images. It is a tedious operation,
-as it requires running an actual data analysis in the container image, to
-identify the packages required by the application. In addition, the
-resulting container image is only valid for the specific type of analysis
-used in the minification process, as other executions might require a
-different set of packages.
 
@@
 and kernel headers reduced the number of vulnerabilities by an important fraction. 
+\revision{Minification did not create any errors in these images as all the
+dependencies were taken care of carefully. Common packages removed by the
+minification process were compilers, unused Python packages, and unused
+file compression utilities.}
 
@@
 vulnerabilities in container images is out of the scope of our study. We
-believe that such attacks are likely to exist, although attacking HPC
-systems through containers is challenging due to their relative isolation
-from the host system. First, under the assumption that legitimate HPC
+believe that such attacks are likely to exist \revision{given that critical vulnerabilities 
+allowing for arbitrary code execution or file injection were found.}
+Attacking HPC
+systems through containers remains challenging due to their relative isolation
+from the host system. Under the assumption that legitimate HPC
 users can be trusted, attackers would have to be remote to the container,
@@
 Several types of escalation attacks could be envisaged once remote
-attackers gain access to the container, in particular related to (1) using
-the resources allocated to the container for malicious use, such as storing
-data in the file system or using CPU cycles, resulting in denial of service
+attackers gain access to the container, in particular related to \revision{(1) stealing user credentials}, (2) using
+the resources allocated to the container for malicious use, resulting in denial of service
 for the user running the container and possibly for other HPC users, and
-(2) attacking a host network service, for instance a scheduler or a file
+(3) attacking a host network service, for instance a scheduler or a file
 system daemon. Exploits in the host kernel to break out of the container
@@
 
+\section{Availability of Data and Materials}
+
+The data and scripts used in this study are available in the GitHub repository at
+\url{https://github.com/big-data-lab-team/container-vulnerabilities-paper}
+with a Jupyter notebook to regenerate the figures. This manuscript is based on 
+version 0.1 of the repository, available as DOI \href{https://doi.org/10.5281/zenodo.4136599}{10.5281/zenodo.4136599}.
+
+\section{Competing interests}
+
+The authors declare that they have no competing interests.
+
 \bibliography{bibliography}

### 2021-03-01 paper.tex
Implemented reviewers comments

@@
 Software containers greatly facilitate the deployment and reproducibility
-of scientific data analyses, \revision{especially} on high-performance computing clusters
-(HPC). However, container images often contain outdated or unnecessary
-software packages, which increases the number of security vulnerabilities
-in the images and widens the attack surface of the infrastructure. This
-paper presents a vulnerability analysis of container images for scientific
-data analysis. We compare results obtained with four vulnerability
-scanners, focusing on the use case of neuroscience data analysis, and
-quantifying the effect of image update and minification on the number of
-vulnerabilities. We find that container images used for neuroscience data analysis
-contain hundreds of vulnerabilities, that software updates remove about two
-thirds of these vulnerabilities, and that removing unused packages is also
+of scientific data analyses \revision{in various platforms.} However,
+container images often contain outdated or unnecessary software packages,
+which increases the number of security vulnerabilities in the images,
+widens the attack surface \revision{in the container host, and creates
+substantial security risks for computing infrastructures at large}. This paper
+presents a vulnerability analysis of container images for scientific data
+analysis. We compare results obtained with four vulnerability scanners,
+focusing on the use case of neuroscience data analysis, and quantifying the
+effect of image update and minification on the number of vulnerabilities.
+We find that container images used for neuroscience data analysis contain
+hundreds of vulnerabilities, that software updates remove about two thirds
+of these vulnerabilities, and that removing unused packages is also
 effective. We conclude with recommendations on how to build container
@@
 Software containers have emerged has an efficient solution to deploy
-scientific data analyses, due
-to their portability, ease of use, and limited overhead. On HPC systems, the
-Singularity~\cite{kurtzer2017singularity} framework is often preferred to
-\href{http://docker.com}{Docker} due to its
-secure handling of multi-user environments and convenient support for
-Docker images. Singularity is now available in dozens of HPC
-clusters around the world and routinely used for Big Data analysis.
-
+scientific data analyses \revision{in various platforms}, due
+to their portability, ease of use, and limited overhead. 
 Taking advantage of core Linux kernel features such as namespaces, control
-groups and chroot, containers isolate processes from the host computer, and \revision{often can}
-control the memory, CPU, network and file-system resources assigned to
+groups\revision{,} and chroot, containers isolate processes from the host computer and \revision{often can}
+control the memory, CPU, network\revision{,} and file-system resources assigned to
 them. However, containers still share the kernel, mounted file systems and
@@
 concerns~\cite{martin2018docker, sultan2019container, combe2016docker} and
-opens the door to privilege escalation, denial of service, information leak
+opens the door to privilege escalation, denial of service, information leak\revision{,}
 and other types of attacks~\cite{gantikow2016providing}.
@@
 
+\revision{Scientific data analyses typically involve a range of computational 
+infrastructures, including personal workstations, lab servers, HPC clusters, 
+and cloud computing platforms. It is common for researchers to have access
+ to multiple systems through a combination of credentials and to migrate
+  analyses depending on their evolution. As a result, an attacker gaining 
+  access to one of these systems, possibly through a vulnerable container, 
+  might be able to compromise an extensive infrastructure and use it for malicious purposes.}
+
 In this study, we focus on the vulnerabilities present in container images
-deployed on HPC clusters for scientific data analysis, in particular in the
+\revision{used in} scientific data analysis, in particular in the
 neuroimaging domain. We address the following questions:
@@
 \textit{What is the current amount of vulnerabilities in
-container images deployed on HPC clusters?} Vulnerabilities are possible
-attack vectors that can seriously compromise the security of HPC clusters
+container images \revision{used in scientific analyses}?} Vulnerabilities are possible
+attack vectors that can seriously compromise the security of \revision{computing systems}
 and the integrity of user data. We report vulnerability scans produced
@@
 \revision{To avoid breaking software dependencies and introducing numerical
- perturbations, container images deployed on HPC clusters often include
+ perturbations, container images used in scientific analyses often include
  outdated software}. We report
@@
 provide a set of image creation guidelines for a more secure deployment of
-containers on HPC clusters.
+containers \revision{in scientific analyses}.
 
@@
 images is to update their packages to the latest version available in the OS
-distribution. To study the effect of such updates, we developed a script
+distribution. To study the effect of such updates, we \revision{created} a script
 (available
@@
 to remove unnecessary packages, an operation potentially specific to each
-analysis. We used the open-source \reprozip tool~\cite{rampin2016reprozip}
+analysis. \revision{Although vulnerabilities in unused packages could not
+be directly exploited when running the analysis provided by the container
+image, they still increase the risk of escalation attacks and should
+therefore be avoided.}
+
+We used the open-source \reprozip tool~\cite{rampin2016reprozip}
 to capture the list of packages used by an analysis. \reprozip first
@@
 review of software dependencies by application developers, to avoid
-unnecessary packages in container images. This is also an argument in favor of lightweight
-distributions such as Alpine. Compared to Ubuntu and Debian distributions,
+unnecessary packages in container images. Compared to Ubuntu and Debian distributions,
 CentOS images seem to have a lower number of vulnerabilities by package on
@@
 package (Fig~\ref{fig:vulnerabilities}-\textbf{D}, r=0.81,
-$p\textless10^{-7}$). Twelve container images are missing on this figure:
-six of them could not be updated due to various issues with the package
-manager, and six of them are Singularity images that we did not update.
-% \change{3 out of these missing 6 images retured an error while updating which
-% indicates a problem with the package installer, 2 were unable to update because they
-% reached EOL and last one with CentOS 7.1.1503 returned libselinux conflicts with systemd} 
+$p\textless10^{-7}$). Twelve container images are missing on this figure.
+Six of them are Singularity images that we did not update and six of them
+\revision{could not be updated by our script due to the following issues.
+One image was built from base Docker image CentOS 7.1.1503 that includes
+package \texttt{fakesystemd} conflicting with several other distribution
+packages: updating would require either updating the base image or swapping
+package \texttt{fakesystemd} for \texttt{systemd}. Three images were build
+from Ubuntu 17.04 or Debian 8 that reached end of life: updading would
+require changing the source list to make it point to old releases. Two
+images could not be updated because some files previously installed through
+the package manager were removed by other means, leading to failure of the
+update process.}
 \revision{Software updates did not break the tested
@@
 \revision{Minification did not create any errors in these images as all the
-dependencies were taken care of carefully. Common packages removed by the
+dependencies were taken care of properly. Common packages removed by the
 minification process were compilers, unused Python packages, and unused
@@
 
-% \begin{table*}
-% 	\csvreader[%
-% 	 tabular={|c|c|c|c|c|c|},
-% 		table head = \hline\textbf{Labels} &\textbf{{Image names}} & \textbf{Anchore} & \textbf{Clair} & \textbf{Vuls} & \textbf{Stools}\\\hline,
-% 		late after line= \\,
-% 			late after last line=\\\hline %
-% 		]{resul.csv}{labels=\labels,names=\names,A=\A,C=\C,V=\V,Stools=\Stools}%
-% 			{\labels & \names & \A & \C & \V & \Stools}
-% 		   \centering
-% 		\vspace*{1mm}
-% 		\caption{\label{table1}Number of vulnerabilities detected by the four scanners.
-Vuls shows \textit{no data} for images \texttt{bids/antscorticalthickness:v2.2.0-1} and \texttt{bids/afni\_proc:latest}
-% 		since their OS distributions reached end of life.} 
-% 	\end{table*}
 \begin{figure}
@@
 \end{figure}
-
-% In most cases,
-% Anchore reports more vulnerabilities than Vuls and Clair resulting in 
-% the Jaccard coefficient of 0.63 with Clair, 0.59 with Vuls,
-% whereas Vuls and Clair share more common vulnerability detection resulting to the Jaccard coefficient of 0.86.
-% Figure~\ref{fig:venn} represents the number of vulnerabilities reported by
-% the scanners in Docker images and the overlap between them.
-% This Figure also excludes two non-comparable images, which cannot be scanned with Vuls.
-% It is interesting to note that out of all reported vulnerabilities, 4453 vulnerabilities are only
-% reported by Anchore, 699 by Clair, and 536 by Vuls.}
-% \newline\\
-% As the number and type of vulnerabilities reported by the these scanners are significantly different from each other,
-% we desire to investigate the reasons behind these differences.
-% Following our investigation, we are able to explain some of the reasons behind
-% the differences. 
-% Such reasons were resulted from the way these scanners function or behave 
-% in particular, the following actions by the scanners are indicative:
-% \begin{itemize}
-%    \item scanners ignoring vulnerabilities in Linux-kernel-header packages,
-%    \item scanners referring to different vulnerability databases,
-%    \item different frequency of updating their databases,
-%    \item bugs in scanners. 
-% \end{itemize}
-
-% Below, we explain these reasons in further details and provide examples
-% for clear illustrations.
-
-% \textbf{Linux-kernel-headers:} Clair and Vuls ignore all vulnerabilities in the Linux-kernel-headers,
-% whereas Anchore reports all of them.
-% We find that 4443 out of 4453 vulnerabilities that are only reported by Anchore are present in Linux-kernel-headers.
-% For example, CVE-2019-9506 present in Linux-libc-dev-4.4.0-31.50, reported by Anchore, is not
-% detected by both Vuls and Clair.
-% Linux-kernel-headers are the header files that only provide function names, their parameters, and their
-% return types.
-% The actual source code of those functions is present in the Linux kernel and is not inside the image.
-% So, vulnerability detection in header files
-% is irrelevant in this case.
-
-% REGION (7)
-% \textbf{Ubuntu vulnerabilities with status as “Not-affected”:} Vuls reports vulnerabilities that have status
-% as "not-affected" in the Ubuntu database. It means that according to Ubuntu the image is not affected
-% by the particular vulnerability. In other words, Vuls reports vulnerabilities that it should not have been reported.
-% For example, when we scan an image having the Trusty release in it and Vuls reports CVE-2015-2305
-% in the package Cups. However, upon checking the Ubuntu vulnerability database, we find that package Cups in Trusty is not
-% affected by this vulnerability.
-
-% HOW ABOUT VULS?
-% \textbf{Ubuntu vulnerabilities with status as "Ignored (reached end-of-life)":}
-% Some vulnerabilities are ignored in Ubuntu 14.04 LTS as it reached end-of-life. 
-% However, in Ubuntu 14.04 ESM release, these vulnerabilities may or may not be present.
-% Anchore checks the last status of these vulnerabilities in LTS whether the package was vulnerable
-% prior to the end-of-life. Only if it was vulnerable, Anchore reports it, otherwise it does not.
-% If this kind of vulnerability is present in ESM release then Clair reports it because it
-% only refers to ESM release. On the other hand, if the vulnerability
-% status in ESM release is "DNE" (Does Not Exist), then Clair does not report it. 
-% For example, CVE-2017-9994 vulnerability in Libav package is ignored in Trusty LTS release due to its end-of-life.
-% Consequently, it is not reported by Anchore. This vulnerability has status as "DNE" in Trusty ESM
-% release so Clair also does not report it. As Ubuntu 14.04 LTS release is present inside the images,
-% Clair's referring to Ubuntu 14.04 ESM release vulnerability database is incorrect.
-
-% REGION (4)
-% \textbf{Vulnerabilities not present in Ubuntu 14.04 ESM release:} These vulnerabilities are not present in Ubuntu 14.04 ESM so they 
-% are not detected by Clair but they affect Ubuntu 14.04 LTS, and hence detected by Vuls and Anchore. The CVE-2017-13758 is an example
-% of such vulnerabilities.
-
-% CHECK THAT
-% \textbf{Misses:} Clair and Vuls
-% missed vulnerabilities that they should have detected. For example, the CVE-2016-9082 
-% is present in package Cairo in Xenial release and it is not detected by Clair.
-% Vuls also missed vulnerabilities such as CVE-2019-5094.
-
-% REGION (3)
-% \textbf{Wrong Detections:} 
-% Some vulnerabilities are not linked to Ubuntu 14.04 LTS which is 
-% present inside the image, however, Clair have reported such vulnerabilities.
-% For instance, CVE-2019-1274 is an example of such vulnerabilities. 
-% %is showing because these vulnerabilities are present in Ubuntu 14.04 ESM and 
-% %Clair is only referring to Ubuntu 14.04 ESM release. 
-% We reported this issue on two Google groups of Clair i.e. CoreOS Dev and
-% clair-dev \url{(https://groups.google.com/forum/\#!topic/clair-dev/8IqCCfd-EEc).}
-
-% \textbf{Database difference:} At the time we pulled Clair's database, through \texttt{arminc/clair-db:latest} Docker image, it was one week old.
-%                               As a result some vulnerabilities were not updated in the database. For instance, CVE-2019-5094, which
-% 		              was published on 2019-09-24, was not 
-% 		              updated in Clair's database. Due to which it is missed by Clair.
-% 			      Consequently, these discrepancies, even small, are sufficient to change the detection of
-% 			      the scanners.
-
-% REGION (6)
-% \textbf{Epoch bug:} There is a bug in the Anchore scanner due to which some vulnerabilities are 
-% 		not detected by Anchore. This bug gets triggered when a package’s version have epoch 
-% 		(1:3.3.9-1ubuntu2.3) in it. For example, CVE-2018-1125 in Procps package is not
-% 		detected by Anchore due to the presence of epoch in the Procps package version.
-% 		We reported this bug to the Anchore development team through their Slack channel.
-
-% \textbf{Ubuntu vulnerabilities with status "Ignored (out of standard support)" bug:} There is another bug in Anchore due to 
-% 		which it is not able to detect some vulnerabilities. Due to this bug, Anchore does not detect 
-% 		vulnerabilities that have a status as “ignored (out of standard support)” in Ubuntu 14.04 LTS. 
-% 		However, if this vulnerability is present in Ubuntu 14.04 ESM release, it is detected by Clair. 
-% 		For instance, CVE-2019-13565, which is present in Ubuntu 14.04 LTS, is an example of such vulnerabilities. 
-% 		We reported this bug as well to the Anchore development team through their Slack
-% 		channel.
-
-% \textbf{Rejected CVEs:} There are some CVEs, such as CVE-2017-13753, that are rejected because they are duplicate copies of other CVEs. 
-% 	So, Anchore and Clair does not report those rejected CVEs, but Vuls reports them.
-
-% \tristan{integrate this part:
-
-% \change{
-
-% The major discrepancies are shown by Anchore and Clair in Ubuntu \tristan{why?}. Both refers to Ubuntu CVE Tracker database for Ubuntu images.
-% The way in which both scanners interpret this database is different.
-% %
-% %There are different vulnerability databases, which have
-% %different formats of data.
-% %Out of which Open Vulnerability and Assessment Language (OVAL) is an international
-% %open standard and a common
-% %means of promoting publicly available security issues. 
-% %It provides details about software vulnerabilities. It helps to determine
-% %whether vulnerabilities exist in local machines or not. Apart from OVAL, operating system
-% %vendors also keep track of their vulnerabilities separately and assign
-% %a status to each vulnerability.
-% %For example, Ubuntu maintains
-% %Ubuntu CVE Tracker, Debian maintains Debian Security Bug Tracker, etc.
-% %Each vulnerability is assigned a unique Common Vulnerabilities and Exposures (CVE) number
-% %by the MITRE corporation, who maintains a list of all vulnerabilities of all distributions.
-% %In this paper, we use vulnerability and CVE interchangeably.
-% %Ubuntu CVE Tracker is used by Anchore and Clair in our experiments
-% %and there is discrepancies in the way both scanners interpret results.
-% %
-% %BIDS apps and Boutiques images in our experiments have four Linux
-% %distributions i.e. Ubuntu, CentOS, Debian, and Alpine. 
-% %Out of these distributions, Ubuntu assigns a vulnerability status to
-% %all vulnerabilities before keeping them in its vulnerability database.
-% %Each vulnerability is assigned a unique Common Vulnerabilities and Exposures (CVE) number
-% %by the MITRE corporation, who maintains a list of all vulnerabilities of all distributions.
-% %Ubuntu keeps a record of Ubuntu-specific vulnerabilities in Ubuntu CVE Tracker using their CVE
-% %numbers. In this paper, we use vulnerability and CVE interchangeably.
-% %The vulnerability status in Ubuntu CVE Tracker is subjected to change
-% %depending on the work progress to fix that vulnerability.
-% %
-% %Regarding Ubuntu, it has different
-% %types of releases e.g. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release.
-% %Ubuntu maintains its vulnerability data in Ubuntu CVE tracker, which is referred by Anchore and Clair.
-% %There is another vulnerability database i.e. Open Vulnerability and Assessment Language (OVAL) repository,
-% %which is maintained by MITRE corporation. Vuls refers to OVAL repository for getting Ubuntu vulnerability feed.
-% %The vulnerability data format of both databases is different. OVAL keeps a separate xml file for each release,
-% %which contains that release specific vulnerability information.
-% Ubuntu CVE Tracker keeps a separate file for each vulnerability, which
-% has an entry for all Ubuntu releases combined with the current status
-% of that vulnerability in that release.
-% In particular, Clair and Anchore show discrepancies for Ubuntu 14.04 which have
-% two entries for each vulnerability, one for Ubuntu 14.04 Long Term Support (LTS)
-% and second for Ubuntu 14.04 Extended Security Maintenance (ESM) release. As Ubuntu 14.04 LTS
-% reached end-of-life on 2019-04-30, so Ubuntu ignores new vulnerabilities in LTS release and
-% fix them only in ESM release. Consequently, a same vulnerability may have different vulnerability status in LTS and ESM releases,
-% which is causing discrepancies. This is because Anchore refers to Ubuntu 14.04 LTS, whereas Clair refers to
-% ESM.
-% %Further, in Ubuntu a particular release can be of different types i.e. Regular, Long Term Support (LTS), and Extended Security Maintenance (ESM) release. 
-% %Through our experiments, we find that Anchore and Clair report Ubuntu vulnerabilities 
-% %differently depending on either the different Ubuntu release type or vulnerability status. 
-% It is important to provide an overview of these Ubuntu vulnerability statuses, 
-% since Ubuntu is heavily utilized in our experiments. 
-% %Ubuntu's Regular release is supported only for 9 months, whereas LTS is supported for 5 years. Once LTS support
-% %reaches End-Of-Life (EOL), Ubuntu decides whether to provide extended security support or not, which comes
-% %in the form of ESM release.
-% %ESM is a paid service that can be requested from Ubuntu to get security 
-% %updates even after the EOL of a particular Ubuntu release. ESM and LTS releases of a particular Ubuntu version have different vulnerability
-% %databases, because after EOL of a release, a vulnerability is fixed only in packages of ESM; however, it still
-% %exists in LTS.
-% %
-% %As an example, Ubuntu has ended support for some releases, such as 14.04 LTS,
-% %17.04, and 17.10, as they reached EOL. However, Ubuntu decided to provide optional extended support for Ubuntu 14.04.
-% %To use this extended support, users have to purchase Ubuntu 14.04 ESM release.
-% %The images in our experiments have Ubuntu 14.04 LTS, so scanners should refer
-% %to LTS release only while collecting data from the vulnerability databases.
-% %More interestingly, Clair refers to ESM release vulnerability database, however, this may lead to discrepancies in results.
-% %Further, if an image is using a Linux release where EOL has been reached that image may
-% %turns to be vulnerable as it is not possible to retrieve any updates.
-% %
-% In Ubuntu CVE Tracker, for a vulnerability all Ubuntu releases are listed with the package name
-% in which that vulnerability exists and are entitled a vulnerability status
-% (\url{https://git.launchpad.net/ubuntu-cve-tracker/plain/README}), which is
-% encoded in the following form:
-% \newline \\
-% \noindent <release>\_<source-package>: <status> (<version/notes>)
-% \newline\\
-% The <version/notes> given with a vulnerability status provide more
-% information about the vulnerability.
-% For a given release, the vulnerability status can be any one of the following:
-
-% \textbf{DNE (Does Not Exist):} The package does not exist in the
-% 		release.
-
-% \textbf{needs-triage:} The vulnerability of this package
-% 		is not known, and hence evaluation is needed.
-
-% \textbf{not-affected:} The package, while related to the
-% 		vulnerability in some way, is not affected by the issue.
-% 	%	The <notes> should
-% 	%	provide detailed information, if needed.
-% 		%For instance, if the given
-% 		%status is "not-affected (1.14.6-1.1)" then this indicates that this specific
-% 		%package version is not affected.
-
-% \textbf{needed:} The package is vulnerable and needs to be fixed.
-
-% \textbf{active:} The package is vulnerable, needs fixing, and is 
-%                  actively being worked on.
-
-% \textbf{ignored:} The package, while related to the
-% 		vulnerability in some way, is being ignored for some reason. 
-% 	%	The
-% 	%	<notes> should provide that reason.
-% 	%	For instance, if status looks like
-% 	%	"ignored (reached end-of-life)", this means that the given Ubuntu release already reached
-% 	%	end-of-life, so this CVE is ignored by Ubuntu. However, if there
-% 	%	is extended security support for this release then this
-% 	%	CVE will be handled in ESM release.
-
-% \textbf{pending:} The package is vulnerable and
-%                   has been fixed but an update has not been yet uploaded or
-% 		  published.
-% 		 % The <version> is given to indicate the particular 
-% 		 % version where the fix has been done.
-
-% \textbf{deferred:} The package is vulnerable, but 
-%                    its fix has been deferred for some reason. 
-% 		  % The <notes>
-% 		  % should provide further details.
-% 		  % If a date is mentioned, e.g.
-% 		  % "deferred (2015-02-02)", the given date specifies the date when
-% 		  % the CVE was deferred.
-
-% \textbf{released:} The package was vulnerable, but
-% 		an update has been already uploaded and published.
-% 	%	e.g. "released (1.2.3)",
-% 	%	<version> indicates the first version where the fix was applied.
-
-% \textbf{released-esm:} The package was vulnerable and
-% 		an update has been already uploaded and published. However,
-% 		this update is published in the Ubuntu ESM release only and not in LTS.}
-% 		%The fixed version of such packages is appended by either
-% 		%+esm or \char`\~esm, indicating that this package version is available
-% 		%only via ESM.
-
-% 		% \newlne\\
-% % Figure~\ref{example} illustrates how the information of a vulnerability is represented
-% % in the Ubuntu CVE Tracker.
-
-% % \begin{figure}[!ht]
-% % 	\fbox{{\includegraphics[scale=2.5,width=\columnwidth]
-% % 	{Figures/vulnExample2.png}}}
-% %         \caption{\label{example} Representation of a vulnerability in Ubuntu CVE Tracker}
-% % \end{figure}
-% % \vspace*{-7mm}
-% }
 
@@
 believe that this position is not viable from an IT security perspective,
-and that it could endanger the entire Big Data processing infrastructure,
-starting with the HPC centers. Instead, we advocate a more systematic
+and that it could endanger the entire Big Data processing infrastructure.
+ Instead, we advocate a more systematic
 analysis of the numerical schemes involved in data analyses, which, coupled
@@
 format conversion, while the same functionality might be available in the
-existing dependencies of the pipeline, albeit in a less convenient way.
-\item \emph{Use lightweight base images such as Alpine Linux}. Base
-images often come with packages that are useful in personal computers or
-servers, but not in containers dedicated to a specific data analysis. In
-addition, lightweight distributions define packages with a fine
-granularity, allowing developers to avoid installing unnecessary
-dependencies. For instance, the compressed size of the Alpine Linux base
-image on DockerHub is only 2.7~MB while that of the Ubuntu base image is
-27~MB.
+existing dependencies of the pipeline, albeit in a less convenient way. \revision{Some package managers such as \texttt{apt} also 
+support ``weak'' package dependencies that are recommended but not necessarily required for installation. Installation of such suggested packages 
+can be avoided using specific options of the package manager (\texttt{--no-install-recommends} in the case of \texttt{apt}).}
+\revision{Using lightweight base OS images such as Alpine Linux can also reduce the number of unnecessary dependencies. 
+However, developers should ensure that this doesn't lead to installing 
+extra dependencies without using the package manager, as mentioned in point (iv) below.}
+
+\revision{\item \emph{Minify container images.} \revision{Minifying container images 
+is another way to reduce software dependencies. However,} the automated minification
+process that we used in our study is unwieldy for a routine use, as it
+requires capturing execution traces with ReproZip to reconstruct the graph
+of package dependencies required for the analysis. In practice, it would be
+more practical for software developers to identify and remove unnecessary
+dependencies when they build containers, based on their knowledge of the
+application.}
+
 \item \emph{Use OS releases with long-term support.} Security updates are
@@
 release every 3-5 years and provide maintenance for 10 years. Similarly,
-Ubuntu LTS (long-term support) distributions provide free security updates
-for 5 years, and Debian stable releases are maintained for 3 years. 
-% Commercial
-% offers for extended maintenance periods are common. 
-\item \emph{Install packages, not files}. Vulnerability scanners such as
-Anchore, Clair or Vuls detect vulnerabilities from the list of packages
-installed in a container image. Therefore, vulnerabilities contained in
-software tools installed through direct file download rather than through
-the package manager would go completely undetected. Domain-specific
-distributions such as \href{http://neuro.debian.net}{NeuroDebian} or
+Ubuntu \revision{and Debian} LTS (long-term support) distributions provide security updates
+for \revision{at least} 5 years.
+
+\item \emph{Install packages, not files}. \revision{Regardless of their support status, base OS distributions 
+covered by the previous recommendation rarely include 
+scientific software. Since 
+ vulnerability scanners detect vulnerabilities from the list of installed packages}, vulnerabilities contained in
+\revision{files installed without the package manger remain undetected.} \revision{To reduce such occurrences, scientific software 
+should as much as possible be linked dynamically against libraries provided by the base OS distribution. The use of} domain-specific
+\revision{repositories} such as \href{http://neuro.debian.net}{NeuroDebian} or
 \href{https://docs.fedoraproject.org/en-US/neurofedora/overview/}{NeuroFedora}
-in neuroimaging are useful in this respect.
-\item \emph{Minify container images.} The automated minification
-process that we used in our study is unwieldy for a routine use, as it
-requires capturing execution traces with ReproZip to reconstruct the graph
-of package dependencies required for the analysis. In practice, it would be
-more practical for software developers to identify and remove unnecessary
-dependencies when they build containers, based on their knowledge of the
-application.
+in neuroimaging \revision{is also} useful in this respect\revision{, as
+these distributions facilitate transparent software updates and might be covered by image scanners in the future}.
+
 \item \emph{Run image scanners during continuous integration.} Scanning
@@
 CI also allows developers to identify vulnerabilities quickly,
-before new software versions are released.
+before new software versions are released. \revision{The Anchore documentation includes
+specific instructions on how to do so at \url{https://anchore.com/cicd}. The Stools repository also includes 
+a \href{https://github.com/singularityhub/stools-clair/blob/master/.travis.yml}{Travis CI file}
+that can be reused for this purpose.}
 \end{enumerate}
 
-Describing specific attacks against HPC systems that would exploit
+Describing specific attacks that would exploit
 vulnerabilities in container images is out of the scope of our study. We
@@
 allowing for arbitrary code execution or file injection were found.}
-Attacking HPC
+Attacking
 systems through containers remains challenging due to their relative isolation
-from the host system. Under the assumption that legitimate HPC
-users can be trusted, attackers would have to be remote to the container,
+from the host system. Under the assumption that \revision{container host}
+users can be trusted, attackers would have to be remote,
 either in the same network or on a remote network. Two main types of
@@
 attackers gain access to the container, in particular related to \revision{(1) stealing user credentials}, (2) using
-the resources allocated to the container for malicious use, resulting in denial of service
-for the user running the container and possibly for other HPC users, and
-(3) attacking a host network service, for instance a scheduler or a file
+the resources allocated to the container for malicious use, resulting in denial of service, and
+(3) attacking a host network service, for instance \revision{a locally-accessible server} or a file
 system daemon. Exploits in the host kernel to break out of the container
@@
 
-Most container images deployed on HPC clusters for scientific data analyses
+Most container images \revision{used in} scientific data analyses
 contain hundreds of security vulnerabilities, many of which are critical.
 In the short term, application software developers can address this issue
-by: (1) minifying container images, by using lightweight OS distributions
-and reducing software dependencies, and (2) applying regular security
+by: (1) reducing software dependencies, and (2) applying regular security
 updates, which requires using OS distributions with long-term support.
@@
 
-This conclusion is not an alarming message urging HPC administrators  
+This conclusion is not an alarming message urging \revision{system} administrators  
 to ban containers from their systems. User-controlled container images are

### 2021-03-15 paper.tex
Updated DOI
Editor revision

@@
 \definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
-\newcommand{\revision}[1]{\color{ao(english)}#1\color{black}\xspace}
+\newcommand{\revision}[1]{#1\xspace} %\color{ao(english)}#1\color{black}\xspace}
 
@@
 
-The data and scripts used in this study are available in the GitHub repository at
-\url{https://github.com/big-data-lab-team/container-vulnerabilities-paper}
-with a Jupyter notebook to regenerate the figures. This manuscript is based on 
-version 0.1 of the repository, available as DOI \href{https://doi.org/10.5281/zenodo.4136599}{10.5281/zenodo.4136599}.
+The data and scripts used in this study are available on GitHub
+with a Jupyter notebook to regenerate the figures:
+\begin{enumerate}
+\item Project name: container-vulnerabilities-paper
+\item Project home page:\\ \url{https://github.com/big-data-lab-team/container-vulnerabilities-paper}
+\item Operating system: Platform independent
+\item Programming language: Python
+\item Other requirements: Jupyter >= 1.0.0, Matplotlib >= 3.3.0, NumPy >= 1.19.1, Pandas >=1.0.5, SciPy >= 1.6.0
+\item License: GNU General Public License v3.0
+\end{enumerate}
+
+\section{Availability of Supporting Data}
+
+Kaur B; Dugré M; Hanna A; Glatard T: Supporting data for ``An Analysis of
+Security Vulnerabilities in Container Images for Scientific Data Analysis"
+GigaScience Database. 2021. \url{http://dx.doi.org/10.5524/100880}
 
